### 2021-02-03 marine/STEP1_species_groups/STEP1_species_groups.Rmd
set up the aquaculture mapping repo

---
title: "Exploring FAO aquaculture data"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(here)
library(countrycode)

source(here('aquaculture/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files

```

```{r}

fao <- read_csv("/home/shares/food-systems/Food_footprint/_raw_data/FAO_aquaculture/v_2020/FAO_GlobalAquacultureProduction_Quantity_1950_2018.csv")

fao <- fao %>%
  rename(country = `Country (Country)`,
         species = `ASFIS species (ASFIS species)`, 
         fao_major_area = `FAO major fishing area (FAO major fishing area)`, 
         environment = `Environment (Environment)`) %>%
  dplyr::select(-Unit)
table(fao$environment)  
## convert to long format and clean FAO codes:
fao <- fao %>%
  gather(key="year", value="value", -country, -species, -fao_major_area, -environment) %>%
    fao_clean_data() %>%
  filter(year >= 2010) %>%
  group_by(country, species, fao_major_area, environment) %>%
  mutate(total_harvest = sum(value, na.rm=TRUE)) %>%
  filter(total_harvest > 0) %>% # data is cut if country/species/major area hasn't been harvested since 2010
  dplyr::select(-total_harvest) %>%
  ungroup()

## convert to iso3c codes
fao <- fao %>% 
  filter(!country == "Totals") %>%  ## filter out "totals" rows
  filter(!is.na(species)) %>%  ## filter out "totals" rows
  mutate(country = ifelse(country == "R\xe9union", "Reunion", country)) %>%
  filter(!country %in% c("Yugoslavia SFR", "Un. Sov. Soc. Rep.")) %>%  # these countries no longer exist  
  mutate(country = ifelse(country=='Zanzibar', "Tanzania", country)) %>%  #semiautonomous region of Tanzania
  mutate(country = ifelse(country=="Eswatini", "Swaziland", country)) %>%  # also goes by this name
  mar_split() %>%   # fixes channel islands, breaks into Guernsey and Jersey
  mutate(iso3c = countrycode(country, "country.name", "iso3c"))
## make sure no NAs:
table(fao$iso3c)
## save
write.csv(fao, here("aquaculture/data/fao_mariculture_clean.csv"), row.names=FALSE)

```

## explore freshwater
```{r}

fao <- read_csv("aquaculture/data/fao_mariculture_clean.csv")

fw <- fao %>%
  dplyr::filter(environment == "Freshwater") %>%
  group_by(species) %>%
  summarize(total = sum(value)) %>%
  ungroup() %>%
  arrange(total)

data.frame(fw)

write.csv(fw, "aquaculture/marine/STEP1_species_groups/int/fw_spp.csv", row.names = FALSE)

```

## explore marine
```{r}

marine <- fao %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  group_by(species) %>%
  summarize(total = sum(value)) %>%
  ungroup() %>%
  arrange(total)

data.frame(marine)

## 323 different species

# emissions <- read_csv("aquaculture/data/emissions_aquaculture.csv")
# unique(emissions$`Scientific Name`)
## 32 different species

fao_marine <- fao %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in list of species from OHI so that we can add higher taxonomic classifications
mar_sp_list <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2020/gh-pages/globalprep/mar/v2020/raw/species_list.csv")

fao_marine_fw_not_included <- fao_marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
  dplyr::select(-exclude, -alias) %>%
  dplyr::filter(str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver"))

fao_marine_clean <- fao_marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
  dplyr::select(-exclude, -alias) %>%
  dplyr::filter(!str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver"),
                Taxon_code != "AL",
                species != "Red oyas",
                species != "Jellyfishes nei") ## delete freshwater, catfish species, seaweeds, jellyfish..
```

Classify species into aquaculture groups 
```{r}
# Need to classify into these groups: 
#  - Bivalves
#  - Tuna
#  - Salmonids
#  - Shrimps and Prawns
#  - crustaceans
#  - marine fish general

## Make a dataframe of each unique species to hand check what category they should fall into
check <- fao_marine_clean %>%
  distinct(species, Taxon_code)

##  Salmonids : "It includes salmon, trout, chars, freshwater whitefishes, and graylings, which collectively are known as the salmonids."
## Safe to classify trout in the same category as salmon: "Farmed steelhead trout also is rainbow trout, but it is farmed in saltwater netpens in the same manner as Atlantic salmon in countries"
## Safe to classify Char in same category as salmon.
## Octopus : use offshore floating sea cages for production and fed bycatch - lump with marine fish - general
## All of those classified as BI will be Bivalves
## CRUST - classified as bivalves
## GAST - classify as bivalves
## sea cucumber - classify as bivalve
## Sandfish == sea cucumber = bivalve
## Tunicates - Use longlines as aquaculture practice - Oysters also use longline - classify these as bivalves 
## Urchins - classify as bivalve
## SH classified as Shrimp
## crabs and lobsters classified as crustaceans

## filter for salmon, char, trout and reclassify to aquaculture group = salmonids
salmon_list <- fao_marine_clean %>%
  dplyr::filter(str_detect(species, "almon|char|rout|European whitefish")) %>% ## filter for salmon, trout, and char
  dplyr::mutate(aq_group = "salmonids")

## filter for Taxon_codes GAST, INV, CRUST, TUN, URCH, NS-INV (sea cucumbers/sandfish), BI  and reclassify to aquaculture group = bivalves
bivalve_list <- fao_marine_clean %>%
  dplyr::filter(Taxon_code %in% c("TUN", "URCH", "NS-INV", "BI", "GAST", "INV")) %>% ## filter for tunicates, urchins, invertebrates, bivalves and gastropods
  dplyr::mutate(aq_group = "bivalves")

## filter for Taxon_code == SH and classify as aquaculture group shrimps_prawns
shrimps_list <- fao_marine_clean %>%
  dplyr::filter(Taxon_code == "SH"|
                str_detect(species, "Metapenaeus shrimps nei")) %>%
  dplyr::mutate(aq_group = "shrimps_prawns")

crustacean_list <- fao_marine_clean %>%
  dplyr::filter(Taxon_code == "CRUST") %>%
  dplyr::mutate(aq_group = "crustaceans")

tuna_list <- fao_marine_clean %>%
  dplyr::filter(str_detect(species, "tuna")) %>%
  dplyr::mutate(aq_group = "tuna")

## Filter out all other lists and classify the rest as marine_fish
marine_fish_list <- fao_marine_clean %>%
  dplyr::filter(species %notin% c(shrimps_list$species, bivalve_list$species, salmon_list$species, crustacean_list$species, tuna_list$species)) %>%
  dplyr::mutate(aq_group = "marine_fish_general")

## combine them all together again 
aquaculture_groups <- rbind(salmon_list, bivalve_list, shrimps_list, marine_fish_list, crustacean_list, tuna_list)

## write it out
write.csv(aquaculture_groups, "aquaculture/marine/STEP1_species_groups/int/marine_groups.csv", row.names = FALSE)

aq_groups <- read.csv("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv")

fao_1 <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  left_join(aq_groups) %>%
  dplyr::filter(year == 2017,
                !is.na(value),
                !is.na(aq_group)) %>%
  dplyr::filter(value >= 500) %>%
  group_by(aq_group, country, species, year) %>%
  summarise(tonnes = sum(value)) %>%
  ungroup() %>%
  # dplyr::filter(tonnes >= 500) %>%
  group_by(country, aq_group, year) %>%
  summarise(total_tonnes = sum(tonnes)) %>%
  arrange(aq_group)

write.csv(fao_1, "aquaculture/marine/STEP1_species_groups/int/tonnes_per_country_group.csv", row.names = FALSE)

test <- fao_1 %>%
  dplyr::filter(aq_group == "bivalves")
sum(test$total_tonnes) # 17439040

test <- fao_1 %>%
  dplyr::filter(aq_group == "shrimps_prawns")
sum(test$total_tonnes) # 5094133

```

### 2021-02-03 marine/bivalve/bivalve_disturbance/bivalve_disturbance.Rmd
set up the aquaculture mapping repo

---
title: "Bivalve disturbance"
author: "Gage Clawson (NCEAS, OHI, UCSB)"
date: "12/29/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in libaries and paths}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(raster)
library(data.table)
library(raster)
library(rgdal)
library(here)
library(taxize)

path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve"

food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

Bivalve specifications:

 - 100 long lines in each km2 
 - each line 4000 meters of rope (13000 feet)
 - each foot of line has 100 bivalves

Which means 130000000 bivalves per km2

We assuming that the rearing time is about 1 year, so no lost bivalves. What is reported is the actual tonnage.

## Estimate number bivalves/tonne production at family level

Using the information in this paper, table 1: https://www.researchgate.net/publication/259436886_Weight_-_Length_relationships_of_25_bivalve_species_Mollusca_Bivalvia_from_the_Algarve_coastsouthern_Portugal

First I need to put the information in table 1 into an excel sheet (do this manually and upload to aurora). I will add a "family_2" column, for the families which do not match our data. It will be the family in our data that is closest in relation (i.e. in the same super family, or the same order)

I will do the same thing with this paper, using table 1 and table 2: http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.825.2317&rep=rep1&type=pdf

We will also use information for oyster species from here (Ostreidae): **be sure to include this as a reference in the supplementary info**

Assume this number for all Ostreidae, regardless of if they are pacific cupped or not (pacific cupped is the most common in our data). 
http://www.ccpo.odu.edu/~klinck/Reprints/PDF/kobayashiAqua1997.pdf
http://www.ccpo.odu.edu/~klinck/Reprints/PDF/kobayashiAqua1997.pdf
Pacific Oyster

Assume live-weight estimates: From Figure 4a

L = 21.4*W^0.377

W = 0.000295836*L^2.563

1. For each species, use their equation and parameter estimates to calculate # bivalves/tonne
2. Average these values at the family level
3. Calculate an average that you can use to gapfill families not included in these studies

```{r}
#### GASPAR (first paper)
## read in the Weight and Length data and wrangle 
gaspar <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/gaspar_bivalve/gaspar_bivalve_WL.csv"))

unique(gaspar$family)

## now lets wrangle a bit, to get family, avg alpga, avg beta

# filter for those that have a "family_2" and get those averages
gaspar_fam_2 <- gaspar %>%
  dplyr::filter(!is.na(family_2)) %>%
  group_by(family_2) %>%
  summarise(alpha = mean(alpha),
            beta = mean(beta)) %>%
  dplyr::rename("family" = "family_2")

# get averages for those that have na for family_2
gaspar_fam <- gaspar %>%
  dplyr::filter(is.na(family_2)) %>%
  group_by(family) %>%
  summarise(alpha = mean(alpha),
            beta = mean(beta))

## bind together and get averages for families
gaspar_final <- rbind(gaspar_fam, gaspar_fam_2) %>%
  group_by(family) %>%
  summarise(alpha = mean(alpha), 
            beta = mean(beta))

#### Park (second paper)

park <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/park_and_oh_bivalve_WL/park_and_oh_bivalve_WL.csv"))

park_final <- park %>%
  group_by(family) %>%
  summarise(alpha = mean(alpha), 
            beta = mean(beta))

## third paper for oysters
koboyashi_final <- data.frame(family = "Ostreidae", alpha = 0.000295836, beta = 2.563)

## combine them all

bivalve_w_l_final <- rbind(park_final, gaspar_final, koboyashi_final) %>%
  group_by(family) %>%
  dplyr::summarise(alpha = mean(alpha), 
            beta = mean(beta))

write.csv(bivalve_w_l_final, file.path("aquaculture/marine/bivalve/bivalve_disturbance/data/weight_length_relationships.csv"), row.names = FALSE)

```

## Convert FAO tonnes of production to number of bivalves
Use FAO mariculture production data for bivalves

1. assign each bivalve to a family
2. merge with paper data by family to add in the number bivalves per tonne production, gapfill missing family data with average (assume an average bivalve length of 4cm (40 mm))
3. Calculate number of bivalves for each taxa/country by dividing tonnes production by number bivalves per tonne 
4. Calculate the number of bivalves for each country (group by country and summarize)
5. Distribute the number of bivalves across the raster based on country and proportion of production for each raster cell
6. Apply model to each raster cell to estimate area:  number bivalves / 130,000,000 bivalves per km2

```{r}
# read in spp specific country bivalve data: 
bivalve_spp <- read_csv(file.path("aquaculture/marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"))

## read in family information
spp_families <- read_csv(file.path("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(species, family) %>%
  distinct()

## left join
bivalve_spp_family <- bivalve_spp %>%
  left_join(spp_families) %>%
  mutate(family = ifelse(species == "Australian mussel", "Mytilidae", family)) %>% ## fix a mistake
  mutate(family = ifelse(species == "Sea snails", "Haliotidae", family)) ## fix mistake (sea snails from fao likely mean abalone)

summary(bivalve_spp_family) ## check to see there are no NAs in family - there aren't

```

Now compare our families in the weight-length data with our fao data

```{r}
sort(unique(bivalve_spp_family$family))

sort(unique(bivalve_w_l_final$family))

sort(setdiff(bivalve_spp_family$family, bivalve_w_l_final$family))

sort(setdiff(bivalve_w_l_final$family, bivalve_spp_family$family))
```

Now do steps 1-6 listed above 
```{r}
# bivalve_w_l_fix <- bivalve_w_l_final %>%
#   dplyr::filter(!(family %in% c("Donacidae", "Phasianellidae", "Solenidae")))

avg_alpha <- mean(bivalve_w_l_final$alpha)
avg_beta <- mean(bivalve_w_l_final$beta)

# avg_alpha_fix <- mean(bivalve_w_l_fix$alpha)
# avg_beta_fix <- mean(bivalve_w_l_fix$beta)

## join them together 
fao_W_L_explore <- bivalve_spp_family %>%
  left_join(bivalve_w_l_final, by = "family") %>%
  dplyr::mutate(weight = alpha*40**beta) %>% ## assume 40 mm 
  group_by(family) %>%
  summarise(weight = mean(weight),
            number_rows = n(),
            total_tonnes = sum(fao_tonnes_production))

## join them and gapfill the missing rows with the average
fao_W_L <- bivalve_spp_family %>%
  left_join(bivalve_w_l_final, by = "family") %>%
  mutate(alpha = ifelse(is.na(alpha), avg_alpha, alpha),
         beta = ifelse(is.na(beta), avg_beta, beta))

## group by family and country to get tonnes
fao_W_L_summarise <- fao_W_L %>%
  dplyr::group_by(country, iso3c, year, family) %>%
  dplyr::summarise(fao_tonnes_production = sum(fao_tonnes_production),
                   alpha = mean(alpha),
                   beta = mean(beta))

## figure out number of bivalves per country

bivalve_per_country <- fao_W_L_summarise %>%
  dplyr::mutate(bivalve_avg_weight_g = alpha*40**beta) %>%
  dplyr::mutate(bivalve_avg_weight_t = bivalve_avg_weight_g/1000000) %>%
  dplyr::mutate(n_bivalves = fao_tonnes_production/bivalve_avg_weight_t) %>%
  group_by(country, iso3c, year) %>%
  dplyr::summarise(fao_tonnes_production = sum(fao_tonnes_production),
                   total_bivalves = sum(n_bivalves),
                   avg_weight = mean(bivalve_avg_weight_t))

## fix HKG and CHN 
CHN_HKG_biv <- bivalve_per_country %>%
  dplyr::filter((iso3c %in% c("CHN", "HKG")))

sum(CHN_HKG_biv$fao_tonnes_production) # 14646903
chn_bivalves <- sum(CHN_HKG_biv$total_bivalves)

CHN_fix <- data.frame(country = "China", iso3c = "CHN/MAC/HKG", year = 2017, fao_tonnes_production = 14646903, total_bivalves = chn_bivalves)

bivalve_per_country_final <- bivalve_per_country %>%
  dplyr::filter(!(iso3c %in% c("CHN", "HKG"))) %>%
  rbind(CHN_fix) %>%
  dplyr::select(country, iso3c, year, total_bivalves)

# 1. stack with the region raster and covert to data.frame.  merge with the dataframe that will convert the ID_0 values to iso3c. 
# 2.  group-by(iso3c), mutate(country_tonnes = sum(tonnes, na.rm=tRUE)), rowwise(), mutate(prop_cell = tonnes/country_tonnes)
# 3.  Then you merge the country count of bivalves to the raster data and multiply by prop_cell.
# 4. This will give you the estimated number of bivalves in each cell
# 5. Apply space model to raster

## read in production csv
production <- read_csv(file.path(path_prep, "bivalve_farm.csv"))
sum(production$tonnes_production)

iso3c_codes <- read_csv(file.path("_spatial/_output/eez_food_rgns.csv"))

land_eez_region_raster <- raster("/home/shares/food-systems/Food_footprint/dataprep/spatial/land_eez_rgns.tif")

land_eez_region_raster_df <- as.data.frame(land_eez_region_raster, xy = TRUE)

region_raster_iso3c_df <- land_eez_region_raster_df %>%
  left_join(iso3c_codes, by = c("land_eez_rgns" = "ID_0"))

production_cell_iso3c <- production %>%
  left_join(region_raster_iso3c_df, by = c("x", "y")) %>%
  group_by(iso3c) %>%
  mutate(country_tonnes = sum(tonnes_production, na.rm = TRUE)) %>%
  rowwise() %>%
  mutate(prop_cell = tonnes_production/country_tonnes) %>%
  dplyr::mutate(prop_cell = ifelse(prop_cell == "NaN", NA, prop_cell)) %>%
  ungroup()

biv_per_cell <- production_cell_iso3c %>%
  left_join(bivalve_per_country_final, by = "iso3c") %>%
  mutate(bivalves_per_cell = total_bivalves*prop_cell)

sum(biv_per_cell$bivalves_per_cell, na.rm = TRUE) # 3.801619e+12

sum(bivalve_per_country_final$total_bivalves) # 3.801619e+12

## apply our disturbance model
biv_disturbance <- biv_per_cell %>%
  dplyr::mutate(disturbance_km2 = bivalves_per_cell/130000000) %>%
  dplyr::select(x, y, disturbance_km2)

sum(biv_disturbance$disturbance_km2, na.rm = TRUE) 
# 29243.22 km2 disturbance
# 17435623 tonnes production bivalve
# tonnes/disturbance = 596.2279

## compare to salmon: 
# 70.82 km2 disturbance
# 2746086 tonnes produciton salmon
# tonnes/disturbance = 38775.57

# 412 times bigger disturbance for bivalves
# ~ 6 times bigger production for bivalves

## compare to tuna:
#  2.817567 km2 disturbance
# 37072.56 tonnes production tuna
# tonnes/disturbance = 13157.65

# 10378.89 times bigger disturbance for bivalves
# 470 times bigger production for bivalves

## Now multiply the disturbance by 0.1, since bivalve aquaculture likely actually creates more habitat than it disturbs.

biv_disturbance <- biv_disturbance %>%
  dplyr::mutate(disturbance_km2 = disturbance_km2*0.1)

sum(biv_disturbance$disturbance_km2, na.rm = TRUE) # 2924.322
# 2924.322 km2 disturbance
# 17435623 tonnes production bivalve
# tonnes/disturbance = 5962.279

## compare to salmon: 
# 70.82 km2 disturbance
# 2746086 tonnes produciton salmon
# tonnes/disturbance = 38775.57

# 41.29232 times bigger disturbance for bivalves
# ~ 6 times bigger production for bivalves

## compare to tuna:
#  2.817567 km2 disturbance
# 37072.56 tonnes production tuna
# tonnes/disturbance = 13157.65

# 1037.889 times bigger disturbance for bivalves
# 470 times bigger production for bivalves
write.csv(biv_disturbance, file.path(path_prep, "bivalve_disturbance.csv"), row.names = FALSE)

# final_layer_dist <- read_csv(file.path(path_prep, "bivalve_disturbance.csv"))

final_rast <- rasterFromXYZ(biv_disturbance, crs = food_crs)
crs(final_rast)
plot(final_rast)
cellStats(final_rast, "sum") # 2924.322
final_rast

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 2924.322
final_rast
plot(log(final_rast+1))

writeRaster(final_rast, file.path(path_final, "marine_bivalve_aquaculture_meat_disturbance.tif"), overwrite = TRUE)

```

### 2021-02-03 marine/crustaceans/crustacean_disturbance/crustacean_disturbance.Rmd
set up the aquaculture mapping repo

---
title: "Crustacean disturbance"
author: "Gage Clawson (NCEAS, OHI, UCSB)"
date: "01/07/2021"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in libaries and paths, eval = FALSE, include = FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(raster)
library(data.table)
library(raster)
library(rgdal)
library(here)

path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/"

food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

For this disturbance, I will focus primarily on mud/swamp crabs, as they are primarily the species produced in this category (aside from a little bit of spiny lobster production).

I was able to find this nifty manual on mud crab aquaculture from the FAO, which basically outlines all of the information we need for disturbance.

http://www.fao.org/3/ba0110e/ba0110e.pdf

**Design**: "The basic design of most earthen ponds used to culture mud crabs (Figure 8.1) is
the same as that used to culture marine shrimp"

**Stocking density and survival rate:** "Compared with penaeid crustacean, mud crabs are stocked at relatively low densities (0.5–1.5 crabs/m2) with survival rates as high as 67 percent."

**Assumptions:**

Source: http://www.fao.org/3/ba0110e/ba0110e.pdf
Note: We will use the same pond dimensions (other than stocking density), as crustacean. The paper states that mud crab earthen ponds are the same as shrimp farms, and sometimes even switch between crab and shrimp farmings.

stocking density = 0.5 - 1.5 crabs/m2: assume 1.5 crabs/m2

area: 1 - 10 hectares per pond : assume 10 hectare ponds

average weight of a crab at harvest: 400 - 427 g: assume 415 g : Taken from this paper, which does some sampling of mud crab growth in aquaculture: https://www.hatcheryfm.com/article-files/file_1326756685_2.pdf

**Conversions:**

$ stocking \ density = \frac{1.5 \ crabs}{m^2} \ *  \frac{415 \ g }{1 \ crab} \ * \ \frac{1 \ kg}{1000 \ g}   = \frac{0.6225 kg}{m^2} $

$ area = 0.10\  km^2 = 100000 \ m^2 $

Steps:

1. calculate occupancy as total number of crabs. There is a 67% survival rate in earthen ponds, which means 33% don't survive... meaning there are 33% more actually occupying the ponds than is reported in the production:
   $live \ tonnes = FAO \ production \ raster * 1.33 $

2. calculate kg/pond:
   $ area \ m^2 * stocking\  density \frac{kg}{m^2} = kg/pond $

3. Calculate number of cages:
   $ \frac{Live \ weight \ (kg)}{kg / pond} = ponds$

4. calculate surface area disturbance,  Pond area will be 0.1 km2. We will also account for infrastructure (drainage canals, buildings, etc), and increase the size by 50% based on figures shown in the FAO shrimp aquaculture report:

  $ disturbance \ (km^2) = ponds*area per pond*1.5 $

## Method

Establish the necessary parameters from above
```{r parameters}

stocking_density = (1.5*415)/1000
pond_area_km2 = 0.1
pond_area_m2 = 100000

```

###Calculate the total number of fish in the water (occupancy)
Read in production map

```{r}
production_raster <- rasterFromXYZ(read_csv(paste0(path_prep, "crustaceans_farm.csv")), crs = food_crs)

#plot(production_raster)
cellStats(production_raster, stat = "sum") # 401719.1

```

```{r calculate crustacean occupancy}
# Assume all kg are live weight 
# as live weight of crustacean, in kg
crustacean_live_kg  <- (production_raster*1000)*1.33 # multiply by 1.33 to increase the total tonnes by 33% (67% survival rate). This means this is the actual amount of crab weight that is in the ponds 
crustacean_live_tonnes  <- production_raster*1.33

cellStats(crustacean_live_kg, "sum") # 534286390
cellStats(crustacean_live_tonnes, "sum") # 534286.4

401719.1*0.33 # 132567.3

132567.3 + 401719.1 # 534286.4
```

### Calculate the total area (from an aerial view) used for crustacean aquaculture

First we determine how many ponds are required given pond dimensions, stocking densities, and kg living crabs.

We used FAO data to estimate ~ 62250 kg crustacean (harvest weight) per pond.

This is based on ~100000 m2 pond.  We assume a stocking density of 0.013 kg/m2

```{r}

kg_per_pond <- pond_area_m2*stocking_density
t_per_pond <- kg_per_pond/1000
# check
(534286.4/t_per_pond)/4 # ~ 2145.729 ponds, if harvest happens 4 times a year

```

Given the kg of crustacean per cell we determine the number of ponds needed as:

We round this value up to the nearest whole number.

```{r}

ponds <- ceiling(crustacean_live_kg/kg_per_pond)
cellStats(ponds, "sum") # 8630

```

2. We the determine how much surface area the ponds disturb, and area for infrastructure.

We will assume a 50% increase in area for infrastructure (buildings, drain/supply canals, etc.).

Justification: 
Cage dimensions of 200 by 500 m2 seems reasonable based on figures. http://www.fao.org/3/ac210e/AC210E05.htm#ch5 (chapter 5 pond figures)

Then increase by 20 on all edges, so 240 * 540 = ~130000

So that is 30%, but then there is additional buildings, and I am sure there is disturbance beyond the canals…etc

```{r}
pond_disturbance_m2 <- pond_area_m2*1.5

total_disturbance_km2 <- (ponds * pond_disturbance_m2)/1000000
total_disturbance_prop <- total_disturbance_km2/raster::area(total_disturbance_km2)
plot(total_disturbance_prop)
plot(total_disturbance_km2)

crustacean_aquaculture_area_df <- as.data.frame(total_disturbance_prop, xy=TRUE) %>% 
  dplyr::rename(crustacean_disturbance_prop = layer )

write_csv(crustacean_aquaculture_area_df, file.path(path_prep, "crustacean_disturbance_prop.csv"))

crustacean_aquaculture_area_df_km2 <- as.data.frame(total_disturbance_km2, xy = TRUE) %>%
  dplyr::rename(crustacean_disturbance_km2 = layer)

write_csv(crustacean_aquaculture_area_df_km2, file.path(path_prep, "crustacean_disturbance_km2.csv"))

## save to datalayers folder with the correct naming conventions: 
final_layer_dist <- read_csv(file.path(path_prep, "crustacean_disturbance_km2.csv"))

final_rast <- rasterFromXYZ(final_layer_dist, crs = food_crs)
crs(final_rast)
plot(final_rast)
plot(log(final_rast + 1))
cellStats(final_rast, "sum") # 1294.5
final_rast
cellStats(production_raster, "sum") # 401719.1

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 1294.5
final_rast
plot(log(final_rast+1))

writeRaster(final_rast, file.path(path_final, "marine_crustaceans_aquaculture_meat_disturbance.tif"), overwrite = TRUE)
```

```{r}
philippines <- raster::crop(total_disturbance_km2, extent(115, 130, 5, 20))
plot(philippines)

viet <- raster::crop(total_disturbance_km2, extent(100, 110, 7, 25))
plot(viet)

```

### 2021-02-03 marine/crustaceans/crustacean_nutrient/step1_nutrient.Rmd
set up the aquaculture mapping repo

---
title: "crustacean_nutrient_pollution"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/22/2020"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

This markdown uses models and species specific parameters from the paper *Aquaculture Production is a Large, Spatially Concentrated Source of Nutrients in Chinese Freshwater and Coastal Seas* (2020 Wang et al).

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

production <- read_csv(file.path(path_prep, "crustaceans_farm.csv"))
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

crustacean N/P pollution values

N: 57 kg/tonne of growth
P: 9.2 kg/tonne of growth

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P value
3. We report in total excess nutrients (N + P): Sum the N and P kg.
4. We report in tonnes, so divide by 1000. We will also so individual N and P rasters for reporting purposes.

```{r}

crustacean_pollution <- production %>%
  dplyr::mutate(prod_growth = tonnes_production*0.95) %>%
  dplyr::mutate(prod_growth_N_poll = prod_growth*57,
                prod_growth_P_poll = prod_growth*9.2) %>% ## in kg pollution now
  # dplyr::mutate(PO4eq_kg = prod_growth_N_poll*0.42 + prod_growth_P_poll*3.07) %>% Don't do this anymore (01/14/2021)
  dplyr::mutate(total_N_P_kg = prod_growth_N_poll + prod_growth_P_poll) %>%
  dplyr::mutate(total_N_P_t = total_N_P_kg/1000,
                N_poll_t = prod_growth_N_poll/1000, 
                P_poll_t = prod_growth_P_poll/1000) %>%
  dplyr::select(x, y, total_N_P_t, N_poll_t, P_poll_t)

sum(crustacean_pollution$total_N_P_t) # 25264.11
sum(production$tonnes_production) # 401719.1

## save to dataprep folder with the correct naming conventions: 
write.csv(crustacean_pollution, file.path(path_prep, "crustacean_nutrient.csv"))

## Save total N P raster
total_df <- crustacean_pollution %>% 
  dplyr::select(x, y, total_N_P_t)

final_rast <- rasterFromXYZ(total_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 25264.11

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 25264.11
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_final, "marine_crustaceans_aquaculture_meat_nutrient.tif"), overwrite = T)

## Save total N raster
total_df <- crustacean_pollution %>% 
  dplyr::select(x, y, N_poll_t)

final_rast <- rasterFromXYZ(total_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 21753.09

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 21753.09
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_crustaceans_aquaculture_meat_nutrientN.tif"), overwrite = T)

## Save total P raster
total_df <- crustacean_pollution %>% 
  dplyr::select(x, y, P_poll_t)

final_rast <- rasterFromXYZ(total_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 3511.025

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 3511.025
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_crustaceans_aquaculture_meat_nutrientP.tif"), overwrite = T)
```

### 2021-02-03 marine/marine_fish_general/finfish_nutrient/step1_nutrient.Rmd
set up the aquaculture mapping repo

---
title: "marine_fish_general_nutrient_pollution"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: 12/22/2020
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

This markdown uses models and species specific parameters from the paper *Hindcasts and Future Projections of Global Inland and Coastal Nitrogen and Phosphorus Loads Due to Finfish Aquaculture* (2013 Bouwman et al)

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

production <- read_csv(file.path(path_prep, "marine_fish_general_farm.csv"))
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

Because we have multiple values and species for nutrient pollution for general marine fish, we will have to do this analysis in a series of steps. Workflow will follow these rules:

1. Apply the general pelagic species pollution numbers to areas with those species
2. Any remaining species apply the regional values for Asia and Europe
3. Any remaining species or areas that don't fall in the above steps, take the average of the Asia and Europe nutrient pollution values.

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P value
3. We report in total excess nutrient: add N and P together.
4. We report in tonnes, so divide by 1000. Save N tonnes, P tonnes, and N + P tonnes layers.

**Numbers for each category:** 
Other finfish - pelagics:  Amberjacks, nei, Cobia, Japanese amberjacks
N = 152, P = 25	P assumes

Other finfish - coastal, Europe: 
N = 80, P =	16

Other finfish - coastal, Asia:
N = 112, P = 18

```{r}
fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon
species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
finfish_list <- species_list$species[species_list$aq_group=="marine_fish_general"]
finfish_list

## write out shrimp taxa and production for Juliette
fao_finfish_taxa_prod <- fao %>%
  filter(species %in% finfish_list) %>%
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

## set up lists of different regions
asia <- c("BGD", "CHN", "HKG", "IDN", "IND", "JPN", "KHM", "KOR", "MYS", "PHL", "SGP", "THA", "TWN", "VNM")

europe <- c("ALB", "HRV", "CYP", "FRA", "GRC", "ITA", "MLT", "NOR", "PRT", "ESP", "TUR")

other <- c("AUS", "CRI", "EGY", "IRN", "ISR", "MUS", "MEX", "PAN", "SAU", "TUN", "ARE", "USA")

## Now we need to get the proportion of catch that falls into each species category (i.e. pelagic or non-pelagic) 
prop_df <- fao_finfish_taxa_prod %>%
  dplyr::mutate(species_cat = ifelse(str_detect(species, "obia|mberjack|Marine fishes nei"), "pelagic", "non_pelagic")) %>%
  group_by(iso3c, species_cat) %>%
  summarise(tonnes = sum(fao_tonnes_production)) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(total_tonnes = sum(tonnes)) %>%
  ungroup()

prop_pel_df <- prop_df %>%
  dplyr::filter(species_cat == "pelagic") %>%
  dplyr::mutate(prop_pelagic = tonnes/total_tonnes) %>%
  dplyr::mutate(prop_non_pelagic = 1-prop_pelagic) %>%
  dplyr::select(iso3c, prop_pelagic, prop_non_pelagic, total_tonnes) %>%
  dplyr::filter(prop_pelagic == 1)

prop_non_pel_df <- prop_df %>%
  dplyr::filter(species_cat == "non_pelagic") %>%
  dplyr::mutate(prop_non_pelagic = tonnes/total_tonnes) %>%
  dplyr::mutate(prop_pelagic = 1-prop_non_pelagic) %>%
  dplyr::select(iso3c, prop_pelagic, prop_non_pelagic, total_tonnes)

prop_total_iso3c <- rbind(prop_pel_df, prop_non_pel_df) ## rbind them

sum(prop_total_iso3c$total_tonnes) # 3901214
sum(fao_finfish_taxa_prod$fao_tonnes_production) # 3901214

## Read in production data 
production_sf <- st_read(file.path("/home/sgclawson/github/food_systems/aquaculture/marine/marine_fish_general/finfish_nutrient/prod_data_by_cell_iso3c.shp")) %>%
  dplyr::rename("tonnes_per_farm" = "tnns_p_")

## join with our proportion data so that we can get tonnes of pelagic and tonnes of non-pelagic per farm 
production_spp_props <- production_sf %>%
  left_join(prop_total_iso3c, by = "iso3c") %>%
  dplyr::mutate(tonnes_pelagic = prop_pelagic*tonnes_per_farm, 
                tonnes_non_pelagic = prop_non_pelagic*tonnes_per_farm)

## Now we can do the actual analysis outlined above

nutrient_data <- production_spp_props %>%
  dplyr::mutate(tonnes_pelagic_growth = tonnes_pelagic*0.95,
                tonnes_non_pelagic_growth = tonnes_non_pelagic*0.95) %>%   ## multiply by 0.95 to correct for growth outside seapen

  dplyr::mutate(N_poll_pel = tonnes_pelagic_growth*152,
                P_poll_pel = tonnes_pelagic_growth*25,
                N_poll_non_pel = case_when(
                  iso3c %in% asia ~ tonnes_non_pelagic_growth*112,
                  iso3c %in% europe ~ tonnes_non_pelagic_growth*80,
                  iso3c %in% other ~ tonnes_non_pelagic_growth*96
                ),
                P_poll_non_pel = case_when(
                  iso3c %in% asia ~ tonnes_non_pelagic_growth*18,
                  iso3c %in% europe ~ tonnes_non_pelagic_growth*16,
                  iso3c %in% other ~ tonnes_non_pelagic_growth*17
                )) %>%  ## get all of out pollution values by species group and region

  dplyr::mutate(N_poll = N_poll_pel + N_poll_non_pel,
                P_poll = P_poll_pel + P_poll_non_pel) %>% ## get total pollution values for each cell in kg

  # dplyr::mutate(po4eq_kg = N_poll*0.42 + P_poll*3.07) %>% ## get po4eq: cut this (01/14/2021)

  dplyr::mutate(total_N_P_t = (N_poll + P_poll)/1000,
                N_poll_t = N_poll/1000, 
                P_poll_t = P_poll/1000) %>%
  dplyr::select(total_N_P_t, N_poll_t, P_poll_t, geometry)

sum(nutrient_data$total_N_P_t) # 507965.9

## Save final N+P layer
finfish_raster_check <- rasterize(nutrient_data, food_raster, field = "total_N_P_t", fun=sum)
plot(log(finfish_raster_check+1))
cellStats(finfish_raster_check, stat = "sum", na.rm = TRUE) # 507965.9

finfish_raster <- rasterize(nutrient_data, food_raster, field = "total_N_P_t", fun=sum, background=0)
plot(log(finfish_raster+1))

finfish_raster_df <- as.data.frame(finfish_raster, xy=TRUE) %>%
  dplyr::select(x,y, N_P_tonnes=layer)

cellStats(finfish_raster, stat = "sum") # 507965.9
sum(finfish_raster_df$N_P_tonnes) # 507965.9
sum(nutrient_data$total_N_P_t, na.rm = TRUE) # 507965.9

## save to dataprep folder with the correct naming conventions: 
write.csv(finfish_raster_df, file.path(path_prep, "marine_fish_general_nutrient.csv"))

final_rast <- rasterFromXYZ(finfish_raster_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 507965.9

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 507965.9
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_final, "marine_marine-fish-general_aquaculture_meat_nutrient.tif"), overwrite = T)

## Save final N layer
finfish_raster_check <- rasterize(nutrient_data, food_raster, field = "N_poll_t", fun=sum)
plot(log(finfish_raster_check+1))
cellStats(finfish_raster_check, stat = "sum", na.rm = TRUE) # 435852.5

finfish_raster <- rasterize(nutrient_data, food_raster, field = "N_poll_t", fun=sum, background=0)
plot(log(finfish_raster+1))

finfish_raster_df <- as.data.frame(finfish_raster, xy=TRUE) %>%
  dplyr::select(x,y, N_tonnes=layer)

cellStats(finfish_raster, stat = "sum") # 435852.5
sum(finfish_raster_df$N_tonnes) # 435852.5
sum(nutrient_data$N_poll_t, na.rm = TRUE) # 435852.5

## save to dataprep folder with the correct naming conventions: 
write.csv(finfish_raster_df, file.path(path_prep, "marine_fish_general_nutrient_N.csv"))

final_rast <- rasterFromXYZ(finfish_raster_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 435852.5

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 435852.5
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_marine-fish-general_aquaculture_meat_nutrientN.tif"), overwrite = T)

## Save final P layer
finfish_raster_check <- rasterize(nutrient_data, food_raster, field = "P_poll_t", fun=sum)
plot(log(finfish_raster_check+1))
cellStats(finfish_raster_check, stat = "sum", na.rm = TRUE) # 72113.4

finfish_raster <- rasterize(nutrient_data, food_raster, field = "P_poll_t", fun=sum, background=0)
plot(log(finfish_raster+1))

finfish_raster_df <- as.data.frame(finfish_raster, xy=TRUE) %>%
  dplyr::select(x,y, P_tonnes=layer)

cellStats(finfish_raster, stat = "sum") # 72113.4
sum(finfish_raster_df$P_tonnes) # 72113.4
sum(nutrient_data$P_poll_t, na.rm = TRUE) # 72113.4

## save to dataprep folder with the correct naming conventions: 
write.csv(finfish_raster_df, file.path(path_prep, "marine_fish_general_nutrient_P.csv"))

final_rast <- rasterFromXYZ(finfish_raster_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 72113.4

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 72113.4
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_marine-fish-general_aquaculture_meat_nutrientP.tif"), overwrite = T)
```

### 2021-02-03 marine/salmon/salmon_disturbance/STEP2_occupancy_distribution.Rmd
set up the aquaculture mapping repo

---
title: "occupancy_distribution"
author: "Juliette Verstaen"
date: "1/24/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in libaries and paths}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(raster)
library(data.table)
library(raster)
library(rgdal)
library(here)

path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/"

food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

In this markdown we are calculating:

1. How many live fish are in the water at a given time.
2. The total volume (and area) used by salmon farming

##Methods

##Conversion Table
Read in and save the necessary values from the salmon conversion table
```{r parameters from conversion table}
salmon_conversion <- read_csv(here("aquaculture/marine/salmon/salmon_disturbance/data/salmon_conversion_factors.csv"))

stocking_density <- as.numeric(salmon_conversion[salmon_conversion$name == "stocking_density", "value"])
live_harvested_conversion <- as.numeric(salmon_conversion[salmon_conversion$name == "live_harvested", "value"])
harvest_weight <- as.numeric(salmon_conversion[salmon_conversion$name == "mean_harvest_weight", "value"])
cage_volume <- as.numeric(salmon_conversion[salmon_conversion$name == "cage_volume", "value"])
```

###Calculate the total number of fish in the water (occupancy)
Read in production map

```{r}
production_raster <- rasterFromXYZ(read_csv(paste0(path_prep, "salmon_farm.csv")), crs = food_crs)

#plot(production_raster)
cellStats(production_raster, stat = "sum") # 2746086

```

```{r calculate salmon occupancy}
#as total number of salmon
salmon_occupancy <- (production_raster*1000)/harvest_weight * live_harvested_conversion
writeRaster(salmon_occupancy, file.path(path_prep, "salmon_occupancy/salmon_occupancy.tif"), format = "GTiff", overwrite = TRUE)

# as live weight of salmon, in kg
salmon_live_kg  <- salmon_occupancy*harvest_weight
salmon_live_tonnes  <- salmon_occupancy*harvest_weight/1000

writeRaster(salmon_live_tonnes, file.path(path_prep, "salmon_occupancy/salmon_live_tonnes.tif"), format = "GTiff", overwrite = TRUE)
```

### Calculate the total area (from an aerial view) used for salmon aquaculture

First we determine how many cages are required given cage dimensions, stocking densities, and kg living fish.

We used Gentry 2017 data to estimate 180,000 kg salmon (harvest weight) per cage.

This is based on 9000 m3 cage that we assume to be circular with a depth of 10 m.  We assume a stocking density of 20kg/m3.

```{r}

kg_per_cage <- cage_volume*stocking_density

```

Given the kg of salmon per cell we determine the number of cages needed as:

kg_salmon/180,000

We round this value up to the nearest whole number and multiply by 1.3 to include fallowing cages.

```{r}

cages <- ceiling(salmon_live_kg/kg_per_cage)

cages_pls_fallow <- ceiling(cages * 1.3)

```

2. We the determine how much surface area the cages disturb including the inner cage area, a 5 meter buffer around the cage, and area for infrastructure.

```{r}
cage_depth_m <- 10
buffer <- 5
infrastructure <- 1.5 #50% of area to infrastructure

cage_area <- cage_volume/cage_depth_m
cage_radius <- sqrt(cage_area/pi)
cage_radius_buffer <- cage_radius + buffer
cage_area_with_buffer <- pi*cage_radius_buffer^2
cage_disturbance_m2 <- cage_area_with_buffer*infrastructure

total_disturbance_km2 <- cages_pls_fallow * cage_disturbance_m2/1000000
total_disturbance_prop <- total_disturbance_km2/raster::area(total_disturbance_km2)
plot(total_disturbance_prop)

salmon_aquaculture_area_df <- as.data.frame(total_disturbance_prop, xy=TRUE) %>% 
  dplyr::rename(salmon_disturbance_prop = layer )

write_csv(salmon_aquaculture_area_df, file.path(path_prep, "salmon_disturbance_prop.csv"))

salmon_aquaculture_area_df_km2 <- as.data.frame(total_disturbance_km2, xy=TRUE) %>% 
  dplyr::rename(salmon_disturbance_km2 = layer)

write_csv(salmon_aquaculture_area_df_km2, file.path(path_prep, "salmon_disturbance_km2.csv"))

## save to datalayers folder with the correct naming conventions: 
final_layer_dist <- read_csv(file.path(path_prep, "salmon_disturbance_km2.csv"))

final_rast <- rasterFromXYZ(final_layer_dist, crs = food_crs)
crs(final_rast)
plot(final_rast)
cellStats(final_rast, "sum") # 70.82137
final_rast

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 70.82137
final_rast

writeRaster(final_rast, file.path(path_final, "marine_salmon_aquaculture_meat_disturbance.tif"), overwrite = TRUE)
```

Look at the pieces more closely
```{r}
norway <- raster::crop(total_disturbance_km2, extent(-25, 50, 50, 75))
plot(norway)
writeRaster(norway, file.path(path_prep, "salmon_occupancy/norway.tif"), overwrite=TRUE)

chile <- raster::crop(total_disturbance_km2, extent(-80, -60, -60, -35))
plot(chile)
writeRaster(chile, file.path(path_prep, "salmon_occupancy/chile.tiff"), overwrite=TRUE)

```

### 2021-02-03 marine/shrimp/shimp_nutrient/step1_nutrient.Rmd
set up the aquaculture mapping repo

---
title: "shrimp_nutrient_pollution"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/22/2020"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

This markdown uses models and species specific parameters from the paper *Aquaculture Production is a Large, Spatially Concentrated Source of Nutrients in Chinese Freshwater and Coastal Seas* (2020 Wang et al)

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"
path_pre <- "/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers"

production <- read_csv(file.path(path_prep, "shrimp_farm.csv"))
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

shrimp N/P pollution values

N: 57 kg/tonne of growth
P: 9.2 kg/tonne of growth

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P value
3. We report in total excess nutrients: Sum the N and P values.
4. We report in tonnes, so divide by 1000.

```{r}

shrimp_pollution <- production %>%
  dplyr::mutate(prod_growth = tonnes_production*0.95) %>%
  dplyr::mutate(prod_growth_N_poll = prod_growth*57,
                prod_growth_P_poll = prod_growth*9.2) %>% ## in kg pollution now
  # dplyr::mutate(PO4eq_kg = prod_growth_N_poll*0.42 + prod_growth_P_poll*3.07) %>% cut (01/14/2021)
  dplyr::mutate(N_P_tonnes = (prod_growth_N_poll + prod_growth_P_poll)/1000,
                N_tonnes = prod_growth_N_poll/1000,
                P_tonnes = prod_growth_P_poll/1000) %>%
  dplyr::select(x, y, N_P_tonnes, N_tonnes, P_tonnes)

sum(shrimp_pollution$N_P_tonnes) # 320370
sum(production$tonnes_production) # 5094133

## save to dataprep folder with the correct naming conventions: 
write.csv(shrimp_pollution, file.path(path_prep, "shrimp_nutrient.csv"))

## save N + P layer
N_P_df <- shrimp_pollution %>%
  dplyr::select(x,y, N_P_tonnes)

final_rast <- rasterFromXYZ(N_P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 320370

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 320370
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_final, "marine_shrimp_aquaculture_meat_nutrient.tif"), overwrite = T)

## save N layer
N_df <- shrimp_pollution %>%
  dplyr::select(x,y, N_tonnes)

final_rast <- rasterFromXYZ(N_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 275847.3

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 275847.3
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_pre, "marine_shrimp_aquaculture_meat_nutrientN.tif"), overwrite = T)

## save P layer
P_df <- shrimp_pollution %>%
  dplyr::select(x,y, P_tonnes)

final_rast <- rasterFromXYZ(P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 44522.72

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 44522.72
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_pre, "marine_shrimp_aquaculture_meat_nutrientP.tif"), overwrite = T)

```

### 2021-02-03 marine/shrimp/shrimp_disturbance/shrimp_disturbance.Rmd
set up the aquaculture mapping repo

---
title: "Shrimp disturbance"
author: "Gage Clawson (NCEAS, OHI, UCSB)"
date: "01/05/2021"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in libaries and paths, eval = FALSE, include = FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(raster)
library(data.table)
library(raster)
library(rgdal)
library(here)

path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/"

food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

Assumptions:

Source: http://www.fao.org/3/ac210e/AC210E02.htm#ch2

**Assuming Traditional or extensive culture**

stocking density = 3000-5000 fry per hectare: assume 4000 fry per hectare

area: 1 - 10 hectares per pond : assume 10 hectare ponds

minimum depth of 1 m: assume 1 m depth (no indication of maximum depth, but I don't think we need this anyways, since we have the area already?)

marketable size: 30 pieces/kg : Assuming that all "fry" grow into marketable size pieces

Conversions:

$ stocking \ density = \frac{400000 \ fry}{km2} \ *  \frac{1 kg }{30 \ pieces\ (or fry)} = \frac{13333.33 kg}{km^2} = \frac{0.0133 kg}{m^2} $

$ area = 0.10\  km^2 = 100000 \ m^2 $

Steps:

1. calculate kg/cage:
   $ area \ m^2 * stocking\  density \frac{kg}{m^2} = kg/cage $
2. Calculate number of cages:
   $ \frac{FAO \ production \ raster \ (kg)}{kg / cage} = cages$

3. calculate surface area disturbance, assume ponds lie next to each other, with no buffer. Cage area will be 0.1 km2:

  $ disturbance \ (km^2) = cages*area $

## Method

Establish the necessary parameters from above
```{r parameters}

stocking_density = (400000/30)/1000000
pond_area_km2 = 0.1
pond_area_m2 = 100000

```

###Calculate the total number of fish in the water (occupancy)
Read in production map

```{r}
production_raster <- rasterFromXYZ(read_csv(paste0(path_prep, "shrimp_farm.csv")), crs = food_crs)

#plot(production_raster)
cellStats(production_raster, stat = "sum") # 5094133

```

```{r calculate shrimp occupancy}
# Assume all kg are live weight 
# as live weight of shrimp, in kg
shrimp_live_kg  <- production_raster*1000
shrimp_live_tonnes  <- production_raster

cellStats(shrimp_live_kg, "sum") # 5094133080
```

### Calculate the total area (from an aerial view) used for shrimp aquaculture

First we determine how many ponds are required given pond dimensions, stocking densities, and kg living fish.

We used FAO data to estimate ~1333 kg shrimp (harvest weight) per pond.

This is based on ~100000 m2 pond.  We assume a stocking density of 0.013 kg/m2

```{r}

kg_per_pond <- pond_area_m2*stocking_density
t_per_pond <- kg_per_pond/1000

# check
(5094133/t_per_pond)/4 # ~ 955150 if harvest happens 4 times a year

5094133080/kg_per_pond # 3820600

```

Given the kg of shrimp per cell we determine the number of ponds needed as:

We round this value up to the nearest whole number.

```{r}

ponds <- ceiling(shrimp_live_kg/kg_per_pond)
cellStats(ponds, "sum") # 3820910

```

2. We the determine how much surface area the ponds disturb, and area for infrastructure.

We will assume a 1.5 increase in area for infrastructure (buildings, drain/supply canals, etc.).

Justification: 
Cage dimensions of 200 by 500 m2 seems reasonable based on figures. http://www.fao.org/3/ac210e/AC210E05.htm#ch5 (chapter 5 pond figures)

Then increase by 20 on all edges, so 240 * 540 = ~130000

So that is 30%, but then there is additional buildings, and I am sure there is disturbance beyond the canals…etc

```{r}
pond_disturbance_m2 <- pond_area_m2*1.5

total_disturbance_km2 <- (ponds * pond_disturbance_m2)/1000000
total_disturbance_prop <- total_disturbance_km2/raster::area(total_disturbance_km2)
plot(total_disturbance_prop)
plot(total_disturbance_km2)

shrimp_aquaculture_area_df <- as.data.frame(total_disturbance_prop, xy=TRUE) %>% 
  dplyr::rename(shrimp_disturbance_prop = layer )

write_csv(shrimp_aquaculture_area_df, file.path(path_prep, "shrimp_disturbance_prop.csv"))

shrimp_aquaculture_area_df_km2 <- as.data.frame(total_disturbance_km2, xy = TRUE) %>%
  dplyr::rename(shrimp_disturbance_km2 = layer)

write_csv(shrimp_aquaculture_area_df_km2, file.path(path_prep, "shrimp_disturbance_km2.csv"))

## save to datalayers folder with the correct naming conventions: 
final_layer_dist <- read_csv(file.path(path_prep, "shrimp_disturbance_km2.csv"))

final_rast <- rasterFromXYZ(final_layer_dist, crs = food_crs)
crs(final_rast)
plot(final_rast)
plot(log(final_rast + 1))
cellStats(final_rast, "sum") # 573136.5
final_rast
cellStats(production_raster, "sum") # 5094133

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 573136.5
final_rast

writeRaster(final_rast, file.path(path_final, "marine_shrimp_aquaculture_meat_disturbance.tif"), overwrite = TRUE)
```

```{r}
philippines <- raster::crop(total_disturbance_km2, extent(115, 130, 5, 20))
plot(philippines)

indo <- raster::crop(total_disturbance_km2, extent(95, 140, -15, 5))
plot(indo)

sri <- raster::crop(total_disturbance_km2, extent(79, 82, 6, 10))
plot(sri)
```

### 2021-02-03 marine/tuna/tuna_ghg/STEP1_ghg_emissions.Rmd
set up the aquaculture mapping repo

---
title: "Tuna: Aquaculture GHG"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Script Description

This markdown calculates the GHG emissions from general tuna aquaculture.

# Data information
We used [Seafood Carbon Emissions Tool data](http://seafoodco2.dal.ca/) to extract ghg emissions associated with carcass weight of tuna from tuna farming.

One factor that we added was aquatic N<sub>2</sub>O emissions as discussed in [Hu *et al*., 2012](https://pubs.acs.org/doi/full/10.1021/es300110x) and [MacLoid *et al*., 2019](http://www.fao.org/3/ca7130en/ca7130en.pdf).

# Methods 
 - Take midpoint of ghg low and ghg high from [seafood carbon emissions tool data](http://seafoodco2.dal.ca/) for all tuna species
 - Multiply by % energy (to cut out the feed emissions)
 - Add the N20 value from the MacLeod paper to the emissions intensity estimate we got for tuna
 - Multiply emissions intensity estimate by tonnes of production in each cell

# Preamble
```{r setup, include = FALSE}
# getting packages we want
library(tidyverse)
library(here)
library(raster)
library(sf)
library(janitor)

# Raster templates
source(here("_spatial/template_raster.R"))

# File paths
raw   <- "/home/shares/food-systems/Food_footprint/_raw_data/"
prep_tuna <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna"
prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/" 
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

# Import master_rgns xy df
master_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))
```

## Import
```{r}
## Read in farmed emissions data

farmed_emissions <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/seafood_carbon_emmisions_tool/d2020/Specie_List_-_11_24_2020,_11_39_21_AM_Farmed.csv")) %>%
  clean_names()

tuna_production <- read_csv(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm.csv"))

fao_tuna_spp <- read_csv(here("aquaculture/marine/tuna/tuna_farms/data/fao_mariculture_tuna_taxa_production.csv"))

```

# Wrangle

```{r}
unique(sort(fao_tuna_spp$species))
# [1] "Atlantic bluefin tuna" "Pacific bluefin tuna"  "Southern bluefin tuna"

unique(sort(farmed_emissions$common_name))
## we only want tunas that are in fao
 #  Emissions spp   -   FAO spp
 ###############################################
# "Atlantic bluefin tuna" - "Atlantic bluefin tuna"
# "Pacific bluefin tuna" - Pacific bluefin tuna
# "Southern bluefin tuna" - Southern bluefin tuna

## Filter for the appropriate species... also filter for "Marine net pen"... since we don't want any inland aquaculture
tuna_emissions_spp <- farmed_emissions %>%
  dplyr::filter(common_name %in% c("Atlantic bluefin tuna", "Pacific bluefin tuna", "Southern bluefin tuna"))

## multiply the ghg low and ghg high by the percent energy
## take the mean of new ghg low and high (the 25th and 75th quantiles)
tuna_emissions <- tuna_emissions_spp %>%
  dplyr::mutate(ghg_low_energy = ghg_low*(percent_energy/100),
                ghg_high_energy = ghg_high*(percent_energy/100)) %>%
  rowwise() %>%
  dplyr::mutate(ghg_kgCO2_kg_fish_mean = mean(c(ghg_low_energy, ghg_high_energy)))

ghg_kgCO2_kg_fish <- mean(tuna_emissions$ghg_kgCO2_kg_fish_mean)

## now multiply by the percent of that which is energy emissions (100%)
ghg_energy_kgCO2_kg_fish <- ghg_kgCO2_kg_fish # *1 ##   0.172 kg CO2eq/ kg fish (live/carcass weight, ratioed)

# Adding Aquatic N2O
# From MacLeod et al. 
# "The amount of N2O per species-group was determined by multiplying the
# production by the N2O emission factor per kg of production (Hu et al., 2012), i.e.
# 1.69 gN2O-N per kg of production, or 0.791 kgCO2e/kgLW production. This equates
# to a conversion rate of N to N2O-N of 1.8 percent, which is higher that the 0.71
# percent used in Henriksson et al. (2014a). "

# 0.791 kgCO2e/kgLW production 
ghg_total_kgCO2_kg_fish <- 0.791 + ghg_energy_kgCO2_kg_fish ## 0.963

## convert to kgco2/tfish
GHG_kgCO2e_tfish <- ghg_total_kgCO2_kg_fish/0.001

## convert to MTco2e/tfish
GHG_MTCO2e_tfish <- GHG_kgCO2e_tfish/1000

tuna_ghg <- tuna_production %>%
  dplyr::mutate(tuna_ghg_tonnes = GHG_MTCO2e_tfish*tonnes_production) %>%
  dplyr::select(x,y, tuna_ghg_tonnes)

sum(tuna_ghg$tuna_ghg_tonnes) # 35700.88

write.csv(tuna_ghg, file.path(prep_tuna, "tuna_ghg.csv"))

## Now multiply this by our production raster
tuna_production_raster <- rasterFromXYZ(tuna_production)
plot(log(tuna_production_raster + 1))
cellStats(tuna_production_raster, "sum") # 37072.56

ghg_em <- tuna_production_raster*GHG_MTCO2e_tfish
plot(log(ghg_em + 1))
cellStats(ghg_em, "sum") # 35700.88
ghg_em

#check
37072.56*GHG_MTCO2e_tfish # 35700.88
# it worked

## Transform CRS to be appropriate
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

crs(ghg_em) <- crs(food_raster)
ghg_em

ghg_em_final <- projectRaster(ghg_em, food_raster, method = "ngb")
plot(log(ghg_em_final+1))
cellStats(ghg_em_final, "sum") # 35700.88 
ghg_em_final

## Save the raster to datalayers folder
writeRaster(ghg_em_final, file.path(path_final, "marine_tuna_aquaculture_meat_ghg.tif"), overwrite = TRUE)

```

### 2021-02-03 workflow/common.R

@@ -1,0 +1,40 @@
+### Script loading paths, data, info, functions, and packages commonly used 
+
+## Libraries
+library(here)
+library(tidyverse)
+
+## Set the aurora and neptune data_edit share based on operating system
+dir_aurora        <- c('Windows' = '//aurora.nceas.ucsb.edu/food-systems/Food_footprint/',
+                       'Darwin'  = '/Volumes/food-systems/Food_footprint/',    ### connect (cmd-K) to smb://aurora/ohi
+                       'Linux'   = '/home/shares/food-systems/Food_footprint/')[[ Sys.info()[['sysname']] ]]
+
+# warning if aurora directory doesn't exist
+if (Sys.info()[['sysname']] != 'Linux' & !file.exists(dir_aurora)){
+  warning(sprintf("The aurora directory dir_aurora set in src/R/common.R does not exist. Do you need to mount Aurora: %s?", dir_aurora))
+}
+
+
+## Paths
+raw   <- paste0(dir_aurora, "_raw_data/")
+prep  <- paste0(dir_aurora,"all_food_systems/dataprep/")
+layers <- paste0(dir_aurora,"all_food_systems/datalayers/")
+
+
+## Load .csv file of food regions and associated naming and numbering conventions
+food_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"), col_types = "cdc")
+  
+  
+## Common functions+packages
+select <- dplyr::select
+summarise <- dplyr::summarise
+
+
+
+
+
+
+
+
+
+

### 2021-02-03 marine/bivalve/food_pressures/bivalve_ghg/STEP1_ghg_emissions.Rmd
organized the files more

---
title: "Bivalve Aquaculture GHG"
author: "Gage Clawson (NCEAS, OHI, UCSB)"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Script Description

This markdown calculates the GHG emissions from bivalve aquaculture.

# Data information
We used [Seafood Carbon Emissions Tool data](http://seafoodco2.dal.ca/) to extract ghg emissions associated with carcass weight of bivalve from bivalve farming.

One factor that we added was aquatic N<sub>2</sub>O emissions as discussed in [Hu *et al*., 2012](https://pubs.acs.org/doi/full/10.1021/es300110x) and [MacLeod *et al*., 2019](http://www.fao.org/3/ca7130en/ca7130en.pdf).

# Methods 
 - Take midpoint of ghg low and ghg high from [seafood carbon emissions tool data](http://seafoodco2.dal.ca/) for all species
 - Multiply by % energy (to cut out the feed emissions)
 - Add the N20 value from the MacLeod paper to the emissions intensity estimate we got for bivalve
 - Multiply emissions intensity estimate by tonnes of production in each cell

# Preamble
```{r setup, include = FALSE}
# getting packages we want
library(tidyverse)
library(here)
library(raster)
library(sf)
library(janitor)

# Raster templates
source(here("_spatial/template_raster.R"))

# File paths
raw   <- "/home/shares/food-systems/Food_footprint/_raw_data/"
prep_bivalve <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve"
prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/" 
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

# Import master_rgns xy df
master_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))
```

## Import
```{r}
## Read in farmed emissions data

farmed_emissions <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/seafood_carbon_emmisions_tool/d2020/Specie_List_-_11_24_2020,_11_39_21_AM_Farmed.csv")) %>%
  clean_names()

bivalve_production <- read_csv(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/bivalve_farm.csv"))

fao_bivalve_spp <- read_csv(here("aquaculture/marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"))

```

# Wrangle

```{r}
unique(fao_bivalve_spp$species)

unique(farmed_emissions$common_name)
## we only want bivalves that are in fao
# Blue mussel
# Mediterranean mussel
# American cupped oyster
# Pacific cupped oyster 
# New Zealand mussel

bivalve_emissions_spp <- farmed_emissions %>%
  dplyr::filter(common_name %in% c("Blue mussel", "Mediterranean mussel", "American cupped oyster", "Pacific cupped oyster", "New Zealand mussel"))

## grab the mean of ghg low and high (the 25th and 75th quantiles)
bivalve_emissions <- bivalve_emissions_spp %>%
  rowwise() %>%
  dplyr::mutate(ghg_kgCO2_kg_fish_mean = mean(c(ghg_low, ghg_high)))

ghg_kgCO2_kg_fish <- mean(bivalve_emissions$ghg_kgCO2_kg_fish_mean)

## now multiply by the percent of that which is energy emissions (100%)
ghg_energy_kgCO2_kg_fish <- ghg_kgCO2_kg_fish*1 ##  0.2471429 kg CO2eq/ kg fish (live/carcass weight, ratioed)

# Adding Aquatic N2O
# From MacLeod et al. 
# "The amount of N2O per species-group was determined by multiplying the
# production by the N2O emission factor per kg of production (Hu et al., 2012), i.e.
# 1.69 gN2O-N per kg of production, or 0.791 kgCO2e/kgLW production. This equates
# to a conversion rate of N to N2O-N of 1.8 percent, which is higher that the 0.71
# percent used in Henriksson et al. (2014a). "

# 0.791 kgCO2e/kgLW production 
ghg_total_kgCO2_kg_fish <- 0.791 + ghg_energy_kgCO2_kg_fish

## convert to kgco2/tfish
GHG_kgCO2e_tfish <- ghg_total_kgCO2_kg_fish/0.001

## convert to MTco2e/tfish
GHG_MTCO2e_tfish <- GHG_kgCO2e_tfish/1000

## Now multiply this by our production raster
bivalve_production_raster <- rasterFromXYZ(bivalve_production)
plot(log(bivalve_production_raster + 1))
cellStats(bivalve_production_raster, "sum") # 17435623

ghg_em <- bivalve_production_raster*GHG_MTCO2e_tfish
plot(log(ghg_em + 1))
cellStats(ghg_em, "sum") # 18100668
ghg_em

#check
17435623*GHG_MTCO2e_tfish #18100667 - close enough
# it worked

## Transform CRS to be appropriate
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

crs(ghg_em) <- crs(food_raster)
ghg_em

ghg_em_final <- projectRaster(ghg_em, food_raster, method = "ngb")
plot(log(ghg_em_final+1))
cellStats(ghg_em_final, "sum") #18100668
ghg_em_final

## Save the raster to datalayers folder
writeRaster(ghg_em_final, file.path(path_final, "marine_bivalve_aquaculture_meat_ghg.tif"), overwrite = TRUE)

```

### 2021-02-03 marine/bivalve/food_pressures/bivalve_nutrient/bivalve_nutrient.Rmd
organized the files more

---
title: "Creating a file for bivalve farming nutrient pollution"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/23/2020"
output: html_document
---

This markdown creates a nutrient pollution impact layer for bivalve aquaculture. This impact is zero for bivalves, but there is an impact from gastropods. This markdown uses models and species specific parameters from the paper *Aquaculture Production is a Large, Spatially Concentrated Source of Nutrients in Chinese Freshwater and Coastal Seas* (Wang et al. 2020; table 1).

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

Because we have multiple values and species for nutrient pollution for bivalves (bivalves and gastropods), we will have to do this analysis in a series of steps. Workflow will follow these rules:

1. Apply the gastropod value to places with gastropod production (and in the right proportion)
2. Apply 0 for other bivalves

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P value
3. We report in summed N and P (total excess nutrients), so sum the N and P rasters (and save each separately as a prep file).
4. We report in tonnes, so divide by 1000

**Numbers for each category:** 
Gastropods: 
N = 110 kg/tonne production, P = 15 kg/tonne production

Bivalves:
N = 0, P = 0

```{r}
fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon
species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

taxon_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, Taxon_code, aq_group)

gastropod_list <- taxon_list %>%
  dplyr::filter(Taxon_code == "GAST") %>%
  dplyr::filter(species != "Marine molluscs nei") %>%
  distinct(species)

gastropod_list <- gastropod_list$species

# the list of species we are including
bivalves_list <- species_list$species[species_list$aq_group=="bivalves"]
bivalves_list

## write out shrimp taxa and production for Juliette
fao_bivalves_taxa_prod <- fao %>%
  filter(species %in% bivalves_list) %>%
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

## Now we need to get the proportion of catch that falls into each species category (i.e. pelagic or non-pelagic) 
prop_df <- fao_bivalves_taxa_prod %>%
  dplyr::mutate(species_cat = ifelse(species %in% gastropod_list, "gastropod", "bivalves")) %>%
  group_by(iso3c, species_cat) %>%
  summarise(tonnes = sum(fao_tonnes_production)) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(total_tonnes = sum(tonnes)) %>%
  ungroup()

prop_bivalve_df <- prop_df %>%
  dplyr::filter(species_cat == "bivalves") %>%
  dplyr::mutate(prop_bivalve = tonnes/total_tonnes) %>%
  dplyr::mutate(prop_gastropod = 1-prop_bivalve) %>%
  dplyr::select(iso3c, prop_gastropod, prop_bivalve, total_tonnes)

sum(prop_bivalve_df$total_tonnes) # 17435623
sum(fao_bivalves_taxa_prod$fao_tonnes_production) # 17435623

## Read in production data 
production_sf <- st_read(file.path("/home/sgclawson/github/food_systems/aquaculture/marine/bivalve/bivalve_nutrient/prod_data_by_cell_iso3c.shp")) %>%
  dplyr::rename("tonnes_per_farm" = "tnns_p_")

## join with our proportion data so that we can get tonnes of pelagic and tonnes of non-pelagic per farm 
production_spp_props <- production_sf %>%
  left_join(prop_bivalve_df, by = "iso3c") %>%
  dplyr::mutate(tonnes_gastropod = prop_gastropod*tonnes_per_farm, 
                tonnes_bivalve = prop_bivalve*tonnes_per_farm)

sum(production_spp_props$tonnes_bivalve) + sum(production_spp_props$tonnes_gastropod) # 17435623

## Now we can do the actual analysis outlined above
nutrient_data <- production_spp_props %>%
  dplyr::mutate(tonnes_gastropod_growth = tonnes_gastropod*0.95,
                tonnes_bivalve_growth = tonnes_bivalve*0.95) %>%   ## multiply by 0.95 to correct for growth outside seapen

  dplyr::mutate(N_poll_gast = tonnes_gastropod_growth*110,
                P_poll_gast = tonnes_gastropod_growth*15,
                N_poll_bivalve = 0*tonnes_bivalve_growth,
                P_poll_bivalve = 0*tonnes_bivalve_growth) %>%  ## get pollution values by species group

  dplyr::mutate(N_poll_kg = N_poll_gast + N_poll_bivalve,
                P_poll_kg = P_poll_gast + P_poll_bivalve) %>% ## get total pollution values for each cell in kg

  # dplyr::mutate(po4eq_kg = N_poll*0.42 + P_poll*3.07) %>% ## get po4eq; not doing this anymore (01/14/2021)

   dplyr::mutate(N_poll_t = N_poll_kg/1000,
                P_poll_t = P_poll_kg/1000) %>% ## get total pollution values for each cell in tonnes

  dplyr::mutate(total_N_P_t = N_poll_t + P_poll_t) %>%
  dplyr::select(N_poll_t, P_poll_t, total_N_P_t)

sum(nutrient_data$total_N_P_t) #  50167.83
sum(production_spp_props$tonnes_gastropod) # 422466

## Save total N_P layer
bivalves_raster_total <- rasterize(nutrient_data, food_raster, field = "total_N_P_t", fun=sum, background=0)
plot(log(bivalves_raster_total+1))

bivalves_raster_df <- as.data.frame(bivalves_raster_total, xy=TRUE) %>%
  dplyr::select(x,y, N_P_tonnes=layer)

cellStats(bivalves_raster_total, stat = "sum") # 50167.83
sum(bivalves_raster_df$N_P_tonnes) # 50167.83
sum(nutrient_data$total_N_P_t, na.rm = TRUE) # 50167.83

## save to dataprep folder with the correct naming conventions: 
write.csv(bivalves_raster_df, file.path(path_prep, "bivalves_nutrient.csv"))

final_rast <- rasterFromXYZ(bivalves_raster_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 50167.83

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 50167.83
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_final, "marine_bivalve_aquaculture_meat_nutrient.tif"), overwrite = T)

## Save N nutrient layer
bivalves_raster_N <- rasterize(nutrient_data, food_raster, field = "N_poll_t", fun=sum, background=0)
plot(log(bivalves_raster_N+1))

bivalves_raster_df <- as.data.frame(bivalves_raster_N, xy=TRUE) %>%
  dplyr::select(x,y, N_tonnes=layer)

cellStats(bivalves_raster_N, stat = "sum") # 44147.69
sum(bivalves_raster_df$N_tonnes) # 44147.69
sum(nutrient_data$N_poll_t, na.rm = TRUE) # 44147.69

## save to dataprep folder with the correct naming conventions: 
write.csv(bivalves_raster_df, file.path(path_prep, "bivalves_nutrient_N.csv"))

final_rast <- rasterFromXYZ(bivalves_raster_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 44147.69

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 44147.69
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_bivalve_aquaculture_meat_nutrientN.tif"), overwrite = T)

## Save P nutrient layer
bivalves_raster_P <- rasterize(nutrient_data, food_raster, field = "P_poll_t", fun=sum, background=0)
plot(log(bivalves_raster_P+1))

bivalves_raster_df <- as.data.frame(bivalves_raster_P, xy=TRUE) %>%
  dplyr::select(x,y, P_tonnes=layer)

cellStats(bivalves_raster_P, stat = "sum") # 6020.14
sum(bivalves_raster_df$P_tonnes) # 6020.14
sum(nutrient_data$P_poll_t, na.rm = TRUE) # 6020.14

## save to dataprep folder with the correct naming conventions: 
write.csv(bivalves_raster_df, file.path(path_prep, "bivalves_nutrient_P.csv"))

final_rast <- rasterFromXYZ(bivalves_raster_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 6020.14

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 6020.14
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_bivalve_aquaculture_meat_nutrientP.tif"), overwrite = T)
```

### 2021-02-03 marine/crustaceans/food_pressures/crustacean_ghg/STEP1_ghg_emissions.Rmd
organized the files more

---
title: "Crustacean: Aquaculture GHG"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/22/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Script Description

This markdown calculates the GHG emissions from general crustacean aquaculture.

# Data information
We used [Seafood Carbon Emissions Tool data](http://seafoodco2.dal.ca/) to extract ghg emissions associated with carcass weight of crustacean from crustacean farming.

One factor that we added was aquatic N<sub>2</sub>O emissions as discussed in [Hu *et al*., 2012](https://pubs.acs.org/doi/full/10.1021/es300110x) and [MacLoid *et al*., 2019](http://www.fao.org/3/ca7130en/ca7130en.pdf).

# Methods 
 - Take midpoint of ghg low and ghg high from [seafood carbon emissions tool data](http://seafoodco2.dal.ca/) for all crustacean species
 - Multiply by % energy (to cut out the feed emissions)
 - Add the N20 value from the MacLeod paper to the emissions intensity estimate we got for crustaceans
 - Multiply emissions intensity estimate by tonnes of production in each cell

# Preamble
```{r setup, include = FALSE}
# getting packages we want
library(tidyverse)
library(here)
library(raster)
library(sf)
library(janitor)

# Raster templates
source(here("_spatial/template_raster.R"))

# File paths
raw   <- "/home/shares/food-systems/Food_footprint/_raw_data/"
prep_crustacean <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans"
prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/" 
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

# Import master_rgns xy df
master_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))
```

## Import
```{r}
## Read in farmed emissions data

farmed_emissions <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/seafood_carbon_emmisions_tool/d2020/Specie_List_-_11_24_2020,_11_39_21_AM_Farmed.csv")) %>%
  clean_names()

crustacean_production <- read_csv(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/crustaceans_farm.csv"))

fao_crustacean_spp <- read_csv(here("aquaculture/marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans_taxa_production.csv"))

```

# Wrangle

```{r}
unique(sort(fao_crustacean_spp$species))
# [1] "Green mud crab"              "Indo-Pacific swamp crab"     "Marine crabs nei"            "Orange mud crab"            
# [5] "Portunus swimcrabs nei"      "Tropical spiny lobsters nei"

unique(sort(farmed_emissions$common_name))
## we only want crustaceans that are in fao
 #  Emissions spp   -   FAO spp
 ###############################################
#

## There are no matches here.. for now I will use the shrimp values for the crustaceans

## Filter for the appropriate species... 
crustacean_emissions_spp <- farmed_emissions %>%
  dplyr::filter(common_name %in% c("Whiteleg shrimp", "Giant tiger prawn"))

## multiply the ghg low and ghg high by the percent energy
## take the mean of new ghg low and high (the 25th and 75th quantiles)
crustacean_emissions <- crustacean_emissions_spp %>%
  dplyr::mutate(ghg_low_energy = ghg_low*(percent_energy/100),
                ghg_high_energy = ghg_high*(percent_energy/100)) %>%
  rowwise() %>%
  dplyr::mutate(ghg_kgCO2_kg_fish_mean = mean(c(ghg_low_energy, ghg_high_energy)))

ghg_kgCO2_kg_fish <- mean(crustacean_emissions$ghg_kgCO2_kg_fish_mean)

ghg_energy_kgCO2_kg_fish <- ghg_kgCO2_kg_fish # *1 ##   0.381375 kg CO2eq/ kg fish (live/carcass weight, ratioed)

# Adding Aquatic N2O
# From MacLeod et al. 
# "The amount of N2O per species-group was determined by multiplying the
# production by the N2O emission factor per kg of production (Hu et al., 2012), i.e.
# 1.69 gN2O-N per kg of production, or 0.791 kgCO2e/kgLW production. This equates
# to a conversion rate of N to N2O-N of 1.8 percent, which is higher that the 0.71
# percent used in Henriksson et al. (2014a). "

# 0.791 kgCO2e/kgLW production 
ghg_total_kgCO2_kg_fish <- 0.791 + ghg_energy_kgCO2_kg_fish ## 3.4445

## convert to kgco2/tfish
GHG_kgCO2e_tfish <- ghg_total_kgCO2_kg_fish/0.001

## convert to MTco2e/tfish
GHG_MTCO2e_tfish <- GHG_kgCO2e_tfish/1000

crustacean_ghg <- crustacean_production %>%
  dplyr::mutate(crustacean_ghg_tonnes = tonnes_production*GHG_MTCO2e_tfish) %>%
  dplyr::select(x, y, crustacean_ghg_tonnes)
sum(crustacean_ghg$crustacean_ghg_tonnes) # 1383721

write.csv(crustacean_ghg, file.path(prep_crustacean, "crustacean_ghg.csv"))

## Now multiply this by our production raster
crustacean_production_raster <- rasterFromXYZ(crustacean_production)
plot(log(crustacean_production_raster + 1))
cellStats(crustacean_production_raster, "sum") # 401719.1

ghg_em <- crustacean_production_raster*GHG_MTCO2e_tfish
plot(log(ghg_em + 1))
cellStats(ghg_em, "sum") # 1383721
ghg_em

#check
401719.1*GHG_MTCO2e_tfish # 1383721
# it worked

## Transform CRS to be appropriate
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

crs(ghg_em) <- crs(food_raster)
ghg_em

ghg_em_final <- projectRaster(ghg_em, food_raster, method = "ngb")
plot(log(ghg_em_final+1))
cellStats(ghg_em_final, "sum") # 1383721
ghg_em_final

## Save the raster to datalayers folder
writeRaster(ghg_em_final, file.path(path_final, "marine_crustaceans_aquaculture_meat_ghg.tif"), overwrite = TRUE)

```

### 2021-02-03 marine/marine_fish_general/food_pressures/finfish_ghg/STEP1_ghg_emissions.Rmd
organized the files more

---
title: "Marine Fish - General: Aquaculture GHG"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Script Description

This markdown calculates the GHG emissions from general finfish aquaculture.

# Data information
We used [Seafood Carbon Emissions Tool data](http://seafoodco2.dal.ca/) to extract ghg emissions associated with carcass weight of finfish from finfish farming.

One factor that we added was aquatic N<sub>2</sub>O emissions as discussed in [Hu *et al*., 2012](https://pubs.acs.org/doi/full/10.1021/es300110x) and [MacLoid *et al*., 2019](http://www.fao.org/3/ca7130en/ca7130en.pdf).

# Methods 
 - Take midpoint of ghg low and ghg high from [seafood carbon emissions tool data](http://seafoodco2.dal.ca/) for all finfish species
 - Multiply by % energy (to cut out the feed emissions)
 - Add the N20 value from the MacLeod paper to the emissions intensity estimate we got for finfish
 - Multiply emissions intensity estimate by tonnes of production in each cell

# Preamble
```{r setup, include = FALSE}
# getting packages we want
library(tidyverse)
library(here)
library(raster)
library(sf)
library(janitor)

# Raster templates
source(here("_spatial/template_raster.R"))

# File paths
raw   <- "/home/shares/food-systems/Food_footprint/_raw_data/"
prep_finfish <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general"
prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/" 
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

# Import master_rgns xy df
master_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))
```

## Import
```{r}
## Read in farmed emissions data

farmed_emissions <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/seafood_carbon_emmisions_tool/d2020/Specie_List_-_11_24_2020,_11_39_21_AM_Farmed.csv")) %>%
  clean_names()

finfish_production <- read_csv(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/marine_fish_general_farm.csv"))

fao_finfish_spp <- read_csv(here("aquaculture/marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish_taxa_production.csv"))

```

# Wrangle

```{r}
unique(sort(fao_finfish_spp$species))

unique(sort(farmed_emissions$common_name))
## we only want finfishs that are in fao
 #  Emissions spp   -   FAO spp
 ###############################################
 # "Almaco jack" - Falls under "Amberjacks nei"                               
 # "Barramundi" -  "Barramundi(=Giant seaperch)"                    
 # "California yellowtail" - "Amberjacks nei"
 # "Cobia" - "Cobia"          
 # "European bass" - "European seabass             
 # "Gilt-head seabream" - "Gilthead seabream"
 # "Japanese amberjack" - "Japanese amberjack"  
 # "Turbot" - "Turbot"

## Filter for the appropriate species... also filter for "Marine net pen" and "Cages".. since we don't want any inland aquaculture
finfish_emissions_spp <- farmed_emissions %>%
  dplyr::filter(common_name %in% c("Almaco jack", "Barramundi", "California yellowtail", "Cobia", "European bass", "Gilt-head seabream", "Japanese amberjack", "Turbot")) %>%
  dplyr::filter(system %in% c("Marine net pen", "Cages"))

## after the filter we lost Turbot... there wasn't that much production anyways.

## This looks pretty good though... all of the ghg low and ghg high are generally between 2 and 4... with the exception of cobia. I feel comfortable just taking the midpoint.

## multiply the ghg low and ghg high by the percent energy
## take the mean of new ghg low and high (the 25th and 75th quantiles)
finfish_emissions <- finfish_emissions_spp %>%
  dplyr::mutate(ghg_low_energy = ghg_low*(percent_energy/100),
                ghg_high_energy = ghg_high*(percent_energy/100)) %>%
  rowwise() %>%
  dplyr::mutate(ghg_kgCO2_kg_fish_mean = mean(c(ghg_low_energy, ghg_high_energy)))

ghg_kgCO2_kg_fish <- mean(finfish_emissions$ghg_kgCO2_kg_fish_mean)

ghg_energy_kgCO2_kg_fish <- ghg_kgCO2_kg_fish # 0.381375 kg CO2eq/ kg fish (live/carcass weight, ratioed)

# Adding Aquatic N2O
# From MacLeod et al. 
# "The amount of N2O per species-group was determined by multiplying the
# production by the N2O emission factor per kg of production (Hu et al., 2012), i.e.
# 1.69 gN2O-N per kg of production, or 0.791 kgCO2e/kgLW production. This equates
# to a conversion rate of N to N2O-N of 1.8 percent, which is higher that the 0.71
# percent used in Henriksson et al. (2014a). "

# 0.791 kgCO2e/kgLW production 
ghg_total_kgCO2_kg_fish <- 0.791 + ghg_energy_kgCO2_kg_fish ## 1.172375

## convert to kgco2/tfish
GHG_kgCO2e_tfish <- ghg_total_kgCO2_kg_fish/0.001

## convert to MTco2e/tfish
GHG_MTCO2e_tfish <- GHG_kgCO2e_tfish/1000

finfish_ghg <- finfish_production %>%
  dplyr::mutate(finfish_ghg_tonnes = GHG_MTCO2e_tfish*tonnes_production) %>%
  dplyr::select(x,y, finfish_ghg_tonnes)

sum(finfish_ghg$finfish_ghg_tonnes)

write.csv(finfish_ghg, file.path(prep_finfish, "marine_fish_general_ghg.csv"))

## Now multiply this by our production raster
finfish_production_raster <- rasterFromXYZ(finfish_production)
plot(log(finfish_production_raster + 1))
cellStats(finfish_production_raster, "sum") # 3901214

ghg_em <- finfish_production_raster*GHG_MTCO2e_tfish
plot(log(ghg_em + 1))
cellStats(ghg_em, "sum") # 4573686
ghg_em

#check
3901214*GHG_MTCO2e_tfish #4573686
# it worked

## Transform CRS to be appropriate
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

crs(ghg_em) <- crs(food_raster)
ghg_em

ghg_em_final <- projectRaster(ghg_em, food_raster, method = "ngb")
plot(log(ghg_em_final+1))
cellStats(ghg_em_final, "sum") # 4573686
ghg_em_final

## Save the raster to datalayers folder
writeRaster(ghg_em_final, file.path(path_final, "marine_marine-fish-general_aquaculture_meat_ghg.tif"), overwrite = TRUE)

```

### 2021-02-03 marine/salmon/food_pressures/salmon_disturbance/STEP1_salmon_tonnes_to_livestock_conversion.Rmd
organized the files more

---
title: "Modeling salmon production (tonnes) to total number"
author: "Juliette Verstaen"
date: "1/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries and paths}
library(dplyr)
library(tidyr)
library(data.table)
library(countrycode)
library(readxl)
library(stringi)
library(stringr)
library(ggplot2)
library(readr)

raw_path <- "/home/shares/food-systems/Food_footprint/_raw_data/"
```

## About

Calculating conversion factor converting production of salmon reported in tonnage to the number of individual salmon.

## Data

1. For this we are going to use the data found [here](https://www.ssb.no/en/statbank/table/09259/), which documents for each county: 
- The stock number as of Jan 1st
- Supplies - how many additional fish were added
- Delivered for sale - how many fish were removed for consumption
- Loss - number of fish died
- The stock number as of Dec 31st
- Percent loss

2. [Aquaculture sales](https://www.ssb.no/en/statbank/table/07326)

## Methods

### Norwegian Fisheries Directorate data wrangling
First we're going to read in the production data we have, and keep all the years. 
```{r wrangling production data}
nor_prod <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>% 
  filter(species == "Salmon") %>% 
  dplyr:: select(year, region,variable, value) %>% 
  spread(variable, value) %>% 
  rename(salmon_tonnes = tonnes_fish) %>% 
  mutate(Stock_Jan1_count = Stock_Jan1_count*1000,
         loss_count = loss_count*1000,
         stock_dec_31_count = stock_dec_31_count*1000,
         delivered_for_sale_count = delivered_for_sale_count*1000,
         supplies_count = supplies_count*1000)

```

Checking the total annual sum of salmon production in Norway
```{r annual totals}
## combine them all together for total salmon in all of Norway.
nor_pro_county<- nor_prod %>% 
  group_by(year) %>% 
  summarize(total_salmon_tonnes = sum(salmon_tonnes))

nor_pro_county
```

Because graphs are fun!!
```{r graph production by region}
# graph!
plot <- ggplot(nor_prod)+
  geom_line(aes(x=year, y = salmon_tonnes, color=region))+
  ggtitle("Salmon Production in Norwegian Counties") +
  ylab("Tonnage of Salmon") +
  xlab("Year") +
  theme_classic() 
plot

```

###SSB Data wrangling

**Pulling out Nord and Sor** 
Up until 2017 Trøndelag was Nord-Trøndelag and Sør-Trøndelag. Since the production data we have combines both of these counties during that time, we are going to do the same here to avoid unnecessary errors in our modeling. Here I pull out that data to work on it so I can better see what's happening.

```{r nord_tron and sor_tron wrangling}

trond <- nor_prod %>% 
  filter(region == "Nord-Trøndelag" | region == "Sør-Trøndelag" | region == "Trøndelag") %>% 
  group_by(year) %>%

  mutate(t_stock = sum(Stock_Jan1_count),
         t_prod = sum(salmon_tonnes),
         t_loss_count = sum(loss_count),
         t_stock_dec_31_count = sum(stock_dec_31_count),
         t_sale = sum(delivered_for_sale_count),
         t_supplies_count = sum(supplies_count)) %>%

  dplyr::select(year, t_stock, t_prod, t_loss_count, t_stock_dec_31_count, t_sale, t_supplies_count) %>%

  rename(Stock_Jan1_count = t_stock,
         salmon_tonnes = t_prod,
         delivered_for_sale_count = t_sale,
         stock_dec_31_count = t_stock_dec_31_count,
         loss_count = t_loss_count,
         supplies_count = t_supplies_count) %>%

  mutate(region = "Trøndelag") %>% 
    unique()

```

**Finishing up SSB data wrangling**
```{r finalizing ssb data wrangling}
nor_prod <- nor_prod %>% 
  ### get rid of the Trondelag, Sor, and Nord that we will add back in consolidated
  filter(region != "Nord-Trøndelag" & region != "Sør-Trøndelag" & region != "Trøndelag") %>%
  bind_rows(trond)

plot <- ggplot(nor_prod)+
  geom_line(aes(x=year, y = salmon_tonnes, color=region))+
  ggtitle("Salmon Production in Norwegian Counties") +
  ylab("Tonnage of Salmon") +
  xlab("Year") +
  theme_classic() 
plot

```

###Combine both data sets

```{r combine data sets}
all_salmon <- nor_prod %>% 
  mutate(salmon_kg = salmon_tonnes*1000,
         avg_harvest_wgt_kg = salmon_kg/delivered_for_sale_count,
         mortality_rate = loss_count/(Stock_Jan1_count)) 
#%>%   filter(num_loss != is.na(num_loss))

write.csv(all_salmon, file = "data/all_salmon_norway.csv")
```

Check to see if the math for adding the number of salmon at the end of the year matches the reported values
```{r}
sal_check <- all_salmon %>% 
  mutate(test = Stock_Jan1_count  + supplies_count - loss_count - delivered_for_sale_count,
         diff = test - stock_dec_31_count,
         perdiff = diff/stock_dec_31_count)
```

Some of these values are off by either 1000 or 2000 fish (weird that they are such even numbers...) but this is mostly a drop in the bucket in the ground scheme of things, so we won't worry about it too much

```{r explore data}
### does larger production mean increased mortality rate?
plot(all_salmon$salmon_kg, all_salmon$mortality_rate) #no

### which counties have higher mortality rates
ggplot(all_salmon)+
  geom_line(aes(x= year, y = mortality_rate, color= region))

salmon_model <- lm(delivered_for_sale_count ~salmon_tonnes, data = all_salmon)
salmon_model
summary(salmon_model)
plot(salmon_model)

ggplot(all_salmon) +
  geom_point(aes(x= salmon_tonnes, y = delivered_for_sale_count))+
  xlab("Tonnage of Salmon") +
  ylab("Number Salmon Sold") +
  theme_classic() +
  stat_smooth(aes(x= salmon_tonnes, y = delivered_for_sale_count), method = "lm")

plot(all_salmon$loss_count, all_salmon$delivered_for_sale_count)
```

Simple model conversion production to numbers
tanding_stock_beginning_year ~ number_produced/sold - 1
```{r conversion production to numbers}

salm_conv_model <- lm(Stock_Jan1_count ~ delivered_for_sale_count - 1, data = test)
salm_conv_model
summary(salm_conv_model)

ggplot(all_salmon)+
  geom_point(aes(x= delivered_for_sale_count, y = Stock_Jan1_count)) + 
  geom_abline(intercept=0, slope = 1.477)
```

Making histogram graphs for harvest weights 
- mean and standard deviations

```{r}

all_salmon_2 <- all_salmon %>% 
  mutate(sd = sd(avg_harvest_wgt_kg),
         mean = mean(avg_harvest_wgt_kg))

hist_harv_weight <- ggplot(all_salmon) +
  geom_histogram(aes(x= avg_harvest_wgt_kg), fill = "gray65") +
  ggtitle("Norwegian Salmon Harvest Weight") +
  ylab("Count") +
  xlab("Harvest Weight (kg)") +
  theme_classic() +
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg)) ,col='dodgerblue2',size=1)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) + sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) - sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) - 2*sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) + 2*sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5) +
  theme(legend.position = "none")

hist_harv_weight

mean(all_salmon$avg_harvest_wgt_kg)
#4.907344
sd(all_salmon$avg_harvest_wgt_kg)
#0.3927127
min(all_salmon$avg_harvest_wgt_kg)
#3.30712
max(all_salmon$avg_harvest_wgt_kg)
#6.53237

```

### 2021-02-03 marine/salmon/food_pressures/salmon_ghg/STEP1_ghg_emissions.Rmd
organized the files more

---
title: "Salmon: Aquaculture GHG"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Script Description

This markdown calculates the GHG emissions from salmon aquaculture.

# Data information
We used [Seafood Carbon Emissions Tool data](http://seafoodco2.dal.ca/) to extract ghg emissions associated with carcass weight of salmon from salmon farming.

One factor that we added was aquatic N<sub>2</sub>O emissions as discussed in [Hu *et al*., 2012](https://pubs.acs.org/doi/full/10.1021/es300110x) and [MacLeod *et al*., 2019](http://www.fao.org/3/ca7130en/ca7130en.pdf).

# Methods 
 - Take midpoint of ghg low and ghg high from [seafood carbon emissions tool data](http://seafoodco2.dal.ca/) for salmon, trout, and char species
 - Multiply by % energy (to cut out the feed emissions)
 - Add the N20 value from the MacLeod paper to the emissions intensity estimate we got for salmon
 - Multiply emissions intensity estimate by tonnes of production in each cell

# Preamble
```{r setup, include = FALSE}
# getting packages we want
library(tidyverse)
library(here)
library(raster)
library(sf)
library(janitor)

# Raster templates
source(here("_spatial/template_raster.R"))

# File paths
raw   <- "/home/shares/food-systems/Food_footprint/_raw_data/"
prep_salmon <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon"
prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/" 
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

# Import master_rgns xy df
master_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))
```

## Import
```{r}
## Read in farmed emissions data

farmed_emissions <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/seafood_carbon_emmisions_tool/d2020/Specie_List_-_11_24_2020,_11_39_21_AM_Farmed.csv")) %>%
  clean_names()

salmon_production <- read_csv(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm.csv"))

fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("aquaculture/marine/species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
salmon_list <- species_list$species[species_list$aq_group=="salmonids"]
salmon_list

# include only salmon
fao_salmon <- fao %>%
  filter(species %in% salmon_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, species, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, species, iso3c, year) %>%
  dplyr::filter(year == 2017)

```

# Wrangle

```{r}
unique(sort(fao_salmon$species))
# [1] "Arctic char"                  "Atlantic salmon"              "Chinook(=Spring=King) salmon" "Coho(=Silver) salmon"        
# [5] "European whitefish"           "Rainbow trout"                "Salmonids nei"                "Trouts nei"

unique(sort(farmed_emissions$common_name))

## we only want salmons that are in fao
 #  Emissions spp   -   FAO spp
 ###############################################
salmon_list <- c("Arctic char", "Atlantic salmon", "Chinook salmon", "Rainbow trout", "Sea trout")

## Filter for the appropriate species... also filter for "Marine net pen".. since we don't want any inland aquaculture
salmon_emissions_spp <- farmed_emissions %>%
  dplyr::filter(common_name %in% salmon_list) %>%
  dplyr::filter(system %in% c("Marine net pen"))

## This looks pretty good though... all of the ghg low and ghg high are between 1 and 3. I feel comfortable just taking the midpoint.

## multiply the ghg low and ghg high by the percent energy
## take the mean of new ghg low and high (the 25th and 75th quantiles)
salmon_emissions <- salmon_emissions_spp %>%
  dplyr::mutate(ghg_low_energy = ghg_low*(percent_energy/100),
                ghg_high_energy = ghg_high*(percent_energy/100)) %>%
  rowwise() %>%
  dplyr::mutate(ghg_kgCO2_kg_fish_mean = mean(c(ghg_low_energy, ghg_high_energy)))

ghg_energy_kgCO2_kg_fish <- mean(salmon_emissions$ghg_kgCO2_kg_fish_mean) # 0.159 kg CO2eq/ kg fish (live/carcass weight, ratioed)

# Adding Aquatic N2O
# From MacLeod et al. 
# "The amount of N2O per species-group was determined by multiplying the
# production by the N2O emission factor per kg of production (Hu et al., 2012), i.e.
# 1.69 gN2O-N per kg of production, or 0.791 kgCO2e/kgLW production. This equates
# to a conversion rate of N to N2O-N of 1.8 percent, which is higher that the 0.71
# percent used in Henriksson et al. (2014a). "

# 0.791 kgCO2e/kgLW production 
ghg_total_kgCO2_kg_fish <- 0.791 + ghg_energy_kgCO2_kg_fish ## 0.95

## convert to kgco2/tfish
GHG_kgCO2e_tfish <- ghg_total_kgCO2_kg_fish/0.001

## convert to MTco2e/tfish
GHG_MTCO2e_tfish <- GHG_kgCO2e_tfish/1000

salmon_production_ghg <- salmon_production %>% 
  dplyr::mutate(ghg_tonnes = tonnes_production*GHG_MTCO2e_tfish) %>%
  dplyr::select(x, y, ghg_tonnes)

sum(salmon_production_ghg$ghg_tonnes) # 2608782

write.csv(salmon_production_ghg, file.path(prep_salmon, "salmon_ghg.csv"))

## Now multiply this by our production raster
salmon_production_raster <- rasterFromXYZ(salmon_production)
plot(log(salmon_production_raster + 1))
cellStats(salmon_production_raster, "sum") # 2746086

ghg_em <- salmon_production_raster*GHG_MTCO2e_tfish
plot(log(ghg_em + 1))
cellStats(ghg_em, "sum") # 2608782
ghg_em

norway <- raster::crop(ghg_em, extent(-25, 50, 50, 75))
par(mar=c(1,1,1,1))
plot(norway)
chile <- raster::crop(ghg_em, extent(-80, -60, -60, -35))
par(mar=c(1,1,1,1))
plot(chile)

#check
2746086*GHG_MTCO2e_tfish #2608782
# it worked

## Transform CRS to be appropriate
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

crs(ghg_em) <- crs(food_raster)
ghg_em

ghg_em_final <- projectRaster(ghg_em, food_raster, method = "ngb")
plot(log(ghg_em_final+1))
cellStats(ghg_em_final, "sum") # 2608782
ghg_em_final

## Save the raster to datalayers folder
writeRaster(ghg_em_final, file.path(path_final, "marine_salmon_aquaculture_meat_ghg.tif"), overwrite = TRUE)

```

### 2021-02-04 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
cleaned up scripts and updated file paths

---
title: "Location of Bivalve Farms"
author: "Gage Clawson (USCB, NCEAS, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script standardizes location of bivalve farms to be lat/long point data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

fao_bivalve_spp <- read_csv("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv") %>%
  dplyr::filter(year == 2017)

fao_bivalve <- read_csv("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv") %>%
  dplyr::filter(year == 2017)

unique(fao_bivalve$country)
#  [1] "Australia"                "Brazil"                   "Bulgaria"                 "Cambodia"                
#  [5] "Canada"                   "Chile"                    "China"                    "China, Hong Kong SAR"    
#  [9] "Croatia"                  "Cuba"                     "Denmark"                  "France"                  
# [13] "French Polynesia"         "Germany"                  "Greece"                   "Guernsey"                
# [17] "India"                    "Indonesia"                "Ireland"                  "Italy"                   
# [21] "Japan"                    "Jersey"                   "Korea, Dem. People's Rep" "Korea, Republic of"      
# [25] "Malaysia"                 "Mexico"                   "Netherlands"              "New Zealand"             
# [29] "Norway"                   "Peru"                     "Philippines"              "Portugal"                
# [33] "Russian Federation"       "Slovenia"                 "South Africa"             "Spain"                   
# [37] "Sweden"                   "Taiwan Province of China" "Thailand"                 "United Kingdom"          
# [41] "United States of America" "Viet Nam"       
```

## explore
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

```{r}
ASC_data <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp"))

ASC_bivalve <- ASC_data %>%
  dplyr::filter(aq_grop == "bivalves")

unique(ASC_bivalve$crt_cnt)
#  [1] "China"                                               
#  [2] "New Zealand"                                         
#  [3] "South Africa"                                        
#  [4] "Australia"                                           
#  [5] "Korea, Republic of"                                  
#  [6] "Japan"                                               
#  [7] "Peru"                                                
#  [8] "Mexico"                                              
#  [9] "France"                                              
# [10] "Chile"                                               
# [11] "United Kingdom of Great Britain and Northern Ireland"
# [12] "Viet Nam"                                            
# [13] "Portugal"

## what is in ASC and not in FAO
setdiff(ASC_bivalve$crt_cnt, fao_bivalve$country)
#[1] "United Kingdom of Great Britain and Northern Ireland"

## what is in FAO and not ASC -- this is what we need to find alternative data sources for (29 countries)
setdiff(fao_bivalve$country, ASC_bivalve$crt_cnt)
#  [1] "Brazil"                   "Bulgaria"                 "Cambodia"                 "Canada"                  
#  [5] "China, Hong Kong SAR"     "Croatia"                  "Cuba"                     "Denmark"                 
#  [9] "French Polynesia"         "Germany"                  "Greece"                   "Guernsey"                
# [13] "India"                    "Indonesia"                "Ireland"                  "Italy"                   
# [17] "Jersey"                   "Korea, Dem. People's Rep" "Malaysia"                 "Netherlands"             
# [21] "Norway"                   "Philippines"              "Russian Federation"       "Slovenia"                
# [25] "Spain"                    "Sweden"                   "Taiwan Province of China" "Thailand"                
# "United States of America"

mapview(ASC_bivalve)
```

# Raster

Standard raster used for this analysis

```{r}

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

# Map data from ASC

Data comes from https://gis.asc-aqua.org/arcgis_app/

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}

# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_bivalve$crt_cnt, origin = 'country.name', destination = 'iso3c'))

# read in shp
farms_all <- ASC_bivalve %>%
  cbind(iso)

mapview(farms_all$geometry)

unique(farms_all$iso3c)

all_pts <- st_centroid(farms_all)

all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry, iso3c)

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

## save farm location
write.csv(farms_all_fin, here("marine/bivalve/bivalve_farms/data/bivalve_sites/ASC_bivalve_farm_lat_lon.csv"), row.names = FALSE)

```

Now we will map the remaining countries with bivalve farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of bivalve farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine bivalve farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia).

## USA 
This has a lot of maps, but almost all don't allow downloads: https://coastalscience.noaa.gov/research/marine-spatial-ecology/coastal-aquaculture-planning-portal-capp/?tx_category=shellfish-algae-planning-and-siting

## US Northeast - NY, CT, ME, NH
 - Regional Ocean Council 2018

Source: 
Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 2020] https://www.northeastoceandata.org/data-download/

```{r}

us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))

unique(us_ne$allSpecies)

unique(fao_bivalve_spp$species)

## need to filter allSpecies for anything with "Oyster", "Mussel", "Shellfish", "Clam", "Quahog",

# id bivalves and active sites
bivalve_species <- grep("Oyster|Mussel|Shellfish|Clam|Quahog", unique(us_ne$allSpecies), value=TRUE)

us_ne_bivalve <- us_ne %>%
  filter(allSpecies %in% bivalve_species) %>%
  filter(status == "Active")
unique(us_ne_bivalve$state)

us_ne_bivalve_mol <- st_transform(us_ne_bivalve, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
us_ne_bivalve_pts <- st_centroid(us_ne_bivalve_mol)
# check
plot(st_geometry(us_ne_bivalve_mol))
plot(st_geometry(st_centroid(us_ne_bivalve_mol)), add=TRUE)

us_ne_bivalve_pts_latlon <- st_transform(us_ne_bivalve_pts, crs = "+init=epsg:4326")

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
names(farms_us_ne) <- c("lon", "lat") 
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA")

# all_farms_sf <- st_as_sf(farms_us_ne, coords = c("lon", "lat"), 
#                          crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(all_farms_sf)

write_csv(farms_us_ne, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ne_usa.csv"))

```

## USA - WA, RI 
 - Aquaculture, Office for Coastal Management (OCM), 2018

Source: 
Aquaculture, Office for Coastal Management (OCM), 2018. [Accessed January 17, 2020] https://www.fisheries.noaa.gov/inport/item/53129/

```{r}
us_aqua <- st_read(file.path(path,"USA/US/us_aqua/us_aqua.shp"))

mapview(us_aqua$geometry)

unique(us_aqua$state)

## filter for species !=NA, any that are not bivalves, those that are active or conditionally active (seasonal), and filter out those we already have (NY, ME, CT, NH)

us_aqua_species <- us_aqua %>%
   dplyr::filter(!is.na(species)) %>%
  dplyr::filter(!(species %in% c("finfish", "Atlantic salmon", "Atlantic cod", "Seaweed", "Shrimp", "Coral", "clam seed, oyster seed", "Gelidium spp., Macrocystis pyrifera, M. angustifolia, M. intergrifolia, Pelagophycus spp. Euchema uncinatum (male plants only)", "oyster seed", "In progress", "Not Available", "Hatchery", "softshell", "softshell, butter", "softshell, varnish", "butter"))) %>%
  dplyr::filter(state != "Federal waters") %>%
  dplyr::filter(!(status %in% c(NA, "Pending", "Restricted-Relay", "Not Available", "Conditional Closure", "Prohibited"))) %>%
dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York")))

unique(us_aqua_species$state)

unique(us_aqua_species$species)

unique(us_aqua_species$status)

mapview(us_aqua_species$geometry)

us_aqua_bivalve_mol <- st_transform(us_aqua_species, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
us_aqua_bivalve_pts <- st_centroid(us_aqua_bivalve_mol)
# check
plot(st_geometry(us_aqua_bivalve_mol))
plot(st_geometry(st_centroid(us_aqua_bivalve_mol)), add=TRUE)

us_aqua_bivalve_pts_latlon <- st_transform(us_aqua_bivalve_pts, crs = "+init=epsg:4326")

farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
names(farms_us_aqua) <- c("lon", "lat")
farms_us_aqua <- farms_us_aqua %>%
  mutate(iso3c = "USA")

all_farms_sf <- st_as_sf(farms_us_aqua, coords = c("lon", "lat"),
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write_csv(farms_us_ne, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_wa_ri_usa.csv"))

```

## HELCOM shellfish mariculture points - Sweden, Germany

Source: 
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

```{r}

## Shellfish points
enc <- readr::guess_encoding(file.path(path, "HELCOM_Baltic/Shellfish_mariculture_points/Shellfish_mariculture_points.shp"), n_max = 1000)[,"encoding"] %>% as.character()

# Read in shapefile
farms_baltic <- st_read(file.path(path, "HELCOM_Baltic/Shellfish_mariculture_points/Shellfish_mariculture_points.shp"), options = "ENCODING=WINDOWS-1252")

mapview(farms_baltic$geometry)

baltic_pts <- st_centroid(farms_baltic)

bal_pts_latlon <- st_transform(baltic_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry, COUNTRY, NAME)

bal_subregions <- bal_pts_latlon %>%
  dplyr::select(COUNTRY, NAME)

farms_bal <- data.frame(do.call(rbind, st_geometry(bal_pts_latlon)))
names(farms_bal) <- c("lon", "lat")

farms_bal <- cbind(farms_bal, bal_subregions) %>%
  mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

write.csv(farms_bal, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_swe_deu.csv"), row.names = FALSE)

```

## HELCOM shellfish mariculture areas - Denmark

Source:
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

```{r}
## SHELLFISH polygons
# shape file
farms_baltic_area <- st_read(file.path(path, "HELCOM_Baltic/Shellfish_mariculture_areas/Shellfish_mariculture_areas.shp"), options = "ENCODING=WINDOWS-1252")

mapview(farms_baltic_area$geometry)

baltic_pts_area <- st_centroid(farms_baltic_area)

bal_pts_latlon_area <- st_transform(baltic_pts_area, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_bal_area <- data.frame(do.call(rbind, st_geometry(bal_pts_latlon_area)))
names(farms_bal_area) <- c("lon", "lat")

farms_bal_area <- farms_bal_area %>%
  mutate(iso3c = "DNK") %>%
  dplyr::select(lon, lat, iso3c)

all_farms_sf <- st_as_sf(farms_bal_area, coords = c("lon", "lat"),
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(farms_bal_area, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_dnk.csv"), row.names = FALSE)
```

## British colombia
Shellfish hatcheries: 
https://catalogue.data.gov.bc.ca/dataset/shellfish-hatcheries-coastal-resource-information-management-system-crims/resource/f161583a-1d73-4c92-bf8d-ea67727a89d3

Source: 
Shellfish Hatcheries - Coastal Resource Information Management System (CRIMS) , 2019. Ministry of Forests, Lands, Natural Resource Operations and Rural Development. [Accessed November 30, 2020] https://catalogue.data.gov.bc.ca/dataset/shellfish-hatcheries-coastal-resource-information-management-system-crims

```{r}

## read shapefile
bc <- st_read(file.path(path, "Canada/CRIMS_SHELLFISH_HATCHERIES/SHLFISH_HT_point.shp"))

mapview(bc)
bc_pts <- st_centroid(bc)

bc_pts_latlon <- st_transform(bc_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon)))
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN")

 write_csv(farms_bc, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_bc_can.csv"))

```

## Nova Scotia
Obtained data from here: https://data.novascotia.ca/Fishing-and-Aquaculture/Aquaculture-License-and-Lease-GIS-Database/h57h-p9mm

Source: 
Nova Scotia Marine Aquaculture Leases , 2020. . Nova Scotia Fisheries and Aquaculture. [Accessed February 18, 2020] https://data.novascotia.ca/Fishing-and-Aquaculture/Nova-Scotia-Marine-Aquaculture-Leases/h57h-p9mm

```{r}
## read shapefile
ns <- st_read(file.path(path,"Canada/Nova_Scotia_Marine_Aquaculture_Sites/geo_export_fcc6f2ef-82bb-4445-98f0-a82a56cd0d00.shp"))
mapview(ns)

unique(ns$aqua_speci)

# id bivalves: filter out anything that is not a bivalve
not_bivalve <- c("Atlantic Salmon; Arctic Char; Rainbow Trout", "Rainbow Trout; Atlantic Salmon; Arctic Char; Brook Trout", "Rainbow Trout; Arctic Char; Brook Trout; Atlantic Salmon","Rainbow Trout", "Atlantic Salmon; Rainbow Trout; Atlantic Halibut; Atlantic Cod; Haddock", "Atlantic Salmon", "Atlantic Salmon; Rainbow Trout", "Rainbow Trout; Atlantic Salmon"  )

ns_bivalve <- ns %>%
  filter(!(aqua_speci %in% not_bivalve))

ns_bivalve_mol <- st_transform(ns_bivalve, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
ns_pts <- st_centroid(ns_bivalve_mol)

ns_pts_latlon <- st_transform(ns_pts, crs = "+init=epsg:4326")

mapview(ns_pts_latlon)

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN")

write_csv(farms_ns, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ns_can.csv"))

```

##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production
https://www.emodnet-humanactivities.eu/view-data.php

Source: 
EMODnet Human Activities: Shellfish aquaculture, 2019. [Accessed November 30, 2020] https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production

```{r}

## read in shapefile
eu <- st_read(file.path(path,"EMODnet_HA_Aquaculture_Shellfish_20191126/EMODnet_HA_Aquaculture_Shellfish_20191126.shp"))
mapview(eu)

unique(eu$COUNTRY)
# [1] "France"         "Ireland"        "Bulgaria"       "United Kingdom" "Italy"          "Norway"        
# [7] "Denmark"        "Netherlands"    "Greece"

unique(eu$FARM_TYPE)

eu_na <- eu %>%
  dplyr::filter(STATUS == "n.a.")
unique(eu_na$COUNTRY)

eu_active <- eu %>%
  dplyr::filter(STATUS == "Active")

unique(eu_active$COUNTRY)

## we will use both "Active" and "n.a." as the status of the farms. I choose this because all of the denmark points are n.a., and they correspond with the HELCOM data that we used. This indicates to me that the farms denoted as "n.a." are probably actually active.

eu_active_na <- eu %>%
  dplyr::filter(STATUS %in% c("Active", "n.a."))

unique(eu_active_na$COUNTRY)

# [1] "France"         "Ireland"        "Bulgaria"       "United Kingdom" "Italy"          "Norway"        
# [7] "Denmark"        "Netherlands"    "Greece"

## Now filter for countries that we want: Ireland, Bulgaria, Italy, Norway, Netherlands, and Greece. UK and DNK are already accounted for in our other datatsets. 
eu_fao_countries <- eu_active_na %>%
  dplyr::filter(!(COUNTRY %in% c("France", "United Kingdom", "Denmark")))

unique(eu_fao_countries$COUNTRY)
mapview(eu_fao_countries)

eu_pts <- st_centroid(eu_fao_countries)

eu_pts_latlon <- st_transform(eu_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(COUNTRY, geometry)

eu_countries <- eu_pts_latlon %>%
  dplyr::select(COUNTRY)

farms_eu <- data.frame(do.call(rbind, st_geometry(eu_pts_latlon)))
names(farms_eu) <- c("lon", "lat")

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Ireland" ~ "IRL",
    COUNTRY == "Bulgaria" ~ "BGR", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Netherlands" ~ "NLD",
    COUNTRY == "Italy" ~ "ITA", 
    COUNTRY == "Greece" ~ "GRC"
  )) %>%
  dplyr::select(-COUNTRY)

 write_csv(farms_eu_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_IRL_BGR_NOR_NLD_ITA_GRC.csv"))

```

## Spain
https://servicio.pesca.mapama.es/acuivisor/
 - This is a map of all aquaculture facilities in Spain. It will not allow for download of the locations of the facilities. However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in. I will filter for unique cities, and place points in each place.

How to download: 
 - Make sure you only have the basemap and the "Instalaciones" layers selected.
 - Click on the filter tab and filter for "Marina" aquaculture, and for these shellfish species: 
 Abalón japonés, Almeja babosa, Almeja fina, Almeja japonesa, Almejas nep (Ruditapes spp), Almejas nep (Veneridae), Berberecho, Berberecho verde, Bivalvos, Bígaro, Coquina, Escupiña grabada, Lapa, Navaja recta, Navaja, Oreja de mar, Ostión u ostra japonesa, Ostra u ostra plana, Ostras u ostras planas, Vieira, Volandeira, Zamburiña
 - Download the data and save as a csv.

General location to place points:
 - Alicante: 38.345509445679276, -0.48793746088812184
 - Almeria: 36.83403538312481, -2.46312530015449
 - Asturias: 43.6586646127094, -5.838989914402157
 - Baleares: 39.578993240236755, 2.6312097506887446
 - Cadiz: 36.55518316813145, -6.2759664948571094
 - Cantabria: 43.488143305644364, -3.808940707432179
 - Castellon: 39.98227981322492, 0.025845987383098443
 - Gerona: 41.893397069777485, 3.1931418366760647
 - Granada: 36.69547948740147, -3.403621978170133
 - La Coruna: 43.36941893593161, -8.412121809979775
 - Las Palmas: 28.17841973419213, -15.411897095500123
 - Lugo: Inland, Don't include
 - Malaga: 36.705816371679525, -4.422146790963811
 - Murcia: Inland, don't include
 - Pontevedra: 42.42511968211785, -8.658739084602496
 - Sevilla: Inland, don't include
 - Santa Cruz de Tenerife: 28.464013540472575, -16.25186419732133
 - Tarragona: 41.109958666992036, 1.2538616546744752
 - Valencia: 39.47564987283762, -0.3208672158378773
 - Vizcaya: 43.436972390962005, -2.9200783381913014

Source: 
Acuivisor, 2019. . Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/

```{r}
## Read in dataset of company names:
spain_shellfish <- read_csv(here("marine/bivalve/bivalve_farms/data/spain_shellfish_aquaculture.csv"))

head(unique(spain_shellfish$Empresa))

communitiy <- data.frame(companies = unique(spain_shellfish$Provincia))

## there are 21 different cities where shellfish is farmed.

farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
  mutate(iso3c = "ESP")

write_csv(farms_esp, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_esp.csv"))

## visualize it 
farms_esp <-  st_as_sf(farms_esp, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_esp)

```

## Jersey 
 - Government of Jersey: https://www.gov.je/SiteCollectionDocuments/Industry%20and%20finance/ID%20Mollusc%20farms%20registered%20businesses%20page%201.pdf
  - https://www.gov.je/SiteCollectionDocuments/Industry%20and%20finance/ID%20Molluscs%20farms%20registered%20businesses%20page%202%2020181030%20DM.pdf

 - 5 licensed farms (only including "mollusc farm open")
 - Jersey Oyster Company Limited: 49.17300525845569, -2.0325974703629277
 - Seymour Oyster Company Ltd: 49.22644208989364, -2.0327040476242284
 - La Rocque Fisheries Limited: 49.17293132589725, -2.0312731919583795
 - Jersey Sea Farms: 49.231523271584344, -2.057638560247779
 - Island Dived Scallops: 49.20231914535721, -2.03533532472839

Source: 
Fish and shellfish farming, 2020. . Government of Jersey: Information and public services for the Island of Jersey. [Accessed December 4, 2020]  https://www.gov.je/Industry/FarmingFishing/Fishing/Pages/FishFarming.aspx

```{r, evalute = F}

farms_jey <- data.frame(lat = c(49.17300525845569, 49.22644208989364, 49.17293132589725, 49.231523271584344, 49.20231914535721),
                        lon = c(-2.0325974703629277, -2.0327040476242284, -2.0312731919583795, -2.057638560247779, -2.03533532472839)) %>%
  mutate(iso3c = "JEY")

write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))

## visualize it 
farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_jey)

```

## Guernsey 
 - https://www.gov.gg/fishing#:~:text=Sea%20Fisheries%20is%20responsible%20for,one%20licensed%20site%20on%20Herm.
 - Sea Fisheries is responsible for the licensing of all shellfish farms within the Bailiwick. There are a total of seven licensed aquaculture sites distributed around Guernsey's west and north coasts, as well as one licensed site on Herm. There is also an oyster farm located in a disused quarry in the north of the island.
 - Allocate 7 farms equally across coastline

Source: 
Fishing and Aquaculture, 2020. . Government of the States of Guernsey. [Accessed December 3, 2020] https://www.gov.gg/fishing#:~:text=Sea%20Fisheries%20is%20responsible%20for,one%20licensed%20site%20on%20Herm

```{r}
world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)

Guernsey <- ne_countries(scale = 10, country = "Guernsey", returnclass = "sf")

#info of our spatial vector object
Guernsey
mapview(Guernsey)
plot(Guernsey)

world <- st_as_sf(world)

Guernsey_world_crs <- st_transform(Guernsey, crs(world))

Guernsey_world_crop <- st_crop(world, Guernsey_world_crs) %>%
  dplyr::filter(scalerank == 5) ## filter for the appropriate island
plot(Guernsey_world_crop)
mapview(Guernsey_world_crop)

Guernsey_crop <- as(Guernsey_world_crop, "Spatial")

Guernsey_points_lines <- sample.line(Guernsey_crop, n = 7) ## equally place the number of farms along the coastline 
class(Guernsey_points_lines)
plot(Guernsey_points_lines)

Guernsey_points <- st_as_sf(Guernsey_points_lines)
mapview(Guernsey_points)

## now prep dataframe for lat lon points
ggy_pts <- st_centroid(Guernsey_points)

ggy_pts_latlon <- st_transform(ggy_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_ggy <- data.frame(do.call(rbind, st_geometry(ggy_pts_latlon)))
names(farms_ggy) <- c("lon", "lat")

farms_ggy_final <- farms_ggy %>%
  mutate(iso3c = "GGY")

## visualize it 
farms_ggy <-  st_as_sf(farms_ggy, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_ggy)

## write to farms folder 
write_csv(farms_ggy_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ggy.csv"))
```

## Slovenia
 - http://www.fao.org/fishery/countrysector/naso_slovenia/en#:~:text=From%20the%20345%20aquaculture%20facilities,facilities%20are%20for%20shellfish%20farming.
 - From the 345 aquaculture facilities in Slovenia, there are 26 marine aquaculture facilities, 1 of which is for fish farming, while the remaining **20 facilities are for shellfish farming**.

Source: 
National Aquaculture Sector Overview. Slovenia, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.

```{r}
world <- rnaturalearth::ne_coastline(scale = 10) #world map with 10m resolution
plot(world)

slovenia <- ne_countries(scale = 10, country = "Slovenia", returnclass = "sf")

#info of our spatial vector object
slovenia
mapview(slovenia)
plot(slovenia)

world <- st_as_sf(world)

slovenia_world_crs <- st_transform(slovenia, crs(world))

slovenia_world_crop <- st_crop(world, slovenia_world_crs) ## crop to slovenia extent
plot(slovenia_world_crop)
mapview(slovenia_world_crop)

slovenia_crop <- as(slovenia_world_crop, "Spatial")
plot(slovenia_crop)
mapview(slovenia_crop)

slovenia_points_lines <- sample.line(slovenia_crop, n = 86) ## equally place the number of farms along the coastline 
class(slovenia_points_lines)
plot(slovenia_points_lines)

slovenia_points <- st_as_sf(slovenia_points_lines)
mapview(slovenia_points)

## Now filter out the points that fall outside of Slovenia
slovenia_points_final <- slovenia_points[12:31,]
mapview(slovenia_points_final)

## prep to get lat lon 
svn_pts <- st_centroid(slovenia_points_final)

svn_pts_latlon <- st_transform(svn_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_svn <- data.frame(do.call(rbind, st_geometry(svn_pts_latlon)))
names(farms_svn) <- c("lon", "lat")

farms_svn_final <- farms_svn %>%
  mutate(iso3c = "SVN")

## visualize it 
farms_svn <-  st_as_sf(farms_svn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_svn)

## write to farms folder 
write_csv(farms_svn_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_svn.csv"))
```

## Croatia
 - This states there are 266 shellfish farm locations in Croatia: https://ec.europa.eu/fisheries/sites/fisheries/files/docs/pages/spatial-planning-for-aquaculture-hr.pdf
 - However, I can't find much else information. Due to this, I will allocate the 266 farms equally along the coast of Croatia.

Source: 
Lukin, A., 2014. Spatial Planning For Marine Aquaculture, Croatia, Zadar County Case. Croatian Ministry of Agriculture, Directorate of Fisheries.

```{r}
world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

croatia <- ne_countries(scale = 110, country = "Croatia", returnclass = "sf")

#info of our spatial vector object
croatia
mapview(croatia)
plot(croatia)

world <- st_as_sf(world)

croatia_world_crs <- st_transform(croatia, crs(world))

croatia_world_crop <- st_crop(world, croatia_world_crs) ## crop to croatia extent
plot(croatia_world_crop)
mapview(croatia_world_crop)

croatia_crop <- as(croatia_world_crop, "Spatial")
plot(croatia_crop)
mapview(croatia_crop)

croatia_points_lines <- sample.line(croatia_crop, n = 340) ## equally place the number of farms along the coastline 
class(croatia_points_lines)
plot(croatia_points_lines)

croatia_points <- st_as_sf(croatia_points_lines)
mapview(croatia_points)

## Now filter out the points that fall outside of croatia: rows 57-70
croatia_points_final <- croatia_points[2:267,]
mapview(croatia_points_final)

## get lat lon
hrv_pts <- st_centroid(croatia_points_final)

hrv_pts_latlon <- st_transform(hrv_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_hrv <- data.frame(do.call(rbind, st_geometry(hrv_pts_latlon)))
names(farms_hrv) <- c("lon", "lat")

farms_hrv_final <- farms_hrv %>%
  mutate(iso3c = "HRV")

## visualize it 
farms_hrv <-  st_as_sf(farms_hrv, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_hrv)

## write to farms folder 
write_csv(farms_hrv_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_hrv.csv"))
```

## Cuba
 - Four sites taken from this paper: https://scielo.conicyt.cl/scielo.php?script=sci_arttext&pid=S0718-560X2017000100024

Cayo Esquivel del Sur: 23.034188, -80.082047
Cayo de la Cruz: 22.994283, -79.994291
Cayo Hachuela: 22.952677, -79.963228
Cayos de la Enfermeria: 22.910246, -79.958924

Source: 
Mazon Suastegui, J.M., Rivero Suarez, S.E., Betanzos Vega, A., Saucedo, P.E., Rodriguez Jaramillo, C., Acosta Salmon, H., 2017. Potential of sites in northern Cuba for developing an industry of the native mangrove oyster (Crassostrea rhizophorae). lajar 45, 218–222. https://doi.org/10.3856/vol45-issue1-fulltext-24

```{r}

farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.910246),
                        lon = c(-80.082047, -79.994291, -79.963228, -79.958924)) %>%
  mutate(iso3c = "CUB")

write_csv(farms_cub, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_cub.csv"))

## visualize it 
farms_cub <-  st_as_sf(farms_cub, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_cub)
```

## Taiwan
 - I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. We will allocate the cells equally along the coastline (like we did for shrimp).
 - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/

Source:
NA

```{r}

gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")

 TWN_shp <- gadm %>%
  filter(GID_0 == "TWN") %>%
  st_transform(., food_crs) %>%
  mutate(Region = 1)
 mapview(TWN_shp)

st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")

twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")

plot(fake_raster)
plot(twn_reg_ras)

writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_spatial <- as(TWN_shp, "Spatial")

twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)

plot(twn_coast)
cellStats(twn_coast, "sum") #464.63

# filter to include >0 <1, o.w. NA

twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
  dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
  mutate(iso3c = "TWN") %>%
  dplyr::select(lon=x, lat=y, iso3c)

farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)

write_csv(twn_coast_df, here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))

twn <- read_csv(here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)
```

## French Polynesia
 - http://www.fao.org/3/t5816e/t5816e04.htm

 - http://www.ressources-marines.gov.pf/aquaculteurs/laquaculture-en-polynesie-francaise/les-filieres-de-laquaculture-en-polynesie-francaise/
 - Aquaculture is: for molluscs: the giant clam (Tridacna maxima).
 - To date (2019), two lagoons are authorized for the collection of giant clam spat, the lagoon of Reao and that of Tatakoto.

Backed up by this: https://aquaculture.spc.int/index.php?option=com_countries&view=country&id=6
Giant clams (Tridacna mamoibroodies_bxima) spat collection and stock enhancement techniques are mastered in Eastern Tuamotu atolls. Small scale collectors should be born in 2007.

I will place the two points at these two lagoons (the production is really small, 1200 tonnes):
 - Tatakoto: -17.349601342130857, -138.40992718639146
 - Reao: -18.50754847683744, -136.38467411084235

Source: 
The aquaculture sectors in French Polynesia , n.d. . Department of Marine Resources Pu Fa’Ahotu Moana. http://www.ressources-marines.gov.pf/aquaculteurs/laquaculture-en-polynesie-francaise/les-filieres-de-laquaculture-en-polynesie-francaise/

```{r}
farms_pyf <- data.frame(lat = c(-17.349601342130857, -18.50754847683744),
                        lon = c(-138.40992718639146, -136.38467411084235)) %>%
  mutate(iso3c = "PYF")

write_csv(farms_pyf, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_pyf.csv"))

## visualize it 
farms_pyf <-  st_as_sf(farms_pyf, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_pyf)
```

## India 
https://www.researchgate.net/publication/285488252_Mussel_Farming_and_Its_Potential_in_India
 - Has a potential map.

http://www.fao.org/fishery/countrysector/naso_india/en
 - Among maritime states, Kerala was the first to recognize the advantages of utilizing mussel farming technology in rural development, from a meagre production in 1997 where cultured mussel production rose to 1 250 tonnes in 2002 with over 250 mussel farms being established in the estuaries of Kerala.

Based on this, I will place 250 mussel farms along the coast in the Kerala state in India.

Source:
FAO Fisheries & Aquaculture - National Aquaculture Sector Overview - India, 2014. National Aquaculture Sector Overview Fact Sheets.

```{r}
world <- ne_coastline(scale = 10) #world map with 10m resolution
plot(world)

## read in state shapefile
kerala_state <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/India/Kerala/state.shp"))

#info of our spatial vector object
kerala_state
mapview(kerala_state)
plot(kerala_state)

world <- st_as_sf(world)

kerala_state_world_crs <- st_transform(kerala_state, crs(world))

kerala_state_world_crop <- st_crop(world, kerala_state_world_crs) ## crop to kerala extent
plot(kerala_state_world_crop)
mapview(kerala_state_world_crop)

kerala_state_crop <- as(kerala_state_world_crop, "Spatial")
plot(kerala_state_crop)
mapview(kerala_state_crop)

kerala_state_points_lines <- sample.line(kerala_state_crop, n = 250) ## equally place the number of farms along the coastline 
class(kerala_state_points_lines)
plot(kerala_state_points_lines)

kerala_state_points <- st_as_sf(kerala_state_points_lines)
mapview(kerala_state_points)

## Now filter out the points that fall outside of kerala_state: rows 57-70
# kerala_state_points_final <- kerala_state_points[c(1:34,42:67), ]
# mapview(kerala_state_points_final)

## get lat lon
ind_pts <- st_centroid(kerala_state_points)

ind_pts_latlon <- st_transform(ind_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_ind <- data.frame(do.call(rbind, st_geometry(ind_pts_latlon)))
names(farms_ind) <- c("lon", "lat")

farms_ind_final <- farms_ind %>%
  mutate(iso3c = "IND")

## visualize it 
farms_ind <-  st_as_sf(farms_ind, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_ind)

## write to farms folder 
write_csv(farms_ind_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ind.csv"))
```

## Thailand
NASO Maps by FAO: 
http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
 - This shows both Shrimp and Bivalve aquaculture sites in Thailand. Although it is not comprehensive, it is the best information I could find. I'll filter for the bivalve sites.

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

```{r}
## read in thailand shp file
thai_file <- file.path(path, "Thailand/Thailand.kmz")

thai_aqua <- read_sf(thai_file)

mapview(thai_aqua)

## We need to filter for just bivalve aquaculture. The best way that I found to do this was to look at the .kmz file in google earth pro, and determine with rows are bivalves..

## NASO 4,5,6,7 are the bivalves:
unique(thai_aqua$Name)

thai_bivalve <- thai_aqua %>%
  dplyr::filter(Name %in% c("[NASO / 4]", "[NASO / 5]", "[NASO / 6]", "[NASO / 7]"))

mapview(thai_bivalve)

tha_bivalve_mol <- st_transform(thai_bivalve, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
tha_pts <- st_centroid(tha_bivalve_mol)

tha_pts_latlon <- st_transform(tha_pts, crs = "+init=epsg:4326")

mapview(tha_pts_latlon)

farms_tha <- data.frame(do.call(rbind, st_geometry(tha_pts_latlon))) 
names(farms_tha) <- c("lon", "lat")
farms_tha <- farms_tha %>%
  mutate(iso3c="THA")

write_csv(farms_tha, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_tha.csv"))

farms_tha <-  st_as_sf(farms_tha, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_tha)
```

## Indonesia 
http://www.fao.org/3/AB716E/AB716E08.htm#:~:text=The%20commercially%20important%20bivalve%20species,is%20largely%20experimental%20at%20present.&text=Total%20shellfish%20production%20for%201984,for%20about%202.2%20%25%20of%20this.

 - This has a map of major oyster capture and culture areas in Indonesia... This will have to do. Approximate locations listed below.

 From left to right on the map: 
 3.2182751224662542, 99.69952320753342
 -5.964150035506321, 106.35924782378112
 -6.2646012824936275, 108.0659620387556
 -6.75680397048712, 108.64496221771543
 -6.975573928794459, 112.61871244712762
 -4.984732967006041, 120.31326531641196
 0.8890896205268102, 123.52557614041675
 -3.436748178542682, 129.1920950239657
 -5.142358892765042, 137.4727448207172

Source:
NETWORK OF AQUACULTURE CENTRES IN ASIA: Status of oyster culture in selected Asian countries, 1988.

```{r}
farms_idn <- data.frame(lat = c(3.2182751224662542, -5.964150035506321, -6.2646012824936275, -6.75680397048712, -6.975573928794459, -4.984732967006041, 0.889089620526810, -3.436748178542682, -5.142358892765042),
                        lon = c(99.69952320753342, 106.35924782378112, 108.0659620387556, 108.64496221771543, 112.61871244712762, 120.31326531641196, 123.52557614041675, 129.1920950239657, 137.4727448207172)) %>%
  mutate(iso3c = "IDN")

write_csv(farms_idn, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_idn.csv"))

## visualize it 
farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_idn)

```

## Russia
 - This probably doesn't really matter, because the production is so low, and the coastline is so big...
 - I can't find any good information on shellfish farming in Russia. I will place a point along the coast.
 - It does seem like scallop farming primarily occurs on the east coast, so I will place it there.

Source:
NA

```{r}

farms_rus <- data.frame(lat = c(43.053493816917545),
                        lon = c(131.95698485517275)) %>%
  mutate(iso3c = "RUS")

write_csv(farms_rus, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_rus.csv"))

## visualize it 
farms_rus <-  st_as_sf(farms_rus, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_rus)

```

## Korea, Dem. People's Rep
**Revisiting Changing Patterns of North Koreaʹs Fisheries Production: 1990s‐2000s**
"By the 1980s, there has been 60 or more fish farming companies in North
Korea's national distribution"

 - I'll place 60 farms along the coast of north korea. Although this specifies "fish farms", it is better than nothing. And there are probably more than 60 farms (shell fish or not), nowadays.

Source:
Park, S., Hong, S., 2012. Revisiting Changing Patterns of North Koreaʹs Fisheries Production: 1990s‐2000s 19.

```{r}
world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

north_korea <- ne_countries(scale = 110, country = "North Korea", returnclass = "sf")

#info of our spatial vector object
north_korea
mapview(north_korea)
plot(north_korea)

world <- st_as_sf(world)

north_korea_world_crs <- st_transform(north_korea, crs(world))

north_korea_world_crop <- st_crop(world, north_korea_world_crs) ## crop to north korea extent
plot(north_korea_world_crop)
mapview(north_korea_world_crop)

north_korea_crop <- as(north_korea_world_crop, "Spatial")
plot(north_korea_crop)
mapview(north_korea_crop)

north_korea_points_lines <- sample.line(north_korea_crop, n = 67) ## equally place the number of farms along the coastline 
class(north_korea_points_lines)
plot(north_korea_points_lines)

north_korea_points <- st_as_sf(north_korea_points_lines)
mapview(north_korea_points)

## Now filter out the points that fall outside of north_korea: rows 57-70
north_korea_points_final <- north_korea_points[c(1:34,42:67), ]
mapview(north_korea_points_final)

# extract lat lon
prk_pts <- st_centroid(north_korea_points_final)

prk_pts_latlon <- st_transform(prk_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_prk <- data.frame(do.call(rbind, st_geometry(prk_pts_latlon)))
names(farms_prk) <- c("lon", "lat")

farms_prk_final <- farms_prk %>%
  mutate(iso3c = "PRK")

## visualize it 
farms_prk <-  st_as_sf(farms_prk, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_prk)

## write to farms folder 
write_csv(farms_prk_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_prk.csv"))
```

## Brazil 
http://www.fao.org/fishery/countrysector/naso_brazil/en
"Mollusc farming was introduced into Brazil in the 1960s but only since 1989 has this activity developed as an important economic alternative for small-scale fishermen. Besides the generation of income and employment, bivalve culture has had a noticeable effect in contributing to the stabilisation of traditional communities on their original lands. Today, there are no large companies in this sector and small farmers are organized into associations and cooperatives. Santa Catarina State in the South region is responsible for 93 percent of Brazilian bivalve mollusc production."

https://onlinelibrary.wiley.com/doi/full/10.1111/raq.12107
 "Currently, the total bivalve production reaches 19 082 tons, with **729 marine farmers** scattered among the 12 municipalities mentioned above, and marine aquaculture has now reached an important position in Santa Catarina State as a significant contributor to food production, providing employment and livelihood opportunities and representing a legitimate use of the marine environment for sustainable food production"

Of the 837 aquaculture areas grouped inside the **27 aquaculture parks** originally proposed by the PLDM, 798 areas and 24 parks are already licensed and attended by **618 shellfish farmers** who represent 74% of all shellfish farmers in Santa Catarina State

 - Based on this paper, I will assign 27 points along the coastline of Santa Catarina state. I'm assuming that the 3 remaining unlicensed aquaculture parks are licensed now.

Source:
Suplicy, F.M., Vianna, L.F. de N., Rupp, G.S., Novaes, A.L.T., Garbossa, L.H.P., de Souza, R.V., Guzenski, J., da Costa, S.W., Silva, F.M., dos Santos, A.A., 2017. Planning and management for sustainable coastal aquaculture development in Santa Catarina State, south Brazil. Rev Aquacult 9, 107–124. https://doi.org/10.1111/raq.12107

```{r}

## read in state shape 
sta_catarina <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Brazil/Santa_Catarina/dc172qt8462.shp"))
mapview(sta_catarina)

world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

#info of our spatial vector object
sta_catarina
mapview(sta_catarina)
plot(sta_catarina)

world <- st_as_sf(world)

sta_catarina_world_crs <- st_transform(sta_catarina, crs(world))

sta_catarina_world_crop <- st_crop(world, sta_catarina_world_crs) ## crop to santa catarina extent
plot(sta_catarina_world_crop)
mapview(sta_catarina_world_crop)

sta_catarina_crop <- as(sta_catarina_world_crop, "Spatial")
plot(sta_catarina_crop)
mapview(sta_catarina_crop)

sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 27) ## equally place the number of farms along the coastline 
class(sta_catarina_points_lines)
plot(sta_catarina_points_lines)

sta_catarina_points <- st_as_sf(sta_catarina_points_lines)
mapview(sta_catarina_points)

## get lat lon
bra_pts <- st_centroid(sta_catarina_points)

bra_pts_latlon <- st_transform(bra_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_bra <- data.frame(do.call(rbind, st_geometry(bra_pts_latlon)))
names(farms_bra) <- c("lon", "lat")

farms_bra_final <- farms_bra %>%
  mutate(iso3c = "BRA")

## visualize it 
farms_bra <-  st_as_sf(farms_bra, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bra)

## write to farms folder 
write_csv(farms_bra_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_bra.csv"))
```

## Philippines

http://www.fao.org/3/AB710E/AB710E18.htm#ann12
 - This has the number of farms per province. I will allocate those number equally along the coastline of each province that has farms

LOCATION	Number of farms	
Zambales	 	 	NA
Bulacan	 	 	NA
Mindoro Oriental	 NA
Palawan	 	 	NA
Quezon	 	  NA
Capiz	**300**		NA
Iloilo	 	 	NA
Aklan	 	 	NA
Negros Occidental	**6** 
Cebu	 	 	NA
Bohol	 	 	NA
Leyte	 	 	NA
Samar	**250**	
Total	**556**

Source:
REPORT OF THE WORKSHOP AND STUDY TOUR ON MOLLUSC SANITATION AND MARKETING, 1989. . Food and Agriculture Organization of the United Nations.

```{r}
## read in province shape
provinces <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/philippines/provinces/Provinces.shp"))

mapview(provinces)

## filter provinces for the ones we want
provinces_farms <- provinces %>%
  dplyr::filter(NAME_1 %in% c("Capiz", "Negros Occidental", "Samar"))

mapview(provinces_farms)

world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

# start with Capiz
capiz <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Capiz")
mapview(capiz)
plot(capiz)

world <- st_as_sf(world)

capiz_world_crs <- st_transform(capiz, crs(world))

capiz_world_crop <- st_crop(world, capiz_world_crs) ## crop to extent
plot(capiz_world_crop)
mapview(capiz_world_crop)

capiz_crop <- as(capiz_world_crop, "Spatial")
plot(capiz_crop)
mapview(capiz_crop)

capiz_points_lines <- sample.line(capiz_crop, n = 300) ## equally place the number of farms along the coastline 
class(capiz_points_lines)
plot(capiz_points_lines)

capiz_points <- st_as_sf(capiz_points_lines)
mapview(capiz_points)

world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

# now do negros
negros <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Negros Occidental")
mapview(negros)
plot(negros)

world <- st_as_sf(world)

negros_world_crs <- st_transform(negros, crs(world))

negros_world_crop <- st_crop(world, negros_world_crs)

negros_world_crop <- head(negros_world_crop, 1)
plot(negros_world_crop)
mapview(negros_world_crop)

negros_crop <- as(negros_world_crop, "Spatial")
plot(negros_crop)
mapview(negros_crop)

negros_points_lines <- sample.line(negros_crop, n = 6) ## equally place the number of farms along the coastline 
class(negros_points_lines)
plot(negros_points_lines)

negros_points <- st_as_sf(negros_points_lines)
mapview(negros_points)

world <- ne_coastline(scale = 110) #world map with 50m resolution
plot(world)

# now do samar 
samar <- provinces_farms %>%
  dplyr::filter(NAME_1 == "Samar")
mapview(samar)
plot(samar)

world <- st_as_sf(world)

samar_world_crs <- st_transform(samar, crs(world))

samar_world_crop <- st_crop(world, samar_world_crs)

samar_world_crop <- head(samar_world_crop, 1)
plot(samar_world_crop)
mapview(samar_world_crop)

samar_crop <- as(samar_world_crop, "Spatial")
plot(samar_crop)
mapview(samar_crop)

samar_points_lines <- sample.line(samar_crop, n = 250) ## equally place the number of farms along the coastline 
class(samar_points_lines)
plot(samar_points_lines)

samar_points <- st_as_sf(samar_points_lines)
mapview(samar_points)

## bind all three states together
all_points <- rbind(samar_points, negros_points, capiz_points)
mapview(all_points)

# get lat lon points
phl_pts <- st_centroid(all_points)

phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
names(farms_phl) <- c("lon", "lat")

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL")

## visualize it 
farms_phl <-  st_as_sf(farms_phl, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_phl)

## write to farms folder 
write_csv(farms_phl_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_phl.csv"))
```

## Malaysia
http://www.fao.org/fishery/countrysector/naso_malaysia/en
"Brackish water aquaculture is characterized by the extensive culture of bivalve molluscs, occupying an area of 7 659 ha, mostly in the western coastal waters where there is an abundance of mud flats suitable for the culture of blood cockles"

 - I'll place a point on the western coast:
 - 4.074359958576369, 100.73343376478226

Source: 
NA

```{r}

farms_mys <- data.frame(lat = c(4.074359958576369),
                        lon = c(100.73343376478226)) %>%
  mutate(iso3c = "MYS")

write_csv(farms_mys, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_mys.csv"))

## visualize it 
farms_mys <-  st_as_sf(farms_mys, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mys)

```

## Cambodia 
http://www.fao.org/fishery/countrysector/naso_cambodia/en
 - There is no good information on the location of farms, I will just place a point on the coast. 
 - 11.069927194335508, 103.64594001534627

Source:
NA

```{r}

farms_khm <- data.frame(lat = c(11.069927194335508),
                        lon = c(103.64594001534627)) %>%
  mutate(iso3c = "KHM")

write_csv(farms_khm, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_khm.csv"))

## visualize it 
farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_khm)

```

## Hong Kong
https://www.afcd.gov.hk/english/fisheries/fish_aqu/fish_aqu_mpo/fish_aqu_mpo.html

All farms are located in Deep Bay, specifically shown in the map.

 - I will place a point in Deep Bay

Source: 
Marine fish culture, pond fish culture and oyster culture, n.d. . Agriculture, Fisheries, and Conservation Department; The Government of the Hong Kong Special Administrative Region.  https://www.afcd.gov.hk/english/fisheries/fish_aqu/fish_aqu_mpo/fish_aqu_mpo.html

```{r}

farms_hkg <- data.frame(lat = c(22.48384043911231),
                        lon = c(113.98143449612208)) %>%
  mutate(iso3c = "HKG")

write_csv(farms_hkg, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_hkg.csv"))

## visualize it 
farms_hkg <-  st_as_sf(farms_hkg, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_hkg)

```

# Join cell count dataframes

```{r}
farm_files <- list.files(here::here("marine/bivalve/bivalve_farms/data/bivalve_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(all_farms, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)

```

### 2021-02-04 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
cleaned up scripts and updated file paths

---
title: "Location of crustacean Farms"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script standardizes location of crustacean farms to be lat/long point data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

fao_crustacean_spp <- read_csv("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans_taxa_production.csv") %>%
  dplyr::filter(year == 2017)
fao_crustacean <- read_csv("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv") %>%
  dplyr::filter(year == 2017)

unique(fao_crustacean$country)

```

# Raster

Standard raster used for this analysis

```{r}

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

Now we will map crustacean farms. Workflow will be as follows:

 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of crustacean farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

## Indonesia
Can't find any infomration on crab farm locations in Indonesia. I will place one farm, randomly on the coast of Indonesia.

Source: 
NA

```{r}

farms_idn <- data.frame(lat = c(0.3359943014669836),
                        lon = c(117.55582991782983)) %>%
  mutate(iso3c = "IDN")

write_csv(farms_idn, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_idn.csv"))

## visualize it 
farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_idn)
```

## China

Can't find any datasets of marine crustacean farm locations in China. I will place one farm randomly on the coast of China.

Source: 
NA

```{r}

farms_chn <- data.frame(lat = c(29.378009267567716),
                        lon = c(121.95043909100868)) %>%
  mutate(iso3c = "CHN")

write_csv(farms_chn, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_chn.csv"))

## visualize it 
farms_chn <-  st_as_sf(farms_chn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_chn)
```

## Bangladesh

https://www.researchgate.net/publication/318250461_Mud_crab_aquaculture_and_fisheries_in_coastal_Bangladesh

"Mud crabs have already gained popularity among coastal communities in greater Khulna and Chittagong regions (Azam et al. 1998) and are being recognized as a candidate species for culture in brackishwater environments (Ballao et al. 1999). There are about 300,000 people directly or indirectly connected with mud crab farming activities."

 - I'll place points in the Khulna and Chittagong regions, since I can't find any other information on mud crab aquaculture locations in Bangladesh.

 - Khulna: 21.876081791221054, 89.49499697244659
 - Chittagong: 22.325919306644522, 91.76441856678511

Source: 
Rahman, M., Islam, M.A., Haque, S.M., Wahab, A., 2017. Mud Crab Aquaculture and Fisheries in Coastal Bangladesh 7.

```{r}

farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325919306644522),
                        lon = c(89.49499697244659, 91.76441856678511)) %>%
  mutate(iso3c = "BGD")

write_csv(farms_bgd, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_bgd.csv"))

## visualize it 
farms_bgd <-  st_as_sf(farms_bgd, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bgd)
```

## Myanmar

http://www.fao.org/3/ad497e/ad497e05.htm
"Mud crab farming is also important in Myanmar. Mud crab (Scylla serrata, and related species) culture in mangroves or tidal flats is practiced mainly in the Ayeyarwaddy delta area, in Rakhine and southern parts of Myanmar."

 - I'll place points in Ayeyarwaddy region and Rakhine state.
 - Ayeyarwaddy: 15.930407995930784, 94.76647475697742
 - Rakhine: 18.615093163569437, 94.24290607527016

Source:
Myanmar aquaculture and inland fisheries, 2003. Food and Agriculture Organization of the United Nations Regional Office For Asia and the Pacific.

```{r}

farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
                        lon = c(94.76647475697742, 94.24290607527016)) %>%
  mutate(iso3c = "MMR")

write_csv(farms_mmr, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_mmr.csv"))

## visualize it 
farms_mmr <-  st_as_sf(farms_mmr, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mmr)
```

## Viet nam

https://aciar.gov.au/sites/default/files/legacy/node/693/ias36_pdf_18085.pdf
"In addition to harvesting wild stock, mud crabs are now being farmed in
many coastal provinces in Vietnam, including Quang Ninh, Hai Phong,
Thanh Hoa, Ninh Binh, Nghe An, Thua Thien–Hue, Ba Ria–Vung Tau,
Ho Chi Minh City, Ben Tre, Tra Vinh, Soc Trang, Minh Hai, Kien Giang
and Bac Lieu."

"It is difficult to know how many people participate in this industry.
Apparently, no formal surveys have been conducted, there are no known
official statistics, and crab farming is typically undertaken together with
other activities, such as shrimp and/or fish aquaculture, other primary
production such as rice growing, or even as a sideline to paid employment."

"Table 4 gives the sole set of official statistics on crab aquaculture area and
production in Vietnam in 2004. The statistics cover both mud crabs and
blue swimmer crabs, and were collated by the Vietnamese Ministry of
Fisheries from reports of provincial fishery departments. "

 - Table on page 20: This is a table from 2004, but it will have to do. It also has production estimates, which is nice. I will randomly place a point along the coast in each province, and allocate the production accordingly in step 3.. 
  - NOTE: for the production, we are assuming that not reported within a province == 0 production, due to the lack of data.

  - Quang Ninh: prod = 0: 21.186050529545593, 107.60858937642442
  - Hai Phong: prod = 1650: 20.840947248646557, 106.77685003845498
  - Thai Binh: prod = 0: 20.454148639095266, 106.59728856581118
  - Nam Dinh: prod = 0: 20.146554460540862, 106.3298019452741
  - Ninh Binh: prod = 1005: 19.955496263213185, 106.03097468374126
  - Thanh Hoa: prod = 970: 19.726817666482322, 105.87661730467457
  - Nghe An: prod = 0: 18.982876968029743, 105.6165097440173
  - Ha Tinh: prod = 200: 18.456817613512555, 105.92726656633255
  - Quang Binh: prod = 110: 17.56001328746647, 106.58039999954293
  - Quang Tri: prod = 20: 16.905826522213328, 107.19194145855845
  - TT Hue: prod = 82: 16.495115996149718, 107.74891583338649
  - Da Nang: prod = 0: 16.167986126005765, 108.15075180169012
  - Quang Nam: prod = 135: 15.699026568754403, 108.48016289264334
  - Quang Ngai: prod = 0: 15.010595152983287, 108.92174225624275
  - Binh Dinh: prod = 130: 14.17668770026659, 109.19617116389627
  - Phu Yen: prod = 0: 13.335760529041393, 109.29183511586322
  - Khanh Hoa: prod = 0: 12.299111935360338, 109.23699322130719
  - Ninh Thuân: prod = 5: 11.62183927318579, 109.1546891359726
  - Binh Thuân: prod = 0: 10.830102342204183, 108.03702110643216
  - Long An: prod = 250: 10.510731358280973, 106.7310999868549
  - Tien Giang: prod = 0: 10.30006571666483, 106.78122716883196
  - Ben Tre: prod = 637: 10.037866832581582, 106.69637036338817
  - Tra Vinh: prod = 1196: 9.592223563185232, 106.54126727713718
  - Soc Trang: prod = 0: 9.389580381208823, 106.1857446280396
  - Bac Lieu: prod = 3466: 9.147921315425062, 105.59613926925006
  - Ca Mau: prod = 0: 8.674166818318303, 105.12379673906345
  - Kien Giang: prod = 170: 10.087872204898957, 104.88743812284027
  - Can Tho: prod = 0: 10.055231, 105.789267

Viet Nam: 
Lindner, B., 2005. IMPACTS OF MUD CRAB HATCHERY TECHNOLOGY IN VIETNAM 68.

```{r}

farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055231),
                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.789267),
                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
  mutate(iso3c = "VNM")

write_csv(farms_vnm, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_vnm.csv"))

## visualize it 
farms_vnm_map <-  st_as_sf(farms_vnm, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_vnm_map)
```

## Philippines

All former reports can be found here: 
https://psa.gov.ph/content/fisheries-statistics-philippines

Fisheries statistics of the Philippines: https://psa.gov.ph/sites/default/files/Fisheries%20Statistics%20of%20the%20Philippines%2C%202017-2019.pdf

Table 125: TABLE 125 Volume of Mud Crab Production in Aquaculture by Region and Province,
 Philippines: 2017 - 2019

 - I've saved the table in Aurora as a .csv.

 - I'll place a point in each location listed in the table, and use the production estimates to allocate the FAO production equally (although the number is almost the same as reported in the FAO, off by 3 tonnes).

Consider using this data for future iterations... 
https://openstat.psa.gov.ph/PXWeb/pxweb/en/DB/search/?searchquery=aquaculture&rxid=bdf9d8da-96f1-4100-ae09-18cb3eaeb313

Source: 
Fisheries Statistics of the Philippines, 2017-2019, 2020. . Philippine Statistics Authority. [Accessed December 18, 2020]

```{r}
phl_mudcrab_prod <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Philippines/phl_mudcrab_production.csv")) %>%
  dplyr::select(-X6) %>%
  mutate(`2017` = as.numeric(`2017`), 
         `2018` = as.numeric(`2018`),
         `2019` = as.numeric(`2019`)) %>%
  pivot_longer(cols = c(`2017`, `2018`, `2019`), names_to = "year", values_to = "prod") %>%
  dplyr::filter(!is.na(prod), 
                year == 2017)

## now we need to find coordinates for each province. I will randomly select a lat lon point along the coast of each province:

provinces <- data.frame(Province = unique(sort(phl_mudcrab_prod$Province))) %>%
  mutate(lat_lon = c("9.190611500208238, 125.52994229122065", "11.737731148020183, 122.36341263788152", "13.21836252920181, 123.77011641931539", "11.096612509189843, 122.04466274447995", "14.588280500720717, 120.39232212075018", "10.062398891617871, 124.08857333922121", "14.759345796261423, 120.79195178365572", "14.278379190276917, 122.80695157663077", "13.728018225223346, 123.21602051808212", "11.544441602769396, 122.87251489793287", "13.600373850277089, 124.08856214435265", "7.226273453773761, 125.8615542691359", "7.29064081849023, 125.70838297490391", "6.8067269257546394, 125.38044959114181", "7.021850825639651, 126.44668668618641", "10.249781995409927, 125.64231490812028", "11.457019560196713, 125.50124809292508", "18.35920136671901, 121.62457647441146", "14.294681717859676, 120.71661934172276", "10.565159685797113, 122.51279683720878", "16.5330902343553, 120.31511351999148", "8.187575265346036, 124.12440346213432", "10.86506672011331, 124.72028684317488", "17.08773382905305, 120.43638606220428", "17.205031284221167, 120.4139227279512", "10.891325726593882, 122.7831164266059", "6.994603962157642, 123.99059538388416", "13.344206870917525, 121.82133665840661", "12.576951933159716, 123.28286940887746", "14.510536378070825, 121.08748285435844", "8.483931963597566, 123.80942490173003", "8.846965587470466, 125.16333794567215", "9.943820309588942, 122.44630440874657", "12.509837523018708, 124.65010656730024", "13.415437014491157, 121.0922973705213", "10.038412865363988, 118.7206892394855", "14.855971440318308, 120.58766325017285", "16.124387999329027, 120.09336724359946", "14.664908885542868, 121.61549543341468", "12.585717059110207, 122.27016916837972", "12.007625357698121, 124.69126813617964", "12.818661572681938, 123.83950186846029", "6.373081834977807, 124.08215994073517", "9.555721530351239, 125.78630860627861", "9.013346905513, 126.23742298508941", "6.9053988560744335, 122.0691745144182", "8.18224915422801, 122.95491554623727", "7.81172076996685, 123.42354992829671", "7.703880319874889, 122.52615049321432", "15.272079732639275, 120.00987788280406")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",")

## Now join together with our larger dataset

phl_lat_lon <- phl_mudcrab_prod %>%
  left_join(provinces, by = "Province") %>%
  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
  mutate(iso3c = "PHL")

write_csv(phl_lat_lon, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_phl.csv"))

## visualize it 
farms_phl_map <-  st_as_sf(phl_lat_lon, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_phl_map)
```

# Join cell count dataframes

```{r}
farm_files <- list.files(here::here("marine/crustaceans/crustacean_farms/data/crustacean_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)

```

### 2021-02-04 marine/marine_fish_general/finfish_farms/STEP1_fao_finfish_production.Rmd
cleaned up scripts and updated file paths

---
title: "FAO marine finfish production"
author: "Gage Clawson"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

All data is ultimately adjusted to FAO production data.  This script cleans the fao mariculture data and subsets it to to the relevant years of data and species (marine fish - general).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))

```

Subset the data to include only the species (marine fish general) and countries we are interested in. Then summarize by total tonnes of finfish per country/year.

```{r}

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for marine fish
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
finfish_list <- species_list$species[species_list$aq_group=="marine_fish_general"]
finfish_list

## write out marine fish taxa and production for Juliette
fao_finfish_taxa_prod <- fao %>%
  filter(species %in% finfish_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

write.csv(fao_finfish_taxa_prod, here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish_taxa_production.csv"), row.names=FALSE)

# include only marine finfish
fao_finfish <- fao %>%
  filter(species %in% finfish_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year)

write.csv(fao_finfish, here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv"), row.names=FALSE)

## Explore some of the data:         
explore <- read_csv(here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round(fao_tonnes_production/sum(fao_tonnes_production)*100,2))

emod_countries <- explore %>%
  dplyr::filter(country %in% c("Cyprus", "Greece", "Malta", "Norway", "Spain"))
sum(emod_countries$percent)
sum(emod_countries$fao_tonnes_production)

## ASC Countries
 # "Turkey", "Croatia", "Greece", "Albania", "Spain", "Japan", "Australia", "Mexico", "Panama", "United States of America", "Viet Nam", "Thailand"

asc_countries <- explore %>%
  dplyr::filter(country %in% c( "Turkey", "Croatia", "Albania", "Japan", "Australia", "Mexico", "Panama", "United States of America", "Viet Nam", "Thailand"))
sum(asc_countries$percent)
sum(asc_countries$fao_tonnes_production)

unique(sort(asc_countries$country))

```

### 2021-02-04 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
cleaned up scripts and updated file paths

---
title: "Location of Marine fish - general Farms"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/08/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script standardizes location of marine fish - general (finfish) farms to be lat/long point data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

fao_finfish_spp <- read_csv("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish_taxa_production.csv") %>%
  dplyr::filter(year == 2017)

fao_finfish <- read_csv("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv") %>%
  dplyr::filter(year == 2017)

unique(fao_finfish$country)

#  [1] "Albania"                  "Australia"                "Bangladesh"               "Cambodia"                
#  [5] "China"                    "China, Hong Kong SAR"     "Costa Rica"               "Croatia"                 
#  [9] "Cyprus"                   "Egypt"                    "France"                   "Greece"                  
# [13] "India"                    "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [17] "Italy"                    "Japan"                    "Korea, Republic of"       "Malaysia"                
# [21] "Malta"                    "Mauritius"                "Mexico"                   "Norway"                  
# [25] "Panama"                   "Philippines"              "Portugal"                 "Saudi Arabia"            
# [29] "Singapore"                "Spain"                    "Taiwan Province of China" "Thailand"                
# [33] "Tunisia"                  "Turkey"                   "United Arab Emirates"     "United States of America"
# [37] "Viet Nam"     
```

## explore
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

```{r}
ASC_data <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp"))

ASC_finfish <- ASC_data %>%
  dplyr::filter(aq_grop == "marine_fish_general")

unique(ASC_finfish$crt_cnt)

#  [1] "Turkey"                   "Croatia"                  "Greece"                   "Albania"                 
#  [5] "Spain"                    "Japan"                    "Netherlands"              "Denmark"                 
#  [9] "Australia"                "Mexico"                   "Panama"                   "United States of America"
# [13] "Germany"                  "Viet Nam"                 "Thailand"

## what is in ASC and not in FAO
setdiff(ASC_finfish$crt_cnt, fao_finfish$country)
# [1] "Netherlands" "Denmark"     "Germany"

## what is in FAO and not ASC -- this is what we need to find alternative data sources for (25 countries)
setdiff(fao_finfish$country, ASC_finfish$crt_cnt)
#  [1] "Bangladesh"               "Cambodia"                 "China"                    "Costa Rica"               "Cyprus"                  
#  [6] "Egypt"                    "France"                   "India"                    "Indonesia"                "Iran (Islamic Rep. of)"  
# [11] "Israel"                   "Italy"                    "Korea, Republic of"       "Malaysia"                 "Malta"                   
# [16] "Mauritius"                "Norway"                   "Philippines"              "Portugal"                 "Saudi Arabia"            
# [21] "Singapore"                "Taiwan Province of China" "Tunisia"                  "United Arab Emirates"

```

# Raster

Standard raster used for this analysis

```{r}

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

# Map data from ASC

Data comes from https://gis.asc-aqua.org/arcgis_app/

Source:
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}

# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_finfish$crt_cnt, origin = 'country.name', destination = 'iso3c'))

# read in shp
farms_all <- ASC_finfish %>%
  cbind(iso) %>%
  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands")))

mapview(farms_all$geometry)

unique(farms_all$iso3c)

all_pts <- st_centroid(farms_all)

all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry, iso3c)

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

## save farm location
write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)

```

Now we will map the remaining countries with marine finfish farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of finfish farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine finfish farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

##  Europe - EMODNET: Malta, Greece, Norway, Cyprus, Spain 
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production
https://www.emodnet-humanactivities.eu/view-data.php

Source:
EMODnet Human Activities: Finfish production, 2019. [Accessed December 8, 2020] 
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production

```{r}

## read in shapefile
eu <- st_read(file.path(path,"EMODnet_HA_Aquaculture_Marine_Finfish_20190104/EMODnet_HA_Aquaculture_Marine_Finfish_20190104.shp"))
mapview(eu)

unique(eu$COUNTRY)
# [1] "Spain"          "United Kingdom" "Greece"         "Finland"        "Norway"         "Ireland"        "Malta"          "Denmark"       
# [9] "Cyprus"

unique(eu$FARM_TYPE)

unique(eu$SPECIES_DE)

unique(eu$STATUS)

eu_spp <- eu %>%
  dplyr::filter(str_detect(SPECIES_DE, "Mediterranean marine fish|alibut|eabass|eabream|urbot|Sole|sole|sea bream|sea bass|Sea bream|Sea bass"))

unique(eu_spp$COUNTRY)

## Need to filter for the ones in FAO dataset
# [1] "Spain" - yes          "United Kingdom" - no "Greece" - yes        "Norway" - yes        "Denmark" - no       "Cyprus" - yes  "Malta" - yes

eu_na <- eu_spp %>%
  dplyr::filter(STATUS == "n.a.")
unique(eu_na$COUNTRY)

eu_active <- eu_spp %>%
  dplyr::filter(STATUS == "Active")

unique(eu_active$COUNTRY)

## we will use both "Active" and "n.a." as the status of the farms. I choose this because all of the denmark points are n.a., and they correspond with the HELCOM data that we used for other spp groups. This indicates to me that the farms denoted as "n.a." are probably actually active.

eu_active_na <- eu_spp %>%
  dplyr::filter(STATUS %in% c("Active", "n.a."))

unique(eu_active_na$COUNTRY)

# [1] "Spain"          "United Kingdom" "Greece"         "Malta"          "Norway"         "Denmark"        "Cyprus"

## Now filter for countries that we want: Spain, Greece, Norway, Cyprus, Malta... the others are not included in FAO 2017
eu_fao_countries <- eu_active_na %>%
  dplyr::filter(COUNTRY %in% c("Spain", "Greece", "Norway", "Cyprus", "Malta"))

unique(eu_fao_countries$COUNTRY)
mapview(eu_fao_countries)

eu_pts <- st_centroid(eu_fao_countries)

eu_pts_latlon <- st_transform(eu_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(COUNTRY, geometry)

eu_countries <- eu_pts_latlon %>%
  dplyr::select(COUNTRY)

farms_eu <- data.frame(do.call(rbind, st_geometry(eu_pts_latlon)))
names(farms_eu) <- c("lon", "lat")

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY)

 write_csv(farms_eu_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ESP_CYP_NOR_GRC_MLT.csv"))

```

## Italy
From http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/italy/en/

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

```{r}
## read in thailand shp file
italy_file <- file.path(path, "FAO_NASO/NASO/Point/Italy.kml")

italy_aqua <- read_sf(italy_file)

unique(italy_aqua$description)

mapview(italy_aqua)

## We need to filter for just the appropriate species of finfish aquaculture

italy_finfish <- italy_aqua %>%
  dplyr::filter(!(description %in% c("Floating Cages","Oysters<br>Mussels", "Freshwater farm<br><br>Strugeons<br>Stripped bass"))) %>%
  dplyr::filter(!is.na(description))

mapview(italy_finfish)

ita_bivalve_mol <- st_transform(italy_finfish, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
ita_pts <- st_centroid(ita_bivalve_mol)

ita_pts_latlon <- st_transform(ita_pts, crs = "+init=epsg:4326")

mapview(ita_pts_latlon)

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA")

write_csv(farms_ita, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ita.csv"))

farms_ita <-  st_as_sf(farms_ita, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_ita)
```

## France, Israel
http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/mediterranean-basin/en/

 - It says both Tuna and Finfish, but we'll assume france and israel are just finfish...

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

```{r}
## read in thailand shp file
france_file <- file.path(path, "FAO_NASO/NASO/Point/Mediterranean.kml")

france_aqua <- read_sf(france_file)

med_countries <- france_aqua %>%
  dplyr::mutate(country = sub("_.*", "", Name)) %>%
  dplyr::mutate(country = sub(" fishpen A", "", country))

unique(med_countries$country)

## We need to filter for just the appropriate species of finfish aquaculture, France, Israel

med_finfish <- med_countries %>%
  dplyr::filter(country %in% c("France", "Israel"))

mapview(med_finfish)

fra_finfish_mol <- st_transform(med_finfish, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
fra_pts <- st_centroid(fra_finfish_mol)

fra_pts_latlon <- st_transform(fra_pts, crs = "+init=epsg:4326")

mapview(fra_pts_latlon)

countries <- fra_pts_latlon %>%
  dplyr::select(country)

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry)

write_csv(farms_fra, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_fra_isr.csv"))

farms_fra <-  st_as_sf(farms_fra, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_fra)
```

## Indonesia
NASO maps 
 - Per the FAO aquaculture sector report, Indonesia basically only grows grouper/milkfish, so I will assume this is all grouper/milkfish.

Source: 
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

```{r}
indo_file <- file.path(path, "FAO_NASO/NASO/Point/Indonesia.kml")

indo_aqua <- read_sf(indo_file)

mapview(indo_aqua)

idn_finfish_mol <- st_transform(indo_aqua, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
idn_pts <- st_centroid(idn_finfish_mol)

idn_pts_latlon <- st_transform(idn_pts, crs = "+init=epsg:4326")

mapview(idn_pts_latlon)

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN")

write_csv(farms_idn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_idn.csv"))

farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_idn)
```

## Portugal
 - https://www.ine.pt/xportal/xmain?xpid=INE&xpgid=ine_publicacoes&PUBLICACOESpub_boui=435690295&PUBLICACOESmodo=2&fbclid=IwAR0-_SHYtw2XGUAXdx71RGer284Vk_u40HYKXyJzeFbpdnsHydKgAfomTvU
 - National Institute of Statistics for Portugal 
 - There is a csv table, "q5_1.csv", which has the number of farms listed by type of system. I will assume that tanks are for finfish, since [this website](https://rea.apambiente.pt/content/aquaculture-production?language=en) says that the tanks are for **fish production**, and floating structures are for **bivalve molluscs**. Located here "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Portugal/EPesca_2019.xlsx"
 - According to the table, by these criteria, there are 112 marine tank farm systems in Portugal. 
 - I will equally allocate 112 points along the coast of Portugal.

Source: 
Estatísticas da Pesca, 2020. . Instituto Nacional de Estatística. [Accessed December 21, 2020]

```{r}
world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
plot(world)

portugal <- ne_countries(scale = 10, country = "Portugal", returnclass = "sf")

#info of our spatial vector object
portugal
mapview(portugal)
plot(portugal)

world <- st_as_sf(world)

portugal_world_crs <- st_transform(portugal, crs(world))

portugal_world_crop <- st_crop(world, portugal_world_crs) #%>%
 # dplyr::filter(scalerank == 5) ## filter for the appropriate island
plot(portugal_world_crop)
mapview(portugal_world_crop)

portugal_crop <- as(portugal_world_crop, "Spatial")

portugal_points_lines <- sample.line(portugal_crop, n = 380) ## equally place the number of farms along the coastline 
class(portugal_points_lines)
plot(portugal_points_lines)

portugal_points <- st_as_sf(portugal_points_lines)
mapview(portugal_points)

portugal_points_final <- portugal_points[253:364, ] ## grab the appropriate number of points
mapview(portugal_points_final)

## now prep dataframe for lat lon points
prt_pts <- st_centroid(portugal_points_final)

prt_pts_latlon <- st_transform(prt_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_prt <- data.frame(do.call(rbind, st_geometry(prt_pts_latlon)))
names(farms_prt) <- c("lon", "lat")

farms_prt_final <- farms_prt %>%
  mutate(iso3c = "PRT")

## visualize it 
farms_prt <-  st_as_sf(farms_prt, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_prt)

## write to farms folder 
write_csv(farms_prt_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_prt.csv"))
```

## Iran

The only species the FAO reports for Iran is "Marine fishes nei", and I can't find any information on number of marine farms there might be in Iran. Therefore I will place one farm on the Caspian Sea coast.

Source:
NA

```{r}

farms_irn <- data.frame(lat = c(37.392419247868425),
                        lon = c(50.1602963496454)) %>%
  mutate(iso3c = "IRN")

write_csv(farms_irn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_irn.csv"))

## visualize it 
farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_irn)
```

## China 
Can't find any datasets of marine finfish farm locations in China. Therefore I will place one farm on the coast of China.

Source: 
NA

```{r}

farms_chn <- data.frame(lat = c(26.649767732301385),
                        lon = c(119.94149300994019)) %>%
  mutate(iso3c = "CHN")

write_csv(farms_chn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_chn.csv"))

## visualize it 
farms_chn <-  st_as_sf(farms_chn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_chn)
```

## Saudi Arabia
 - There is really only one marine fish aquaculture producer in Saudi Arabia, and it happens to be the same company that produces almost all of its shrimp. It is one of the largest facilities in the world. http://www.naqua.com.sa/barramundi.php
 - I'll place a point there: 20.287253, 40.030864

Source:
National Aquaculture Group, n.d. [Accessed November 12, 2020]. http://www.naqua.com.sa/about-us.php

```{r}

farms_sau <- data.frame(lat = c(20.287253),
                        lon = c(40.030864)) %>%
  mutate(iso3c = "SAU")

write_csv(farms_sau, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_sau.csv"))

## visualize it 
farms_sau <-  st_as_sf(farms_sau, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sau)
```

## Mauritius

Can't find any datasets of marine finfish farm locations. Therefore I will place one farm on the coast. It probably doesn't matter, since Mauritius is so small anyways.

Source:
NA

```{r}

farms_mus <- data.frame(lat = c(-20.005039247819017),
                        lon = c(57.67022708374523)) %>%
  mutate(iso3c = "MUS")

write_csv(farms_mus, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_mus.csv"))

## visualize it 
farms_mus <-  st_as_sf(farms_mus, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mus)
```

## United Arab Emirates

http://www.fishfarm.ae/facilities.html
 - One here in Dibba Al Fujairah. 
 - They do sea bream and sea bass, which matches what the FAO reports.

The above is also corroborated by the FAO here: http://www.fao.org/fishery/countrysector/naso_uae/en

I will place a point off of the coast of Dibba Al Fujairah: 25.604715925918068, 56.340214330776234

Source: 
National Aquaculture Sector Overview. United Arab Emirates, 2016. , National Aquaculture Sector Overview Fact Sheets.

```{r}

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE")

write_csv(farms_are, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_are.csv"))

## visualize it 
farms_are <-  st_as_sf(farms_are, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_are)
```

## Tunisia

https://apps.fas.usda.gov/newgainapi/api/report/downloadreportbyfilename?filename=Aquaculture%20Industry%20Small%20but%20Growing_Tunis_Tunisia_5-31-2017.pdf
"At present, there are roughly 50 companies involved in aquaculture production:
 - Shellfish farming: 12 private companies
 - Bluefin tuna fattening: 5 private companies
 - Other marine fish farming: 20 private companies
 - Inland fish farming: 15 private companies"

 "The primary marine aquaculture production area is in the Monastir governorate, along Tunisia’s eastern
shore. Marine aquaculture is practiced using modern and innovative techniques, whether in concrete
facilities with a density of 60 kg/m3
or in floating cages on the high seas. Alevin are exclusively
imported for sea bass and sea bream production while bluefin tuna are imported for fattening."

 - I'll place 20 points along the coast of Monastir

Source: 
Aquaculture Industry Small but Growing: Tunisia, 2017. Fishery and Agriculture Society, Tunis.

```{r}
## load municipality shapefile, downloaded from here: https://gadm.org/download_country_v3.html
tunisia <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Tunisia/gadm36_TUN_shp/gadm36_TUN_1.shp")) %>%
  dplyr::filter(NAME_1 == "Monastir")

mapview(tunisia)

## OR if you don't municipality and only country info you could use this: 
# tunisia <- rnaturalearth::ne_countries(country = "Tunisia")

world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)
class(world)

#info of our spatial vector object
tunisia
mapview(tunisia)

world <- st_as_sf(world)

tunisia_world_crs <- st_transform(tunisia, crs(world))

tunisia_world_crop <- st_crop(world, tunisia_world_crs) 
plot(tunisia_world_crop)
mapview(tunisia_world_crop)

tunisia_crop <- as(tunisia_world_crop, "Spatial")
class(tunisia_crop)
mapview(tunisia_crop)

tunisia_points_lines <- sample.line(tunisia_crop, n = 20) ## equally place the number of farms along the coastline 
class(tunisia_points_lines)
plot(tunisia_points_lines)

tunisia_points <- st_as_sf(tunisia_points_lines)
mapview(tunisia_points)

## now prep dataframe for lat lon points
tun_pts <- st_centroid(tunisia_points)

tun_pts_latlon <- st_transform(tun_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_tun <- data.frame(do.call(rbind, st_geometry(tun_pts_latlon)))
names(farms_tun) <- c("lon", "lat")

farms_tun_final <- farms_tun %>%
  mutate(iso3c = "TUN")

## visualize it 
farms_tun <-  st_as_sf(farms_tun, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_tun)

## write to farms folder 
write_csv(farms_tun_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_tun.csv"))
```

## Taiwan
The two main species farmed in Taiwan are Milkfish and Grouper. I will place farms for these two species

Milkfish:
https://digitalarchive.worldfishcenter.org/bitstream/handle/20.500.12348/3610/Pub%20TR4%206.pdf?sequence=1&isAllowed=y
 - I will use the respondents from the survey, and place the appropriate number of points in each location (table located on page 6, I will only use "gatherers"). This is a really old paper, but it is the best I can find. 42 total points

 - Putai (Budai): 4 points: 
 23.396775208505524, 120.1486974182384
 23.391435122712778, 120.14508600806049
 23.379465182872867, 120.13344924193156
 23.37173018517046, 120.12923593005728

 - Peimen (Beimen): 4 points
 23.328815202320154, 120.11007291797651
 23.30989854415313, 120.10560972235575
 23.286248936869796, 120.09462339467383
 23.24808538030484, 120.08741361713255

 - Chiku (Cigu): 2 points
 23.098351835751856, 120.0340739167051
 23.08684757757559, 120.0323838672442

 - Yungan: 4 points
 22.84129712135721, 120.19480335124462
 22.83607641104833, 120.19703494905501
 22.823893974670515, 120.19737827179506
 22.808703955682557, 120.19960986960544

 - Lingpien (Linbian) : 6 points
 22.427007004796724, 120.48594464702815
 22.42449445979184, 120.48934227493775
 22.419155150689896, 120.4981761075027
 22.413920334638384, 120.50893526254974
 22.41119815232611, 120.51527750131434
 22.40868532131159, 120.51890163775126

 - Taitung City: 6 points
 22.729748162448605, 121.13759861706552
 22.73478926413642, 121.14388413948092
 22.73995620049436, 121.14975973652137
 22.74096436042943, 121.15167272160434
 22.746257078096264, 121.15631854252005
 22.74965943121689, 121.16246742314381

 - Chungkung (Chengkung): 6 points
 23.094448352409827, 121.3724851599623
 23.100673804589537, 121.38612214670725
 23.110708254441576, 121.39450636818748
 23.118419405368904, 121.4097595903985
 23.12715198105829, 121.40864842851558
 23.13662711164484, 121.40026420703533

 - Erhchieh (River delta below Yilan City): 6 points
 24.718398599156366, 121.83377270959099
 24.72276233035146, 121.83292494893261
 24.7123233460693, 121.83961283857079
 24.734911520797553, 121.82878034126954
 24.707959248912765, 121.8381057085115
 24.70256809420227, 121.83829409976889

 - Suao: 4 points
 24.59561929860139, 121.87509035189372
 24.591466187548917, 121.87405621071602
 24.466470314555245, 121.84309342644401
 24.43396678054247, 121.80292466585698

Source:
Lee, C.-S., 1983. Production and marketing of milkfish in Taiwan: an economic analysis.

```{r}
milkfish_points <- data.frame(lat = c(23.396775208505524, 23.391435122712778, 23.379465182872867, 23.37173018517046, 23.328815202320154, 23.30989854415313, 23.286248936869796, 23.24808538030484, 23.098351835751856, 23.08684757757559, 22.84129712135721, 22.83607641104833, 22.823893974670515, 22.808703955682557, 22.427007004796724, 22.42449445979184, 22.419155150689896, 22.413920334638384, 22.41119815232611, 22.40868532131159, 22.729748162448605, 22.73478926413642, 22.73995620049436, 22.74096436042943, 22.746257078096264, 22.74965943121689,  23.094448352409827, 23.100673804589537, 23.110708254441576, 23.118419405368904, 23.12715198105829, 23.13662711164484, 24.718398599156366, 24.72276233035146, 24.7123233460693, 24.734911520797553, 24.707959248912765, 24.70256809420227, 24.59561929860139, 24.591466187548917, 24.466470314555245, 24.43396678054247),

                              lon = c(120.1486974182384, 120.14508600806049, 120.13344924193156, 120.12923593005728, 120.11007291797651, 120.10560972235575, 120.09462339467383, 120.08741361713255, 120.0340739167051, 120.0323838672442, 120.19480335124462, 120.19703494905501, 120.19737827179506, 120.19960986960544, 120.48594464702815, 120.48934227493775, 120.4981761075027, 120.50893526254974, 120.51527750131434, 120.51890163775126, 121.13759861706552, 121.14388413948092, 121.14975973652137, 121.15167272160434, 121.15631854252005, 121.16246742314381, 121.3724851599623, 121.38612214670725, 121.39450636818748, 121.4097595903985, 121.40864842851558, 121.40026420703533, 121.83377270959099, 121.83292494893261, 121.83961283857079, 121.82878034126954, 121.8381057085115, 121.83829409976889, 121.87509035189372, 121.87405621071602, 121.84309342644401, 121.80292466585698))
```

Grouper:
https://www.researchgate.net/publication/49753615_Real-Time_Quantitative_PCR_Assay_for_Monitoring_of_Nervous_Necrosis_Virus_Infection_in_Grouper_Aquaculture
 - Although this is just a sample of grouper farm locations, I will use this and place the points accordingly. Table and map on the second page. 24 total farms.

 - Kunshen: 5 points
 22.963578173481825, 120.16265849315296
 22.958915389973615, 120.16450385288077
 22.958796842534618, 120.16420344548321
 22.95887587417216, 120.16630629726609
 22.962708853156307, 120.16480426027832

 - Budai: 2 points
23.366020730714546, 120.12803212666465
23.344101510137286, 120.11599409273818

 - Linyuan: 4 points
 22.5060215233288, 120.361518692894
 22.495712950055186, 120.37199003646582
 22.489210224135196, 120.38503630058813
 22.478900398348003, 120.40220243759113

 - Jiading: 5 points
 22.910490254668936, 120.17469982002679
 22.900053951559105, 120.17658809509712
 22.88771910346936, 120.18208125893808
 22.87475049020418, 120.18637279318882
 22.85735162493687, 120.18688777729894

 - Cigu: 3 points
23.11902593130365, 120.05874863883409
23.124310527454163, 120.07531112355083
23.130061175003874, 120.08122629666394

 - An-Nan: 2 points
 23.033784880994748, 120.07405573439489
 23.01988231566828, 120.09946161715932

 - Anping: 2 points
 22.990894265701648, 120.14268135694375
 22.969242998130003, 120.15847420298654

 - Linbian: 1 points
 22.412837508670247, 120.5141089682018

Source:
Kuo, H.-C., Wang, T.-Y., Chen, P.-P., Chen, Y.-M., Chuang, H.-C., Chen, T.-Y., 2011. Real-Time Quantitative PCR Assay for Monitoring of Nervous Necrosis Virus Infection in Grouper Aquaculture. Journal of Clinical Microbiology 49, 1090–1096. https://doi.org/10.1128/JCM.01016-10

```{r}
grouper_points <- data.frame(lat = c(23.366020730714546, 23.344101510137286, 23.11902593130365, 23.124310527454163, 23.130061175003874, 22.412837508670247, 22.5060215233288, 22.495712950055186, 22.489210224135196, 22.478900398348003, 22.963578173481825, 22.958915389973615, 22.958796842534618, 22.95887587417216, 22.962708853156307, 22.910490254668936, 22.900053951559105, 22.88771910346936, 22.87475049020418, 22.85735162493687, 23.033784880994748, 23.01988231566828, 22.990894265701648, 22.969242998130003),
                             lon = c(120.12803212666465, 120.11599409273818, 120.05874863883409, 120.07531112355083, 120.08122629666394, 120.5141089682018, 120.361518692894, 120.37199003646582, 120.38503630058813, 120.40220243759113, 120.16265849315296, 120.16450385288077, 120.16420344548321,  120.16630629726609, 120.16480426027832, 120.17469982002679, 120.17658809509712, 120.18208125893808, 120.18637279318882, 120.18688777729894, 120.07405573439489, 120.09946161715932, 120.14268135694375, 120.15847420298654))

```

Combine milkfish and grouper points

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN")

farms_twn <-  st_as_sf(all_points_twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)

## write to farms folder 
write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_twn.csv"))

```

## Costa Rica 
There is only one species farmed in Costa Rice, Spotted Rose Snapper.

https://www.researchgate.net/profile/Angel_Herrera-Ulloa/publication/235638071_Spotted_rose_snapper_Lutjanus_guttatus_aquaculture_research_and_development_as_socio-economic_alternative_for_Costa_Rican_fishing_communities/links/5acd4d66aca2723a333f53f8/Spotted-rose-snapper-Lutjanus-guttatus-aquaculture-research-and-development-as-socio-economic-alternative-for-Costa-Rican-fishing-communities.pdf
 - States that there are 3 pilot farms along the Gulf of Nicoya.

This says that Martec is the only company in the world which farms spotted rose snapper: https://www.seafoodsource.com/news/aquaculture/industrias-martec-plots-expansion-of-its-spotted-rose-snapper-offshore-aquaculture-operation

https://www.martec.co.cr/#aquaculture
 - Also states that they are the only company in the world to produce Spotted Rose Snapper commercially, and their farms are 3 miles off shore.... based on this I will place one point 3 miles offshore of where "Martec Industries" is located on google maps.

9.423478373794573, -84.20910189917947

Source:
Martec Industries Aquaculture , n.d. . Martec.  https://www.martec.co.cr/#aquaculture

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI")

write_csv(farms_cri, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_cri.csv"))

## visualize it 
farms_cri <-  st_as_sf(farms_cri, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_cri)
```

## Egypt

There is a map provided by the FAO (2010) here: http://www.fao.org/fishery/countrysector/naso_egypt/en
 - It has both production and locations.... I think I will need to hand place them, but we can use this. 
 - I will only use the ones that have Mullet, Seabass, Seabream, or Meagre, and that are along the coast, using ponds or cages.

 - Mersa Matruh: 31.360400495764903, 27.236078999801336: Production = 5
 - Alexandria: 31.15023941171644, 29.81109569981684: Production = 1521
 - Behira: 31.319036258284083, 30.225935332660324 : Production = 20376
 - Dakahlia: 31.491306679824632, 31.4278324391214 : Production = 5460
 - Damietta: 31.52619128473819, 31.849352783373792 : Production = 55551
 - Port Said: 31.275726202441984, 32.30190584291966 : Production = 16233 
 - Suez: 29.944394112057978, 32.54627145839493 : Production = 750
 - South Sinai: 27.80632012228518, 34.29387671355847 : Production = 30

Source:
FAO Fisheries & Aquaculture - National Aquaculture Sector Overview - Egypt, 2010. , National Aquaculture Sector Overview Fact Sheets.

```{r}
farms_egy <- data.frame(lat = c(31.360400495764903, 31.15023941171644, 31.319036258284083, 31.491306679824632, 31.52619128473819, 31.275726202441984, 29.944394112057978, 27.80632012228518),
                        lon = c(27.236078999801336, 29.81109569981684, 30.225935332660324, 31.4278324391214, 31.849352783373792, 32.30190584291966, 32.54627145839493,  34.29387671355847),
                        rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
  mutate(iso3c = "EGY")

write_csv(farms_egy, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_egy.csv"))

## visualize it 
farms_egy <-  st_as_sf(farms_egy, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_egy)
```

## India

There is not much information on locations of aquaculture facilities. However, this shows "Mandapam Hatchery" 80000 tonnes of marine finfish in 2015... The total for 2017 is 96000. I think it is reasonable to place a point on Mandapam, at the CMFRI farm, and leave it at that. 
http://www.cmfri.org.in/division/mariculture

9.28696221512509, 79.13007737814245

Source:
Indian Council of Agriculture Research - Central Marine Fisheries Research Institute, 2015.  http://www.cmfri.org.in/division/mariculture

```{r}
farms_ind <- data.frame(lat = c(9.28696221512509),
                        lon = c(79.13007737814245)) %>%
  mutate(iso3c = "IND")

write_csv(farms_ind, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ind.csv"))

## visualize it 
farms_ind <-  st_as_sf(farms_ind, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_ind)
```

## Singapore
Barramundi and milkfish

https://www.sfa.gov.sg/food-farming/food-farms/farming-in-singapore
 - This says 109 sea based fish farms.
 - Seems like a pretty reliable source.

I'll place 109 farms equally along the coast of Singapore.

Source: 
Food Farms in Singapore, 2019. . Singapore Food Agency. [Accessed December 17, 2020] https://www.sfa.gov.sg/food-farming/food-farms/farming-in-singapore

```{r}
world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
plot(world)

singapore <- ne_countries(scale = 50, country = "Singapore", returnclass = "sf")

#info of our spatial vector object
singapore
mapview(singapore)
plot(singapore)

world <- st_as_sf(world)

singapore_world_crs <- st_transform(singapore, crs(world))

singapore_world_crop <- st_crop(world, singapore_world_crs) %>%
  dplyr::filter(scalerank == 3) ## filter for the appropriate area
plot(singapore_world_crop)
mapview(singapore_world_crop)

singapore_crop <- as(singapore_world_crop, "Spatial")

singapore_points_lines <- sample.line(singapore_crop, n = 225) ## equally place the number of farms along the coastline 
class(singapore_points_lines)
plot(singapore_points_lines)

singapore_points <- st_as_sf(singapore_points_lines)
mapview(singapore_points)

singapore_points_final <- singapore_points[106:214, ] ## grab the appropriate number of points
mapview(singapore_points_final)

## now prep dataframe for lat lon points
sgp_pts <- st_centroid(singapore_points_final)

sgp_pts_latlon <- st_transform(sgp_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_sgp <- data.frame(do.call(rbind, st_geometry(sgp_pts_latlon)))
names(farms_sgp) <- c("lon", "lat")

farms_sgp_final <- farms_sgp %>%
  mutate(iso3c = "SGP")

## visualize it 
farms_sgp <-  st_as_sf(farms_sgp, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sgp)

## write to farms folder 
write_csv(farms_sgp_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_sgp.csv"))
```

## Malaysia

FAO Sector overview:
"The culture of marine fish in floating net-cages in
lagoons and sheltered coastal waters occupies an area of 102 ha, and is concentrated mainly in the western
coast of Peninsular Malaysia."

 - I can only find the broad suitable areas: https://www.dof.gov.my/ 
 - Broad suitable areas https://www.dof.gov.my/index.php/pages/view/78. I'll use these and use the area as a production estimate. Saved onto aurora /home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Malaysia/malaysia_finfish_farms.csv.

Source:
Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. . Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78

```{r}
malaysia_finfish_loc <- read_csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Malaysia/malaysia_finfish_farms.csv") %>%
  clean_names()

```

Farms: 
 - SEMPANG (PT Lot 389, 390), MELAKA : 2.131733588116292, 102.40118069215845
 - KG. AYAU, ROMPIN, PAHANG : 2.8071936098459522, 103.49758024234029
 - PERMATANG PAUH ISLAND, PAHANG : 5.384539285193906, 100.35040003558889
 - KG. SABAK FERI, ROMPIN, PAHANG : 2.8056383383493353, 103.49881667894354
 - SEMPANG (PT Lot 387), MELAKA : 2.1305137929032876, 102.40627304737939

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(2.131733588116292, 2.8071936098459522, 5.384539285193906, 2.8056383383493353, 2.1305137929032876),
                        lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
  mutate(iso3c = "MYS")

write_csv(farms_mys, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_mys.csv"))

## visualize it 
farms_mys <-  st_as_sf(farms_mys, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mys)
```

## Bangladesh

There isn't much information. I will place a point randomly on the coast of Bangladesh.

Source:
NA

```{r}
farms_bgd <- data.frame(lat=c(21.802433819366538),
                        lon=c(90.40418040967)) %>%
  mutate(iso3c = "BGD")

write_csv(farms_bgd, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_bgd.csv"))

## visualize it 
farms_bgd <-  st_as_sf(farms_bgd, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bgd)
```

## Cambodia

The only species is Barramundi.

https://www.researchgate.net/publication/340828970_Asian_seabass_Lates_calcarifer_farming_practices_in_Cambodia
 - Farms are definitely located in Prey Nob, Stoeng Hav, and Thomnob Rolork. 
 - This is the only information I can find on Cambodian Barramundi fishing, so I will place 3 points in these 3 places. It is really small production anyways.

Prey Nob: 10.53427341558665, 103.57357940185497
Stoeng Hav: 10.748668380457524, 103.6089106992865
Thomnob Rolork: 10.647924480438327, 103.5006922685572

Source:
Chankakada, M., Sros, K., Ramana, O., Phearum, H., Laining, A., Rimmer, M.A., Somony, T., Viseth, H., 2020. Asian Seabass Farming Practices in Cambodia 5.

```{r}
farms_khm <- data.frame(lat=c(10.53427341558665, 10.748668380457524, 10.647924480438327),
                        lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
  mutate(iso3c = "KHM")

write_csv(farms_khm, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_khm.csv"))

## visualize it 
farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_khm)
```

## Korea, Republic of (South Korea)

http://www.fao.org/fishery/countrysector/naso_korea/en
 - Lists 612 finfish farms. I will place 612 farms along the coast of South Korea.

Source:
National Aquaculture Sector Overview. Korea, 2005. , National Aquaculture Sector Overview Fact Sheets.

```{r}
world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
plot(world)

south_korea <- ne_countries(scale = 50, country = "South Korea", returnclass = "sf")

#info of our spatial vector object
south_korea
mapview(south_korea)
plot(south_korea)

world <- st_as_sf(world)

south_korea_world_crs <- st_transform(south_korea, crs(world))

south_korea_world_crop <- st_crop(world, south_korea_world_crs) #%>%
 # dplyr::filter(scalerank == 3) ## filter for the appropriate area

south_korea_world_crop <- south_korea_world_crop[2, ]
plot(south_korea_world_crop)
mapview(south_korea_world_crop)

south_korea_crop <- as(south_korea_world_crop, "Spatial")

south_korea_points_lines <- sample.line(south_korea_crop, n = 612) ## equally place the number of farms along the coastline 
class(south_korea_points_lines)
plot(south_korea_points_lines)

south_korea_points <- st_as_sf(south_korea_points_lines)
mapview(south_korea_points)

## now prep dataframe for lat lon points
kor_pts <- st_centroid(south_korea_points)

kor_pts_latlon <- st_transform(kor_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_kor <- data.frame(do.call(rbind, st_geometry(kor_pts_latlon)))
names(farms_kor) <- c("lon", "lat")

farms_kor_final <- farms_kor %>%
  mutate(iso3c = "KOR")

## visualize it 
farms_kor <-  st_as_sf(farms_kor, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_kor)

## write to farms folder 
write_csv(farms_kor_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_kor.csv"))
```

## Philippines
The only  species listed is Milkfish. 
There is no exact number listed, however I know that there are a lot of milkfish farms in the Philippines, as it is their oldest aquaculture method. There are definitely over 300. I will randomly place over 300 farms along the coast of the philippines.

Source:
NA

```{r}
world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
plot(world)

philippines <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")

#info of our spatial vector object
philippines
mapview(philippines)
plot(philippines)

world <- st_as_sf(world)

philippines_world_crs <- st_transform(philippines, crs(world))

philippines_world_crop <- st_crop(world, philippines_world_crs) #%>%
 # dplyr::filter(scalerank == 3) ## filter for the appropriate area

philippines_world_crop <- philippines_world_crop[-1, ]
plot(philippines_world_crop)
mapview(philippines_world_crop)

philippines_crop <- as(philippines_world_crop, "Spatial")

philippines_points_lines <- sample.line(philippines_crop, n = 43) ## equally place the number of farms along the coastline 
class(philippines_points_lines)
plot(philippines_points_lines)

philippines_points <- st_as_sf(philippines_points_lines)
mapview(philippines_points)

## now prep dataframe for lat lon points
phl_pts <- st_centroid(philippines_points)

phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
names(farms_phl) <- c("lon", "lat")

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL")

## visualize it 
farms_phl <-  st_as_sf(farms_phl, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_phl)

## write to farms folder 
write_csv(farms_phl_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_phl.csv"))
```

## Hong Kong

https://www.afcd.gov.hk/english/fisheries/fish_aqu/fish_aqu_mpo/fish_aqu_mpo.html
From HK government.

This shows a map fish culture zones, fish ponds, and oyster production areas. I will place a point in all of the "Fish culture zones" shown on the map. Most of the fish cages are visible on google maps when you search these locations.

Sha Tau Kok: 22.537974350807968, 114.22465750899093
Ap Chau: 22.549021238266082, 114.27266261841545
Kat O: 22.549243173819686, 114.29054140885648
0 Pui Tong: 22.545901930448537, 114.29912254835972
Sai Lau Kong: 22.524524976629923, 114.28385013462695
Wong Wan: 22.507936457313377, 114.30641749235996
Tap Mun: 22.47796934657302, 114.35412559932351
Kau Lau Wan: 22.459641511472412, 114.360272945696
Sham Wan: 22.4435502213444, 114.35400029960742
Lo Fu Wat: 22.46853714662761, 114.2720207303674
Yung Shue Au: 22.42337637093222, 114.27819733339493
Leung Shuen Wan: 22.349528341786087, 114.35178911904846
Tiu Cham Wan: 22.367924650829952, 114.31997002657292
Tai Tau Chau: 22.368469602475702, 114.3230438982345 
Kai Lung Wan: 22.3691151827537, 114.30143307907038
Kau Sai: 22.341819373881275, 114.31744391160476
Ma Nam Wat: 22.35464650188533, 114.26990023341041
Po Toi O: 22.274992746117093, 114.29389242171153
Po Toi: 22.164051938726015, 114.25252757025574
Sok Kwu Wan: 22.20591578796148, 114.12923505969019
Lo Tik Wan: 22.221779736133797, 114.12958553008323
Ma Wan: 22.352165476146805, 114.05569941361628
Yim Tin Tsai: 22.45358281100093, 114.2079128367368
Cheung Sha Wan: 22.235400816169882, 114.00599898096631
Yim Tin Tsai (East): 22.454708931476908, 114.22148845386273
Tung Lung Chau: 22.25579039550771, 114.28554310187128

Source:
Marine fish culture, pond fish culture and oyster culture, n.d. . Agriculture, Fisheries, and Conservation Department; The Government of the Hong Kong Special Administrative Region.  https://www.afcd.gov.hk/english/fisheries/fish_aqu/fish_aqu_mpo/fish_aqu_mpo.html

```{r}
farms_hkg <- data.frame(lat_lon = c("22.537974350807968, 114.22465750899093", "22.549021238266082, 114.27266261841545", "22.549243173819686, 114.29054140885648", "22.545901930448537, 114.29912254835972", "22.524524976629923, 114.28385013462695", "22.507936457313377, 114.30641749235996", "22.47796934657302, 114.35412559932351", "22.459641511472412, 114.360272945696", "22.4435502213444, 114.35400029960742", "22.46853714662761, 114.2720207303674", "22.42337637093222, 114.27819733339493", "22.349528341786087, 114.35178911904846", "22.367924650829952, 114.31997002657292", "22.368469602475702, 114.3230438982345", "22.3691151827537, 114.30143307907038", "22.341819373881275, 114.31744391160476", "22.35464650188533, 114.26990023341041", "22.274992746117093, 114.29389242171153", "22.164051938726015, 114.25252757025574", "22.20591578796148, 114.12923505969019", "22.221779736133797, 114.12958553008323", "22.352165476146805, 114.05569941361628", "22.45358281100093, 114.2079128367368", "22.235400816169882, 114.00599898096631", "22.454708931476908, 114.22148845386273", "22.25579039550771, 114.28554310187128")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
  mutate(iso3c = "HKG")

write_csv(farms_hkg, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_hkg.csv"))

## visualize it 
farms_hkg <-  st_as_sf(farms_hkg, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_hkg)
```

# Join cell count dataframes

```{r}
farm_files <- list.files(here::here("marine/marine_fish_general/finfish_farms/data/finfish_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)

```

### 2021-02-04 marine/marine_fish_general/finfish_farms/STEP3_rasterize_production.Rmd
cleaned up scripts and updated file paths

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

farms <- read.csv(here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"))

farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sf)
```

# determine subregions where points are located

```{r}

farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)

farms_sf <- farms_sf %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

# CYP:XAD
# ESP:PRT
# GRC:ALB
# GRC:TUR
# KOR:PRK
# HKG:CHN

mapview(filter(farms_sf, check=="CYP:XAD"))
mapview(filter(farms_sf, check=="ESP:PRT"))
mapview(filter(farms_sf, check =="GRC:ALB"))
mapview(filter(farms_sf, check == "GRC:TUR"))
mapview(filter(farms_sf, check == "KOR:PRK"))

# some annoying mismatches due to raster resolution. Fix these

unique(farms_sf$NAME_1)

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "KOR:PRK", "KOR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KOR:PRK", "South Korea", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

```

# FAO shrimp production data per country
```{r}

fao <- read.csv(here::here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

setdiff(fao$iso3c, farms_sf$iso3c)
setdiff(farms_sf$iso3c, fao$iso3c)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with regional production data and calculate production per farm
```{r}

## Egypt is the only one with regional production
farms_rgn_prod <- farms_sf_correct %>%
  dplyr::filter(!is.na(rgn_production))

## calculate farm production
farms_rgn_prod <- farms_rgn_prod %>%
  mutate(prop_production = rgn_production/sum(rgn_production)) %>%
  mutate(regional_prod = fao_tonnes_production*prop_production) %>%
  group_by(NAME_1) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = regional_prod/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry) %>%
  dplyr::filter(iso3c != "EGY") ## filter out EGY since we have regional production estimates

```

# combine and check it all matches ok

```{r}

farm_production <- rbind(farms_prod, farms_rgn_prod)

test <- farm_production %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

farms_sf_prod <- st_as_sf(farm_production)

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "marine/marine_fish_general/finfish_nutrient/prod_data_by_cell_iso3c.shp")
```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farm_production)
mapview(farms_sf)

sum(farms_sf$tonnes_per_farm) # 3901214

finfish_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(finfish_raster_check+1))
cellStats(finfish_raster_check, stat = "sum", na.rm = TRUE) # 3901214

finfish_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(finfish_raster+1))

finfish_raster_df <- as.data.frame(finfish_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(finfish_raster, stat = "sum") # 3901214
sum(finfish_raster_df$tonnes_production) # 3901214
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3901214
sum(fao$fao_tonnes_production) # 3901214

write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/marine_fish_general_farm.csv")

```

### 2021-02-04 marine/salmon/salmon_farm/STEP1_fao_salmon_production.Rmd
cleaned up scripts and updated file paths

---
title: "FAO salmon production"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

All data is ultimately adjusted to FAO production data.  This script cleans the fao mariculture data and subsets it to the relevant years of data and species (salmonids).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))

```

Subset the data to include only the species and countries we are interested in.  Then summarize by total tonnes of salmonids per country/year. (There are multiple salmon species)

```{r}

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
salmon_list <- species_list$species[species_list$aq_group=="salmonids"]
salmon_list

# include only salmon
fao_salmon <- fao %>%
  filter(species %in% salmon_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year)

write.csv(fao_salmon, here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv"), row.names=FALSE)

 explore <- read_csv(here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   dplyr::mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100,2))

sum(explore$fao_tonnes_production) # 2753752
sum(explore$percent) # 100.01
```

### 2021-02-04 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
cleaned up scripts and updated file paths

---
title: "Location of Salmon Farms"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script standarizes location of salmon farms to be lat/long point data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"
fao_salmon <- read_csv("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv") %>%
     dplyr::filter(year == 2017)

sort(unique(fao_salmon$country))

#  [1] "Australia"                "Canada"                   "Chile"                    "Denmark"                 
#  [5] "Faroe Islands"            "Finland"                  "Iceland"                  "Ireland"                 
#  [9] "Japan"                    "New Zealand"              "Norway"                   "Russian Federation"      
# [13] "Sweden"                   "Turkey"                   "United Kingdom"           "United States of America"
```

# Raster

Standard raster used for this analysis

```{r}

source(here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

# Chile

Data for Chile comes from https://mapas.subpesca.cl/ideviewer/?locale=en-gb.

There is also a list of concessions here: http://www.subpesca.cl/portal/619/w3-article-92935.html

I was in contact with Valeria Tamayo at UCSB who helped me with some spanish translations concerning this data.

Source:
Undersecretariat for Fisheries and Aquaculture, 2020. [Accessed Feb 2020] https://mapas.subpesca.cl/ideviewer/?locale=en-gb

```{r}

# Column meaning and names
#0 LINK_DOC - URL of the SUBPESCA resolution approving the aquaculture or resolution technical project that cartographically regulates the aquaculture concession
#1 CARTA - Name of the geographic reference letter
#2 DATUM - Reference datum name
#3 HUSO - Spindle Name
#4 COMUNA - Name of the commune
#5 N_PERT - Pert number, code of the application for admission to process
#6 N_CODIGOCE - Farming center code according to the national aquaculture registry
#7 N_RESOLSSP - Resolution number of the undersecretary of fisheries and aquaculture that apprehends the aquaculture technical project
#8 F_RESOLSSP - Date of issuance of the resolution of the undersecretary of fisheries and aquaculture approving the aquaculture technical project
#9 N_RESOLSSF - Resolution number of the undersecretary for the armed forces granted by the aquaculture concession
#10 F_RESOLSSF - Date of issuance of the resolution of the undersecretary for the armed forces granted by the aquaculture concession
#11 TOPONIMIO - Geographical location of the aquaculture concession
#12 ESPECIES - Name of crop species
#13 AGRUPCONCE - Identifier of the salmonid concession group or sanitary neighborhood
#14 SUPERFICIE - Surface in hectares
#15 TITULAR - Name of the holder of the aquaculture concession
#16 COORDENADS - List of geographical coordinates of the aquaculture concession corresponding to each of the vertices of the polygon
#17 REGION - Region name
#18 GRUPO_ESP - Group of crop species
#19 TIPO_PORCI - Type of space where the aquaculture concession is located
#20 ESTADO - Processing status of the aquaculture concession
#21 ESTADO_SOL - Status of the aquaculture application process

chile_dat <- st_read(file.path(path, "Chile"), layer = "Concesiones_de_Acuicultura")

```

We filter to only those that produce salmon, but note that this is ALL leases, not neccesarily only active sites. 
```{r}

#Filter to only salmon farming
chile <- chile_dat %>% 
  filter(grepl("SALMON", REP_SUB_13))

# convert polygons to points
chile_pts <- st_centroid(chile)
chile_pts <- st_transform(chile_pts, food_crs)

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL")

write_csv(farms_chile, here("marine/salmon/salmon_farm/data/farm_sites/farms_chile.csv"))

```

# Norway

We use the number of salmon licenses to get a proxy for the relative distribution of production along the Norwegian coast.

## Load csv with lat long
License data.

Source: 
Fiskeridirektoratet, 2019. 2019 aquaculture license data. [accessed May 2019] https://fiskeridir.no/Akvakultur/Registre-og-skjema/Akvakulturregisteret

```{r}

enc <- readr::guess_encoding(file.path(path, "Norway/Akvakulturregisteret.csv"), n_max = 1000)[,"encoding"] %>% as.character()

norway_csv <- read.csv(file = file.path(path, "/Norway/Akvakulturregisteret.csv"), skip = 1, header = TRUE, sep = ";", fileEncoding = enc)

#Variable translations
#Akvakulturregisteret – variables:
#TILL_NR - License number
#ORG.NR/PERS.NR - Company official number
#NAVN - company name
#ADRESSE - address
#POSTNR - post number
#POSTSTED - regional center
#TILDELINGSTIDSPUNKT - date that the license got accepted
#TIDSBEGRENSET - time bound of license
#TILL_KOMNR - license municipality number
#TILL_KOM - License municipality
#FORMÅL - purpose of use - Purpose (you probaly want "kommersiell" =commercial)
#PRODUKSJONSFORM - Production form (Matfisk = grow out)
#ART - Species (Laks=salmon, ørret=trout, regnbueørret = rainbow trout)
#TILL_KAP - Maximum allowed biomass for the license - some kind of capacity
#TILL_ENHET - units of measure (TN = ton, KG = kilogram)
#LOK_NR - Location number (identifies actual group of pens)
#LOK_NAVN - Location name
#LOK_KOMNR - Location municipality number
#LOK_KOM - Location municipality
#LOK_PLASS - Location place (land or sea) - sea 
#VANNMILJØ - Water environment (freshwater, saltwater or both) - saltvann and freskvann/saltvann
#LOK_KAP - Location max allowed biomass
#LOK_ENHET - 
#N_GEOWGS84 - GPS North
#Ø_GEOWGS84 - GPS East

```

We filter the data to only include commercial marine salmon production. We also only include farms that are growing salmon for food.

The dataset also has rows with the same lat/lon coordinates, so we only use unique lat/lon after filtering to get single points for each location.

http://www.fao.org/fishery/countrysector/naso_norway/en
"By the end of 2003, 832 licences for ongrowing in sea water".  And 1,018 here (includes salmon and rainbow trout): https://www.ssb.no/en/statbank/table/08967/tableViewLayout1/. 
I get a similar value of 893 by including all years to 2013 and removing duplicate regions.  So, I am assuming that most of these licenses in these data are active.  Regardless, this should provide a reasonable estimate of production distribution.

For 2018 (https://www.ssb.no/en/statbank/table/08967/tableViewLayout1/) including salmon and rainbow trout: 1,160
These data have 920 licenses for salmon only. These values seem reasonably aligned to me.  I am using this information to make sure these data do not include inactive licenses, how to best account for multiple license listings at the same location (conclusion: count only once), and whether we need to subset by year enacted (no).

```{r}

#FORMAL = Kommersiell, Slaktemerd, 
unique(norway_csv$FORMÅL)

#Kommersiell = Commerical
#Forskning = Research
#Slaktemerd  = Slaughter  cage             
#Fangstbasert akvakultur = Catch-based aquaculture, i.e., wild caught fish are stored in pens to hold them until prices increase during non-fishing season, https://www.sciencedirect.com/science/article/pii/S0308597X18302252
#Undervisning    =  Teaching
#Manntall =   Census            
#Visning =  Display
# Fiskepark = Fishpark
# Utvikling = Development

unique(norway_csv$PRODUKSJONSFORM)

#MATFISK = food fish                             
#SETTEFISK  = hatcheries                        
#STAMFISK = broodstock                         
#STAMDYR = broodstock                            
#AKVAKULTURDYR I TIDLIGE LIVSSTADIER =AQUACULTURE ANIMALS IN EARLY LIFE STAGES
#AKVAKULTURDYR TIL KONSUM = AQUACULTURE ANIMALS FOR CONSUME          
#MATFISK-GRØNN KONVERTERT = FOOD FISH GREEN CONVERTED         
#MATFISK-GRØNN A  = Food fish green A              
#MATFISK - (5% MTB ØKNING)  = FOOD - (5% MTB INCREASE)         
#ALGER TIL  fôr/konsum    = ALGER FOR FOOD / CONSUMPTION
#SKALLDYR   = SHELLFISH
#ANDRE FORMÅL   = Other objective                     
#MATFISK-GRØNN C = Food fish green C                    
#ALGER TIDLIG FASE  = ALGER EARLY PHASE
#HAVBEITE = ranching                           
#MATFISK-GRØNN B   = food fish green B                 
#ØKOLOGISK MATFISK   =  organic food fish                
#MATFISK-GRØNN A (5% MTB ØKNING) = FOOD FISH GREEN A (5% MTB INCREASE

unique(norway_csv$ART)
species <- "Laks"

unique(norway_csv$VANNMILJØ)
# FERSKVANN = freshwater
# BRAKKVANN = brackishwater
# SALTVANN = saltwater

# Only include Commercial production
purpose <- c("Kommersiell")

#Only include salmon for food
objective <- c("MATFISK", "AKVAKULTURDYR TIL KONSUM", "MATFISK-GRØNN KONVERTERT", "MATFISK - (5% MTB ØKNING)", "MATFISK-GRØNN C", "HAVBEITE", "MATFISK-GRØNN B", "ØKOLOGISK MATFISK", "MATFISK-GRØNN A (5% MTB ØKNING)")

# Subset
sub_norway <- norway_csv %>% 
  filter(ART == species,
         FORMÅL %in% purpose,
         PRODUKSJONSFORM %in% objective,
         VANNMILJØ %in% c("SALTVANN")) #only 1 FERSKVANN/SALTVANN, not going to have a large effect on results if we cut/include

#There are multiple liscenses for the same place.  This may be for multiple pens or across time.  
# We will count them as one location given that the data then match well with other sources
sub_norway %>%  
arrange(N_GEOWGS84, Ø_GEOWGS84)

farms_nor <- sub_norway %>% 
  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") # Counting duplicate liscense locations once

write_csv(farms_nor, here("marine/salmon/salmon_farm/data/farm_sites/farms_nor.csv"))

```

# Scotland

Based on these data for the UK region, it appears that salmon aquaculture is occurring only in Scotland.

```{r}

## another dataset for entire UK region
## want to make sure salmon aquaculture is occurring only in Scottland in UK
test <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/UK/EMOD/EMODnet_HA_Aquaculture_Marine_Finfish_20190104.shp") %>%
  filter(COUNTRY == "United Kingdom",
         SALMON == "Yes", 
         STATUS == "Active")
## based on plot, this is all in Scottland.

mapview(test)
```

Source: 
http://aquaculture.scotland.gov.uk/
```{r}
## get scotland data: http://aquaculture.scotland.gov.uk/
# Load in data and select sites that have been producing in the last 3 years

#### TODO #### This could probably be improved by setting up a way to webscrape these data... not sure how this was compiled previously.

scotland_csv <- as.data.frame(read_csv(file.path(path, "Scotland/Scotland_site_details.csv")))

# Subset to salmon farms
sub_scotland <- scotland_csv %>% 
  dplyr::select(ID = `Marine Scotland Site ID`, Easting, Northing, `Producing in Last 3 Years`, `Aquaculture Type`, `Water Type`, Species, subregion = `Local Authority` ) %>% 
  filter(`Producing in Last 3 Years` == c("Yes", "New"),
         `Water Type` %in% c("Seawater", "Freshwater and Seawater"), 
         grepl("Salmon", Species))

new_names <- data.frame(subregion = c("Argyll and Bute", "North Ayrshire", "Western Isles", "Shetland", "Orkney", "Highland"),
                         subregion_new = c("Argyll & Clyde", "Argyll & Clyde", "Outer Hebrides", "Shetland Isles", "Orkney Islands", 
                                       "North Coast & West Highlands"))

sub_scotland <- sub_scotland %>%
  left_join(new_names, by="subregion") %>%
  dplyr::select(Easting, Northing, subregion = subregion_new)

coordinates(sub_scotland) <- cbind(sub_scotland$Easting, sub_scotland$Northing)
crs(sub_scotland) <- "+init=epsg:7405"
scotland <- spTransform(sub_scotland, CRS('+init=epsg:4326'))

scotland <- st_as_sf(scotland) %>% st_zm()

farms_scotland <- data.frame(do.call(rbind, st_geometry(scotland))) 
names(farms_scotland) <- c("lon", "lat")

farms_scotland$subregion <- sub_scotland$subregion
farms_scotland <- farms_scotland %>%
  mutate(iso3c="GBR")

write_csv(farms_scotland, here("marine/salmon/salmon_farm/data/farm_sites/farms_scotland.csv"))

```

# Faroe Islands

We consider Faroe Islands as a single region. We have data from ASC to use for our farms.

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}
ASC_salmon_sf <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp"))

fro_salmon_sf <- ASC_salmon_sf %>%
  dplyr::filter(crt_cnt == "Faroe Islands")

mapview(fro_salmon_sf)

fro_pts <- st_centroid(fro_salmon_sf)

fro_pts_latlon <- st_transform(fro_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry) %>%
  mutate(iso3c = "FRO")

farms_fro <- data.frame(do.call(rbind, st_geometry(fro_pts_latlon))) 
names(farms_fro) <- c("lon", "lat")
farms_all_fro <- farms_fro %>%
  cbind(iso3c = fro_pts_latlon$iso3c)

write_csv(farms_all_fro, here("marine/salmon/salmon_farm/data/farm_sites/farms_fro.csv"))

```

# Australia

Data is from the national map (https://nationalmap.gov.au/#share=s-9CWx9q1BlcDp56T59yiCGgZDU3Q). Instructions on how to access raw data are here: https://nationalmap.gov.au/help/help.html.

Julia Blanchard's RA helped extract the data by manually going through the map and selecting individual farm leases to record their locations, then reading the DPIPWE documentation to identify the species farmed at each location.

According to this source: https://data.gov.au/dataset/ds-dga-c12a0597-b535-48b3-a602-1f8382d8dae6/details
In 2015-2016, >98% of salmonid aquaculture was in Tasmania.  So limiting to Tasmania is probably fine.

TODO: 
There is probably a way to automate this by web scraping, like we did for Australia tuna aquaculture.

Source: 
Tasmanian Government Department of Primary Industries, Parks, Water and Environment, 2019. Sea fishing & aquaculture. [Accessed Jun 2019] https://dpipwe.tas.gov.au/sea-fishing-aquaculture/marine-farming-aquaculture

Australian Government National Map, 2019. Marine framing zones. [accessed June 2019]
https://nationalmap.gov.au/#share=s-9CWx9q1BlcDp56T59yiCGgZDU3Q

```{r}

#Tasmania
tas_csv <- read.csv(file = file.path(path, "/Australia/NationalMap_AquacultureFarms.csv"), header = T)

farms_tas <- tas_csv %>% 
  filter(species_farmed1 == "salmon" | species_farmed2 == "salmon" | species_farmed3 == "salmon") %>%
  dplyr::select(lon, lat) %>%
  mutate(iso3c="AUS")

write_csv(farms_tas, here("marine/salmon/salmon_farm/data/farm_sites/farms_tas.csv"))

```

# Canada
TODO: This could probably updated with more current data.

An annual average of 122,300 tonnes of salmon was produced in the last five years (2011-2015). Salmon has represented an average of 70% of total Canadian aquaculture volume. British Columbia’s salmon production represents over 60% of this total. (https://www.dfo-mpo.gc.ca/aquaculture/sector-secteur/species-especes/salmon-saumon-eng.htm).

These data suggest production occurs in: Nova Scotia, New Brunswick, and BC.

British Colombia data with species information: https://catalogue.data.gov.bc.ca/dataset/saltwater-finfish-tenures-coastal-resource-information-management-system

PEI data is available, but no salmon: http://www.arcgis.com/home/webmap/viewer.html?webmap=16aa8830c7084a8a92ce066b525978b4

Newfoundland and Labrador data was extracted from figures found on the web: https://www.fishaq.gov.nl.ca/aquaculture/index.html
(sites are for 2015)

## British colombia

Source: 
Saltwater Finfish Tenures - Coastal Resource Information Management System (CRIMS) , 2019. Ministry of Forests, Lands, Natural Resource Operations and Rural Development. [Accessed January 17, 2020] https://catalogue.data.gov.bc.ca/dataset/saltwater-finfish-tenures-coastal-resource-information-management-system

```{r}

bc <- st_read(file.path(path, "Canada/CRIMS_S_WATER_FINFISH_TENURES/WAT_FNF_TN_polygon.shp"))

bc_pts <- st_centroid(bc)

bc_pts_latlon <- st_transform(bc_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry)

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon))) 
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN")

write_csv(farms_bc, here("marine/salmon/salmon_farm/data/farm_sites/farms_bc_can.csv"))

```

## New Brunswick
Source: 
NB Agriculture, Aquaculture and Fisheries, 2019. Finfish. [Accessed Oct 2019]
https://hub.arcgis.com/datasets/DAAF-MAAP::masmps-data

```{r}

nb <- st_read(file.path(path,"/Canada/New_brunswick_Finfish_mol.shp"))
mapview(nb)
nb_pts <- st_centroid(nb)

nb_pts_latlon<-st_transform(nb_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry)

farms_nb <- data.frame(do.call(rbind, st_geometry(nb_pts_latlon))) 
names(farms_nb) <- c("lon", "lat")
farms_nb <- farms_nb %>%
  mutate(iso3c="CAN")

write_csv(farms_nb, here("marine/salmon/salmon_farm/data/farm_sites/farms_nb_can.csv"))

```

## Nova Scotia
Originally tried using points along the entire coastline.  But this was far too many points.  Here is a good site:
https://www.nsgc.gov.ns.ca/fishaqua/provinceSalmon.htm (other aquaculture species also available).

Obtained data from here: https://data.novascotia.ca/Fishing-and-Aquaculture/Aquaculture-License-and-Lease-GIS-Database/h57h-p9mm
(Feb 18 2020)

Source: 
Nova Scotia Marine Aquaculture Leases , 2020. . Nova Scotia Fisheries and Aquaculture. [Accessed February 18, 2020] https://data.novascotia.ca/Fishing-and-Aquaculture/Nova-Scotia-Marine-Aquaculture-Leases/h57h-p9mm

```{r}

ns <- st_read(file.path(path,"Canada/Nova_Scotia_Marine_Aquaculture_Sites/geo_export_fcc6f2ef-82bb-4445-98f0-a82a56cd0d00.shp"))
mapview(ns)
# id salmon
salmon <- grep("Salmon|salmon", unique(ns$aqua_speci), value=TRUE)

ns_salmon <- ns %>%
  filter(aqua_speci %in% salmon)

ns_salmon_mol <- st_transform(ns_salmon, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
ns_pts <- st_centroid(ns_salmon_mol)

ns_pts_latlon <- st_transform(ns_pts, crs = "+init=epsg:4326")

mapview(ns_pts_latlon)

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN")

write_csv(farms_ns, here("marine/salmon/salmon_farm/data/farm_sites/farms_ns_can.csv"))

```

## Newfoundland and Labrador

Source: 
Newfoundland Labrador Fisheries, Forestry and Agriculture, 2015. [Accessed February 18, 2020] https://www.gov.nl.ca/flr/lands/ownership/commercial/aquaculture/

```{r}

new_lab <- read.csv(file.path(path,"Canada/NewFoundland_Labrador/NewFoundland_Labrador_salmon.csv"))

farms_new_lab <- new_lab %>%
  mutate(iso3c = "CAN") %>%
  dplyr::select(lon, lat, iso3c)

write_csv(farms_new_lab, here("marine/salmon/salmon_farm/data/farm_sites/farms_new_lab_can.csv"))

```

# United States
Salmon aquaculture occurs along the Atlantic coast and in Puget sound.

Puget Sound data (2018 data): http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/

Source:

## Puget Sound

Source: 
Our Sound, Our Salmon, 2017. [Accessed January 31, 2020] http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/

```{r}

farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
  mutate(iso3c = "USA") %>%
  dplyr::select(lon, lat, iso3c)

write_csv(farms_ps, here("marine/salmon/salmon_farm/data/farm_sites/farms_ps_usa.csv"))

```

## US Northeast
Source:
Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 17, 2020] https://www.northeastoceandata.org/data-download/

```{r}

us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))

# id salmon and active sites
salmon_species <- grep("Salmon|salmon", unique(us_ne$allSpecies), value=TRUE)

us_ne_salmon <- us_ne %>%
  filter(allSpecies %in% salmon_species) %>%
  filter(status == "Active")

us_ne_salmon_mol <- st_transform(us_ne_salmon, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
us_ne_salmon_pts <- st_centroid(us_ne_salmon_mol)
# check
plot(st_geometry(us_ne_salmon_mol))
plot(st_geometry(st_centroid(us_ne_salmon_mol)), add=TRUE)

us_ne_salmon_pts_latlon <- st_transform(us_ne_salmon_pts, crs = "+init=epsg:4326")

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon))) 
names(farms_us_ne) <- c("lon", "lat")
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA")

write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/farm_sites/farms_ne_usa.csv"))

```

# New Zealand

We use the data from ASC for our New Zealand farms.

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}
ASC_salmon_sf <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp"))

nzl_salmon_sf <- ASC_salmon_sf %>%
  dplyr::filter(crt_cnt == "New Zealand") %>%
  dplyr::filter(spcs__c == "Salmon")

mapview(nzl_salmon_sf)

nzl_pts <- st_centroid(nzl_salmon_sf)

nzl_pts_latlon <- st_transform(nzl_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry) %>%
  mutate(iso3c = "NZL")

farms_nzl <- data.frame(do.call(rbind, st_geometry(nzl_pts_latlon))) 
names(farms_nzl) <- c("lon", "lat")
farms_all_nzl <- farms_nzl %>%
  cbind(iso3c = nzl_pts_latlon$iso3c)

write_csv(farms_all_nzl, here("marine/salmon/salmon_farm/data/farm_sites/farms_nz.csv"))

```

# Ireland
Downloaded from here (Jan 31 2020): https://www.agriculture.gov.ie/seafood/engineering/publications/gisdata/

Source:
Ireland Department of Agriculture, Food and the Marine., 2019. Aquaculture licence GIS data. [accessed January 31, 2020]  https://www.agriculture.gov.ie/seafood/engineering/publications/gisdata/

```{r}

ireland <- st_read(file.path(path,"Ireland/AquacultureLicenceGISData23122019/Aqua_Sites_Redacted_23-12-2019.shp"))

ire_salmon <- ireland %>%
  dplyr::filter(Species_Na %in% "Salmon")

ire_pts <- st_centroid(ire_salmon)

ire_pts_latlon <- st_transform(ire_pts, crs = "+init=epsg:4326")

farms_ire <- data.frame(do.call(rbind, st_geometry(ire_pts_latlon))) 
names(farms_ire) <- c("lon", "lat")
farms_ire <- farms_ire %>%
  mutate(iso3c="IRL")

write_csv(farms_ire, here("marine/salmon/salmon_farm/data/farm_sites/farms_ire.csv"))

```

# Russia

https://salmonbusiness.com/russian-aquaculture-harvested-over-over-17000-tonnes-of-fish-last-year/

https://www.intrafish.com/finance/russian-aquaculture-sets-huge-salmon-production-target-as-earnings-spike/2-1-662980

Russian Aquaculture is the only in Russia company farming Atlantic salmon. The company has 49 sites for salmon and trout farming in the Barents and the White Seas and in Karelia (Trout), with annual potential production capacity of around 50,000 metric tons of salmonids.

Appears that most of Russia's salmon aquaculture occurs in the Barents Sea in the Murmansk region.  Trout are in the White Seas and lakes of the Republic of Karelia (not sure if this is freshwater).  There are multiple salmon sites within the region, but we do not have specific locations.

```{r}

# lat long estimates from google earth
farms_russia <- data.frame(lon=c(33.7149),
                    lat=c(69.4953)) %>%
  mutate(iso3c = "RUS")

write_csv(farms_russia, here("marine/salmon/salmon_farm/data/farm_sites/farms_russia.csv"))

```

# Japan
We are using the ASC map data for Japan farms.

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}
ASC_salmon_sf <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp"))

JPN_salmon_sf <- ASC_salmon_sf %>%
  dplyr::filter(crt_cnt == "Japan") %>%
  dplyr::filter(aq_grop == "salmonids")

mapview(JPN_salmon_sf)

JPN_pts <- st_centroid(JPN_salmon_sf)

JPN_pts_latlon <- st_transform(JPN_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry) %>%
  mutate(iso3c = "JPN")

farms_JPN <- data.frame(do.call(rbind, st_geometry(JPN_pts_latlon))) 
names(farms_JPN) <- c("lon", "lat")
farms_all_JPN <- farms_JPN %>%
  cbind(iso3c = JPN_pts_latlon$iso3c)

write_csv(farms_all_JPN, here("marine/salmon/salmon_farm/data/farm_sites/farms_japan.csv"))

```

# Denmark
I've found some good information on farms in Denmark. There is a HELCOM dataset with finfish locations, and there are 20 farms. Other sources indicate there are 19 salmon specific farms in Denmark, which seems close enough to me.

Columns of interest: 
 - geometry to get lat/lon
 - PR_AV_TON : Average tonnes of production per year

Source: 
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

```{r}

enc <- readr::guess_encoding(file.path(path, "HELCOM_Baltic/Finfish_mariculture.shp"), n_max = 1000)[,"encoding"] %>% as.character()

# lat long estimates from google earth
farms_denmark <- st_read(file.path(path, "HELCOM_Baltic/Finfish_mariculture.shp"), options = "ENCODING=WINDOWS-1252") %>%
  filter(COUNTRY == "DK")

mapview(farms_denmark$geometry)

dk_pts <- st_centroid(farms_denmark)

dk_pts_latlon <- st_transform(dk_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry, NAME)

dk_subregions <- dk_pts_latlon %>%
  dplyr::select(NAME)

farms_dk <- data.frame(do.call(rbind, st_geometry(dk_pts_latlon))) 
names(farms_dk) <- c("lon", "lat")
farms_dk <- farms_dk %>%
  mutate(iso3c="DNK")

farms_dk <- cbind(farms_dk, dk_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

write.csv(farms_dk, here("marine/salmon/salmon_farm/data/farm_sites/farms_denmark.csv"), row.names = FALSE)

#farms_dk <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/farm_sites/farms_denmark.csv"))
```

# Turkey
There is salmon and trout aquaculture in Turkey.

Page 33 of this indicates there are 12 marine rainbow trout farms in turkey: http://tudav.org/wp-content/uploads/2018/04/marine_aquaculture_in_turkey.pdf

It says that half of those farms (6 farms) are located in Persembe bay. I will allocate the remaining 6 equally across Sinop bay, Sana bay, and Rize bay (2 farms each).

Source: 
Candan, A., Karatas, S., Kücüktas, H., Okumus, I. (Eds.), 2007. Marine aquaculture in Turkey. Türk Denzi Araştırmaları Vakfı, İstanbul.

```{r}

# Sinop: 2 farms, randomly picked locations
# lat 42.011686, lon 35.193134
# 42.015462, 35.168353

# Persembe: 6 farms
# 41.073031, 37.776490
# 41.071171, 37.776501
# 41.103902, 37.788303
# 41.106756, 37.788893
# 41.111485, 37.788643
# 41.114387, 37.788943

# Sana: 2 farms
# 40.991640, 39.812112
# 40.994117, 39.803345

# Rize: 2 farms
# 41.038866, 40.562498,
# 41.036462, 40.558582

farms_turkey <- data.frame(lon=c(35.193, 35.168, 37.776,  37.776, 37.788, 37.789, 37.789, 37.789, 39.812, 39.803, 40.562, 40.558),
                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
  mutate(iso3c = "TUR")

write_csv(farms_turkey, here("marine/salmon/salmon_farm/data/farm_sites/farms_tur.csv"))

```

# Finland

Source: 
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

```{r}

enc <- readr::guess_encoding(file.path(path, "HELCOM_Baltic/Finfish_mariculture.shp"), n_max = 1000)[,"encoding"] %>% as.character()

# lat long estimates from google earth
farms_fin <- st_read(file.path(path, "HELCOM_Baltic/Finfish_mariculture.shp"), options = "ENCODING=WINDOWS-1252") %>%
  filter(COUNTRY == "FI")

mapview(farms_fin$geometry)

fi_pts <- st_centroid(farms_fin)

fi_pts_latlon <- st_transform(fi_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry, NAME)

fi_subregions <- fi_pts_latlon %>%
  dplyr::select(NAME)

farms_fi <- data.frame(do.call(rbind, st_geometry(fi_pts_latlon))) 
names(farms_fi) <- c("lon", "lat")
farms_fi <- farms_fi %>%
  mutate(iso3c="FIN")

farms_fi <- cbind(farms_fi, fi_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

write.csv(farms_fi, here("marine/salmon/salmon_farm/data/farm_sites/farms_finland.csv"), row.names = FALSE)

farms_fi <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_finland.csv"))
```

# Sweden 
Source:
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

```{r}

enc <- readr::guess_encoding(file.path(path, "HELCOM_Baltic/Finfish_mariculture.shp"), n_max = 1000)[,"encoding"] %>% as.character()

# lat long estimates from google earth
farms_swe <- st_read(file.path(path, "HELCOM_Baltic/Finfish_mariculture.shp"), options = "ENCODING=WINDOWS-1252") %>%
  filter(COUNTRY == "SE") %>%
  dplyr::filter(PRODUCTION %in% c("Rainbow trout (Oncorhynchus mykiss)", "Salmon, Rainbow trout (Oncorhynchus mykiss), Char (salvelinus)", "Salmon, Trout (Salmo trutta)", "Salmon", "Salmon, Trout (Salmo trutta), Rainbow trout (Oncorhynchus mykiss), Char (salvelinus)", "Perch (perca fluviatilis), Pikeperch (Sander lucioperca), Rainbow trout (Oncorhynchus mykiss)", "Trout (Salmo trutta)", "Salmon, Trout (Salmo trutta) - breeding", "Perch (perca fluviatilis), Grayling (thymallus thymallus), Rainbow trout (Oncorhynchus mykiss), Char (salvelinus), tropical fish species"))

mapview(farms_swe$geometry)

unique(farms_swe$PRODUCTION)

sw_pts <- st_centroid(farms_swe)

sw_pts_latlon <- st_transform(sw_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry, NAME)

sw_subregions <- sw_pts_latlon %>%
  dplyr::select(NAME)

farms_sw <- data.frame(do.call(rbind, st_geometry(sw_pts_latlon))) 
names(farms_sw) <- c("lon", "lat")
farms_sw <- farms_sw %>%
  mutate(iso3c="SWE")

farms_sw <- cbind(farms_sw, sw_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  filter(!is.na(lat))

write.csv(farms_sw, here("marine/salmon/salmon_farm/data/farm_sites/farms_sweden.csv"), row.names = FALSE)

#farms_sw <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_sweden.csv"))
```

## Iceland

We are using the ASC data for this:

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}
ASC_salmon_sf <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp"))

ISL_salmon_sf <- ASC_salmon_sf %>%
  dplyr::filter(crt_cnt == "Iceland")

mapview(ISL_salmon_sf)

ISL_pts <- st_centroid(ISL_salmon_sf)

ISL_pts_latlon <- st_transform(ISL_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry) %>%
  mutate(iso3c = "ISL")

farms_ISL <- data.frame(do.call(rbind, st_geometry(ISL_pts_latlon))) 
names(farms_ISL) <- c("lon", "lat")
farms_all_ISL <- farms_ISL %>%
  cbind(iso3c = ISL_pts_latlon$iso3c)

write_csv(farms_all_ISL, here("marine/salmon/salmon_farm/data/farm_sites/farms_isl.csv"))

```

# Join cell count dataframes

```{r}

farm_files <- list.files(here("marine/salmon/salmon_farm/data/farm_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)

# all_farms <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), col_types = "ddcc")

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

unique(all_farms$iso3c)
```

### 2021-02-04 marine/salmon/salmon_farm/STEP3_regional_salmon_production.Rmd
cleaned up scripts and updated file paths

---
title: "Regional Production"
author: "Gage Clawson"
date: "10/29/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

We do not have salmon production by farm, however, for some countries we have salmon production according to region. We will use this information to distribute production among the farms within a region.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/"

#Set the year that we want to use
data_year <- 2017 # corresponds to the year of local production

```

# Chile

```{r}

# make sure the names in our data match the official names:
chile_reg <- read.csv(here("_spatial/_output/food_subrgns.csv")) %>% 
  filter(iso3c == "CHL")

# rainbow trout = TRUCHA ARCOIRIS
chile_salmon <- c("SALMON PLATEADO O COHO", "SALMON DEL ATLANTICO")

chile_prod <- fread(file.path(path, "/Regional_aquaculture_production/Chile/Chile_harvest_by_species_region_2017.csv"), skip = 4, header = TRUE, na.string = "-") %>% 
  dplyr::select(-"V18", -"Total") %>% 
  gather(Region, Reg_production, `XV`:`XII`) %>% 
  filter(ESPECIE %in% chile_salmon) %>%   
  mutate(Reg_production = as.numeric(gsub(",", "", Reg_production)),
         iso3c = "CHL",
         year = data_year) %>% 
  group_by(Region, iso3c, year) %>% 
  summarise(Salmon_tonnes = sum(Reg_production, na.rm = TRUE)) %>%
  ungroup()

total_prod_chl <- sum(chile_prod$Salmon_tonnes)

regions <- data.frame(Region = c("I", "II", "III", "IV", "V", "RM", "VI", "VII", "VIII", "IX", "X", "XI", "XII", "XIV", "XV"),
                      Region_name = c("Tarapacá", "Antofagasta", "Atacama", "Coquimbo", "Valparaíso", "Región Metropolitana de Santiago",
                                      "Libertador General Bernardo O'Higgins", "Maule", "Bío-Bío", "Araucanía", "Los Lagos", 
                                      "Aisén del General Carlos Ibáñez del Campo", "Magallanes y Antártica Chilena", "Los Ríos", "Arica y Parinacota"))

chile_prod <- chile_prod %>% 
  mutate(Total_Salmon_t = total_prod_chl) %>% 
left_join(regions, by="Region") %>%
  mutate(prop_production = Salmon_tonnes/Total_Salmon_t) %>%
  dplyr::select(iso3c, region = Region_name, year, prop_production)

```

# Norway
Data from:
https://www.ssb.no/en/statbank/table/09259/
09259: Aquaculture. Stock and loss of live fish for food (rough classification) (C) 2010 - 2018 (replaced ":" with NA)

https://www.ssb.no/en/statbank/table/07326
07326: Aquaculture. Sales of slaughtered fish for food, by region, fish species, contents and year
(replaced "-" with 0; replaced, ":" with NA)

Downloaded: Jan 22 2020

Gapfilling missing data.  loss-percent variable is cut because it cannot be gapfilled.
```{r}

#gapfill missing data

norway_mar <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Regional_aquaculture_production/Norway/norway_mariculture.csv") %>%
  gather(key = "year", value = "value", -region, -species, -variable, -units) %>%
  mutate(year = gsub("X", "", year)) %>%
  filter(variable != "loss_percent")

# first round of gapfilling if every year is NA or 0, then 0
norway_mar_gf <- norway_mar %>%
  group_by(region, species, variable) %>%
  mutate(total_sp = sum(value, na.rm=TRUE)) %>%   # if all NA or 0 for a species across years, then 0
  mutate(gapfilled = ifelse(total_sp==0 & is.na(value), "gapfilled", NA)) %>%
    mutate(value = ifelse(total_sp == 0 & is.na(value), 0, value)) %>%
  dplyr::select(-total_sp)

# second round of gapfilling, gapfill based on unaccounted fish and avg proportion of aquaculture in previous years

avg_totals <- filter(norway_mar, species == "Total") %>%
  group_by(region, variable) %>%
  summarize(total_mean = mean(value))

totals <- filter(norway_mar, species=="Total") %>%
  dplyr::select(-species, total_value=value)

norway_mar_gf <- norway_mar_gf %>%
  left_join(avg_totals) %>%               
  left_join(totals) %>%
  group_by(region, species, variable) %>%
  mutate(avg_value = mean(value, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(proportion = avg_value/total_mean) %>%
  group_by(region, variable, year) %>%
  mutate(total_obs = sum(value[.$species != "Total"], na.rm=TRUE)) %>%
  mutate(unaccounted = total_value - total_obs) %>%
  mutate(unaccounted = ifelse(unaccounted < 0, 0, unaccounted))  %>%     # some negatives due to rounding and possible data entry error
  mutate(avg_value_missing = proportion * ifelse(is.na(value), 1, 0)) %>%                            # figure out proportion of only missing
   mutate(prop_value_missing = avg_value_missing/sum(avg_value_missing, na.rm=TRUE)) %>%
  mutate(gf_value = prop_value_missing * unaccounted) %>%                           # gapfill missing data with unaccounted production multiplied by the average proportion of production for each species in previous years 
mutate(gapfilled = ifelse(is.na(value) & !is.na(gf_value), "gapfilled", gapfilled)) %>%
  mutate(value = ifelse(is.na(value), gf_value, value))

## watch these be gapfilled
summary(norway_mar_gf) # make sure no NA values
data.frame(filter(norway_mar_gf, is.na(value)))
filter(norway_mar_gf, year==2017)
filter(norway_mar_gf, region=="Rogaland", variable == "tonnes_fish")

summary(norway_mar_gf)
dim(norway_mar_gf)
summary(norway_mar)
dim(norway_mar)

## clean and save data
norway_mar_gf <- norway_mar_gf %>%
dplyr::select(region, species, variable, units, year, value, gapfilled) %>%
  filter(species != "Total")
write.csv(norway_mar_gf, here("marine/salmon/salmon_farm/data/norway_mariculture_gf.csv"), row.names=FALSE )

```

Organize data to match names on map.
```{r}

norway_reg <- read.csv(file.path(path, "Country_regions/Country_regions_cellindex.csv")) %>% 
  filter(ISO3 == "NOR")
unique(norway_reg$Region_name)

  # other regions: could also include: Hedmark and Uppland (inland regions), and Akershus, Vestfold, Buskerud (no farm points)
  # Trondelag regions: combined after 2017, about equal number of production
region_splits <- data.frame(region = c("Trøndelag", "Trøndelag",                                  
                                            "Other Counties", "Other Counties", "Other Counties", "Other Counties", "Other Counties"),
                            Region_name_split = c("Sør-Trøndelag", "Nord-Trøndelag",
                                                  "Oslo", "Telemark", "Ãstfold", "Aust-Agder", "Vest-Agder")) %>%
  group_by(region) %>%
  mutate(region_split_n = n())

# sum salmon production among species
production <- read.csv(here("marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>%
  filter(variable=="tonnes_fish") %>%
  filter(species %in% c("Salmon")) %>%
  filter(year == 2017) %>%
  group_by(year, region) %>%
  summarize(tonnes_salmon = sum(value, na.rm=TRUE)) %>%
  ungroup()

# spliting regions
production <- production %>%
  left_join(region_splits) %>%
  mutate(region_split_n = ifelse(is.na(region_split_n), 1, region_split_n)) %>%
  mutate(tonnes_salmon_corrected = tonnes_salmon/region_split_n) %>%
  mutate(region_corrected = ifelse(is.na(Region_name_split), as.character(region), as.character(Region_name_split))) %>%
  group_by(region_corrected, year) %>%
  summarize(Salmon_tonnes = sum(tonnes_salmon_corrected, na.rm=TRUE)) %>%
  ungroup()

# no farms showing up in Oslo or Troms.  This is such a low proportion of production, will cut.  This production 
# will be distributed over other farms
production <- production %>%
  mutate(Salmon_tonnes = ifelse(region_corrected %in% c("Troms", "Oslo"), 0, Salmon_tonnes))

# cleaning and adding total
nor_prod <- production %>%
  mutate(iso3c = "NOR") %>%
  group_by(year) %>%
  mutate(Total_Salmon_t = sum(Salmon_tonnes, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(prop_production = Salmon_tonnes/Total_Salmon_t) %>%
  filter(year == data_year) %>%
  dplyr::select(iso3c, region = region_corrected, year, prop_production)

```

# UK: Scotland

https://www.mcsuk.org/media/seafood/Farmed_Fish.pdf
> In the UK open sea cage farming happens almost exclusively in the west coast of Scotland and the Scottish Islands due to their good water quality and coastline topography, which provides numerous sheltered sea-lochs and voes.

Scottland point data:
https://data.gov.uk/data/map-preview?e=-0.53202&n=61.46459&s=54.53297&url=http%3A%2F%2Fmsmap1.atkinsgeospatial.com%2Fgeoserver%2Fnmpwfs%2Fows%3Ftoken%3Dd46ffd2a-e192-4e51-8a6a-b3292c20f1ee%26service%3Dwms%26request%3DgetCapabilities&w=-7.75714
```{r}

uk_reg <- read.csv(file.path(path, "Country_regions/Country_regions_cellindex.csv")) %>% 
  filter(ISO3 == "GBR")

scot_prod <- fread(file.path(path, "/Regional_aquaculture_production/Scotland/Scotland_regional_salmon_production.csv")) %>% 
  dplyr::select(Region, year = Year, Tonnage) %>% 
  dplyr::filter(year == data_year,
         !Region == "All Scotland") %>% 
  dplyr::mutate(Salmon_tonnes = as.numeric(gsub(",","",Tonnage)),
         iso3c = "GBR") %>% 
  dplyr::select(-Tonnage)

total_prod_scot <- sum(scot_prod$Salmon_tonnes, na.rm = TRUE)

uk_prod <- scot_prod %>% 
  mutate(Total_Salmon_t = total_prod_scot) %>%
  mutate(prop_production = Salmon_tonnes/Total_Salmon_t) %>%
  dplyr::select(iso3c, region=Region, year, prop_production)

```

# Canada

Data can be found here: http://www.dfo-mpo.gc.ca/stats/aqua/aqua-prod-eng.htm

Adding in Newfoundland and Labrador data based on this information:

https://www.fishaq.gov.nl.ca/pdf/aquaculture_2015_year.pdf
https://www.fishaq.gov.nl.ca/stats/pdf/aqua_production_and_%20value_%202016%20aqua.pdf

```{r}

can_reg <- read.csv(file.path(path, "Country_regions/Country_regions_cellindex.csv")) %>% 
  filter(ISO3 == "CAN")
unique(can_reg$Region_name)

can_prod <- read_csv(file.path(path, "Regional_aquaculture_production/Canada/Regional_production_by_species_2017.csv")) %>% 
    rename(species = X1) %>% 
    gather(region, Production_t, NL:Canda) %>% 
  filter(species == "Salmon",
         !is.na(Production_t),
         !Production_t == 0,
         !region == "Canda") %>% 
  rename(Salmon_tonnes = Production_t) %>% 
  mutate(region = ifelse(region == "NS", "Nova Scotia",
                              ifelse(region == "BC", "British Columbia",
                                     ifelse(region == "NB", "New Brunswick", NA))),
    iso3c = "CAN")

NL <- data.frame(species = "Salmon", Year = 2017, region="Newfoundland and Labrador", Salmon_tonnes = 19684, iso3c="CAN")

can_prod <- rbind(can_prod, NL) %>%
  mutate(Salmon_tonnes = as.numeric(Salmon_tonnes)) %>%
  mutate(Salmon_tonnes = ifelse(is.na(Salmon_tonnes), 11078, Salmon_tonnes))

total_prod_can <- sum(can_prod$Salmon_tonnes, na.rm = TRUE)

can_prod <- can_prod %>% 
  mutate(Total_Salmon_t = total_prod_can) %>%
  mutate(prop_production = Salmon_tonnes/Total_Salmon_t) %>%
  dplyr::select(iso3c, region, year=Year, prop_production)

```

## Denmark

Data from http://maps.helcom.fi/website/mapservice/

```{r}
farms_denmark <- st_read(file.path(path, "Aquaculture_locations/HELCOM_Baltic/Finfish_mariculture.shp"), options = "ENCODING=WINDOWS-1252") %>%
  filter(COUNTRY == "DK") %>%
  dplyr::select(region = NAME, PR_AV_TON) %>%
  mutate(iso3c = "DNK")

dnk_prod_reg <- st_set_geometry(farms_denmark, NULL)

total_prod_DNK <- sum(dnk_prod_reg$PR_AV_TON)

dnk_prod <- dnk_prod_reg %>%
  mutate(prop_production = PR_AV_TON/total_prod_DNK) %>%
  mutate(year = 2017) %>%
  dplyr::select(iso3c, region, year, prop_production)

```

## Finland

Data from http://maps.helcom.fi/website/mapservice/

```{r}
farms_finland <- st_read(file.path(path, "Aquaculture_locations/HELCOM_Baltic/Finfish_mariculture.shp"), options = "ENCODING=WINDOWS-1252") %>%
  filter(COUNTRY == "FI") %>%
  dplyr::select(region = NAME, P_AV_TON) %>%
  mutate(iso3c = "FIN")

fin_prod_reg <- st_set_geometry(farms_finland, NULL)

total_prod_FIN <- sum(fin_prod_reg$P_AV_TON)

fin_prod <- fin_prod_reg %>%
  mutate(prop_production = P_AV_TON/total_prod_FIN) %>%
  mutate(year = 2017) %>%
  dplyr::select(iso3c, region, year, prop_production)
sum(fin_prod$prop_production)
```

## Sweden

Data from http://maps.helcom.fi/website/mapservice/

```{r}
farms_sweden <- st_read(file.path(path, "Aquaculture_locations/HELCOM_Baltic/Finfish_mariculture.shp"), options = "ENCODING=WINDOWS-1252") %>%
  filter(COUNTRY == "SE") %>%
  dplyr::filter(PRODUCTION %in% c("Rainbow trout (Oncorhynchus mykiss)", "Salmon, Rainbow trout (Oncorhynchus mykiss), Char (salvelinus)", "Salmon, Trout (Salmo trutta)", "Salmon", "Salmon, Trout (Salmo trutta), Rainbow trout (Oncorhynchus mykiss), Char (salvelinus)", "Perch (perca fluviatilis), Pikeperch (Sander lucioperca), Rainbow trout (Oncorhynchus mykiss)", "Trout (Salmo trutta)", "Salmon, Trout (Salmo trutta) - breeding", "Perch (perca fluviatilis), Grayling (thymallus thymallus), Rainbow trout (Oncorhynchus mykiss), Char (salvelinus), tropical fish species")) %>%
  dplyr::select(region = NAME, P_AV_TON) %>%
  mutate(iso3c = "SWE")

swe_prod_reg <- st_set_geometry(farms_sweden, NULL)

total_prod_SWE <- sum(swe_prod_reg$P_AV_TON)

swe_prod <- swe_prod_reg %>%
  mutate(prop_production = P_AV_TON/total_prod_SWE) %>%
  mutate(year = 2017) %>%
  dplyr::select(iso3c, region, year, prop_production)

```

# Join regional data and save
```{r}

all_prod <- Reduce(function(x, y) merge(x, y, all=TRUE), list(chile_prod, nor_prod, uk_prod, can_prod, dnk_prod, swe_prod, fin_prod))

write_csv(all_prod, here("marine/salmon/salmon_farm/data/proportional_regional_production.csv"))

# all_prod <-  read_csv(here("marine/salmon/salmon_farm/data/proportional_regional_production.csv"))
```

### 2021-02-04 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
cleaned up scripts and updated file paths

---
title: "FAO shrimp production"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

All data is ultimately adjusted to FAO production data.  This script cleans the fao mariculture data and subsets it to to the relevant years of data and species (shrimp).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))

```

Subset the data to include only the species (shrimp) and countries we are interested in. Then summarize by total tonnes of shrimp per country/year. (There are multiple shrimp species)

```{r}

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
shrimp_list <- species_list$species[species_list$aq_group=="shrimps_prawns"]
shrimp_list

## write out shrimp taxa and production for Juliette
fao_shrimp_taxa_prod <- fao %>%
  filter(species %in% shrimp_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

write.csv(fao_shrimp_taxa_prod, here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp_taxa_production.csv"), row.names=FALSE)

# include only shrimp
fao_shrimp <- fao %>%
  filter(species %in% shrimp_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year)

write.csv(fao_shrimp, here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv"), row.names=FALSE)

## Do some exploration:

 explore <- read_csv(here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production)*100),2))

sum(explore$fao_tonnes_production)

asc_countries <- c("Australia", "Bangladesh", "Belize", "China", "Colombia", "Ecuador", "Guatemala", "Honduras", "India", "Indonesia", "Madagascar", "Mexico", "New Caledonia", "Nicaragua", "Panama", "Peru", "Thailand", "Venezuela, Boliv Rep of", "Viet Nam")

explore_test <- explore %>%
  dplyr::filter(!(country %in% asc_countries))

sum(explore_test$percent) 
 100 - 6.38 # 93.62

asc_explore <- explore %>%
  dplyr::filter(country %in% asc_countries)

## missing venezuela

sum(asc_explore$fao_tonnes_production)
sum(asc_explore$percent) + sum(explore_test$percent)
sum(asc_explore$fao_tonnes_production) + sum(explore_test$fao_tonnes_production)

sum(explore$fao_tonnes_production)
```

### 2021-02-04 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
cleaned up scripts and updated file paths

---
title: "Location of Shrimp Farms"
author: "Gage Clawson (USCB, NCEAS, OHI)"
date: "10/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script standardizes location of shrimp farms to be lat/long point data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"
fao_shrimp <- read_csv("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv") %>%
  dplyr::filter(year == 2017)

unique(fao_shrimp$country)
#  [1] "Australia"                "Bangladesh"               "Belize"                   "Brazil"                  
#  [5] "Brunei Darussalam"        "Cambodia"                 "China"                    "Colombia"                
#  [9] "Costa Rica"               "Cuba"                     "Ecuador"                  "El Salvador"             
# [13] "Guatemala"                "Honduras"                 "India"                    "Indonesia"               
# [17] "Iran (Islamic Rep. of)"   "Japan"                    "Korea, Republic of"       "Madagascar"              
# [21] "Malaysia"                 "Mexico"                   "Myanmar"                  "New Caledonia"           
# [25] "Nicaragua"                "Panama"                   "Peru"                     "Philippines"             
# [29] "Saudi Arabia"             "Sri Lanka"                "Taiwan Province of China" "Thailand"                
# [33] "United States of America" "Venezuela, Boliv Rep of"  "Viet Nam" 
```

## explore
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

```{r}
ASC_data <- st_read(file.path(path, "ASC_data/ASC_all_sf.shp"))

unique(ASC_data$spcs__c)

ASC_shrimp <- ASC_data %>%
  dplyr::filter(spcs__c == "Shrimp")

countries <- c(sort(unique(ASC_shrimp$crt_cnt)))

#  [1] "India" (FAO)                              "Viet Nam"    (FAO)                      
#  [3] "Ecuador"    (FAO)                        "Venezuela (Bolivarian Republic of)" (FAO)
#  [5] "Honduras"      (FAO)                     "China"           (FAO)                  
#  [7] "Mexico"      (FAO)                       "Thailand"                          
#  [9] "Madagascar"    (FAO)                     "Panama"   (FAO)                         
# [11] "Indonesia"  (FAO)                        "Nigeria"    (NO FAO)                       
# [13] "Bangladesh" (FAO)                        "Guatemala"    (FAO)                     
# [15] "Nicaragua"     (FAO)                     "Belize"         (FAO)                   
# [17] "New Caledonia"  (FAO)                    "Tanzania, United Republic of"      (NO FAO)
# [19] "Australia"      (FAO)                    "Mozambique"  (NO FAO)                      
# [21] "Peru"    (FAO)                           "Colombia"   (FAO)

setdiff(ASC_shrimp$crt_cnt, fao_shrimp$country) # don't worry about venezuela... just a mispelling mismatch
# In ASC and not in FAO:
# [1] "Nigeria"                           
# [3] "Tanzania, United Republic of"       "Mozambique"

setdiff(fao_shrimp$country, ASC_shrimp$crt_cnt)
## Need to find the farm locations for these countries:

#  [1] "Brazil"                   "Brunei Darussalam"        "Cambodia"                 "Costa Rica"              
#  [5] "Cuba"                     "El Salvador"              "Iran (Islamic Rep. of)"   "Japan"                   
#  [9] "Korea, Republic of"       "Malaysia"                 "Myanmar"                  "Philippines"             
# [13] "Saudi Arabia"             "Sri Lanka"                "Taiwan Province of China" "United States of America"

```

# Raster

Standard raster used for this analysis

```{r}

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

# Map data from ASC (contains 19/35 countries)

Data comes from https://gis.asc-aqua.org/arcgis_app/

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

```{r}

# get iso3c codes
iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))

# read in shp and filter out countries not in FAO
farms_all <- ASC_shrimp %>%
  cbind(iso) %>%
  dplyr::filter(iso3c != "NGA",
                iso3c != "TZA",
                iso3c != "MOZ")

mapview(farms_all$geometry)

unique(farms_all$iso3c)

all_pts <- st_centroid(farms_all)

all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
  dplyr::select(geometry, iso3c)

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

## save farm location
write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/farm_sites/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)

```

Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

# Brazil
 - Has a map of major shrimp farming locations (from 2002): http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.200.2425&rep=rep1&type=pdf
 - Also has a table of number of farms and area per state. I will just place one point at on each state, and add up the area listed in the table.

 - Pará: -0.952238, -48.466718: 70 hectares
 - Maranhão: -2.365963, -44.263791: 64 hectares
 - Piauí: -2.859201, -41.551117: 425 hectares
 - Ceará: -3.646201, -38.627546: 982 hectares
 - Rio G. do Norte: -5.100375, -35.667111: 1752 hectares
 - Paraíba: -7.089602, -34.818058: 420 hectares
 - Pernambuco: -8.115310, -34.840892: 670 hectares
 - Alagoas: -9.700209, -35.739681: 20 hectares
 - Sergipe: -10.991527, -37.030238: 47 hectares
 - Bahia: -13.046432, -38.515139: 1510 hectares
 - São Paulo: inland, don't include
 - Paraná: -25.535885, -48.268714: 50 hectares
 - Sta. Catarina: -27.505551, -48.393581: 200 hectares

Source:
Mole, P., Bunge, J., 2002. Shrimp Farming in Brazil: An Industry Overview.

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
  mutate(iso3c = "BRA")

write_csv(farms_bra, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_bra.csv"))

## visualize it 
farms_bra <-  st_as_sf(farms_bra, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bra)
```

# Brunei
Note: These are all ponds on land, that use seawater.

 - shrimp farms from this company: http://www.golden-corp.com/facilities.php?view=shrimp-farm-and-processing
 - the above map matches well with this... https://www.slideshare.net/ridzaludin/brunei-darussalam

 - ARDC: 4.716865, 114.535353: 14 hectares : Has a production table here: https://www.aquaculturealliance.org/advocate/brunei-project-develops-technology-for-large-black-tiger-shrimp-production-part-5/ : Uses seawater
 - Semaun Aquaculture: 4.722253, 114.541318: [40 hectares](https://pghjismail.wixsite.com/semaunaquaculture) : produce an average total of 60 metric tons of shrimp yearly : uses seawater
 - Keramut Shrimp Culture Industrial Site: 4.742089, 114.574539 : [92 hectares](https://borneobulletin.com.bn/2020/03/minister-visits-shrimp-farm-site-2/) :  : uses seawater
 - Penyatang Shrimp Culture Industrial Site: 4.761099, 114.610558: 200 hectares (from the map): uses seawater
 - Semaun Marine hatchery: 4.781321, 114.607222: 0.4 hectares (measured on google maps)
 - TMM phase 1/2: 4.970718, 115.043816: 51.471511 hectares (measured on google maps)

Source: 
Golden Corporation Shrimp Farm and Processing Map, n.d. http://www.golden-corp.com/facilities.php?view=shrimp-farm-and-processing

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN")

write_csv(farms_brn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_brn.csv"))

## visualize it 
farms_brn <-  st_as_sf(farms_brn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_brn)
```

# Cambodia 
 - There is a table in here that has potential. We will just place a point on the coast for each of these coastal places, and use the area noted in the paper later if needed. If the province is not coastal, it will not be placed on the map: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf

 - Kampot: 10.559329, 104.213349: 1516 hectares
 - Kep: 10.449929, 104.404934: 459 hectare
 - Koh Kong: 11.740932, 102.898284: 26762 hectare
 - Preah Sihanouk: 10.743017, 103.653332: 6388 hectares
 - Pursat: Inland, don't include
 - Svay Rieng: Inland, don't include
 - Takeo: Inland, don't include

Source: 
Eastman, J.R., Crema, S.C., Sangermano, F., Cunningham, S., Xiao, X., Hu, P., Johnson, C., Arakwiye, B., Crone, N., 2015. A Baseline Mapping of Aquaculture and Coastal Habitats in Thailand, Cambodia and Vietnam 14.

```{r}
farms_khm <- data.frame(lat=c(10.559329, 10.449929, 11.740932, 10.743017),
                        lon=c(104.213349, 104.404934, 102.898284, 103.653332),
                        area_ha = c(1516, 459, 26762, 6388)) %>%
  mutate(iso3c = "KHM")

write_csv(farms_khm, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_khm.csv"))

## visualize it 
farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_khm)
```

# Costa Rica
 - This says there are 90 shrimp producers in Costa Rica. all located in Puntarenas and Guanacaste provinces: http://www.fao.org/fishery/countrysector/naso_costarica/en
 - I will equally allocate the farm points along the coast line of these two provinces (90 farms total).

Source: 
National Aquaculture Sector Overview. Costa Rica, 2005. , National Aquaculture Sector Overview Fact Sheets.

```{r}
provinces <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Costa_rica/gadm36_CRI_1.shp"))
mapview(provinces)

guana_punta <- provinces  %>%
  dplyr::filter(NAME_1 %in% c("Guanacaste", "Puntarenas"))

mapview(guana_punta)

world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

world <- st_as_sf(world)

costa_world_crs <- st_transform(guana_punta, crs(world))

costa_world_crop <- st_crop(world, costa_world_crs) ## crop to costa rica extent 
plot(costa_world_crop)
mapview(costa_world_crop)

costa_crop <- as(costa_world_crop, "Spatial")
plot(costa_crop)
mapview(costa_crop)

costa_points_lines <- sample.line(costa_crop, n = 121) ## equally place the number of farms along the coastline 
class(costa_points_lines)
plot(costa_points_lines)

costa_points <- st_as_sf(costa_points_lines)
mapview(costa_points)

## Now filter out the points that fall outside of costa rica 
costa_points_final <- costa_points[4:93,]
mapview(costa_points_final)

cri_pts <- st_centroid(costa_points_final)

cri_pts_latlon <- st_transform(cri_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_cri <- data.frame(do.call(rbind, st_geometry(cri_pts_latlon)))
names(farms_cri) <- c("lon", "lat")

farms_cri_final <- farms_cri %>%
  mutate(iso3c = "CRI")

## visualize it 
farms_cri <-  st_as_sf(farms_cri, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_cri)

## write to farms folder 
write_csv(farms_cri_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_cri.csv"))

```

# Cuba

http://www.fao.org/fishery/countrysector/naso_cuba/en
 - "Marine cultures are being developed experimentally in conjunction with shrimp culture under the guidance of the Fisheries Research Center of the MIP.

Up-to-date, investment development and activities have been directed towards two zones:
Experimental Spawning Center at Cabo Cruz (some 100 km from Manzanillo).
 - 19.841789, -77.737212

The on-growing area in Niquero (70 km from Manzanillo), where packing facilities on land are available." 
 - 20.047065, -77.593449

Source: 
National Aquaculture Sector Overview. Cuba, 2005. , National Aquaculture Sector Overview Fact Sheets.

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB")

write_csv(farms_cub, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_cub.csv"))

## visualize it 
farms_cub <-  st_as_sf(farms_cub, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_cub)
```

# El Salvador 
 - Could use the table here. We would just assign one farm per each city listed: http://www.fao.org/fishery/countrysector/naso_elsalvador/en

 - Ahuachapan: seems inland
 - Sonsonate: seems inland
 - La Paz: 13.336985, -89.014470: 8.2 hectares
 - Usulután: seems inland
 - La Unión: 13.354459, -87.863771: 50 hectares

 Source: 
National Aquaculture Sector Overview. El Salvador, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50)) %>%
  mutate(iso3c = "SLV")

write_csv(farms_slv, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_slv.csv"))

## visualize it 
farms_slv <-  st_as_sf(farms_slv, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_slv)
```

# Iran 
 - Claims 205 farms in 2000: http://library.enaca.org/Shrimp/Case/Africa/FinalAfrica.pdf

NASO Maps 
 - This is better information, so I will use these points. 
http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/iran/en/

Source: 
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

```{r}
## read in thailand shp file
iran_file <- file.path(path, "FAO_NASO/NASO/Point/Iran.kml")

iran_aqua <- read_sf(iran_file)

unique(iran_aqua$description)

mapview(iran_aqua)

## We need to filter for just the appropriate species of shrimp aquaculture

iran_finfish <- iran_aqua %>%
  dplyr::filter(!(str_detect(description, "Freshwater|freshwater"))) %>% ## Filter out freshwater systems
  dplyr::filter(!is.na(description))

mapview(iran_finfish) ## these are all marine shrimp farms now

irn_bivalve_mol <- st_transform(iran_finfish, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
irn_pts <- st_centroid(irn_bivalve_mol)

irn_pts_latlon <- st_transform(irn_pts, crs = "+init=epsg:4326")

mapview(irn_pts_latlon)

farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon))) 
names(farms_irn) <- c("lon", "lat")
farms_irn <- farms_irn %>%
  mutate(iso3c="IRN")

write_csv(farms_irn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))

farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_irn)
```

old methods: 
```{r}
# iran <- ne_countries(scale = 10, country = "Iran", returnclass = "sf")
# mapview(iran)
# 
# world <- ne_coastline(scale = 10) #world map with 10m resolution
# plot(world)
# 
# world <- st_as_sf(world)
# 
# iran_world_crs <- st_transform(iran, crs(world))
# 
# iran_world_crop <- st_crop(world, iran_world_crs) ## crop to iran extent
# plot(iran_world_crop)
# mapview(iran_world_crop)
# 
# iran_world_crop <- head(iran_world_crop, 2) ## filter out lines not in iran
# mapview(iran_world_crop)
# 
# iran_world_crop <- tail(iran_world_crop, 1)
# 
# iran_crop <- as(iran_world_crop, "Spatial")
# plot(iran_crop)
# mapview(iran_crop)
# 
# 
# 
# iran_points_lines <- sample.line(iran_crop, n = 221) ## equally place the number of farms along the coastline 
# class(iran_points_lines)
# plot(iran_points_lines)
# 
# iran_points <- st_as_sf(iran_points_lines)
# mapview(iran_points)
# 
# ## Now filter out the points that fall outside of iran
# iran_points_final <- iran_points[17:221,]
# mapview(iran_points_final)
# 
# 
# irn_pts <- st_centroid(iran_points_final)
# 
# irn_pts_latlon <- st_transform(irn_pts, crs = "+init=epsg:4326") %>%
#   dplyr::select(geometry)
# 
# farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon)))
# names(farms_irn) <- c("lon", "lat")
# 
# farms_irn_final <- farms_irn %>%
#   mutate(iso3c = "IRN")
# 
# ## visualize it 
# farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_irn)
# 
# ## write to farms folder 
# write_csv(farms_irn_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))

```

old old methods:
 - From google maps: 
    - Sea waves TRD: 26.790754, 55.396608: 582 hectares 
    - Iran Aquatic: 27.135585, 56.887211: 1877 hectares 
    - Technoshrimp: 29.227964, 50.709040: 1303 hectares 
    - Shrimp Breeders Delvar site: 28.770827, 51.046329: 312 hectares
    - Pars Abzistan Shrimp & Fish Hatchery: 28.781671, 51.048787: 280 hectares
    - Shrimp Marjan: 27.851429, 51.984108: 156.5493 hectares
    - Shrimp Aquaculture: 26.671137, 55.902159: 31 hectares 
    - Pardis: looks like indoor, don't include
    - Sontderaf: looks like indoor, don't include

```{r}
# farms_irn <- data.frame(lat=c(26.790754, 27.135585, 29.227964, 28.770827, 28.781671, 27.851429, 26.671137),
#                         lon=c(55.396608, 56.887211, 50.709040, 51.046329, 51.048787, 51.984108, 55.902159),
#                         area_ha = c(582, 1877, 1303, 312, 280, 156.5493, 31)) %>%
#   mutate(iso3c = "IRN")
# 
# write_csv(farms_irn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))
# 
# ## visualize it 
# farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
#                  crs = crs(gadm_latlon), agr = "constant")
# 
# mapview(farms_irn)
```

# Japan
 - One shrimp farm on this companies map: https://fis.com/fis/worldnews/worldnews.asp?l=e&id=100979&ndb=1
    - Near Minamikyūshū: 31.182129, 130.604815

Source: 
NA

```{r}
farms_jpn <- data.frame(lat=c(31.182129),
                        lon=c(130.604815),
                        area_ha = c(NA)) %>%
  mutate(iso3c = "JPN")

write_csv(farms_jpn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_jpn.csv"))

## visualize it 
farms_jpn <-  st_as_sf(farms_jpn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_jpn)
```

# Korea, Republic of

https://www.fftc.org.tw/htmlarea_file/activities/20110719101541/13.pdf
 - "West coast: shrimp (Penaeus japonicus, P. chinensis) is mainly cultivated in Taean, ChungNam"
 - I will put a point there. 
 - Taean: 36.752683, 126.150252: 672 hectares (taken from "Korean Aquaculture at a glance")

Source: 
NA

```{r}
farms_kor <- data.frame(lat=c(36.752683),
                        lon=c(126.150252),
                        area_ha = c(672)) %>%
  mutate(iso3c = "KOR")

write_csv(farms_kor, here("aquaculture/marine/shrimp/shrimp_farms/data/farm_sites/farms_kor.csv"))

## visualize it 
farms_kor <-  st_as_sf(farms_kor, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_kor)
```

# Malaysia
 - [Seafood watch](https://www.seafoodwatch.org/-/m/sfw/pdf/reports/s/mba_seafoodwatch_malaysian_farmed_marine_shrimp_report.pdf) claims you can find the names and locations of registered shrimp farms here, but I can only find the broad suitable areas: https://www.dof.gov.my/ 
 - Broad suitable areas https://www.dof.gov.my/index.php/pages/view/78. I'll use these and use the area as a production estimate. Saved onto aurora /home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Malaysia/malaysia_shrimp_farms.csv.

Source: 
Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. . Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78

```{r}
malaysia_shrimp_loc <- read_csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Malaysia/malaysia_shrimp_farms.csv") %>%
  clean_names()

mys_area <- c(malaysia_shrimp_loc$luas_hektar)
```

Farms: 
 - AIR HANGAT, LANGKAWI, KEDAH: 6.433288, 99.826952
 - TAMAN AKUAKULTUR SEBATU MELAKA: 2.108604, 102.463536
 - TAMAN AKUAKULTUR LKIM TELAGA AIR, SARAWAK: 1.676758, 110.210032
 - KG. MERCHONG, PEKAN, PAHANG: 3.018320, 103.430156
 - KG. PENGKALAN GELAP, SETIU, TERENGGANU: 5.674088, 102.721589
 - KG. PASIR PUTEH, MARANG, TERENGGANU: 4.984545, 103.328932
 - PENARIK, SETIU, TERENGGANU: 5.596019, 102.826214
 - TANJUNG MANIS, SARAWAK: 2.197050, 111.183470
 - RUNGKUP HILIR, PERAK: 3.888025, 100.704595
 - SG. NIPAH, SABAK BERNAM, SELANGOR: 3.663462, 100.975557
 - TANJUNG BATU, PEKAN, PAHANG: 3.203638, 103.446051

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018320, 5.674088, 4.984545, 5.596019, 2.197050, 3.888025, 3.663462, 3.203638),
                        lon=c(99.826952, 102.463536, 110.210032, 103.430156, 102.721589, 103.328932, 102.826214, 111.183470, 100.704595, 100.975557, 103.446051),
                        area_ha =mys_area) %>%
  mutate(iso3c = "MYS")

write_csv(farms_mys, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_mys.csv"))

## visualize it 
farms_mys <-  st_as_sf(farms_mys, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mys)
```

# Myanmar
 - http://www.fao.org/3/ad497e/ad497e05.htm
 "The largest area of shrimp farming is found in Rakhine State (155,533 acres), followed by Ayeyarwaddy (33 373 acres), Yangon (7 394 acres), with smaller areas in Bago, Kayin, Mon and Thaninthary"
 - We will use that for our points. One point for each state. 
 - Rakhine State: 20.117197, 92.884433: 62941.972 hectares
 - Ayeyarwaddy: 15.967665, 94.337465: 13505.574 hectares
 - Yangon: 16.441903, 96.371311: 2992.246 hectares
 - Bago: Inland, don't include
 - Kayin: Inland, don't include
 - Mon: 16.100756, 97.581799
 - Thaninthary: 13.436424, 98.323120

Source: 
Myanmar aquaculture and inland fisheries, 2003. Food and Agriculture Organization of the United Nations Regional Office For Asia and the Pacific.

```{r}
farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
  mutate(iso3c = "MMR")

write_csv(farms_mmr, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_mmr.csv"))

## visualize it 
farms_mmr <-  st_as_sf(farms_mmr, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mmr)
```

# Phillipines

https://juniperpublishers.com/ofoaj/pdf/OFOAJ.MS.ID.555668.pdf
"There are 271 brackish water shrimp farms (3,617.8ha) registered at the Bureau of Fisheries and Aquatic Resources of the Philippines as of 2013. "

 - I will equally place 271 farms along the coast of the philippines
 - We know that there are 3617.8 hectares of farms... we will allocate that area evenly... 3617.8/271 = 13.35

Source: 
Vergel, C., 2017. Current Trends in the Philippines’ Shrimp Aquaculture lndustry:A Booming Blue Economy in the Pacific. OFOAJ 5. https://doi.org/10.19080/OFOAJ.2017.05.555668

```{r}
philly <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
mapview(philly)

world <- ne_coastline(scale = 110) #world map with 110m resolution
plot(world)

world <- st_as_sf(world)

philly_world_crs <- st_transform(philly, crs(world))

philly_world_crop <- st_crop(world, philly_world_crs) ## crop to philippines extent
plot(philly_world_crop)
mapview(philly_world_crop)

philly_world_crop <- philly_world_crop[-c(1), ] ## delete lines that are not in philippines

mapview(philly_world_crop)

philly_crop <- as(philly_world_crop, "Spatial")
plot(philly_crop)
mapview(philly_crop)

philly_points_lines <- sample.line(philly_crop, n = 39) ## equally place the number of farms along the coastline 
class(philly_points_lines)
plot(philly_points_lines)

philly_points <- st_as_sf(philly_points_lines)
mapview(philly_points)

## Now filter out the points that fall outside of 271
philly_points_final <- philly_points[1:271,]
mapview(philly_points_final)

phl_pts <- st_centroid(philly_points_final)

phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
names(farms_phl) <- c("lon", "lat")

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(area_ha = 13.35)

## visualize it 
farms_phl <-  st_as_sf(farms_phl, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_phl)

## write to farms folder 
write_csv(farms_phl_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_phl.csv"))

```

# Saudi Arabia
http://www.naqua.com.sa/about-us.php
"Its shrimp hatchery can produce 5.5 billion nauplii and 2.5 billion postlarvae a year, and its 4,177 hectares of shrimp ponds along 65 kilometers of coastline are capable of producing *35,000* metric tons of shrimp a year, between 120 and 140 tons a day.  From harvest to processing takes less than four hours, and its plant can process up to 140 metric tons of shrimp a day." 
 - National aquaculture group: 16 shrimp farms (in one location): 7189 hectares (from google maps): 20.287253, 40.030864

https://www.alasmak.com.sa/en/about-us-en/index.html
 - Saudi Fisheries Company: *3000* tonnes per year: 17.806544, 41.897791: 206 hectares (taken from google maps)

Sources: 
National Aquaculture Group, n.d. [Accessed 11.12.20]. http://www.naqua.com.sa/about-us.php

Saudi Fish Company, n.d. [Accessed November 12, 2020]. https://www.alasmak.com.sa/en/about-us-en/index.html

```{r}
farms_sau <- data.frame(lat=c(20.287253, 17.806544),
                        lon=c(40.030864, 41.897791),
                        area_ha = c(7189, 206), 
                        prod = c(35000, 3000)) %>%
  mutate(iso3c = "SAU")

write_csv(farms_sau, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_sau.csv"))

## visualize it 
farms_sau <-  st_as_sf(farms_sau, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sau)
```

# Sri Lanka 
http://www.fao.org/fishery/countrysector/naso_sri-lanka/en#:~:text=The%20current%20shrimp%20aquaculture%20industry,of%20around%203%20000%20ha.
"The current shrimp aquaculture industry in Sri Lanka is concentrated in the north western coastal belt **(Puttalam district)** covering a farm area of more than 4 500 ha with 70 hatcheries, of the total farm area the ponds themselves occupy an area of around 3 000 ha. There are a total of 1 344 farm establishments, of which 47.7 percent are considered to be establishments operating without proper licences (Siriwardena, 2001b). On the eastern coast in Batticaloa District, where shrimp farming in Sri Lanka first began in the late 1970s but was abandoned due to civil unrest, operations have recommenced in recent years. Over 60 small farms with an average farm area of between 1–2 ha were in operation at the end of 2002, with a total pond area of 155 ha."

 - Puttalam district : 1344 farms, 4500/1344 = 3.348214 hectares per farm
 - Batticalao district : 60 farms, 155/60 = 2.583333 hectares per farm

Source: 
National Aquaculture Sector Overview. Sri Lanka, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.

```{r}
districts <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Sri_Lanka/gadm36_LKA_1.shp"))
mapview(districts)

batticaloa_shp <- districts %>%
  dplyr::filter(NAME_1 == "Batticaloa")

mapview(batticaloa_shp)

puttalam_shp <- districts %>%
  dplyr::filter(NAME_1 == "Puttalam")
mapview(puttalam_shp)

## Start with Batticaloa
world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

world <- st_as_sf(world)

batticaloa_world_crs <- st_transform(batticaloa_shp, crs(world))

batticaloa_world_crop <- st_crop(world, batticaloa_world_crs) ## crop to batticaloa extent
plot(batticaloa_world_crop)
mapview(batticaloa_world_crop)

batticaloa_crop <- as(batticaloa_world_crop, "Spatial")
plot(batticaloa_crop)
mapview(batticaloa_crop)

batticaloa_points_lines <- sample.line(batticaloa_crop, n = 60) ## equally place the number of farms along the coastline 
class(batticaloa_points_lines)
plot(batticaloa_points_lines)

batticaloa_points <- st_as_sf(batticaloa_points_lines)
mapview(batticaloa_points)

bat_lka_pts <- st_centroid(batticaloa_points)

bat_lka_pts_latlon <- st_transform(bat_lka_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_bat_lka <- data.frame(do.call(rbind, st_geometry(bat_lka_pts_latlon)))
names(farms_bat_lka) <- c("lon", "lat")

farms_bat_lka_final <- farms_bat_lka %>%
  mutate(area_ha = 2.583333)

## visualize it 
farms_bat_lka <-  st_as_sf(farms_bat_lka, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bat_lka)

## Now do puttalam
world <- ne_coastline(scale = 50) #world map with 50m resolution
plot(world)

world <- st_as_sf(world)

puttalam_world_crs <- st_transform(puttalam_shp, crs(world))

puttalam_world_crop <- st_crop(world, puttalam_world_crs) ## crop to puttalam extent
plot(puttalam_world_crop)
mapview(puttalam_world_crop)

puttalam_crop <- as(puttalam_world_crop, "Spatial")
plot(puttalam_crop)
mapview(puttalam_crop)

puttalam_points_lines <- sample.line(puttalam_crop, n = 1344) ## equally place the number of farms along the coastline 
class(puttalam_points_lines)
plot(puttalam_points_lines)

puttalam_points <- st_as_sf(puttalam_points_lines)
mapview(puttalam_points)

put_lka_pts <- st_centroid(puttalam_points)

put_lka_pts_latlon <- st_transform(put_lka_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_put_lka <- data.frame(do.call(rbind, st_geometry(put_lka_pts_latlon)))
names(farms_put_lka) <- c("lon", "lat")

farms_put_lka_final <- farms_put_lka %>%
  mutate(area_ha = 3.348214)

## visualize it 
farms_put_lka <-  st_as_sf(farms_put_lka, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_put_lka)

## combine put and bat

farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
  dplyr::mutate(iso3c = "LKA")

## write to farms folder 
write_csv(farms_all_lka, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_lka.csv"))

```

# Taiwan
https://www.taipeitimes.com/News/taiwan/archives/2020/06/19/2003738488
 - There are definitely a lot of farms

 - It is unclear how many farms are in Taiwan. I will randomly place the farms along the coast.

Source: 
NA

```{r, evalute = F}

gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")

 TWN_shp <- gadm %>%
  filter(GID_0 == "TWN") %>%
  st_transform(., food_crs) %>%
  mutate(Region = 1)
 mapview(TWN_shp)

st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")

twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")

plot(fake_raster)
plot(twn_reg_ras)

writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")

twn_spatial <- as(TWN_shp, "Spatial")

twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)

plot(twn_coast)
cellStats(twn_coast, "sum") #464.63

# filter to include >0 <1, o.w. NA

twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
  dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
  mutate(iso3c = "TWN") %>%
  dplyr::select(lon=x, lat=y, iso3c)

farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)

write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))

twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_twn)
```

# United States of America

https://www.seafoodwatch.org/-/m/sfw/pdf/reports/s/mba_seafoodwatch_usfarmedshrimpreport.pdf
 - "Most commercial shrimp aquaculture production in the US is located in Texas, which has seven commercial farms. There is less production and fewer shrimp farms in Alabama (3), Florida (3), Hawaii (2), Nevada (1), Michigan (1), Indiana (1), Iowa (1), Maryland (1), and Massachusetts (1)."
 - We will only map for Alabama, Texas, Hawaii, and Florida. The rest are inland/indoor farms.

Texas: 
http://www.texasaquaculture.org/TxShrimpFms.html
 - They have texas locations listed here. 
    - Bowers Shrimp Farm: 28.709786, -96.209726: 159.4461 hectares of ponds 
    - St. Martins Seafood: 28.731171, -96.203732: 80 hectares of ponds
    - Austwell Aqua Farm: 28.369096, -96.813910: 40 hectares
    - Southern Star Inc: 26.323330, -97.452599: 445 hectares
    - Harlinger Shrimp Farms: 26.149413, -97.322755: 182 hectares

Source:
Texas Aquaculture Association, 2018. [Accessed November 18, 2020] http://www.texasaquaculture.org/TxShrimpFms.html

Alabama: 
 - 3 locations according to SFW. From what I can tell, one of them is inland. And can only find 1 other.... 
 - Coordinates taken from google maps: 
    - Graham fisheries inc: 30.403144, -88.254304

Source: 
NA

Hawaii: 
 - 2 locations according to SFW.. I can only find one
     - [Kauai Shrimp](https://www.kauaishrimp.com/en/about-us/): 21.957597, -159.669555: 104 hectares

Source: 
NA

Florida: https://www.shrimpnews.com/FreeReportsFolder/NewsReportsFolder/USAflFiveShrimpFarmsAndHatchery.html
 - 3 marine locations according to SFW
    - [Gulf American Shrimp](https://www.gulfamericanshrimp.com/about-the-farm): 29.859915, -85.287438: 22 hectares
    - American Mariculture LLC: 26.602097, -82.113475: 3 hectares
    - Shrimp Improvement Systems: 24.972378, -80.555590: 0.88 hectares

Source: 
NA

```{r}
farms_usa <- data.frame(lat=c(28.709786, 28.731171, 28.369096, 26.323330, 26.149413, 30.403144, 21.957597,  29.859915, 26.602097, 24.972378),
                        lon=c(-96.209726, -96.203732, -96.813910, -97.452599, -97.322755, -88.254304, -159.669555, -85.287438, -82.113475, -80.555590),
                        area_ha = c(159.4461, 80, 40, 445, 182, NA, 104, 22, 3, 0.88)) %>%
  mutate(iso3c = "USA")

write_csv(farms_usa, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_usa.csv"))

## visualize it 
farms_usa <-  st_as_sf(farms_usa, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_usa)
```

# Join cell count dataframes

```{r}
farm_files <- list.files(here::here("marine/shrimp/shrimp_farms/data/farm_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(all_farms, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon.csv"), row.names = FALSE)

```

### 2021-02-04 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
cleaned up scripts and updated file paths

---
title: "Location of Tuna farms"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script standardizes location of tuna farms to be lat/long point data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

fao_tuna_spp <- read_csv("marine/tuna/tuna_farms/data/fao_mariculture_tuna_taxa_production.csv") %>%
  dplyr::filter(year == 2017)
fao_tuna <- read_csv("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv") %>%
  dplyr::filter(year == 2017)

unique(fao_tuna$country)

# Need to map these 7 countries
# [1] "Australia" "Croatia"   "Japan"     "Malta"     "Mexico"    "Spain"     "Turkey"

```

# Raster

Standard raster used for this analysis

```{r}

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

Now we will map the remaining countries with marine tuna farms. Workflow will be as follows:

 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of tuna farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
 - Lastly, if there is no evidence of marine tuna farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e. what we've done for Russia for bivalves).

##  Europe - EMODNET: Spain, Malta
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production
https://www.emodnet-humanactivities.eu/view-data.php

Source:
EMODnet Human Activities: Finfish production, 2019. [Accessed December 8, 2020] 
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production

```{r}

## read in shapefile
eu <- st_read(file.path(path,"EMODnet_HA_Aquaculture_Marine_Finfish_20190104/EMODnet_HA_Aquaculture_Marine_Finfish_20190104.shp"))
mapview(eu)

unique(eu$COUNTRY)
# [1] "Spain"          "United Kingdom" "Greece"         "Finland"        "Norway"         "Ireland"        "Malta"          "Denmark"       
# [9] "Cyprus"

unique(eu$FARM_TYPE)

unique(eu$SPECIES_DE)

unique(eu$STATUS)

eu_spp <- eu %>%
  dplyr::filter(str_detect(SPECIES_DE, "Tuna|tuna"))

unique(eu_spp$COUNTRY)
# [1] "Spain" "Malta"

eu_na <- eu_spp %>%
  dplyr::filter(STATUS == "n.a.")
unique(eu_na$COUNTRY)

eu_active <- eu_spp %>%
  dplyr::filter(STATUS == "Active")

unique(eu_active$COUNTRY)

## we will use both "Active" and "n.a." as the status of the farms. I choose this because all of the denmark points are n.a. for salmon and bivalve, and they correspond with the HELCOM data that we used for other spp groups. This indicates to me that the farms denoted as "n.a." are probably actually active.

eu_active_na <- eu_spp %>%
  dplyr::filter(STATUS %in% c("Active", "n.a."))

unique(eu_active_na$COUNTRY)

# [1] "Spain"     "Malta"

## Now filter for countries that we want: Spain, Greece, Norway, Cyprus, Malta... the others are not included in FAO 2017
eu_fao_countries <- eu_active_na %>%
  dplyr::filter(COUNTRY %in% c("Spain", "Malta"))

unique(eu_fao_countries$COUNTRY)
mapview(eu_fao_countries)

eu_pts <- st_centroid(eu_fao_countries)

eu_pts_latlon <- st_transform(eu_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(COUNTRY, geometry)

eu_countries <- eu_pts_latlon %>%
  dplyr::select(COUNTRY)

farms_eu <- data.frame(do.call(rbind, st_geometry(eu_pts_latlon)))
names(farms_eu) <- c("lon", "lat")

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY)

 write_csv(farms_eu_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_ESP_MLT.csv"))

```

## Croatia, Turkey
http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/mediterranean-basin/en/

 - It says both Tuna and Finfish, but we'll assume Croatia and Turkey are tuna...

Source:
NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/

```{r}
## read in thailand shp file
med_file <- file.path(path, "FAO_NASO/NASO/Point/Mediterranean.kml")

med_aqua <- read_sf(med_file)

med_countries <- france_aqua %>%
  dplyr::mutate(country = sub("_.*", "", Name)) %>%
  dplyr::mutate(country = sub(" fishpen A", "", country))

unique(med_countries$country)

## We need to filter for just the appropriate species of finfish aquaculture, France, Israel

med_tuna <- med_countries %>%
  dplyr::filter(country %in% c("Croatia", "Turkey"))

mapview(med_tuna)

med_tuna_mol <- st_transform(med_tuna, crs = "+init=epsg:3035") # convert to equal area projection to find centroids.
med_pts <- st_centroid(med_tuna_mol)

med_pts_latlon <- st_transform(med_pts, crs = "+init=epsg:4326")

mapview(med_pts_latlon)

countries <- med_pts_latlon %>%
  dplyr::select(country)

farms_med <- data.frame(do.call(rbind, st_geometry(med_pts_latlon)))
names(farms_med) <- c("lon", "lat")
farms_med <- farms_med %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
  dplyr::select(-country, -geometry)

write_csv(farms_med, here("marine/tuna/tuna_farms/data/tuna_sites/farms_hrv_tur.csv"))

farms_med <-  st_as_sf(farms_med, coords = c("lon", "lat"),
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_med)
```

## Australia
https://www.pir.sa.gov.au/aquaculture/marine_aquaculture/species
"Southern Bluefin Tuna
The farming of Southern Bluefin Tuna (Thunnus maccoyi) generates the highest farm-gate sales in South Australia’s industry. Tuna farming is unique to South Australia. Its development in 1991 drew attention to the potential of South Australia’s aquaculture. All of Australia’s Southern Bluefin Tuna are farmed in waters off Port Lincoln.

Southern Bluefin Tuna are mostly found in the world’s southern oceans."

This shows leases: https://www.aginsight.sa.gov.au/?Bookmark=Ox473rlD

Source: https://www.pir.sa.gov.au/aquaculture/aquaculture_public_register

 - To download the appropriate data, go here: https://www.aginsight.sa.gov.au/?Bookmark=Ox473rlD. Filter for the appropriate layers, i.e. Tuna leases. Click "Select focus", and draw a circle (or square) around your area of interest. You will then be prompted to download an excel or csv file which will contain the lease holder information, and a url to the lease. 
 - We will scrape the coordinates from each lease document url that is shown in the download from the aquaculture public register to obtain the lat lon points needed.

Source:  
Aquaculture public register - Government of South Australia, 2017. [Accessed November 14, 2020] https://www.pir.sa.gov.au/aquaculture/aquaculture_public_register

```{r}
south_au <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Australia/south_au_leases.csv"))

tuna_leases <- south_au %>%
  dplyr::filter(str_detect(`Registration Category`, "Tuna|Miscellaneous"))

## now we need to look at each link and make sure they are tuna (because some of them are listed as "Miscellaneous")

unique(tuna_leases$`Lease Document`)

# row 1 : tuna
# row 2 : tuna
# row 3 : tuna
# row 4 : tuna
# row 5 : tuna
# row 6 : doesn't indicate tuna, filter out 
# row 7 : tuna
# row 8 : tuna
# row 9 : tuna
# row 10: tuna
# row 11: tuna
# row 12: tuna
# row 13: doesn't indicate tuna, filter out 
# row 14: tuna
# row 15: tuna
# row 16: tuna
# row 17: tuna

## Filter out rows 6 and 13
tuna_leases_df <- tuna_leases[c(-6, -13), ]

tuna_links <- c(tuna_leases_df$`Lease Document`)

#install.packages("rvest")
library("rvest")

coords_list <- list()

for(i in seq_along(tuna_links)){

  # i = 2
# Read the webpage into R
webpage <- read_html(tuna_links[i])

# Parse the webpage for coords
coords <- html_nodes(webpage, "dd div")

# Extract the coords
coord_numbers <- html_text(coords)

coords_df <- as.data.frame(coord_numbers) %>%
  dplyr::filter(str_detect(coord_numbers, "°")) ## filter for coordinates

## Format to lat lon: decimal degrees. Right now they are in degrees mins secs 
lat_lon_df <- do.call("cbind", split(coords_df, rep(c(1, 2), length.out = nrow(coords_df)))) %>%
  dplyr::rename("lat" = "coord_numbers") %>%
  dplyr::rename("lon" = "coord_numbers")

## covert to appropriate coordinate system
lat_lon_df_clean <- data.frame(lapply(lat_lon_df, function(x) {
                gsub("[^0-9.]", " ", x)
             })) %>%
  separate(lat, into = c("lat_d", "lat_m", "lat_s"), sep = "  ") %>%
  separate(lon, into = c("lon_d", "lon_m", "lon_s"), sep = "  ") %>%
  mutate_each(funs(as.numeric)) %>%
  transmute(lat = lat_d + lat_m/60 + lat_s/60^2,
            lon = lon_d + lon_m/60 + lon_s/60^2)

coords_list[[i]] <- lat_lon_df_clean

}

## unlist the list to get our coordinates 
lat_lon_final <- coords_list %>%
    bind_rows() %>%
  mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
  mutate(iso3c = "AUS")
## now that we have coordinates, place them on a map and save

farms_aus_map <-  st_as_sf(lat_lon_final, coords = c("lon", "lat"),
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_aus_map)

write_csv(lat_lon_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_AUS.csv"))
```

## Japan
http://www.fao.org/fishery/countrysector/naso_japan/en
Currently 92 firms are operating the Atlantic bluefin tuna aquaculture, and the total number of aquaculture firms and cages are regulated by the government since 2012.

I'll place 92 farms along Japan's coast

Source:
FAO Fisheries & Aquaculture - National Aquaculture Sector Overview - Japan, 2017. National Aquaculture Sector Overview Fact Sheets.

```{r}
world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
plot(world)

japan <- ne_countries(scale = 10, country = "Japan", returnclass = "sf")

#info of our spatial vector object
japan
mapview(japan)
plot(japan)

world <- st_as_sf(world)

japan_world_crs <- st_transform(japan, crs(world))

japan_world_crop <- st_crop(world, japan_world_crs)

japan_world_crop <- japan_world_crop[-c(2,3,4), ]
plot(japan_world_crop)
mapview(japan_world_crop)

japan_crop <- as(japan_world_crop, "Spatial")

japan_points_lines <- sample.line(japan_crop, n = 92) ## equally place the number of farms along the coastline 
class(japan_points_lines)
plot(japan_points_lines)

japan_points <- st_as_sf(japan_points_lines)
mapview(japan_points)

## now prep dataframe for lat lon points
jpn_pts <- st_centroid(japan_points)

jpn_pts_latlon <- st_transform(jpn_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_jpn <- data.frame(do.call(rbind, st_geometry(jpn_pts_latlon)))
names(farms_jpn) <- c("lon", "lat")

farms_jpn_final <- farms_jpn %>%
  mutate(iso3c = "JPN")

## visualize it 
farms_jpn <-  st_as_sf(farms_jpn, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_jpn)

## write to farms folder 
write_csv(farms_jpn_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_jpn.csv"))
```

## Mexico 
https://www.gob.mx/inapesca/acciones-y-programas/atun-aleta-azul
Only located in Baja California and Baja California Sur

 - 8 commercial farms in Baja California
 - 3 commercial farms in Baja California Sur

 Seafood Watch:
 https://www.seafoodwatch.org/recommendation/tuna/tuna-pacific-bluefin-mexico-marine-net-pen?species=386

 "In Mexico, the tuna farming industry is primarily located 15 km north of Ensenada, Baja California, in Salsipuedes Bay, with some farms in Todos Los Santos Bay and others off the coast of Ensenada."

 "Mexico’s current National Aquaculture Charter indicates that 6 aquaculture companies were operating 13 net pens with a maximum capacity of 6,800 MT in 2011 (SAGARPA 2013), though personal communication with an industry expert indicates that the active companies have been consolidated into two."

**Based on this, I will place 13 farms in Salsipuedes Bay.**

Source:
Monterey Bay Aquarium Seafood Watch Report on Pacific Bluefin Tuna Farming in Mexico, 2016.

```{r}

farms_mex <- data.frame(lat = c(31.972882899404116, 31.96836856413186, 31.963417102445995, 31.95861101663323, 31.955698114940013, 31.952930772763118, 31.95030900327055, 31.945939221180044, 31.932974311561416, 31.929769220541903, 31.95016334721594, 31.959630510399904, 31.96764042474878),
                          lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183), 
                          iso3c = "MEX")

farms_mex_map <-  st_as_sf(farms_mex, coords = c("lon", "lat"),
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_mex_map)

write_csv(farms_mex, here("marine/tuna/tuna_farms/data/tuna_sites/farms_MEX.csv"))

```

# Join cell count dataframes

```{r}
farm_files <- list.files(here::here("marine/tuna/tuna_farms/data/tuna_sites"), full=TRUE)
all_farms = plyr::ldply(farm_files, read_csv)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

write.csv(all_farms, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"), row.names = FALSE)

```

### 2021-02-04 workflow/common.R

@@ -19,19 +19,14 @@ if (Sys.info()[['sysname']] != 'Linux' & !file.exists(dir_aurora)){
 raw   <- paste0(dir_aurora, "_raw_data/")
 prep  <- paste0(dir_aurora,"all_food_systems/dataprep/")
 layers <- paste0(dir_aurora,"all_food_systems/datalayers/")
-
-
-## Load .csv file of food regions and associated naming and numbering conventions
-food_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"), col_types = "cdc")
   
   
 ## Common functions+packages
 select <- dplyr::select
 summarise <- dplyr::summarise
 
-
-
-
+# make not in function 
+`%notin%` <- Negate(`%in%`) 
 
 
 

### 2021-02-04 workflow/common_spatial.R

@@ -19,7 +19,7 @@ food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90
 # loads the unique food regions and associated naming and numbering conventions commonly seen/used
     food_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))    
 
-    
 
-
+# make not in function 
+`%notin%` <- Negate(`%in%`) 
  

### 2021-02-08 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
finished salmon data quality metric

@@
 
+```{r}
+
+coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
+
+mapview(head(coast_raw))
+
+```
+
 # Global regions
@@
 ```
+
+For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0).
+
+Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+
+Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps)
+
+Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+
+Bad qualifications: Per province/state locations (i.e.
+placing a point randomly in each provice), no data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.
 
@@
 farms_chile <- farms_chile %>%
-  mutate(iso3c="CHL")
+  mutate(iso3c="CHL") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_nor <- sub_norway %>% 
-  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") # Counting duplicate liscense locations once
+  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") %>% # Counting duplicate liscense locations once
+  mutate(data_quality = 1.0)
 
@@
 farms_scotland <- farms_scotland %>%
-  mutate(iso3c="GBR")
+  mutate(iso3c = "GBR") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_all_fro <- farms_fro %>%
-  cbind(iso3c = fro_pts_latlon$iso3c)
+  cbind(iso3c = fro_pts_latlon$iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
   dplyr::select(lon, lat) %>%
-  mutate(iso3c="AUS")
+  mutate(iso3c="AUS") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_bc <- farms_bc %>%
-  mutate(iso3c="CAN")
+  mutate(iso3c="CAN") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_nb <- farms_nb %>%
-  mutate(iso3c="CAN")
+  mutate(iso3c="CAN") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_ns <- farms_ns %>%
-  mutate(iso3c="CAN")
+  mutate(iso3c="CAN") %>%
+  mutate(data_quality = 1.0)
 
@@
   mutate(iso3c = "CAN") %>%
-  dplyr::select(lon, lat, iso3c)
+  dplyr::select(lon, lat, iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
 
+ - this will receive a 0.667 (good quality), since I do not believe it is comprehensive, and is only a sample of points.
+
 ```{r}
@@
   mutate(iso3c = "USA") %>%
-  dplyr::select(lon, lat, iso3c)
+  dplyr::select(lon, lat, iso3c) %>%
+  mutate(data_quality = 0.667)
 
@@
 farms_us_ne <- farms_us_ne %>%
-  mutate(iso3c = "USA")
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_all_nzl <- farms_nzl %>%
-  cbind(iso3c = nzl_pts_latlon$iso3c)
+  cbind(iso3c = nzl_pts_latlon$iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_ire <- farms_ire %>%
-  mutate(iso3c="IRL")
+  mutate(iso3c="IRL") %>%
+  mutate(data_quality = 1.0)
 
@@
                     lat=c(69.4953)) %>%
-  mutate(iso3c = "RUS")
+  mutate(iso3c = "RUS") %>%
+  mutate(data_quality = 0.0)
 
@@
 farms_all_JPN <- farms_JPN %>%
-  cbind(iso3c = JPN_pts_latlon$iso3c)
+  cbind(iso3c = JPN_pts_latlon$iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
 Source: 
-HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM Map and Data Service, n.d. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
 farms_dk <- cbind(farms_dk, dk_subregions ) %>%
-  dplyr::select(lon, lat, iso3c, subregion = NAME)
+  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
+  mutate(data_quality = 1.0)
 
@@
                     lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
-  mutate(iso3c = "TUR")
+  mutate(iso3c = "TUR") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_fi <- cbind(farms_fi, fi_subregions ) %>%
-  dplyr::select(lon, lat, iso3c, subregion = NAME)
+  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
+  mutate(data_quality = 1.0)
 
@@
   dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
-  filter(!is.na(lat))
+  filter(!is.na(lat)) %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_all_ISL <- farms_ISL %>%
-  cbind(iso3c = ISL_pts_latlon$iso3c)
+  cbind(iso3c = ISL_pts_latlon$iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
 
-write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality)
+
+write.csv(all_farms_1, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), row.names = FALSE)
 

### 2021-02-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished marine bivalve data quality

@@
 
+For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0).
+
+Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+
+Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps)
+
+Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+Or Per province/state locations (i.e.
+placing a point randomly in each province) or sub regional location.
+
+Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.
+
 # Map data from ASC
@@
 farms_all_fin <- farms_all_fin %>%
-  cbind(iso3c = all_pts_latlon$iso3c)
+  cbind(iso3c = all_pts_latlon$iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
   dplyr::filter(!(status %in% c(NA, "Pending", "Restricted-Relay", "Not Available", "Conditional Closure", "Prohibited"))) %>%
-dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York")))
+dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York"))) ## filter out the states we already have
 
@@
 farms_us_aqua <- farms_us_aqua %>%
-  mutate(iso3c = "USA")
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 1.0)
 
@@
   mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
-  dplyr::select(lon, lat, iso3c, subregion = NAME)
+  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
+  mutate(data_quality = 1.0)
 
@@
   mutate(iso3c = "DNK") %>%
-  dplyr::select(lon, lat, iso3c)
+  dplyr::select(lon, lat, iso3c) %>%
+  mutate(data_quality = 1.0)
 
@@
 
-## Now filter for countries that we want: Ireland, Bulgaria, Italy, Norway, Netherlands, and Greece. UK and DNK are already accounted for in our other datatsets. 
+## Now filter for countries that we want: Ireland, Bulgaria, Italy, Norway, Netherlands, and Greece. UK and DNK are already accounted for in our other datasets. 
 eu_fao_countries <- eu_active_na %>%
@@
   )) %>%
-  dplyr::select(-COUNTRY)
+  dplyr::select(-COUNTRY) %>%
+  mutate(data_quality = 1.0)
 
@@
 ## Spain
+TODO: Figure out how to download exact locations
+
 https://servicio.pesca.mapama.es/acuivisor/
@@
                         lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
-  mutate(iso3c = "ESP")
+  mutate(iso3c = "ESP") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon = c(-2.0325974703629277, -2.0327040476242284, -2.0312731919583795, -2.057638560247779, -2.03533532472839)) %>%
-  mutate(iso3c = "JEY")
+  mutate(iso3c = "JEY") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_ggy_final <- farms_ggy %>%
-  mutate(iso3c = "GGY")
+  mutate(iso3c = "GGY") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_svn_final <- farms_svn %>%
-  mutate(iso3c = "SVN")
+  mutate(iso3c = "SVN") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_hrv_final <- farms_hrv %>%
-  mutate(iso3c = "HRV")
+  mutate(iso3c = "HRV") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon = c(-80.082047, -79.994291, -79.963228, -79.958924)) %>%
-  mutate(iso3c = "CUB")
+  mutate(iso3c = "CUB") %>%
+  mutate(data_quality = 0.667)
 
@@
 ## Taiwan
- - I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. We will allocate the cells equally along the coastline (like we did for shrimp).
+- I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. I will randomly place a point in the Qigu lagoon (see article). 
  - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/
@@
 
-gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
-
- TWN_shp <- gadm %>%
-  filter(GID_0 == "TWN") %>%
-  st_transform(., food_crs) %>%
-  mutate(Region = 1)
- mapview(TWN_shp)
-
-st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
-
-twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
-
-plot(fake_raster)
-plot(twn_reg_ras)
-
-writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-
-twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-
-twn_spatial <- as(TWN_shp, "Spatial")
-
-twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
-
-plot(twn_coast)
-cellStats(twn_coast, "sum") #464.63
-
-# filter to include >0 <1, o.w. NA
-
-twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
-  dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
+farms_twn <- data.frame(lat = c(23.12185817551473),
+                        lon = c(120.05482898155049)) %>%
   mutate(iso3c = "TWN") %>%
-  dplyr::select(lon=x, lat=y, iso3c)
-
-farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
+  mutate(data_quality = 0.0)
+
+write_csv(farms_twn, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))
+
+## visualize it 
+farms_twn <-  st_as_sf(farms_twn, coords = c("lon", "lat"), 
                  crs = crs(gadm_latlon), agr = "constant")
@@
 
-write_csv(twn_coast_df, here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
-
-twn <- read_csv(here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
-farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_twn)
+```
+
+OLD WAY: 
+```{r}
+
+# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
+# 
+#  TWN_shp <- gadm %>%
+#   filter(GID_0 == "TWN") %>%
+#   st_transform(., food_crs) %>%
+#   mutate(Region = 1)
+#  mapview(TWN_shp)
+# 
+# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
+# 
+# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
+# 
+# 
+# plot(fake_raster)
+# plot(twn_reg_ras)
+# 
+# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
+# 
+# 
+# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
+# 
+# twn_spatial <- as(TWN_shp, "Spatial")
+# 
+# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
+# 
+# plot(twn_coast)
+# cellStats(twn_coast, "sum") #464.63
+# 
+# # filter to include >0 <1, o.w. NA
+# 
+# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
+#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
+#   mutate(iso3c = "TWN") %>%
+#   dplyr::select(lon=x, lat=y, iso3c)
+# 
+# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
+#                  crs = crs(gadm_latlon), agr = "constant")
+# 
+# mapview(farms_twn)
+# 
+# 
+# write_csv(twn_coast_df, here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
+# 
+# 
+# twn <- read_csv(here::here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))
+# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
+#                  crs = crs(gadm_latlon), agr = "constant")
+# 
+# mapview(farms_twn)
 ```
@@
                         lon = c(-138.40992718639146, -136.38467411084235)) %>%
-  mutate(iso3c = "PYF")
+  mutate(iso3c = "PYF") %>%
+  mutate(data_quality = 1.0)
 
@@
 farms_ind_final <- farms_ind %>%
-  mutate(iso3c = "IND")
+  mutate(iso3c = "IND") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_tha <- farms_tha %>%
-  mutate(iso3c="THA")
+  mutate(iso3c = "THA") %>%
+  mutate(data_quality = 0.667)
 
@@
                         lon = c(99.69952320753342, 106.35924782378112, 108.0659620387556, 108.64496221771543, 112.61871244712762, 120.31326531641196, 123.52557614041675, 129.1920950239657, 137.4727448207172)) %>%
-  mutate(iso3c = "IDN")
+  mutate(iso3c = "IDN") %>%
+  mutate(data_quality = 0.667)
 
@@
                         lon = c(131.95698485517275)) %>%
-  mutate(iso3c = "RUS")
+  mutate(iso3c = "RUS") %>%
+  mutate(data_quality = 0.0)
 
@@
 farms_prk_final <- farms_prk %>%
-  mutate(iso3c = "PRK")
+  mutate(iso3c = "PRK") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_bra_final <- farms_bra %>%
-  mutate(iso3c = "BRA")
+  mutate(iso3c = "BRA") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_phl_final <- farms_phl %>%
-  mutate(iso3c = "PHL")
+  mutate(iso3c = "PHL") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon = c(100.73343376478226)) %>%
-  mutate(iso3c = "MYS")
+  mutate(iso3c = "MYS") %>%
+  mutate(data_quality = 0.0)
 
@@
                         lon = c(103.64594001534627)) %>%
-  mutate(iso3c = "KHM")
+  mutate(iso3c = "KHM") %>%
+  mutate(data_quality = 0.0)
 
@@
                         lon = c(113.98143449612208)) %>%
-  mutate(iso3c = "HKG")
+  mutate(iso3c = "HKG") %>%
+  mutate(data_quality = 0.667)
 
@@
 
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality)
+
 all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
@@
 
-write.csv(all_farms, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)
-
-```
+write.csv(all_farms_1, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv"))
+```

### 2021-02-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

@@
 For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
-
-Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
-
-Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps)
-
-Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+ - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+ - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
+ - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
 Or Per province/state locations (i.e.
 placing a point randomly in each province) or sub regional location.
-
-Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.
+ - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).
 

### 2021-02-09 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

@@
 If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
  - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
 what we've done for Russia for bivalves).
+
+For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
+ - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+ - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps) 
+ - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+Or Per province/state locations (i.e.
+placing a point randomly in each province) or sub regional location.
+ - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.
 
@@
                         lon = c(117.55582991782983)) %>%
-  mutate(iso3c = "IDN")
+  mutate(iso3c = "IDN") %>%
+  mutate(data_quality = 0.0)
 
@@
                         lon = c(121.95043909100868)) %>%
-  mutate(iso3c = "CHN")
+  mutate(iso3c = "CHN") %>%
+  mutate(data_quality = 0.0)
 
@@
 
-farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325919306644522),
-                        lon = c(89.49499697244659, 91.76441856678511)) %>%
-  mutate(iso3c = "BGD")
+farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325670145257305),
+                        lon = c(89.49499697244659, 91.76091935028879)) %>%
+  mutate(iso3c = "BGD") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon = c(94.76647475697742, 94.24290607527016)) %>%
-  mutate(iso3c = "MMR")
+  mutate(iso3c = "MMR") %>%
+  mutate(data_quality = 0.333)
 
@@
 
-farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055231),
-                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.789267),
+farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055819944690162),
+                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
                         prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
-  mutate(iso3c = "VNM")
+  mutate(iso3c = "VNM") %>%
+  mutate(data_quality = 0.333)
 
@@
   dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
-  mutate(iso3c = "PHL")
+  mutate(iso3c = "PHL") %>%
+  mutate(data_quality = 0.333)
 
@@
 
-write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
+write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv"), row.names = FALSE)
 
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality)
+
+write.csv(all_farms_1, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
 ```

### 2021-02-09 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

@@
 what we've done for Russia for bivalves).
+
+For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
+ - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+ - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
+ - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+Or Per province/state locations (i.e.
+placing a point randomly in each province) or sub regional location.
+ - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).
 
@@
 farms_ita <- farms_ita %>%
-  mutate(iso3c="ITA")
+  mutate(iso3c="ITA") %>%
+  mutate(data_quality = 0.667)
 
@@
   mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
-  dplyr::select(-country, -geometry)
+  dplyr::select(-country, -geometry) %>%
+  mutate(data_quality = 0.667)
 
@@
 farms_idn <- farms_idn %>%
-  mutate(iso3c = "IDN")
+  mutate(iso3c = "IDN") %>%
+  mutate(data_quality = 0.667)
 
@@
 farms_prt_final <- farms_prt %>%
-  mutate(iso3c = "PRT")
+  mutate(iso3c = "PRT") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon = c(50.1602963496454)) %>%
-  mutate(iso3c = "IRN")
+  mutate(iso3c = "IRN") %>%
+  mutate(data_quality = 0.0)
 
@@
                         lon = c(119.94149300994019)) %>%
-  mutate(iso3c = "CHN")
+  mutate(iso3c = "CHN") %>%
+  mutate(data_quality = 0.0)
 
@@
 
-farms_sau <- data.frame(lat = c(20.287253),
-                        lon = c(40.030864)) %>%
-  mutate(iso3c = "SAU")
+farms_sau <- data.frame(lat = c(20.27293672234808),
+                        lon = c(40.03614937279944)) %>%
+  mutate(iso3c = "SAU") %>%
+  mutate(data_quality = 0.667)
 
@@
                         lon = c(57.67022708374523)) %>%
-  mutate(iso3c = "MUS")
+  mutate(iso3c = "MUS") %>%
+  mutate(data_quality = 0.0)
 
@@
                         lon = c(56.340214330776234)) %>%
-  mutate(iso3c = "ARE")
+  mutate(iso3c = "ARE") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_tun_final <- farms_tun %>%
-  mutate(iso3c = "TUN")
+  mutate(iso3c = "TUN") %>%
+  mutate(data_quality = 0.333)
 
@@
 all_points_twn <- rbind(milkfish_points, grouper_points) %>%
-  dplyr::mutate(iso3c = "TWN")
+  dplyr::mutate(iso3c = "TWN") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon = c(-84.20910189917947)) %>%
-  mutate(iso3c = "CRI")
+  mutate(iso3c = "CRI") %>%
+  mutate(data_quality = 0.667)
 
@@
                         subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
-  mutate(iso3c = "EGY")
+  mutate(iso3c = "EGY") %>%
+  mutate(data_quality = 1.0)
 
@@
                         lon = c(79.13007737814245)) %>%
-  mutate(iso3c = "IND")
+  mutate(iso3c = "IND") %>%
+  mutate(data_quality = 0.667)
 
@@
 farms_sgp_final <- farms_sgp %>%
-  mutate(iso3c = "SGP")
+  mutate(iso3c = "SGP") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
-  mutate(iso3c = "MYS")
+  mutate(iso3c = "MYS") %>%
+  mutate(data_quality = 0.333)
 
@@
                         lon=c(90.40418040967)) %>%
-  mutate(iso3c = "BGD")
+  mutate(iso3c = "BGD") %>%
+  mutate(data_quality = 0.0)
 
@@
                         lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
-  mutate(iso3c = "KHM")
+  mutate(iso3c = "KHM") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_kor_final <- farms_kor %>%
-  mutate(iso3c = "KOR")
+  mutate(iso3c = "KOR") %>%
+  mutate(data_quality = 0.333)
 
@@
   separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
-  mutate(iso3c = "HKG")
+  mutate(iso3c = "HKG") %>%
+  mutate(data_quality = 1.0)
 
@@
 
-write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)
-
-```
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality)
+
+write.csv(all_farms_1, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon_data_quality.csv"), row.names = FALSE)
+
+```

### 2021-02-09 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

@@
 library(janitor)
+library(rnaturalearth)
+library(spatialEco)
 
@@
 Source: 
-Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
+Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
 https://gis.asc-aqua.org/arcgis_app/
@@
 ```{r}
-
+library(countrycode)
 # get iso3c codes
@@
  - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
+
+For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
+ - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+ - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates.
+ - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+Or Per province/state locations (i.e.
+placing a point randomly in each province) or sub regional location.
+ - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).
 
@@
                         area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
-  mutate(iso3c = "BRA")
+  mutate(iso3c = "BRA") %>%
+  mutate(data_quality = 0.333)
 
@@
                         area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
-  mutate(iso3c = "BRN")
+  mutate(iso3c = "BRN") %>%
+  mutate(data_quality = 0.667)
 
@@
 # Cambodia 
- - There is a table in here that has potential.
+ - There is a table in here.
 We will just place a point on the coast for each of these coastal places, and use the area noted in the paper later if needed.
@@
 ```{r}
-farms_khm <- data.frame(lat=c(10.559329, 10.449929, 11.740932, 10.743017),
-                        lon=c(104.213349, 104.404934, 102.898284, 103.653332),
+
+farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
+                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                         area_ha = c(1516, 459, 26762, 6388)) %>%
-  mutate(iso3c = "KHM")
+  mutate(iso3c = "KHM") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_cri_final <- farms_cri %>%
-  mutate(iso3c = "CRI")
+  mutate(iso3c = "CRI") %>%
+  mutate(data_quality = 0.333)
 
@@
                         area_ha = c(NA, NA)) %>%
-  mutate(iso3c = "CUB")
+  mutate(iso3c = "CUB") %>%
+  mutate(data_quality = 0.667)
 
@@
                         area_ha = c(8.2, 50)) %>%
-  mutate(iso3c = "SLV")
+  mutate(iso3c = "SLV") %>%
+  mutate(data_quality = 0.333)
 
@@
 farms_irn <- farms_irn %>%
-  mutate(iso3c="IRN")
+  mutate(iso3c="IRN") %>%
+  mutate(data_quality = 0.667)
 
@@
                         area_ha = c(NA)) %>%
-  mutate(iso3c = "JPN")
+  mutate(iso3c = "JPN") %>%
+  mutate(data_quality = 0.0)
 
@@
                         area_ha = c(672)) %>%
-  mutate(iso3c = "KOR")
-
-write_csv(farms_kor, here("aquaculture/marine/shrimp/shrimp_farms/data/farm_sites/farms_kor.csv"))
+  mutate(iso3c = "KOR") %>% 
+  mutate(data_quality = 0.0)
+
+write_csv(farms_kor, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_kor.csv"))
 
@@
                         area_ha =mys_area) %>%
-  mutate(iso3c = "MYS")
+  mutate(iso3c = "MYS") %>%
+  mutate(data_quality = 0.333)
 
@@
                         area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
-  mutate(iso3c = "MMR")
+  mutate(iso3c = "MMR") %>%
+  mutate(data_quality = 0.333)
 
@@
   mutate(iso3c = "PHL") %>%
-  mutate(area_ha = 13.35)
+  mutate(area_ha = 13.35) %>%
+  mutate(data_quality = 0.333)
 
@@
                         prod = c(35000, 3000)) %>%
-  mutate(iso3c = "SAU")
+  mutate(iso3c = "SAU") %>%
+  mutate(data_quality = 0.667)
 
@@
 farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
-  dplyr::mutate(iso3c = "LKA")
+  dplyr::mutate(iso3c = "LKA") %>%
+  mutate(data_quality = 0.333)
 
@@
 
- - It is unclear how many farms are in Taiwan. I will randomly place the farms along the coast.
+ - It is unclear how many farms are in Taiwan. I will randomly place a farm on the coast.
 
@@
 
+```{r}
+
+farms_twn <- data.frame(lat = c(22.33895226304863),
+                        lon = c(120.60403687783123)) %>%
+  mutate(iso3c = "TWN") %>%
+  mutate(data_quality = 0.0)
+
+write_csv(farms_twn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
+
+## visualize it 
+farms_twn <-  st_as_sf(farms_twn, coords = c("lon", "lat"), 
+                 crs = crs(gadm_latlon), agr = "constant")
+
+mapview(farms_twn)
+
+```
+
 ```{r, evalute = F}
 
-gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
-
- TWN_shp <- gadm %>%
-  filter(GID_0 == "TWN") %>%
-  st_transform(., food_crs) %>%
-  mutate(Region = 1)
- mapview(TWN_shp)
-
-st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
-
-twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
-
-plot(fake_raster)
-plot(twn_reg_ras)
-
-writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-
-twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-
-twn_spatial <- as(TWN_shp, "Spatial")
-
-twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
-
-plot(twn_coast)
-cellStats(twn_coast, "sum") #464.63
-
-# filter to include >0 <1, o.w. NA
-
-twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
-  dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
-  mutate(iso3c = "TWN") %>%
-  dplyr::select(lon=x, lat=y, iso3c)
-
-farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_twn)
-
-write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
-
-twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
-farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_twn)
+# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
+# 
+#  TWN_shp <- gadm %>%
+#   filter(GID_0 == "TWN") %>%
+#   st_transform(., food_crs) %>%
+#   mutate(Region = 1)
+#  mapview(TWN_shp)
+# 
+# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
+# 
+# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
+# 
+# 
+# plot(fake_raster)
+# plot(twn_reg_ras)
+# 
+# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
+# 
+# 
+# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
+# 
+# twn_spatial <- as(TWN_shp, "Spatial")
+# 
+# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
+# 
+# plot(twn_coast)
+# cellStats(twn_coast, "sum") #464.63
+# 
+# # filter to include >0 <1, o.w. NA
+# 
+# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
+#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
+#   mutate(iso3c = "TWN") %>%
+#   dplyr::select(lon=x, lat=y, iso3c)
+# 
+# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
+#                  crs = crs(gadm_latlon), agr = "constant")
+# 
+# mapview(farms_twn)
+# 
+# 
+# write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
+# 
+# 
+# twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
+# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
+#                  crs = crs(gadm_latlon), agr = "constant")
+# 
+# mapview(farms_twn)
 ```
@@
                         area_ha = c(159.4461, 80, 40, 445, 182, NA, 104, 22, 3, 0.88)) %>%
-  mutate(iso3c = "USA")
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 0.667)
 
@@
 
-write.csv(all_farms, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon.csv"), row.names = FALSE)
-
-```
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality)
+
+write.csv(all_farms_1, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon.csv"), row.names = FALSE)
+write.csv(all_farms, here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon_data_quality.csv"), row.names = FALSE)
+
+```

### 2021-02-09 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
finished adding data quality markers to all species groups. Now I need to summarize

@@
 
-med_countries <- france_aqua %>%
+med_countries <- med_aqua %>%
   dplyr::mutate(country = sub("_.*", "", Name)) %>%
@@
 
-## We need to filter for just the appropriate species of finfish aquaculture, France, Israel
+## We need to filter for just the appropriate countries (that we don't already have): Croatia, Turkey
 
@@
 mapview(med_tuna)
+mapview(med_aqua)
 
@@
   mutate(iso3c = ifelse(country == "Croatia", "HRV", "TUR")) %>%
-  dplyr::select(-country, -geometry)
+  dplyr::select(-country, -geometry) %>%
+  mutate(data_quality = 0.667)
 
@@
 ```{r}
-south_au <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Australia/south_au_leases.csv"))
+south_au <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Australia/tuna/south_au_leases.csv"))
 
@@
   mutate(lat = -lat) %>% ## change lat to have a negative in front of it (because it S)
-  mutate(iso3c = "AUS")
+  mutate(iso3c = "AUS") %>%
+  mutate(data_quality = 1.0)
 ## now that we have coordinates, place them on a map and save
@@
 farms_jpn_final <- farms_jpn %>%
-  mutate(iso3c = "JPN")
+  mutate(iso3c = "JPN") %>%
+  mutate(data_quality = 0.333)
 
@@
                           lon = c(-116.81987407899483, -116.8094027351974, -116.80339458711688, -116.7956698252991, -116.79343822744065, -116.79000499996607, -116.78777340210759, -116.78193691540082, -116.77575710594658, -116.77180889435084, -116.77060726473474, -116.78262356089573, -116.79395321156183),
-                          iso3c = "MEX")
+                          iso3c = "MEX") %>%
+  mutate(data_quality = 0.667)
 
@@
 
-write.csv(all_farms, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"), row.names = FALSE)
+write.csv(all_farms_1, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon_data_quality.csv"), row.names = FALSE)
 

### 2021-02-10 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
made a script to explore the new data quality flags, and posted an issue about it.

@@
 # [41] "United States of America" "Viet Nam"
+
+coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
+mapview(coast_raw)
 ```
@@
 # gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
+# plot(gadm)
 # 

### 2021-02-10 marine/explore_spatial_allocation.Rmd
made a script to explore the new data quality flags, and posted an issue about it.

---
title: "Explore spatial allocation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

Read in and summarise all data quality farm data 
```{r}
bivalves <- read_csv(here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "bivalve") %>%
  dplyr::select(-X1, -subregion)

shrimp <- read_csv(here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "shrimp") %>%
  dplyr::select(-area_ha, -prod)

marine_fish <- read_csv(here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "marine_fish_general") %>%
  dplyr::select(-rgn_production, -subrgn_name)

salmon <- read_csv(here::here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv")) %>%
  mutate(group = "salmon") %>%
  dplyr::select(-subregion)

crustaceans <- read_csv(here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "crustaceans") %>%
  dplyr::select(-prod, -sub_rgn)

tuna <- read_csv(here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "tuna")

all_farms <- rbind(shrimp, bivalves, marine_fish, salmon, crustaceans, tuna)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(avg_quality = mean(data_quality)) %>%
  ungroup()

## n_farms shows us the number of points that will need spatial allocation within each country according to our new rules (any of the rows that score 0.333 in the data quality column)

n_countries <- n_farms %>%
  group_by(data_quality, group) %>%
  summarise(n_countries = n()) %>%
  ungroup() %>%
  group_by(group) %>%
  mutate(total_countries = sum(n_countries)) %>%
  ungroup() %>%
  mutate(percent = n_countries/total_countries)

## n_countries shows us the number of countries that will need spatial allocation within each species group according to our new rules (any of the rows that score 0.333 in the data quality column)

n_countries_allocated <- n_countries %>%
  dplyr::filter(data_quality == 0.333)
sum(n_countries_allocated$n_countries)
## 31 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)

n_countries_no_data <- n_countries %>%
  dplyr::filter(data_quality == 0.0)
sum(n_countries_no_data$n_countries) # 14
## 14 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)

sum(n_countries_allocated$n_countries)

## these were the rules for the data quality column: 
# For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
#  - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
#  - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
#  - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations. Or Per province/state locations (i.e. placing a point randomly in each province or sub regional location). 
#  - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number). 
```

### 2021-02-10 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished up making sure no bivalve points fall on land

@@
 coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
-mapview(coast_raw)
+# mapview(coast_raw)
 ```
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
-plot(world)
-
+## read in country shapefile
 Guernsey <- ne_countries(scale = 10, country = "Guernsey", returnclass = "sf")
@@
 #info of our spatial vector object
-Guernsey
 mapview(Guernsey)
@@
 
-world <- st_as_sf(world)
-
-Guernsey_world_crs <- st_transform(Guernsey, crs(world))
-
-Guernsey_world_crop <- st_crop(world, Guernsey_world_crs) %>%
-  dplyr::filter(scalerank == 5) ## filter for the appropriate island
+## transform to same crs at the coast file so we can crop
+Guernsey_world_crs <- st_transform(Guernsey, crs(coast_raw))
+
+# crop the to the coast file, and select the main island 
+Guernsey_world_crop <- st_crop(coast_raw, Guernsey_world_crs) %>%
+  dplyr::filter(FID %in% c(220920, 220921, 220922)) %>% ## filter for the appropriate island
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
+  ungroup()
+
 plot(Guernsey_world_crop)
 mapview(Guernsey_world_crop)
-
-Guernsey_crop <- as(Guernsey_world_crop, "Spatial")
+class(Guernsey_world_crop)
+crs(Guernsey_world_crop)
+
+g_meters <- st_transform(Guernsey_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(g_meters)
+
+buff <- st_buffer(g_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+plot(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+buffer_outline <- linestring[1,]  ## grab the outline row 
+mapview(buffer_outline)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(buffer_outline, crs = crs(Guernsey_world_crop))
+
+## make a spatiallinesdataframe so we can use sample.line
+Guernsey_crop <- as(buffer_outline_fixed, "Spatial")
+class(Guernsey_crop)
+mapview(Guernsey_crop)
 
@@
 Guernsey_points <- st_as_sf(Guernsey_points_lines)
-mapview(Guernsey_points)
+mapview(Guernsey_points, color = "red") + mapview(Guernsey_world_crop)
+
+st_distance(Guernsey_points, Guernsey_world_crop)
+# Units: [m]
+#          [,1]
+# [1,] 992.6726
+# [2,] 992.6273
+# [3,] 992.6395
+# [4,] 992.3816
+# [5,] 992.3755
+# [6,] 992.7368
+# [7,] 992.6771
+## close enough to 1 km
 
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 10) #world map with 10m resolution
-plot(world)
+# world <- rnaturalearth::ne_coastline(scale = 10) #world map with 10m resolution
+# plot(world)
 
@@
 #info of our spatial vector object
-slovenia
 mapview(slovenia)
@@
 
-slovenia_world_crs <- st_transform(slovenia, crs(world))
-
-slovenia_world_crop <- st_crop(world, slovenia_world_crs) ## crop to slovenia extent
+slovenia_world_crs <- st_transform(slovenia, crs(coast_raw))
+
+slovenia_world_crop <- st_crop(coast_raw, slovenia_world_crs) %>% ## crop to slovenia extent
+  filter(FID %in% c(46261, 46262)) %>%
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
+  ungroup()
+
 plot(slovenia_world_crop)
@@
 
-slovenia_crop <- as(slovenia_world_crop, "Spatial")
-plot(slovenia_crop)
+s_meters <- st_transform(slovenia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(s_meters)
+
+buff <- st_buffer(s_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+plot(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(slovenia_world_crop))
+
+linestring_fix <- st_difference(buffer_outline_fixed, slovenia) ## now grab only the outline 
+mapview(linestring_fix)
+
+## make a spatiallinesdataframe so we can use sample.line
+slovenia_crop <- as(linestring_fix, "Spatial")
+class(slovenia_crop)
 mapview(slovenia_crop)
 
-slovenia_points_lines <- sample.line(slovenia_crop, n = 86) ## equally place the number of farms along the coastline 
+slovenia_points_lines <- sample.line(slovenia_crop, n = 41) ## equally place the number of farms along the coastline 
 class(slovenia_points_lines)
@@
 
-slovenia_points <- st_as_sf(slovenia_points_lines)
+slovenia_points <- st_as_sf(slovenia_points_lines) %>%
+  mutate(new_id = 1:41)
 mapview(slovenia_points)
@@
 ## Now filter out the points that fall outside of Slovenia
-slovenia_points_final <- slovenia_points[12:31,]
+slovenia_points_final <- slovenia_points[2:21,]
 mapview(slovenia_points_final)
+
+mean(st_distance(slovenia_points_final, slovenia_world_crop))
+# 998.6394 [m]
+## close enough to 1 km
 
@@
 
-croatia <- ne_countries(scale = 110, country = "Croatia", returnclass = "sf")
+croatia <- ne_countries(scale = 10, country = "Croatia", returnclass = "sf")
 
 #info of our spatial vector object
-croatia
 mapview(croatia)
@@
 
-croatia_world_crop <- st_crop(world, croatia_world_crs) ## crop to croatia extent
-plot(croatia_world_crop)
+croatia_world_crop <- st_crop(world, croatia_world_crs)
+
+croatia_world_crop <- st_intersection(croatia_world_crop, croatia)
 mapview(croatia_world_crop)
-
-croatia_crop <- as(croatia_world_crop, "Spatial")
+# %>% ## crop to croatia extent
+#   filter(!(FID %in% c(46278:46281, 643461:643463, 156618, 46260:46269, 46178:46182, 46177, 206670:206671))) %>%
+#   mutate(new_id = 1) %>%
+#   group_by(new_id) %>%
+#   summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
+#   ungroup()
+# mapview(croatia_world_crop)
+
+c_meters <- st_transform(croatia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(c_meters)
+
+buff <- st_buffer(c_meters, dist = 40000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+plot(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(croatia_world_crop))
+
+linestring_fix <- st_difference(buffer_outline_fixed, croatia) ## now grab only the outline 
+mapview(linestring_fix)
+
+croatia_crop <- as(linestring_fix, "Spatial")
 plot(croatia_crop)
@@
 
-croatia_points_lines <- sample.line(croatia_crop, n = 340) ## equally place the number of farms along the coastline 
+croatia_points_lines <- sample.line(croatia_crop, n = 640) ## equally place the number of farms along the coastline 
 class(croatia_points_lines)
@@
 
-croatia_points <- st_as_sf(croatia_points_lines)
+croatia_points <- st_as_sf(croatia_points_lines) %>%
+  mutate(new_id = 1:640)
 mapview(croatia_points)
@@
 ## Now filter out the points that fall outside of croatia: rows 57-70
-croatia_points_final <- croatia_points[2:267,]
+croatia_points_final <- croatia_points %>%
+  dplyr::filter(new_id %in% c(2:24, 395:640)) %>%
+  dplyr::filter(!(new_id %in% c(419, 533, 561)))
 mapview(croatia_points_final)
+
+mean(st_distance(croatia_points_final, croatia_world_crop))
 
@@
 ```{r}
-world <- ne_coastline(scale = 10) #world map with 10m resolution
-plot(world)
+# world <- ne_coastline(scale = 10) #world map with 10m resolution
+# plot(world)
 
@@
 #info of our spatial vector object
-kerala_state
 mapview(kerala_state)
@@
 
-world <- st_as_sf(world)
-
-kerala_state_world_crs <- st_transform(kerala_state, crs(world))
-
-kerala_state_world_crop <- st_crop(world, kerala_state_world_crs) ## crop to kerala extent
-plot(kerala_state_world_crop)
+# world <- st_as_sf(world)
+
+kerala_state_world_crs <- st_transform(kerala_state, crs(coast_raw))
+
+kerala_state_world_crop <- st_crop(coast_raw, kerala_state_world_crs) %>% ## crop to kerala extent
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
+  ungroup()
 mapview(kerala_state_world_crop)
 
-kerala_state_crop <- as(kerala_state_world_crop, "Spatial")
+k_meters <- st_transform(kerala_state_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(k_meters)
+
+buff <- st_buffer(k_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+plot(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(kerala_state_world_crop))
+
+india <- ne_countries(scale = 10, country = "India", returnclass = "sf")
+mapview(india)
+
+linestring_fix <- st_difference(buffer_outline_fixed, india) ## now grab only the outline 
+mapview(linestring_fix)
+mapview(kerala_state_world_crop)
+mapview(kerala_state)
+
+kerala_state_crop <- as(linestring_fix, "Spatial")
 plot(kerala_state_crop)
@@
 
-kerala_state_points_lines <- sample.line(kerala_state_crop, n = 250) ## equally place the number of farms along the coastline 
+kerala_state_points_lines <- sample.line(kerala_state_crop, n = 280) ## equally place the number of farms along the coastline 
 class(kerala_state_points_lines)
@@
 
-kerala_state_points <- st_as_sf(kerala_state_points_lines)
+kerala_state_points <- st_as_sf(kerala_state_points_lines) %>%
+  mutate(new_id = 1:280) 
 mapview(kerala_state_points)
 
-## Now filter out the points that fall outside of kerala_state: rows 57-70
-# kerala_state_points_final <- kerala_state_points[c(1:34,42:67), ]
-# mapview(kerala_state_points_final)
+# Now filter out the points that fall outside of kerala_state: rows 57-70
+kerala_state_points_final <- kerala_state_points %>%
+  filter(new_id %in% c(31:280))
+mapview(kerala_state_points_final)
+
+mean(st_distance(kerala_state_points_final, kerala_state_world_crop))
 
 ## get lat lon
-ind_pts <- st_centroid(kerala_state_points)
+ind_pts <- st_centroid(kerala_state_points_final)
 
@@
 ```{r}
-world <- ne_coastline(scale = 110) #world map with 110m resolution
-plot(world)
+# world <- ne_coastline(scale = 110) #world map with 110m resolution
+# plot(world)
 
@@
 #info of our spatial vector object
-north_korea
 mapview(north_korea)
@@
 
-world <- st_as_sf(world)
-
-north_korea_world_crs <- st_transform(north_korea, crs(world))
-
-north_korea_world_crop <- st_crop(world, north_korea_world_crs) ## crop to north korea extent
-plot(north_korea_world_crop)
+# world <- st_as_sf(world)
+
+north_korea_world_crs <- st_transform(north_korea, crs(coast_raw))
+
+north_korea_world_crop <- st_crop(coast_raw, north_korea_world_crs) %>% ## crop to north korea extent
+  dplyr::filter(!(FID %in% c(44790, 135067, 44788:44789, 135092, 135103, 87219, 44955))) %>%
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
+
 mapview(north_korea_world_crop)
 
-north_korea_crop <- as(north_korea_world_crop, "Spatial")
+nk_meters <- st_transform(north_korea_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(nk_meters)
+
+buff <- st_buffer(nk_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+plot(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(north_korea_world_crop))
+
+linestring_fix <- st_difference(buffer_outline_fixed, north_korea) ## now grab only the outline 
+mapview(linestring_fix)
+
+north_korea_crop <- as(linestring_fix, "Spatial")
 plot(north_korea_crop)
@@
 
-north_korea_points_lines <- sample.line(north_korea_crop, n = 67) ## equally place the number of farms along the coastline 
+north_korea_points_lines <- sample.line(north_korea_crop, n = 85) ## equally place the number of farms along the coastline 
 class(north_korea_points_lines)
@@
 
-north_korea_points <- st_as_sf(north_korea_points_lines)
+north_korea_points <- st_as_sf(north_korea_points_lines) %>%
+  mutate(new_id = 1:85)
 mapview(north_korea_points)
@@
 ## Now filter out the points that fall outside of north_korea: rows 57-70
-north_korea_points_final <- north_korea_points[c(1:34,42:67), ]
+north_korea_points_final <- north_korea_points %>%
+  filter(new_id %in% c(1:32, 46:47, 55:80 ))
 mapview(north_korea_points_final)
@@
 
-world <- ne_coastline(scale = 110) #world map with 110m resolution
-plot(world)
-
-#info of our spatial vector object
-sta_catarina
-mapview(sta_catarina)
-plot(sta_catarina)
-
-world <- st_as_sf(world)
-
-sta_catarina_world_crs <- st_transform(sta_catarina, crs(world))
-
-sta_catarina_world_crop <- st_crop(world, sta_catarina_world_crs) ## crop to santa catarina extent
+# world <- ne_coastline(scale = 110) #world map with 110m resolution
+# plot(world)
+
+# world <- st_as_sf(world)
+
+sta_catarina_world_crs <- st_transform(sta_catarina, crs(coast_raw))
+
+sta_catarina_world_crop <- st_crop(coast_raw, sta_catarina_world_crs) %>% ## crop to santa catarina extent
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
+
+mapview(sta_catarina_world_crop)
+
+sc_meters <- st_transform(sta_catarina_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(sc_meters)
+
+buff <- st_buffer(sc_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+plot(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+linestring <- st_cast(linestring, "LINESTRING")
+
+brazil <- ne_countries(scale = 10, country = "Brazil", returnclass = "sf")
+mapview(brazil)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(brazil))
+
+linestring_fix <- st_difference(buffer_outline_fixed, brazil) ## now grab only the outline 
+mapview(linestring_fix)
 plot(sta_catarina_world_crop)
@@
 
-sta_catarina_crop <- as(sta_catarina_world_crop, "Spatial")
+sta_catarina_crop <- as(linestring_fix, "Spatial")
 plot(sta_catarina_crop)
@@
 
-sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 27) ## equally place the number of farms along the coastline 
+sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 4) ## equally place the number of farms along the coastline 
 class(sta_catarina_points_lines)
@@
 
-sta_catarina_points <- st_as_sf(sta_catarina_points_lines)
+sta_catarina_points <- st_as_sf(sta_catarina_points_lines) %>%
+  mutate(new_id = 1:28) %>%
+  filter(new_id != 12)
 mapview(sta_catarina_points)
@@
 
-world <- ne_coastline(scale = 50) #world map with 50m resolution
-plot(world)
+# world <- ne_coastline(scale = 50) #world map with 50m resolution
+# plot(world)
 
@@
 
-world <- st_as_sf(world)
-
-capiz_world_crs <- st_transform(capiz, crs(world))
-
-capiz_world_crop <- st_crop(world, capiz_world_crs) ## crop to extent
-plot(capiz_world_crop)
+# world <- st_as_sf(world)
+
+capiz_world_crs <- st_transform(capiz, crs(coast_raw))
+
+capiz_world_crop <- st_crop(coast_raw, capiz_world_crs) %>% ## crop to extent
+  dplyr::filter(!(FID %in% c(443449, 439815, 443448, 439801))) %>%
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
+
 mapview(capiz_world_crop)
 
-capiz_crop <- as(capiz_world_crop, "Spatial")
+cp_meters <- st_transform(capiz_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(cp_meters)
+
+buff <- st_buffer(cp_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+linestring <- st_cast(linestring, "LINESTRING")
+
+philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
+mapview(philippines)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))
+
+linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
+mapview(linestring_fix)
+
+capiz_crop <- as(linestring_fix, "Spatial")
 plot(capiz_crop)
@@
 
-capiz_points_lines <- sample.line(capiz_crop, n = 300) ## equally place the number of farms along the coastline 
+capiz_points_lines <- sample.line(capiz_crop, n = 151) ## equally place the number of farms along the coastline 
 class(capiz_points_lines)
@@
 
-capiz_points <- st_as_sf(capiz_points_lines)
+capiz_points <- st_as_sf(capiz_points_lines) %>%
+  mutate(new_id = 1:302) %>%
+  filter(!(new_id %in% c(150, 146))) %>%
+  dplyr::select(-new_id)
 mapview(capiz_points)
-
-world <- ne_coastline(scale = 110) #world map with 110m resolution
-plot(world)
 
@@
 mapview(negros)
-plot(negros)
-
-world <- st_as_sf(world)
-
-negros_world_crs <- st_transform(negros, crs(world))
-
-negros_world_crop <- st_crop(world, negros_world_crs)
-
-negros_world_crop <- head(negros_world_crop, 1)
-plot(negros_world_crop)
+
+negros_world_crs <- st_transform(negros, crs(coast_raw))
+
+negros_world_crop <- st_crop(coast_raw, negros_world_crs) %>%
+  filter(FID %in% c(224916:224917, 224908:224912)) %>%
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
+
 mapview(negros_world_crop)
 
-negros_crop <- as(negros_world_crop, "Spatial")
+n_meters <- st_transform(negros_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(n_meters)
+
+buff <- st_buffer(n_meters, dist = 5000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+linestring <- st_cast(linestring, "LINESTRING")
+
+philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
+mapview(philippines)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))
+
+linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
+mapview(linestring_fix)
+
+negros_crop <- as(linestring_fix, "Spatial")
 plot(negros_crop)
@@
 mapview(negros_points)
-
-world <- ne_coastline(scale = 110) #world map with 50m resolution
-plot(world)
 
@@
 mapview(samar)
-plot(samar)
-
-world <- st_as_sf(world)
-
-samar_world_crs <- st_transform(samar, crs(world))
-
-samar_world_crop <- st_crop(world, samar_world_crs)
-
-samar_world_crop <- head(samar_world_crop, 1)
-plot(samar_world_crop)
+
+samar_world_crs <- st_transform(samar, crs(coast_raw))
+
+# marabut to veriato
+
+samar_world_crop <- st_crop(coast_raw, samar_world_crs) %>%
+  filter(FID %in% c(222688:222691, 222671:222673)) %>%
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
+
 mapview(samar_world_crop)
 
-samar_crop <- as(samar_world_crop, "Spatial")
+sm_meters <- st_transform(samar_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(sm_meters)
+
+buff <- st_buffer(sm_meters, dist = 3000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+linestring <- st_cast(linestring, "LINESTRING")
+
+philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
+mapview(philippines)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))
+
+linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
+mapview(linestring_fix)
+
+samar_crop <- as(linestring_fix, "Spatial")
 plot(samar_crop)
@@
 
-samar_points_lines <- sample.line(samar_crop, n = 250) ## equally place the number of farms along the coastline 
+samar_points_lines <- sample.line(samar_crop, n = 283) ## equally place the number of farms along the coastline 
 class(samar_points_lines)
@@
 
-samar_points <- st_as_sf(samar_points_lines)
+samar_points <- st_as_sf(samar_points_lines) %>%
+  mutate(new_id = 1:283) %>%
+  filter(!(new_id %in% c(2:13, 108:109, 98:100, 79, 74:76, 62:66, 52:53, 14:16, 95:96))) %>%
+  dplyr::select(-new_id)
 mapview(samar_points)

### 2021-02-12 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

@@
 coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
-# mapview(coast_raw)
+
 ```
@@
 
-For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
- - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
- - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
- - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
-Or Per province/state locations (i.e.
-placing a point randomly in each province) or sub regional location.
- - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+4: Good qualifications - Locations are projected or it is a only sample of total locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+   - Must be allocated spatially
+   - Must not intersect with land mask
+   - Flagged as "allocate spatially"
+
+2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+   - Must be allocated using suitability analysis.
+   - Flagged as 2 and "state/province suitability"
+
+1: Very Bad qualifications - No data at all.
+   - Must be allocated using suitability analysis.
+   - Flagged as 1 and "country suitability"
 
@@
   cbind(iso3c = all_pts_latlon$iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5.0) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   dplyr::select(lon, lat, iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c="CAN") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   dplyr::select(-COUNTRY) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "ESP") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 
- - 5 licensed farms (only including "mollusc farm open")
- - Jersey Oyster Company Limited: 49.17300525845569, -2.0325974703629277
- - Seymour Oyster Company Ltd: 49.22644208989364, -2.0327040476242284
- - La Rocque Fisheries Limited: 49.17293132589725, -2.0312731919583795
- - Jersey Sea Farms: 49.231523271584344, -2.057638560247779
- - Island Dived Scallops: 49.20231914535721, -2.03533532472839
+ - 5 licensed farms (only including "mollusc farm open"): Locations estimated from maps and addresses listed 
+ - Jersey Oyster Company Limited: 49.172680993306905, -2.0255193115109957
+ - Seymour Oyster Company Ltd: 49.220095937386375, -2.0215887506551438
+ - La Rocque Fisheries Limited: 49.169912669200976, -2.0230904378277916
+ - Jersey Sea Farms: 49.242435452408536, -2.060618920921559
+ - Island Dived Scallops: 49.20656011166959, -2.0158403231425996
 
@@
 
-farms_jey <- data.frame(lat = c(49.17300525845569, 49.22644208989364, 49.17293132589725, 49.231523271584344, 49.20231914535721),
-                        lon = c(-2.0325974703629277, -2.0327040476242284, -2.0312731919583795, -2.057638560247779, -2.03533532472839)) %>%
+farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
+                        lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
   mutate(iso3c = "JEY") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 
-buff <- st_buffer(g_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(g_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
   mutate(iso3c = "GGY") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
 
-world <- st_as_sf(world)
+# world <- st_as_sf(world)
 
@@
 
-plot(slovenia_world_crop)
 mapview(slovenia_world_crop)
@@
 
-buff <- st_buffer(s_meters, dist = 1000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(s_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
   mutate(iso3c = "SVN") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
 
-buff <- st_buffer(c_meters, dist = 40000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(c_meters, dist = 40000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
   mutate(iso3c = "HRV") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
 Cayo Hachuela: 22.952677, -79.963228
-Cayos de la Enfermeria: 22.910246, -79.958924
+Cayos de la Enfermeria: 22.90988409545137, -79.94865189587235
 
@@
 
-farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.910246),
-                        lon = c(-80.082047, -79.994291, -79.963228, -79.958924)) %>%
+farms_cub <- data.frame(lat = c(23.0341889, 22.994283, 22.952677, 22.90988409545137),
+                        lon = c(-80.082047, -79.994291, -79.963228, -79.94865189587235)) %>%
   mutate(iso3c = "CUB") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "TWN") %>%
-  mutate(data_quality = 0.0)
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
   mutate(iso3c = "PYF") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 
-buff <- st_buffer(k_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(k_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
   mutate(iso3c = "IND") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   mutate(iso3c = "THA") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "IDN") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "RUS") %>%
-  mutate(data_quality = 0.0)
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
 
-buff <- st_buffer(nk_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(nk_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
   mutate(iso3c = "PRK") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
+  summarise(geometry = st_union(geometry)) %>% ## union all the geometries
   ungroup()
@@
 
-buff <- st_buffer(sc_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(sc_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
 
-sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 4) ## equally place the number of farms along the coastline 
+sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 24) ## equally place the number of farms along the coastline 
 class(sta_catarina_points_lines)
@@
 sta_catarina_points <- st_as_sf(sta_catarina_points_lines) %>%
-  mutate(new_id = 1:28) %>%
-  filter(new_id != 12)
+  mutate(new_id = 1:168)  %>%
+  filter(new_id %in% c(1:24, 158, 64, 78))
+
 mapview(sta_catarina_points)
@@
   mutate(iso3c = "BRA") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
 
-# start with Capiz
+# start with Capiz by placing 300 points along the coast 
 capiz <- provinces_farms %>%
@@
 
-buff <- st_buffer(cp_meters, dist = 7000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(cp_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
 
-# now do negros
+# now lets place 10 points along the coast of Negros Occidental 
 negros <- provinces_farms %>%
@@
 
-buff <- st_buffer(n_meters, dist = 5000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(n_meters, dist = 5000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
 
-# now do samar 
+# now lets place 250 points along the coast of samar 
 samar <- provinces_farms %>%
@@
 samar_world_crs <- st_transform(samar, crs(coast_raw))
-
-# marabut to veriato
 
@@
 
-buff <- st_buffer(sm_meters, dist = 3000) # buffer out to 1 km so that we can place points along a line 1 km from the coastline
+buff <- st_buffer(sm_meters, dist = 3000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
   mutate(iso3c = "PHL") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   mutate(iso3c = "MYS") %>%
-  mutate(data_quality = 0.0)
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
   mutate(iso3c = "KHM") %>%
-  mutate(data_quality = 0.0)
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
   mutate(iso3c = "HKG") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 all_farms_1 <- all_farms %>%
-  dplyr::select(-data_quality)
+  dplyr::select(-data_quality, -action_needed)
 

### 2021-02-12 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

--- 2021-02-04 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
@@
 
-Now we will map crustacean farms. Workflow will be as follows:
-
+Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
  - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
  - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of crustacean farms, equally allocate the farms across the coastline.
+ -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline.
 If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
- - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
-what we've done for Russia for bivalves).
+ - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
+ - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+4: Good qualifications - Locations are projected or it is a only sample of total locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+   - Must be allocated spatially
+   - Must not intersect with land mask
+   - Flagged as "Allocate spatially"
+
+2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+   - Must be allocated using suitability analysis.
+   - Flagged as 2 and "state/province suitability"
+
+1: Very Bad qualifications - No data at all.
+   - Must be allocated using suitability analysis.
+   - Flagged as 1 and "country suitability"
 
@@
                         lon = c(117.55582991782983)) %>%
-  mutate(iso3c = "IDN")
+  mutate(iso3c = "IDN") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
                         lon = c(121.95043909100868)) %>%
-  mutate(iso3c = "CHN")
+  mutate(iso3c = "CHN") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
 
-farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325919306644522),
-                        lon = c(89.49499697244659, 91.76441856678511)) %>%
-  mutate(iso3c = "BGD")
+farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325670145257305),
+                        lon = c(89.49499697244659, 91.76091935028879)) %>%
+  mutate(iso3c = "BGD") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
                         lon = c(94.76647475697742, 94.24290607527016)) %>%
-  mutate(iso3c = "MMR")
+  mutate(iso3c = "MMR") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 
-farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055231),
-                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.789267),
+farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055819944690162),
+                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
                         prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
-  mutate(iso3c = "VNM")
+  mutate(iso3c = "VNM") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
   dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
-  mutate(iso3c = "PHL")
+  mutate(iso3c = "PHL") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 
-write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
+write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv"), row.names = FALSE)
 
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality, -action_needed)
+
+write.csv(all_farms_1, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
 ```

### 2021-02-12 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

--- 2021-02-04 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
@@
 
-# Map data from ASC
-
-Data comes from https://gis.asc-aqua.org/arcgis_app/
-
-Source:
-Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
-https://gis.asc-aqua.org/arcgis_app/
-
-```{r}
-
-# get iso3c codes
-iso <-   data.frame(iso3c = countrycode(ASC_finfish$crt_cnt, origin = 'country.name', destination = 'iso3c'))
-
-# read in shp
-farms_all <- ASC_finfish %>%
-  cbind(iso) %>%
-  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands")))
-
-mapview(farms_all$geometry)
-
-unique(farms_all$iso3c)
-
-all_pts <- st_centroid(farms_all)
-
-all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
-  dplyr::select(geometry, iso3c)
-
-farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
-names(farms_all_fin) <- c("lon", "lat")
-farms_all_fin <- farms_all_fin %>%
-  cbind(iso3c = all_pts_latlon$iso3c)
-
-## save farm location
-write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)
-
-```
-
 Now we will map the remaining countries with marine finfish farms that are not included in the ASC dataset. Workflow will be as follows: 
@@
 what we've done for Russia for bivalves).
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+4: Good qualifications - Locations are projected or it is a only sample of total locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+   - Must be allocated spatially
+   - Must not intersect with land mask
+   - Flagged as "Allocate spatially"
+
+2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+   - Must be allocated using suitability analysis.
+   - Flagged as 2 and "state/province suitability"
+
+1: Very Bad qualifications - No data at all.
+   - Must be allocated using suitability analysis.
+   - Flagged as 1 and "country suitability"
+
+# Map data from ASC
+
+Data comes from https://gis.asc-aqua.org/arcgis_app/
+
+Source:
+Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
+https://gis.asc-aqua.org/arcgis_app/
+
+```{r}
+
+# get iso3c codes
+iso <-   data.frame(iso3c = countrycode(ASC_finfish$crt_cnt, origin = 'country.name', destination = 'iso3c'))
+
+# read in shp
+farms_all <- ASC_finfish %>%
+  cbind(iso) %>%
+  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands")))
+
+mapview(farms_all$geometry)
+
+unique(farms_all$iso3c)
+
+all_pts <- st_centroid(farms_all)
+
+all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
+  dplyr::select(geometry, iso3c)
+
+farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
+names(farms_all_fin) <- c("lon", "lat")
+farms_all_fin <- farms_all_fin %>%
+  cbind(iso3c = all_pts_latlon$iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
+
+## save farm location
+write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)
+
+```
 
@@
   )) %>%
-  dplyr::select(-COUNTRY)
+  dplyr::select(-COUNTRY) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_ita <- farms_ita %>%
-  mutate(iso3c="ITA")
+  mutate(iso3c="ITA") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
-  dplyr::select(-country, -geometry)
+  dplyr::select(-country, -geometry) %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_idn <- farms_idn %>%
-  mutate(iso3c = "IDN")
+  mutate(iso3c = "IDN") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_prt_final <- farms_prt %>%
-  mutate(iso3c = "PRT")
+  mutate(iso3c = "PRT") %>%
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
                         lon = c(50.1602963496454)) %>%
-  mutate(iso3c = "IRN")
+  mutate(iso3c = "IRN") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
                         lon = c(119.94149300994019)) %>%
-  mutate(iso3c = "CHN")
+  mutate(iso3c = "CHN") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
 
-farms_sau <- data.frame(lat = c(20.287253),
-                        lon = c(40.030864)) %>%
-  mutate(iso3c = "SAU")
+farms_sau <- data.frame(lat = c(20.27293672234808),
+                        lon = c(40.03614937279944)) %>%
+  mutate(iso3c = "SAU") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
                         lon = c(57.67022708374523)) %>%
-  mutate(iso3c = "MUS")
+  mutate(iso3c = "MUS") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
                         lon = c(56.340214330776234)) %>%
-  mutate(iso3c = "ARE")
+  mutate(iso3c = "ARE") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 farms_tun_final <- farms_tun %>%
-  mutate(iso3c = "TUN")
+  mutate(iso3c = "TUN") %>%
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
 all_points_twn <- rbind(milkfish_points, grouper_points) %>%
-  dplyr::mutate(iso3c = "TWN")
+  dplyr::mutate(iso3c = "TWN") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
                         lon = c(-84.20910189917947)) %>%
-  mutate(iso3c = "CRI")
+  mutate(iso3c = "CRI") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
                         subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
-  mutate(iso3c = "EGY")
+  mutate(iso3c = "EGY") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
                         lon = c(79.13007737814245)) %>%
-  mutate(iso3c = "IND")
+  mutate(iso3c = "IND") %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_sgp_final <- farms_sgp %>%
-  mutate(iso3c = "SGP")
+  mutate(iso3c = "SGP") %>%
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
                         lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
-  mutate(iso3c = "MYS")
+  mutate(iso3c = "MYS") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
                         lon=c(90.40418040967)) %>%
-  mutate(iso3c = "BGD")
+  mutate(iso3c = "BGD") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
                         lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
-  mutate(iso3c = "KHM")
+  mutate(iso3c = "KHM") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 farms_kor_final <- farms_kor %>%
-  mutate(iso3c = "KOR")
+  mutate(iso3c = "KOR") %>%
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
 farms_phl_final <- farms_phl %>%
-  mutate(iso3c = "PHL")
+  mutate(iso3c = "PHL") %>%
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
-  mutate(iso3c = "HKG")
+  mutate(iso3c = "HKG") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 
-write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)
-
-```
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality, -action_needed)
+
+write.csv(all_farms_1, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon_data_quality.csv"), row.names = FALSE)
+
+```

### 2021-02-12 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
finished marine bivalve data quality
finished updating data quality flags. Still need to buffer points into water for some

--- 2021-02-04 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
@@
 ```
+Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
+ - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
+ - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
+ -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline.
+If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
+ - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
+ - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+4: Good qualifications - Locations are projected or it is a only sample of total locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+   - Must be allocated spatially
+   - Must not intersect with land mask
+   - Flagged as "Allocate spatially"
+
+2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+   - Must be allocated using suitability analysis.
+   - Flagged as 2 and "state/province suitability"
+
+1: Very Bad qualifications - No data at all.
+   - Must be allocated using suitability analysis.
+   - Flagged as 1 and "country suitability"
 
@@
 farms_chile <- farms_chile %>%
-  mutate(iso3c="CHL")
+  mutate(iso3c="CHL") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_nor <- sub_norway %>% 
-  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") # Counting duplicate liscense locations once
+  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") %>% # Counting duplicate liscense locations once
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_scotland <- farms_scotland %>%
-  mutate(iso3c="GBR")
+  mutate(iso3c = "GBR") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_all_fro <- farms_fro %>%
-  cbind(iso3c = fro_pts_latlon$iso3c)
+  cbind(iso3c = fro_pts_latlon$iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   dplyr::select(lon, lat) %>%
-  mutate(iso3c="AUS")
+  mutate(iso3c="AUS") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_bc <- farms_bc %>%
-  mutate(iso3c="CAN")
+  mutate(iso3c="CAN") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_nb <- farms_nb %>%
-  mutate(iso3c="CAN")
+  mutate(iso3c="CAN") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_ns <- farms_ns %>%
-  mutate(iso3c="CAN")
+  mutate(iso3c="CAN") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "CAN") %>%
-  dplyr::select(lon, lat, iso3c)
+  dplyr::select(lon, lat, iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "USA") %>%
-  dplyr::select(lon, lat, iso3c)
+  dplyr::select(lon, lat, iso3c) %>%
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_us_ne <- farms_us_ne %>%
-  mutate(iso3c = "USA")
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_all_nzl <- farms_nzl %>%
-  cbind(iso3c = nzl_pts_latlon$iso3c)
+  cbind(iso3c = nzl_pts_latlon$iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_ire <- farms_ire %>%
-  mutate(iso3c="IRL")
+  mutate(iso3c="IRL") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
                     lat=c(69.4953)) %>%
-  mutate(iso3c = "RUS")
+  mutate(iso3c = "RUS") %>%
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
 farms_all_JPN <- farms_JPN %>%
-  cbind(iso3c = JPN_pts_latlon$iso3c)
+  cbind(iso3c = JPN_pts_latlon$iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_dk <- cbind(farms_dk, dk_subregions ) %>%
-  dplyr::select(lon, lat, iso3c, subregion = NAME)
+  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
                     lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
-  mutate(iso3c = "TUR")
+  mutate(iso3c = "TUR") %>%
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 farms_fi <- cbind(farms_fi, fi_subregions ) %>%
-  dplyr::select(lon, lat, iso3c, subregion = NAME)
+  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 Source:
-HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM Map and Data Service, n.d. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
   dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
-  filter(!is.na(lat))
+  filter(!is.na(lat)) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 farms_all_ISL <- farms_ISL %>%
-  cbind(iso3c = ISL_pts_latlon$iso3c)
+  cbind(iso3c = ISL_pts_latlon$iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 
@@
 
-write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)
+all_farms_1 <- all_farms %>%
+  dplyr::select(-data_quality, -action_needed)
 
-# all_farms <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), col_types = "ddcc")
+write.csv(all_farms_1, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), row.names = FALSE)
+
+# all_farms <- read_csv(here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), col_types = "ddccd")
 

### 2021-02-12 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

@@
 library(spatialEco)
+library(countrycode)
 
@@
 # [33] "United States of America" "Venezuela, Boliv Rep of"  "Viet Nam"
+
+coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
 ```
@@
 
-# Map data from ASC (contains 19/35 countries)
-
-Data comes from https://gis.asc-aqua.org/arcgis_app/
-
-Source: 
-Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
-https://gis.asc-aqua.org/arcgis_app/
-
-```{r}
-library(countrycode)
-# get iso3c codes
-iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))
-
-# read in shp and filter out countries not in FAO
-farms_all <- ASC_shrimp %>%
-  cbind(iso) %>%
-  dplyr::filter(iso3c != "NGA",
-                iso3c != "TZA",
-                iso3c != "MOZ")
-
-mapview(farms_all$geometry)
-
-unique(farms_all$iso3c)
-
-all_pts <- st_centroid(farms_all)
-
-all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
-  dplyr::select(geometry, iso3c)
-
-farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
-names(farms_all_fin) <- c("lon", "lat")
-farms_all_fin <- farms_all_fin %>%
-  cbind(iso3c = all_pts_latlon$iso3c) %>%
-  mutate(data_quality = 1.0)
-
-## save farm location
-write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/farm_sites/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)
-
-```
-
 Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
@@
 
-For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
- - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
- - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates.
- - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
-Or Per province/state locations (i.e.
-placing a point randomly in each province) or sub regional location.
- - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number).
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+4: Good qualifications - Locations are projected or it is a only sample of total locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+   - Must be allocated spatially
+   - Must not intersect with land mask
+   - Flagged as "Allocate spatially"
+
+2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+   - Must be allocated using suitability analysis.
+   - Flagged as 2 and "state/province suitability"
+
+1: Very Bad qualifications - No data at all.
+   - Must be allocated using suitability analysis.
+   - Flagged as 1 and "country suitability"
+
+# Map data from ASC (contains 19/35 countries)
+
+Data comes from https://gis.asc-aqua.org/arcgis_app/
+
+Source: 
+Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
+https://gis.asc-aqua.org/arcgis_app/
+
+```{r}
+
+# get iso3c codes
+iso <-   data.frame(iso3c = countrycode(ASC_shrimp$crt_cnt, origin = 'country.name', destination = 'iso3c'))
+
+# read in shp and filter out countries not in FAO
+farms_all <- ASC_shrimp %>%
+  cbind(iso) %>%
+  dplyr::filter(iso3c != "NGA",
+                iso3c != "TZA",
+                iso3c != "MOZ")
+
+mapview(farms_all$geometry)
+
+unique(farms_all$iso3c)
+
+all_pts <- st_centroid(farms_all)
+
+all_pts_latlon <- st_transform(all_pts, crs = "+init=epsg:4326") %>% 
+  dplyr::select(geometry, iso3c)
+
+farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
+names(farms_all_fin) <- c("lon", "lat")
+farms_all_fin <- farms_all_fin %>%
+  cbind(iso3c = all_pts_latlon$iso3c) %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
+
+## save farm location
+write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/farm_sites/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)
+
+```
 
@@
   mutate(iso3c = "BRA") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
   mutate(iso3c = "BRN") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "KHM") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 
-world <- ne_coastline(scale = 50) #world map with 50m resolution
-plot(world)
-
-world <- st_as_sf(world)
-
-costa_world_crs <- st_transform(guana_punta, crs(world))
-
-costa_world_crop <- st_crop(world, costa_world_crs) ## crop to costa rica extent 
-plot(costa_world_crop)
+# world <- ne_coastline(scale = 50) #world map with 50m resolution
+# plot(world)
+
+# world <- st_as_sf(world)
+
+costa_world_crs <- st_transform(guana_punta, crs(coast_raw))
+
+costa_world_crop <- st_crop(coast_raw, costa_world_crs) %>% ## crop to costa rica extent 
+  filter(FID %in% c(245909:245926)) %>% ## filter for the correct coastline 
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
 mapview(costa_world_crop)
 
-costa_crop <- as(costa_world_crop, "Spatial")
-plot(costa_crop)
+c_meters <- st_transform(costa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(c_meters)
+
+buff <- st_buffer(c_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(costa_world_crop))
+mapview(buffer_outline_fixed)
+
+costa_rica <- ne_countries(scale = 10, country = "Costa Rica", returnclass = "sf")
+mapview(costa_rica)
+
+linestring_fix <- st_difference(buffer_outline_fixed, costa_rica) ## now grab only the outline 
+mapview(linestring_fix)
+
+costa_crop <- as(linestring_fix, "Spatial")
 mapview(costa_crop)
 
-costa_points_lines <- sample.line(costa_crop, n = 121) ## equally place the number of farms along the coastline 
-class(costa_points_lines)
-plot(costa_points_lines)
-
-costa_points <- st_as_sf(costa_points_lines)
+costa_points_lines <- sample.line(costa_crop, n = 106) ## equally place the number of farms along the coastline
+
+costa_points <- st_as_sf(costa_points_lines) %>%
+  mutate(new_id = 1:318) %>%
+  filter(new_id %in% c(1:88, 105:106))
 mapview(costa_points)
 
-## Now filter out the points that fall outside of costa rica 
-costa_points_final <- costa_points[4:93,]
-mapview(costa_points_final)
-
-cri_pts <- st_centroid(costa_points_final)
+cri_pts <- st_centroid(costa_points)
 
@@
   mutate(iso3c = "CRI") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   mutate(iso3c = "CUB") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "SLV") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
 NASO aquaculture maps collection , 2010.
-.
 Food and Agriculture Organization of the United Nations.
@@
   mutate(iso3c="IRN") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 mapview(farms_irn)
-```
-
-old methods: 
-```{r}
-# iran <- ne_countries(scale = 10, country = "Iran", returnclass = "sf")
-# mapview(iran)
-# 
-# world <- ne_coastline(scale = 10) #world map with 10m resolution
-# plot(world)
-# 
-# world <- st_as_sf(world)
-# 
-# iran_world_crs <- st_transform(iran, crs(world))
-# 
-# iran_world_crop <- st_crop(world, iran_world_crs) ## crop to iran extent
-# plot(iran_world_crop)
-# mapview(iran_world_crop)
-# 
-# iran_world_crop <- head(iran_world_crop, 2) ## filter out lines not in iran
-# mapview(iran_world_crop)
-# 
-# iran_world_crop <- tail(iran_world_crop, 1)
-# 
-# iran_crop <- as(iran_world_crop, "Spatial")
-# plot(iran_crop)
-# mapview(iran_crop)
-# 
-# 
-# 
-# iran_points_lines <- sample.line(iran_crop, n = 221) ## equally place the number of farms along the coastline 
-# class(iran_points_lines)
-# plot(iran_points_lines)
-# 
-# iran_points <- st_as_sf(iran_points_lines)
-# mapview(iran_points)
-# 
-# ## Now filter out the points that fall outside of iran
-# iran_points_final <- iran_points[17:221,]
-# mapview(iran_points_final)
-# 
-# 
-# irn_pts <- st_centroid(iran_points_final)
-# 
-# irn_pts_latlon <- st_transform(irn_pts, crs = "+init=epsg:4326") %>%
-#   dplyr::select(geometry)
-# 
-# farms_irn <- data.frame(do.call(rbind, st_geometry(irn_pts_latlon)))
-# names(farms_irn) <- c("lon", "lat")
-# 
-# farms_irn_final <- farms_irn %>%
-#   mutate(iso3c = "IRN")
-# 
-# ## visualize it 
-# farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_irn)
-# 
-# ## write to farms folder 
-# write_csv(farms_irn_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))
-
-```
-
-old old methods:
- - From google maps: 
-    - Sea waves TRD: 26.790754, 55.396608: 582 hectares 
-    - Iran Aquatic: 27.135585, 56.887211: 1877 hectares 
-    - Technoshrimp: 29.227964, 50.709040: 1303 hectares 
-    - Shrimp Breeders Delvar site: 28.770827, 51.046329: 312 hectares
-    - Pars Abzistan Shrimp & Fish Hatchery: 28.781671, 51.048787: 280 hectares
-    - Shrimp Marjan: 27.851429, 51.984108: 156.5493 hectares
-    - Shrimp Aquaculture: 26.671137, 55.902159: 31 hectares 
-    - Pardis: looks like indoor, don't include
-    - Sontderaf: looks like indoor, don't include
-
-```{r}
-# farms_irn <- data.frame(lat=c(26.790754, 27.135585, 29.227964, 28.770827, 28.781671, 27.851429, 26.671137),
-#                         lon=c(55.396608, 56.887211, 50.709040, 51.046329, 51.048787, 51.984108, 55.902159),
-#                         area_ha = c(582, 1877, 1303, 312, 280, 156.5493, 31)) %>%
-#   mutate(iso3c = "IRN")
-# 
-# write_csv(farms_irn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))
-# 
-# ## visualize it 
-# farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_irn)
 ```
@@
   mutate(iso3c = "JPN") %>%
-  mutate(data_quality = 0.0)
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
   mutate(iso3c = "KOR") %>% 
-  mutate(data_quality = 0.0)
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
 
@@
  - TAMAN AKUAKULTUR LKIM TELAGA AIR, SARAWAK: 1.676758, 110.210032
- - KG. MERCHONG, PEKAN, PAHANG: 3.018320, 103.430156
+ - KG. MERCHONG, PEKAN, PAHANG: 3.018046544221823, 103.43838831493285
  - KG. PENGKALAN GELAP, SETIU, TERENGGANU: 5.674088, 102.721589
  - KG. PASIR PUTEH, MARANG, TERENGGANU: 4.984545, 103.328932
- - PENARIK, SETIU, TERENGGANU: 5.596019, 102.826214
+ - PENARIK, SETIU, TERENGGANU: 5.597252273526056, 102.82739417198427
  - TANJUNG MANIS, SARAWAK: 2.197050, 111.183470
@@
 ```{r}
-farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018320, 5.674088, 4.984545, 5.596019, 2.197050, 3.888025, 3.663462, 3.203638),
-                        lon=c(99.826952, 102.463536, 110.210032, 103.430156, 102.721589, 103.328932, 102.826214, 111.183470, 100.704595, 100.975557, 103.446051),
+farms_mys <- data.frame(lat=c(6.433288, 2.108604, 1.676758, 3.018046544221823, 5.674088, 4.984545, 5.597252273526056, 2.197050, 3.888025, 3.663462, 3.203638),
+                        lon=c(99.826952, 102.463536, 110.210032, 103.43838831493285, 102.721589, 103.328932, 102.82739417198427, 111.183470, 100.704595, 100.975557, 103.446051),
                         area_ha =mys_area) %>%
   mutate(iso3c = "MYS") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
   mutate(iso3c = "MMR") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 2) %>%
+  mutate(action_needed = "state/province based suitability")
 
@@
   mutate(area_ha = 13.35) %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   mutate(iso3c = "SAU") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   dplyr::mutate(iso3c = "LKA") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 

### 2021-02-12 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

@@
 
-Now we will map the remaining countries with marine tuna farms. Workflow will be as follows:
-
+Now we will map the remaining countries with tuna farms that are not included in the ASC dataset. Workflow will be as follows: 
  - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
  - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of tuna farms, equally allocate the farms across the coastline.
+ -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline.
 If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
- - Lastly, if there is no evidence of marine tuna farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
-what we've done for Russia for bivalves).
+ - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
+ - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+4: Good qualifications - Locations are projected or it is a only sample of total locations
+   - Must not intersect with land mask
+   - "Land mask"
+
+3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+   - Must be allocated spatially
+   - Must not intersect with land mask
+   - Flagged as "Allocate spatially"
+
+2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+   - Must be allocated using suitability analysis.
+   - Flagged as 2 and "state/province suitability"
+
+1: Very Bad qualifications - No data at all.
+   - Must be allocated using suitability analysis.
+   - Flagged as 1 and "country suitability"
 
@@
   dplyr::select(-country, -geometry) %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
   mutate(iso3c = "AUS") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
 ## now that we have coordinates, place them on a map and save
@@
   mutate(iso3c = "JPN") %>%
-  mutate(data_quality = 0.333)
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 
@@
                           iso3c = "MEX") %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 

### 2021-02-16 marine/explore_spatial_allocation.Rmd
updated data quality exploration

@@
 ```
+
+This script explores the distribution/data quality of aquaculture within each country.
 
@@
 path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"
+
+source(here::here("_spatial/template_raster.R"))
+```
+
+```{r}
+
+gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
+
+gadm_latlon <- projectRaster(gadm, food_raster)
+
+gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
+  mutate(reg_id = as.numeric(reg_id))
+
+```
+
+```{r}
+
+gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
+  mutate(cellvalue = round(cellvalue, 0))
+
+gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
 
@@
 
-## n_farms shows us the number of points that will need spatial allocation within each country according to our new rules (any of the rows that score 0.333 in the data quality column)
+## n_farms shows us the number of points that will need spatial allocation within each country according to our new rules (any of the rows that score 3.
+Those that score 1 or 2, will need some sort of suitability analysis.)
 
@@
 
-## n_countries shows us the number of countries that will need spatial allocation within each species group according to our new rules (any of the rows that score 0.333 in the data quality column)
+## n_countries shows us the number of countries that will need spatial allocation within each species group according to our new rules (any of the rows that score 3 in the data quality column.
+Those that score 1 or 2, will need some sort of suitability analysis, based on country or provice/state.)
 
 n_countries_allocated <- n_countries %>%
-  dplyr::filter(data_quality == 0.333)
+  dplyr::filter(data_quality == 3)
 sum(n_countries_allocated$n_countries)
-## 31 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)
+## 16 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)
 
 n_countries_no_data <- n_countries %>%
-  dplyr::filter(data_quality == 0.0)
+  dplyr::filter(data_quality == 1)
 sum(n_countries_no_data$n_countries) # 14
-## 14 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)
+## 14 countries/species group combos that will need country level spatial allocation according to our rules (7-10km to port, depth requirements)
 
-sum(n_countries_allocated$n_countries)
+n_states_no_data <- n_countries %>%
+  dplyr::filter(data_quality == 2)
+sum(n_states_no_data$n_countries) # 14
+## 14 countries/species group combos that will need subregional spatial allocation according to our rules (7-10km to port, depth requirements)
 
 ## these were the rules for the data quality column: 
-# For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
-#  - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
-#  - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps). Google maps estimates. 
-#  - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
-Or Per province/state locations (i.e.
-placing a point randomly in each province or sub regional location).
-#  - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number). 
+# For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+#  5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
+#    - Must not intersect with land mask
+#    - "Land mask"
+# 
+# 4: Good qualifications - Locations are projected or it is a only sample of total locations
+#    - Must not intersect with land mask
+#    - "Land mask"
+# 
+# 3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
+#    - Must be allocated spatially
+#    - Must not intersect with land mask
+#    - Flagged as "allocate spatially"
+# 
+# 2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
+#    - Must be allocated using suitability analysis.
+#    - Flagged as 2 and "state/province suitability"
+# 
+# 1: Very Bad qualifications - No data at all.
+#    - Must be allocated using suitability analysis.
+#    - Flagged as 1 and "country suitability"  
 ```

### 2021-02-16 marine/explore_spatial_allocation.Rmd
fixed coastal buffer for all countries that needed it

@@
 sum(n_countries_allocated$n_countries)
-## 16 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)
+## 15 countries/species group combos that will need spatial allocation according to our rules (7-10km to port, depth requirements)
 
@@
   dplyr::filter(data_quality == 1)
-sum(n_countries_no_data$n_countries) # 14
-## 14 countries/species group combos that will need country level spatial allocation according to our rules (7-10km to port, depth requirements)
+sum(n_countries_no_data$n_countries) # 15
+## 15 countries/species group combos that will need country level spatial allocation according to our rules (7-10km to port, depth requirements)
 

### 2021-02-16 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
fixed coastal buffer for all countries that needed it

@@
 # [37] "Viet Nam"
+
+coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
 ```
@@
 #info of our spatial vector object
-portugal
 mapview(portugal)
-plot(portugal)
 
@@
 
-portugal_world_crop <- st_crop(world, portugal_world_crs) #%>%
- # dplyr::filter(scalerank == 5) ## filter for the appropriate island
-plot(portugal_world_crop)
+portugal_world_crop <- st_crop(world, portugal_world_crs) # %>%
+  # filter(FID %in% c(41705:41729)) %>%
+  # mutate(new_id = 1) %>%
+  # group_by(new_id) %>%
+  # summarise(geometry = st_union(geometry)) %>%
+  # ungroup()
 mapview(portugal_world_crop)
 
-portugal_crop <- as(portugal_world_crop, "Spatial")
-
-portugal_points_lines <- sample.line(portugal_crop, n = 380) ## equally place the number of farms along the coastline 
+p_meters <- st_transform(portugal_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(p_meters)
+
+buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(portugal_world_crop))
+
+linestring_fix <- st_difference(buffer_outline_fixed, portugal) ## now grab only the outline 
+mapview(linestring_fix)
+
+portugal_crop <- as(linestring_fix, "Spatial")
+
+portugal_points_lines <- sample.line(portugal_crop, n = 480) ## equally place the number of farms along the coastline 
 class(portugal_points_lines)
@@
 
-portugal_points_final <- portugal_points[253:364, ] ## grab the appropriate number of points
+portugal_points_final <- portugal_points[28:139, ] ## grab the appropriate number of points
 mapview(portugal_points_final)
@@
 
-## OR if you don't municipality and only country info you could use this: 
-# tunisia <- rnaturalearth::ne_countries(country = "Tunisia")
-
-world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
-plot(world)
-class(world)
-
-#info of our spatial vector object
-tunisia
-mapview(tunisia)
-
-world <- st_as_sf(world)
-
-tunisia_world_crs <- st_transform(tunisia, crs(world))
-
-tunisia_world_crop <- st_crop(world, tunisia_world_crs) 
-plot(tunisia_world_crop)
+# world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
+# plot(world)
+# class(world)
+
+# world <- st_as_sf(world)
+
+tunisia_world_crs <- st_transform(tunisia, crs(coast_raw))
+
+tunisia_world_crop <- st_crop(coast_raw, tunisia_world_crs)  %>%
+  filter(FID %in% c(652755:652756)) %>%
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
 mapview(tunisia_world_crop)
 
-tunisia_crop <- as(tunisia_world_crop, "Spatial")
+t_meters <- st_transform(tunisia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(t_meters)
+
+buff <- st_buffer(t_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(tunisia_world_crop))
+
+tunisia2 <- ne_countries(scale = 10, country = "Tunisia", returnclass = "sf")
+
+linestring_fix <- st_difference(buffer_outline_fixed, tunisia2) ## now grab only the outline 
+mapview(linestring_fix)
+
+tunisia_crop <- as(linestring_fix, "Spatial")
 class(tunisia_crop)
@@
 
-tunisia_points_lines <- sample.line(tunisia_crop, n = 20) ## equally place the number of farms along the coastline 
+tunisia_points_lines <- sample.line(tunisia_crop, n = 25) ## equally place the number of farms along the coastline 
 class(tunisia_points_lines)
@@
 
-tunisia_points <- st_as_sf(tunisia_points_lines)
+tunisia_points <- st_as_sf(tunisia_points_lines) %>%
+  mutate(new_id = 1:25) %>%
+  filter(new_id %in% c(2:21))
 mapview(tunisia_points)
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
-plot(world)
-
-singapore <- ne_countries(scale = 50, country = "Singapore", returnclass = "sf")
-
-#info of our spatial vector object
-singapore
+# world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
+# plot(world)
+
+singapore <- ne_countries(scale = 10, country = "Singapore", returnclass = "sf")
+
 mapview(singapore)
-plot(singapore)
-
-world <- st_as_sf(world)
-
-singapore_world_crs <- st_transform(singapore, crs(world))
-
-singapore_world_crop <- st_crop(world, singapore_world_crs) %>%
-  dplyr::filter(scalerank == 3) ## filter for the appropriate area
-plot(singapore_world_crop)
+
+# world <- st_as_sf(world)
+
+singapore_world_crs <- st_transform(singapore, crs(coast_raw))
+
+singapore_world_crop <- st_crop(coast_raw, singapore_world_crs) %>%
+  dplyr::filter(FID %in% c(242908)) ## filter for the appropriate area
+
 mapview(singapore_world_crop)
 
-singapore_crop <- as(singapore_world_crop, "Spatial")
+s_meters <- st_transform(singapore_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(s_meters)
+
+buff <- st_buffer(s_meters, dist = 8000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(singapore_world_crop))
+
+linestring_fix <- st_difference(buffer_outline_fixed, singapore) ## now grab only the outline 
+mapview(linestring_fix)
+
+singapore_crop <- as(linestring_fix, "Spatial")
 
 singapore_points_lines <- sample.line(singapore_crop, n = 225) ## equally place the number of farms along the coastline
-class(singapore_points_lines)
-plot(singapore_points_lines)
 
@@
 
-south_korea <- ne_countries(scale = 50, country = "South Korea", returnclass = "sf")
+south_korea <- ne_countries(scale = 110, country = "South Korea", returnclass = "sf")
 
 #info of our spatial vector object
-south_korea
 mapview(south_korea)
-plot(south_korea)
 
@@
 
-south_korea_world_crop <- st_crop(world, south_korea_world_crs) #%>%
+south_korea_world_crop <- st_crop(world, south_korea_world_crs) # %>%
+  # filter(FID %in% c(44825:44924)) %>%
+  # mutate(new_id = 1) %>% 
+  # group_by(new_id) %>%
+  # summarise(geometry %in% st_union(geometry)) %>%
+  # ungroup()
  # dplyr::filter(scalerank == 3) ## filter for the appropriate area
 
-south_korea_world_crop <- south_korea_world_crop[2, ]
-plot(south_korea_world_crop)
 mapview(south_korea_world_crop)
 
-south_korea_crop <- as(south_korea_world_crop, "Spatial")
-
-south_korea_points_lines <- sample.line(south_korea_crop, n = 612) ## equally place the number of farms along the coastline 
+k_meters <- st_transform(south_korea_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(k_meters)
+
+buff <- st_buffer(k_meters, dist = 20000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(south_korea_world_crop))
+
+linestring_fix <- st_difference(buffer_outline_fixed, south_korea) ## now grab only the outline 
+mapview(linestring_fix)
+
+south_korea_crop <- as(linestring_fix, "Spatial")
+
+south_korea_points_lines <- sample.line(south_korea_crop, n = 800) ## equally place the number of farms along the coastline 
 class(south_korea_points_lines)
@@
 
-south_korea_points <- st_as_sf(south_korea_points_lines)
+south_korea_points <- st_as_sf(south_korea_points_lines) %>%
+  mutate(new_id = 1:800) %>%
+  filter(!(new_id %in% c(96:130, 50:51, 92, 16:37, 712, 753, 665:682, 634:646, 607:620, 561, 531:532, 491, 469:493, 131:183)))
 mapview(south_korea_points)
@@
 The only  species listed is Milkfish. 
-There is no exact number listed, however I know that there are a lot of milkfish farms in the Philippines, as it is their oldest aquaculture method.
-There are definitely over 300.
-I will randomly place over 300 farms along the coast of the philippines.
+There is no exact number listed, however I know that there are a lot of milkfish farms in the Philippines, as it is their oldest aquaculture method. I will just place 1 point randomly along the coast.
 
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
-plot(world)
-
-philippines <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
-
-#info of our spatial vector object
-philippines
-mapview(philippines)
-plot(philippines)
-
-world <- st_as_sf(world)
-
-philippines_world_crs <- st_transform(philippines, crs(world))
-
-philippines_world_crop <- st_crop(world, philippines_world_crs) #%>%
- # dplyr::filter(scalerank == 3) ## filter for the appropriate area
-
-philippines_world_crop <- philippines_world_crop[-1, ]
-plot(philippines_world_crop)
-mapview(philippines_world_crop)
-
-philippines_crop <- as(philippines_world_crop, "Spatial")
-
-philippines_points_lines <- sample.line(philippines_crop, n = 43) ## equally place the number of farms along the coastline 
-class(philippines_points_lines)
-plot(philippines_points_lines)
-
-philippines_points <- st_as_sf(philippines_points_lines)
-mapview(philippines_points)
-
-## now prep dataframe for lat lon points
-phl_pts <- st_centroid(philippines_points)
-
-phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
-names(farms_phl) <- c("lon", "lat")
-
-farms_phl_final <- farms_phl %>%
+
+# 14.230786241168634, 120.57029349583156
+farms_phl <- data.frame(lat=c(14.230786241168634),
+                        lon=c(120.57029349583156)) %>%
   mutate(iso3c = "PHL") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
+  mutate(data_quality = 1) %>%
+  mutate(action_needed = "country based suitability")
+
+write_csv(farms_phl, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_phl.csv"))
 
@@
 mapview(farms_phl)
-
-## write to farms folder 
-write_csv(farms_phl_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_phl.csv"))
 ```

### 2021-02-16 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed coastal buffer for all countries that needed it

@@
 world <- ne_coastline(scale = 110) #world map with 110m resolution
-plot(world)
 
@@
 philly_world_crop <- st_crop(world, philly_world_crs) ## crop to philippines extent
-plot(philly_world_crop)
+
 mapview(philly_world_crop)
@@
 philly_world_crop <- philly_world_crop[-c(1), ] ## delete lines that are not in philippines
-
 mapview(philly_world_crop)
 
+# philly_world_crop <- philly_world_crop %>%
+#   mutate(new_id = 1) %>%
+#   group_by(new_id) %>%
+#   summarise(geometry = st_union(geometry)) %>%
+#   ungroup()
+# 
+# mapview(philly_world_crop)
+# 
+# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+# mapview(p_meters)
+# 
+# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+# mapview(buff)
+# 
+# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+# mapview(linestring)
+# 
+# ## now reproject back to original 
+# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
+# mapview(buffer_outline_fixed)
+# 
+# 
+# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
+# mapview(philly2)
+#   
+# linestring_fix <- st_difference(buffer_outline_fixed, philly) ## now grab only the outline 
+# mapview(linestring_fix)
+
 philly_crop <- as(philly_world_crop, "Spatial")
-plot(philly_crop)
 mapview(philly_crop)
 
-philly_points_lines <- sample.line(philly_crop, n = 39) ## equally place the number of farms along the coastline 
+philly_points_lines <- sample.line(philly_crop, n = 2) ## equally place the number of farms along the coastline 
 class(philly_points_lines)
@@
 ## Start with Batticaloa
-world <- ne_coastline(scale = 50) #world map with 50m resolution
-plot(world)
-
-world <- st_as_sf(world)
-
-batticaloa_world_crs <- st_transform(batticaloa_shp, crs(world))
-
-batticaloa_world_crop <- st_crop(world, batticaloa_world_crs) ## crop to batticaloa extent
-plot(batticaloa_world_crop)
+# world <- ne_coastline(scale = 50) #world map with 50m resolution
+# plot(world)
+
+# world <- st_as_sf(world)
+
+batticaloa_world_crs <- st_transform(batticaloa_shp, crs(coast_raw))
+
+batticaloa_world_crop <- st_crop(coast_raw, batticaloa_world_crs) %>% ## crop to batticaloa extent
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
 mapview(batticaloa_world_crop)
 
-batticaloa_crop <- as(batticaloa_world_crop, "Spatial")
-plot(batticaloa_crop)
+b_meters <- st_transform(batticaloa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(b_meters)
+
+buff <- st_buffer(b_meters, dist = 4000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(batticaloa_world_crop))
+mapview(buffer_outline_fixed)
+
+sri_lanka <- ne_countries(scale = 10, country = "Sri Lanka", returnclass = "sf")
+mapview(sri_lanka)
+
+linestring_fix <- st_difference(buffer_outline_fixed, sri_lanka) ## now grab only the outline 
+mapview(linestring_fix)
+
+batticaloa_crop <- as(linestring_fix, "Spatial")
 mapview(batticaloa_crop)
 
-batticaloa_points_lines <- sample.line(batticaloa_crop, n = 60) ## equally place the number of farms along the coastline 
+batticaloa_points_lines <- sample.line(batticaloa_crop, n = 80) ## equally place the number of farms along the coastline 
 class(batticaloa_points_lines)
@@
 
-batticaloa_points <- st_as_sf(batticaloa_points_lines)
+batticaloa_points <- st_as_sf(batticaloa_points_lines) %>%
+  mutate(new_id = 1:80) %>%
+  dplyr::filter(new_id %in% c(1:60))
 mapview(batticaloa_points)
@@
 ## Now do puttalam
-world <- ne_coastline(scale = 50) #world map with 50m resolution
-plot(world)
-
-world <- st_as_sf(world)
-
-puttalam_world_crs <- st_transform(puttalam_shp, crs(world))
-
-puttalam_world_crop <- st_crop(world, puttalam_world_crs) ## crop to puttalam extent
-plot(puttalam_world_crop)
+# world <- ne_coastline(scale = 50) #world map with 50m resolution
+# plot(world)
+# 
+# world <- st_as_sf(world)
+
+puttalam_world_crs <- st_transform(puttalam_shp, crs(coast_raw))
+
+puttalam_world_crop <- st_crop(coast_raw, puttalam_world_crs) %>% ## crop to puttalam extent
+  filter(FID %in% c(153735)) %>% 
+    mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
 mapview(puttalam_world_crop)
 
-puttalam_crop <- as(puttalam_world_crop, "Spatial")
-plot(puttalam_crop)
+p_meters <- st_transform(puttalam_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(p_meters)
+
+buff <- st_buffer(p_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(puttalam_world_crop))
+mapview(buffer_outline_fixed)
+
+sri_lanka <- ne_countries(scale = 10, country = "Sri Lanka", returnclass = "sf")
+mapview(sri_lanka)
+
+linestring_fix <- st_difference(buffer_outline_fixed, sri_lanka) ## now grab only the outline 
+mapview(linestring_fix)
+
+puttalam_crop <- as(linestring_fix, "Spatial")
 mapview(puttalam_crop)
 
-puttalam_points_lines <- sample.line(puttalam_crop, n = 1344) ## equally place the number of farms along the coastline 
+puttalam_points_lines <- sample.line(puttalam_crop, n = 1361) ## equally place the number of farms along the coastline 
 class(puttalam_points_lines)
@@
 
-puttalam_points <- st_as_sf(puttalam_points_lines)
+puttalam_points <- st_as_sf(puttalam_points_lines) %>%
+  mutate(new_id = 1:1361) %>%
+  filter(new_id %in% c(230:1360, 1:194, 199:217))
 mapview(puttalam_points)
@@
 
-```
-
-```{r, evalute = F}
-
-# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
-# 
-#  TWN_shp <- gadm %>%
-#   filter(GID_0 == "TWN") %>%
-#   st_transform(., food_crs) %>%
-#   mutate(Region = 1)
-#  mapview(TWN_shp)
-# 
-# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
-# 
-# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
-# 
-# 
-# plot(fake_raster)
-# plot(twn_reg_ras)
-# 
-# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-# 
-# 
-# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-# 
-# twn_spatial <- as(TWN_shp, "Spatial")
-# 
-# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
-# 
-# plot(twn_coast)
-# cellStats(twn_coast, "sum") #464.63
-# 
-# # filter to include >0 <1, o.w. NA
-# 
-# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
-#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
-#   mutate(iso3c = "TWN") %>%
-#   dplyr::select(lon=x, lat=y, iso3c)
-# 
-# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_twn)
-# 
-# 
-# write_csv(twn_coast_df, here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
-# 
-# 
-# twn <- read_csv(here::here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
-# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_twn)
 ```

### 2021-02-16 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
fixed coastal buffer for all countries that needed it

@@
 
-japan_crop <- as(japan_world_crop, "Spatial")
+j_meters <- st_transform(japan_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(j_meters)
 
-japan_points_lines <- sample.line(japan_crop, n = 92) ## equally place the number of farms along the coastline 
+buff <- st_buffer(j_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(japan_world_crop))
+
+japan <- ne_countries(scale = 10, country = "Japan", returnclass = "sf")
+
+linestring_fix <- st_difference(buffer_outline_fixed, japan) ## now grab only the outline 
+mapview(linestring_fix)
+
+japan_crop <- as(buffer_outline_fixed, "Spatial")
+
+japan_points_lines <- sample.line(japan_crop, n = 190) ## equally place the number of farms along the coastline 
 class(japan_points_lines)
@@
 
-japan_points <- st_as_sf(japan_points_lines)
+japan_points <- st_as_sf(japan_points_lines) %>%
+  mutate(new_id = 1:190) %>%
+  filter(!(new_id %in% c(2, 95, 73, 67, 62, 56, 48, 47, 33,  32, 31, 29, 23, 12, 9,  93:112, 116, 118, 121, 123:126, 129:140, 124:145, 148:167, 171:174, 176, 178:190)))
 mapview(japan_points)

### 2021-02-17 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed philippines shrimp points... should probably standardize the distance from coast, but for now this will do... especially since we are going to change it

@@
 # 
-# linestring_fix <- st_difference(buffer_outline_fixed, philly) ## now grab only the outline 
+# p_meters2 <- st_transform(philly2, crs = 7801) ## transform to a crs that can buffer in meters
+# mapview(p_meters2)
+# 
+# buff2 <- st_buffer(p_meters2, dist = 9000)
+# mapview(buff2)
+# intersection_fixed <- st_transform(buff2, crs = crs(philly_world_crop))
+# mapview(intersection_fixed)
+# 
+# linestring_fix <- st_difference(buffer_outline_fixed, intersection_fixed) ## now grab only the outline
 # mapview(linestring_fix)
 
-philly_crop <- as(philly_world_crop, "Spatial")
+p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters
+mapview(p_meters)
+
+buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+philly_crop <- as(buff, "Spatial")
 mapview(philly_crop)
 
-philly_points_lines <- sample.line(philly_crop, n = 2) ## equally place the number of farms along the coastline 
+fix <- as(philly_crop, "SpatialLinesDataFrame")
+class(fix)
+mapview(fix)
+
+philly_points_lines <- sample.line(fix, n = 80) ## equally place the number of farms along the coastline 
 class(philly_points_lines)
@@
 
-philly_points <- st_as_sf(philly_points_lines)
+philly_points <- st_as_sf(philly_points_lines) %>%
+  mutate(new_id = 1:560)
 mapview(philly_points)
 
-## Now filter out the points that fall outside of 271
-philly_points_final <- philly_points[1:271,]
-mapview(philly_points_final)
-
-phl_pts <- st_centroid(philly_points_final)
+philly_points_fix <- philly_points %>%
+  filter(new_id %in% c(241:285, 1:47, 161:201, 321:361, 481:523, 401:446, 81:123)) %>%
+  filter(!(new_id %in% c(23:27, 32, 184, 298, 300, 303, 273, 280, 63, 57, 242:244, 88, 79, 123, 112, 125, 127, 153, 424:427, 90, 496:497, 198, 193, 191, 182, 170, 515:516, 328, 276, 9, 168:170, 82)))
+
+mapview(philly_points_fix)
+
+# ## Now filter out the points that fall outside of 271
+# philly_points_final <- philly_points[1:271,]
+# mapview(philly_points_final)
+
+phl_pts <- st_centroid(philly_points_fix)
 

### 2021-02-17 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
added and fixed subregions. Fixed some other classifications too

@@
 farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
-                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014)) %>%
+                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014),
+                        subregion = c("Alicante", "Almeria", "Asturias", "Baleares", "Cadiz", "Cantabria", "Castellon", "Gerona", "Granada", "La Coruna", "Las Palmas", "Malaga", "Pontevedra", "Santa Cruz de Tenerife", "Tarragona", "Valencia", "Vizcaya")) %>%
   mutate(iso3c = "ESP") %>%
@@
 
-OLD WAY: 
-```{r}
-
-# gadm <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/manipulated_data/GADM36/gadm36molcountries_simp.shp")
-# plot(gadm)
-# 
-#  TWN_shp <- gadm %>%
-#   filter(GID_0 == "TWN") %>%
-#   st_transform(., food_crs) %>%
-#   mutate(Region = 1)
-#  mapview(TWN_shp)
-# 
-# st_write(TWN_shp, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.shp")
-# 
-# twn_reg_ras <- fasterize::fasterize(TWN_shp, fake_raster, fun = "sum")
-# 
-# 
-# plot(fake_raster)
-# plot(twn_reg_ras)
-# 
-# writeRaster(twn_reg_ras, "/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-# 
-# 
-# twn_reg_ras <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/taiwan/taiwan.tif")
-# 
-# twn_spatial <- as(TWN_shp, "Spatial")
-# 
-# twn_coast <- rasterize(twn_spatial, twn_reg_ras, getCover = TRUE)
-# 
-# plot(twn_coast)
-# cellStats(twn_coast, "sum") #464.63
-# 
-# # filter to include >0 <1, o.w. NA
-# 
-# twn_coast_df <- as.data.frame(twn_coast, xy=TRUE) %>%
-#   dplyr::filter(layer <1 & layer >0) %>% ## filter out anything not on taiwan coast
-#   mutate(iso3c = "TWN") %>%
-#   dplyr::select(lon=x, lat=y, iso3c)
-# 
-# farms_twn <-  st_as_sf(twn_coast_df, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_twn)
-# 
-# 
-# write_csv(twn_coast_df, here::here("marine/bivalve/bivalve_farms/data/farm_sites/farms_twn.csv"))
-# 
-# 
-# twn <- read_csv(here::here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))
-# farms_twn <-  st_as_sf(twn, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_twn)
-```
-
 ## French Polynesia
@@
 ```{r}
-# world <- ne_coastline(scale = 10) #world map with 10m resolution
-# plot(world)
 
@@
 mapview(kerala_state)
-plot(kerala_state)
-
-# world <- st_as_sf(world)
 
@@
 mapview(buff)
-plot(buff)
 
@@
 kerala_state_crop <- as(linestring_fix, "Spatial")
-plot(kerala_state_crop)
 mapview(kerala_state_crop)
@@
   mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
+  mutate(action_needed = "Allocate spatially") %>%
+  mutate(subregion = "Kerala")
 
@@
 
-# world <- ne_coastline(scale = 110) #world map with 110m resolution
-# plot(world)
-
-# world <- st_as_sf(world)
-
 sta_catarina_world_crs <- st_transform(sta_catarina, crs(coast_raw))
@@
 mapview(linestring_fix)
-plot(sta_catarina_world_crop)
 mapview(sta_catarina_world_crop)
@@
 sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 24) ## equally place the number of farms along the coastline
-class(sta_catarina_points_lines)
-plot(sta_catarina_points_lines)
 
@@
   mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
+  mutate(action_needed = "Allocate spatially") %>%
+  mutate(subregion = "Santa Catarina")
 
@@
 
+samar_points_final <- samar_points %>%
+  mutate(subregion = "Samar")
+
+negros_points_final <- negros_points %>%
+  mutate(subregion = "Negros Occidental")
+
+capiz_points_final <- capiz_points %>%
+  mutate(subregion = "Capiz")
+
 ## bind all three states together
-all_points <- rbind(samar_points, negros_points, capiz_points)
+all_points <- rbind(samar_points_final, negros_points_final, capiz_points_final)
 mapview(all_points)
@@
 
+phl_pts_rgn <-  st_transform(phl_pts, crs = "+init=epsg:4326") %>%
+  dplyr::select(subregion)
+
 farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
@@
 
-farms_phl_final <- farms_phl %>%
+farms_phl_rgn <- cbind(farms_phl, phl_pts_rgn)
+
+farms_phl_final <- farms_phl_rgn %>%
   mutate(iso3c = "PHL") %>%
   mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
+  mutate(action_needed = "Allocate spatially") %>%
+  dplyr::select(-geometry)
 

### 2021-02-17 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
added and fixed subregions. Fixed some other classifications too

@@
   mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(action_needed = "state/province based suitability",
+         subregion = c("Khulna", "Chittagong"))
 
@@
   mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(action_needed = "state/province based suitability",
+         subregion = c("Ayeyarwaddy", "Rakhine"))
 
@@
                         lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
-                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
+                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), subregion = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
   mutate(iso3c = "VNM") %>%
@@
   left_join(provinces, by = "Province") %>%
-  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
+  dplyr::select(lat, lon, prod, "subregion" = "Province") %>%
   mutate(iso3c = "PHL") %>%

### 2021-02-17 marine/explore_spatial_allocation.Rmd
added and fixed subregions. Fixed some other classifications too

@@
   mutate(group = "bivalve") %>%
-  dplyr::select(-X1, -subregion)
+  dplyr::select(-X1)
 
@@
   mutate(group = "marine_fish_general") %>%
-  dplyr::select(-rgn_production, -subrgn_name)
+  dplyr::select(-rgn_production)
 
 salmon <- read_csv(here::here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv")) %>%
-  mutate(group = "salmon") %>%
-  dplyr::select(-subregion)
+  mutate(group = "salmon")
 
@@
   mutate(group = "crustaceans") %>%
-  dplyr::select(-prod, -sub_rgn)
+  dplyr::select(-prod)
 
 tuna <- read_csv(here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon_data_quality.csv")) %>%
-  mutate(group = "tuna")
+  mutate(group = "tuna") %>%
+  mutate(subregion = NA)
 
@@
 
+n_countries_test <- all_farms_sf %>%
+  filter(data_quality == 3) %>%
+  group_by(iso3c, action_needed, data_quality, group, subregion) %>%
+  summarise(count = n())
+
 n_countries_no_data <- n_countries %>%
@@
   dplyr::filter(data_quality == 2)
-sum(n_states_no_data$n_countries) # 14
+sum(n_states_no_data$n_countries) # 10
 ## 14 countries/species group combos that will need subregional spatial allocation according to our rules (7-10km to port, depth requirements)

### 2021-02-17 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
added and fixed subregions. Fixed some other classifications too

@@
   mutate(iso3c = "ARE") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
 mapview(tunisia)
-
-# world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
-# plot(world)
-# class(world)
-
-# world <- st_as_sf(world)
 
@@
 tunisia_points_lines <- sample.line(tunisia_crop, n = 25) ## equally place the number of farms along the coastline
-class(tunisia_points_lines)
-plot(tunisia_points_lines)
 
@@
   mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
+  mutate(action_needed = "Allocate spatially") %>%
+  mutate(subregion = "Monastir")
 
@@
                         rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
-                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
+                        subregion = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
   mutate(iso3c = "EGY") %>%
@@
   mutate(iso3c = "MYS") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask") %>%
+  mutate(subregion = c("Sempang, Malacca", "Rompin, Pahang", "Permatang Pauh, Pahang", "Rompin, Pahang", "Sempang, Malacca"))
 
@@
   mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(action_needed = "state/province based suitability") %>%
+  mutate(subregion = c("Prey Nob", "Stoeng Hav", "Thomnob Rolork"))
 

### 2021-02-17 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
added and fixed subregions. Fixed some other classifications too

@@
 farms_turkey <- data.frame(lon=c(35.193, 35.168, 37.776,  37.776, 37.788, 37.789, 37.789, 37.789, 39.812, 39.803, 40.562, 40.558),
-                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
+                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036),
+                    subregion = c("Sinop", "Sinop", "Persembe", "Persembe", "Persembe", "Persembe", "Persembe", "Persembe", "Sana", "Sana", "Rize", "Rize")) %>%
   mutate(iso3c = "TUR") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially")
 

### 2021-02-17 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
added and fixed subregions. Fixed some other classifications too

@@
                         lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
-                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
+                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200),
+                        subregion = c("Pará", "Maranhão", "Piauí", "Ceará", "Rio Grande do Norte", "Paraíba", "Pernambuco", "Alagoas", "Sergipe", "Bahia", "Paraná", "Santa Catarina")) %>%
   mutate(iso3c = "BRA") %>%
@@
                         lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
-                        area_ha = c(1516, 459, 26762, 6388)) %>%
+                        area_ha = c(1516, 459, 26762, 6388), subregion = c("Kampot", "Kep", "Koh Kong", "Preah Sihanouk")) %>%
   mutate(iso3c = "KHM") %>%
@@
 
-guana_punta <- provinces  %>%
-  dplyr::filter(NAME_1 %in% c("Guanacaste", "Puntarenas"))
-
-mapview(guana_punta)
-
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-
-# world <- st_as_sf(world)
-
-costa_world_crs <- st_transform(guana_punta, crs(coast_raw))
-
-costa_world_crop <- st_crop(coast_raw, costa_world_crs) %>% ## crop to costa rica extent 
-  filter(FID %in% c(245909:245926)) %>% ## filter for the correct coastline 
+guana <- provinces  %>%
+  dplyr::filter(NAME_1 %in% c("Guanacaste"))
+
+punta <- provinces  %>%
+  dplyr::filter(NAME_1 %in% c("Puntarenas"))
+
+mapview(guana)
+mapview(punta)
+
+## First do Guanacaste
+guana_world_crs <- st_transform(guana, crs(coast_raw))
+
+guana_world_crop <- st_crop(coast_raw, guana_world_crs) %>% ## crop to costa rica extent 
+  filter(FID %in% c(245921:245926)) %>% ## filter for the correct coastline 
   mutate(new_id = 1) %>%
@@
   ungroup()
-mapview(costa_world_crop)
-
-c_meters <- st_transform(costa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(c_meters)
-
-buff <- st_buffer(c_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(guana_world_crop)
+
+g_meters <- st_transform(guana_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(g_meters)
+
+buff <- st_buffer(g_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
 mapview(buff)
@@
 ## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(costa_world_crop))
+buffer_outline_fixed <- st_transform(linestring, crs = crs(guana_world_crop))
 mapview(buffer_outline_fixed)
@@
 
-costa_crop <- as(linestring_fix, "Spatial")
-mapview(costa_crop)
-
-costa_points_lines <- sample.line(costa_crop, n = 106) ## equally place the number of farms along the coastline
-
-costa_points <- st_as_sf(costa_points_lines) %>%
-  mutate(new_id = 1:318) %>%
-  filter(new_id %in% c(1:88, 105:106))
-mapview(costa_points)
-
-cri_pts <- st_centroid(costa_points)
-
-cri_pts_latlon <- st_transform(cri_pts, crs = "+init=epsg:4326") %>%
+guana_crop <- as(linestring_fix, "Spatial")
+mapview(guana_crop)
+
+guana_points_lines <- sample.line(guana_crop, n = 55) ## equally place the number of farms along the coastline
+
+guana_points <- st_as_sf(guana_points_lines) %>%
+  mutate(new_id = 1:55) %>%
+  filter(new_id %in% c(5:49))
+mapview(guana_points)
+
+guana_pts <- st_centroid(guana_points)
+
+guana_pts_latlon <- st_transform(guana_pts, crs = "+init=epsg:4326") %>%
   dplyr::select(geometry)
 
-farms_cri <- data.frame(do.call(rbind, st_geometry(cri_pts_latlon)))
-names(farms_cri) <- c("lon", "lat")
-
-farms_cri_final <- farms_cri %>%
+farms_guana <- data.frame(do.call(rbind, st_geometry(guana_pts_latlon)))
+names(farms_guana) <- c("lon", "lat")
+
+farms_guana_final <- farms_guana %>%
   mutate(iso3c = "CRI") %>%
   mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_cri <-  st_as_sf(farms_cri, coords = c("lon", "lat"), 
+  mutate(action_needed = "Allocate spatially") %>%
+  mutate(subregion = "Guanacaste")
+
+## Now do puntarenas
+punta_world_crs <- st_transform(punta, crs(coast_raw))
+
+punta_world_crop <- st_crop(coast_raw, punta_world_crs) %>% ## crop to costa rica extent 
+  filter(FID %in% c(245909:245917, 245919:245920)) %>% ## filter for the correct coastline 
+  mutate(new_id = 1) %>%
+  group_by(new_id) %>%
+  summarise(geometry = st_union(geometry)) %>%
+  ungroup()
+mapview(punta_world_crop)
+
+p_meters <- st_transform(punta_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
+mapview(p_meters)
+
+buff <- st_buffer(p_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
+mapview(buff)
+
+linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
+mapview(linestring)
+
+## now reproject back to original 
+buffer_outline_fixed <- st_transform(linestring, crs = crs(punta_world_crop))
+mapview(buffer_outline_fixed)
+
+buffer_outlined_fixed2 <- buffer_outline_fixed[1, ]
+mapview(buffer_outlined_fixed2)
+
+costa_rica <- ne_countries(scale = 10, country = "Costa Rica", returnclass = "sf")
+mapview(costa_rica)
+
+linestring_fix <- st_difference(buffer_outlined_fixed2, costa_rica) ## now grab only the outline 
+mapview(linestring_fix)
+
+punta_crop <- as(linestring_fix, "Spatial")
+mapview(punta_crop)
+
+punta_points_lines <- sample.line(punta_crop, n = 60) ## equally place the number of farms along the coastline
+
+punta_points <- st_as_sf(punta_points_lines) %>%
+  mutate(new_id = 1:60) %>%
+  filter(new_id %in% c(2:46))
+mapview(punta_points)
+
+punta_pts <- st_centroid(punta_points)
+
+punta_pts_latlon <- st_transform(punta_pts, crs = "+init=epsg:4326") %>%
+  dplyr::select(geometry)
+
+farms_punta <- data.frame(do.call(rbind, st_geometry(punta_pts_latlon)))
+names(farms_punta) <- c("lon", "lat")
+
+farms_punta_final <- farms_punta %>%
+  mutate(iso3c = "CRI") %>%
+  mutate(data_quality = 3) %>%
+  mutate(action_needed = "Allocate spatially") %>%
+  mutate(subregion = "Puntarenas")
+
+farms_cri_final <- rbind(farms_punta_final, farms_guana_final)
+
+## visualize it 
+farms_cri <-  st_as_sf(farms_cri_final, coords = c("lon", "lat"), 
                  crs = crs(gadm_latlon), agr = "constant")
@@
                         lon=c(-89.014470, -87.863771),
-                        area_ha = c(8.2, 50)) %>%
+                        area_ha = c(8.2, 50),
+                        subregion = c("La Paz", "La Unión")) %>%
   mutate(iso3c = "SLV") %>%
@@
                         lon=c(99.826952, 102.463536, 110.210032, 103.43838831493285, 102.721589, 103.328932, 102.82739417198427, 111.183470, 100.704595, 100.975557, 103.446051),
-                        area_ha =mys_area) %>%
+                        area_ha =mys_area,
+                        subregion = c("Ayer Hangat, Kedah", "Sebatu, Malacca", "Kuching, Sarawak", "Pekan, Pahang", "Setiu, Terengganu", "Marang, Terengganu", "Setiu, Terengganu", "Tanjung Manis, Sarawak", "Rungkup, Perak", "Sabak, Selangor", "Pekan, Pahang")) %>%
   mutate(iso3c = "MYS") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
+  mutate(data_quality = 4) %>%
+  mutate(action_needed = "Land mask")
 
@@
                         lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
-                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
+                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA ), 
+                        subregion = c("Rahkine", "Ayeyarwaddy", "Yangon", "Mon", "Thaninthary")) %>%
   mutate(iso3c = "MMR") %>%
@@
 mapview(philly_world_crop)
-
-# philly_world_crop <- philly_world_crop %>%
-#   mutate(new_id = 1) %>%
-#   group_by(new_id) %>%
-#   summarise(geometry = st_union(geometry)) %>%
-#   ungroup()
-# 
-# mapview(philly_world_crop)
-# 
-# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters
-# mapview(p_meters)
-# 
-# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-# mapview(buff)
-# 
-# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline
-# mapview(linestring)
-# 
-# ## now reproject back to original
-# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
-# mapview(buffer_outline_fixed)
-# 
-# 
-# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
-# mapview(philly2)
-# 
-# p_meters2 <- st_transform(philly2, crs = 7801) ## transform to a crs that can buffer in meters
-# mapview(p_meters2)
-# 
-# buff2 <- st_buffer(p_meters2, dist = 9000)
-# mapview(buff2)
-# intersection_fixed <- st_transform(buff2, crs = crs(philly_world_crop))
-# mapview(intersection_fixed)
-# 
-# linestring_fix <- st_difference(buffer_outline_fixed, intersection_fixed) ## now grab only the outline
-# mapview(linestring_fix)
 
@@
 ## Start with Batticaloa
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-
-# world <- st_as_sf(world)
 
@@
 farms_bat_lka_final <- farms_bat_lka %>%
-  mutate(area_ha = 2.583333)
+  mutate(area_ha = 2.583333) %>%
+  mutate(subregion = "Batticaloa")
 
@@
 ## Now do puttalam
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-# 
-# world <- st_as_sf(world)
-
 puttalam_world_crs <- st_transform(puttalam_shp, crs(coast_raw))
@@
 
-puttalam_points_lines <- sample.line(puttalam_crop, n = 1361) ## equally place the number of farms along the coastline 
-class(puttalam_points_lines)
-plot(puttalam_points_lines)
+puttalam_points_lines <- sample.line(puttalam_crop, n = 1800) ## equally place the number of farms along the coastline
 
 puttalam_points <- st_as_sf(puttalam_points_lines) %>%
-  mutate(new_id = 1:1361) %>%
-  filter(new_id %in% c(230:1360, 1:194, 199:217))
+  mutate(new_id = 1:1800) %>%
+  filter(new_id %in% c(457:1800))
 mapview(puttalam_points)
@@
 farms_put_lka_final <- farms_put_lka %>%
-  mutate(area_ha = 3.348214)
+  mutate(area_ha = 3.348214)  %>%
+  mutate(subregion = "Puttalam")
 

### 2021-02-22 marine/explore_spatial_allocation.Rmd
finished calculating distance to shore for each mariculture practice

@@
 source(here::here("_spatial/template_raster.R"))
+
+gordon_coast <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline_st.shp"))
 ```
@@
 
+## find average distance to shore per each spp group
+
+## do bivalves 
+datalist_biv = list()
+
+  group_df <- all_farms_sf %>%
+    filter(action_needed == "Land mask") %>%
+    filter(group == "bivalve")
+
+  num_rows <- nrow(group_df)
+
+  group_df_final <- group_df %>%
+    mutate(row_number = 1:num_rows) %>%
+    filter(row_number > 2322) ## now delete the rows that have already been completed
+
+num_rows_final <- group_df_final$row_number
+
+for(i in num_rows_final){
+
+    # i = 1411 # testing
+  final_df <- group_df_final %>%
+    filter(row_number == i)
+
+  datalist_biv[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))
+
+}
+
+dist_data_biv = do.call(rbind, datalist_biv)
+
+## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
+st_write(dist_data_biv, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/bivalve_dist.shp"))
+
+## do tunas 
+datalist_tuna = list()
+
+  group_df <- all_farms_sf %>%
+    filter(action_needed == "Land mask") %>%
+    filter(group == "tuna")
+
+  num_rows <- nrow(group_df)
+
+  group_df_final <- group_df %>%
+    mutate(row_number = 1:num_rows) #%>%
+    #filter(row_number > 2322) ## now delete the rows that have already been completed
+
+num_rows_final <- group_df_final$row_number
+
+for(i in num_rows_final){
+
+    # i = 1411 # testing
+  final_df <- group_df_final %>%
+    filter(row_number == i)
+
+  datalist_tuna[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))
+
+}
+
+dist_data_tuna = do.call(rbind, datalist_tuna)
+
+## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
+st_write(dist_data_tuna, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/tuna_dist.shp"))
+
+## do marine fish  
+datalist_mf = list()
+
+  group_df <- all_farms_sf %>%
+    filter(action_needed == "Land mask") %>%
+    filter(group == "marine_fish_general")
+
+  num_rows <- nrow(group_df)
+
+  group_df_final <- group_df %>%
+    mutate(row_number = 1:num_rows) #%>%
+    #filter(row_number > 2322) ## now delete the rows that have already been completed
+
+num_rows_final <- group_df_final$row_number
+
+for(i in num_rows_final){
+
+    # i = 1411 # testing
+  final_df <- group_df_final %>%
+    filter(row_number == i)
+
+  datalist_mf[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))
+
+}
+
+dist_data_mf = do.call(rbind, datalist_mf)
+
+## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
+st_write(dist_data_mf, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/marine_fish_general_dist.shp"))
+
+## do salmon 
+datalist_salmon = list()
+
+  group_df <- all_farms_sf %>%
+    filter(action_needed == "Land mask") %>%
+    filter(group == "salmon")
+
+  num_rows <- nrow(group_df)
+
+  group_df_final <- group_df %>%
+    mutate(row_number = 1:num_rows)#  %>%
+# filter(row_number < 2345, row_number > 2235) ## now delete the rows that have already been completed
+
+num_rows_final <- group_df_final$row_number
+
+for(i in num_rows_final){
+
+    # i = 2235 # testing
+  final_df <- group_df_final %>%
+    filter(row_number == i)
+
+  datalist_salmon[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))
+
+}
+
+dist_data_salmon = do.call(rbind, datalist_salmon)
+## ~100 per hour = there are 3400 rows... = 34 hours to run....
+
+## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
+st_write(dist_data_salmon, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/salmon_dist.shp"))
+
+## do shrimp
+datalist_shrimp = list()
+
+  group_df <- all_farms_sf %>%
+    filter(action_needed == "Land mask") %>%
+    filter(group == "shrimp")
+
+  num_rows <- nrow(group_df)
+
+  group_df_final <- group_df %>%
+     mutate(row_number = 1:num_rows)
+    # filter(row_number > 3464) ## now delete the rows that have already been completed
+
+num_rows_final <- group_df_final$row_number
+
+for(i in num_rows_final){
+
+    # i = 1411 # testing
+  final_df <- group_df_final %>%
+    filter(row_number == i)
+
+  datalist_shrimp[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))
+
+}
+
+  dist_data_shrimp = do.call(rbind, datalist_shrimp)
+
+st_write(dist_data_shrimp, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/shrimp_dist.shp"))
+
+## there are no crustaceans that fall in that category
+```
+
+```{r}
 n_farms <- all_farms %>%

### 2021-02-22 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished distance to coast calcs. Fixed jersey bivalves so we aren't double counting

@@
 farms_all <- ASC_bivalve %>%
-  cbind(iso)
+  cbind(iso) %>%
+  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c))
 
@@
 
+ - UPDATE: This is not necessary. These companies are represented in the ASC data, but listed under the UK. I will fix this, so that we aren't double counting these farms.
+
 ```{r, evalute = F}
 
-farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
-                        lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
-  mutate(iso3c = "JEY") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))
-
-## visualize it 
-farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_jey)
+# farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
+#                         lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
+#   mutate(iso3c = "JEY") %>%
+#   mutate(data_quality = 4) %>%
+#   mutate(action_needed = "Land mask")
+# 
+# write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))
+# 
+# ## visualize it 
+# farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
+#                  crs = crs(gadm_latlon), agr = "constant")
+# 
+# mapview(farms_jey)
 

### 2021-02-22 marine/explore_spatial_allocation.Rmd
finished distance to coast calcs. Fixed jersey bivalves so we aren't double counting

--- 2021-02-17 marine/explore_spatial_allocation.Rmd
@@
 
+```
+
+```{r}
 n_farms <- all_farms %>%

### 2021-03-09 workflow/qualtiy_control_filters.R
having issues with spatialEco::sample.line(). Close to solving.

@@ -9,6 +9,7 @@
 #### load libraries and data ####
 #------------------------------------------------------------------------------#
 library(sf)
+library(spatialEco)
 library(tidyverse)
 library(raster)
 library(rgeos)
@@ -34,8 +35,8 @@ bathy_raw <- raster("/home/shares/clean-seafood/raw_data/bathymetry_data/full_ba
 bathy_raw2 <- bathy_raw2 %>% 
   projectRaster(to = fake_raster)
 
-bathy_raw2 <- bathy_raw
-bathy_raw <- bathy_raw2
+#bathy_raw2 <- bathy_raw
+#bathy_raw <- bathy_raw2
 bathy_raw[bathy_raw >    1] <- NA # replace all values over 1m asl as NA
 bathy_raw[bathy_raw < -250] <- NA # replace all values under 250 bsl as NA
 bathy_raw[!is.na(bathy_raw)] <- 1 # replace all suitable depths with 1
@@ -47,8 +48,7 @@ all_farms_raw   <-
               mutate(type = "bivalve") %>% 
               select(-X1),
             read_csv("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv") %>% 
-              mutate(type = "crustacean") %>% 
-              rename(subregion = sub_rgn),
+              mutate(type = "crustacean"),
             read_csv("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv") %>% 
               mutate(type = "salmon"),
             read_csv("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon_data_quality.csv") %>% 
@@ -75,10 +75,24 @@ need_national_allocation <- all_farms_raw %>%
   filter(action_needed == "Allocate spatially", 
          is.na(subregion))
 
+# stucture of the loop for each country 
+# 1. Get the country ranges land-eez-bbox
+# 2. Calculate the dist to shore, port, and pull depth
+# 3. Create final acceptable range rasters
+# 4. Create buffered coast line
+
+# layers of data needed gadm_full, eez_sf, coastline, 
+
 # generate prediction points for each national allocation area
 for (i in 1:unique(need_national_allocation$iso3c)) {
   
[…]

### 2021-03-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
made a dataset for number of farms modeling

@@
   cbind(iso) %>%
-  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c))
+  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c)) ## fix Jersey
 
@@
 If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
  - Lastly, if there is no evidence of marine bivalve farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
@@
 Source: 
-HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM HOLAS II Dataset: Shellfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
 Source:
-HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM HOLAS II Dataset: Shellfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
 Source: 
-Shellfish Hatcheries - Coastal Resource Information Management System (CRIMS) , 2019.
+Shellfish Hatcheries - Coastal Resource Information Management System (CRIMS), 2019.
 Ministry of Forests, Lands, Natural Resource Operations and Rural Development.
@@
 ```{r}
+# library(jsonlite)
+# test <- fromJSON("https://data.novascotia.ca/resource/h57h-p9mm.json")
+
 ## read shapefile
@@
 https://servicio.pesca.mapama.es/acuivisor/
+
  - This is a map of all aquaculture facilities in Spain.
@@
 Source: 
-Acuivisor, 2019. . Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/
+Acuivisor, 2019. Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/
 
@@
 
-## Jersey 
- - Government of Jersey: https://www.gov.je/SiteCollectionDocuments/Industry%20and%20finance/ID%20Mollusc%20farms%20registered%20businesses%20page%201.pdf
-  - https://www.gov.je/SiteCollectionDocuments/Industry%20and%20finance/ID%20Molluscs%20farms%20registered%20businesses%20page%202%2020181030%20DM.pdf
-
- - 5 licensed farms (only including "mollusc farm open"): Locations estimated from maps and addresses listed 
- - Jersey Oyster Company Limited: 49.172680993306905, -2.0255193115109957
- - Seymour Oyster Company Ltd: 49.220095937386375, -2.0215887506551438
- - La Rocque Fisheries Limited: 49.169912669200976, -2.0230904378277916
- - Jersey Sea Farms: 49.242435452408536, -2.060618920921559
- - Island Dived Scallops: 49.20656011166959, -2.0158403231425996
-
-Source: 
-Fish and shellfish farming, 2020.
-.
-Government of Jersey: Information and public services for the Island of Jersey.
-[Accessed December 4, 2020]  https://www.gov.je/Industry/FarmingFishing/Fishing/Pages/FishFarming.aspx
-
- - UPDATE: This is not necessary. These companies are represented in the ASC data, but listed under the UK. I will fix this, so that we aren't double counting these farms.
-
-```{r, evalute = F}
-
-# farms_jey <- data.frame(lat = c(49.172680993306905, 49.220095937386375, 49.169912669200976, 49.242435452408536, 49.20656011166959),
-#                         lon = c(-2.0255193115109957, -2.0215887506551438, -2.0230904378277916, -2.060618920921559, -2.0158403231425996)) %>%
-#   mutate(iso3c = "JEY") %>%
-#   mutate(data_quality = 4) %>%
-#   mutate(action_needed = "Land mask")
-# 
-# write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_jey.csv"))
-# 
-# ## visualize it 
-# farms_jey <-  st_as_sf(farms_jey, coords = c("lon", "lat"), 
-#                  crs = crs(gadm_latlon), agr = "constant")
-# 
-# mapview(farms_jey)
-
-```
-
 ## Guernsey 
@@
 Fishing and Aquaculture, 2020.
-.
 Government of the States of Guernsey.
@@
 ## Taiwan
-- I can't find any information on the locations of shellfish farms in Taiwan, however, they have a lot of production. I will randomly place a point in the Qigu lagoon (see article). 
+- I can't find any information on the locations of shellfish farms in Taiwan. I will randomly place a point in the Qigu lagoon (see article). 
  - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/
@@
 Source:
-NASO aquaculture maps collection , 2010.
-.
+NASO aquaculture maps collection, 2010.
 Food and Agriculture Organization of the United Nations.
@@
 Marine fish culture, pond fish culture and oyster culture, n.d.
-.
 Agriculture, Fisheries, and Conservation Department; The Government of the Hong Kong Special Administrative Region.

### 2021-03-09 marine/explore_spatial_allocation.Rmd
made a dataset for number of farms modeling

@@
 
-Read in and summarise all data quality farm data 
+Read in and combine all farm data 
 ```{r}
@@
 
+Read in and combine all FAO tonnage data per country
+```{r}
+bivalves_tonnes <- read_csv(here::here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
+  mutate(group = "bivalve")
+
+shrimp_tonnes <- read_csv(here::here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
+  mutate(group = "shrimp") %>%
+  filter(year == 2017)
+
+marine_fish_tonnes <- read_csv(here::here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
+  mutate(group = "marine_fish_general") %>%
+  filter(year == 2017)
+
+salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
+  mutate(group = "salmon") %>%
+  filter(year == 2017)
+
+crustaceans_tonnes <- read_csv(here::here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
+  mutate(group = "crustaceans") %>%
+  filter(year == 2017)
+
+tuna_tonnes <- read_csv(here::here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
+  mutate(group = "tuna") %>%
+  filter(year == 2017)
+
+all_species_country_tonnes <- rbind(bivalves_tonnes, shrimp_tonnes, marine_fish_tonnes, salmon_tonnes, crustaceans_tonnes, tuna_tonnes)
+```
+
 ```{r}
@@
   summarise(n_farms = n()) %>%
-  ungroup() %>%
-  group_by(iso3c) %>%
-  mutate(avg_quality = mean(data_quality)) %>%
   ungroup()
@@
 
+## make a dataset with the country, species type (farm type), tonnage, and # of farms, for those that score data quality %in% c(3,4,5)
+sum(all_species_country_tonnes$fao_tonnes_production) # 29623515
+
+n_farms_final <- n_farms %>%
+  filter(data_quality %in% c(3,4,5)) %>%
+  group_by(iso3c, group) %>%
+  summarise(n_farms = sum(n_farms)) %>%
+  left_join(all_species_country_tonnes, by = c("iso3c", "group")) %>%
+  dplyr::select(iso3c, country, year, group, n_farms, fao_tonnes_production)
+sum(n_farms_final$fao_tonnes_production) # 26812832
+
+n_farms_tonnes_no_info <- n_farms %>%
+  filter(data_quality %in% c(1, 2)) %>%
+  group_by(iso3c, group) %>%
+  summarise(n_farms = sum(n_farms)) %>%
+  left_join(all_species_country_tonnes, by = c("iso3c", "group")) %>%
+  mutate(n_farms = NA)
+sum(n_farms_tonnes_no_info$fao_tonnes_production) # 2810682
+
+26812832 + 2810682 # 29623514 # perfect
+
+n_farms_final_final <- rbind(n_farms_final, n_farms_tonnes_no_info)
+sum(n_farms_final_final$fao_tonnes_production) # 29623515
+
+## save n_farms_final to use to make a model of farms and production
+write.csv(n_farms_final_final, "data/n_farms_production_data.csv", row.names = FALSE)
+
+```
+
+Now let's do some exploration:
+
+```{r}
 n_countries <- n_farms %>%
@@
   mutate(percent = n_countries/total_countries)
+
+test2 <- n_farms %>%
+  group_by(data_quality) %>%
+  summarise(n_countries = n())
+
+countries <- data.frame(iso3c = unique(all_farms_sf$iso3c)) %>%
+  mutate(country = countrycode(iso3c, origin = 'iso3c', destination = 'country.name'))
 

### 2021-03-09 workflow/qualtiy_control_filters.R
got random sampling of the line to work!

@@ -91,8 +91,12 @@ for (i in 1:unique(need_national_allocation$iso3c)) {
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[7]
   
+  the_farm_number <- all_farms_raw %>% 
+    filter(iso3c == this_iso3,
+           data_quality != 5) %>% 
+    nrow()
   
-  the_farm_number <- 100
+  
   
   this_country <- gadm_full %>% 
     filter(GID_0 == this_iso3) %>% 
@@ -167,68 +171,25 @@ for (i in 1:unique(need_national_allocation$iso3c)) {
     
   # 5 Create a buffered coastline
   this_coast_meters <- st_transform(this_coast, crs = 7801) %>% ## transform to a crs that can buffer in meters 
-    st_buffer(dist = 10000) %>% # buffer in meters
+    st_buffer(dist = 200) %>% # buffer in meters
     st_cast("MULTILINESTRING") %>% 
     st_transform(crs = crs(the_crs)) %>%  # 
-    st_difference(this_country)
+    st_difference(this_country) %>% 
+    mutate(info = "names")
   
+  ## create polygons of suitable rasters
   this_cell_polygons <- rasterToPolygons(suitability_rast)%>% 
     st_as_sf() %>% 
     st_union()%>% 
     sf::st_as_sf()
   
-  x_test <- st_intersection(this_coast_meters, this_cell_polygons) %>%  
-    as_Spatial() 
+  this_suitable_coast <- st_intersection(this_coast_meters, this_cell_polygons) %>% 
+    as_Spatial()
   
-  c <- length(x_test@lines[[1]]@Lines)
-  c_n <- c(1:c)
-  
-  x_lines <- SpatialLines(x_test@lines)#[[1]]@Lines)
-
+  # regularly sample points along line
+  this_farm_points <- sp::spsample(this_suitable_coast, n=the_farm_number, type = "regular") %>% 
+    sf::st_as_sf()
   
   
-  df <- data.frame(len = sapply(1:length(x_lines), function(i) gLength(x_lines[i, ])))
-  rownames(df) <- sapply(1:length(x_lines), function(i) x_lines@lines[[i]]@ID)
-  
-  y_test <- SpatialLinesDataFrame(x_lines, data = df )
-
-  
-  ## equally place the number of farms along
-  this_points_lines <- spatialEco::sample.line(y_test, 
[…]

### 2021-03-11 workflow/predict_farm_numbers.Rmd
working on raster issues

---
title: "get number of farms"
author: "Gordon Blasco"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(WDI)
library(countrycode)

raw <- read_csv("marine/data/n_farms_production_data.csv")

ready <- raw %>% 
  mutate(iso2c = purrr::map_chr(.x = iso3c, 
                           ~countrycode(sourcevar = .x, 
                                        origin = "iso3c", 
                                        destination = "iso2c")))

# helper functions
test <- possibly(countryname, NA_character_)

# pulls most recent information from the WDI call
get_most_recent_variable <- function(data){
 data %>% 
    filter(!is.na()) %>% 
    arrange(-year) %>% 
    slice(., 1) %>% 
    pull()

}

poss <- possibly(get_most_recent_variable, NA_real_)

```

pull WDI stats for each country
```{r}

wdi_info <- ready %>% 
  distinct(iso2c) %>% 
  mutate(wdi_data_pull = purrr::map(.x = iso2c, 
                               ~possibly(
                                 WDI(indicator= c("gdp_per_capita" = "NY.GDP.PCAP.KD",
                                                 "population" = "SP.POP.TOTL",
                                                 "literacy_rate" = "LO.PIAAC.LIT",
                                                 "life_expectancy"="SP.DYN.LE00.IN",
                                                 "GNI_PPP_per_cap" = "NY.GNP.PCAP.PP.KD",
                                                 "industrial_prod" = "IPTOTNSKD",
                                                 "greenhouse_gas_kt" = "EN.ATM.GHGT.KT.CE"),
                                    country=.x, 
                                    start=2010, end=2017), NA))
  )

wdi_test <- wdi_info %>% 
  mutate(

    gdp_final = map2_dbl(.x = GDP,
                         .y = c("gdp_per_capita", "population"),
                         ~poss(data = .x,
                               variable_name = .y))

  )

```

### 2021-03-11 workflow/qualtiy_control_filters.R

@@ -32,12 +32,12 @@ bathy_raw <- raster("/home/shares/clean-seafood/raw_data/bathymetry_data/full_ba
   #projectRaster(to = fake_raster,
                 #res = res(fake_raster))
 
-bathy_raw2 <- bathy_raw2 %>% 
+bathy_raw <- bathy_raw %>% 
   projectRaster(to = fake_raster)
 
 #bathy_raw2 <- bathy_raw
 #bathy_raw <- bathy_raw2
-bathy_raw[bathy_raw >    1] <- NA # replace all values over 1m asl as NA
+bathy_raw[bathy_raw >    10] <- NA # replace all values over 1m asl as NA
 bathy_raw[bathy_raw < -250] <- NA # replace all values under 250 bsl as NA
 bathy_raw[!is.na(bathy_raw)] <- 1 # replace all suitable depths with 1
 
@@ -86,7 +86,7 @@ need_national_allocation <- all_farms_raw %>%
 # generate prediction points for each national allocation area
 for (i in 1:unique(need_national_allocation$iso3c)) {
   
-  #1. Get country ranges
+  #1. Get the country ranges land-eez-bbox
   
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[7]
@@ -119,7 +119,7 @@ for (i in 1:unique(need_national_allocation$iso3c)) {
     bind_rows(this_eez)
   
   ## 1.d get bounding box
-  this_bbox <- st_bbox(this_eez)
+  this_bbox <- st_bbox(this_area)
   
   ## 1.e filter for ports and coast line of this country
   this_coast <- this_country %>%
@@ -140,6 +140,9 @@ for (i in 1:unique(need_national_allocation$iso3c)) {
   
   ## 2.a prep the coasts, ports, and eez to spatial points 
   this_raster_points <- as(this_eez_mask, "SpatialPoints")
+  
+  mapview(this_raster_points)
+  this_area_sp <- as(this_area, "Spatial")
   this_coast_sp <- as(this_coast, "Spatial")
   this_port_sp <- as(these_ports, "Spatial")
   
@@ -160,18 +163,22 @@ for (i in 1:unique(need_national_allocation$iso3c)) {
   dis_to_port_rast[!is.na(dis_to_port_rast[])]=this_dmin_port
   
   port_test_rast <- dis_to_port_rast
-  port_test_rast[port_test_rast >.5 ] <- NA
+  port_test_rast[port_test_rast >.2 ] <- NA
   
[…]

### 2021-03-15 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
checked over sources again

@@
 If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
  - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
@@
 Source:
-EMODnet Human Activities: Finfish production, 2019. [Accessed December 8, 2020] 
+EMODnet Human Activities: Marine Finfish Aquaculture, 2019. [Accessed December 8, 2020] 
 https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production

### 2021-03-15 workflow/predict_farm_numbers.Rmd
adding farm numbers, quality control fixes, as well as continent group information

@@
 library(tidyverse)
+library(janitor)
 library(tidymodels)
@@
 
-raw <- read_csv("marine/data/n_farms_production_data.csv")
+aq_info <- read_csv('/home/shares/clean-seafood/raw_data/FAO/production/CL_FI_COUNTRY_GROUPS.csv') %>% 
+  clean_names() %>% 
+  select(iso3_code, geo_region_group, continent_group, eco_class_group)
 
+raw <- read_csv("/home/blasco/github/aquaculture_mapping/marine/data/n_farms_production_data.csv") %>% 
+  left_join(aq_info, by = c('iso3c' = 'iso3_code'))
+
+aq_types <- raw %>% 
+  filter(!is.na(n_farms)) %>% 
+  mutate(tonnes_per_farm = fao_tonnes_production/n_farms) %>% 
+  group_by(continent_group, group) %>% 
+  summarise(tonnes_per_farm = mean(tonnes_per_farm))
+```
+
+```{r}
 ready <- raw %>% 

### 2021-03-15 workflow/qualtiy_control_filters.R

@@ -46,9 +46,10 @@ bathy_raw[!is.na(bathy_raw)] <- 1 # replace all suitable depths with 1
 all_farms_raw   <-
   bind_rows(read_csv("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv") %>% 
               mutate(type = "bivalve") %>% 
-              select(-X1),
+              dplyr::select(-X1),
             read_csv("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv") %>% 
-              mutate(type = "crustacean"),
+              mutate(type = "crustacean") %>% 
+              dplyr::select(-prod),
             read_csv("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv") %>% 
               mutate(type = "salmon"),
             read_csv("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon_data_quality.csv") %>% 
@@ -61,6 +62,10 @@ all_farms_raw   <-
            coords = c("lon", "lat"),
            crs = crs(food_raster), 
            agr = "constant") 
+
+all_the_farm_points <- all_farms_raw %>% 
+  dplyr::select(iso3c, data_quality, type) %>%
+  .[0, ]
 
 
 ####  Allocate spatially ####
@@ -84,16 +89,20 @@ need_national_allocation <- all_farms_raw %>%
 # layers of data needed gadm_full, eez_sf, coastline, 
 
 # generate prediction points for each national allocation area
-for (i in 1:unique(need_national_allocation$iso3c)) {
+for (i in 1:length(unique(need_national_allocation$iso3c))) {
   
   #1. Get the country ranges land-eez-bbox
   
   ## 1.a get country shape file
-  this_iso3 <- unique(need_national_allocation$iso3c)[7]
+  this_iso3 <- unique(need_national_allocation$iso3c)[8]
   
-  the_farm_number <- all_farms_raw %>% 
+  this_farm_info <- all_farms_raw %>% 
     filter(iso3c == this_iso3,
-           data_quality != 5) %>% 
+           data_quality == 3) 
+  
+  this_type_vector <- this_farm_info$type
+  
+  the_farm_number <- this_farm_info %>% 
     nrow()
   
   
@@ -134,14 +143,14 @@ for (i in 1:unique(need_national_allocation$iso3c)) {
[…]

### 2021-03-23 marine/LAST_STEP_compile_data.Rmd
Finished reorganizing data

---
title: "Compile known farm locations and farms to add data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all known farms data and bind together for one file.

```{r}
bivalve_farms <- read_csv(here("marine/bivalve/bivalve_farms/output/all_known_bivalve_farms_final.csv"))

# crustacean_farms <- read_csv(here("marine/crustaceans/crustacean_farms/output/all_known_crustacean_farms_final.csv")) ## there are none

finfish_farms <-  read_csv(here("marine/marine_fish_general/finfish_farms/output/all_known_finfish_farms_final.csv"))

shrimp_farms <-  read_csv(here("marine/shrimp/shrimp_farms/output/all_known_shrimp_farms_final.csv"))

tuna_farms <-  read_csv(here("marine/tuna/tuna_farms/output/all_known_tuna_farms_final.csv"))

salmon_farms <-  read_csv(here("marine/salmon/salmon_farm/output/all_known_salmon_farms_final.csv")) %>%
  dplyr::select(-subregion)

## bind together

all_farms <- rbind(bivalve_farms, finfish_farms, shrimp_farms, tuna_farms, salmon_farms)

## now write to our output folder
write.csv(all_farms, here("marine/output/all_marine_farms.csv"), row.names = FALSE)

unique(all_farms$type)

```

Read in the points to add data and bind together for one file.

```{r}
bivalve_farms_add <- read_csv(here("marine/bivalve/bivalve_farms/output/bivalve_points_to_add_final.csv"))

crustacean_farms_add <- read_csv(here("marine/crustaceans/crustacean_farms/output/crustaceans_points_to_add_final.csv"))

finfish_farms_add <-  read_csv(here("marine/marine_fish_general/finfish_farms/output/marine_fish_general_points_to_add_final.csv"))

shrimp_farms_add <-  read_csv(here("marine/shrimp/shrimp_farms/output/shrimp_points_to_add_final.csv"))

tuna_farms_add<-  read_csv(here("marine/tuna/tuna_farms/output/tuna_points_to_add_final.csv"))

salmon_farms_add <-  read_csv(here("marine/salmon/salmon_farm/output/salmon_points_to_add_final.csv"))

all_point_additions <- rbind(bivalve_farms_add, crustacean_farms_add, finfish_farms_add, shrimp_farms_add, tuna_farms_add, salmon_farms_add)

## write to our output folder
write.csv(all_point_additions, here("marine/output/all_points_to_add.csv"), row.names = FALSE)

str(all_point_additions)
summary(all_point_additions)
unique(all_point_additions$type)
```

### 2021-03-23 marine/archive/LAST_STEP_distance_to_shore_calcs.Rmd
Finished reorganizing data

---
title: "Distance to shore calcs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script calculates the distance to shore for each aquaculture point that falls under data quality = 4 or data quality = 5.

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(janitor)
library(rnaturalearth)
library(spatialEco)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

source(here::here("_spatial/template_raster.R"))

gordon_coast <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline_st.shp"))
```

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

Read in and summarise all data quality farm data 
```{r}
bivalves <- read_csv(here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "bivalve") %>%
  dplyr::select(-X1)

shrimp <- read_csv(here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "shrimp") %>%
  dplyr::select(-area_ha, -prod)

marine_fish <- read_csv(here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "marine_fish_general") %>%
  dplyr::select(-rgn_production)

salmon <- read_csv(here::here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv")) %>%
  mutate(group = "salmon")

crustaceans <- read_csv(here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "crustaceans") %>%
  dplyr::select(-prod)

tuna <- read_csv(here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon_data_quality.csv")) %>%
  mutate(group = "tuna") %>%
  mutate(subregion = NA)

all_farms <- rbind(shrimp, bivalves, marine_fish, salmon, crustaceans, tuna)

all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(all_farms_sf)

## find average distance to shore per each spp group

## do bivalves 
datalist_biv = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "bivalve")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows) %>%
    filter(row_number > 2322) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_biv[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_biv = do.call(rbind, datalist_biv)

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_biv, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/bivalve_dist.shp"))

## do tunas 
datalist_tuna = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "tuna")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows) #%>%
    #filter(row_number > 2322) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_tuna[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_tuna = do.call(rbind, datalist_tuna)

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_tuna, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/tuna_dist.shp"))

## do marine fish  
datalist_mf = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "marine_fish_general")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows) #%>%
    #filter(row_number > 2322) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_mf[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_mf = do.call(rbind, datalist_mf)

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_mf, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/marine_fish_general_dist.shp"))

## do salmon 
datalist_salmon = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "salmon")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows)#  %>%
# filter(row_number < 2345, row_number > 2235) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 2235 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_salmon[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_salmon = do.call(rbind, datalist_salmon)
## ~100 per hour = there are 3400 rows... = 34 hours to run....

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_salmon, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/salmon_dist.shp"))

## do shrimp
datalist_shrimp = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "shrimp")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
     mutate(row_number = 1:num_rows)
    # filter(row_number > 3464) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_shrimp[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

  dist_data_shrimp = do.call(rbind, datalist_shrimp)

st_write(dist_data_shrimp, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/shrimp_dist.shp"))

## there are no crustaceans that fall in that category.. we will probably just need to use the shrimp distance for crustaceans
  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "crustaceans")

## Now compile them together and write as a shp. And calculate some summary stats.

all_farms_bad <- all_farms_sf %>%
  dplyr::filter(action_needed != "Land mask")

biv_dist <- st_read(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/bivalve_dist.shp"))

shrimp_dist <- st_read(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/shrimp_dist.shp"))

tuna_dist <- st_read(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/tuna_dist.shp"))

mf_dist <- st_read(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/marine_fish_general_dist.shp"))

salmon_dist <- st_read(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/salmon_dist.shp"))

crust_dist <- all_farms_sf %>%
  dplyr::filter(group == "crustaceans") %>%
  dplyr::filter(action_needed == "Land mask") %>%
  dplyr::filter(distance = NA) ## there are none...

all_farms_distance <- rbind(biv_dist, shrimp_dist, tuna_dist, mf_dist, salmon_dist)

## save this file
st_write(all_farms_distance, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/all_farms_distance.shp"))

## Now calculate some summary stats
stats <- all_farms_distance %>%
  mutate(distanc_km = distanc/1000) %>%
  group_by(group) %>%
  summarise(mean_dist = mean(distanc_km), 
            sd_dist = sd(distanc_km),
            max_dist = max(distanc_km), 
            min_dist = min(distanc_km), 
            quant_90 = quantile(distanc_km, 0.9),
            quant_10 = quantile(distanc_km, 0.1), 
            points = n()) %>%
  ungroup()

data.table(stats)

## lets explore some outliers...

shrimp_outliers <- shrimp_dist %>%
  mutate(distanc_km = distanc/1000) %>%
  filter(distanc_km > 10)

mapview(shrimp_outliers) ## it appears all of the shrimp outliers are on land... which makes sense, because marine shrimp ponds are usually on land. I think they are ok. But I wonder if we should only grab those points that dont fall on land for our spatial allocation. Or maybe just place the shrimp ones very close to the shore.

biv_outliers <- biv_dist %>%
  mutate(distanc_km = distanc/1000) %>%
  filter(distanc_km > 10)

mapview(biv_outliers) ## similarly, the largest outliers are on land. Aside from one in New Zealand, but it comes from the ASC dataset, and I think is probably a mistake.. removing it doesn't make much of a difference anyways.

biv_fix <- biv_dist %>%
  filter(distanc < 200000)
mean(biv_fix$distanc)/1000 # 2.502882

## tuna seems fine

mf_outliers <- mf_dist %>%
  mutate(distanc_km = distanc/1000) %>%
  filter(distanc_km > 10)

mapview(mf_outliers) ## similarly, the largest outliers are on land.

salmon_outliers <- salmon_dist %>%
  mutate(distanc_km = distanc/1000) %>%
  filter(distanc_km > 10)

mapview(salmon_outliers) ## similarly, the largest outliers are on land/along waterways/lakes.

mapview(biv_dist)
mapview(shrimp_dist)
mapview(salmon_dist)
mapview(mf_dist)
mapview(tuna_dist)
```

### 2021-03-23 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
Finished reorganizing data

@@
 
-coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
-
-```
-
-## explore
+```
+
+# Raster
+
+Standard raster used for this analysis
+
+```{r}
+
+source(here::here("_spatial/template_raster.R"))
+
+```
+
+# Global regions
+
+```{r}
+
+gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
+
+gadm_latlon <- projectRaster(gadm, food_raster)
+
+gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
+  mutate(reg_id = as.numeric(reg_id))
+
+```
+
+```{r}
+
+gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
+  mutate(cellvalue = round(cellvalue, 0))
+
+gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
+
+```
+
+Now we will map the remaining countries with bivalve farms. Workflow will be as follows: 
+ - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
+ - If there are not exact locations or comprehensive locations, find the number of farms. 
+ - If there is no information at all, note it. We will gapfill later.
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).
+
+5: Comprehensive number of exact farms
+
+4: Subset of exact locations, need to add a specific number of farms to existing locations. 
+  - country|species|farm locations
+  - country|species|additional points
+
+3: A specific number of farms are known, but no locations 
+ - country|species|additional points
+
+2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
+ - country, species, n_existing_points
+
+2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.
+
+1: No information on number of farms at all. Need to be gapfilled by tonnage. 
+ - country|species|# additional farms (this will be NA)
+
+## Read in ASC data
 https://gis.asc-aqua.org/arcgis_app/
@@
 
-# Raster
-
-Standard raster used for this analysis
-
-```{r}
-
-source(here::here("_spatial/template_raster.R"))
-
-```
-
-# Global regions
-
-```{r}
-
-gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
-
-gadm_latlon <- projectRaster(gadm, food_raster)
-
-gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
-  mutate(reg_id = as.numeric(reg_id))
-
-```
-
-```{r}
-
-gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
-  mutate(cellvalue = round(cellvalue, 0))
-
-gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
-
-```
-
-For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
- 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
-   - Must not intersect with land mask
-   - "Land mask"
-
-4: Good qualifications - Locations are projected or it is a only sample of total locations
-   - Must not intersect with land mask
-   - "Land mask"
-
-3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
-   - Must be allocated spatially
-   - Must not intersect with land mask
-   - Flagged as "allocate spatially"
-
-2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
-   - Must be allocated using suitability analysis.
-   - Flagged as 2 and "state/province suitability"
-
-1: Very Bad qualifications - No data at all.
-   - Must be allocated using suitability analysis.
-   - Flagged as 1 and "country suitability"
-
 # Map data from ASC
@@
 Data comes from https://gis.asc-aqua.org/arcgis_app/
+
+We filter out france and great britain, because those farms are already accounted for in the EMODnet database (which are comprehensive datasets taken from lease data).
 
@@
   cbind(iso) %>%
-  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c)) ## fix Jersey
+  mutate(iso3c = ifelse(str_detect(comp_nm, "Jersey"), "JEY", iso3c)) %>% ## fix Jersey
+  filter(!(iso3c %in% c("GBR", "FRA"))) ## filter out france and GBR... because they are in EMODnet
 
@@
 farms_all_fin <- farms_all_fin %>%
-  cbind(iso3c = all_pts_latlon$iso3c) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
+  cbind(iso3c = all_pts_latlon$iso3c)
 
 ## save farm location
-write.csv(farms_all_fin, here("marine/bivalve/bivalve_farms/data/bivalve_sites/ASC_bivalve_farm_lat_lon.csv"), row.names = FALSE)
-
-```
-
-Now we will map the remaining countries with bivalve farms that are not included in the ASC dataset. Workflow will be as follows: 
- - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
- - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of bivalve farms, equally allocate the farms across the coastline.
-If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - Lastly, if there is no evidence of marine bivalve farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
-what we've done for Russia).
+write.csv(farms_all_fin, here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv"), row.names = FALSE)
+
+```
+
+Now we need to map for each country, and assign a flag for gapfilling which will be completed later. I will start with all of the countries list in the ASC data.
+
+# China
+
+Current data is from ASC, only 11 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of China.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_chn <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "CHN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_chn, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
+
+```
+
+# New Zealand
+
+We currently know the exact location of 2 bivalve farms in New Zealand, however there is much more production that just 2 farms in New Zealand.
+Although outdated, the FAO report tells us there are 910 total abaolne, mussel, and oyster farms in New Zealand.
+We will treat this as truth.
+
+ -  Need to add 908 points to existing 2 (a final total of 910 points)
+
+ - http://www.fao.org/fishery/countrysector/naso_newzealand/en
+
+  - “In 2004 there were 645 New Zealand mussel farms occupying a total of 4 747 hectares of water space and producing over 85 000 tonnes of mussels (NZAC, 2005).
+The majority of these farms were in the Marlborough Sounds at the northern end of the South Island.
+A smaller proportion of the mussel farms are located in the Coromandel and Hauraki Gulf in the north of the North Island, and a smaller number again at Stewart Island.
+More recently, permission has been given to develop farming in some larger offshore areas in the Bay of Plenty and Hawkes Bay off the eastern coast of the North Island.”
+
+  - “In 2004 there were 230 oyster farms covering 750 hectares of marine waters mostly in a series of sheltered harbours on the north-eastern coast of the North Island (NZAC, 2005).
+These farms produced around 3 300 tonnes of oysters.”
+
+  - “A further 35 abalone farms operated over 20 hectares of marine water space producing only 2 tonnes of product in 2004 (NZAC, 2005).
+Most of these farms were located in the Marlborough Sounds or on Banks Peninsula on the eastern coast of the South Island.”
+
+```{r}
+farms_nzl <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "NZL") %>%
+  mutate(data_quality = 4)
+
+write.csv(farms_nzl, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_nzl.csv"), row.names = FALSE)
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+nz_additional <- data.frame(iso3c = "NZL", type = "bivalve", num_additional_farms = 908, data_quality = 4, total_farms = 910)
+write.csv(nz_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_nz.csv"), row.names = FALSE)
+```
+
+# South Africa
+
+We currently know the exact location of 2 bivalve farms in South Africa, however there is much more production that just 2 farms.
+However, governemnt websites and research papers say that there are 4 mussel farms and 21 abalone farms.
+We will treat this as truth.
+
+ - Need to add 23 points to existing 2 (a final total of 25 points)
+ - https://southafrica.co.za/mussel-production.html
+   - “According to The Department of Agriculture, Forestry and Fisheries (DAFF), mussel farming in South Africa is conducted entirely in Saldanha Bay, Western Cape, where four mussel farms are operational.”
+ - https://core.ac.uk/download/pdf/62634432.pdf
+  - We can tell from Figure 1B that there are 21 abalone farms in South Africa
+
+```{r}
+farms_zaf <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "ZAF") %>%
+  mutate(data_quality = 4)
+
+write.csv(farms_zaf, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_zaf.csv"), row.names = FALSE)
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+zaf_additional <- data.frame(iso3c = "ZAF", type = "bivalve", num_additional_farms = 23, data_quality = 4, total_farms = 25)
+write.csv(zaf_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_zaf.csv"), row.names = FALSE)
+```
+
+# Australia
+
+We currently know the exact location of 1 bivalve farms in Australia, however there is much more production that just 1 farm.
+However, aquaculture websites say there are 20 abalone farms, 14 oyster farms, and 25 mussel farms in Australia
+
+Need to add 68 points to existing 1 point (for a total of 69 points)
+
+ - Abalone
+  - https://www.oceanwatch.org.au/seafood/aquaculture/species/abalone/
+  - “There are around 20 farms that produce about 725 tonnes of abalone every year, with production volume increasing by about 25% every year.”
+  - 725 tonnes of abalone matches really well to what is reported for abalone in Australia by the FAO.
+
+ - Oysters
+  - This states that nearly all oyster license holders are a part of this association:   
+  - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
+  - We will use this as truth: http://www.oysterssa.com.au/south-australian-oyster-growers
+  - We will need to place an additional 14 oyster farms in Australia
+
+ - Mussels
+  - https://www.oceanwatch.org.au/seafood/aquaculture/species/mussels/
+  - “Concentrated in the south of country, there are about 25 mussel farms spread across SA, Tasmania, Victoria, Tasmania and the south coasts of both NSW and WA.”
+
+  - We will place a total of 69 bivalve points in Australia.
+
+```{r}
+farms_AUS <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "AUS") %>%
+  mutate(data_quality = 4)
+
+write.csv(farms_AUS, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"), row.names = FALSE)
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+AUS_additional <- data.frame(iso3c = "AUS", type = "bivalve", num_additional_farms = 68, data_quality = 4, total_farms = 69)
+write.csv(AUS_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_aus.csv"), row.names = FALSE)
+```
+
+# South Korea 
+We currently know the exact location of 27 bivalve farms in South Korea, however there is much more production that just 27 farms.
+However, FAO says there are 5245 shell fish leases in South Korea.
+WE will place an additional 5218 farms.
+
+Need to add 5218 points to existing 27 (a final total of 5245 points)
+ - FAO states there are 5,245 shellfish leases in operation:     
+  - http://www.fao.org/fishery/countrysector/naso_korea/en
+
+```{r}
+farms_kor <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "KOR") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_kor, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_kor.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+kor_additional <- data.frame(iso3c = "KOR", type = "bivalve", num_additional_farms = 5218, data_quality = 4, total_farms = 5245)
+write.csv(kor_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_kor.csv"), row.names = FALSE)
+```
+
+# Japan
+
+Current data is from ASC, only 55 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Japan.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_jpn <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "JPN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_jpn, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_jpn.csv"))
+
+```
+
+# Peru
+
+We currently know the exact location of 25 bivalve farms in Peru, however there is much more production that just 25 farms.
+However, FAO says there are 52 bivalve farms in Peru.
+We will place an additional 27 farms (for a total of 52 farms).
+
+ - Need to add 27 points to existing 25 (a final total of 52 points)
+   - http://www.fao.org/fishery/countrysector/naso_peru/en
+   - “It is estimated that Peru has some 14 164 ha apt for the development of marine cultures; of which 86 percent correspond to the region of Ancash (7 228.14ha) and to Ica (5 017.97 ha).
+Nevertheless, as of December 2003, leased and authorized areas amount to only 8 858 ha.
+Of this total, 3 033 ha are dedicated to the cultivation of the fan shell.
+   - At present, of the 44 referred enterprises, 26 holding 1 662.8 ha are located in the Ancash region; followed by the Ica region, where 18 enterprises occupy 136.8 ha; and the Piura Region has 8 enterprises that develop their activities in 787,6 ha.
+The majority are large scale operations, with the exception of those located in the Ica region which are relatively small.”
+
+```{r}
+farms_per <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "PER") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_per, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_per.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+per_additional <- data.frame(iso3c = "PER", type = "bivalve", num_additional_farms = 27, data_quality = 4, total_farms = 52)
+write.csv(per_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_per.csv"), row.names = FALSE)
+```
+
+# Mexico
+Current data is from ASC, only 1 farm, so definitely not comprehensive, just a drop in the bucket compared to the production of Mexico.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_mex <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "MEX") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_mex, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_mex.csv"))
+
+```
+
+# Jersey
+Current data is from ASC, only 5 farm. However, this is comprehensive. When comparing to governmental lease data, there are only 7 leases in Jersey.
+
+```{r}
+farms_jey <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "JEY") %>%
+  mutate(data_quality = 5)
+
+write_csv(farms_jey, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_jey.csv"))
+
+```
+
+# Viet Nam
+
+Current data is from ASC, only 1 farm, so definitely not comprehensive, just a drop in the bucket compared to the production of Viet Nam.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_vnm <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "VNM") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_vnm, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_vnm.csv"))
+
+```
+
+# Portugal
+
+We currently know the exact location of 1 bivalve farm in Portugal, however there is much more production that just 1 farm.
+However, Portuguese government data says there are 30 bivalve farms in Portugal We will place an additional 29 farms (for a total of 30 farms).
+
+Need to add 29 points to existing 1 (a final total of 30 points)
+
+Current data is ASC data which is only a subset of total farms.
+
+ - https://www.ine.pt/xportal/xmain?xpid=INE&xpgid=ine_publicacoes&PUBLICACOESpub_boui=435690295&PUBLICACOESmodo=2&fbclid=IwAR0-_SHYtw2XGUAXdx71RGer284Vk_u40HYKXyJzeFbpdnsHydKgAfomTvU
+  - National Institute of Statistics for Portugal 
+  - There is a csv table, "q5_1.csv", which has the number of farms listed by type of system.
+I will assume that floating marine structures are for bivalves, since [this website](https://rea.apambiente.pt/content/aquaculture-production?language=en) says that the tanks are for **fish production**, and floating structures are for **bivalve molluscs**.
+
+  - Located here "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Portugal/EPesca_2019.xlsx"
+
+ - According to this table, there are 30 total marine floating structures
+
+```{r}
+farms_prt <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "PRT") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_prt, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_prt.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+prt_additional <- data.frame(iso3c = "PRT", type = "bivalve", num_additional_farms = 29, data_quality = 4, total_farms = 30)
+write.csv(prt_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_prt.csv"), row.names = FALSE)
+```
+
+# Chile
+This data is comprehensive. No gapfilling needed.
+
+Data for Chile comes from https://mapas.subpesca.cl/ideviewer/?locale=en-gb.
+
+There is also a list of concessions here: http://www.subpesca.cl/portal/619/w3-article-92935.html
+
+I was in contact with Valeria Tamayo at UCSB who helped me with some spanish translations concerning this data.
+
+Source:
+Undersecretariat for Fisheries and Aquaculture, 2020. [Accessed Feb 2020] https://mapas.subpesca.cl/ideviewer/?locale=en-gb
+
+```{r}
+
+# Column meaning and names
+#0 LINK_DOC - URL of the SUBPESCA resolution approving the aquaculture or resolution technical project that cartographically regulates the aquaculture concession
+#1 CARTA - Name of the geographic reference letter
+#2 DATUM - Reference datum name
+#3 HUSO - Spindle Name
+#4 COMUNA - Name of the commune
+#5 N_PERT - Pert number, code of the application for admission to process
+#6 N_CODIGOCE - Farming center code according to the national aquaculture registry
+#7 N_RESOLSSP - Resolution number of the undersecretary of fisheries and aquaculture that apprehends the aquaculture technical project
+#8 F_RESOLSSP - Date of issuance of the resolution of the undersecretary of fisheries and aquaculture approving the aquaculture technical project
+#9 N_RESOLSSF - Resolution number of the undersecretary for the armed forces granted by the aquaculture concession
+#10 F_RESOLSSF - Date of issuance of the resolution of the undersecretary for the armed forces granted by the aquaculture concession
+#11 TOPONIMIO - Geographical location of the aquaculture concession
+#12 ESPECIES - Name of crop species
+#13 AGRUPCONCE - Identifier of the salmonid concession group or sanitary neighborhood
+#14 SUPERFICIE - Surface in hectares
+#15 TITULAR - Name of the holder of the aquaculture concession
+#16 COORDENADS - List of geographical coordinates of the aquaculture concession corresponding to each of the vertices of the polygon
+#17 REGION - Region name
+#18 GRUPO_ESP - Group of crop species
+#19 TIPO_PORCI - Type of space where the aquaculture concession is located
+#20 ESTADO - Processing status of the aquaculture concession
+#21 ESTADO_SOL - Status of the aquaculture application process
+
+chile_dat <- st_read(file.path(path, "Chile"), layer = "Concesiones_de_Acuicultura")
+
+```
+
+We filter to only those that produce salmon, but note that this is ALL leases, not neccesarily only active sites. 
+```{r}
+unique(chile_dat$REP_SUB_13)
+
+#Filter to only bivalve farming (mussel, abalone, oysters, clams, and scallops)
+chile <- chile_dat %>% 
+  filter(grepl("CHORO|ABALON|OSTRA|CHOLGA|CHORITO|OSTION|ALMEJA|MITILIDOS", REP_SUB_13)) %>%
+  filter(!grepl("SALMON", REP_SUB_13))
+
+# convert polygons to points
+chile_pts <- st_centroid(chile)
+chile_pts <- st_transform(chile_pts, food_crs)
+
+# save as a dataframe
+farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
+names(farms_chile) <- c("lon", "lat")
+farms_chile <- farms_chile %>%
+  mutate(iso3c="CHL") %>%
+  mutate(data_quality = 5)
+
+write_csv(farms_chile, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_chl.csv"))
+
+```
 
 ## USA
-This has a lot of maps, but almost all don't allow downloads: https://coastalscience.noaa.gov/research/marine-spatial-ecology/coastal-aquaculture-planning-portal-capp/?tx_category=shellfish-algae-planning-and-siting
+
+Based on the two datasets below, we have an existing 442 bivalve farms. We need to add 761 points to existing 442 (a final total of 1203 points)
+
+Our current information is taken from many different state level sources, but we are definitely still missing some, as California is not included...
+
+ - However, per FAO 2005, there were 1203 saltwater shellfish farms in the USA
+  - http://www.fao.org/fishery/countrysector/naso_usa/en
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 5.0) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 4)
 
@@
 # mapview(all_farms_sf)
-
-write_csv(farms_us_ne, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ne_usa.csv"))
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
-all_farms_sf <- st_as_sf(farms_us_aqua, coords = c("lon", "lat"),
+  mutate(data_quality = 4)
+
+farms_usa_total <- rbind(farms_us_ne, farms_us_aqua)
+
+all_farms_sf <- st_as_sf(farms_usa_total, coords = c("lon", "lat"),
                          crs = crs(gadm_latlon), agr = "constant")
@@
 
-write_csv(farms_us_ne, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_wa_ri_usa.csv"))
-
+write_csv(farms_usa_total, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_usa.csv"))
+
+## Now lets make a df for the additional points we will fill in later
+
+usa_additional <- data.frame(iso3c = "USA", type = "bivalve", num_additional_farms = 761 , data_quality = 4, total_farms = 1203)
+write.csv(usa_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_usa.csv"), row.names = FALSE)
 ```
@@
 HELCOM HOLAS II Dataset: Shellfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+
+Sweden:
+
+Current data is from HELCOM, but they state that some data is missing for Sweden (likely a very small amount, given the production).
+There is not much information on how many farms there might be, so we will gapfill Sweden later.
+Data quality = 2
+
+Germany:
+
+Need to add 10 points to existing 1 point
+ - Current data is from HELCOM, which takes from lease data 
+ - Data quality = 4
+
+ - However, the only type farmed in germany is the blue mussel, and this source says there are 11 farms there: 
+  - https://onlinelibrary.wiley.com/doi/full/10.1111/raq.12465
+  - “The German blue mussel aquaculture takes place at the world heritage and National Park of the Wadden Sea.
+Therein strict restrictions limit the total number of licenses for harvesting mussel seeds and culture areas (Schlauch 1999).
+In consequence, the number of enterprises, which are organised in two producer associations, is stable at 11 to ten companies since the 1990s.”
 
@@
   mutate(iso3c = ifelse(COUNTRY == "DE", "DEU", "SWE")) %>%
-  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
-write.csv(farms_bal, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_swe_deu.csv"), row.names = FALSE)
+  dplyr::select(lon, lat, iso3c, subregion = NAME)
+
+## Sweden
+
+farms_swe <- farms_bal %>%
+  dplyr::filter(iso3c == "SWE") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_swe, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_swe.csv"))
+
+## Germany
+
+farms_deu <- farms_bal %>%
+  dplyr::filter(iso3c == "DEU") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_deu, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_deu.csv"))
+
+deu_additional <- data.frame(iso3c = "DEU", type = "bivalve", num_additional_farms = 10 , data_quality = 4, total_farms = 11)
+write.csv(deu_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_deu.csv"), row.names = FALSE)
 
@@
 ## HELCOM shellfish mariculture areas - Denmark
+This data is comprehensive, data quality = 5
 
@@
   dplyr::select(lon, lat, iso3c) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 5)
 
@@
 
-write.csv(farms_bal_area, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_dnk.csv"), row.names = FALSE)
-```
+write.csv(farms_bal_area, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_dnk.csv"), row.names = FALSE)
+```
+
+## Canada
+All of these data are taken from specific governmental sources. They are comprehensive. Data quality = 5.
 
@@
   mutate(iso3c="CAN") %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_bc, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_bc_can.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_bc, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_bc_can.csv"))
 
@@
   mutate(iso3c="CAN") %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_ns, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ns_can.csv"))
-
-```
-
-##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece
+  mutate(data_quality = 5)
+
+write_csv(farms_ns, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_ns_can.csv"))
+
+```
+
+##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece, UK, France
+
+Almost all of this data is comprehensive. The only one that is not is the netherlands. We will note that and gapfill netherlands later on.
+
 https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production
@@
 EMODnet Human Activities: Shellfish aquaculture, 2019. [Accessed November 30, 2020] https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production
+
+Netherlands
+ - Need to add 76 points to existing 6 (a final total of 82 points)
+ - Current data is from EMODnet and is NOT comprehensive. Only 6 farms locations.
+  - http://www.fao.org/fishery/countrysector/naso_netherlands/en
+  - “The shellfish sub-sector is the older and economically more significant of the two and consists of 50 companies growing blue mussels (Mytilus edulis) and 32 companies growing oysters (Ostrea edulis and Crassostrea gigas).”
 
@@
 
-## Now filter for countries that we want: Ireland, Bulgaria, Italy, Norway, Netherlands, and Greece. UK and DNK are already accounted for in our other datasets. 
+## Now filter for countries that we want: Ireland, France, UK, Bulgaria, Italy, Norway, Netherlands, and Greece. Filter out denmark, since there is overlap between HELCOM and EMODnet
 eu_fao_countries <- eu_active_na %>%
-  dplyr::filter(!(COUNTRY %in% c("France", "United Kingdom", "Denmark")))
+  dplyr::filter(!(COUNTRY %in% c("Denmark")))
 
@@
     COUNTRY == "Italy" ~ "ITA", 
-    COUNTRY == "Greece" ~ "GRC"
+    COUNTRY == "Greece" ~ "GRC",
+    COUNTRY == "France" ~ "FRA",
+    COUNTRY == "United Kingdom" ~ "GBR"
   )) %>%
-  dplyr::select(-COUNTRY) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
- write_csv(farms_eu_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_IRL_BGR_NOR_NLD_ITA_GRC.csv"))
+  dplyr::select(-COUNTRY)
+
+farms_eu_no_nld <- farms_eu_final %>%
+  filter(iso3c != "NLD") %>%
+  mutate(data_quality = 5)
+
+write_csv(farms_eu_no_nld, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_GBR_FRA_IRL_BGR_NOR_ITA_GRC.csv"))
+
+farms_nld <- farms_eu_final %>%
+  filter(iso3c == "NLD") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_nld, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_NLD.csv"))
+
+nld_additional <- data.frame(iso3c = "NLD", type = "bivalve", num_additional_farms = 76 , data_quality = 4, total_farms = 82)
+write.csv(nld_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_nld.csv"), row.names = FALSE)
 
@@
 ## Spain
-TODO: Figure out how to download exact locations
 
@@
 It will not allow for download of the locations of the facilities.
-However, I have downloaded all of the names of each shellfish installation, with the company name, and what general location they are located in.
-I will filter for unique cities, and place points in each place.
-
-How to download: 
- - Make sure you only have the basemap and the "Instalaciones" layers selected.
- - Click on the filter tab and filter for "Marina" aquaculture, and for these shellfish species: 
- Abalón japonés, Almeja babosa, Almeja fina, Almeja japonesa, Almejas nep (Ruditapes spp), Almejas nep (Veneridae), Berberecho, Berberecho verde, Bivalvos, Bígaro, Coquina, Escupiña grabada, Lapa, Navaja recta, Navaja, Oreja de mar, Ostión u ostra japonesa, Ostra u ostra plana, Ostras u ostras planas, Vieira, Volandeira, Zamburiña
- - Download the data and save as a csv.
-
-General location to place points:
- - Alicante: 38.345509445679276, -0.48793746088812184
- - Almeria: 36.83403538312481, -2.46312530015449
- - Asturias: 43.6586646127094, -5.838989914402157
- - Baleares: 39.578993240236755, 2.6312097506887446
- - Cadiz: 36.55518316813145, -6.2759664948571094
- - Cantabria: 43.488143305644364, -3.808940707432179
- - Castellon: 39.98227981322492, 0.025845987383098443
- - Gerona: 41.893397069777485, 3.1931418366760647
- - Granada: 36.69547948740147, -3.403621978170133
- - La Coruna: 43.36941893593161, -8.412121809979775
- - Las Palmas: 28.17841973419213, -15.411897095500123
- - Lugo: Inland, Don't include
- - Malaga: 36.705816371679525, -4.422146790963811
- - Murcia: Inland, don't include
- - Pontevedra: 42.42511968211785, -8.658739084602496
- - Sevilla: Inland, don't include
- - Santa Cruz de Tenerife: 28.464013540472575, -16.25186419732133
- - Tarragona: 41.109958666992036, 1.2538616546744752
- - Valencia: 39.47564987283762, -0.3208672158378773
- - Vizcaya: 43.436972390962005, -2.9200783381913014
-
-Source: 
-Acuivisor, 2019. Ministerio de Agricultura, Pesca Y Alimentacion, Gobierno de Espana. [Accessed December 2, 2020] https://servicio.pesca.mapama.es/acuivisor/
-
-```{r}
-## Read in dataset of company names:
-spain_shellfish <- read_csv(here("marine/bivalve/bivalve_farms/data/spain_shellfish_aquaculture.csv"))
-
-head(unique(spain_shellfish$Empresa))
-
-communitiy <- data.frame(companies = unique(spain_shellfish$Provincia))
-
-## there are 21 different cities where shellfish is farmed.
-
-farms_esp <- data.frame(lat = c(38.345509445679276, 36.83403538312481, 43.6586646127094, 39.578993240236755, 36.55518316813145, 43.488143305644364, 39.98227981322492, 41.893397069777485, 36.69547948740147, 43.36941893593161, 28.17841973419213, 36.705816371679525, 42.42511968211785, 28.464013540472575, 41.109958666992036, 39.47564987283762, 43.436972390962005),
-                        lon = c(-0.48793746088812184, -2.46312530015449, -5.838989914402157, 2.6312097506887446, -6.2759664948571094, -3.808940707432179, 0.025845987383098443, 3.1931418366760647,-3.403621978170133,  -8.412121809979775, -15.411897095500123, -4.422146790963811, -8.658739084602496, -16.25186419732133, 1.2538616546744752, -0.3208672158378773, -2.9200783381913014),
-                        subregion = c("Alicante", "Almeria", "Asturias", "Baleares", "Cadiz", "Cantabria", "Castellon", "Gerona", "Granada", "La Coruna", "Las Palmas", "Malaga", "Pontevedra", "Santa Cruz de Tenerife", "Tarragona", "Valencia", "Vizcaya")) %>%
-  mutate(iso3c = "ESP") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_esp, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_esp.csv"))
-
-## visualize it 
-farms_esp <-  st_as_sf(farms_esp, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_esp)
-
+If we could download tha exact locations, this would be ideal.
+However, since we can't, we will gapfill locations instead.
+See archive for how we previously attempted.
+
+Spain bivalves will be treated as if there is no available information, data quality = 1.
+
+```{r}
+# Write a file for russia to indicate it has no information and will need to be fully gapfilled
+esp_gf <- data.frame(iso3c = "ESP", type = "bivalve", num_additional_farms = NA, data_quality = 1)
+write_csv(esp_gf, here("marine/bivalve/bivalve_farms/data/no_info_1/gf_esp.csv"))
 ```
@@
 There is also an oyster farm located in a disused quarry in the north of the island.
- - Allocate 7 farms equally across coastline
+ - Allocate 7 farms into the most suitable locations in Guernsey (this is done later, along with the rest of the gapfilling.)
+ - For now we will flag this so that we can gapfill later.
 
@@
 ```{r}
-## read in country shapefile
-Guernsey <- ne_countries(scale = 10, country = "Guernsey", returnclass = "sf")
-
-#info of our spatial vector object
-mapview(Guernsey)
-plot(Guernsey)
-
-## transform to same crs at the coast file so we can crop
-Guernsey_world_crs <- st_transform(Guernsey, crs(coast_raw))
-
-# crop the to the coast file, and select the main island 
-Guernsey_world_crop <- st_crop(coast_raw, Guernsey_world_crs) %>%
-  dplyr::filter(FID %in% c(220920, 220921, 220922)) %>% ## filter for the appropriate island
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
-  ungroup()
-
-plot(Guernsey_world_crop)
-mapview(Guernsey_world_crop)
-class(Guernsey_world_crop)
-crs(Guernsey_world_crop)
-
-g_meters <- st_transform(Guernsey_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(g_meters)
-
-buff <- st_buffer(g_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-plot(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-buffer_outline <- linestring[1,]  ## grab the outline row 
-mapview(buffer_outline)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(buffer_outline, crs = crs(Guernsey_world_crop))
-
-## make a spatiallinesdataframe so we can use sample.line
-Guernsey_crop <- as(buffer_outline_fixed, "Spatial")
-class(Guernsey_crop)
-mapview(Guernsey_crop)
-
-Guernsey_points_lines <- sample.line(Guernsey_crop, n = 7) ## equally place the number of farms along the coastline 
-class(Guernsey_points_lines)
-plot(Guernsey_points_lines)
-
-Guernsey_points <- st_as_sf(Guernsey_points_lines)
-mapview(Guernsey_points, color = "red") + mapview(Guernsey_world_crop)
-
-st_distance(Guernsey_points, Guernsey_world_crop)
-# Units: [m]
-#          [,1]
-# [1,] 992.6726
-# [2,] 992.6273
-# [3,] 992.6395
-# [4,] 992.3816
-# [5,] 992.3755
-# [6,] 992.7368
-# [7,] 992.6771
-## close enough to 1 km
-
-## now prep dataframe for lat lon points
-ggy_pts <- st_centroid(Guernsey_points)
-
-ggy_pts_latlon <- st_transform(ggy_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_ggy <- data.frame(do.call(rbind, st_geometry(ggy_pts_latlon)))
-names(farms_ggy) <- c("lon", "lat")
-
-farms_ggy_final <- farms_ggy %>%
-  mutate(iso3c = "GGY") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_ggy <-  st_as_sf(farms_ggy, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_ggy)
-
-## write to farms folder 
-write_csv(farms_ggy_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ggy.csv"))
+farms_ggy <- data.frame(iso3c = "GGY", type = "bivalve", num_additional_farms = 7, data_quality = 3)
+
+write_csv(farms_ggy, here("marine/bivalve/bivalve_farms/data/known_number_farms_3/farms_ggy.csv"))
+
 ```
@@
 
+ - Allocate 20 farms into the most suitable locations in Slovenia (this is done later, along with the rest of the gapfilling.)
+ - For now we will flag this so that we can gapfill later.
+
 Source: 
@@
 ```{r}
-# world <- rnaturalearth::ne_coastline(scale = 10) #world map with 10m resolution
-# plot(world)
-
-slovenia <- ne_countries(scale = 10, country = "Slovenia", returnclass = "sf")
-
-#info of our spatial vector object
-mapview(slovenia)
-plot(slovenia)
-
-# world <- st_as_sf(world)
-
-slovenia_world_crs <- st_transform(slovenia, crs(coast_raw))
-
-slovenia_world_crop <- st_crop(coast_raw, slovenia_world_crs) %>% ## crop to slovenia extent
-  filter(FID %in% c(46261, 46262)) %>%
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
-  ungroup()
-
-mapview(slovenia_world_crop)
-
-s_meters <- st_transform(slovenia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(s_meters)
-
-buff <- st_buffer(s_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-plot(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(slovenia_world_crop))
-
-linestring_fix <- st_difference(buffer_outline_fixed, slovenia) ## now grab only the outline 
-mapview(linestring_fix)
-
-## make a spatiallinesdataframe so we can use sample.line
-slovenia_crop <- as(linestring_fix, "Spatial")
-class(slovenia_crop)
-mapview(slovenia_crop)
-
-slovenia_points_lines <- sample.line(slovenia_crop, n = 41) ## equally place the number of farms along the coastline 
-class(slovenia_points_lines)
-plot(slovenia_points_lines)
-
-slovenia_points <- st_as_sf(slovenia_points_lines) %>%
-  mutate(new_id = 1:41)
-mapview(slovenia_points)
-
-## Now filter out the points that fall outside of Slovenia
-slovenia_points_final <- slovenia_points[2:21,]
-mapview(slovenia_points_final)
-
-mean(st_distance(slovenia_points_final, slovenia_world_crop))
-# 998.6394 [m]
-## close enough to 1 km
-
-## prep to get lat lon 
-svn_pts <- st_centroid(slovenia_points_final)
-
-svn_pts_latlon <- st_transform(svn_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_svn <- data.frame(do.call(rbind, st_geometry(svn_pts_latlon)))
-names(farms_svn) <- c("lon", "lat")
-
-farms_svn_final <- farms_svn %>%
-  mutate(iso3c = "SVN") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_svn <-  st_as_sf(farms_svn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_svn)
-
-## write to farms folder 
-write_csv(farms_svn_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_svn.csv"))
+farms_svn <- data.frame(iso3c = "SVN", type = "bivalve", num_additional_farms = 20, data_quality = 3)
+
+write_csv(farms_svn, here("marine/bivalve/bivalve_farms/data/known_number_farms_3/farms_svn.csv"))
 ```
@@
 
+  - Allocate 266 farms into the most suitable locations in Croatia (this is done later, along with the rest of the gapfilling.)
+ - For now we will flag this so that we can gapfill later.
+
 Source: 
@@
 ```{r}
-world <- ne_coastline(scale = 110) #world map with 110m resolution
-plot(world)
-
-croatia <- ne_countries(scale = 10, country = "Croatia", returnclass = "sf")
-
-#info of our spatial vector object
-mapview(croatia)
-plot(croatia)
-
-world <- st_as_sf(world)
-
-croatia_world_crs <- st_transform(croatia, crs(world))
-
-croatia_world_crop <- st_crop(world, croatia_world_crs)
-
-croatia_world_crop <- st_intersection(croatia_world_crop, croatia)
-mapview(croatia_world_crop)
-# %>% ## crop to croatia extent
-#   filter(!(FID %in% c(46278:46281, 643461:643463, 156618, 46260:46269, 46178:46182, 46177, 206670:206671))) %>%
-#   mutate(new_id = 1) %>%
-#   group_by(new_id) %>%
-#   summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
-#   ungroup()
-# mapview(croatia_world_crop)
-
-c_meters <- st_transform(croatia_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(c_meters)
-
-buff <- st_buffer(c_meters, dist = 40000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-plot(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(croatia_world_crop))
-
-linestring_fix <- st_difference(buffer_outline_fixed, croatia) ## now grab only the outline 
-mapview(linestring_fix)
-
-croatia_crop <- as(linestring_fix, "Spatial")
-plot(croatia_crop)
-mapview(croatia_crop)
-
-croatia_points_lines <- sample.line(croatia_crop, n = 640) ## equally place the number of farms along the coastline 
-class(croatia_points_lines)
-plot(croatia_points_lines)
-
-croatia_points <- st_as_sf(croatia_points_lines) %>%
-  mutate(new_id = 1:640)
-mapview(croatia_points)
-
-## Now filter out the points that fall outside of croatia: rows 57-70
-croatia_points_final <- croatia_points %>%
-  dplyr::filter(new_id %in% c(2:24, 395:640)) %>%
-  dplyr::filter(!(new_id %in% c(419, 533, 561)))
-mapview(croatia_points_final)
-
-mean(st_distance(croatia_points_final, croatia_world_crop))
-
-## get lat lon
-hrv_pts <- st_centroid(croatia_points_final)
-
-hrv_pts_latlon <- st_transform(hrv_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_hrv <- data.frame(do.call(rbind, st_geometry(hrv_pts_latlon)))
-names(farms_hrv) <- c("lon", "lat")
-
-farms_hrv_final <- farms_hrv %>%
-  mutate(iso3c = "HRV") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_hrv <-  st_as_sf(farms_hrv, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_hrv)
-
-## write to farms folder 
-write_csv(farms_hrv_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_hrv.csv"))
+farms_hrv <- data.frame(iso3c = "HRV", type = "bivalve", num_additional_farms = 266, data_quality = 3)
+
+write_csv(farms_hrv, here("marine/bivalve/bivalve_farms/data/known_number_farms_3/farms_hrv.csv"))
 ```
@@
 
+However, these are just a subset of possible locations in Cuba.
+Because there is no other information, we will have to gapfill the rest of the possible locations based on a global tonnes/farm.
+Data quality = 2
+
 ```{r}
@@
   mutate(iso3c = "CUB") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_cub, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_cub.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_cub, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_cub.csv"))
 
@@
 ## Taiwan
-- I can't find any information on the locations of shellfish farms in Taiwan. I will randomly place a point in the Qigu lagoon (see article). 
+- I can't find any information on the locations of shellfish farms in Taiwan. 
  - https://www.newsecuritybeat.org/2019/10/taiwan-beach-snow/
 
+ - Because of this, we will have to gapfill all points based on global tonnes/farm. Data quality = 1
+
 Source:
@@
 
-farms_twn <- data.frame(lat = c(23.12185817551473),
-                        lon = c(120.05482898155049)) %>%
-  mutate(iso3c = "TWN") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_twn, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))
-
-## visualize it 
-farms_twn <-  st_as_sf(farms_twn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_twn)
+twn_gf <- data.frame(iso3c = "TWN", type = "bivalve", num_additional_farms = NA, data_quality = 1)
+write_csv(twn_gf, here("marine/bivalve/bivalve_farms/data/no_info_1/gf_twn.csv"))
 
@@
 
+ - We are treating this information as comprehensive.
+
 ```{r}
@@
   mutate(iso3c = "PYF") %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_pyf, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_pyf.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_pyf, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_pyf.csv"))
 
@@
 
-Based on this, I will place 250 mussel farms along the coast in the Kerala state in India.
+ - This is only a subset of existing points...
+we know there are AT LEAST 250 farms in the state of Kerala, but there could be more elsewhere.
+Based on this, we will estimate the remaining number of farms for India bivalves based on a global tonnes/farm estimate.
 
@@
 
-## read in state shapefile
-kerala_state <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/India/Kerala/state.shp"))
-
-#info of our spatial vector object
-mapview(kerala_state)
-
-kerala_state_world_crs <- st_transform(kerala_state, crs(coast_raw))
-
-kerala_state_world_crop <- st_crop(coast_raw, kerala_state_world_crs) %>% ## crop to kerala extent
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>% ## merge all the geometries into one
-  ungroup()
-mapview(kerala_state_world_crop)
-
-k_meters <- st_transform(kerala_state_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(k_meters)
-
-buff <- st_buffer(k_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(kerala_state_world_crop))
-
-india <- ne_countries(scale = 10, country = "India", returnclass = "sf")
-mapview(india)
-
-linestring_fix <- st_difference(buffer_outline_fixed, india) ## now grab only the outline 
-mapview(linestring_fix)
-mapview(kerala_state_world_crop)
-mapview(kerala_state)
-
-kerala_state_crop <- as(linestring_fix, "Spatial")
-mapview(kerala_state_crop)
-
-kerala_state_points_lines <- sample.line(kerala_state_crop, n = 280) ## equally place the number of farms along the coastline 
-class(kerala_state_points_lines)
-plot(kerala_state_points_lines)
-
-kerala_state_points <- st_as_sf(kerala_state_points_lines) %>%
-  mutate(new_id = 1:280) 
-mapview(kerala_state_points)
-
-# Now filter out the points that fall outside of kerala_state: rows 57-70
-kerala_state_points_final <- kerala_state_points %>%
-  filter(new_id %in% c(31:280))
-mapview(kerala_state_points_final)
-
-mean(st_distance(kerala_state_points_final, kerala_state_world_crop))
-
-## get lat lon
-ind_pts <- st_centroid(kerala_state_points_final)
-
-ind_pts_latlon <- st_transform(ind_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_ind <- data.frame(do.call(rbind, st_geometry(ind_pts_latlon)))
-names(farms_ind) <- c("lon", "lat")
-
-farms_ind_final <- farms_ind %>%
-  mutate(iso3c = "IND") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially") %>%
-  mutate(subregion = "Kerala")
-
-## visualize it 
-farms_ind <-  st_as_sf(farms_ind, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_ind)
-
-## write to farms folder 
-write_csv(farms_ind_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_ind.csv"))
+farms_ind <- data.frame(iso3c = "IND", type = "bivalve", n_existing_farms = 250, data_quality = 2.5)
+
+write_csv(farms_ind, here("marine/bivalve/bivalve_farms/data/known_subset_2.5/farms_ind.csv"))
+
 ```
@@
 
+ - Because this is not comprehensive, we will have to gapfill the remaining farms based on a global tonnes/farm estimate. This will be done later, but we will flag this as data_quality = 2 for now.
+
 Source:
@@
   mutate(iso3c = "THA") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_tha, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_tha.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_tha, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_tha.csv"))
 
@@
 
+  - Because this is not comprehensive, we will have to gapfill the remaining farms based on a global tonnes/farm estimate. This will be done later, but we will flag this as data_quality = 2 for now.
+
 ```{r}
@@
   mutate(iso3c = "IDN") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_idn, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_idn.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_idn, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_idn.csv"))
 
@@
  - I can't find any good information on shellfish farming in Russia. I will place a point along the coast.
- - It does seem like scallop farming primarily occurs on the east coast, so I will place it there.
+ - Based on this, we will have to gapfill based on a global tonnes/farm estimate to get a proper number of farm points. Then we will place those points in suitable locations for aquaculture.
 
@@
 ```{r}
-
-farms_rus <- data.frame(lat = c(43.053493816917545),
-                        lon = c(131.95698485517275)) %>%
-  mutate(iso3c = "RUS") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_rus, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_rus.csv"))
-
-## visualize it 
-farms_rus <-  st_as_sf(farms_rus, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_rus)
+rus_gf <- data.frame(iso3c = "RUS", type = "bivalve", num_additional_farms = NA, data_quality = 1)
+write_csv(rus_gf, here("marine/bivalve/bivalve_farms/data/no_info_1/gf_rus.csv"))
 
@@
 
- - I'll place 60 farms along the coast of north korea. Although this specifies "fish farms", it is better than nothing. And there are probably more than 60 farms (shell fish or not), nowadays.
+ - Because this is a very outdated source, and likely includes some fish farms, we will include the 60 fish farms, and later gapfill based on a global tonnes/farm, like we are going to do for India.
 
@@
 ```{r}
-# world <- ne_coastline(scale = 110) #world map with 110m resolution
-# plot(world)
-
-north_korea <- ne_countries(scale = 110, country = "North Korea", returnclass = "sf")
-
-#info of our spatial vector object
-mapview(north_korea)
-plot(north_korea)
-
-# world <- st_as_sf(world)
-
-north_korea_world_crs <- st_transform(north_korea, crs(coast_raw))
-
-north_korea_world_crop <- st_crop(coast_raw, north_korea_world_crs) %>% ## crop to north korea extent
-  dplyr::filter(!(FID %in% c(44790, 135067, 44788:44789, 135092, 135103, 87219, 44955))) %>%
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-
-mapview(north_korea_world_crop)
-
-nk_meters <- st_transform(north_korea_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(nk_meters)
-
-buff <- st_buffer(nk_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-plot(buff)
-
-linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(north_korea_world_crop))
-
-linestring_fix <- st_difference(buffer_outline_fixed, north_korea) ## now grab only the outline 
-mapview(linestring_fix)
-
-north_korea_crop <- as(linestring_fix, "Spatial")
-plot(north_korea_crop)
-mapview(north_korea_crop)
-
-north_korea_points_lines <- sample.line(north_korea_crop, n = 85) ## equally place the number of farms along the coastline 
-class(north_korea_points_lines)
-plot(north_korea_points_lines)
-
-north_korea_points <- st_as_sf(north_korea_points_lines) %>%
-  mutate(new_id = 1:85)
-mapview(north_korea_points)
-
-## Now filter out the points that fall outside of north_korea: rows 57-70
-north_korea_points_final <- north_korea_points %>%
-  filter(new_id %in% c(1:32, 46:47, 55:80 ))
-mapview(north_korea_points_final)
-
-# extract lat lon
-prk_pts <- st_centroid(north_korea_points_final)
-
-prk_pts_latlon <- st_transform(prk_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_prk <- data.frame(do.call(rbind, st_geometry(prk_pts_latlon)))
-names(farms_prk) <- c("lon", "lat")
-
-farms_prk_final <- farms_prk %>%
-  mutate(iso3c = "PRK") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_prk <-  st_as_sf(farms_prk, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_prk)
-
-## write to farms folder 
-write_csv(farms_prk_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_prk.csv"))
+farms_prk <- data.frame(iso3c = "PRK", type = "bivalve", n_existing_farms = 60, data_quality = 2.5)
+
+write_csv(farms_prk, here("marine/bivalve/bivalve_farms/data/known_subset_2.5/farms_prk.csv"))
 ```
@@
 
-```{r}
-
-## read in state shape 
-sta_catarina <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Brazil/Santa_Catarina/dc172qt8462.shp"))
-mapview(sta_catarina)
-
-sta_catarina_world_crs <- st_transform(sta_catarina, crs(coast_raw))
-
-sta_catarina_world_crop <- st_crop(coast_raw, sta_catarina_world_crs) %>% ## crop to santa catarina extent
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>% ## union all the geometries
-  ungroup()
-
-mapview(sta_catarina_world_crop)
-
-sc_meters <- st_transform(sta_catarina_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(sc_meters)
-
-buff <- st_buffer(sc_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-linestring <- st_cast(linestring, "LINESTRING")
-
-brazil <- ne_countries(scale = 10, country = "Brazil", returnclass = "sf")
-mapview(brazil)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(brazil))
-
-linestring_fix <- st_difference(buffer_outline_fixed, brazil) ## now grab only the outline 
-mapview(linestring_fix)
-mapview(sta_catarina_world_crop)
-
-sta_catarina_crop <- as(linestring_fix, "Spatial")
-plot(sta_catarina_crop)
-mapview(sta_catarina_crop)
-
-sta_catarina_points_lines <- sample.line(sta_catarina_crop, n = 24) ## equally place the number of farms along the coastline
-
-sta_catarina_points <- st_as_sf(sta_catarina_points_lines) %>%
-  mutate(new_id = 1:168)  %>%
-  filter(new_id %in% c(1:24, 158, 64, 78))
-
-mapview(sta_catarina_points)
-
-## get lat lon
-bra_pts <- st_centroid(sta_catarina_points)
-
-bra_pts_latlon <- st_transform(bra_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_bra <- data.frame(do.call(rbind, st_geometry(bra_pts_latlon)))
-names(farms_bra) <- c("lon", "lat")
-
-farms_bra_final <- farms_bra %>%
-  mutate(iso3c = "BRA") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially") %>%
-  mutate(subregion = "Santa Catarina")
-
-## visualize it 
-farms_bra <-  st_as_sf(farms_bra, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_bra)
-
-## write to farms folder 
-write_csv(farms_bra_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_bra.csv"))
+ - Although outdated, I will treat this as truth. The FAO backs up that the majority of shell fish farming occurs in Santa Catarina state. Data_quality = 3
+
+```{r}
+
+farms_bra <- data.frame(iso3c = "BRA", type = "bivalve", num_additional_farms = 27, data_quality = 3)
+
+write_csv(farms_bra, here("marine/bivalve/bivalve_farms/data/known_number_farms_3/farms_bra.csv"))
 ```
@@
 http://www.fao.org/3/AB710E/AB710E18.htm#ann12
- - This has the number of farms per province. I will allocate those number equally along the coastline of each province that has farms
+ - This has the number of farms per province. Although a little dated, we will allocate this number (556) of farms into the suitable locations
 
@@
 ```{r}
-## read in province shape
-provinces <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/philippines/provinces/Provinces.shp"))
-
-mapview(provinces)
-
-## filter provinces for the ones we want
-provinces_farms <- provinces %>%
-  dplyr::filter(NAME_1 %in% c("Capiz", "Negros Occidental", "Samar"))
-
-mapview(provinces_farms)
-
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-
-# start with Capiz by placing 300 points along the coast 
-capiz <- provinces_farms %>%
-  dplyr::filter(NAME_1 == "Capiz")
-mapview(capiz)
-plot(capiz)
-
-# world <- st_as_sf(world)
-
-capiz_world_crs <- st_transform(capiz, crs(coast_raw))
-
-capiz_world_crop <- st_crop(coast_raw, capiz_world_crs) %>% ## crop to extent
-  dplyr::filter(!(FID %in% c(443449, 439815, 443448, 439801))) %>%
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-
-mapview(capiz_world_crop)
-
-cp_meters <- st_transform(capiz_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(cp_meters)
-
-buff <- st_buffer(cp_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-linestring <- st_cast(linestring, "LINESTRING")
-
-philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
-mapview(philippines)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))
-
-linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
-mapview(linestring_fix)
-
-capiz_crop <- as(linestring_fix, "Spatial")
-plot(capiz_crop)
-mapview(capiz_crop)
-
-capiz_points_lines <- sample.line(capiz_crop, n = 151) ## equally place the number of farms along the coastline 
-class(capiz_points_lines)
-plot(capiz_points_lines)
-
-capiz_points <- st_as_sf(capiz_points_lines) %>%
-  mutate(new_id = 1:302) %>%
-  filter(!(new_id %in% c(150, 146))) %>%
-  dplyr::select(-new_id)
-mapview(capiz_points)
-
-# now lets place 10 points along the coast of Negros Occidental 
-negros <- provinces_farms %>%
-  dplyr::filter(NAME_1 == "Negros Occidental")
-mapview(negros)
-
-negros_world_crs <- st_transform(negros, crs(coast_raw))
-
-negros_world_crop <- st_crop(coast_raw, negros_world_crs) %>%
-  filter(FID %in% c(224916:224917, 224908:224912)) %>%
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-
-mapview(negros_world_crop)
-
-n_meters <- st_transform(negros_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(n_meters)
-
-buff <- st_buffer(n_meters, dist = 5000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-linestring <- st_cast(linestring, "LINESTRING")
-
-philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
-mapview(philippines)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))
-
-linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
-mapview(linestring_fix)
-
-negros_crop <- as(linestring_fix, "Spatial")
-plot(negros_crop)
-mapview(negros_crop)
-
-negros_points_lines <- sample.line(negros_crop, n = 6) ## equally place the number of farms along the coastline 
-class(negros_points_lines)
-plot(negros_points_lines)
-
-negros_points <- st_as_sf(negros_points_lines)
-mapview(negros_points)
-
-# now lets place 250 points along the coast of samar 
-samar <- provinces_farms %>%
-  dplyr::filter(NAME_1 == "Samar")
-mapview(samar)
-
-samar_world_crs <- st_transform(samar, crs(coast_raw))
-
-samar_world_crop <- st_crop(coast_raw, samar_world_crs) %>%
-  filter(FID %in% c(222688:222691, 222671:222673)) %>%
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-
-mapview(samar_world_crop)
-
-sm_meters <- st_transform(samar_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(sm_meters)
-
-buff <- st_buffer(sm_meters, dist = 3000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-linestring <- st_cast(linestring, "LINESTRING")
-
-philippines <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
-mapview(philippines)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(philippines))
-
-linestring_fix <- st_difference(buffer_outline_fixed, philippines) ## now grab only the outline 
-mapview(linestring_fix)
-
-samar_crop <- as(linestring_fix, "Spatial")
-plot(samar_crop)
-mapview(samar_crop)
-
-samar_points_lines <- sample.line(samar_crop, n = 283) ## equally place the number of farms along the coastline 
-class(samar_points_lines)
-plot(samar_points_lines)
-
-samar_points <- st_as_sf(samar_points_lines) %>%
-  mutate(new_id = 1:283) %>%
-  filter(!(new_id %in% c(2:13, 108:109, 98:100, 79, 74:76, 62:66, 52:53, 14:16, 95:96))) %>%
-  dplyr::select(-new_id)
-mapview(samar_points)
-
-samar_points_final <- samar_points %>%
-  mutate(subregion = "Samar")
-
-negros_points_final <- negros_points %>%
-  mutate(subregion = "Negros Occidental")
-
-capiz_points_final <- capiz_points %>%
-  mutate(subregion = "Capiz")
-
-## bind all three states together
-all_points <- rbind(samar_points_final, negros_points_final, capiz_points_final)
-mapview(all_points)
-
-# get lat lon points
-phl_pts <- st_centroid(all_points)
-
-phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-phl_pts_rgn <-  st_transform(phl_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(subregion)
-
-farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
-names(farms_phl) <- c("lon", "lat")
-
-farms_phl_rgn <- cbind(farms_phl, phl_pts_rgn)
-
-farms_phl_final <- farms_phl_rgn %>%
-  mutate(iso3c = "PHL") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially") %>%
-  dplyr::select(-geometry)
-
-## visualize it 
-farms_phl <-  st_as_sf(farms_phl, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_phl)
-
-## write to farms folder 
-write_csv(farms_phl_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_phl.csv"))
+farms_phl <- data.frame(iso3c = "PHL", type = "bivalve", num_additional_farms = 556, data_quality = 3)
+
+write_csv(farms_phl, here("marine/bivalve/bivalve_farms/data/known_number_farms_3/farms_phl.csv"))
 ```
@@
 
- - I'll place a point on the western coast:
- - 4.074359958576369, 100.73343376478226
+ - Because of a lack of information, this country will need to be gapfilled based on a global tonnes/farm estimate to get an estimate number of farm points to place in suitable locations.
 
@@
 ```{r}
-
-farms_mys <- data.frame(lat = c(4.074359958576369),
-                        lon = c(100.73343376478226)) %>%
-  mutate(iso3c = "MYS") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_mys, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_mys.csv"))
-
-## visualize it 
-farms_mys <-  st_as_sf(farms_mys, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_mys)
+mys_gf <- data.frame(iso3c = "MYS", type = "bivalve", num_additional_farms = NA, data_quality = 1)
+write_csv(mys_gf, here("marine/bivalve/bivalve_farms/data/no_info_1/gf_mys.csv"))
 
@@
 http://www.fao.org/fishery/countrysector/naso_cambodia/en
- - There is no good information on the location of farms, I will just place a point on the coast. 
- - 11.069927194335508, 103.64594001534627
+ - Because of a lack of information, this country will need to be gapfilled based on a global tonnes/farm estimate to get an estimate number of farm points to place in suitable locations.
 
@@
 
-farms_khm <- data.frame(lat = c(11.069927194335508),
-                        lon = c(103.64594001534627)) %>%
-  mutate(iso3c = "KHM") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_khm, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_khm.csv"))
-
-## visualize it 
-farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_khm)
+khm_gf <- data.frame(iso3c = "KHM", type = "bivalve", num_additional_farms = NA, data_quality = 1)
+write_csv(khm_gf, here("marine/bivalve/bivalve_farms/data/no_info_1/gf_khm.csv"))
 
@@
 
- - I will place a point in Deep Bay
+ - I will place a point in Deep Bay. Data quality = 5
 
@@
   mutate(iso3c = "HKG") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_hkg, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_hkg.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_hkg, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_hkg.csv"))
 
@@
 ```{r}
-farm_files <- list.files(here::here("marine/bivalve/bivalve_farms/data/bivalve_sites"), full=TRUE)
+farm_files <- list.files(here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5"), full=TRUE)
 all_farms = plyr::ldply(farm_files, read_csv)
@@
 all_farms_1 <- all_farms %>%
-  dplyr::select(-data_quality, -action_needed)
+  dplyr::select(-data_quality)
+
+write.csv(all_farms_1, here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)
+
+write.csv(all_farms, here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_quality.csv"), row.names = FALSE)
+
+# all_farms <- read_csv(here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), col_types = "ddccd")
 
@@
 
-write.csv(all_farms_1, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"), row.names = FALSE)
-
-write.csv(all_farms, here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv"))
-```
+unique(all_farms$iso3c)
+```

### 2021-03-23 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
Finished reorganizing data

---
title: "Gapfilling the number of farms to add for bivalve countries based on tonnes of production"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all the relevant farm datasets

```{r}

farm_files <- list.files(here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "bivalve")

number_files <- list.files(here("marine/bivalve/bivalve_farms/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

number_files_2.5 <- list.files(here("marine/bivalve/bivalve_farms/data/known_subset_2.5"), full=TRUE)
all_number_2.5 = plyr::ldply(number_files_2.5, read_csv)

subset_farms_files <- list.files(here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/bivalve/bivalve_farms/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

subset_gapfill_2 <- all_known_farms %>%
  filter(data_quality == 2)
```

Read in relevant production data
```{r}
bivalve_tonnes <- read_csv(here::here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
  mutate(type = "bivalve") %>%
  filter(year == 2017)
```

Calculate a global tonnes per farm for bivalve

```{r}
## Filter for data_quality = 4 or 5 and group by country to get number of farms
comprehensive_farms <- all_known_farms %>%
  filter(data_quality %in% c(4,5)) %>% 
  group_by(iso3c, type, data_quality) %>%
  summarise(n_farms = n()) %>% ## now we can see the places that has additional farms to add
  ungroup()

## Join this with the additional farms we need to add to some places, so we can calculate a comprehensive tonnes/farm for bivalve

data_quality_3 <- all_number_3 %>%
    rename("n_farms" = "num_additional_farms")

data_quality_4 <- subset_add_4 %>%
    rename("n_farms" = "num_additional_farms")

comprehensive_farms_total <- comprehensive_farms %>%
  full_join(data_quality_3) %>%
  full_join(data_quality_4) %>%
  group_by(iso3c, type) %>%
  summarise(n_farms = sum(n_farms))

tonnes_per_farm <- comprehensive_farms_total %>%
  left_join(bivalve_tonnes) %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms)

avg_global_bivalve_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_bivalve_tonnes_per_farm # 283.4135
```

Now let's gapfill those that are data quality = 2 and data quality = 1, and data quality = 2.5

```{r}
## start with the subset of locations that need gapfilling based on tonnes/farm
gapfill_2 <- subset_gapfill_2 %>%
  group_by(iso3c, type) %>%
  summarise(n_existing_farms = n()) %>%
  ungroup() %>%
  left_join(bivalve_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## now lets do the locations that have no info and need gapfilling based on tonnes/farm
gapfill_1 <- no_info_1 %>%
  left_join(bivalve_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm) %>%
  mutate(num_additional_farms = ceiling(fao_tonnes_production/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## now lets do the locations that have some information regarding number of farms 
gapfill_2.5 <- all_number_2.5 %>%
  left_join(bivalve_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  mutate(num_additional_farms = num_additional_farms + n_existing_farms) %>% 
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## Wrangle those that just need a specific number of points added (data_quality = 4)

number_add_points_4 <- subset_add_4 %>%
  dplyr::select(-data_quality, -total_farms) %>%
  mutate(estimated = 0, 
         avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm)

```

Now join the gapfilled number of farms with data quality = 3 and write the final file of points that need to allocated

```{r}
number_additional_points <- all_number_3 %>%
  mutate(estimated = 0,
         avg_tonnes_per_farm = avg_global_bivalve_tonnes_per_farm) %>%
  dplyr::select(-data_quality) %>%
  rbind(gapfill_1, gapfill_2, gapfill_2.5, number_add_points_4)

## write this out to our data folder

write.csv(number_additional_points, here("marine/bivalve/bivalve_farms/output/bivalve_points_to_add_final.csv"), row.names = FALSE)
```

Now lets make the file with all of the known farms

```{r}
all_known_farms_final <- all_known_farms %>%
  dplyr::select(-data_quality, -subregion)

write.csv(all_known_farms_final, here("marine/bivalve/bivalve_farms/output/all_known_bivalve_farms_final.csv"), row.names = FALSE)

```

Data check

```{r}
test <- all_known_farms %>% filter(data_quality == 5| iso3c == "CUB") %>%
  group_by(iso3c) %>%
  summarise(n_farms = n()) %>%
  dplyr::select(iso3c)

test_2 <- number_additional_points %>%
  dplyr::select(iso3c)

test_all <- rbind(test, test_2)
length(unique(test_all$iso3c)) ## 42 countries

length(unique(bivalve_tonnes$iso3c)) ## 42 countries

## perfect

```

### 2021-03-23 marine/crustaceans/crustacean_farms/STEP3_gapfill_crustaceans.Rmd
Finished reorganizing data

---
title: "Gapfilling the number of farms to add for shrimp countries based on tonnes of production"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all the relevant farm datasets... the only one that is represented for crustaceans are data_quality = 1.

```{r}

no_info_files <- list.files(here("marine/crustaceans/crustacean_farms/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

```

Read in relevant production data
```{r}
crustaceans_tonnes <- read_csv(here::here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
  mutate(type = "crustaceans") %>%
  filter(year == 2017)
```

Calculate a global tonnes per farm for crustaceans

 - We don't have any tonnes per farm estimates for crustaceans... Therefore we will use the shrimp tonnes/farm, as it is the most similar aquaculture practice to crustaceans.

```{r}
avg_global_shrimp_tonnes_per_farm = 337.7357
avg_global_shrimp_tonnes_per_farm # 337.7357
```

Now let's gapfill those that are data quality = 1
```{r}

## now lets do the locations that have no info and need gapfilling based on tonnes/farm
gapfill_1 <- no_info_1 %>%
  left_join(crustaceans_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_shrimp_tonnes_per_farm) %>%
  mutate(num_additional_farms = ceiling(fao_tonnes_production/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

```

```{r}

## write this out to our data folder

write.csv(gapfill_1, here("marine/crustaceans/crustacean_farms/output/crustaceans_points_to_add_final.csv"), row.names = FALSE)
```

Data check

```{r}

test_2 <- gapfill_1 %>%
  dplyr::select(iso3c)

length(unique(test_2$iso3c)) ## 6 countries

length(unique(crustaceans_tonnes$iso3c)) ## 6 countries

## Perfect

```

### 2021-03-23 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
checked over sources again
Finished reorganizing data

--- 2021-02-12 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
@@
 # [37] "Viet Nam"
-```
-
-## explore
+
+```
+
+# Raster
+
+Standard raster used for this analysis
+
+```{r}
+
+source(here::here("_spatial/template_raster.R"))
+
+```
+
+# Global regions
+
+```{r}
+
+gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
+
+gadm_latlon <- projectRaster(gadm, food_raster)
+
+gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
+  mutate(reg_id = as.numeric(reg_id))
+
+```
+
+```{r}
+
+gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
+  mutate(cellvalue = round(cellvalue, 0))
+
+gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
+
+```
+
+Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
+ - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
+ - If there are not exact locations or comprehensive locations, find the number of farms. 
+ - If there is no information at all, note it. We will gapfill later.
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).
+
+5: Comprehensive number of exact farms
+
+4: Subset of exact locations, need to add a specific number of farms to existing locations. 
+  - country|species|farm locations
+  - country|species|additional points
+
+3: A specific number of farms are known, but no locations 
+ - country|species|additional points
+
+2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
+ - country, species, n_existing_points
+
+2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.
+
+1: No information on number of farms at all. Need to be gapfilled by tonnage. 
+ - country|species|# additional farms (this will be NA)
+
+## Read in ASC data
 https://gis.asc-aqua.org/arcgis_app/
@@
 
-# Raster
-
-Standard raster used for this analysis
-
-```{r}
-
-source(here::here("_spatial/template_raster.R"))
-
-```
-
-# Global regions
-
-```{r}
-
-gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
-
-gadm_latlon <- projectRaster(gadm, food_raster)
-
-gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
-  mutate(reg_id = as.numeric(reg_id))
-
-```
-
-```{r}
-
-gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
-  mutate(cellvalue = round(cellvalue, 0))
-
-gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
-
-```
-
-Now we will map the remaining countries with marine finfish farms that are not included in the ASC dataset. Workflow will be as follows: 
- - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
- - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of finfish farms, equally allocate the farms across the coastline.
-If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
- - Lastly, if there is no evidence of marine finfish farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
-what we've done for Russia for bivalves).
-
-For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
- 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
-   - Must not intersect with land mask
-   - "Land mask"
-
-4: Good qualifications - Locations are projected or it is a only sample of total locations
-   - Must not intersect with land mask
-   - "Land mask"
-
-3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
-   - Must be allocated spatially
-   - Must not intersect with land mask
-   - Flagged as "Allocate spatially"
-
-2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
-   - Must be allocated using suitability analysis.
-   - Flagged as 2 and "state/province suitability"
-
-1: Very Bad qualifications - No data at all.
-   - Must be allocated using suitability analysis.
-   - Flagged as 1 and "country suitability"
-
 # Map data from ASC
@@
   cbind(iso) %>%
-  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands")))
+  dplyr::filter(!(crt_cnt %in% c("Denmark", "Germany", "Netherlands", "Greece", "Spain"))) ## don't need Spain or greece since it is already represented in EMODnet data
 
@@
 farms_all_fin <- farms_all_fin %>%
-  cbind(iso3c = all_pts_latlon$iso3c) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
+  cbind(iso3c = all_pts_latlon$iso3c)
 
 ## save farm location
-write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)
+write.csv(farms_all_fin, here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv"), row.names = FALSE)
+
+```
+
+Now we need to map for each country, and assign a flag for gapfilling which will be completed later. I will start with all of the countries list in the ASC data.
+
+## Turkey
+
+Need to add 301 points to existing 22 (a final total of 323 points)
+
+Data is from the ASC so it is a subset.
+
+However, the FAO gives us specific numbers: http://www.fao.org/fishery/countrysector/naso_turkey/en
+ - 309 Seabass/seabream farms 
+ - 1 seabass farm, 13 seabass and bream and new species
+
+ Data quality = 4
+
+```{r}
+farms_tur <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "TUR") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_tur, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_tur.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+tur_additional <- data.frame(iso3c = "TUR", type = "marine_fish_general", num_additional_farms = 301, data_quality = 4, total_farms = 323)
+write.csv(tur_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_tur.csv"), row.names = FALSE)
+```
+
+## Croatia
+
+Need to add 48 points to existing 11 (a final total of 59 points)
+
+Current data is 11 points from ASC
+
+This claims there are 59 total farms in Croatia, so we will add more to the current points there: 
+Lukin, A., 2014. Spatial Planning For Marine Aquaculture, Croatia, Zadar County Case. Croatian Ministry of Agriculture, Directorate of Fisheries.
+
+```{r}
+farms_hrv <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "HRV") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_hrv, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_hrv.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+hrv_additional <- data.frame(iso3c = "HRV", type = "marine_fish_general", num_additional_farms = 48, data_quality = 4, total_farms = 59)
+write.csv(hrv_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_hrv.csv"), row.names = FALSE)
+```
+
+## Albania
+
+Need to add 22 points to existing 1 (a final total of 23 points)
+
+Current data is from the ASC, which is a subset of farms.
+
+http://www.fao.org/fishery/countrysector/naso_albania/en
+“There are 23 marine cage farms, all of them situated in the Ionic Sea. They produce sea bream and sea bass”
+
+```{r}
+farms_alb <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "ALB") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_alb, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_alb.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+alb_additional <- data.frame(iso3c = "ALB", type = "marine_fish_general", num_additional_farms = 22, data_quality = 4, total_farms = 23)
+write.csv(alb_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_alb.csv"), row.names = FALSE)
+```
+
+## Japan
+Current data is from ASC, only 8 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Japan.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_jpn <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "JPN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_jpn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_jpn.csv"))
+
+```
+
+## Australia 
+Current data is from ASC, only 5 farms, so probably not comprehensive.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_aus <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "AUS") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_aus, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_aus.csv"))
+
+```
+
+## Mexico
+
+Current data is from ASC, only 2 farms, so maybe not comprehensive.
+There are likely more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_mex <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "MEX") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_mex, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_mex.csv"))
+
+```
+
+## Panama
+Current data is from ASC, only 1 farms, so probably not comprehensive.
+There are likely more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_pan <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "PAN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_pan, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_pan.csv"))
+
+```
+
+## USA
+Current data is from ASC, only 1 farms, so definitely not comprehensive.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_usa <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "USA") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_usa, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_usa.csv"))
+
+```
+
+## Viet Nam
+Current data is from ASC, only 5 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Viet Nam.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_vnm <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "VNM") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_vnm, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_vnm.csv"))
+
+```
+
+## Thailand
+Current data is from ASC, only 1 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Thailand.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_tha <- read.csv(here("marine/marine_fish_general/finfish_farms/data/ASC_finfish_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "THA") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_tha, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_tha.csv"))
 
@@
   dplyr::select(-COUNTRY) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
- write_csv(farms_eu_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ESP_CYP_NOR_GRC_MLT.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_eu_final, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_ESP_CYP_NOR_GRC_MLT.csv"))
 
@@
 From http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/italy/en/
-
-Source:
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+ - We will use these as existing farm points, but need to add the remaining farms that are known about.
+
+Source:
+NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
+
+Need to add 81 points to existing 9 (a final total of 90 points)
+
+Only a subset of points based on NASO satellite maps
+
+However FAO reports there were 90 finfish farms in 2013...
+
+"Ninety farms (11 percent of the total number of aquaculture farms) operated in 2013.
+Seabass and seabream as well as other species such as grey mullets and European eel are also cultured under extensive and semi-extensive conditions in coastal areas (e.g.
+“valli”, ponds and lagoons) of the northern Adriatic regions and in Sardinia, Sicily, Apulia and Lazio."
+http://www.fao.org/fishery/countrysector/naso_italy/en
 
@@
   mutate(iso3c="ITA") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_ita, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ita.csv"))
+  mutate(data_quality = 4)
+
+write_csv(farms_ita, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_ita.csv"))
 
@@
 mapview(farms_ita)
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+ita_additional <- data.frame(iso3c = "ITA", type = "marine_fish_general", num_additional_farms = 81, data_quality = 4, total_farms = 90)
+write.csv(ita_additional, here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4/add_farms_ita.csv"), row.names = FALSE)
 ```
@@
 Source:
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites
+
+ - These are both not comprehensive, and I can't find any information on specific numbers of farms. So both will be labeled as data quality = 2 and need to be gapfilled based on the remaining tonnes.
 
@@
   dplyr::select(-country, -geometry) %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_fra, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_fra_isr.csv"))
-
-farms_fra <-  st_as_sf(farms_fra, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_fra)
+  mutate(data_quality = 2)
+
+write_csv(farms_fra, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_fra_isr.csv"))
+
 ```
@@
 Source: 
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
+
+Current data is a subset, only 6 farms, so definitely not comprehensive, just a drop in the bucket compared to the production of Indonesia.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
 
@@
 indo_aqua <- read_sf(indo_file)
-
-mapview(indo_aqua)
 
@@
   mutate(iso3c = "IDN") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_idn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_idn.csv"))
-
-farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_idn)
+  mutate(data_quality = 2)
+
+write_csv(farms_idn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_idn.csv"))
+
 ```
@@
  - According to the table, by these criteria, there are 112 marine tank farm systems in Portugal. 
- - I will equally allocate 112 points along the coast of Portugal.
-
-Source: 
-Estatísticas da Pesca, 2020. . Instituto Nacional de Estatística. [Accessed December 21, 2020]
-
-```{r}
-world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
-plot(world)
-
-portugal <- ne_countries(scale = 10, country = "Portugal", returnclass = "sf")
-
-#info of our spatial vector object
-portugal
-mapview(portugal)
-plot(portugal)
-
-world <- st_as_sf(world)
-
-portugal_world_crs <- st_transform(portugal, crs(world))
-
-portugal_world_crop <- st_crop(world, portugal_world_crs) #%>%
- # dplyr::filter(scalerank == 5) ## filter for the appropriate island
-plot(portugal_world_crop)
-mapview(portugal_world_crop)
-
-portugal_crop <- as(portugal_world_crop, "Spatial")
-
-portugal_points_lines <- sample.line(portugal_crop, n = 380) ## equally place the number of farms along the coastline 
-class(portugal_points_lines)
-plot(portugal_points_lines)
-
-portugal_points <- st_as_sf(portugal_points_lines)
-mapview(portugal_points)
-
-portugal_points_final <- portugal_points[253:364, ] ## grab the appropriate number of points
-mapview(portugal_points_final)
-
-## now prep dataframe for lat lon points
-prt_pts <- st_centroid(portugal_points_final)
-
-prt_pts_latlon <- st_transform(prt_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_prt <- data.frame(do.call(rbind, st_geometry(prt_pts_latlon)))
-names(farms_prt) <- c("lon", "lat")
-
-farms_prt_final <- farms_prt %>%
-  mutate(iso3c = "PRT") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_prt <-  st_as_sf(farms_prt, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_prt)
-
-## write to farms folder 
-write_csv(farms_prt_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_prt.csv"))
+ - I will equally allocate 112 points along the coast of Portugal in suitable locations.
+
+Source: 
+Estatísticas da Pesca, 2020. Instituto Nacional de Estatística. [Accessed December 21, 2020]
+
+```{r}
+farms_prt <- data.frame(iso3c = "PRT", type = "marine_fish_general", num_additional_farms = 112, data_quality = 3)
+
+write_csv(farms_prt, here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3/farms_prt.csv"))
+
 ```
@@
 
-The only species the FAO reports for Iran is "Marine fishes nei", and I can't find any information on number of marine farms there might be in Iran.
-Therefore I will place one farm on the Caspian Sea coast.
+The only species the FAO reports for Iran is "Marine fishes nei", and I can't find any information on number of marine farms there might be in Iran. This will have to be fully gapfilled.
 
@@
 ```{r}
-
-farms_irn <- data.frame(lat = c(37.392419247868425),
-                        lon = c(50.1602963496454)) %>%
-  mutate(iso3c = "IRN") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_irn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_irn.csv"))
-
-## visualize it 
-farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_irn)
+irn_gf <- data.frame(iso3c = "IRN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(irn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_irn.csv"))
+
 ```
@@
 ## China 
-Can't find any datasets of marine finfish farm locations in China. Therefore I will place one farm on the coast of China.
+Can't find any datasets of marine finfish farm locations in China. This will need to be fully gapfilled.
 
@@
 ```{r}
-
-farms_chn <- data.frame(lat = c(26.649767732301385),
-                        lon = c(119.94149300994019)) %>%
-  mutate(iso3c = "CHN") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_chn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_chn.csv"))
-
-## visualize it 
-farms_chn <-  st_as_sf(farms_chn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_chn)
+chn_gf <- data.frame(iso3c = "CHN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(chn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_chn.csv"))
+
 ```
@@
 
+ - I beleive this is comprehensive.
+
 Source:
@@
   mutate(iso3c = "SAU") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_sau, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_sau.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_sau, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_sau.csv"))
 
@@
 
-Can't find any datasets of marine finfish farm locations. Therefore I will place one farm on the coast. It probably doesn't matter, since Mauritius is so small anyways.
+Can't find any datasets of marine finfish farm locations. This will need to be fully gapfilled.
 
@@
 ```{r}
-
-farms_mus <- data.frame(lat = c(-20.005039247819017),
-                        lon = c(57.67022708374523)) %>%
-  mutate(iso3c = "MUS") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_mus, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_mus.csv"))
-
-## visualize it 
-farms_mus <-  st_as_sf(farms_mus, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_mus)
+mus_gf <- data.frame(iso3c = "MUS", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(mus_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_mus.csv"))
+
 ```
@@
   mutate(iso3c = "ARE") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_are, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_are.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_are, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_are.csv"))
 
@@
 
- - I'll place 20 points along the coast of Monastir
+ - I'll place 20 points along the coast of Monastir in suitable locations.
 
@@
 ```{r}
-## load municipality shapefile, downloaded from here: https://gadm.org/download_country_v3.html
-tunisia <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Tunisia/gadm36_TUN_shp/gadm36_TUN_1.shp")) %>%
-  dplyr::filter(NAME_1 == "Monastir")
-
-mapview(tunisia)
-
-## OR if you don't municipality and only country info you could use this: 
-# tunisia <- rnaturalearth::ne_countries(country = "Tunisia")
-
-world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
-plot(world)
-class(world)
-
-#info of our spatial vector object
-tunisia
-mapview(tunisia)
-
-world <- st_as_sf(world)
-
-tunisia_world_crs <- st_transform(tunisia, crs(world))
-
-tunisia_world_crop <- st_crop(world, tunisia_world_crs) 
-plot(tunisia_world_crop)
-mapview(tunisia_world_crop)
-
-tunisia_crop <- as(tunisia_world_crop, "Spatial")
-class(tunisia_crop)
-mapview(tunisia_crop)
-
-tunisia_points_lines <- sample.line(tunisia_crop, n = 20) ## equally place the number of farms along the coastline 
-class(tunisia_points_lines)
-plot(tunisia_points_lines)
-
-tunisia_points <- st_as_sf(tunisia_points_lines)
-mapview(tunisia_points)
-
-## now prep dataframe for lat lon points
-tun_pts <- st_centroid(tunisia_points)
-
-tun_pts_latlon <- st_transform(tun_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_tun <- data.frame(do.call(rbind, st_geometry(tun_pts_latlon)))
-names(farms_tun) <- c("lon", "lat")
-
-farms_tun_final <- farms_tun %>%
-  mutate(iso3c = "TUN") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_tun <-  st_as_sf(farms_tun, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_tun)
-
-## write to farms folder 
-write_csv(farms_tun_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_tun.csv"))
+farms_tun <- data.frame(iso3c = "TUN", type = "marine_fish_general", num_additional_farms = 20, data_quality = 3)
+
+write_csv(farms_tun, here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3/farms_tun.csv"))
 ```
@@
 This is a really old paper, but it is the best I can find.
-42 total points
+42 total points.
 
@@
 
-Combine milkfish and grouper points
+Combine milkfish and grouper points. These are not comprehensive points, so the rest of the production is going to need to be gapfilled.
 
@@
   dplyr::mutate(iso3c = "TWN") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 2)
 
@@
 ## write to farms folder 
-write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_twn.csv"))
+write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_twn.csv"))
 
@@
 
-9.423478373794573, -84.20910189917947
+9.423478373794573, -
+
+ - This is likely just a subset of total farms, so I will gapfill the remaining production. Data quality = 2
 
@@
   mutate(iso3c = "CRI") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_cri, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_cri.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_cri, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_cri.csv"))
 
@@
 
+ - The map shown here is the MAIN aquaculture farms, meaning that there could be more. I will gapfill the rest.
+
 ```{r}
@@
                         rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
-                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
+                        subregion = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
   mutate(iso3c = "EGY") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_egy, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_egy.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_egy, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_egy.csv"))
 
@@
 
-There is not much information on locations of aquaculture facilities.
-However, this shows "Mandapam Hatchery" 80000 tonnes of marine finfish in 2015...
-The total for 2017 is 96000.
-I think it is reasonable to place a point on Mandapam, at the CMFRI farm, and leave it at that.
+There is not much information on locations of aquaculture facilities. This will be fully gapfilled.
+
 http://www.cmfri.org.in/division/mariculture
 
-9.28696221512509, 79.13007737814245
-
-Source:
-Indian Council of Agriculture Research - Central Marine Fisheries Research Institute, 2015.  http://www.cmfri.org.in/division/mariculture
-
-```{r}
-farms_ind <- data.frame(lat = c(9.28696221512509),
-                        lon = c(79.13007737814245)) %>%
-  mutate(iso3c = "IND") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_ind, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_ind.csv"))
-
-## visualize it 
-farms_ind <-  st_as_sf(farms_ind, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_ind)
+```{r}
+ind_gf <- data.frame(iso3c = "IND", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(ind_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_ind.csv")) 
 ```
@@
 Source: 
-Food Farms in Singapore, 2019. . Singapore Food Agency. [Accessed December 17, 2020] https://www.sfa.gov.sg/food-farming/food-farms/farming-in-singapore
-
-```{r}
-world <- rnaturalearth::ne_coastline(scale = 10) # world map with 10m resolution
-plot(world)
-
-singapore <- ne_countries(scale = 50, country = "Singapore", returnclass = "sf")
-
-#info of our spatial vector object
-singapore
-mapview(singapore)
-plot(singapore)
-
-world <- st_as_sf(world)
-
-singapore_world_crs <- st_transform(singapore, crs(world))
-
-singapore_world_crop <- st_crop(world, singapore_world_crs) %>%
-  dplyr::filter(scalerank == 3) ## filter for the appropriate area
-plot(singapore_world_crop)
-mapview(singapore_world_crop)
-
-singapore_crop <- as(singapore_world_crop, "Spatial")
-
-singapore_points_lines <- sample.line(singapore_crop, n = 225) ## equally place the number of farms along the coastline 
-class(singapore_points_lines)
-plot(singapore_points_lines)
-
-singapore_points <- st_as_sf(singapore_points_lines)
-mapview(singapore_points)
-
-singapore_points_final <- singapore_points[106:214, ] ## grab the appropriate number of points
-mapview(singapore_points_final)
-
-## now prep dataframe for lat lon points
-sgp_pts <- st_centroid(singapore_points_final)
-
-sgp_pts_latlon <- st_transform(sgp_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_sgp <- data.frame(do.call(rbind, st_geometry(sgp_pts_latlon)))
-names(farms_sgp) <- c("lon", "lat")
-
-farms_sgp_final <- farms_sgp %>%
-  mutate(iso3c = "SGP") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_sgp <-  st_as_sf(farms_sgp, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_sgp)
-
-## write to farms folder 
-write_csv(farms_sgp_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_sgp.csv"))
+Food Farms in Singapore, 2019. Singapore Food Agency. [Accessed December 17, 2020] https://www.sfa.gov.sg/food-farming/food-farms/farming-in-singapore
+
+```{r}
+farms_sgp <- data.frame(iso3c = "SGP", type = "marine_fish_general", num_additional_farms = 109, data_quality = 3)
+
+write_csv(farms_sgp, here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3/farms_sgp.csv"))
 ```
@@
 Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. . Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78
+
+ - This is just a subset of farms, since this only represents industrial practices. We will need to gapfill some.
 
@@
   mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_mys, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_mys.csv"))
+  mutate(subregion = c("Sempang, Malacca", "Rompin, Pahang", "Permatang Pauh, Pahang", "Rompin, Pahang", "Sempang, Malacca"))
+
+write_csv(farms_mys, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_mys.csv"))
 
@@
 ```{r}
-farms_bgd <- data.frame(lat=c(21.802433819366538),
-                        lon=c(90.40418040967)) %>%
-  mutate(iso3c = "BGD") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_bgd, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_bgd.csv"))
-
-## visualize it 
-farms_bgd <-  st_as_sf(farms_bgd, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_bgd)
+bgd_gf <- data.frame(iso3c = "BGD", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(bgd_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_bgd.csv")) 
 ```
@@
  - Farms are definitely located in Prey Nob, Stoeng Hav, and Thomnob Rolork. 
- - This is the only information I can find on Cambodian Barramundi fishing, so I will place 3 points in these 3 places. It is really small production anyways.
-
-Prey Nob: 10.53427341558665, 103.57357940185497
-Stoeng Hav: 10.748668380457524, 103.6089106992865
-Thomnob Rolork: 10.647924480438327, 103.5006922685572
-
+ - This is the only information I can find on Cambodian Barramundi fishing. 
 Source:
@@
 
-```{r}
-farms_khm <- data.frame(lat=c(10.53427341558665, 10.748668380457524, 10.647924480438327),
-                        lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
-  mutate(iso3c = "KHM") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_khm, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_khm.csv"))
-
-## visualize it 
-farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_khm)
+ - Although this source is really good, there are no specific locations or numbers. This will need to be fully gapfilled.
+
+```{r}
+khm_gf <- data.frame(iso3c = "KHM", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(khm_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_khm.csv")) 
 ```
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
-plot(world)
-
-south_korea <- ne_countries(scale = 50, country = "South Korea", returnclass = "sf")
-
-#info of our spatial vector object
-south_korea
-mapview(south_korea)
-plot(south_korea)
-
-world <- st_as_sf(world)
-
-south_korea_world_crs <- st_transform(south_korea, crs(world))
-
-south_korea_world_crop <- st_crop(world, south_korea_world_crs) #%>%
- # dplyr::filter(scalerank == 3) ## filter for the appropriate area
-
-south_korea_world_crop <- south_korea_world_crop[2, ]
-plot(south_korea_world_crop)
-mapview(south_korea_world_crop)
-
-south_korea_crop <- as(south_korea_world_crop, "Spatial")
-
-south_korea_points_lines <- sample.line(south_korea_crop, n = 612) ## equally place the number of farms along the coastline 
-class(south_korea_points_lines)
-plot(south_korea_points_lines)
-
-south_korea_points <- st_as_sf(south_korea_points_lines)
-mapview(south_korea_points)
-
-## now prep dataframe for lat lon points
-kor_pts <- st_centroid(south_korea_points)
-
-kor_pts_latlon <- st_transform(kor_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_kor <- data.frame(do.call(rbind, st_geometry(kor_pts_latlon)))
-names(farms_kor) <- c("lon", "lat")
-
-farms_kor_final <- farms_kor %>%
-  mutate(iso3c = "KOR") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_kor <-  st_as_sf(farms_kor, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_kor)
-
-## write to farms folder 
-write_csv(farms_kor_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_kor.csv"))
+farms_kor <- data.frame(iso3c = "KOR", type = "marine_fish_general", num_additional_farms = 612, data_quality = 3)
+
+write_csv(farms_kor, here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3/farms_kor.csv"))
 ```
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
-plot(world)
-
-philippines <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
-
-#info of our spatial vector object
-philippines
-mapview(philippines)
-plot(philippines)
-
-world <- st_as_sf(world)
-
-philippines_world_crs <- st_transform(philippines, crs(world))
-
-philippines_world_crop <- st_crop(world, philippines_world_crs) #%>%
- # dplyr::filter(scalerank == 3) ## filter for the appropriate area
-
-philippines_world_crop <- philippines_world_crop[-1, ]
-plot(philippines_world_crop)
-mapview(philippines_world_crop)
-
-philippines_crop <- as(philippines_world_crop, "Spatial")
-
-philippines_points_lines <- sample.line(philippines_crop, n = 43) ## equally place the number of farms along the coastline 
-class(philippines_points_lines)
-plot(philippines_points_lines)
-
-philippines_points <- st_as_sf(philippines_points_lines)
-mapview(philippines_points)
-
-## now prep dataframe for lat lon points
-phl_pts <- st_centroid(philippines_points)
-
-phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
-names(farms_phl) <- c("lon", "lat")
-
-farms_phl_final <- farms_phl %>%
-  mutate(iso3c = "PHL") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_phl <-  st_as_sf(farms_phl, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_phl)
-
-## write to farms folder 
-write_csv(farms_phl_final, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_phl.csv"))
+phl_gf <- data.frame(iso3c = "PHL", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+write_csv(phl_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_phl.csv"))
+
 ```
@@
   mutate(iso3c = "HKG") %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_hkg, here("marine/marine_fish_general/finfish_farms/data/finfish_sites/farms_hkg.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_hkg, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_hkg.csv"))
 
@@
 ```{r}
-farm_files <- list.files(here::here("marine/marine_fish_general/finfish_farms/data/finfish_sites"), full=TRUE)
+farm_files <- list.files(here::here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5"), full=TRUE)
 all_farms = plyr::ldply(farm_files, read_csv)
@@
 all_farms_1 <- all_farms %>%
-  dplyr::select(-data_quality, -action_needed)
+  dplyr::select(-data_quality)
 

### 2021-03-23 marine/marine_fish_general/finfish_farms/STEP3_gapfill_finfish.Rmd
Finished reorganizing data

---
title: "Gapfilling the number of farms to add for marine_fish_general countries based on tonnes of production"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all the relevant farm datasets

```{r}

farm_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "marine_fish_general")

number_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

number_files_2.5 <- list.files(here("marine/marine_fish_general/finfish_farms/data/known_subset_2.5"), full=TRUE)
all_number_2.5 = plyr::ldply(number_files_2.5, read_csv)

subset_farms_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

subset_gapfill_2 <- all_known_farms %>%
  filter(data_quality == 2)
```

Read in relevant production data
```{r}
marine_fish_general_tonnes <- read_csv(here::here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
  mutate(type = "marine_fish_general") %>%
  filter(year == 2017)
```

Calculate a global tonnes per farm for marine_fish_general

```{r}
## Filter for data_quality = 4 or 5 and group by country to get number of farms
comprehensive_farms <- all_known_farms %>%
  filter(data_quality %in% c(4,5)) %>% 
  group_by(iso3c, type, data_quality) %>%
  summarise(n_farms = n()) %>% ## now we can see the places that has additional farms to add
  ungroup()

## Join this with the additional farms we need to add to some places, so we can calculate a comprehensive tonnes/farm for marine_fish_general

data_quality_3 <- all_number_3 %>%
    rename("n_farms" = "num_additional_farms")

data_quality_4 <- subset_add_4 %>%
    rename("n_farms" = "num_additional_farms")

comprehensive_farms_total <- comprehensive_farms %>%
  full_join(data_quality_3) %>%
  full_join(data_quality_4) %>%
  group_by(iso3c, type) %>%
  summarise(n_farms = sum(n_farms))

tonnes_per_farm <- comprehensive_farms_total %>%
  left_join(marine_fish_general_tonnes) %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms)

avg_global_marine_fish_general_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_marine_fish_general_tonnes_per_farm # 864.3575
```

Now let's gapfill those that are data quality = 2 and data quality = 1, and data quality = 2.5 (if applicable)

```{r}
## start with the subset of locations that need gapfilling based on tonnes/farm
gapfill_2 <- subset_gapfill_2 %>%
  group_by(iso3c, type) %>%
  summarise(n_existing_farms = n()) %>%
  ungroup() %>%
  left_join(marine_fish_general_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_marine_fish_general_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## now lets do the locations that have no info and need gapfilling based on tonnes/farm
gapfill_1 <- no_info_1 %>%
  left_join(marine_fish_general_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_marine_fish_general_tonnes_per_farm) %>%
  mutate(num_additional_farms = ceiling(fao_tonnes_production/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## Wrangle those that just need a specific number of points added (data_quality = 4)

number_add_points_4 <- subset_add_4 %>%
  dplyr::select(-data_quality, -total_farms) %>%
  mutate(estimated = 0, 
         avg_tonnes_per_farm = avg_global_marine_fish_general_tonnes_per_farm)

```

Now join the gapfilled number of farms with data quality = 3 and write the final file of points that need to allocated

```{r}
number_additional_points <- all_number_3 %>%
  mutate(estimated = 0,
         avg_tonnes_per_farm = avg_global_marine_fish_general_tonnes_per_farm) %>%
  dplyr::select(-data_quality) %>%
  rbind(gapfill_1, gapfill_2, number_add_points_4)

## write this out to our data folder

write.csv(number_additional_points, here("marine/marine_fish_general/finfish_farms/output/marine_fish_general_points_to_add_final.csv"), row.names = FALSE)
```

Now lets make the file with all of the known farms

```{r}
all_known_farms_final <- all_known_farms %>%
  dplyr::select(-data_quality, -rgn_production, -subregion)

write.csv(all_known_farms_final, here("marine/marine_fish_general/finfish_farms/output/all_known_finfish_farms_final.csv"), row.names = FALSE)

```

Data check

```{r}
test <- all_known_farms %>%
  group_by(iso3c) %>%
  summarise(n_farms = n()) %>%
  dplyr::select(iso3c)

test_2 <- number_additional_points %>%
  dplyr::select(iso3c)

test_all <- rbind(test, test_2)
length(unique(test_all$iso3c)) ## 37 countries

length(unique(marine_fish_general_tonnes$iso3c)) ## 37 countries

## Perfect

```

### 2021-03-23 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
Finished reorganizing data

--- 2021-02-08 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
@@
 
-```{r}
-
-coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
-
-mapview(head(coast_raw))
-
-```
-
 # Global regions
@@
 
-For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0).
+Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
+ - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
+ - If there are not exact locations or comprehensive locations, find the number of farms. 
+ - If there is no information at all, note it.
 
-Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
+ 5: Comprehensive number of exact farms
 
-Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps)
+4: Subset of exact locations, need to add a specific number of farms to existing locations. 
+  - country|species|farm locations
+  - country|species|additional points
 
-Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
+3: A specific number of farms are known, but no locations 
+ - country|species|additional points
 
-Bad qualifications: Per province/state locations (i.e.
-placing a point randomly in each provice), no data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.
+2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.
+
+1: No information on number of farms at all. Need to be gapfilled by tonnage. 
+ - country|species|# additional farms (this will be NA)
 
@@
   mutate(iso3c="CHL") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_chile, here("marine/salmon/salmon_farm/data/farm_sites/farms_chile.csv"))
+write_csv(farms_chile, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_chile.csv"))
 
@@
 We use the number of salmon licenses to get a proxy for the relative distribution of production along the Norwegian coast. 
-
+†
 ## Load csv with lat long
-License data.
+Comprehensive License data.
 
@@
   distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") %>% # Counting duplicate liscense locations once
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_nor, here("marine/salmon/salmon_farm/data/farm_sites/farms_nor.csv"))
+write_csv(farms_nor, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nor.csv"))
+
+norway <- read_csv(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nor.csv"))
+
+norway_sf <- st_as_sf(norway, coords = c("lon", "lat"), 
+                         crs = crs(gadm_latlon), agr = "constant")
+
+mapview(norway_sf)
 
@@
 # Scotland
+ - Comprehensive data
 
@@
   mutate(iso3c = "GBR") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_scotland, here("marine/salmon/salmon_farm/data/farm_sites/farms_scotland.csv"))
+write_csv(farms_scotland, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_scotland.csv"))
 
@@
 
+ - Even though it is ASC, all indications point to that it is comprehensive.
+
 Source: 
-Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
+Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
 https://gis.asc-aqua.org/arcgis_app/
@@
   cbind(iso3c = fro_pts_latlon$iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_all_fro, here("marine/salmon/salmon_farm/data/farm_sites/farms_fro.csv"))
+write_csv(farms_all_fro, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_fro.csv"))
 
@@
 # Australia
+
+ - Comprehensive data
 
@@
   mutate(iso3c="AUS") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_tas, here("marine/salmon/salmon_farm/data/farm_sites/farms_tas.csv"))
+write_csv(farms_tas, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_tas.csv"))
 
@@
 
+ - Comprehensive data
+
 Source: 
@@
   mutate(iso3c="CAN") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_bc, here("marine/salmon/salmon_farm/data/farm_sites/farms_bc_can.csv"))
+write_csv(farms_bc, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_bc_can.csv"))
 
@@
 ## New Brunswick
+
+ - Comprehensive data
+
 Source: 
@@
   mutate(iso3c="CAN") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_nb, here("marine/salmon/salmon_farm/data/farm_sites/farms_nb_can.csv"))
+write_csv(farms_nb, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nb_can.csv"))
 
@@
 
+ - Comprehensive data
+
 Source: 
 Nova Scotia Marine Aquaculture Leases , 2020.
-.
 Nova Scotia Fisheries and Aquaculture.
@@
   mutate(iso3c="CAN") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_ns, here("marine/salmon/salmon_farm/data/farm_sites/farms_ns_can.csv"))
+write_csv(farms_ns, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ns_can.csv"))
 
@@
 ## Newfoundland and Labrador
+
+ - Comprehensive data
 
@@
   dplyr::select(lon, lat, iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_new_lab, here("marine/salmon/salmon_farm/data/farm_sites/farms_new_lab_can.csv"))
+write_csv(farms_new_lab, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_new_lab_can.csv"))
 
@@
 
-Source:
-
 ## Puget Sound
@@
 
- - this will receive a 0.667 (good quality), since I do not believe it is comprehensive, and is only a sample of points.
+ - NOT comprehensive, existing points need gapfilling
 
@@
   dplyr::select(lon, lat, iso3c) %>%
-  mutate(data_quality = 0.667)
+  mutate(data_quality = 2)
 
-write_csv(farms_ps, here("marine/salmon/salmon_farm/data/farm_sites/farms_ps_usa.csv"))
+write_csv(farms_ps, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ps_usa.csv"))
 
@@
 Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 17, 2020] https://www.northeastoceandata.org/data-download/
+
+ - NOT comprehensive, existing points need gapfilling
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 2)
 
-write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/farm_sites/farms_ne_usa.csv"))
+write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ne_usa.csv"))
 
@@
 https://gis.asc-aqua.org/arcgis_app/
+
+ - comprehensive (need to add to existing points) - We need add 22 points to existing 1 (a final total 23 of  points)
+
+http://www.fao.org/fishery/countrysector/naso_newzealand/en
+“There were 23 king salmon farms in 2004 occupying 60 hectares of water space and producing 7 400 tonnes of fish (NZAC, 2005).
+Most of these farms were located in marine waters in the Marlborough Sounds, and Stewart Island, but also a smaller number in freshwater in hydroelectric water channels”
 
@@
   cbind(iso3c = nzl_pts_latlon$iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 4)
 
-write_csv(farms_all_nzl, here("marine/salmon/salmon_farm/data/farm_sites/farms_nz.csv"))
+write_csv(farms_all_nzl, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_nz.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+nz_additional <- data.frame(iso3c = "NZL", type = "salmon", num_additional_farms = 22, data_quality = 4)
+write.csv(nz_additional, here("marine/salmon/salmon_farm/data/subset_known_add_points_4/add_farms_nz.csv"), row.names = FALSE)
 
@@
 Downloaded from here (Jan 31 2020): https://www.agriculture.gov.ie/seafood/engineering/publications/gisdata/
+
+ - Comprehensive data
 
@@
   mutate(iso3c="IRL") %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write_csv(farms_ire, here("marine/salmon/salmon_farm/data/farm_sites/farms_ire.csv"))
+write_csv(farms_ire, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ire.csv"))
 
@@
 
+ - No info at all, needs to be fully gapfilled
+
 ```{r}
 
-# lat long estimates from google earth
-farms_russia <- data.frame(lon=c(33.7149),
-                    lat=c(69.4953)) %>%
-  mutate(iso3c = "RUS") %>%
-  mutate(data_quality = 0.0)
+# farms_russia <- data.frame(lon=c(33.7149),
+#                     lat=c(69.4953)) %>%
+#   mutate(iso3c = "RUS") %>%
+#   mutate(data_quality = 1) %>%
+#   mutate(action_needed = "country based suitability")
+# 
+# write_csv(farms_russia, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_russia.csv"))
 
-write_csv(farms_russia, here("marine/salmon/salmon_farm/data/farm_sites/farms_russia.csv"))
-
+# Write a file for russia to indicate it has no information and will need to be fully gapfilled
+rus_gf <- data.frame(iso3c = "RUS", type = "salmon", num_additional_farms = NA, data_quality = 1)
+write_csv(rus_gf, here("marine/salmon/salmon_farm/data/no_info_1/gf_rus.csv"))
 ```
@@
   cbind(iso3c = JPN_pts_latlon$iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 2)
 
-write_csv(farms_all_JPN, here("marine/salmon/salmon_farm/data/farm_sites/farms_japan.csv"))
+write_csv(farms_all_JPN, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_japan.csv"))
 
@@
 Source: 
-HELCOM Map and Data Service, n.d. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM HOLAS II Dataset: Finfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
   dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write.csv(farms_dk, here("marine/salmon/salmon_farm/data/farm_sites/farms_denmark.csv"), row.names = FALSE)
+write.csv(farms_dk, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_denmark.csv"), row.names = FALSE)
 
-#farms_dk <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/farm_sites/farms_denmark.csv"))
+#farms_dk <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_denmark.csv"))
 ```
@@
 
-Page 33 of this indicates there are 12 marine rainbow trout farms in turkey: http://tudav.org/wp-content/uploads/2018/04/marine_aquaculture_in_turkey.pdf
+http://www.fao.org/fishery/countrysector/naso_turkey/en
+14 Trout and seabass farms, 6 trout farms, 1 seabass and bream and trout,  
+Based on this, we will treat the FAO as truth… and spatially allocate 21 farms.
 
-It says that half of those farms (6 farms) are located in Persembe bay. I will allocate the remaining 6 equally across Sinop bay, Sana bay, and Rize bay (2 farms each).
-
-Source: 
-Candan, A., Karatas, S., Kücüktas, H., Okumus, I. (Eds.), 2007. Marine aquaculture in Turkey. Türk Denzi Araştırmaları Vakfı, İstanbul.
+ - comprehensive - need to spatially allocate 21 farms randomly in turkey
 
@@
 
-# Sinop: 2 farms, randomly picked locations
-# lat 42.011686, lon 35.193134
-# 42.015462, 35.168353
+farms_turkey <- data.frame(iso3c = "TUR", type = "salmon", num_additional_farms = 21, data_quality = 3)
 
-# Persembe: 6 farms
-# 41.073031, 37.776490
-# 41.071171, 37.776501
-# 41.103902, 37.788303
-# 41.106756, 37.788893
-# 41.111485, 37.788643
-# 41.114387, 37.788943
-
-# Sana: 2 farms
-# 40.991640, 39.812112
-# 40.994117, 39.803345
-
-# Rize: 2 farms
-# 41.038866, 40.562498,
-# 41.036462, 40.558582
-
-farms_turkey <- data.frame(lon=c(35.193, 35.168, 37.776,  37.776, 37.788, 37.789, 37.789, 37.789, 39.812, 39.803, 40.562, 40.558),
-                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
-  mutate(iso3c = "TUR") %>%
-  mutate(data_quality = 0.333)
-
-write_csv(farms_turkey, here("marine/salmon/salmon_farm/data/farm_sites/farms_tur.csv"))
+write_csv(farms_turkey, here("marine/salmon/salmon_farm/data/known_number_farms_3/farms_tur.csv"))
 
@@
 # Finland
+ - Comprehensive data
 
 Source: 
-HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM HOLAS II Dataset: Finfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
   dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write.csv(farms_fi, here("marine/salmon/salmon_farm/data/farm_sites/farms_finland.csv"), row.names = FALSE)
+write.csv(farms_fi, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_finland.csv"), row.names = FALSE)
 
-farms_fi <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_finland.csv"))
+farms_fi <- read_csv(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_finland.csv"))
 ```
@@
 # Sweden
+
+ - Comprehensive data
+
 Source:
-HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM HOLAS II Dataset: Finfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 
@@
   filter(!is.na(lat)) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 5)
 
-write.csv(farms_sw, here("marine/salmon/salmon_farm/data/farm_sites/farms_sweden.csv"), row.names = FALSE)
+write.csv(farms_sw, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_sweden.csv"), row.names = FALSE)
 
-#farms_sw <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_sweden.csv"))
+#farms_sw <- read_csv(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_sweden.csv"))
 ```
@@
 
-We are using the ASC data for this:
+We are using the ASC data for this, however this is only a subset of farms in Iceland. We will treat this as needed to be gapfilled with existing points (data_quality = 2)
 
 Source: 
-Aquaculture Stewardship Council Data Mapping Study, n.d. . Aquaculture Stewardship Council. [Accessed November 11, 2020] 
+Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
 https://gis.asc-aqua.org/arcgis_app/
@@
   cbind(iso3c = ISL_pts_latlon$iso3c) %>%
-  mutate(data_quality = 1.0)
+  mutate(data_quality = 2)
 
-write_csv(farms_all_ISL, here("marine/salmon/salmon_farm/data/farm_sites/farms_isl.csv"))
+write_csv(farms_all_ISL, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_isl.csv"))
 
@@
 
-farm_files <- list.files(here("marine/salmon/salmon_farm/data/farm_sites"), full=TRUE)
+farm_files <- list.files(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5"), full=TRUE)
 all_farms = plyr::ldply(farm_files, read_csv)
@@
 
-# all_farms <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), col_types = "ddcc")
+# all_farms <- read_csv(here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), col_types = "ddccd")
 

### 2021-03-23 marine/salmon/salmon_farm/STEP3_gapfill_salmon.Rmd
Finished reorganizing data

---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all the relevant farm datasets

```{r}

farm_files <- list.files(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "salmon")

number_files <- list.files(here("marine/salmon/salmon_farm/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

subset_farms_files <- list.files(here("marine/salmon/salmon_farm/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/salmon/salmon_farm/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

subset_gapfill_2 <- all_known_farms %>%
  filter(data_quality == 2)
```

Read in relevant production data
```{r}
salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
  mutate(type = "salmon") %>%
  filter(year == 2017)
```

Calculate a global tonnes per farm for salmon

```{r}
## Filter for data_quality = 4 or 5 and group by country to get number of farms
comprehensive_farms <- all_known_farms %>%
  filter(data_quality %in% c(4,5)) %>% 
  group_by(iso3c, type, data_quality) %>%
  summarise(n_farms = n()) %>% ## now we can see that new zealand has additional farms to add
  ungroup()

## Join this with the additional farms we need to add to new zealand, so we can calculate a comprehensive tonnes/farm for salmon

data_quality_3 <- all_number_3 %>%
    rename("n_farms" = "num_additional_farms")

data_quality_4 <- subset_add_4 %>%
    rename("n_farms" = "num_additional_farms")

comprehensive_farms_total <- comprehensive_farms %>%
  full_join(data_quality_3) %>%
  full_join(data_quality_4) %>%
  group_by(iso3c, type) %>%
  summarise(n_farms = sum(n_farms))

tonnes_per_farm <- comprehensive_farms_total %>%
  left_join(salmon_tonnes) %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms)

avg_global_salmon_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_salmon_tonnes_per_farm # 930.3976
```

Now let's gapfill those that are data quality = 2 and data quality = 1

```{r}
## start with the subset of locations that need gapfilling based on tonnes/farm
gapfill_2 <- subset_gapfill_2 %>%
  group_by(iso3c, type) %>%
  summarise(n_existing_farms = n()) %>%
  ungroup() %>%
  left_join(salmon_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_salmon_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## now lets do the locations that have no info and need gapfilling based on tonnes/farm
gapfill_1 <- no_info_1 %>%
  left_join(salmon_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_salmon_tonnes_per_farm) %>%
  mutate(num_additional_farms = ceiling(fao_tonnes_production/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## Wrangle those that just need a specific number of points added to existing points (data_quality = 4)

number_add_points_4 <- subset_add_4 %>%
  dplyr::select(-data_quality) %>%
  mutate(estimated = 0, 
         avg_tonnes_per_farm = avg_global_salmon_tonnes_per_farm)
```

Now join the gapfilled number of farms with data quality = 3 and write the final file of points that need to allocated

```{r}
number_additional_points <- all_number_3 %>%
  mutate(estimated = 0,
         avg_tonnes_per_farm = avg_global_salmon_tonnes_per_farm) %>%
  dplyr::select(-data_quality) %>%
  rbind(gapfill_1, gapfill_2, number_add_points_4)

## write this out to our final data folder

write.csv(number_additional_points, here("marine/salmon/salmon_farm/output/salmon_points_to_add_final.csv"), row.names = FALSE)
```

Now lets make the file with all of the known farms

```{r}
all_known_farms_final <- all_known_farms %>%
  dplyr::select(-data_quality)

write.csv(all_known_farms_final, here("marine/salmon/salmon_farm/output/all_known_salmon_farms_final.csv"), row.names = FALSE)
```

Data check

```{r}
test <- all_known_farms %>% 
  group_by(iso3c) %>%
  summarise(n_farms = n()) %>%
  dplyr::select(iso3c)

test_2 <- number_additional_points %>%
  dplyr::select(iso3c)

test_all <- rbind(test, test_2)
length(unique(test_all$iso3c)) ## 16 countries

length(unique(salmon_tonnes$iso3c)) ## 16 countries

## perfect

```

### 2021-03-23 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
made a dataset for number of farms modeling
Finished reorganizing data

--- 2021-02-16 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
@@
 
-coast_raw <- st_read("/home/shares/food-systems/Aquaculture_mapping/Data/Jared/Marine_Brackish/raw_data/Coastline/lines.shp")
-```
-
-## explore
+```
+
+# Raster
+
+Standard raster used for this analysis
+
+```{r}
+
+source(here::here("_spatial/template_raster.R"))
+
+```
+
+# Global regions
+
+```{r}
+
+gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
+
+gadm_latlon <- projectRaster(gadm, food_raster)
+
+gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
+  mutate(reg_id = as.numeric(reg_id))
+
+```
+
+```{r}
+
+gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
+  mutate(cellvalue = round(cellvalue, 0))
+
+gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
+
+```
+
+Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
+ - Try to obtain exact locations of farms from published source or 
+ dataset (such as FAO or a research paper)
+ - If there are not exact locations or comprehensive locations, find the number of farms. 
+ - If there is no information at all, note it. We will gapfill later.
+
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).
+
+5: Comprehensive number of exact farms
+
+4: Subset of exact locations, need to add a specific number of farms to existing locations. 
+  - country|species|farm locations
+  - country|species|additional points
+
+3: A specific number of farms are known, but no locations 
+ - country|species|additional points
+
+2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
+ - country, species, n_existing_points
+
+2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.
+
+1: No information on number of farms at all. Need to be gapfilled by tonnage. 
+ - country|species|# additional farms (this will be NA)
+
+## Read in ASC data
 https://gis.asc-aqua.org/arcgis_app/
@@
 
-# Raster
-
-Standard raster used for this analysis
-
-```{r}
-
-source(here::here("_spatial/template_raster.R"))
-
-```
-
-# Global regions
-
-```{r}
-
-gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
-
-gadm_latlon <- projectRaster(gadm, food_raster)
-
-gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
-  mutate(reg_id = as.numeric(reg_id))
-
-```
-
-```{r}
-
-gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
-  mutate(cellvalue = round(cellvalue, 0))
-
-gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))
-
-```
-
-Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
- - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
- - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline.
-If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
- - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
-
-For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
- 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
-   - Must not intersect with land mask
-   - "Land mask"
-
-4: Good qualifications - Locations are projected or it is a only sample of total locations
-   - Must not intersect with land mask
-   - "Land mask"
-
-3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
-   - Must be allocated spatially
-   - Must not intersect with land mask
-   - Flagged as "Allocate spatially"
-
-2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
-   - Must be allocated using suitability analysis.
-   - Flagged as 2 and "state/province suitability"
-
-1: Very Bad qualifications - No data at all.
-   - Must be allocated using suitability analysis.
-   - Flagged as 1 and "country suitability"
-
 # Map data from ASC (contains 19/35 countries)
@@
   cbind(iso3c = all_pts_latlon$iso3c) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 5)
 
 ## save farm location
-write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/farm_sites/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)
-
+write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)
+
+```
+
+Now we need to map for each country, and assign a flag for gapfilling which will be completed later. I will start with all of the countries list in the ASC data.
+
+# Indonesia 
+Current data is from ASC, only 5 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Indonesia.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_idn <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "IDN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_idn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_idn.csv"))
+
+```
+
+# New Caledonia
+
+Current data is from ASC, only 2 farms, so probably not comprehensive.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_ncl <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "NCL") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_ncl, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ncl.csv"))
+
+```
+
+# Mexico 
+Current data is from ASC, only 11 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Mexico.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_mex <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "MEX") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_mex, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_mex.csv"))
+
+```
+
+# Venezuela 
+Current data is from ASC, only 11 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Venezuela.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_ven <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "VEN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_ven, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ven.csv"))
+
+```
+
+# India
+
+Current data is from ASC, only 104 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of India.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_ind <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "IND") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_ind, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ind.csv"))
+
+```
+
+# Viet Nam
+
+Current data is from ASC, only 173 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of viet nam.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_vnm <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "VNM") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_vnm, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_vnm.csv"))
+
+```
+
+# Ecuador
+
+Current data is from ASC, which is likely not comprehensive.
+
+The FAO states this: 
+"Until 1998 (the last period for which statistics on the subject area available), the Under-Ministry of Fisheries Resources registered 2 006 shrimp industries, 312 larvae hatcheries, 21 feed manufacturing plants and 76 processing plants."
+
+It is hard to tell how many shrimp farms are actually in Ecuador.
+I do think the ASC number is a good number, but it is probably not comprehensive given the amount of production from Ecuador.
+Data quality = 2.
+
+```{r}
+farms_ecu <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "ECU") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))
+
+```
+
+# Honduras
+
+Current data is from ASC, only 20 farms, so probably not comprehensive.
+There are likely many more farms than this.
+The FAO states there are many smal lscale shrimp farms tat are not documented, so it is impossible to tell how many there are from current information.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_hnd <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "HND") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_hnd, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_hnd.csv"))
+
+```
+
+# China
+
+Current data is from ASC, only 4 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of China.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_chn <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "CHN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_chn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
+
+```
+
+# Thailand
+Current data is from ASC, only 18 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Thailand.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_tha <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "THA") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_tha, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_tha.csv"))
+
+```
+
+# Madagasgar
+
+Need to add 4 points to existing 2 (a final total of 6 points)
+
+From FAO:
+For marine aquaculture, the six shrimp breeding companies created 4 325 full-time jobs, 4 267 of which were for local people and 58 for expatriates (Anon.
+2005b).
+These 4 325 full-time jobs were distributed as follows: 90 mariners, 1 072 in the processing plant, 400 in administration, 267 in hatcheries, 2 114 in farms, and 382 in other areas.
+This kind of shrimp farming also created 30 000 indirect jobs.
+Seaweed culture was being practised by 126 farmers.
+
+Data quality = 4
+
+```{r}
+farms_mdg <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "MDG") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_mdg, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_mdg.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+mdg_additional <- data.frame(iso3c = "MDG", type = "shrimp", num_additional_farms = 4, data_quality = 4, total_farms = 6)
+write.csv(mdg_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_mdg.csv"), row.names = FALSE)
+```
+
+# Panama
+Current data is from ASC, only 1 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Panama.
+There are likely more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_pan <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "PAN") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_pan, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_pan.csv"))
+
+```
+
+# Bangladesh
+Current data is from ASC, only 1 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Bangladesh There are likely more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_bgd <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "BGD") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_bgd, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_bgd.csv"))
+
+```
+
+# Guatemala
+
+Need to add 19 points to existing 3 (a final total of 22 points)
+
+Current data is from the ASC, which is not comprehensive.
+
+http://www.fao.org/fishery/countrysector/naso_guatemala/en
+ - “There are 34 shrimp farms of which 22 are active and 12 inactive.”
+
+```{r}
+farms_gtm <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "GTM") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_gtm, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_gtm.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+gtm_additional <- data.frame(iso3c = "GTM", type = "shrimp", num_additional_farms = 19, data_quality = 4, total_farms = 22)
+write.csv(gtm_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_gtm.csv"), row.names = FALSE)
+```
+
+# Nicaragua
+
+Seafood watch claims there is no available information other than the ASC farms. 
+https://seafood.ocean.org/wp-content/uploads/2018/12/MBA_SeafoodWatch_FarmedShrimp_Nicaragua_Report.pdf
+
+Current data is from ASC, only 2 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Nicaragua.
+There are likely more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_nic <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "NIC") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_nic, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_nic.csv"))
+
+```
+
+# Australia
+Current data is from ASC, only 2 farms, so probably not comprehensive.
+There are likely more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+farms_aus <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "AUS") %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_aus, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_aus.csv"))
+
+```
+
+# Peru
+
+Need to add 71 points to existing 1 (a final total of 72 points).
+
+Current data is a subset of farms from ASC. There is currently 1 point.
+
+https://seafood-tip.com/sourcing-intelligence/countries/peru/shrimp/
+ - “22 Medium and large corporate farms are responsible for the majority of shrimp exports, while 50 small-scale farmers mainly produce for the domestic market”
+
+```{r}
+farms_per <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "PER") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_per, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_per.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+per_additional <- data.frame(iso3c = "PER", type = "shrimp", num_additional_farms = 71, data_quality = 4, total_farms = 72)
+write.csv(per_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_per.csv"), row.names = FALSE)
+```
+
+# Colombia 
+Need to add 19 points to existing 1 (a final total of 20 points)
+
+Current data is from the ASC, which is a subset of points.
+
+http://www.fao.org/fishery/countrysector/naso_colombia/en
+ - “The shrimp farming industry operates nine maturation laboratories, eighteen larval culture laboratories, twenty shrimp farms and seven processing plants.
+All of them employ qualified labour force, made up of professionals and expert technicians in their respective field of work (Minagricultura and ACUANAL, 2002).”
+
+```{r}
+farms_col <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "COL") %>%
+  mutate(data_quality = 4)
+
+write_csv(farms_col, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_col.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+col_additional <- data.frame(iso3c = "COL", type = "shrimp", num_additional_farms = 19, data_quality = 4, total_farms = 20)
+write.csv(col_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_col.csv"), row.names = FALSE)
+```
+
+# Belize
+ - There are 3 shrimp farms represented in the ASC data. However, the FAO report on aquaculture reports a number of other farms. Specifically: 
+ - http://www.fao.org/fishery/countrysector/naso_belize/en
+ -  “The fourteen shrimp farms operational are all located on the lower coastal plain of mainland Belize.
+The two northern-most of these farms (Nova Ladyville Shrimp Farm, Caribbean Shrimp Farm) are located in the Ladyville area, just north-east of the PSW Goldson International Airport.
+There are three shrimp farms (Crown Shrimp Limited, Paradise Shrimp Farm, Melinda Mariculture Limited) located between the Coastal Road and Dangriga area.
+There are two shrimp farms (Triton Mariculture, Haney's Shrimp Farm) situated between Dangriga and Riversdale.
+There are another four farms (Belize Aquaculture Limited, Royal Mayan Shrimp Farm, Texmar Shrimp Farm, Crustaceans Shrimp Farm) located between Riversdale and the lower reaches of the Placencia Lagoon.
+Three of these farms (Aquamar Shrimp Farm, Nova Toledo Shrimp Farm, Toledo Fish Farm) are also located in the Big Creek/Monkey River area.”
+
+ - Since we have the names of these… I will google and attempt to place on the map.
+The ASC already has 3 mapped (Aquamar shrimp farm, Cardelli farms, and Royal Mayan Shrimp Farms).
+Only 2 of these overlap, so we will assume that Cardelli has been added since the FAO report was published.
+ - I will need to place Nova Ladyville Shrimp Farm, Caribbean Shrimp Farm, Crown Shrimp Limited, Paradise Shrimp Farm, Melinda Mariculture Limited, Triton Mariculture, Haney's Shrimp Farm, Belize Aquaculture Limited, Texmar Shrimp Farm, Crustaceans Shrimp Farm, Nova Toledo Shrimp Farm, Toledo Fish Farm.
+If I can’t find these on google, then we will place the remaining number of farms randomly in suitable locations.
+
+Nova Ladyville Shrimp Farm - This one has since been closed. 
+Caribbean Shrimp Farm - 17.565826428687156, -88.30446591534489
+Crown Shrimp Limited - Not on the map... I believe this has likely closed. 
+Paradise Shrimp Farm - 17.088537866900786, -88.3141468760761
+Melinda Mariculture Limited - 16.996401736714773, -88.28891758186664
+Triton Mariculture - 16.91300830350531, -88.30401223336973
+Haney's Shrimp Farm - 16.77084262777864, -88.3358879288162
+Belize Aquaculture Limited - 16.664824857803115, -88.39502139821094
+Texmar Shrimp Farm - 16.56115563573352, -88.41922498380852
+Crustaceans Shrimp Farm - Not on the map... I believe this has likely closed. 
+Nova Toledo Shrimp Farm - 16.460774477225453, -88.43760570009555
+Toledo Fish Farm - 16.43434608053408, -88.4650001965993
+
+```{r}
+
+farms_blz <- data.frame(lat=c(17.565826428687156, 17.088537866900786, 16.996401736714773, 16.91300830350531, 16.77084262777864, 16.664824857803115, 16.56115563573352, 16.460774477225453, 16.43434608053408),
+                        lon=c(-88.30446591534489, -88.3141468760761, -88.28891758186664, -88.30401223336973, -88.3358879288162, -88.39502139821094, -88.41922498380852, -88.43760570009555, -88.4650001965993),
+                        subregion = c("Nova Ladyville Shrimp Farm", "Paradise Shrimp Farm", "Melinda Mariculture Limited", "Triton Mariculture", "Haney's Shrimp Farm", "Belize Aquaculture Limited", "Texmar Shrimp Farm", "Nova Toledo Shrimp Farm", "Toledo Fish Farm")) %>%
+  mutate(iso3c = "BLZ") %>%
+  mutate(data_quality = 5)
+
+# now join with the ASC data
+farms_blz_asc <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "BLZ")
+
+farms_blz_total <- full_join(farms_blz, farms_blz_asc)
+
+write_csv(farms_blz, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_blz.csv"))
+
+## visualize it 
+farms_blz <-  st_as_sf(farms_blz_total, coords = c("lon", "lat"), 
+                 crs = crs(gadm_latlon), agr = "constant")
+
+mapview(farms_blz)
 ```
@@
  - Has a map of major shrimp farming locations (from 2002): http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.200.2425&rep=rep1&type=pdf
- - Also has a table of number of farms and area per state. I will just place one point at on each state, and add up the area listed in the table.
-
- - Pará: -0.952238, -48.466718: 70 hectares
- - Maranhão: -2.365963, -44.263791: 64 hectares
- - Piauí: -2.859201, -41.551117: 425 hectares
- - Ceará: -3.646201, -38.627546: 982 hectares
- - Rio G. do Norte: -5.100375, -35.667111: 1752 hectares
- - Paraíba: -7.089602, -34.818058: 420 hectares
- - Pernambuco: -8.115310, -34.840892: 670 hectares
- - Alagoas: -9.700209, -35.739681: 20 hectares
- - Sergipe: -10.991527, -37.030238: 47 hectares
- - Bahia: -13.046432, -38.515139: 1510 hectares
- - São Paulo: inland, don't include
- - Paraná: -25.535885, -48.268714: 50 hectares
- - Sta. Catarina: -27.505551, -48.393581: 200 hectares
+ - Also has a table of area per state.
 
@@
 
-```{r}
-farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
-                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
-                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200)) %>%
-  mutate(iso3c = "BRA") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_bra, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_bra.csv"))
-
-## visualize it 
-farms_bra <-  st_as_sf(farms_bra, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_bra)
+ - Because this source doesn't hav especifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.
+
+```{r}
+bra_gf <- data.frame(iso3c = "BRA", type = "shrimp", num_additional_farms = NA, data_quality = 1)
+write_csv(bra_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_bra.csv")) 
 ```
@@
 
+ - Because this is just data from one shrimp company in the Brunei, we will assume this is not comprehensive, and we will need to gapfill the remaining tonnage.
+
 ```{r}
@@
   mutate(iso3c = "BRN") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_brn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_brn.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_brn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_brn.csv"))
 
@@
 # Cambodia 
- - There is a table in here.
-We will just place a point on the coast for each of these coastal places, and use the area noted in the paper later if needed.
-If the province is not coastal, it will not be placed on the map: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf
-
- - Kampot: 10.559329, 104.213349: 1516 hectares
- - Kep: 10.449929, 104.404934: 459 hectare
- - Koh Kong: 11.740932, 102.898284: 26762 hectare
- - Preah Sihanouk: 10.743017, 103.653332: 6388 hectares
- - Pursat: Inland, don't include
- - Svay Rieng: Inland, don't include
- - Takeo: Inland, don't include
+ - There is a table in here. But it only has area estimates: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf
 
@@
 
-```{r}
-
-farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
-                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
-                        area_ha = c(1516, 459, 26762, 6388)) %>%
-  mutate(iso3c = "KHM") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_khm, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_khm.csv"))
-
-## visualize it 
-farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_khm)
+ - Because this source doesn't hav especifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.
+
+```{r}
+khm_gf <- data.frame(iso3c = "KHM", type = "shrimp", num_additional_farms = NA, data_quality = 1)
+write_csv(khm_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_khm.csv")) 
 ```
@@
  - This says there are 90 shrimp producers in Costa Rica. all located in Puntarenas and Guanacaste provinces: http://www.fao.org/fishery/countrysector/naso_costarica/en
- - I will equally allocate the farm points along the coast line of these two provinces (90 farms total).
+ - We will place 90 farms into suitable locations along Costa Rica's coast.
 
@@
 ```{r}
-provinces <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Costa_rica/gadm36_CRI_1.shp"))
-mapview(provinces)
-
-guana_punta <- provinces  %>%
-  dplyr::filter(NAME_1 %in% c("Guanacaste", "Puntarenas"))
-
-mapview(guana_punta)
-
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-
-# world <- st_as_sf(world)
-
-costa_world_crs <- st_transform(guana_punta, crs(coast_raw))
-
-costa_world_crop <- st_crop(coast_raw, costa_world_crs) %>% ## crop to costa rica extent 
-  filter(FID %in% c(245909:245926)) %>% ## filter for the correct coastline 
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-mapview(costa_world_crop)
-
-c_meters <- st_transform(costa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(c_meters)
-
-buff <- st_buffer(c_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(costa_world_crop))
-mapview(buffer_outline_fixed)
-
-costa_rica <- ne_countries(scale = 10, country = "Costa Rica", returnclass = "sf")
-mapview(costa_rica)
-
-linestring_fix <- st_difference(buffer_outline_fixed, costa_rica) ## now grab only the outline 
-mapview(linestring_fix)
-
-costa_crop <- as(linestring_fix, "Spatial")
-mapview(costa_crop)
-
-costa_points_lines <- sample.line(costa_crop, n = 106) ## equally place the number of farms along the coastline
-
-costa_points <- st_as_sf(costa_points_lines) %>%
-  mutate(new_id = 1:318) %>%
-  filter(new_id %in% c(1:88, 105:106))
-mapview(costa_points)
-
-cri_pts <- st_centroid(costa_points)
-
-cri_pts_latlon <- st_transform(cri_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_cri <- data.frame(do.call(rbind, st_geometry(cri_pts_latlon)))
-names(farms_cri) <- c("lon", "lat")
-
-farms_cri_final <- farms_cri %>%
-  mutate(iso3c = "CRI") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_cri <-  st_as_sf(farms_cri, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_cri)
-
-## write to farms folder 
-write_csv(farms_cri_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_cri.csv"))
+farms_cri <- data.frame(iso3c = "CRI", type = "shrimp", num_additional_farms = 90, data_quality = 3)
+
+write_csv(farms_cri, here("marine/shrimp/shrimp_farms/data/known_number_farms_3/farms_cri.csv"))
 
@@
 Source: 
-National Aquaculture Sector Overview. Cuba, 2005. , National Aquaculture Sector Overview Fact Sheets.
+National Aquaculture Sector Overview. Cuba, 2005. National Aquaculture Sector Overview Fact Sheets.
+
+“Production of market-size shrimp takes place in 5 state-owned farms that are located at Cuba’s southern coast (which is less prone to the impact of storms than the country’s northern coast)”
+
+This means that we need to place 3 more farms in Cuba.
 
@@
   mutate(iso3c = "CUB") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_cub, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_cub.csv"))
+  mutate(data_quality = 4)
+
+write_csv(farms_cub, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_cub.csv"))
 
@@
 mapview(farms_cub)
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+cub_additional <- data.frame(iso3c = "CUB", type = "shrimp", num_additional_farms = 3, data_quality = 4, total_farms = 5)
+write.csv(cub_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_cub.csv"), row.names = FALSE)
 ```
@@
 # El Salvador 
- - Could use the table here. We would just assign one farm per each city listed: http://www.fao.org/fishery/countrysector/naso_elsalvador/en
-
- - Ahuachapan: seems inland
- - Sonsonate: seems inland
- - La Paz: 13.336985, -89.014470: 8.2 hectares
- - Usulután: seems inland
- - La Unión: 13.354459, -87.863771: 50 hectares
-
- Source: 
-National Aquaculture Sector Overview. El Salvador, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
-
-```{r}
-farms_slv <- data.frame(lat=c(13.336985, 13.354459),
-                        lon=c(-89.014470, -87.863771),
-                        area_ha = c(8.2, 50)) %>%
-  mutate(iso3c = "SLV") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_slv, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_slv.csv"))
-
-## visualize it 
-farms_slv <-  st_as_sf(farms_slv, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_slv)
+http://www.fao.org/fishery/countrysector/naso_elsalvador/en
+
+ = “According to the aquaculture method and the scale of production, aquaculture production units are distributed as follows: 15 production units of tilapia cages, 26 reservoirs for household consumption, 50 small and medium scale units, 1 industrial scale unit; 2 ornamental fish production units, 23 units of fresh water prawns, and 39 marine shrimp farms.”
+
+ - I must’ve missed this my first lit review, so we will place 39 marine shrimp farms in suitable locations along the El Salvador coast.
+
+ Source: 
+National Aquaculture Sector Overview. El Salvador, 2005. National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
+
+```{r}
+farms_slv <- data.frame(iso3c = "SLV", type = "shrimp", num_additional_farms = 39, data_quality = 3)
+
+write_csv(farms_slv, here("marine/shrimp/shrimp_farms/data/known_number_farms_3/farms_slv.csv"))
 ```
@@
 Source: 
-NASO aquaculture maps collection , 2010.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/iran/en/
+
+ - We will use the existing points for exact locations, and then gapfill the remaining to reach a total of 205 farms.
 
@@
   mutate(iso3c="IRN") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_irn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_irn.csv"))
-
-farms_irn <-  st_as_sf(farms_irn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_irn)
+  mutate(data_quality = 4)
+
+write_csv(farms_irn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_irn.csv"))
+
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+irn_additional <- data.frame(iso3c = "IRN", type = "shrimp", num_additional_farms = 191, data_quality = 4, total_farms = 205)
+write.csv(irn_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_irn.csv"), row.names = FALSE)
+
 ```
@@
 # Japan
- - One shrimp farm on this companies map: https://fis.com/fis/worldnews/worldnews.asp?l=e&id=100979&ndb=1
-    - Near Minamikyūshū: 31.182129, 130.604815
+ - No info at all... needs to be fully gapfilled.
 
@@
 ```{r}
-farms_jpn <- data.frame(lat=c(31.182129),
-                        lon=c(130.604815),
-                        area_ha = c(NA)) %>%
-  mutate(iso3c = "JPN") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_jpn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_jpn.csv"))
-
-## visualize it 
-farms_jpn <-  st_as_sf(farms_jpn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_jpn)
+jpn_gf <- data.frame(iso3c = "JPN", type = "shrimp", num_additional_farms = NA, data_quality = 1)
+write_csv(jpn_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_jpn.csv")) 
 ```
@@
  - "West coast: shrimp (Penaeus japonicus, P. chinensis) is mainly cultivated in Taean, ChungNam"
- - I will put a point there. 
- - Taean: 36.752683, 126.150252: 672 hectares (taken from "Korean Aquaculture at a glance")
 
@@
 
-```{r}
-farms_kor <- data.frame(lat=c(36.752683),
-                        lon=c(126.150252),
-                        area_ha = c(672)) %>%
-  mutate(iso3c = "KOR") %>% 
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_kor, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_kor.csv"))
-
-## visualize it 
-farms_kor <-  st_as_sf(farms_kor, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_kor)
+ - Because of the lack of information, this will need to be fully gapfilled.
+
+```{r}
+
+kor_gf <- data.frame(iso3c = "KOR", type = "shrimp", num_additional_farms = NA, data_quality = 1)
+write_csv(kor_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_kor.csv")) 
 ```
@@
 Source: 
-Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. . Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78
+Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78
+
+ - This is only a subset of total shrimp farms most likely, since this only represents industrial scale projects. The rest will need to be gapfilled if necessary.
 
@@
                         lon=c(99.826952, 102.463536, 110.210032, 103.43838831493285, 102.721589, 103.328932, 102.82739417198427, 111.183470, 100.704595, 100.975557, 103.446051),
-                        area_ha =mys_area) %>%
+                        area_ha =mys_area,
+                        subregion = c("Ayer Hangat, Kedah", "Sebatu, Malacca", "Kuching, Sarawak", "Pekan, Pahang", "Setiu, Terengganu", "Marang, Terengganu", "Setiu, Terengganu", "Tanjung Manis, Sarawak", "Rungkup, Perak", "Sabak, Selangor", "Pekan, Pahang")) %>%
   mutate(iso3c = "MYS") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_mys, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_mys.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_mys, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_mys.csv"))
 
@@
 mapview(farms_mys)
+
 ```
@@
  "The largest area of shrimp farming is found in Rakhine State (155,533 acres), followed by Ayeyarwaddy (33 373 acres), Yangon (7 394 acres), with smaller areas in Bago, Kayin, Mon and Thaninthary"
- - We will use that for our points. One point for each state. 
- - Rakhine State: 20.117197, 92.884433: 62941.972 hectares
- - Ayeyarwaddy: 15.967665, 94.337465: 13505.574 hectares
- - Yangon: 16.441903, 96.371311: 2992.246 hectares
- - Bago: Inland, don't include
- - Kayin: Inland, don't include
- - Mon: 16.100756, 97.581799
- - Thaninthary: 13.436424, 98.323120
 
@@
 
-```{r}
-farms_mmr <- data.frame(lat=c(20.117197, 15.967665, 16.441903, 16.100756, 13.436424),
-                        lon=c(92.884433, 94.337465, 96.371311, 97.581799, 98.323120),
-                        area_ha = c(62941.972, 13505.574, 2992.246, NA, NA )) %>%
-  mutate(iso3c = "MMR") %>%
-  mutate(data_quality = 2) %>%
-  mutate(action_needed = "state/province based suitability")
-
-write_csv(farms_mmr, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_mmr.csv"))
-
-## visualize it 
-farms_mmr <-  st_as_sf(farms_mmr, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_mmr)
+ - Because there is no other information, we will completely gapfill this country.
+
+```{r}
+mmr_gf <- data.frame(iso3c = "MMR", type = "shrimp", num_additional_farms = NA, data_quality = 1)
+write_csv(mmr_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_mmr.csv")) 
 ```
@@
 
- - I will equally place 271 farms along the coast of the philippines
- - We know that there are 3617.8 hectares of farms... we will allocate that area evenly... 3617.8/271 = 13.35
+ - We will place 271 farms in suitable locations along the philipino coast.
 
@@
 ```{r}
-philly <- ne_countries(scale = 10, country = "Philippines", returnclass = "sf")
-mapview(philly)
-
-world <- ne_coastline(scale = 110) #world map with 110m resolution
-
-world <- st_as_sf(world)
-
-philly_world_crs <- st_transform(philly, crs(world))
-
-philly_world_crop <- st_crop(world, philly_world_crs) ## crop to philippines extent
-
-mapview(philly_world_crop)
-
-philly_world_crop <- philly_world_crop[-c(1), ] ## delete lines that are not in philippines
-mapview(philly_world_crop)
-
-# philly_world_crop <- philly_world_crop %>%
-#   mutate(new_id = 1) %>%
-#   group_by(new_id) %>%
-#   summarise(geometry = st_union(geometry)) %>%
-#   ungroup()
-# 
-# mapview(philly_world_crop)
-# 
-# p_meters <- st_transform(philly_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-# mapview(p_meters)
-# 
-# buff <- st_buffer(p_meters, dist = 10000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-# mapview(buff)
-# 
-# linestring <- st_cast(buff, "MULTILINESTRING") ## make a line string so we can filter for the outline 
-# mapview(linestring)
-# 
-# ## now reproject back to original 
-# buffer_outline_fixed <- st_transform(linestring, crs = crs(philly_world_crop))
-# mapview(buffer_outline_fixed)
-# 
-# 
-# philly2 <- ne_countries(scale = 50, country = "Philippines", returnclass = "sf")
-# mapview(philly2)
-#   
-# linestring_fix <- st_difference(buffer_outline_fixed, philly) ## now grab only the outline 
-# mapview(linestring_fix)
-
-philly_crop <- as(philly_world_crop, "Spatial")
-mapview(philly_crop)
-
-philly_points_lines <- sample.line(philly_crop, n = 2) ## equally place the number of farms along the coastline 
-class(philly_points_lines)
-plot(philly_points_lines)
-
-philly_points <- st_as_sf(philly_points_lines)
-mapview(philly_points)
-
-## Now filter out the points that fall outside of 271
-philly_points_final <- philly_points[1:271,]
-mapview(philly_points_final)
-
-phl_pts <- st_centroid(philly_points_final)
-
-phl_pts_latlon <- st_transform(phl_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_phl <- data.frame(do.call(rbind, st_geometry(phl_pts_latlon)))
-names(farms_phl) <- c("lon", "lat")
-
-farms_phl_final <- farms_phl %>%
-  mutate(iso3c = "PHL") %>%
-  mutate(area_ha = 13.35) %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_phl <-  st_as_sf(farms_phl, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_phl)
-
-## write to farms folder 
-write_csv(farms_phl_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_phl.csv"))
-
+
+farms_phl <- data.frame(iso3c = "PHL", type = "shrimp", num_additional_farms = 271, data_quality = 3)
+
+write_csv(farms_phl, here("marine/shrimp/shrimp_farms/data/known_number_farms_3/farms_phl.csv"))
 ```
@@
 
+ - Because of the large production out of SAU, this is probably not the only two farms. The remaining tonnage will be gapfilled. Data quality = 2
+
 ```{r}
 farms_sau <- data.frame(lat=c(20.287253, 17.806544),
-                        lon=c(40.030864, 41.897791),
-                        area_ha = c(7189, 206), 
-                        prod = c(35000, 3000)) %>%
+                        lon=c(40.030864, 41.897791)) %>%
   mutate(iso3c = "SAU") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_sau, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_sau.csv"))
+  mutate(data_quality = 2)
+
+write_csv(farms_sau, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_sau.csv"))
 
@@
 http://www.fao.org/fishery/countrysector/naso_sri-lanka/en#:~:text=The%20current%20shrimp%20aquaculture%20industry,of%20around%203%20000%20ha.
-"The current shrimp aquaculture industry in Sri Lanka is concentrated in the north western coastal belt **(Puttalam district)** covering a farm area of more than 4 500 ha with 70 hatcheries, of the total farm area the ponds themselves occupy an area of around 3 000 ha.
-There are a total of 1 344 farm establishments, of which 47.7 percent are considered to be establishments operating without proper licences (Siriwardena, 2001b).
+"The current shrimp aquaculture industry in Sri Lanka is concentrated in the north western coastal belt **(Puttalam district)** covering a farm area of more than 4 500 ha with 70 hatcheries, of the total farm area the ponds themselves occupy an area of around 3 000 ha....
 On the eastern coast in Batticaloa District, where shrimp farming in Sri Lanka first began in the late 1970s but was abandoned due to civil unrest, operations have recommenced in recent years.
@@
 
- - Puttalam district : 1344 farms, 4500/1344 = 3.348214 hectares per farm
- - Batticalao district : 60 farms, 155/60 = 2.583333 hectares per farm
-
-Source: 
-National Aquaculture Sector Overview. Sri Lanka, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
-
-```{r}
-districts <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Sri_Lanka/gadm36_LKA_1.shp"))
-mapview(districts)
-
-batticaloa_shp <- districts %>%
-  dplyr::filter(NAME_1 == "Batticaloa")
-
-mapview(batticaloa_shp)
-
-puttalam_shp <- districts %>%
-  dplyr::filter(NAME_1 == "Puttalam")
-mapview(puttalam_shp)
-
-## Start with Batticaloa
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-
-# world <- st_as_sf(world)
-
-batticaloa_world_crs <- st_transform(batticaloa_shp, crs(coast_raw))
-
-batticaloa_world_crop <- st_crop(coast_raw, batticaloa_world_crs) %>% ## crop to batticaloa extent
-  mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-mapview(batticaloa_world_crop)
-
-b_meters <- st_transform(batticaloa_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(b_meters)
-
-buff <- st_buffer(b_meters, dist = 4000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(batticaloa_world_crop))
-mapview(buffer_outline_fixed)
-
-sri_lanka <- ne_countries(scale = 10, country = "Sri Lanka", returnclass = "sf")
-mapview(sri_lanka)
-
-linestring_fix <- st_difference(buffer_outline_fixed, sri_lanka) ## now grab only the outline 
-mapview(linestring_fix)
-
-batticaloa_crop <- as(linestring_fix, "Spatial")
-mapview(batticaloa_crop)
-
-batticaloa_points_lines <- sample.line(batticaloa_crop, n = 80) ## equally place the number of farms along the coastline 
-class(batticaloa_points_lines)
-plot(batticaloa_points_lines)
-
-batticaloa_points <- st_as_sf(batticaloa_points_lines) %>%
-  mutate(new_id = 1:80) %>%
-  dplyr::filter(new_id %in% c(1:60))
-mapview(batticaloa_points)
-
-bat_lka_pts <- st_centroid(batticaloa_points)
-
-bat_lka_pts_latlon <- st_transform(bat_lka_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_bat_lka <- data.frame(do.call(rbind, st_geometry(bat_lka_pts_latlon)))
-names(farms_bat_lka) <- c("lon", "lat")
-
-farms_bat_lka_final <- farms_bat_lka %>%
-  mutate(area_ha = 2.583333)
-
-## visualize it 
-farms_bat_lka <-  st_as_sf(farms_bat_lka, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_bat_lka)
-
-## Now do puttalam
-# world <- ne_coastline(scale = 50) #world map with 50m resolution
-# plot(world)
-# 
-# world <- st_as_sf(world)
-
-puttalam_world_crs <- st_transform(puttalam_shp, crs(coast_raw))
-
-puttalam_world_crop <- st_crop(coast_raw, puttalam_world_crs) %>% ## crop to puttalam extent
-  filter(FID %in% c(153735)) %>% 
-    mutate(new_id = 1) %>%
-  group_by(new_id) %>%
-  summarise(geometry = st_union(geometry)) %>%
-  ungroup()
-mapview(puttalam_world_crop)
-
-p_meters <- st_transform(puttalam_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
-mapview(p_meters)
-
-buff <- st_buffer(p_meters, dist = 1000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
-mapview(buff)
-
-linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
-mapview(linestring)
-
-## now reproject back to original 
-buffer_outline_fixed <- st_transform(linestring, crs = crs(puttalam_world_crop))
-mapview(buffer_outline_fixed)
-
-sri_lanka <- ne_countries(scale = 10, country = "Sri Lanka", returnclass = "sf")
-mapview(sri_lanka)
-
-linestring_fix <- st_difference(buffer_outline_fixed, sri_lanka) ## now grab only the outline 
-mapview(linestring_fix)
-
-puttalam_crop <- as(linestring_fix, "Spatial")
-mapview(puttalam_crop)
-
-puttalam_points_lines <- sample.line(puttalam_crop, n = 1361) ## equally place the number of farms along the coastline 
-class(puttalam_points_lines)
-plot(puttalam_points_lines)
-
-puttalam_points <- st_as_sf(puttalam_points_lines) %>%
-  mutate(new_id = 1:1361) %>%
-  filter(new_id %in% c(230:1360, 1:194, 199:217))
-mapview(puttalam_points)
-
-put_lka_pts <- st_centroid(puttalam_points)
-
-put_lka_pts_latlon <- st_transform(put_lka_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_put_lka <- data.frame(do.call(rbind, st_geometry(put_lka_pts_latlon)))
-names(farms_put_lka) <- c("lon", "lat")
-
-farms_put_lka_final <- farms_put_lka %>%
-  mutate(area_ha = 3.348214)
-
-## visualize it 
-farms_put_lka <-  st_as_sf(farms_put_lka, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_put_lka)
-
-## combine put and bat
-
-farms_all_lka <- rbind(farms_bat_lka_final, farms_put_lka_final) %>%
-  dplyr::mutate(iso3c = "LKA") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## write to farms folder 
-write_csv(farms_all_lka, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_lka.csv"))
+ - We will place 130 shrimp farms in suitable locations along the Sri Lanka coast.
+
+Source: 
+National Aquaculture Sector Overview. Sri Lanka, 2005. National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
+
+```{r}
+farms_lka <- data.frame(iso3c = "LKA", type = "shrimp", num_additional_farms = 130, data_quality = 3)
+
+write_csv(farms_lka, here("marine/shrimp/shrimp_farms/data/known_number_farms_3/farms_lka.csv"))
 
@@
 
- - It is unclear how many farms are in Taiwan. I will randomly place a farm on the coast.
+ - It is unclear how many farms are in Taiwan. This will be fully gapfilled. Data quality = 1.
 
@@
 ```{r}
-
-farms_twn <- data.frame(lat = c(22.33895226304863),
-                        lon = c(120.60403687783123)) %>%
-  mutate(iso3c = "TWN") %>%
-  mutate(data_quality = 1) %>%
-  mutate(action_needed = "country based suitability")
-
-write_csv(farms_twn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_twn.csv"))
-
-## visualize it 
-farms_twn <-  st_as_sf(farms_twn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_twn)
+twn_gf <- data.frame(iso3c = "TWN", type = "shrimp", num_additional_farms = NA, data_quality = 1)
+write_csv(twn_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_twn.csv"))
 
@@
 Source:
-NA
+
+ - I will consider this comprehensive based on my research.
 
@@
   mutate(iso3c = "USA") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
-
-write_csv(farms_usa, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_usa.csv"))
+  mutate(data_quality = 5)
+
+write_csv(farms_usa, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_usa.csv"))
 
@@
 ```{r}
-farm_files <- list.files(here::here("marine/shrimp/shrimp_farms/data/farm_sites"), full=TRUE)
+farm_files <- list.files(here::here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5"), full=TRUE)
 all_farms = plyr::ldply(farm_files, read_csv)

### 2021-03-23 marine/shrimp/shrimp_farms/STEP3_gapfill_shrimp.Rmd
Finished reorganizing data

---
title: "Gapfilling the number of farms to add for shrimp countries based on tonnes of production"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all the relevant farm datasets

```{r}

farm_files <- list.files(here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "shrimp")

number_files <- list.files(here("marine/shrimp/shrimp_farms/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

number_files_2.5 <- list.files(here("marine/shrimp/shrimp_farms/data/known_subset_2.5"), full=TRUE)
all_number_2.5 = plyr::ldply(number_files_2.5, read_csv)

subset_farms_files <- list.files(here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/shrimp/shrimp_farms/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

subset_gapfill_2 <- all_known_farms %>%
  filter(data_quality == 2)
```

Read in relevant production data
```{r}
shrimp_tonnes <- read_csv(here::here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
  mutate(type = "shrimp") %>%
  filter(year == 2017)
```

Calculate a global tonnes per farm for shrimp

```{r}
## Filter for data_quality = 4 or 5 and group by country to get number of farms
comprehensive_farms <- all_known_farms %>%
  filter(data_quality %in% c(4,5)) %>% 
  group_by(iso3c, type, data_quality) %>%
  summarise(n_farms = n()) %>% ## now we can see the places that has additional farms to add
  ungroup()

## Join this with the additional farms we need to add to some places, so we can calculate a comprehensive tonnes/farm for shrimp

data_quality_3 <- all_number_3 %>%
    rename("n_farms" = "num_additional_farms")

data_quality_4 <- subset_add_4 %>%
    rename("n_farms" = "num_additional_farms")

comprehensive_farms_total <- comprehensive_farms %>%
  full_join(data_quality_3) %>%
  full_join(data_quality_4) %>%
  group_by(iso3c, type) %>%
  summarise(n_farms = sum(n_farms))

tonnes_per_farm <- comprehensive_farms_total %>%
  left_join(shrimp_tonnes) %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms)

avg_global_shrimp_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_shrimp_tonnes_per_farm # 337.7357
```

Now let's gapfill those that are data quality = 2 and data quality = 1, and data quality = 2.5 (if applicable)

```{r}
## start with the subset of locations that need gapfilling based on tonnes/farm
gapfill_2 <- subset_gapfill_2 %>%
  group_by(iso3c, type) %>%
  summarise(n_existing_farms = n()) %>%
  ungroup() %>%
  left_join(shrimp_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_shrimp_tonnes_per_farm) %>%
  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## now lets do the locations that have no info and need gapfilling based on tonnes/farm
gapfill_1 <- no_info_1 %>%
  left_join(shrimp_tonnes) %>%
  mutate(avg_tonnes_per_farm = avg_global_shrimp_tonnes_per_farm) %>%
  mutate(num_additional_farms = ceiling(fao_tonnes_production/avg_tonnes_per_farm)) %>%
  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
  mutate(estimated = 1) %>%
  filter(num_additional_farms != 0)

## Wrangle those that just need a specific number of points added (data_quality = 4)

number_add_points_4 <- subset_add_4 %>%
  dplyr::select(-data_quality, -total_farms) %>%
  mutate(estimated = 0, 
         avg_tonnes_per_farm = avg_global_shrimp_tonnes_per_farm)

```

Now join the gapfilled number of farms with data quality = 3 and write the final file of points that need to allocated

```{r}
number_additional_points <- all_number_3 %>%
  mutate(estimated = 0,
         avg_tonnes_per_farm = avg_global_shrimp_tonnes_per_farm) %>%
  dplyr::select(-data_quality) %>%
  rbind(gapfill_1, gapfill_2, number_add_points_4)

## write this out to our data folder

write.csv(number_additional_points, here("marine/shrimp/shrimp_farms/output/shrimp_points_to_add_final.csv"), row.names = FALSE)
```

Now lets make the file with all of the known farms

```{r}
all_known_farms_final <- all_known_farms %>%
  dplyr::select(-data_quality, -subregion, -area_ha)

write.csv(all_known_farms_final, here("marine/shrimp/shrimp_farms/output/all_known_shrimp_farms_final.csv"), row.names = FALSE)

```

Data check

```{r}
test <- all_known_farms %>%
  group_by(iso3c) %>%
  summarise(n_farms = n()) %>%
  dplyr::select(iso3c)

test_2 <- number_additional_points %>%
  dplyr::select(iso3c)

test_all <- rbind(test, test_2)
length(unique(test_all$iso3c)) ## 35 countries

length(unique(shrimp_tonnes$iso3c)) ## 35 countries

## Perfect

```

### 2021-03-23 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
Finished reorganizing data

--- 2021-02-12 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
@@
 
-Now we will map the remaining countries with tuna farms that are not included in the ASC dataset. Workflow will be as follows: 
+Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
  - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
- - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline.
-If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
- - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).
+ - If there are not exact locations or comprehensive locations, find the number of farms. 
+ - If there is no information at all, note it. We will gapfill later.
 
 For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).
- 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
-   - Must not intersect with land mask
-   - "Land mask"
 
-4: Good qualifications - Locations are projected or it is a only sample of total locations
-   - Must not intersect with land mask
-   - "Land mask"
+5: Comprehensive number of exact farms
 
-3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
-   - Must be allocated spatially
-   - Must not intersect with land mask
-   - Flagged as "Allocate spatially"
+4: Subset of exact locations, need to add a specific number of farms to existing locations. 
+  - country|species|farm locations
+  - country|species|additional points
 
-2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
-   - Must be allocated using suitability analysis.
-   - Flagged as 2 and "state/province suitability"
+3: A specific number of farms are known, but no locations 
+ - country|species|additional points
 
-1: Very Bad qualifications - No data at all.
-   - Must be allocated using suitability analysis.
-   - Flagged as 1 and "country suitability"
+2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
+ - country, species, n_existing_points
+
+2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.
+
+1: No information on number of farms at all. Need to be gapfilled by tonnage. 
+ - country|species|# additional farms (this will be NA)
 
@@
 Source:
-EMODnet Human Activities: Finfish production, 2019. [Accessed December 8, 2020] 
+EMODnet Human Activities: Marine Finfish Aquaculture, 2019. [Accessed December 8, 2020] 
 https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production
+
+ - Comprehensive
 
@@
   dplyr::select(-COUNTRY) %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 5)
 
- write_csv(farms_eu_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_ESP_MLT.csv"))
+ write_csv(farms_eu_final, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_ESP_MLT.csv"))
 
@@
 
- - It says both Tuna and Finfish, but we'll assume Croatia and Turkey are tuna...
+Source:
+NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
 
-Source:
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+Croatia: 
+Need to add 14 points to existing 1 (a final total of 15 points)
+
+Current data is from NASO maps collection and is only a subset of farms
+
+NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
+
+We need to add 14 farms to match the total listed by this government source: 
+Lukin, A., 2014. Spatial Planning For Marine Aquaculture, Croatia, Zadar County Case. Croatian Ministry of Agriculture, Directorate of Fisheries.
+
+Turkey:
+Need to add 5 points to existing 3 (a final total of 8 points)
+
+Data is from NASO maps collection, so only a subset
+
+However the FAO gives us specific numbers 
+ - http://www.fao.org/fishery/countrysector/naso_turkey/en
+ - 8 farms
 
@@
   dplyr::select(-country, -geometry) %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 4)
 
-write_csv(farms_med, here("marine/tuna/tuna_farms/data/tuna_sites/farms_hrv_tur.csv"))
+write_csv(farms_med, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_hrv_tur.csv"))
 
@@
 mapview(farms_med)
+
+#### Croatia
+## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
+hrv_additional <- data.frame(iso3c = "HRV", type = "tuna", num_additional_farms = 14, data_quality = 4, total_farms = 15)
+write.csv(hrv_additional, here("marine/tuna/tuna_farms/data/subset_known_add_points_4/add_farms_hrv.csv"), row.names = FALSE)
+
+#### Turkey 
+tur_additional <- data.frame(iso3c = "TUR", type = "tuna", num_additional_farms = 5, data_quality = 4, total_farms = 8)
+write.csv(tur_additional, here("marine/tuna/tuna_farms/data/subset_known_add_points_4/add_farms_tur.csv"), row.names = FALSE)
+
 ```
@@
 
-for(i in seq_along(tuna_links)){
+for(i in 2:seq_along(tuna_links)){
 
-  # i = 2
+  # i = 1
 # Read the webpage into R
@@
   mutate(iso3c = "AUS") %>%
-  mutate(data_quality = 5) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 5) 
 ## now that we have coordinates, place them on a map and save
@@
 
-write_csv(lat_lon_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_AUS.csv"))
+write_csv(lat_lon_final, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"))
 ```
@@
 ```{r}
-world <- rnaturalearth::ne_coastline(scale = 110) # world map with 10m resolution
-plot(world)
+farms_jpn <- data.frame(iso3c = "JPN", type = "tuna", num_additional_farms = 92, data_quality = 3)
 
-japan <- ne_countries(scale = 10, country = "Japan", returnclass = "sf")
-
-#info of our spatial vector object
-japan
-mapview(japan)
-plot(japan)
-
-world <- st_as_sf(world)
-
-japan_world_crs <- st_transform(japan, crs(world))
-
-japan_world_crop <- st_crop(world, japan_world_crs)
-
-japan_world_crop <- japan_world_crop[-c(2,3,4), ]
-plot(japan_world_crop)
-mapview(japan_world_crop)
-
-japan_crop <- as(japan_world_crop, "Spatial")
-
-japan_points_lines <- sample.line(japan_crop, n = 92) ## equally place the number of farms along the coastline 
-class(japan_points_lines)
-plot(japan_points_lines)
-
-japan_points <- st_as_sf(japan_points_lines)
-mapview(japan_points)
-
-## now prep dataframe for lat lon points
-jpn_pts <- st_centroid(japan_points)
-
-jpn_pts_latlon <- st_transform(jpn_pts, crs = "+init=epsg:4326") %>%
-  dplyr::select(geometry)
-
-farms_jpn <- data.frame(do.call(rbind, st_geometry(jpn_pts_latlon)))
-names(farms_jpn) <- c("lon", "lat")
-
-farms_jpn_final <- farms_jpn %>%
-  mutate(iso3c = "JPN") %>%
-  mutate(data_quality = 3) %>%
-  mutate(action_needed = "Allocate spatially")
-
-## visualize it 
-farms_jpn <-  st_as_sf(farms_jpn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_jpn)
-
-## write to farms folder 
-write_csv(farms_jpn_final, here("marine/tuna/tuna_farms/data/tuna_sites/farms_jpn.csv"))
+write_csv(farms_jpn, here("marine/tuna/tuna_farms/data/known_number_farms_3/farms_jpn.csv"))
 ```
@@
                           iso3c = "MEX") %>%
-  mutate(data_quality = 4) %>%
-  mutate(action_needed = "Land mask")
+  mutate(data_quality = 5)
 
@@
 
-write_csv(farms_mex, here("marine/tuna/tuna_farms/data/tuna_sites/farms_MEX.csv"))
+write_csv(farms_mex, here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5/farms_MEX.csv"))
 
@@
 ```{r}
-farm_files <- list.files(here::here("marine/tuna/tuna_farms/data/tuna_sites"), full=TRUE)
+farm_files <- list.files(here::here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5"), full=TRUE)
 all_farms = plyr::ldply(farm_files, read_csv)

### 2021-03-23 marine/tuna/tuna_farms/STEP3_gapfill_tuna.Rmd
Finished reorganizing data

---
title: "Gapfilling the number of farms to add for tuna countries based on tonnes of production"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in all the relevant farm datasets

```{r}

farm_files <- list.files(here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5"), full=TRUE)
all_known_farms = plyr::ldply(farm_files, read_csv) %>%
  mutate(type = "tuna")

number_files <- list.files(here("marine/tuna/tuna_farms/data/known_number_farms_3"), full=TRUE)
all_number_3 = plyr::ldply(number_files, read_csv)

number_files_2.5 <- list.files(here("marine/tuna/tuna_farms/data/known_subset_2.5"), full=TRUE)
all_number_2.5 = plyr::ldply(number_files_2.5, read_csv)

subset_farms_files <- list.files(here("marine/tuna/tuna_farms/data/subset_known_add_points_4"), full=TRUE)
subset_add_4 = plyr::ldply(subset_farms_files, read_csv)

no_info_files <- list.files(here("marine/tuna/tuna_farms/data/no_info_1"), full=TRUE)
no_info_1 = plyr::ldply(no_info_files, read_csv)

subset_gapfill_2 <- all_known_farms %>%
  filter(data_quality == 2)
```

Read in relevant production data
```{r}
tuna_tonnes <- read_csv(here::here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
  mutate(type = "tuna") %>%
  filter(year == 2017)
```

Calculate a global tonnes per farm for tuna

```{r}
## Filter for data_quality = 4 or 5 and group by country to get number of farms
comprehensive_farms <- all_known_farms %>%
  filter(data_quality %in% c(4,5)) %>% 
  group_by(iso3c, type, data_quality) %>%
  summarise(n_farms = n()) %>% ## now we can see the places that has additional farms to add
  ungroup()

## Join this with the additional farms we need to add to some places, so we can calculate a comprehensive tonnes/farm for tuna

data_quality_3 <- all_number_3 %>%
    rename("n_farms" = "num_additional_farms")

data_quality_4 <- subset_add_4 %>%
    rename("n_farms" = "num_additional_farms")

comprehensive_farms_total <- comprehensive_farms %>%
  full_join(data_quality_3) %>%
  full_join(data_quality_4) %>%
  group_by(iso3c, type) %>%
  summarise(n_farms = sum(n_farms)) %>%
  ungroup()

tonnes_per_farm <- comprehensive_farms_total %>%
  left_join(tuna_tonnes) %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n_farms)

avg_global_tuna_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
avg_global_tuna_tonnes_per_farm # 277.4158
```

Now let's gapfill those that are data quality = 2 and data quality = 1, and data quality = 2.5 (if applicable)

```{r}
## start with the subset of locations that need gapfilling based on tonnes/farm
# there are none for tuna

## now lets do the locations that have no info and need gapfilling based on tonnes/farm
# there are none for tuna

## Wrangle those that just need a specific number of points added (data_quality = 4)

number_add_points_4 <- subset_add_4 %>%
  dplyr::select(-data_quality, -total_farms) %>%
  mutate(estimated = 0, 
         avg_tonnes_per_farm = avg_global_tuna_tonnes_per_farm)

```

Now join the gapfilled number of farms with data quality = 3 and write the final file of points that need to allocated

```{r}
number_additional_points <- all_number_3 %>%
  mutate(estimated = 0,
         avg_tonnes_per_farm = avg_global_tuna_tonnes_per_farm) %>%
  dplyr::select(-data_quality) %>%
  rbind(number_add_points_4)

## write this out to our data folder

write.csv(number_additional_points, here("marine/tuna/tuna_farms/output/tuna_points_to_add_final.csv"), row.names = FALSE)
```

Now lets make the file with all of the known farms

```{r}
all_known_farms_final <- all_known_farms %>%
  dplyr::select(-data_quality)

write.csv(all_known_farms_final, here("marine/tuna/tuna_farms/output/all_known_tuna_farms_final.csv"), row.names = FALSE)

```

Data check

```{r}
test <- all_known_farms %>%
  group_by(iso3c) %>%
  summarise(n_farms = n()) %>%
  dplyr::select(iso3c)

test_2 <- number_additional_points %>%
  dplyr::select(iso3c)

test_all <- rbind(test, test_2)
length(unique(test_all$iso3c)) ## 7 countries

length(unique(tuna_tonnes$iso3c)) ## 7 countries

## Perfect

```

### 2021-03-23 marine_mapping_archive_v1/STEP1_species_groups/STEP1_species_groups.Rmd
Finished reorganizing data

--- 2021-02-03 marine/STEP1_species_groups/STEP1_species_groups.Rmd
@@
 
-source(here('aquaculture/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
+source(here('R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
 source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
-
+source(here('workflow/common.R'))
 ```
@@
 table(fao$environment)
+
 ## convert to long format and clean FAO codes:
@@
     fao_clean_data() %>%
-  filter(year >= 2010) %>%
-  group_by(country, species, fao_major_area, environment) %>%
-  mutate(total_harvest = sum(value, na.rm=TRUE)) %>%
-  filter(total_harvest > 0) %>% # data is cut if country/species/major area hasn't been harvested since 2010
+  dplyr::filter(year >= 2010) %>%
+  dplyr::group_by(country, species, fao_major_area, environment) %>%
+  dplyr::mutate(total_harvest = sum(value, na.rm=TRUE)) %>%
+  dplyr::filter(total_harvest > 0) %>% # data is cut if country/species/major area hasn't been harvested since 2010
   dplyr::select(-total_harvest) %>%
-  ungroup()
+  dplyr::ungroup()
 
@@
 ## save
-write.csv(fao, here("aquaculture/data/fao_mariculture_clean.csv"), row.names=FALSE)
+write.csv(fao, here("data/fao_aquaculture_clean.csv"), row.names=FALSE)
 
@@
 
-fao <- read_csv("aquaculture/data/fao_mariculture_clean.csv")
+fao <- read_csv("data/fao_aquaculture_clean.csv")
 
@@
 
-write.csv(fw, "aquaculture/marine/STEP1_species_groups/int/fw_spp.csv", row.names = FALSE)
+write.csv(fw, "marine/STEP1_species_groups/int/fw_spp.csv", row.names = FALSE)
 
@@
 
-# emissions <- read_csv("aquaculture/data/emissions_aquaculture.csv")
-# unique(emissions$`Scientific Name`)
-## 32 different species
-
 fao_marine <- fao %>%
@@
   dplyr::select(-exclude, -alias) %>%
-  dplyr::filter(str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver"))
+  dplyr::filter(str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver")) ## look at those species we will be cutting (because they are freshwater)
 
@@
                 species != "Red oyas",
-                species != "Jellyfishes nei") ## delete freshwater, catfish species, seaweeds, jellyfish..
+                species != "Jellyfishes nei") ## delete freshwater, catfish species, tilapia, river species, seaweeds, jellyfish..
 ```
@@
 ```{r}
-# Need to classify into these groups: 
+# Need to classify into these groups, for easier mapping and pressure calculations: 
 #  - Bivalves
@@
 #  - crustaceans
-#  - marine fish general
+#  - marine fish general (all the other finfish species)
 
@@
 ## All of those classified as BI will be Bivalves
-## CRUST - classified as bivalves
+## CRUST - classified as crustaceans
 ## GAST - classify as bivalves
@@
 ## write it out
-write.csv(aquaculture_groups, "aquaculture/marine/STEP1_species_groups/int/marine_groups.csv", row.names = FALSE)
+write.csv(aquaculture_groups, "marine/STEP1_species_groups/int/marine_groups.csv", row.names = FALSE)
 
-aq_groups <- read.csv("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv")
+aq_groups <- read.csv("marine/STEP1_species_groups/int/marine_groups.csv")
 
-fao_1 <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
+fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
   filter(environment %in% c("Marine", "Brackishwater")) %>%
@@
 
-write.csv(fao_1, "aquaculture/marine/STEP1_species_groups/int/tonnes_per_country_group.csv", row.names = FALSE)
+write.csv(fao_1, "marine/STEP1_species_groups/int/tonnes_per_country_group.csv", row.names = FALSE)
 
@@
   dplyr::filter(aq_group == "bivalves")
-sum(test$total_tonnes) # 17439040
+sum(test$total_tonnes) # 17435623
 

### 2021-03-23 marine_mapping_archive_v1/STEP1_species_groups/STEP2_ASC_data_prep.Rmd
Finished reorganizing data

---
title: "Prep ASC data"
output: html_document
---

Prep the aquaculture stewardship data and save as a shp to use for the different species groups.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)
library(sf)
library(mapview)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))
```

```{r}
fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))

fao_all <- species_list %>%
  # filter(species %in% shrimp_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>% 
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  # dplyr::filter(aq_group == "bivalves") %>%
  # dplyr::filter(year == 2017) # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, aq_group, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year) %>%
  dplyr::filter(year == 2017)
```

```{r}
ASC_data <- read_csv(file.path(here::here("data/ASC_farms.csv"))) ## downloaded from ASC website

unique(fao_all$aq_group)
# [1] "marine_fish_general" "bivalves"            "salmonids"           "shrimps_prawns"     
# [5] "tuna"                "crustaceans"

unique(ASC_data$species__c)

unique(ASC_data$farm_species)

unique(ASC_data$cert_country)

ASC_classified <- ASC_data %>%
  dplyr::filter(species__c %notin% c("Freshwater Trout", "Pangasius", "Seaweed (Algae)", "Tilapia")) %>%
  mutate(aq_group = case_when(
    species__c %in% c("Shrimp") ~ "shrimps_prawns",
    species__c %in% c("Abalone", "Bivalve") ~ "bivalves",
    species__c %in% c("Salmon") ~ "salmonids",
    species__c %in% c("Seabass, Seabream and Meagre", "Seriola and Cobia", "Tropical Marine Finfish") ~ "marine_fish_general"
  ))

## Now we need to make the ASC data into an sf
ASC_all_sf <- ASC_classified %>%
  mutate(geometry = str_replace_all(geom, "POINT|[()]", "")) %>%
  mutate(geometry = trimws(geometry)) %>%
  mutate(x= as.numeric(gsub(" .*$", "", geometry))) %>%
  dplyr::filter(!is.na(geom)) %>%
  mutate(y = as.numeric(sub("^\\S+\\s+", '', geometry))) %>%
  dplyr::select(-geometry, -geom, -X10, -X11, -X12, -X13, -X14)  %>%
  st_as_sf(coords = c("x", "y"), crs = 4326)

mapview(ASC_all_sf$geometry)

## now we need to write as a shapefile 
# st_write(ASC_all_sf, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/ASC_all_sf.shp", overwrite = TRUE)

st_write(ASC_all_sf, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/ASC_data/ASC_all_sf.shp", overwrite = TRUE)
```

See how many countries from FAO are represented in ASC for marine_fish_general category

```{r}
fao_marine_fish <- fao_all %>%
  dplyr::filter(aq_group == "marine_fish_general")

ASC_marine_fish <- ASC_all_sf %>%
  dplyr::filter(aq_group == "marine_fish_general")

setdiff(fao_marine_fish$country, ASC_marine_fish$cert_country)

#  [1] "Bangladesh"               "Cambodia"                 "China"                   
#  [4] "China, Hong Kong SAR"     "Costa Rica"               "Cyprus"                  
#  [7] "Egypt"                    "France"                   "India"                   
# [10] "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
# [13] "Italy"                    "Korea, Republic of"       "Malaysia"                
# [16] "Malta"                    "Mauritius"                "Norway"                  
# [19] "Philippines"              "Portugal"                 "Saudi Arabia"            
# [22] "Singapore"                "Taiwan Province of China" "Tunisia"                 
# [25] "United Arab Emirates"

setdiff(ASC_marine_fish$cert_country, fao_marine_fish$country)
# [1] "Netherlands" "Denmark"     "Germany"

unique(ASC_marine_fish$cert_country)
```

See how many countries from FAO are represented in ASC for bivalves category

```{r}
fao_bivalve <- fao_all %>%
  dplyr::filter(aq_group == "bivalves")

ASC_bivalve <- ASC_all_sf %>%
  dplyr::filter(aq_group == "bivalves")

setdiff(fao_bivalve$country, ASC_bivalve$cert_country)

#  [1] "Brazil"                   "Bulgaria"                 "Cambodia"                
#  [4] "Canada"                   "China, Hong Kong SAR"     "Croatia"                 
#  [7] "Cuba"                     "Denmark"                  "French Polynesia"        
# [10] "Germany"                  "Greece"                   "Guernsey"                
# [13] "India"                    "Indonesia"                "Ireland"                 
# [16] "Italy"                    "Jersey"                   "Korea, Dem. People's Rep"
# [19] "Malaysia"                 "Netherlands"              "Norway"                  
# [22] "Philippines"              "Russian Federation"       "Slovenia"                
# [25] "Spain"                    "Sweden"                   "Taiwan Province of China"
# [28] "Thailand"                        "United States of America"

setdiff(ASC_bivalve$cert_country, fao_bivalve$country)
# United kingdom spelled differently.. don't worry about it

unique(ASC_bivalve$cert_country)
```

Tuna
```{r}
fao_tuna <- fao_all %>%
  dplyr::filter(aq_group == "tuna")

ASC_tuna <- ASC_all_sf %>%
  dplyr::filter(aq_group == "tuna")

unique(fao_tuna$country)
```

Crustaceans
```{r}
fao_crust <- fao_all %>%
  dplyr::filter(aq_group == "crustaceans")

ASC_crust <- ASC_all_sf %>%
  dplyr::filter(aq_group == "crustaceans")

unique(fao_crust$country)
```

### 2021-03-23 marine_mapping_archive_v1/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
Finished reorganizing data

---
title: "FAO bivalve production"
author: "Gage Clawson (USCB, NCEAS, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

All data is ultimately adjusted to FAO production data.  This script cleans the fao mariculture data and subsets it to to the relevant years of data and species (bivalve).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))

```

Subset the data to include only the species (bivalve) and countries we are interested in. Then summarize by total tonnes of bivalve per country/year. (There are multiple bivalve species)

```{r}

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon 
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
bivalve_list <- species_list$species[species_list$aq_group=="bivalves"]
bivalve_list

## write out bivalve taxa and production for Juliette
fao_bivalve_taxa_prod <- fao %>%
  filter(species %in% bivalve_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

write.csv(fao_bivalve_taxa_prod, here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"), row.names=FALSE)

# include only bivalves
fao_bivalve <- fao %>%
  filter(species %in% bivalve_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500,
         year == 2017) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year)

write.csv(fao_bivalve, here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv"), row.names=FALSE)

 explore <- read_csv(here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = fao_tonnes_production/sum(fao_tonnes_production)*100)

sum(explore$fao_tonnes_production) # 17435623

explore <- fao_bivalve %>%
  dplyr::filter(year == 2017)
```

Abalones nei, American cupped oyster, Aquatic invertebrates nei, Australian mussel, Blacklip pearl oyster, Blood cockle, Blue mussel, Butter clam, Chilean mussel, Cholga mussel, Choro mussel, Clams, etc. nei, Common edible cockle, Constricted tagelus, Cortez oyster, Cupped oysters nei, European flat oyster, Flat and cupped oysters nei, Green mussel, Grooved carpet shell, Indian backwater oyster, Inflated ark, Japanese carpet shell, Japanese hard clam, Japanese sea cucumber, Korean mussel, Mangrove cupped oyster, Marine molluscs nei, Mediterranean mussel, New Zealand mussel, Northern quahog, Pacific cupped oyster, Pacific geoduck, Pen shells nei, Penguin wing oyster, Perlemoen abalone, Peruvian calico scallop, Red abalone, Sand gaper, Scallops nei, Sea cucumbers nei, Sea mussels nei, Sea snails, Sea squirts nei, Sea urchins nei, Slipper cupped oyster, South American rock mussel, Yesso scallop

### 2021-03-23 marine_mapping_archive_v1/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
Finished reorganizing data

--- 2021-03-09 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
@@
 
+We filter out france and great britain, because those farms are already accounted for in the EMODnet database.
+
 Source: 
@@
 what we've done for Russia).
+
+# Chile
+
+Data for Chile comes from https://mapas.subpesca.cl/ideviewer/?locale=en-gb.
+
+There is also a list of concessions here: http://www.subpesca.cl/portal/619/w3-article-92935.html
+
+I was in contact with Valeria Tamayo at UCSB who helped me with some spanish translations concerning this data.
+
+Source:
+Undersecretariat for Fisheries and Aquaculture, 2020. [Accessed Feb 2020] https://mapas.subpesca.cl/ideviewer/?locale=en-gb
+
+```{r}
+
+# Column meaning and names
+#0 LINK_DOC - URL of the SUBPESCA resolution approving the aquaculture or resolution technical project that cartographically regulates the aquaculture concession
+#1 CARTA - Name of the geographic reference letter
+#2 DATUM - Reference datum name
+#3 HUSO - Spindle Name
+#4 COMUNA - Name of the commune
+#5 N_PERT - Pert number, code of the application for admission to process
+#6 N_CODIGOCE - Farming center code according to the national aquaculture registry
+#7 N_RESOLSSP - Resolution number of the undersecretary of fisheries and aquaculture that apprehends the aquaculture technical project
+#8 F_RESOLSSP - Date of issuance of the resolution of the undersecretary of fisheries and aquaculture approving the aquaculture technical project
+#9 N_RESOLSSF - Resolution number of the undersecretary for the armed forces granted by the aquaculture concession
+#10 F_RESOLSSF - Date of issuance of the resolution of the undersecretary for the armed forces granted by the aquaculture concession
+#11 TOPONIMIO - Geographical location of the aquaculture concession
+#12 ESPECIES - Name of crop species
+#13 AGRUPCONCE - Identifier of the salmonid concession group or sanitary neighborhood
+#14 SUPERFICIE - Surface in hectares
+#15 TITULAR - Name of the holder of the aquaculture concession
+#16 COORDENADS - List of geographical coordinates of the aquaculture concession corresponding to each of the vertices of the polygon
+#17 REGION - Region name
+#18 GRUPO_ESP - Group of crop species
+#19 TIPO_PORCI - Type of space where the aquaculture concession is located
+#20 ESTADO - Processing status of the aquaculture concession
+#21 ESTADO_SOL - Status of the aquaculture application process
+
+chile_dat <- st_read(file.path(path, "Chile"), layer = "Concesiones_de_Acuicultura")
+
+```
+
+We filter to only those that produce salmon, but note that this is ALL leases, not neccesarily only active sites. 
+```{r}
+unique(chile_dat$REP_SUB_13)
+
+#Filter to only bivalve farming (mussel, abalone, oysters, clams, and scallops)
+chile <- chile_dat %>% 
+  filter(grepl("CHORO|ABALON|OSTRA|CHOLGA|CHORITO|OSTION|ALMEJA|MITILIDOS", REP_SUB_13)) %>%
+  filter(!grepl("SALMON", REP_SUB_13))
+
+# convert polygons to points
+chile_pts <- st_centroid(chile)
+chile_pts <- st_transform(chile_pts, food_crs)
+
+# save as a dataframe
+farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
+names(farms_chile) <- c("lon", "lat")
+farms_chile <- farms_chile %>%
+  mutate(iso3c="CHL") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land mask")
+
+write_csv(farms_chile, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_chl.csv"))
+
+```
 
@@
 
-##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece
+##  Europe - EMODNET: Ireland, Bulgaria, Italy, Norway, Netherlands, Greece, UK, France
 https://www.emodnet-humanactivities.eu/search-results.php?dataname=Shellfish+Production
@@
     COUNTRY == "Italy" ~ "ITA", 
-    COUNTRY == "Greece" ~ "GRC"
+    COUNTRY == "Greece" ~ "GRC",
+    COUNTRY == "France" ~ "FRA",
+    COUNTRY == "United Kingdom" ~ "GBR"
   )) %>%
@@
 
- write_csv(farms_eu_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_IRL_BGR_NOR_NLD_ITA_GRC.csv"))
+write_csv(farms_eu_final, here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_GBR_FRA_IRL_BGR_NOR_NLD_ITA_GRC.csv"))
 

### 2021-03-23 marine_mapping_archive_v1/bivalve/bivalve_farms/STEP3_rasterize_production.Rmd
Finished reorganizing data

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (USCB, NCEAS, OHI)"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

farms <- read.csv(here::here("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon.csv"))

farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sf)
```

# determine subregions where points are located

```{r}

farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)

farms_sf <- farms_sf %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

## read in those needed to check 
ireland <- read_csv(here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_IRL_BGR_NOR_NLD_ITA_GRC.csv")) %>%
  dplyr::filter(iso3c == "IRL")

britain <- read_csv(here("marine/bivalve/bivalve_farms/data/bivalve_sites/ASC_bivalve_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "GBR")

taiwan <- read_csv(here("marine/bivalve/bivalve_farms/data/bivalve_sites/farms_twn.csv"))

## Need to be changed to this 
# GBR:JEY - GBR
# HRV:MNE - HRV
# TWN:CHN - TWN
# IRL:GBR - IRL
# PRK:RUS - PRK
# SVN:HRV - SVN
# SVN:ITA - SVN
# HKG:CHN - HKG

# some annoying mismatches due to raster resolution. Fix these

unique(farms_sf$NAME_1)

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "GBR:JEY", "GBR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GBR:JEY", "United Kingdom", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:MNE", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:MNE", "Croatia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "PRK:RUS", "PRK", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "SVN:ITA", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:ITA", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

```

# FAO bivalve production data per country
```{r}

fao <- read.csv(here::here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

setdiff(fao$iso3c, farms_sf$iso3c)
setdiff(farms_sf$iso3c, fao$iso3c)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# combine and check it all matches ok

```{r}

test <- farms_prod %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

farms_sf_prod <- st_as_sf(farms_prod)

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "marine/bivalve/bivalve_nutrient/prod_data_by_cell_iso3c.shp")

```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farms_prod)
mapview(farms_sf)

sum(farms_sf$tonnes_per_farm) # 17435623

bivalve_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(bivalve_raster_check+1))
cellStats(bivalve_raster_check, stat = "sum", na.rm = TRUE) # 17435623

bivalve_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)

plot(log(bivalve_raster+1))

bivalve_raster_df <- as.data.frame(bivalve_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(bivalve_raster, stat = "sum") # 17435623
sum(bivalve_raster_df$tonnes_production) # 17435623
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17435623
sum(fao$fao_tonnes_production) # 17435623

write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/bivalve_farm.csv")

```

### 2021-03-23 marine_mapping_archive_v1/crustaceans/crustacean_farms/STEP1_fao_crustacean_production.Rmd
Finished reorganizing data

---
title: "FAO crustaceam production"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "12/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

All data is ultimately adjusted to FAO production data.  This script cleans the fao mariculture data and subsets it to to the relevant years of data and species (crustaceans).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))

```

Subset the data to include only the species (crustacean) and countries we are interested in. Then summarize by total tonnes of crustacean per country/year. (There are multiple crustacean species)

```{r}

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for crustaceans 
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
crustaceans_list <- species_list$species[species_list$aq_group=="crustaceans"]
crustaceans_list

## write out crustacean taxa and production for Juliette
fao_crustaceans_taxa_prod <- fao %>%
  filter(species %in% crustaceans_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

write.csv(fao_crustaceans_taxa_prod, here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans_taxa_production.csv"), row.names=FALSE)

# include only crustacean
fao_crustaceans <- fao %>%
  filter(species %in% crustaceans_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year)

write.csv(fao_crustaceans, here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv"), row.names=FALSE)

 explore <- read_csv(here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100,2))

```

### 2021-03-23 marine_mapping_archive_v1/crustaceans/crustacean_farms/STEP3_rasterize_production.Rmd
Finished reorganizing data

--- 2021-02-04 marine/marine_fish_general/finfish_farms/STEP3_rasterize_production.Rmd
@@
 author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/17/2020"
 output: html_document
@@
 
-farms <- read.csv(here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"))
+farms <- read.csv(here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"))
 
@@
 
-# CYP:XAD
-# ESP:PRT
-# GRC:ALB
-# GRC:TUR
-# KOR:PRK
-# HKG:CHN
-
-mapview(filter(farms_sf, check=="CYP:XAD"))
-mapview(filter(farms_sf, check=="ESP:PRT"))
-mapview(filter(farms_sf, check =="GRC:ALB"))
-mapview(filter(farms_sf, check == "GRC:TUR"))
-mapview(filter(farms_sf, check == "KOR:PRK"))
-
-# some annoying mismatches due to raster resolution. Fix these
-
-unique(farms_sf$NAME_1)
-
-farms_sf_correct <- farms_sf %>%
-  mutate(GID_0 = as.character(GID_0)) %>%
-  mutate(NAME_0 = as.character(NAME_0)) %>%
-  mutate(NAME_1 = as.character(NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "KOR:PRK", "KOR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "KOR:PRK", "South Korea", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0))
-
-farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
-table(farms_sf_correct$check)
-
 ```
 
-# FAO shrimp production data per country
+# FAO crustacean production data per country
 ```{r}
 
-fao <- read.csv(here::here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
+fao <- read.csv(here::here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
   dplyr::filter(year == 2017) %>%
@@
 
-farms_sf_correct <- farms_sf_correct %>%
+farms_sf_correct <- farms_sf %>%
   left_join(fao, by="iso3c")
@@
 
-## Egypt is the only one with regional production
+## Vietnam and Philippines have regional production
 farms_rgn_prod <- farms_sf_correct %>%
-  dplyr::filter(!is.na(rgn_production))
+  dplyr::filter(!is.na(prod))
 
@@
 farms_rgn_prod <- farms_rgn_prod %>%
-  mutate(prop_production = rgn_production/sum(rgn_production)) %>%
+  group_by(iso3c) %>%
+  mutate(prop_production = prod/sum(prod)) %>%
   mutate(regional_prod = fao_tonnes_production*prop_production) %>%
-  group_by(NAME_1) %>%
+  group_by(iso3c, sub_rgn) %>%
   add_tally() %>%
@@
 
+## Check to make sure the totals match
+test <- farms_rgn_prod %>%
+  dplyr::filter(iso3c == "VNM")
+
+sum(test$tonnes_per_farm)
 ```
@@
   dplyr::select(iso3c, tonnes_per_farm, geometry) %>%
-  dplyr::filter(iso3c != "EGY") ## filter out EGY since we have regional production estimates
+  dplyr::filter(!(iso3c %in% c("VNM", "PHL"))) ## filter out VNM and PHL since we have regional production estimates for those countries
 
@@
 
-farms_sf_prod <- st_as_sf(farm_production)
-
-## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "marine/marine_fish_general/finfish_nutrient/prod_data_by_cell_iso3c.shp")
 ```
@@
 
-sum(farms_sf$tonnes_per_farm) # 3901214
+sum(farms_sf$tonnes_per_farm) # 401719.1
+sum(fao$fao_tonnes_production) # 401719.1
 
-finfish_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
-plot(log(finfish_raster_check+1))
-cellStats(finfish_raster_check, stat = "sum", na.rm = TRUE) # 3901214
+crustacean_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
+plot(log(crustacean_raster_check+1))
+cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 401719.1
 
-finfish_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
-plot(log(finfish_raster+1))
+crustacean_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
 
-finfish_raster_df <- as.data.frame(finfish_raster, xy=TRUE) %>%
+plot(log(crustacean_raster+1))
+
+crustacean_raster_df <- as.data.frame(crustacean_raster, xy=TRUE) %>%
   dplyr::select(x,y, tonnes_production=layer)
 
-cellStats(finfish_raster, stat = "sum") # 3901214
-sum(finfish_raster_df$tonnes_production) # 3901214
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3901214
-sum(fao$fao_tonnes_production) # 3901214
+cellStats(crustacean_raster, stat = "sum") # 401719.1
+sum(crustacean_raster_df$tonnes_production) # 401719.1
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 401719.1
+sum(fao$fao_tonnes_production) # 401719.1
 
-write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/marine_fish_general_farm.csv")
+write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/crustaceans_farm.csv")
 

### 2021-03-23 marine_mapping_archive_v1/explore_spatial_allocation.Rmd
Finished reorganizing data

--- 2021-03-09 marine/explore_spatial_allocation.Rmd
@@
 
-## make a dataset with the country, species type (farm type), tonnage, and # of farms, for those that score data quality %in% c(3,4,5)
+## make a dataset with the country, species type (farm type), tonnage, and # of farms, for those that score data quality %in% c(3, 4, 5)...
+review all of these, since many of these are just subsets of total number of farms...
+
 sum(all_species_country_tonnes$fao_tonnes_production) # 29623515
+
+n_farms_final <- n_farms %>%
+  filter(data_quality %in% c(3,4,5))
 

### 2021-03-23 marine_mapping_archive_v1/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
Finished reorganizing data

--- 2021-02-17 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
@@
 If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan bivalve/shrimp). 
  - Lastly, if there is no evidence of marine finfish farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
@@
 Source:
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
 
@@
 Source:
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites
 
@@
 Source: 
-NASO aquaculture maps collection , 2010.
-.
-Food and Agriculture Organization of the United Nations.
-[Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/thailand/en/
+NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
 
@@
 Source: 
-Estatísticas da Pesca, 2020. . Instituto Nacional de Estatística. [Accessed December 21, 2020]
+Estatísticas da Pesca, 2020. Instituto Nacional de Estatística. [Accessed December 21, 2020]
 
@@
 Source: 
-Food Farms in Singapore, 2019. . Singapore Food Agency. [Accessed December 17, 2020] https://www.sfa.gov.sg/food-farming/food-farms/farming-in-singapore
+Food Farms in Singapore, 2019. Singapore Food Agency. [Accessed December 17, 2020] https://www.sfa.gov.sg/food-farming/food-farms/farming-in-singapore
 

### 2021-03-23 marine_mapping_archive_v1/marine_fish_general/food_pressures/finfish_nutrient/step1_nutrient.Rmd
Finished reorganizing data

--- 2021-02-03 marine/marine_fish_general/finfish_nutrient/step1_nutrient.Rmd
@@
 ## Read in fao data and get a species list for salmon
-species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
+species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
   distinct(species, aq_group)

### 2021-03-23 marine_mapping_archive_v1/salmon/food_pressures/salmon_disturbance/STEP2_occupancy_distribution.Rmd
Finished reorganizing data

--- 2021-02-03 marine/salmon/salmon_disturbance/STEP2_occupancy_distribution.Rmd
@@
 ```{r parameters from conversion table}
-salmon_conversion <- read_csv(here("aquaculture/marine/salmon/salmon_disturbance/data/salmon_conversion_factors.csv"))
+salmon_conversion <- read_csv(here("marine/salmon/food_pressures/salmon_disturbance/data/salmon_conversion_factors.csv"))
 

### 2021-03-23 marine_mapping_archive_v1/salmon/food_pressures/salmon_ghg/STEP1_ghg_emissions.Rmd
Finished reorganizing data

--- 2021-02-03 marine/salmon/food_pressures/salmon_ghg/STEP1_ghg_emissions.Rmd
@@
 
-fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
+fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
   filter(environment %in% c("Marine", "Brackishwater"))
@@
 ## Read in fao data and get a species list for salmon 
-species_list <- read.csv(here("aquaculture/marine/species_groups/int/marine_groups.csv"))  %>%
+species_list <- read.csv(here("marine/species_groups/int/marine_groups.csv"))  %>%
   distinct(species, aq_group)

### 2021-03-23 marine_mapping_archive_v1/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
Finished reorganizing data

--- 2021-02-17 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
@@
 ```
+
 Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
@@
 We use the number of salmon licenses to get a proxy for the relative distribution of production along the Norwegian coast. 
-
+†
 ## Load csv with lat long
@@
 
+norway <- read_csv(here("marine/salmon/salmon_farm/data/farm_sites/farms_nor.csv"))
+
+norway_sf <- st_as_sf(norway, coords = c("lon", "lat"), 
+                         crs = crs(gadm_latlon), agr = "constant")
+
+mapview(norway_sf)
+
 ```
@@
 Nova Scotia Marine Aquaculture Leases , 2020.
-.
 Nova Scotia Fisheries and Aquaculture.
@@
 
- - this will receive a 0.667 (good quality), since I do not believe it is comprehensive, and is only a sample of points.
+ - this will receive a 4 (good quality), since I do not believe it is comprehensive, and is only a sample of points.
 
@@
 Source:
-HELCOM Map and Data Service, n.d. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
+HELCOM HOLAS II Dataset: Finfish mariculture, 2017. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]
 

### 2021-03-23 marine_mapping_archive_v1/salmon/salmon_farm/STEP4_rasterize_production.Rmd
Finished reorganizing data

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this script we allocated the production per farm (equally if there is no subregional production estimates).

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

farms <- read.csv(here("aquaculture/marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"))

farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

```

# determine subregions where points are located

```{r}

farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)

farms_sf <- farms_sf %>%
  left_join(gadm_codes, by="reg_id") %>%
    dplyr::mutate(subregion = as.character(subregion)) %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1)) %>%
  dplyr::mutate(NAME_1 = ifelse(is.na(subregion), NAME_1, subregion))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)
mapview(filter(farms_sf, check=="CAN:USA"))
mapview(filter(farms_sf, check=="USA:CAN"))
mapview(filter(farms_sf, check =="SWE:SWE"))
mapview(filter(farms_sf, check == "FIN:ALA"))
mapview(filter(farms_sf, check == "FIN:RUS"))

mapview(filter(farms_sf, check == "RUS:RUS"))
mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

unique(farms_sf$NAME_1)

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CAN:USA", "CAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CAN:USA", "Canada", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "CAN:USA", "New Brunswick", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "USA:CAN", "Maine", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:ALA", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:ALA", "Finland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```

# FAO salmon production data per country
```{r}

fao <- read.csv(here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with regional production data and calculate production per farm
```{r}

rgn_prod <- read_csv(here("marine/salmon/salmon_farm/data/proportional_regional_production.csv")) %>%
  dplyr::select(iso3c, NAME_1 = region, prop_production)

rgn_prod_country <- unique(rgn_prod$iso3c)

farms_rgn_prod <- farms_sf_correct %>%
  dplyr::filter(GID_0 %in% rgn_prod_country)

# make sure region names match
no_match <- setdiff(rgn_prod$NAME_1, farms_rgn_prod$NAME_1)
no_match

setdiff(farms_rgn_prod$NAME_1, rgn_prod$NAME_1)

#this is ok: little or no production in these regions
test <- filter(rgn_prod, NAME_1 %in% no_match)

## calculate farm production
farms_rgn_prod <- farms_rgn_prod %>%
  left_join(rgn_prod) %>%
  mutate(regional_prod = fao_tonnes_production*prop_production) %>%
  group_by(NAME_1) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = regional_prod/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

test <- farms_rgn_prod %>%
  dplyr::filter(iso3c == "NOR")

sum(test$tonnes_per_farm) # 1299663

test2 <- fao %>%
  dplyr::filter(iso3c == "NOR")

sum(test2$fao_tonnes_production) # 1303255
```

# get areas with no regional production data and calculate production per farm

```{r}

rgn_prod <- read_csv(here("marine/salmon/salmon_farm/data/proportional_regional_production.csv")) %>%
  dplyr::select(iso3c, NAME_1 = region, prop_production)
rgn_prod_country <- unique(rgn_prod$iso3c)

farms_prod <- farms_sf_correct %>%
  dplyr::filter(!(GID_0 %in% rgn_prod_country))

## calculate farm production
farms_prod <- farms_prod %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# combine and check it all matches ok

```{r}

farm_production <- rbind(farms_prod, farms_rgn_prod)

test <- farm_production %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farm_production)
mapview(farms_sf)

salmon_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
mapview(salmon_raster_check)

salmon_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(salmon_raster + 1))

salmon_raster_df <- as.data.frame(salmon_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(salmon_raster, stat = "sum") # 2746086
sum(salmon_raster_df$tonnes_production) # 2746086
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2746086
sum(fao$fao_tonnes_production) #2753752

write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm.csv")

```

### 2021-03-23 marine_mapping_archive_v1/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
Finished reorganizing data

--- 2021-02-17 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
@@
 
+```
+
+# Belize
+ - There are 3 shrimp farms represented in the ASC data. However, the FAO report on aquaculture reports a number of other farms. Specifically: 
+ - http://www.fao.org/fishery/countrysector/naso_belize/en
+ -  “The fourteen shrimp farms operational are all located on the lower coastal plain of mainland Belize.
+The two northern-most of these farms (Nova Ladyville Shrimp Farm, Caribbean Shrimp Farm) are located in the Ladyville area, just north-east of the PSW Goldson International Airport.
+There are three shrimp farms (Crown Shrimp Limited, Paradise Shrimp Farm, Melinda Mariculture Limited) located between the Coastal Road and Dangriga area.
+There are two shrimp farms (Triton Mariculture, Haney's Shrimp Farm) situated between Dangriga and Riversdale.
+There are another four farms (Belize Aquaculture Limited, Royal Mayan Shrimp Farm, Texmar Shrimp Farm, Crustaceans Shrimp Farm) located between Riversdale and the lower reaches of the Placencia Lagoon.
+Three of these farms (Aquamar Shrimp Farm, Nova Toledo Shrimp Farm, Toledo Fish Farm) are also located in the Big Creek/Monkey River area.”
+
+ - Since we have the names of these… I will google and attempt to place on the map.
+The ASC already has 3 mapped (Aquamar shrimp farm, Cardelli farms, and Royal Mayan Shrimp Farms).
+Only 2 of these overlap, so we will assume that Cardelli has been added since the FAO report was published.
+ - I will need to place Nova Ladyville Shrimp Farm, Caribbean Shrimp Farm, Crown Shrimp Limited, Paradise Shrimp Farm, Melinda Mariculture Limited, Triton Mariculture, Haney's Shrimp Farm, Belize Aquaculture Limited, Texmar Shrimp Farm, Crustaceans Shrimp Farm, Nova Toledo Shrimp Farm, Toledo Fish Farm.
+If I can’t find these on google, then we will place the remaining number of farms randomly in suitable locations.
+
+Nova Ladyville Shrimp Farm - This one has since been closed. 
+Caribbean Shrimp Farm - 17.565826428687156, -88.30446591534489
+Crown Shrimp Limited - Not on the map... I believe this has likely closed. 
+Paradise Shrimp Farm - 17.088537866900786, -88.3141468760761
+Melinda Mariculture Limited - 16.996401736714773, -88.28891758186664
+Triton Mariculture - 16.91300830350531, -88.30401223336973
+Haney's Shrimp Farm - 16.77084262777864, -88.3358879288162
+Belize Aquaculture Limited - 16.664824857803115, -88.39502139821094
+Texmar Shrimp Farm - 16.56115563573352, -88.41922498380852
+Crustaceans Shrimp Farm - Not on the map... I believe this has likely closed. 
+Nova Toledo Shrimp Farm - 16.460774477225453, -88.43760570009555
+Toledo Fish Farm - 16.43434608053408, -88.4650001965993
+
+```{r}
+
+farms_blz <- data.frame(lat=c(17.565826428687156, 17.088537866900786, 16.996401736714773, 16.91300830350531, 16.77084262777864, 16.664824857803115, 16.56115563573352, 16.460774477225453, 16.43434608053408),
+                        lon=c(-88.30446591534489, -88.3141468760761, -88.28891758186664, -88.30401223336973, -88.3358879288162, -88.39502139821094, -88.41922498380852, -88.43760570009555, -88.4650001965993),
+                        subregion = c("Nova Ladyville Shrimp Farm", "Paradise Shrimp Farm", "Melinda Mariculture Limited", "Triton Mariculture", "Haney's Shrimp Farm", "Belize Aquaculture Limited", "Texmar Shrimp Farm", "Nova Toledo Shrimp Farm", "Toledo Fish Farm")) %>%
+  mutate(iso3c = "BLZ") %>%
+  mutate(data_quality = 5) %>%
+  mutate(action_needed = "Land Mask")
+
+write_csv(farms_blz, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_blz.csv"))
+
+## visualize it 
+farms_blz <-  st_as_sf(farms_blz, coords = c("lon", "lat"), 
+                 crs = crs(gadm_latlon), agr = "constant")
+
+mapview(farms_blz)
 ```
@@
 Source: 
-National Aquaculture Sector Overview. Cuba, 2005. , National Aquaculture Sector Overview Fact Sheets.
+National Aquaculture Sector Overview. Cuba, 2005. National Aquaculture Sector Overview Fact Sheets.
 
@@
  Source: 
-National Aquaculture Sector Overview. El Salvador, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
+National Aquaculture Sector Overview. El Salvador, 2005. National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
 
@@
 Source: 
-Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. . Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78
+Aquaculture Industrial Zone Area for High Impact Projects (HIP), n.d. Department of Fisheries Malaysia. [Accessed November 12, 2020] https://www.dof.gov.my/index.php/pages/view/78
 
@@
 Source: 
-National Aquaculture Sector Overview. Sri Lanka, 2005. , National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
+National Aquaculture Sector Overview. Sri Lanka, 2005. National Aquaculture Sector Overview Fact Sheets. Food and Agriculture Organization of the United Nations.
 

### 2021-03-23 marine_mapping_archive_v1/tuna/food_pressures/tuna_disturbance/tuna_disturbance.Rmd
Finished reorganizing data

---
title: "Tuna disturbance"
author: "Gage Clawson (NCEAS, OHI, UCSB)"
date: "12/29/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in libaries and paths}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(raster)
library(data.table)
library(raster)
library(rgdal)
library(here)

path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/"

food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

Because the pacific, atlantic, and southern blue fin tuna are so similar, we will treat them the same in this analysis (i.e. same average weight, stocking density, cage volume, etc.). Although Croatia and Japan rear their tuna for 1 - 3 years, the rest of the countries only rear for 2 - 10 months. Because of this, we will make the assumption that tuna are only farmed for 1 year, and there is minimal loss. Meaning that the production reported from the FAO is the true live weight tonnes in each cage.

Assumptions: **make sure to both cite in the SI methods, already in Zotero**

stocking density = 2 - 5 kg/m3 (from http://www.fao.org/3/a1290e/a1290e04.pdf): We will assume 3 kg/m3

diameter = 50 - 120 m (from http://www.fao.org/fishery/culturedspecies/Thunnus_thynnus/en)

depth = 25 - 35 m (from http://www.fao.org/fishery/culturedspecies/Thunnus_thynnus/en)

To get the cage volume we will take the midpoint of diameter/2 and depth

radius = 85/2 = 42.5 m
depth = 30 m

volume = pi*42.5*42.5*30 = 170235.1 m3

## Method

Establish the necessary parameters from above
```{r parameters}
# harvest_weight = 38.98

stocking_density = 3
cage_depth = 30
radius = 42.5

cage_volume = pi*radius**2*cage_depth

```

###Calculate the total number of fish in the water (occupancy)
Read in production map

```{r}
production_raster <- rasterFromXYZ(read_csv(paste0(path_prep, "tuna_farm.csv")), crs = food_crs)

#plot(production_raster)
cellStats(production_raster, stat = "sum") # 37072.56

```

```{r calculate tuna occupancy}
# Assume all kg are live weight 
# as live weight of tuna, in kg
tuna_live_kg  <- production_raster*1000
tuna_live_tonnes  <- production_raster

writeRaster(tuna_live_tonnes, file.path(path_prep, "tuna_occupancy/tuna_live_tonnes.tif"), format = "GTiff", overwrite = TRUE)
```

### Calculate the total area (from an aerial view) used for tuna aquaculture

First we determine how many cages are required given cage dimensions, stocking densities, and kg living fish.

We used FAO data to estimate ~510705 kg tuna (harvest weight) per cage.

This is based on ~170000 m3 cage that we assume to be circular with a depth of 30 m.  We assume a stocking density of 3 kg/m3.

```{r}

kg_per_cage <- cage_volume*stocking_density

```

Given the kg of tuna per cell we determine the number of cages needed as:

kg_tuna/510705

```{r}

cages <- ceiling(tuna_live_kg/kg_per_cage)

```

2. We the determine how much surface area the cages disturb including the inner cage area, a 5 meter buffer around the cage, and area for infrastructure.

```{r}
buffer <- 5
infrastructure <- 1.5 #50% of area to infrastructure

cage_area <- cage_volume/cage_depth
cage_radius <- sqrt(cage_area/pi)
cage_radius_buffer <- cage_radius + buffer
cage_area_with_buffer <- pi*cage_radius_buffer^2
cage_disturbance_m2 <- cage_area_with_buffer*infrastructure

total_disturbance_km2 <- cages * cage_disturbance_m2/1000000
total_disturbance_prop <- total_disturbance_km2/raster::area(total_disturbance_km2)
plot(total_disturbance_prop)

tuna_aquaculture_area_df <- as.data.frame(total_disturbance_prop, xy=TRUE) %>% 
  dplyr::rename(tuna_disturbance_prop = layer )

write_csv(tuna_aquaculture_area_df, file.path(path_prep, "tuna_disturbance_prop.csv"))

tuna_aquaculture_area_df_km2 <- as.data.frame(total_disturbance_km2, xy = TRUE) %>%
  dplyr::rename(tuna_disturbance_km2 = layer)

write_csv(tuna_aquaculture_area_df_km2, file.path(path_prep, "tuna_disturbance_km2.csv"))

## save to datalayers folder with the correct naming conventions: 
final_layer_dist <- read_csv(file.path(path_prep, "tuna_disturbance_km2.csv"))

final_rast <- rasterFromXYZ(final_layer_dist, crs = food_crs)
crs(final_rast)
plot(final_rast)
cellStats(final_rast, "sum") # 1.55232
final_rast

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 1.55232
final_rast

writeRaster(final_rast, file.path(path_final, "marine_tuna_aquaculture_meat_disturbance.tif"), overwrite = TRUE)
```

### 2021-04-01 marine/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
finished a little datachecking for the methods

--- 2021-03-23 marine_mapping_archive_v1/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
@@
   arrange(-value, country) %>%
+  # group_by(country, year) %>%
+  # summarise(value = sum(value)) %>%
   filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
@@
   arrange(country, iso3c, species, year)
+
+sum(fao_bivalve_taxa_prod$fao_tonnes_production) # 17435623
+unique(fao_bivalve_taxa_prod$country) # 42 countries
+
+## When doing the filter for >500 tonnes by taxa group: 
+# sum(fao_bivalve_taxa_prod$value) # 17446096
+# unique(fao_bivalve_taxa_prod$country) # 43 countries - senegal added
 

### 2021-04-01 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished a little datachecking for the methods

@@
 We currently know the exact location of 1 bivalve farms in Australia, however there is much more production that just 1 farm.
-However, aquaculture websites say there are 20 abalone farms, 14 oyster farms, and 25 mussel farms in Australia
+However, aquaculture websites say there are 20 abalone farms, 22 oyster farms, and 25 mussel farms in Australia
 
@@
  - Abalone
-  - https://www.oceanwatch.org.au/seafood/aquaculture/species/abalone/
+  - https://www.oceanwatch.org.au/aquaculture-species/
   - “There are around 20 farms that produce about 725 tonnes of abalone every year, with production volume increasing by about 25% every year.”
@@
   - https://www.aquaculturealliance.org/advocate/oyster-farming-in-south-australia/
-  - We will use this as truth: http://www.oysterssa.com.au/south-australian-oyster-growers
-  - We will need to place an additional 14 oyster farms in Australia
+  - We will use this as truth: https://oysterssa.com.au/oyster-growers/
+  - We will need to place an additional 22 oyster farms in Australia
 
  - Mussels
-  - https://www.oceanwatch.org.au/seafood/aquaculture/species/mussels/
+  - https://www.oceanwatch.org.au/aquaculture-species/
   - “Concentrated in the south of country, there are about 25 mussel farms spread across SA, Tasmania, Victoria, Tasmania and the south coasts of both NSW and WA.”
@@
 # Jersey
-Current data is from ASC, only 5 farm. However, this is comprehensive. When comparing to governmental lease data, there are only 7 leases in Jersey.
+Current data is from ASC, only 5 farm. However, this is comprehensive. When comparing to governmental lease data, there are 5 leases in Jersey.
 

### 2021-04-01 marine/marine_fish_general/finfish_farms/STEP1_fao_finfish_production.Rmd
finished a little datachecking for the methods

@@
 
+sum(explore$fao_tonnes_production) # 3901214
+unique(explore$country) # 37 countries
+
+## explore ASC and emod data
+
 emod_countries <- explore %>%
@@
 ```
+
+```{r}
+## write out bivalve taxa and production for Juliette
+fao_finfish_taxa_prod <- fao %>%
+  filter(species %in% finfish_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_finfish_taxa_prod$value) # 3916717
+
+unique(fao_finfish_taxa_prod$country) # 37 countries 
+```

### 2021-04-01 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
finished a little datachecking for the methods

@@
 
-sum(explore$fao_tonnes_production)
+sum(explore$fao_tonnes_production) # 5094133
+unique(explore$country) # 35 countries
+
+## explore ASC data
 
@@
 ```
+
+```{r}
+## write out bivalve taxa and production for Juliette
+fao_shrimp_taxa_prod <- fao %>%
+  filter(species %in% shrimp_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_shrimp_taxa_prod$value) # 5095394 - adds ~1000 tonnes
+
+unique(fao_shrimp_taxa_prod$country) # 35 countries 
+```

### 2021-04-01 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
finished a little datachecking for the methods

@@
 
-write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))
+75+write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))
 
@@
 
-From FAO:
-For marine aquaculture, the six shrimp breeding companies created 4 325 full-time jobs, 4 267 of which were for local people and 58 for expatriates (Anon.
+From FAO: http://www.fao.org/fishery/countrysector/naso_madagascar/en
+
+"For marine aquaculture, the **six shrimp breeding companies** created 4 325 full-time jobs, 4 267 of which were for local people and 58 for expatriates (Anon.
 2005b).
@@
 This kind of shrimp farming also created 30 000 indirect jobs.
-Seaweed culture was being practised by 126 farmers.
+Seaweed culture was being practised by 126 farmers."
 
@@
 
- - Because this source doesn't hav especifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.
+ - Because this source doesn't have specifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.
 

### 2021-04-01 marine/tuna/tuna_farms/STEP1_fao_tuna_production.Rmd
finished a little datachecking for the methods

---
title: "FAO marine tuna production"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/11/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

All data is ultimately adjusted to FAO production data.  This script cleans the fao mariculture data and subsets it to to the relevant years of data and species (tuna).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(data.table)
library(countrycode)
library(here)
library(stringr)

path <- "/home/shares/food-systems/Food_footprint/_raw_data"
source(here('marine/salmon/salmon_farm/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files
source(here('workflow/common.R'))

```

Subset the data to include only the species (tuna) and countries we are interested in. Then summarize by total tonnes of tuna per country/year. (There are multiple tuna species)

```{r}

fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for tuna
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

# the list of species we are including
tuna_list <- species_list$species[species_list$aq_group=="tuna"]
tuna_list

## write out tuna taxa and production for Juliette
fao_tuna_taxa_prod <- fao %>%
  filter(species %in% tuna_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, species, year) %>%
  dplyr::filter(year == 2017) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, species, year)

write.csv(fao_tuna_taxa_prod, here("marine/tuna/tuna_farms/data/fao_mariculture_tuna_taxa_production.csv"), row.names=FALSE)

# include only tuna
fao_tuna <- fao %>%
  filter(species %in% tuna_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
  group_by(country, iso3c, year) %>%
  summarize(fao_tonnes_production = sum(value)) %>%
  arrange(country, iso3c, year)

write.csv(fao_tuna, here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv"), row.names=FALSE)

 explore <- read_csv(here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
   filter(year==2017) %>%
   arrange(-fao_tonnes_production) %>%
   mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100, 2))
 sum(explore$fao_tonnes_production) # 37072.56
 unique(explore$country) # 7 countries 
```

```{r}
## write out bivalve taxa and production for Juliette
fao_tuna_taxa_prod <- fao %>%
  filter(species %in% tuna_list) %>%  
  filter(!is.na(value)) %>%
  arrange(-value, country) %>%
  group_by(country, year) %>%
  summarise(value = sum(value)) %>%
  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
  filter(year == 2017)

sum(fao_tuna_taxa_prod$value) # 37072.56

unique(fao_tuna_taxa_prod$country) # 16 countries 
```

### 2021-04-02 workflow/predict_farm_numbers.Rmd
finalized loop

@@
 
-aq_info <- read_csv('/home/shares/clean-seafood/raw_data/FAO/production/CL_FI_COUNTRY_GROUPS.csv') %>% 
-  clean_names() %>% 
+continent_info <- read_csv('data/CL_FI_COUNTRY_GROUPS.csv') %>% 
+  janitor::clean_names() %>% 
   select(iso3_code, geo_region_group, continent_group, eco_class_group)
@@
 
-aq_types <- raw %>% 
-  filter(!is.na(n_farms)) %>% 
-  mutate(tonnes_per_farm = fao_tonnes_production/n_farms) %>% 
-  group_by(continent_group, group) %>% 
-  summarise(tonnes_per_farm = mean(tonnes_per_farm))
 ```

### 2021-04-02 workflow/place_unknown_farms.R

@@ -1,0 +1,186 @@
+#### load libraries and data ####
+#------------------------------------------------------------------------------#
+library(sf)
+library(spatialEco)
+library(tidyverse)
+library(raster)
+library(rgeos)
+library(rmapshaper)
+library(mapview)
+
+# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
+source("./_spatial/template_raster.R")
+gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
+gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
+land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
+eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
+eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
+coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
+
+
+blank_raster <- food_raster
+blank_raster[] <- 1
+
+the_crs <- crs(fake_raster, asText = TRUE)
+
+ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
+  st_transform(the_crs)
+
+
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant") 
+
+tonnage_per_farms <- read_csv("marine/output/all_points_to_add.csv") %>% 
+  distinct(type, avg_tonnes_per_farm)
+
+need_national_allocation <- read_csv("marine/output/all_points_to_add.csv") %>% 
+  group_by(iso3c, type) %>% 
+  summarize(num_farms = sum(num_additional_farms))
+
+all_the_farm_points <- data %>% 
+  dplyr::select(iso3c, type) %>%
+  .[0, ]
+
+
+for (i in 3:length(unique(need_national_allocation$iso3c))) {
+  
+  ## 1.a get country shape file
[…]

### 2021-04-02 workflow/qualtiy_control_filters.R

@@ -23,49 +23,97 @@ eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquacultu
 eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
 coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
 
+#x <- raster("/home/shares/food-systems/Aquaculture_mapping/Data/ports/distance-from-port-v20201104.tiff")
+
+#plot(x)
+# ports_gfw <- read_csv("/home/shares/food-systems/Aquaculture_mapping/Data/ports/named_anchorages_v2_20201104.csv") %>% 
+#   st_as_sf(coords = c("lon", "lat"),
+#            crs = 4326) %>% 
+#   head(400)
+
+#mapview::mapview(ports_gfw, zcol = "at_dock")
+
 the_crs <- crs(fake_raster, asText = TRUE)
 # depth and ports
 ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
   st_transform(the_crs)
-bathy_raw <- raster("/home/shares/clean-seafood/raw_data/bathymetry_data/full_bathy_layer.tif") %>%
-  resample(fake_raster, method = 'bilinear')
-  #projectRaster(to = fake_raster,
-                #res = res(fake_raster))
 
-bathy_raw <- bathy_raw %>% 
-  projectRaster(to = fake_raster)
-
-#bathy_raw2 <- bathy_raw
-#bathy_raw <- bathy_raw2
-bathy_raw[bathy_raw >    10] <- NA # replace all values over 1m asl as NA
-bathy_raw[bathy_raw < -250] <- NA # replace all values under 250 bsl as NA
-bathy_raw[!is.na(bathy_raw)] <- 1 # replace all suitable depths with 1
+#all_ports_sp <- as(ports_raw, "Spatial")
+#dist_ports_raster <- distanceFromPoints(food_raster, all_ports_sp)
+#write_rds(dist_ports_raster, "dist_ports_raster.rds")
 
 
-# load in each of the aquaculture maps and convert to sf objects
-all_farms_raw   <-
-  bind_rows(read_csv("marine/bivalve/bivalve_farms/data/global_bivalve_farm_lat_lon_data_quality.csv") %>% 
-              mutate(type = "bivalve") %>% 
-              dplyr::select(-X1),
[…]

### 2021-04-02 workflow/small_split.R

@@ -1,0 +1,129 @@
+#### load libraries and data ####
+#------------------------------------------------------------------------------#
+library(sf)
+library(spatialEco)
+library(tidyverse)
+library(raster)
+library(rgeos)
+
+# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
+source("./_spatial/template_raster.R")
+gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
+gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
+land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
+eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
+eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
+coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
+
+
+the_crs <- crs(fake_raster, asText = TRUE)
+
+ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
+  st_transform(the_crs)
+
+
+
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant") 
+
+need_national_allocation <- read_csv("marine/output/all_points_to_add.csv") %>% 
+  group_by(iso3c, type) %>% 
+  summarize(num_farms = sum(num_additional_farms))
+
+all_the_farm_points <- data %>% 
+  dplyr::select(iso3c, type) %>%
+  .[0, ]
+
+
+#4326
+# use     #st_transform(crs = "+proj=moll") %>%  for buffering in meters
+
+for (i in 1:length(unique(need_national_allocation$iso3c))) {
+
+  this_iso3 <- unique(need_national_allocation$iso3c)[i]
+  
+  this_country <- gadm_full %>% 
+    filter(GID_0 == this_iso3) %>% 
+    group_by(GID_0) %>% 
[…]

### 2021-04-05 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
equally allocated FAO production per species group to all of our points (modelled and known)

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this script we allocated the production per farm (equally if there is no subregional production estimates).

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

data <- read_csv("marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

bivalve_farms <- all_farms %>%
  filter(type == "bivalve")

```

# determine subregions where points are located

```{r}

bivalve_farms$reg_id <- raster::extract(gadm_latlon, bivalve_farms)

farms_sf <- bivalve_farms %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

CHN:HKG
CHN:MAC
ESP:MAR
ESP:PRT
HKG:CHN
HRV:BIH
HRV:MNE
HRV:SVN
IDN:PNG
IRL:GBR
JPN:RUS
KHM:VNM
MEX:USA
MYS:BRN
MYS:THA
NLD:BEL
NLD:DEU
PRK:RUS
PRT:ESP
SVN:ITA
THA:MMR
THA:MYS
TWN:CHN
USA:CAN
USA:MEX
VNM:KHM

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:MAR", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:MAR", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ESP:FRA", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:FRA", "Spain", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:BIH", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:BIH", "Croatia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HRV:MNE", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:MNE", "Croatia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HRV:SVN", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "JPN:RUS", "JPN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "JPN:RUS", "Japan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:BEL", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:BEL", "Netherlands", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRK:RUS", "PRK", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:ITA", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:ITA", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:MEX", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:MEX", "United States", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```

# FAO salmon production data per country
```{r}

fao <- read.csv(here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# combine and check it all matches ok

```{r}

test <- farms_prod %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farms_prod)
mapview(farms_sf)

bivalve_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
mapview(bivalve_raster_check)

bivalve_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(bivalve_raster + 1))

bivalve_raster_df <- as.data.frame(bivalve_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(bivalve_raster, stat = "sum") # 17435623
sum(bivalve_raster_df$tonnes_production) # 17435623
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17435623
sum(fao$fao_tonnes_production) # 17435623

write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/bivalve_farm_updated.csv")

```

### 2021-04-05 marine/crustaceans/crustacean_farms/STEP4_rasterize_production.Rmd
equally allocated FAO production per species group to all of our points (modelled and known)

--- 2021-03-23 marine_mapping_archive_v1/crustaceans/crustacean_farms/STEP3_rasterize_production.Rmd
@@
 
-farms <- read.csv(here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"))
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
-farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
+all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
+  map_df(., readRDS) %>% 
+  rename(iso3c = iso3) %>% 
+  mutate(source = "modeled") %>% 
+  #left_join(tonnage_per_farms)
+  rbind(data %>% mutate(source = "real"))
 
-mapview(farms_sf)
+crust_farms <- all_farms %>%
+  filter(type == "crustaceans")
 ```
@@
 
-farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)
+crust_farms$reg_id <- raster::extract(gadm_latlon, crust_farms)
 
-farms_sf <- farms_sf %>%
+farms_sf <- crust_farms %>%
   left_join(gadm_codes, by="reg_id") %>%
@@
 table(farms_sf$check)
+
+unique(farms_sf$iso3c)
+
+# some annoying mismatches due to raster resolution. Fix these
+
+unique(farms_sf$NAME_1)
+
+farms_sf_correct <- farms_sf %>%
+  mutate(GID_0 = as.character(GID_0)) %>%
+  mutate(NAME_0 = as.character(NAME_0)) %>%
+  mutate(NAME_1 = as.character(NAME_1)) %>%
+  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "MMR:THA", "MMR", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))
+
+farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
+table(farms_sf_correct$check)
 
@@
 
-setdiff(fao$iso3c, farms_sf$iso3c)
-setdiff(farms_sf$iso3c, fao$iso3c)
+setdiff(fao$iso3c, farms_sf_correct$iso3c)
+setdiff(farms_sf_correct$iso3c, fao$iso3c)
 
@@
 
-farms_sf_correct <- farms_sf %>%
+farms_sf_correct <- farms_sf_correct %>%
   left_join(fao, by="iso3c")
@@
 
-```
-
-# get areas with regional production data and calculate production per farm
-```{r}
-
-## Vietnam and Philippines have regional production
-farms_rgn_prod <- farms_sf_correct %>%
-  dplyr::filter(!is.na(prod))
-
-## calculate farm production
-farms_rgn_prod <- farms_rgn_prod %>%
-  group_by(iso3c) %>%
-  mutate(prop_production = prod/sum(prod)) %>%
-  mutate(regional_prod = fao_tonnes_production*prop_production) %>%
-  group_by(iso3c, sub_rgn) %>%
-  add_tally() %>%
-  ungroup() %>%
-  mutate(tonnes_per_farm = regional_prod/n) %>%
-  dplyr::select(iso3c, tonnes_per_farm, geometry)
-
-## Check to make sure the totals match
-test <- farms_rgn_prod %>%
-  dplyr::filter(iso3c == "VNM")
-
-sum(test$tonnes_per_farm)
 ```
@@
   mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
-  dplyr::select(iso3c, tonnes_per_farm, geometry) %>%
-  dplyr::filter(!(iso3c %in% c("VNM", "PHL"))) ## filter out VNM and PHL since we have regional production estimates for those countries
+  dplyr::select(iso3c, tonnes_per_farm, geometry)
 
@@
 
-farm_production <- rbind(farms_prod, farms_rgn_prod)
-
-test <- farm_production %>%
+test <- farms_prod %>%
   dplyr::group_by(iso3c) %>%
@@
 
-farms_sf <- st_as_sf(farm_production)
+farms_sf <- st_as_sf(farms_prod)
 mapview(farms_sf)
@@
 
-write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/crustaceans_farm.csv")
+write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/crustaceans_farm_updated.csv")
 

### 2021-04-05 marine/marine_fish_general/finfish_farms/STEP4_rasterize_production.Rmd
equally allocated FAO production per species group to all of our points (modelled and known)

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this script we allocated the production per farm (equally if there is no subregional production estimates).

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

data <- read_csv("marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

finfish_farms <- all_farms %>%
  filter(type == "marine_fish_general")

```

# determine subregions where points are located

```{r}

finfish_farms$reg_id <- raster::extract(gadm_latlon, finfish_farms)

farms_sf <- finfish_farms %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

# ALB:MNE
# CHN:HKG
# CHN:MAC
# CYP:XAD
# EGY:ISR
# ESP:PRT
# GRC:ALB
# GRC:TUR
# HKG:CHN
# HRV:SVN
# IDN:PNG
# IDN:TLS
# ISR:EGY
# ITA:FRA
# MYS:SGP
# MYS:THA
# PRT:ESP
# SGP:MYS
# TUR:BGR
# TUR:GRC
# TWN:CHN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "ALB:MNE", "ALB", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ALB:MNE", "Albania", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "EGY:ISR", "EGY", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "EGY:ISR", "Egypt", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "HRV:SVN", "HRV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "ISR:EGY", "ISR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ISR:EGY", "Israel", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ITA:FRA", "ITA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ITA:FRA", "Italy", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TUR:BGR", "TUR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TUR:BGR", "Turkey", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TUR:GRC", "TUR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```

# FAO salmon production data per country
```{r}

fao <- read.csv(here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# combine and check it all matches ok

```{r}

test <- farms_prod %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farms_prod)
mapview(farms_sf)

finfish_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
mapview(finfish_raster_check)

finfish_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(finfish_raster + 1))

finfish_raster_df <- as.data.frame(finfish_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(finfish_raster, stat = "sum") # 3901214
sum(finfish_raster_df$tonnes_production) # 3901214
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3901214
sum(fao$fao_tonnes_production) #3901214

write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/marine_fish_general_farm_updated.csv")

```

### 2021-04-05 marine/salmon/salmon_farm/STEP4_rasterize_production.Rmd
equally allocated FAO production per species group to all of our points (modelled and known)

--- 2021-03-23 marine_mapping_archive_v1/salmon/salmon_farm/STEP4_rasterize_production.Rmd
@@
 
-farms <- read.csv(here("aquaculture/marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"))
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
-farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
+all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
+  map_df(., readRDS) %>% 
+  rename(iso3c = iso3) %>% 
+  mutate(source = "modeled") %>% 
+  #left_join(tonnage_per_farms)
+  rbind(data %>% mutate(source = "real"))
+
+salmon_farms <- all_farms %>%
+  filter(type == "salmon")
 
@@
 
-farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)
+salmon_farms$reg_id <- raster::extract(gadm_latlon, salmon_farms)
 
-farms_sf <- farms_sf %>%
+farms_sf <- salmon_farms %>%
   left_join(gadm_codes, by="reg_id") %>%
-    dplyr::mutate(subregion = as.character(subregion)) %>%
-  dplyr::mutate(NAME_1 = as.character(NAME_1)) %>%
-  dplyr::mutate(NAME_1 = ifelse(is.na(subregion), NAME_1, subregion))
+  dplyr::mutate(NAME_1 = as.character(NAME_1))
 
@@
 table(farms_sf$check)
-mapview(filter(farms_sf, check=="CAN:USA"))
-mapview(filter(farms_sf, check=="USA:CAN"))
-mapview(filter(farms_sf, check =="SWE:SWE"))
-mapview(filter(farms_sf, check == "FIN:ALA"))
-mapview(filter(farms_sf, check == "FIN:RUS"))
 
@@
 # some annoying mismatches due to raster resolution. Fix these
-
-unique(farms_sf$NAME_1)
 
@@
 
-# get areas with regional production data and calculate production per farm
-```{r}
-
-rgn_prod <- read_csv(here("marine/salmon/salmon_farm/data/proportional_regional_production.csv")) %>%
-  dplyr::select(iso3c, NAME_1 = region, prop_production)
-
-rgn_prod_country <- unique(rgn_prod$iso3c)
-
-farms_rgn_prod <- farms_sf_correct %>%
-  dplyr::filter(GID_0 %in% rgn_prod_country)
-
-# make sure region names match
-no_match <- setdiff(rgn_prod$NAME_1, farms_rgn_prod$NAME_1)
-no_match
-
-setdiff(farms_rgn_prod$NAME_1, rgn_prod$NAME_1)
-
-#this is ok: little or no production in these regions
-test <- filter(rgn_prod, NAME_1 %in% no_match)
-
-## calculate farm production
-farms_rgn_prod <- farms_rgn_prod %>%
-  left_join(rgn_prod) %>%
-  mutate(regional_prod = fao_tonnes_production*prop_production) %>%
-  group_by(NAME_1) %>%
-  add_tally() %>%
-  ungroup() %>%
-  mutate(tonnes_per_farm = regional_prod/n) %>%
-  dplyr::select(iso3c, tonnes_per_farm, geometry)
-
-test <- farms_rgn_prod %>%
-  dplyr::filter(iso3c == "NOR")
-
-sum(test$tonnes_per_farm) # 1299663
-
-test2 <- fao %>%
-  dplyr::filter(iso3c == "NOR")
-
-sum(test2$fao_tonnes_production) # 1303255
-```
-
 # get areas with no regional production data and calculate production per farm
@@
 
-rgn_prod <- read_csv(here("marine/salmon/salmon_farm/data/proportional_regional_production.csv")) %>%
-  dplyr::select(iso3c, NAME_1 = region, prop_production)
-rgn_prod_country <- unique(rgn_prod$iso3c)
-
+## calculate farm production
 farms_prod <- farms_sf_correct %>%
-  dplyr::filter(!(GID_0 %in% rgn_prod_country))
-
-## calculate farm production
-farms_prod <- farms_prod %>%
   group_by(NAME_0) %>%
@@
 
-farm_production <- rbind(farms_prod, farms_rgn_prod)
-
-test <- farm_production %>%
+test <- farms_prod %>%
   group_by(iso3c) %>%
@@
 
-cellStats(salmon_raster, stat = "sum") # 2746086
-sum(salmon_raster_df$tonnes_production) # 2746086
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2746086
+cellStats(salmon_raster, stat = "sum") # 2753752
+sum(salmon_raster_df$tonnes_production) # 2753752
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2753752
 sum(fao$fao_tonnes_production) #2753752
 
-write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm.csv")
+write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm_updated.csv")
 

### 2021-04-05 marine/shrimp/shrimp_farms/STEP4_rasterize_production.Rmd
equally allocated FAO production per species group to all of our points (modelled and known)

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this script we allocated the production per farm (equally if there is no subregional production estimates).

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

data <- read_csv("marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  rbind(data %>% mutate(source = "real"))

shrimp_farms <- all_farms %>%
  filter(type == "shrimp")

```

# determine subregions where points are located

```{r}

shrimp_farms$reg_id <- raster::extract(gadm_latlon, shrimp_farms)

farms_sf <- shrimp_farms %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

# CHN:HKG
# CHN:MAC
# CRI:NIC
# CRI:PAN
# ECU:COL
# GTM:HND
# GTM:MEX
# HND:NIC
# HND:SLV
# IDN:PNG
# IDN:TLS
# IRN:IRQ
# MEX:GTM
# MEX:USA
# MYS:BRN
# MYS:SGP
# MYS:THA
# PER:ECU
# SAU:KWT
# SLV:HND
# THA:MMR
# THA:MYS
# VNM:KHM

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:NIC", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:NIC", "Costa Rica", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "ECU:COL", "ECU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ECU:COL", "Ecuador", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:HND", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:HND", "Guatemala", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GTM:MEX", "GTM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GTM:MEX", "Guatemala", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "MEX:GTM", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:GTM", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "PER:ECU", "PER", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PER:ECU", "Peru", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SLV:HND", "SLV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SLV:HND", "El Salvador", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```

# FAO salmon production data per country
```{r}

fao <- read.csv(here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# combine and check it all matches ok

```{r}

test <- farms_prod %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farms_prod)
mapview(farms_sf)

shrimp_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
mapview(shrimp_raster_check)

shrimp_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(shrimp_raster + 1))

shrimp_raster_df <- as.data.frame(shrimp_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(shrimp_raster, stat = "sum") # 5094133
sum(shrimp_raster_df$tonnes_production) # 5094133
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5094133
sum(fao$fao_tonnes_production) # 5094133

write_csv(shrimp_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/shrimp_farm_updated.csv")

```

### 2021-04-05 marine/tuna/tuna_farms/STEP4_rasterize_production.Rmd
equally allocated FAO production per species group to all of our points (modelled and known)

--- 2021-04-05 marine/salmon/salmon_farm/STEP4_rasterize_production.Rmd
@@
 title: "Rasterizing prodution per each region"
-author: "Gage Clawson (UCSB, NCEAS, OHI)"
-date: "10/09/2020"
+author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/14/2020"
 output: html_document
@@
 ---
-
-In this script we allocated the production per farm (equally if there is no subregional production estimates).
 
@@
 
-source(here("_spatial/template_raster.R"))
+source(here::here("_spatial/template_raster.R"))
+source(here::here('workflow/common.R'))
 
@@
 
-salmon_farms <- all_farms %>%
-  filter(type == "salmon")
+tuna_farms <- all_farms %>%
+  dplyr::filter(type == "tuna")
 
+mapview(tuna_farms)
 ```
@@
 
-salmon_farms$reg_id <- raster::extract(gadm_latlon, salmon_farms)
+tuna_farms$reg_id <- raster::extract(gadm_latlon, tuna_farms)
 
-farms_sf <- salmon_farms %>%
+farms_sf <- tuna_farms %>%
   left_join(gadm_codes, by="reg_id") %>%
@@
 
-mapview(filter(farms_sf, check == "RUS:RUS"))
-mapview(farms_sf)
-# some annoying mismatches due to raster resolution. Fix these
-
-farms_sf_correct <- farms_sf %>%
-  mutate(GID_0 = as.character(GID_0)) %>%
-  mutate(NAME_0 = as.character(NAME_0)) %>%
-  mutate(NAME_1 = as.character(NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% "CAN:USA", "CAN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CAN:USA", "Canada", NAME_0)) %>%
-  mutate(NAME_1 = ifelse(check %in% "CAN:USA", "New Brunswick", NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
-  mutate(NAME_1 = ifelse(check %in% "USA:CAN", "Maine", NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% "FIN:ALA", "FIN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "FIN:ALA", "Finland", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))
-
-farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
-table(farms_sf_correct$check)
-
-mapview(farms_sf_correct) # this all looks reasonable, no crazy points
+## no mismatches
 ```
 
-# FAO salmon production data per country
+# FAO tuna production data per country
 ```{r}
 
-fao <- read.csv(here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
+fao <- read.csv(here::here("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv")) %>%
   dplyr::filter(year == 2017) %>%
   dplyr::select(iso3c, fao_tonnes_production)
+
+setdiff(fao$iso3c, farms_sf$iso3c)
+setdiff(farms_sf$iso3c, fao$iso3c)
 
@@
 
-test <- farms_prod %>%
-  group_by(iso3c) %>%
-  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
-  left_join(fao) %>%
+farm_production <- farms_prod
+
+test <- farm_production %>%
+  dplyr::group_by(iso3c) %>%
+  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
+  left_join(fao, by = "iso3c") %>%
   mutate(difference = fao_tonnes_production - total_tonnes)
+
+farms_sf_prod <- st_as_sf(farm_production)
+mapview(farms_sf_prod)
+
+## write the production data so that we can use it for the nutrient layer. 
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/prod_data_by_cell_iso3c.shp")
 
@@
 
-farms_sf <- st_as_sf(farms_prod)
+farms_sf <- st_as_sf(farm_production)
 mapview(farms_sf)
 
-salmon_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
-mapview(salmon_raster_check)
+sum(farms_sf$tonnes_per_farm) # 37072.56
 
-salmon_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
-plot(log(salmon_raster + 1))
+tuna_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
+plot(log(tuna_raster_check+1))
+cellStats(tuna_raster_check, stat = "sum", na.rm = TRUE) # 37072.56
 
-salmon_raster_df <- as.data.frame(salmon_raster, xy=TRUE) %>%
+mapview(tuna_raster_check)
+
+tuna_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
+mapview(log(tuna_raster+1))
+
+plot(log(tuna_raster+1))
+
+tuna_raster_df <- as.data.frame(tuna_raster, xy=TRUE) %>%
   dplyr::select(x,y, tonnes_production=layer)
 
-cellStats(salmon_raster, stat = "sum") # 2753752
-sum(salmon_raster_df$tonnes_production) # 2753752
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2753752
-sum(fao$fao_tonnes_production) #2753752
+cellStats(tuna_raster, stat = "sum") # 37072.56
+sum(tuna_raster_df$tonnes_production) # 37072.56
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 37072.56
+sum(fao$fao_tonnes_production) # 37072.56
 
-write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm_updated.csv")
+write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm_updated.csv")
 

### 2021-04-06 data_check/farms_data_check.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

--- 2021-04-05 marine/shrimp/shrimp_farms/STEP4_rasterize_production.Rmd
@@
 ---
-title: "Rasterizing prodution per each region"
+title: "Data checking"
 author: "Gage Clawson (UCSB, NCEAS, OHI)"
-date: "10/09/2020"
+date: "03/06/2021"
 output: html_document
@@
 source(here("_spatial/template_raster.R"))
+
+path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"
 
@@
 
-shrimp_farms <- all_farms %>%
-  filter(type == "shrimp")
+by_type <- all_farms %>%
+  group_by(type) %>%
+  summarise(n()) %>%
+  st_drop_geometry()
+
+by_country_type <- all_farms %>%
+  st_drop_geometry() %>%
+  group_by(iso3c, type) %>%
+  summarise(n())
 
 ```
-
-# determine subregions where points are located
-
-```{r}
-
-shrimp_farms$reg_id <- raster::extract(gadm_latlon, shrimp_farms)
-
-farms_sf <- shrimp_farms %>%
-  left_join(gadm_codes, by="reg_id") %>%
-  dplyr::mutate(NAME_1 = as.character(NAME_1))
-
-farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
-table(farms_sf$check)
-
-mapview(farms_sf)
-# some annoying mismatches due to raster resolution. Fix these
-
-# CHN:HKG
-# CHN:MAC
-# CRI:NIC
-# CRI:PAN
-# ECU:COL
-# GTM:HND
-# GTM:MEX
-# HND:NIC
-# HND:SLV
-# IDN:PNG
-# IDN:TLS
-# IRN:IRQ
-# MEX:GTM
-# MEX:USA
-# MYS:BRN
-# MYS:SGP
-# MYS:THA
-# PER:ECU
-# SAU:KWT
-# SLV:HND
-# THA:MMR
-# THA:MYS
-# VNM:KHM
-
-farms_sf_correct <- farms_sf %>%
-  mutate(GID_0 = as.character(GID_0)) %>%
-  mutate(NAME_0 = as.character(NAME_0)) %>%
-  mutate(NAME_1 = as.character(NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "CRI:NIC", "CRI", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CRI:NIC", "Costa Rica", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "ECU:COL", "ECU", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ECU:COL", "Ecuador", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "GTM:HND", "GTM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "GTM:HND", "Guatemala", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "GTM:MEX", "GTM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "GTM:MEX", "Guatemala", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "MEX:GTM", "MEX", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MEX:GTM", "Mexico", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "PER:ECU", "PER", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "PER:ECU", "Peru", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "SLV:HND", "SLV", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "SLV:HND", "El Salvador", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))
-
-farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
-table(farms_sf_correct$check)
-
-mapview(farms_sf_correct) # this all looks reasonable, no crazy points
-```
-
-# FAO salmon production data per country
-```{r}
-
-fao <- read.csv(here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
-  dplyr::filter(year == 2017) %>%
-  dplyr::select(iso3c, fao_tonnes_production)
-
-```
-
-# join country production to farms by iso3c
-
-```{r}
-
-farms_sf_correct <- farms_sf_correct %>%
-  left_join(fao, by="iso3c")
-
-summary(farms_sf_correct) # make sure no production NA values
-
-```
-
-# get areas with no regional production data and calculate production per farm
-
-```{r}
-
-## calculate farm production
-farms_prod <- farms_sf_correct %>%
-  group_by(NAME_0) %>%
-  add_tally() %>%
-  ungroup() %>%
-  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
-  dplyr::select(iso3c, tonnes_per_farm, geometry)
-
-```
-
-# combine and check it all matches ok
-
-```{r}
-
-test <- farms_prod %>%
-  group_by(iso3c) %>%
-  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
-  left_join(fao) %>%
-  mutate(difference = fao_tonnes_production - total_tonnes)
-
-```
-
-## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.
-
-```{r}
-
-farms_sf <- st_as_sf(farms_prod)
-mapview(farms_sf)
-
-shrimp_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
-mapview(shrimp_raster_check)
-
-shrimp_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
-plot(log(shrimp_raster + 1))
-
-shrimp_raster_df <- as.data.frame(shrimp_raster, xy=TRUE) %>%
-  dplyr::select(x,y, tonnes_production=layer)
-
-cellStats(shrimp_raster, stat = "sum") # 5094133
-sum(shrimp_raster_df$tonnes_production) # 5094133
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5094133
-sum(fao$fao_tonnes_production) # 5094133
-
-write_csv(shrimp_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/shrimp_farm_updated.csv")
-
-```

### 2021-04-06 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

@@
 
-Need to add 68 points to existing 1 point (for a total of 69 points)
+Need to add 45 points to existing 24 point (for a total of 69 points)
 
@@
   - We will use this as truth: https://oysterssa.com.au/oyster-growers/
-  - We will need to place an additional 22 oyster farms in Australia
+  - We will need to place an additional 23 oyster farms in Australia
 
@@
   dplyr::filter(iso3c == "AUS") %>%
+  mutate(data_quality = 4) ## this is an abalone farm
+
+## now we need to add the oyster farms from this map: https://oysterssa.com.au/oyster-growers/
+farms_AUS_2 <- data.frame(lat_lon = c("-32.377148325671286, 133.93965198614558", "-34.91844207220454, 137.7783987555795", "-35.77943962962783, 137.77191642975748", "-33.693162657803185, 136.924417900667", "-32.37607854727286, 133.94039259834852", "-32.373416358293625, 133.9357013204693", "-32.80283080755049, 134.1850786971314", "-34.62455022926624, 135.46366166621291", "-33.67979293746246, 136.91678920994693", "-34.551319592404916, 135.3981400818773", "-34.61868048533167, 135.4628853832039", "-32.3774179110106, 133.94079648728368", "-33.71698462803702, 136.90259542838538", "-34.90762372887531, 137.7836548109512", "-34.623471540228394, 135.46192328133426", "-33.67594103960825, 136.92673532055025", "-32.37775541730595, 133.94005795577584", "-34.52175570620221, 135.38834856713308", "-33.677446237574934, 136.92623952576452", "-32.37683026324807, 133.94078430357064", "-34.625125897259146, 135.46296226954271", "-34.61986531053386, 135.46279518888247", "-32.3779085349619, 133.9409211712551")) %>%
+  separate(col = lat_lon, sep = ", ", into = c("lat", "lon")) %>% 
+  mutate(iso3c = "AUS") %>%
   mutate(data_quality = 4)
 
-write.csv(farms_AUS, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"), row.names = FALSE)
+all_farms_AUS <- rbind(farms_AUS, farms_AUS_2)
+
+write.csv(all_farms_AUS, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_AUS.csv"), row.names = FALSE)
+
+all_farms_sf <- st_as_sf(all_farms_AUS, coords = c("lon", "lat"),
+                         crs = crs(gadm_latlon), agr = "constant")
+
+mapview(all_farms_sf)
 
 ## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
-AUS_additional <- data.frame(iso3c = "AUS", type = "bivalve", num_additional_farms = 68, data_quality = 4, total_farms = 69)
+AUS_additional <- data.frame(iso3c = "AUS", type = "bivalve", num_additional_farms = 45, data_quality = 4, total_farms = 69)
 write.csv(AUS_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_aus.csv"), row.names = FALSE)

### 2021-04-06 marine/marine_fish_general/finfish_farms/STEP3_gapfill_finfish.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

@@
 avg_global_marine_fish_general_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
-avg_global_marine_fish_general_tonnes_per_farm # 864.3575
+avg_global_marine_fish_general_tonnes_per_farm # 865.6905
 ```
@@
 
+test <- all_known_farms_final %>%
+  filter(iso3c == "GRC") # perfect
 ```

### 2021-04-06 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)

@@
 
-75+write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))
+write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))
 
@@
 http://www.fao.org/fishery/countrysector/naso_colombia/en
- - “The shrimp farming industry operates nine maturation laboratories, eighteen larval culture laboratories, twenty shrimp farms and seven processing plants.
+ - “The shrimp farming industry operates nine maturation laboratories, eighteen larval culture laboratories, **twenty shrimp farms** and seven processing plants.
 All of them employ qualified labour force, made up of professionals and expert technicians in their respective field of work (Minagricultura and ACUANAL, 2002).”
@@
 
-write_csv(farms_blz, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_blz.csv"))
+write_csv(farms_blz_total, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_blz.csv"))
 

### 2021-04-08 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
finished datachecking my end

@@
 
-We currently know the exact location of 1 bivalve farms in Australia, however there is much more production that just 1 farm.
-However, aquaculture websites say there are 20 abalone farms, 22 oyster farms, and 25 mussel farms in Australia
-
-Need to add 45 points to existing 24 point (for a total of 69 points)
+We currently know the exact location of 1 ASC bivalve farm, and 23 oyster farms in Australia, however there is much more production that just 24 farms.
+Aquaculture websites say there are 20 abalone farms, 23 oyster farms, and 25 mussel farms in Australia
+
+Need to add 45 points to existing 24 points (for a total of 69 points)
 
@@
 
+test <- farms_eu_final %>%
+  group_by(iso3c) %>%
+  summarise(n())
+
 ```

### 2021-04-22 workflow/place_unknown_farms.R
added arctic mask

@@ -26,6 +26,8 @@ the_crs <- crs(fake_raster, asText = TRUE)
 ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
   st_transform(the_crs)
 
+# consider removing "L" HARB_SIZE_ points
+
 
 data <- read_csv("marine/output/all_marine_farms.csv") %>% 
   st_as_sf(., 
@@ -44,8 +46,16 @@ all_the_farm_points <- data %>%
   dplyr::select(iso3c, type) %>%
   .[0, ]
 
+# create arctic raster 
+arctic_raster <- raster("/home/shares/food-systems/Aquaculture_mapping/latitude_abs.tif")
+crs(arctic_raster) <- crs(fake_raster)
+m <- c(-1000, -66, 1, 1000, 66, 1,  -66, 66, NA)
+rclmat <- matrix(m, ncol=3, byrow=TRUE)
+arctic_raster <- reclassify(arctic_raster, c(66,Inf, NA, 0,66,1))
 
-for (i in 3:length(unique(need_national_allocation$iso3c))) {
+arctic_fixed <- resample(arctic_raster, blank_raster, method = "ngb")
+
+for (i in 1:length(unique(need_national_allocation$iso3c))) {
   
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[i]
@@ -113,7 +123,7 @@ for (i in 3:length(unique(need_national_allocation$iso3c))) {
   dis_to_port_rast <- distanceFromPoints(this_raster_area, these_ports)
   port_test_rast <- dis_to_port_rast
   port_test_rast[port_test_rast >35000 ] <- NA
-  suitability_rast <- port_test_rast
+  suitability_rast <- port_test_rast+arctic_fixed
   
 
   this_coast_meters <- st_transform(this_simplified_coast, crs = "+proj=moll") %>% ## transform to a crs that can buffer in meters 
@@ -140,22 +150,49 @@ for (i in 3:length(unique(need_national_allocation$iso3c))) {
       type = this_type_vector
     )
   
-  write_rds(this_farm_points, paste0("data/temp_data/temp_farms_", i, ".rds"))
+  if (nrow(this_farm_points) != the_farm_number) stop
   
+  write_rds(this_farm_points, paste0("data/temp_data/temp_marine_final/temp_farms_", i, ".rds"))
+  print(paste0(this_iso3, " has been saved"))
   
 }
 
 
[…]

### 2021-04-23 analysis/summary_tables.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

---
title: "Summary information"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "03/06/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(RCurl)
library(mosaic)
library(googlesheets4)
library(janitor)

source(here("_spatial/template_raster.R"))

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

data <- read_csv(file.path("marine/output/all_marine_farms.csv")) %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms_to_place <- read_csv(file.path("marine/output/all_points_to_add.csv")) %>%
  distinct(iso3c, type, estimated)

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  left_join(all_farms_to_place) %>%
  mutate(source = "modeled") %>%
  rbind(data %>% mutate(source = "real", estimated = 0)) %>%
  mutate(data_type = case_when(
    source == "real" ~ "known location", 
    source == "modeled" & estimated == 0 ~ "modeled location, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
  ))
summary(all_farms)

by_type <- all_farms %>%
  group_by(type) %>%
  summarise(n()) %>%
  st_drop_geometry()

by_country_type <- all_farms %>%
  st_drop_geometry() %>%
  group_by(iso3c, type) %>%
  summarise(n())

by_data_type_country <- all_farms %>%
  st_drop_geometry() %>%
  group_by(iso3c, type, data_type) %>%
  summarise(n()) %>%
  ungroup()

known_countries <- by_data_type_country %>%
  filter(data_type == "known location") %>%
  distinct(iso3c)

by_data_type <- all_farms %>%
  st_drop_geometry %>%
  group_by(type, data_type) %>%
  summarise(n_obs = n()) %>%
  mutate(total_obs = sum(n_obs)) %>% 
  ungroup() %>%
  mutate(pct = n_obs/total_obs*100)

sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans"))

## join all farms with sources data 
all_farms_sources <- all_farms %>%
  left_join(sources, by = c("iso3c", "type")) %>%
  mutate(data_source = case_when(
    data_type == "modeled location, known number of farms" ~ datasource_number_of_farms,
    data_type == "modeled location, estimated number of farms" ~ "NA", 
    data_type == "known location" ~ datasource_farm_locations
  )) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, geometry)

test <- all_farms_sources %>%
  filter(iso3c == "IRN",
         species == "Shrimp")
```

### 2021-04-23 data_check/farms_data_check.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

@@
 library(mapview)
+library(janitor)
 
@@
 
-all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
+all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
   map_df(., readRDS) %>% 
@@
   rbind(data %>% mutate(source = "real"))
+
+sources_spreadsheet <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
+  clean_names() %>%
+    mutate(type = case_when(species == "Salmonids" ~ "salmon",
+                          species == "Unfed or algae fed shellfish" ~ "bivalve",
+                          species == "Shrimp" ~ "shrimp", 
+                          species == "Tuna" ~ "tuna", 
+                          species == "General Marine Fish" ~ "marine_fish_general", 
+                          species == "Crustaceans" ~ "crustaceans"))
+
+all_farms_sources <- all_farms %>%
+  left_join(sources_spreadsheet, by = c("iso3c", "type"))
 
@@
   group_by(iso3c, type) %>%
-  summarise(n())
+  summarise(n_obs = n()) %>%
+  left_join(sources_spreadsheet, by = c("iso3c", "type")) %>%
+  dplyr::select(iso3c, type, n_obs, number_of_total_farms) %>%
+  mutate(difference = n_obs - number_of_total_farms)
 
+canada_salmon <- all_farms_sources %>%
+  dplyr::filter(iso3c == "CAN", 
+                type == "salmon")
+
+mapview(canada_salmon)
 ```

### 2021-04-23 marine/STEP1_species_groups/STEP1_species_groups.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

@@
 
+test <- fao_1 %>%
+  dplyr::filter(aq_group == "crustaceans")
+sum(test$total_tonnes) # 5094133
+
+test <- fao_1 %>%
+  dplyr::filter(aq_group == "marine_fish_general")
+sum(test$total_tonnes) # 5094133
+
+test <- fao_1 %>%
+  dplyr::filter(aq_group == "tuna")
+sum(test$total_tonnes) # 5094133
+
+test <- fao_1 %>%
+  dplyr::filter(aq_group == "salmonids")
+sum(test$total_tonnes) # 5094133
 ```

### 2021-04-23 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

@@
 # South Korea 
-We currently know the exact location of 27 bivalve farms in South Korea, however there is much more production that just 27 farms.
-However, FAO says there are 5245 shell fish leases in South Korea.
-WE will place an additional 5218 farms.
+We currently know the exact location of 27 bivalve farms in South Korea. However, FAO says there are 5245 shell fish leases in South Korea. WE will place an additional 5218 farms.
 
@@
 
-We currently know the exact location of 25 bivalve farms in Peru, however there is much more production that just 25 farms.
-However, FAO says there are 52 bivalve farms in Peru.
-We will place an additional 27 farms (for a total of 52 farms).
+We currently know the exact location of 25 bivalve farms in Peru. However, FAO says there are 52 bivalve farms in Peru. We will place an additional 27 farms (for a total of 52 farms).
 
@@
   - Allocate 266 farms into the most suitable locations in Croatia (this is done later, along with the rest of the gapfilling.)
- - For now we will flag this so that we can gapfill later.
 
@@
 Source: 
-The aquaculture sectors in French Polynesia , n.d.
-.
+The aquaculture sectors in French Polynesia , 2019.
 Department of Marine Resources Pu Fa’Ahotu Moana.

### 2021-04-23 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

@@
 
-CHN:HKG
-CHN:MAC
-ESP:MAR
-ESP:PRT
-HKG:CHN
-HRV:BIH
-HRV:MNE
-HRV:SVN
-IDN:PNG
-IRL:GBR
-JPN:RUS
-KHM:VNM
-MEX:USA
-MYS:BRN
-MYS:THA
-NLD:BEL
-NLD:DEU
-PRK:RUS
-PRT:ESP
-SVN:ITA
-THA:MMR
-THA:MYS
-TWN:CHN
-USA:CAN
-USA:MEX
-VNM:KHM
+# CHN:HKG
+# CHN:MAC
+# ESP:MAR
+# ESP:PRT
+# HKG:CHN
+# HRV:BIH
+# HRV:MNE
+# HRV:SVN
+# IDN:PNG
+# IRL:GBR
+# JPN:RUS
+# KHM:VNM
+# MEX:USA
+# MYS:BRN
+# MYS:THA
+# NLD:BEL
+# NLD:DEU
+# PRK:RUS
+# PRT:ESP
+# SVN:ITA
+# THA:MMR
+# THA:MYS
+# TWN:CHN
+# USA:CAN
+# USA:MEX
+# VNM:KHM
 

### 2021-04-23 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

--- 2021-02-04 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
@@
 ```
+
+```{r}
+## write out shrimp taxa and production for Juliette
+fao_shrimp_taxa_prod <- fao %>%
+  filter(species %in% shrimp_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_shrimp_taxa_prod$value) # 5095394 - adds ~1000 tonnes
+
+unique(fao_shrimp_taxa_prod$country) # 35 countries 
+```

### 2021-04-23 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now

@@
 
+https://edepot.wur.nl/531775
+
 “Production of market-size shrimp takes place in 5 state-owned farms that are located at Cuba’s southern coast (which is less prone to the impact of storms than the country’s northern coast)”
@@
 This means that we need to place 3 more farms in Cuba.
+
+Source: 
+Van Der Heijden, P., 2020. Aquaculture in Cuba. Aquaculture Europe 45.
 
@@
 
- = “According to the aquaculture method and the scale of production, aquaculture production units are distributed as follows: 15 production units of tilapia cages, 26 reservoirs for household consumption, 50 small and medium scale units, 1 industrial scale unit; 2 ornamental fish production units, 23 units of fresh water prawns, and 39 marine shrimp farms.”
+ “According to the aquaculture method and the scale of production, aquaculture production units are distributed as follows: 15 production units of tilapia cages, 26 reservoirs for household consumption, 50 small and medium scale units, 1 industrial scale unit; 2 ornamental fish production units, 23 units of fresh water prawns, and 39 marine shrimp farms.”
 

### 2021-04-23 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
rasterized production for food systems run

--- 2021-04-05 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
@@
 
-CHN:HKG
-CHN:MAC
-ESP:MAR
-ESP:PRT
-HKG:CHN
-HRV:BIH
-HRV:MNE
-HRV:SVN
-IDN:PNG
-IRL:GBR
-JPN:RUS
-KHM:VNM
-MEX:USA
-MYS:BRN
-MYS:THA
-NLD:BEL
-NLD:DEU
-PRK:RUS
-PRT:ESP
-SVN:ITA
-THA:MMR
-THA:MYS
-TWN:CHN
-USA:CAN
-USA:MEX
-VNM:KHM
+# CHN:HKG
+# CHN:MAC
+# ESP:FRA
+# ESP:MAR
+# ESP:PRT
+# HKG:CHN
+# HRV:BIH
+# HRV:MNE
+# HRV:SVN
+# IRL:GBR
+# JPN:RUS
+# KHM:VNM
+# MYS:BRN
+# MYS:THA
+# NLD:BEL
+# NLD:DEU
+# PRK:RUS
+# PRT:ESP
+# RUS:POL
+# SVN:ITA
+# THA:MMR
+# THA:MYS
+# TWN:CHN
+# USA:CAN
+# USA:MEX
+# VNM:KHM
 
@@
   mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "JPN:RUS", "JPN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "JPN:RUS", "Japan", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
   mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>%  
+  mutate(GID_0 = ifelse(check %in% "RUS:POL", "RUS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "RUS:POL", "Russia", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "SVN:ITA", "SVN", GID_0)) %>%
@@
 test <- farms_prod %>%
+  st_drop_geometry() %>%
   group_by(iso3c) %>%

### 2021-04-23 marine/shrimp/shrimp_farms/STEP4_rasterize_production.Rmd
rasterized production for food systems run

@@
   mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>%   
+  mutate(GID_0 = ifelse(check %in% "MMR:THA", "MMR", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%

### 2021-04-23 marine/tuna/tuna_farms/STEP4_rasterize_production.Rmd
rasterized production for food systems run

@@
 test <- farm_production %>%
+  st_drop_geometry() %>%
   dplyr::group_by(iso3c) %>%

### 2021-04-26 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
wrote READMEs and cleaned up organization

--- 2021-04-23 marine/bivalve/bivalve_farms/STEP4_rasterize_production.Rmd
@@
 library(mapview)
+library(tidyverse)
 
@@
 
+farms_sf_prod <- st_as_sf(farms_prod)
+
+## write the production data so that we can use it for the nutrient layer. 
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/prod_data_by_cell_iso3c.shp")
+
 ```

### 2021-04-26 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
wrote READMEs and cleaned up organization

--- 2021-04-05 marine/crustaceans/crustacean_farms/STEP4_rasterize_production.Rmd
@@
            crs = crs(food_raster), 
-           agr = "constant")
+           agr = "constant") %>%
+  mutate(source = "real")
 
-all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
+all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
   map_df(., readRDS) %>% 
   rename(iso3c = iso3) %>% 
-  mutate(source = "modeled") %>% 
+ dplyr::mutate(source = "modeled") %>% 
   #left_join(tonnage_per_farms)
-  rbind(data %>% mutate(source = "real"))
+  rbind(data)
 
@@
 # some annoying mismatches due to raster resolution. Fix these
+# CHN:HKG
+# CHN:MAC
 
@@
   mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "MMR:THA", "MMR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0))
 
@@
 test <- farms_prod %>%
+  st_drop_geometry() %>%
   dplyr::group_by(iso3c) %>%

### 2021-04-26 marine/last_step_rasterize/finfish_rasterize_production.Rmd
wrote READMEs and cleaned up organization

--- 2021-04-23 marine/marine_fish_general/finfish_farms/STEP4_rasterize_production.Rmd
@@
 
+farms_sf_prod <- st_as_sf(farms_prod)
+mapview(farms_sf_prod)
+
+## write the production data so that we can use it for the nutrient layer. 
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/prod_data_by_cell_iso3c.shp")
+
 ```

### 2021-04-26 marine/last_step_rasterize/salmon_rasterize_production.Rmd
wrote READMEs and cleaned up organization

--- 2021-04-05 marine/salmon/salmon_farm/STEP4_rasterize_production.Rmd
@@
 
+# CAN:USA
+# FIN:ALA
+# FIN:RUS
+# RUS:CHN
+# USA:CAN
+
 mapview(filter(farms_sf, check == "RUS:RUS"))
@@
   mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "RUS:CHN", "RUS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "RUS:CHN", "Russia", NAME_0))
 

### 2021-04-26 marine_mapping_OLD_v1/STEP1_species_groups/summarise_tonnes_for_paper.Rmd
wrote READMEs and cleaned up organization

---
title: "Summarise total tonnes for report"
output: html_document
editor_options: 
  chunk_output_type: console
---

Putting this script here to check total numbers of aquaculture.

```{r}
library(tidyverse)
library(here)
library(countrycode)

source(here('aquaculture/R/fao_mar_clean.R')) # functions specific to mariculture dealing with compound countries
source('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2019/gh-pages/workflow/R/fao_fxn.R') # function for cleaning FAO files

```

```{r}

fao <- read_csv("/home/shares/food-systems/Food_footprint/_raw_data/FAO_aquaculture/v_2020/FAO_GlobalAquacultureProduction_Quantity_1950_2018.csv") ## read in the foa data

fao <- fao %>%
  rename(country = `Country (Country)`,
         species = `ASFIS species (ASFIS species)`, 
         fao_major_area = `FAO major fishing area (FAO major fishing area)`, 
         environment = `Environment (Environment)`) %>%
  dplyr::select(-Unit)
table(fao$environment)  
## convert to long format and clean FAO codes:
fao <- fao %>%
  gather(key="year", value="value", -country, -species, -fao_major_area, -environment) %>%
    fao_clean_data() %>%
  dplyr::filter(year >= 2010) %>%
  group_by(country, species, fao_major_area, environment) %>%
  dplyr::mutate(total_harvest = sum(value, na.rm=TRUE)) %>%
  filter(total_harvest > 0) %>% # data is cut if country/species/major area hasn't been harvested since 2010
  dplyr::select(-total_harvest) %>%
  ungroup()

## convert to iso3c codes
fao <- fao %>% 
  filter(!country == "Totals") %>% 
  filter(!is.na(species)) %>%
  mutate(country = ifelse(country == "R\xe9union", "Reunion", country)) %>%
  filter(!country %in% c("Yugoslavia SFR", "Un. Sov. Soc. Rep.")) %>%  # these countries no longer exist  
  mutate(country = ifelse(country=='Zanzibar', "Tanzania", country)) %>%  #semiautonomous region of Tanzania
  mutate(country = ifelse(country=="Eswatini", "Swaziland", country)) %>%  # also goes by this name
  mar_split() %>%   # fixes channel islands, breaks into Guernsey and Jersey
  mutate(iso3c = countrycode(country, "country.name", "iso3c"))

```

## explore freshwater
```{r}

fao <- read_csv("aquaculture/data/fao_mariculture_clean.csv")

fw_test <- fao %>%
  dplyr::filter(environment == "Freshwater") %>%
  dplyr::filter(year == 2017)

sum(fw_test$value, na.rm = TRUE) # 48671218

fw <- fao %>%
  dplyr::filter(environment == "Freshwater") %>%
  dplyr::filter(year == 2017) %>%
  group_by(species) %>%
  summarize(total = sum(value, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(total)

sum(fw$total, na.rm = TRUE) # 48671218
data.frame(fw)

```

## explore marine
```{r}
## Read in list of species from OHI so that we can add higher taxonomic classifications
mar_sp_list <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2020/gh-pages/globalprep/mar/v2020/raw/species_list.csv")

marine <- fao %>%
  filter(environment %in% c("Marine", "Brackishwater")) %>%
  dplyr::filter(year == 2017) %>%
  group_by(country, species) %>%
  summarize(total = sum(value, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(total)

#### get seaweeds totals 
marine_seaweeds <- marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
  dplyr::filter(Taxon_code == "AL"|
                species == "Red oyas")

sum(marine_seaweeds$total, na.rm = TRUE) # 32560138 tonnes of seaweeds not included

#### get marine animals totals by filtering out the seaweeds
marine_animals_total <- marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
  dplyr::filter(Taxon_code != "AL",
                  species != "Red oyas") ## filter out seaweeds
sum(marine_animals_total$total, na.rm = TRUE) # 30991774 - total marine animals production (including those spp that we will not include in the analysis)

#### Now get what we included for marine animals:
## filter out all seaweeds 
## filter out all faux freshwater species listed as marine or brackishwater: "Freshwater|catfish|Cyprinids|ilapia|iver"
## filter out all jellyfish
## filter out and species/country producing <500 tonnes
marine_included_analysis <- marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
   dplyr::filter(Taxon_code != "AL",
                species != "Red oyas") %>%
  dplyr::filter(!str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver|ellyfish")) %>%
  dplyr::filter(total >= 500)
sum(marine_included_analysis$total, na.rm = TRUE) # 29630029 tonnes were included in our analysis

#### Now lets get a list of marine animals not included in our analysys (just do the opposite of above)
marine_animal_spp_not_included_analysis <- marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
   dplyr::filter(str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver|ellyfish")) %>%
  dplyr::filter(total > 0)
unique(marine_animal_spp_not_included_analysis$species)

marine_other_not_included_analysis <- marine %>%
  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
  dplyr::filter(Taxon_code != "AL",
                species != "Red oyas") %>%
  dplyr::filter(!str_detect(species, "Freshwater|catfish|Cyprinids|ilapia|iver|ellyfish")) %>%
  dplyr::filter(total < 500) %>%
  dplyr::filter(total > 0)

marine_all_not_included_analysis <- rbind(marine_animal_spp_not_included_analysis, marine_other_not_included_analysis)
sum(marine_all_not_included_analysis$total, na.rm = TRUE) # 1361746 - matches the difference... perfect

unique(marine_all_not_included_analysis$species)

```

This is how we filtered for our production analysis: 
 - we filtered out these species :
[1] "Tilapias nei"          "River Plata mussel"    "River eels nei"        "Giant river prawn"     "Bagrid catfish"       
 [6] "Freshwater fishes nei" "Mozambique tilapia"    "Nile tilapia"          "Blackchin tilapia"     "Sabaki tilapia"       
[11] "Blue tilapia"          "North African catfish" "Cyprinids nei"         "Jellyfishes nei"  
 - we filtered out species within countries that have production < 500

### 2021-04-26 marine_mapping_OLD_v1/bivalve/food_pressures/bivalve_disturbance/bivalve_disturbance.Rmd
wrote READMEs and cleaned up organization

--- 2021-02-03 marine/bivalve/bivalve_disturbance/bivalve_disturbance.Rmd
@@
 
-write.csv(bivalve_w_l_final, file.path("aquaculture/marine/bivalve/bivalve_disturbance/data/weight_length_relationships.csv"), row.names = FALSE)
+write.csv(bivalve_w_l_final, file.path("marine/bivalve/food_pressures/bivalve_disturbance/data/weight_length_relationships.csv"), row.names = FALSE)
 
@@
 # read in spp specific country bivalve data: 
-bivalve_spp <- read_csv(file.path("aquaculture/marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"))
+bivalve_spp <- read_csv(file.path("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"))
 
 ## read in family information
-spp_families <- read_csv(file.path("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv")) %>%
+spp_families <- read_csv(file.path("marine/STEP1_species_groups/int/marine_groups.csv")) %>%
   dplyr::filter(year == 2017) %>%

### 2021-04-26 marine_mapping_OLD_v1/bivalve/food_pressures/bivalve_nutrient/bivalve_nutrient.Rmd
wrote READMEs and cleaned up organization

--- 2021-02-03 marine/bivalve/food_pressures/bivalve_nutrient/bivalve_nutrient.Rmd
@@
 ```{r}
-fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
+fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
   filter(environment %in% c("Marine", "Brackishwater"))
@@
 ## Read in fao data and get a species list for salmon
-species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
+species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
   distinct(species, aq_group)
 
-taxon_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
+taxon_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
   distinct(species, Taxon_code, aq_group)

### 2021-04-26 marine_mapping_OLD_v1/salmon/food_pressures/salmon_water/salmon_water.Rmd
wrote READMEs and cleaned up organization

---
title: "Creating a file for salmon farming water usage"
author: "Gage Clawson"
date: "12/21/2020"
output: html_document
---

This markdown creates a water useage impact layer for salmon aquaculture. This impact is zero, so we will use the salmon occupany layer to create the water impact one. The occupancy layer is created from the spatial production data. We can assume that the areas with 0 mean that there is no farm/salmon so no water impact (if there was one)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(raster)
library(tidyverse)

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/"
food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

```{r}
occupancy <- read_csv(file.path(path_prep, "salmon_disturbance.csv"))

water <- occupancy %>% 
  mutate(salmon_water_m3 = ifelse(salmon_disturbance_prop == 0, NA,
                                  ifelse(salmon_disturbance_prop > 0, 0, salmon_disturbance_prop))) %>% 
  dplyr::select(x,y,salmon_water_m3)

write_csv(water, file.path(path_prep, "salmon_water.csv"))

## save to datalayers folder with the correct naming conventions: 
final_layer_water <- read_csv(file.path(path_prep, "salmon_water.csv"))

final_rast <- rasterFromXYZ(final_layer_water, crs = food_crs)
crs(final_rast)
plot(final_rast)
cellStats(final_rast, "sum") # 0

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 0
final_rast

writeRaster(final_rast, file.path(path_final, "marine_salmon_aquaculture_meat_water.tif"), overwrite = T)
```

### 2021-04-26 marine_mapping_OLD_v1/shrimp/shrimp_farms/STEP3_rasterize_production.Rmd
wrote READMEs and cleaned up organization

---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (USCB, NCEAS, OHI)"
date: "10/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

source(here::here("_spatial/template_raster.R"))

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

farms <- read.csv(here::here("marine/shrimp/shrimp_farms/data/global_shrimp_farm_lat_lon.csv"))

farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sf)

test <- rasterize(farms_sf, food_raster, fun = "count")
plot(log(test + 1))

```

# determine subregions where points are located

```{r}

farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)

farms_sf <- farms_sf %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

# CRI:PAN - CRI
# HND:NIC - HND
# KHM:THA - KHM
# TWN:CHN - TWN

mapview(filter(farms_sf, check=="HND:HND"))
mapview(filter(farms_sf, check=="HND:NIC"))
mapview(filter(farms_sf, check =="KHM:KHM"))
mapview(filter(farms_sf, check == "KHM:THA"))
mapview(filter(farms_sf, check == "TWN:CHN"))
mapview(filter(farms_sf, check == "CHN:CHN"))
mapview(filter(farms_sf, check == "CRI:PAN"))
mapview(farms_sf)

# some annoying mismatches due to raster resolution. Fix these

unique(farms_sf$NAME_1)

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "KHM:THA", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:THA", "Cambodia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0))

farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)

```

# FAO shrimp production data per country
```{r}

fao <- read.csv(here::here("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

setdiff(fao$iso3c, farms_sf$iso3c)
setdiff(farms_sf$iso3c, fao$iso3c)

```

# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with regional production data and calculate production per farm
```{r}

## Saudi Arabia is the only one with regional production
farms_rgn_prod <- farms_sf_correct %>%
  dplyr::filter(!is.na(prod))

## calculate farm production
farms_rgn_prod <- farms_rgn_prod %>%
  mutate(prop_production = prod/sum(prod)) %>%
  mutate(regional_prod = fao_tonnes_production*prop_production) %>%
  group_by(NAME_1) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = regional_prod/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry) %>%
  dplyr::filter(iso3c != "SAU") ## filter out SAU since we have regional production estimates

```

# combine and check it all matches ok

```{r}

farm_production <- rbind(farms_prod, farms_rgn_prod)

test <- farm_production %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farm_production)
mapview(farms_sf)

sum(farms_sf$tonnes_per_farm) # 5094133

shrimp_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(shrimp_raster_check+1))
cellStats(shrimp_raster_check, stat = "sum", na.rm = TRUE) # 5094133

mapview(shrimp_raster_check)

shrimp_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
mapview(log(shrimp_raster+1))

plot(log(shrimp_raster+1))

shrimp_raster_df <- as.data.frame(shrimp_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(shrimp_raster, stat = "sum") # 5094133
sum(shrimp_raster_df$tonnes_production) # 5094133
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5094133
sum(fao$fao_tonnes_production) # 5094133

write_csv(shrimp_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/shrimp_farm.csv")

```

### 2021-04-26 marine_mapping_OLD_v1/tuna/tuna_farms/STEP3_rasterize_production.Rmd
wrote READMEs and cleaned up organization

--- 2021-04-05 marine/tuna/tuna_farms/STEP4_rasterize_production.Rmd
@@
 
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant")
+farms <- read.csv(here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"))
 
-all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
-  mutate(source = "modeled") %>% 
-  #left_join(tonnage_per_farms)
-  rbind(data %>% mutate(source = "real"))
+farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
+                 crs = crs(gadm_latlon), agr = "constant")
 
-tuna_farms <- all_farms %>%
-  dplyr::filter(type == "tuna")
-
-mapview(tuna_farms)
+mapview(farms_sf)
 ```
@@
 
-tuna_farms$reg_id <- raster::extract(gadm_latlon, tuna_farms)
+farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)
 
-farms_sf <- tuna_farms %>%
+farms_sf <- farms_sf %>%
   left_join(gadm_codes, by="reg_id") %>%
@@
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/prod_data_by_cell_iso3c.shp")
+st_write(farms_sf_prod, "marine/tuna/tuna_nutrient/prod_data_by_cell_iso3c.shp")
 
@@
 
-write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm_updated.csv")
+write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm.csv")
 

### 2021-04-27 analysis/match_data_sources.Rmd
added a script for summary stats for paper. Added a script to match sources and data years (or lack thereof) to every farm mapped

---
title: "Match point to sources"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "04/26/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes the farms dataset produced from prior steps, and matches to our data source spreadsheet, so that each point in the final database has a source associated with it (or an NA, if it was estimated).

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(RCurl)
library(mosaic)
library(googlesheets4)
library(janitor)

source(here("_spatial/template_raster.R"))

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and convert to spatial dataframe
```{r}

data <- read_csv(file.path("marine/output/all_marine_farms.csv")) %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms_to_place <- read_csv(file.path("marine/output/all_points_to_add.csv")) %>%
  distinct(iso3c, type, estimated)

all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  left_join(all_farms_to_place) %>%
  mutate(source = "modeled") %>%
  mutate(estimated = ifelse(iso3c == "IND" & type == "bivalve", 0, estimated)) %>% # fix india mistake
  rbind(data %>% mutate(source = "real", estimated = 0)) %>%
  mutate(data_type = case_when(
    source == "real" ~ "known location", 
    source == "modeled" & estimated == 0 ~ "modeled location, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
  ))
summary(all_farms)
```

# Match to our sources dataset 
```{r}

# read in our sources spreadsheet (manually uploaded by GC)
sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans")) %>%
  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms))

## join all farms with sources data 
all_farms_sources <- all_farms %>%
  left_join(sources, by = c("iso3c", "type")) %>%
  mutate(data_source = case_when(
    data_type == "modeled location, known number of farms" ~ datasource_number_of_farms,
    data_type == "modeled location, estimated number of farms" ~ "NA", 
    data_type == "known location" ~ datasource_farm_locations), 
  data_year = case_when(
    data_type == "modeled location, known number of farms" ~ data_year_number_of_farms,
    data_type == "modeled location, estimated number of farms" ~ "NA", 
    data_type == "known location" ~ data_year_farm_locations)) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

unique(all_farms_sources$data_year)
```

# Fix instances where a known location has multiple sources
```{r}
test <- all_farms_sources %>%
  filter(iso3c == "AUS", species == "Unfed or algae fed shellfish")
unique(all_farms_sources$species)

test <- all_farms_sources %>%
  filter(iso3c == "IND", species == "Unfed or algae fed shellfish")

## Have multiple location data sources...  fix these so that each point has only one of the datasources

# Salmon: CAN, USA
# Shrimp: USA 
# Bivalve: AUS, CAN, USA
# General marine fish: TWN

## add in subregional information
all_farms_sources_gadm <- all_farms_sources
all_farms_sources_gadm$reg_id <- raster::extract(gadm_latlon, all_farms_sources)

all_farms_sources_gadm <- all_farms_sources_gadm %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

## Canada Salmon fix: 
CAN_salmon_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "CAN", 
               species == "Salmonids") %>%
  separate(col = data_source, into = c("ds_1", "ds_2", "ds_3", "ds_4"), sep = ";") %>%
  separate(col = data_year, into = c("dy_1", "dy_2", "dy_3", "dy_4"), sep = ",") %>%
  mutate(data_source = case_when(
    NAME_1 == "British Columbia" ~ ds_1, 
    NAME_1 %in% c("New Brunswick", "Maine") ~ ds_2, 
    NAME_1 %in% c("Newfoundland and Labrador") ~ ds_4,
    NAME_1 == "Nova Scotia" ~ ds_3

  )) %>%
  mutate(data_year = case_when(
    NAME_1 == "British Columbia" ~ dy_1, 
    NAME_1 %in% c("New Brunswick", "Maine") ~ dy_2, 
    NAME_1 %in% c("Newfoundland and Labrador") ~ dy_4,
    NAME_1 == "Nova Scotia" ~ dy_3

  )) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

# check <- CAN_salmon_fix %>%
#   st_drop_geometry() %>%
#   group_by(data_source) %>%
#   summarise(n()) ## numbers are correct

## Canada Bivalve fix: 
CAN_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "CAN", 
               species == "Unfed or algae fed shellfish") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = case_when(
    NAME_1 == "British Columbia" ~ ds_1, 
    NAME_1 == "Nova Scotia" ~ ds_2

  )) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

# check <- CAN_bivalve_fix %>%
#   st_drop_geometry() %>%
#   group_by(data_source) %>%
#   summarise(n()) ## numbers are correct

## USA Salmon fix: 
USA_salmon_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "USA", 
               species == "Salmonids") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  separate(col = data_year, into = c("dy_1", "dy_2"), sep = ",") %>%
  mutate(data_source = case_when(
    NAME_1 %in% c("New Brunswick", "Maine") ~ ds_2, 
    NAME_1 == "Washington" ~ ds_1
  )) %>%
    mutate(data_year = case_when(
    NAME_1 %in% c("New Brunswick", "Maine") ~ dy_2, 
    NAME_1 == "Washington" ~ dy_1
  )) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

# check <- USA_bivalve_fix %>%
#   st_drop_geometry() %>%
#   group_by(data_source) %>%
#   summarise(n()) ## numbers are correct

## USA Shrimp fix: 
USA_shrimp_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "USA", 
               species == "Shrimp") %>%
  separate(col = data_source, into = c("ds_1", "ds_2", "ds_3", "ds_4", "ds_5"), sep = ";") %>%
  separate(col = data_year, into = c("dy_1", "dy_2"), sep = ",") %>%
  mutate(data_source = case_when(
    NAME_1 %in% c("Texas") ~ ds_2, 
    NAME_1 == "Alabama" ~ ds_3, 
    NAME_1 == "Hawaii" ~ ds_4, 
    NAME_1 == "Florida" ~ ds_5
  )) %>%
    mutate(data_year = case_when(
    NAME_1 %in% c("Texas") ~ dy_1, 
    NAME_1 == "Alabama" ~ dy_2, 
    NAME_1 == "Hawaii" ~ dy_2, 
    NAME_1 == "Florida" ~ dy_2
  )) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

## USA Bivalve fix: 
USA_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "USA", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known location") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = ifelse(NAME_1 == "Washington"| NAME_1 == "Rhode Island", ds_2, ds_1)) %>% 
  mutate(data_year = 2018) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

# check <- USA_bivalve_fix %>%
#   st_drop_geometry() %>%
#   group_by(data_source) %>%
#   summarise(n()) ## numbers are correct

## AUS Bivalve fix: 
AUS_bivalve_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "AUS", 
               species == "Unfed or algae fed shellfish", 
               data_type == "known location") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
  mutate(data_source = ifelse(NAME_1 == "Victoria", ds_1, ds_2)) %>%
  mutate(data_year = 2021) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

## TWN marine fish fix: 
# read in taiwan sources sheet
twn_sources <- read_csv(here("marine/marine_fish_general/finfish_farms/data/taiwan_farms_sources.csv"))

twn_sources_sf <- st_as_sf(twn_sources, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

## rows 1-40 are lee, rows 41-66 are kuo
TWN_finfish_fix <- all_farms_sources_gadm %>%
  dplyr::filter(iso3c == "TWN", 
               species == "General Marine Fish", 
               data_type == "known location") %>%
  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>% 
  separate(col = data_year, into = c("dy_1", "dy_2"), sep = ",") %>% 
  mutate(row = row_number()) %>%
  mutate(data_source = ifelse(row %in% c(1:40), ds_1, ds_2)) %>%
  mutate(data_year = ifelse(row %in% c(1:40), dy_1, dy_2)) %>%
  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)

##### Now add these back into total dataset #####

all_farms_sources_final <- all_farms_sources %>%
  filter(iso3c != "CAN"|species != "Salmonids") %>%
  filter(iso3c != "CAN"|species != "Unfed or algae fed shellfish") %>%
  filter(iso3c != "USA"|species != "Salmonids") %>%
  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known location") %>%
  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known location") %>%
  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known location") %>%
  filter(iso3c != "USA"|species != "Shrimp") %>%
  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix) %>%
  mutate(data_year = as.numeric(data_year))

summary(all_farms_sources_final)
unique(all_farms_sources_final$data_year)

## Now save this as a csv
st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources.csv", layer_options = "GEOMETRY=AS_XY")

## check that it wrote correctly

all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
```

### 2021-04-27 analysis/paper_stats.Rmd
added a script for summary stats for paper. Added a script to match sources and data years (or lack thereof) to every farm mapped

---
title: "Summary stats for paper"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "04/26/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes our final farms dataset and calculates summary statistics that will be used in the paper.

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(RCurl)
library(mosaic)
library(googlesheets4)
library(janitor)

source(here("_spatial/template_raster.R"))

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))
```

# Read in farms data and convert to sf

```{r}
all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources.csv") %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- all_farms_sf %>%
  st_drop_geometry()

```

```{r}
sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans"))

## Numbers by data type
by_data_type <- all_farms %>%
  group_by(data_type) %>%
  summarise(n_obs = n()) %>%
  mutate(total_obs = sum(n_obs)) %>% 
  ungroup() %>%
  mutate(pct = n_obs/total_obs*100)

by_data_type
# A tibble: 3 x 4
#   data_type                                   n_obs total_obs   pct
#   <chr>                                       <int>     <int> <dbl>
# 1 known location                               9750     95341  10.2
# 2 modeled location, estimated number of farms 75072     95341  78.7
# 3 modeled location, known number of farms     10519     95341  11.0

# How many countries have spatial locations information?
known_countries <- all_farms %>%
  filter(data_type == "known location") %>%
  distinct(iso3c)

# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of the total estimated points, and only had 15 known location points

chn_data_estimated <- all_farms %>%
  filter(iso3c == "CHN") %>%
  filter(data_type == "modeled location, estimated number of farms")
# 58151 points
58151/75073 # 0.7745927 = 77%

chn_data_known <- all_farms %>%
  filter(iso3c == "CHN") %>%
  filter(data_type == "known location") # 15 locations

# Chile, Norway, Peru, the United States, Canada and Ireland provided a substantial number of known locations (>1000).
top_known <- all_farms %>%
  filter(data_type == "known location") %>%
  group_by(iso3c) %>%
    summarise(n_obs = n())

# Only 5 countries (Cambodia, Mauritius, Myanmar, North Korea, and Russia) had no form of farm data at all, however, these countries only account for 0.5% of marine aquaculture production included.

no_info_at_all <- sources %>%
  dplyr::filter(known_farms_location == 0, known_farms_no_location == 0) ## only 5 with no information at all

mar_production <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv")

no_info_production <- mar_production %>%
  filter(country %in% c("Cambodia", "Mauritius", "Myanmar", "Korea, Dem. People's Rep", "Russian Federation"))
sum(no_info_production$total_tonnes) # 152800.1

sum(mar_production$total_tonnes) # 29623515
152800.1/29623515

chn_production <- mar_production %>%
  filter(country == "China")
sum(chn_production$total_tonnes)
17696822/29623515

# Per species group, salmon was the most data rich (98% of points had location information, 1.13% of points were known with no location information, 0.87% estimated), followed by Tuna (34% of points had location information, 66% of points were known with no location information, 0% estimated).

by_species_data_type <- all_farms %>%
  group_by(species, data_type) %>%
  summarise(n_obs = n()) %>%
  mutate(total_obs = sum(n_obs)) %>% 
  ungroup() %>%
  mutate(pct = n_obs/total_obs*100)
```

Check some of the data
```{r}
by_type <- all_farms %>%
  group_by(species) %>%
  summarise(n_obs = n())

by_country_type <- all_farms %>%
  group_by(iso3c, species) %>%
  summarise(n_obs = n()) %>%
  left_join(sources) %>%
  dplyr::select(iso3c, species, n_obs, number_of_total_farms) %>%
  mutate(difference = n_obs - number_of_total_farms)

by_data_type_country <- all_farms %>%
  group_by(iso3c, species, data_type) %>%
  summarise(n_obs = n()) %>%
  ungroup() %>%
  left_join(sources) %>%
  dplyr::select(iso3c, species, data_type, n_obs, number_of_total_farms, known_farms_location, known_farms_no_location, estimated_farms)

known <- by_data_type_country %>%
  filter(data_type == "known location") %>%
  dplyr::select(iso3c, species, data_type, n_obs, known_farms_location) %>%
  mutate(difference = n_obs - known_farms_location)

number_known <- by_data_type_country %>% 
  filter(data_type == "modeled location, known number of farms") %>%
  dplyr::select(iso3c, species, data_type, n_obs, known_farms_no_location) %>%
  mutate(difference = n_obs - known_farms_no_location)

estimated <- by_data_type_country %>% 
  filter(data_type == "modeled location, estimated number of farms") %>%
  dplyr::select(iso3c, species, data_type, n_obs, estimated_farms) %>%
  mutate(difference = n_obs - estimated_farms)

```

### 2021-04-27 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
added a script for summary stats for paper. Added a script to match sources and data years (or lack thereof) to every farm mapped

@@
   dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
-  mutate(estimated = 1) %>%
+  mutate(estimated = ifelse(iso3c == "IND", 0, 1)) %>%
   filter(num_additional_farms != 0)

### 2021-04-27 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
finished datachecking my end
fixed missed nova scotia salmon points.. one more farm needs to be added to russia salmon now
added a script for summary stats for paper. Added a script to match sources and data years (or lack thereof) to every farm mapped

@@
 
+test <- farms_eu_final %>%
+  group_by(iso3c) %>%
+  summarise(n())
 ```
@@
 Source:
-NASO aquaculture maps collection , 2010. . Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
+NASO aquaculture maps collection , 2010. Food and Agriculture Organization of the United Nations. [Accessed January 17, 2020] http://www.fao.org/fishery/naso-maps/selected-aquaculture-sites/
 
@@
 Source:
-National Aquaculture Group, n.d. [Accessed November 12, 2020]. http://www.naqua.com.sa/about-us.php
+National Aquaculture Group, 2020. [Accessed November 12, 2020]. http://www.naqua.com.sa/about-us.php
 
@@
 
-                              lon = c(120.1486974182384, 120.14508600806049, 120.13344924193156, 120.12923593005728, 120.11007291797651, 120.10560972235575, 120.09462339467383, 120.08741361713255, 120.0340739167051, 120.0323838672442, 120.19480335124462, 120.19703494905501, 120.19737827179506, 120.19960986960544, 120.48594464702815, 120.48934227493775, 120.4981761075027, 120.50893526254974, 120.51527750131434, 120.51890163775126, 121.13759861706552, 121.14388413948092, 121.14975973652137, 121.15167272160434, 121.15631854252005, 121.16246742314381, 121.3724851599623, 121.38612214670725, 121.39450636818748, 121.4097595903985, 121.40864842851558, 121.40026420703533, 121.83377270959099, 121.83292494893261, 121.83961283857079, 121.82878034126954, 121.8381057085115, 121.83829409976889, 121.87509035189372, 121.87405621071602, 121.84309342644401, 121.80292466585698))
+                              lon = c(120.1486974182384, 120.14508600806049, 120.13344924193156, 120.12923593005728, 120.11007291797651, 120.10560972235575, 120.09462339467383, 120.08741361713255, 120.0340739167051, 120.0323838672442, 120.19480335124462, 120.19703494905501, 120.19737827179506, 120.19960986960544, 120.48594464702815, 120.48934227493775, 120.4981761075027, 120.50893526254974, 120.51527750131434, 120.51890163775126, 121.13759861706552, 121.14388413948092, 121.14975973652137, 121.15167272160434, 121.15631854252005, 121.16246742314381, 121.3724851599623, 121.38612214670725, 121.39450636818748, 121.4097595903985, 121.40864842851558, 121.40026420703533, 121.83377270959099, 121.83292494893261, 121.83961283857079, 121.82878034126954, 121.8381057085115, 121.83829409976889, 121.87509035189372, 121.87405621071602, 121.84309342644401, 121.80292466585698)) %>%
+  mutate(source = "Lee")
 ```
@@
 grouper_points <- data.frame(lat = c(23.366020730714546, 23.344101510137286, 23.11902593130365, 23.124310527454163, 23.130061175003874, 22.412837508670247, 22.5060215233288, 22.495712950055186, 22.489210224135196, 22.478900398348003, 22.963578173481825, 22.958915389973615, 22.958796842534618, 22.95887587417216, 22.962708853156307, 22.910490254668936, 22.900053951559105, 22.88771910346936, 22.87475049020418, 22.85735162493687, 23.033784880994748, 23.01988231566828, 22.990894265701648, 22.969242998130003),
-                             lon = c(120.12803212666465, 120.11599409273818, 120.05874863883409, 120.07531112355083, 120.08122629666394, 120.5141089682018, 120.361518692894, 120.37199003646582, 120.38503630058813, 120.40220243759113, 120.16265849315296, 120.16450385288077, 120.16420344548321,  120.16630629726609, 120.16480426027832, 120.17469982002679, 120.17658809509712, 120.18208125893808, 120.18637279318882, 120.18688777729894, 120.07405573439489, 120.09946161715932, 120.14268135694375, 120.15847420298654))
+                             lon = c(120.12803212666465, 120.11599409273818, 120.05874863883409, 120.07531112355083, 120.08122629666394, 120.5141089682018, 120.361518692894, 120.37199003646582, 120.38503630058813, 120.40220243759113, 120.16265849315296, 120.16450385288077, 120.16420344548321,  120.16630629726609, 120.16480426027832, 120.17469982002679, 120.17658809509712, 120.18208125893808, 120.18637279318882, 120.18688777729894, 120.07405573439489, 120.09946161715932, 120.14268135694375, 120.15847420298654)) %>%
+  mutate(source = "Kuo")
 
@@
 farms_twn <-  st_as_sf(all_points_twn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
+                 crs = crs(gadm_latlon), agr = "constant") %>%
+  dplyr::select(-source)
 
@@
 write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_twn.csv"))
+
+## Save a file with the sources so we can match the sources to the correct point later
+farms_twn_source <-  st_as_sf(all_points_twn, coords = c("lon", "lat"), 
+                 crs = crs(gadm_latlon), agr = "constant")
+
+mapview(farms_twn)
+
+## write to farms folder 
+write_csv(all_points_twn, here("marine/marine_fish_general/finfish_farms/data/taiwan_farms_sources.csv"))
 
@@
 Source:
-Martec Industries Aquaculture , n.d. . Martec.  https://www.martec.co.cr/#aquaculture
+Martec Industries Aquaculture , 2020. Martec.  https://www.martec.co.cr/#aquaculture
 

### 2021-05-11 analysis/paper_figs.Rmd
made the figures!

---
title: "Figures for paper"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "05/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes our final farms dataset and calculates summary statistics that will be used in the paper.

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)
library(RCurl)
library("rnaturalearth")
library("rnaturalearthdata")
library(cowplot) 
library(ggpubr)
library(RColorBrewer)
library(OpenStreetMap)
library(ggspatial)

source(here("_spatial/template_raster.R"))

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))
```

# Read in farms data and convert to sf

```{r}
all_farms_sf <- read_csv("../all_marine_aquaculture_farms_sources.csv") %>%
    st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- all_farms_sf %>%
  st_drop_geometry()

```

```{r}

all_farms <- read_csv("../all_marine_aquaculture_farms_sources.csv")

unique(sort(all_farms$country))

all_farms_stat <- all_farms %>%
  mutate(lon = round(X, 0), 
         lat = round(Y, 0))

lon_stat <- all_farms_stat %>%
  group_by(lon) %>%
  summarise(n())

lat_stat <- all_farms_stat %>%
  group_by(lat) %>%
  summarise(n())

```

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)

# https://stackoverflow.com/questions/8545035/scatterplot-with-marginal-histograms-in-ggplot2

## This one works!

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9) )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
    #  geom_vline(xintercept = 135) + # check to make sure it lines up
  #geom_hline(yintercept = 0) # check to make sure it lines up

total_map

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
plot_x

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogramh(data = all_farms, aes(y = Y, fill = data_type), bins = 180) +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
 # coord_flip() 
plot_y

# Combine all plots into one
plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
ggdraw(plot_final)
ggsave("analysis/figs/map_fig.jpg")

## zoomed maps

chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.7, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-75, -72), ylim = c(-46, -44), expand = FALSE) +
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", ## put legend on bottom
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("A")  # + 
 #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
chl_zoom

## philippines
phl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 1, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(120.25, 122.5), ylim = c(17, 19), expand = FALSE) +
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("B")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
phl_zoom

(chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (phl_zoom + theme(legend.position = "none")) ## save this output in the plot window...

```

ARCHIVE: Other ways of trying
```{r}

## all together
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.2) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(), 
        legend.position = "none") 
total_map

## make longitude histogram

lon_hist <- ggplot(data = all_farms) + 
  geom_histogram(aes(X, fill = data_type), bins = 360) + 
  # scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180)) +
  # scale_y_reverse() +
   theme_void() + 
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(), 
        legend.position = "none") # +
  # geom_vline(xintercept = 135) 
lon_hist

## make latitude histogram
lat_hist <- ggplot(data = all_farms) + 
  geom_histogram(aes(Y, fill = data_type), bins = 180) + 
  # scale_x_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  # xlim(-58, 73) + 
  coord_flip() +
   theme_void() + 
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(), 
        legend.position = "none") # + 
  # geom_vline(xintercept = 0)

lat_hist

require(gridExtra)
library(cowplot)
library(egg)

## using ggExtra
library(ggExtra)
ggExtra::ggMarginal(total_map, type = "histogram", groupFill = TRUE, size = 2)

## using patchwork
lon_hist + plot_spacer() + total_map + lat_hist + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

## using cowplot
plot_grid(
  lon_hist
  , NULL
  , total_map
  , lat_hist
  , ncol = 2
  , nrow = 2
  , rel_heights = c(0.2, 1)
  , rel_widths = c(1, 0.2)
)

```

```{r}
## by species group, colored by estimation type
ggplot(data = world) +
  geom_sf() + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.3) +
  facet_wrap(~species)

## by estimation type
ggplot(data = world) +
  geom_sf() + 
  geom_point(data = all_farms, aes(x = X, y = Y), size = 0.3) +
  facet_wrap(~data_type)

## by estimation type, colored by species 
ggplot(data = world) +
  geom_sf() + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = species), size = 0.3) +
  facet_wrap(~data_type)
```

### 2021-05-11 analysis/paper_stats.Rmd
made the figures!

@@
 ```
+
+```{r}
+
+all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
+
+unique(sort(all_farms$country))
+
+all_known_locations <- all_farms %>%
+  filter(data_type == "known location")
+
+unique(all_known_locations$country)
+
+## read in each of the comprehensive locations
+
+farms_folder <- file.path("aquaculture_mapping/marine")
+
+bivalve_comp_files <- list.files(here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+
+bivalve_comp <- plyr::ldply(bivalve_comp_files, read_csv) %>%
+  mutate(type = "bivalve") %>%
+  dplyr::select(lat, lon, iso3c, data_quality, type)
+
+shrimp_comp_files <- list.files(here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+
+shrimp_comp <- plyr::ldply(shrimp_comp_files, read_csv) %>%
+  mutate(type = "shrimp")%>%
+  dplyr::select(lat, lon, iso3c, data_quality, type)
+
+salmon_comp_files <- list.files(here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+
+salmon_comp <- plyr::ldply(salmon_comp_files, read_csv) %>%
+  mutate(type = "salmon")%>%
+  dplyr::select(lat, lon, iso3c, data_quality, type)
+
+tuna_comp_files <- list.files(here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+
+tuna_comp <- plyr::ldply(tuna_comp_files, read_csv) %>%
+  mutate(type = "tuna")%>%
+  dplyr::select(lat, lon, iso3c, data_quality, type)
+
+finfish_comp_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+
+finfish_comp <- plyr::ldply(finfish_comp_files, read_csv) %>%
+  mutate(type = "finfish")%>%
+  dplyr::select(lat, lon, iso3c, data_quality, type)
+
+crustaceans_comp_files <- list.files(here("marine/crustaceans/crustaceans_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+
+crustaceans_comp <- plyr::ldply(crustaceans_comp_files, read_csv) %>%
+  mutate(type = "crustaceans")%>%
+  dplyr::select(lat, lon, iso3c, data_quality, type)
+
+all_comp_farms <- rbind(finfish_comp, bivalve_comp, salmon_comp, tuna_comp, shrimp_comp) %>%
+  filter(data_quality == 5) %>%
+  group_by(iso3c, type) %>%
+  summarise(n_obs = n())
+
+unique(all_comp_farms$iso3c)
+
+## Countries that have comprehensive location data across all their species reported:
+# - ARE (1 type), GRC (2 type), MLT (2 types), NOR (3 types), CYP (1 type), HKG (2 type), BLG (1 type), BLZ (1 type), CAN (2 types), CHL (2 types), DNK (2 types), FIN (1 type), FRO (1 type), GBR (2 types), IRL (2 types), JEY (1 type)
+```

### 2021-05-11 analysis/prod_farm_rel_explore.Rmd
made the figures!

---
title: "Explore production and farm trends"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "04/28/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("analysis/R/comp_farms_production.R")

## Bivalve
bivalve <- comp_farms_production("bivalve")

plot_farms_prod(bivalve)

lm_farms_prod(bivalve)

## cambodia has 8300 tonnes of production, plugging into model we get
8300*8.740e-03 - 4.778e+01 # ~25 farms

8300/mean(bivalve$tonnes_per_farm) # ~ 30 farms rounding up

## Salmon
salmon <- comp_farms_production("salmon")

plot_farms_prod(salmon)

lm_farms_prod(salmon)

## Russia has 13016 tonnes of production, plugging into model we get
13016*1.060e-03 + 7.318e+01 # ~87 farms

13016/mean(salmon$tonnes_per_farm) # ~ 15 farms rounding up

## Shrimp
shrimp <- comp_farms_production("shrimp")

plot_farms_prod(shrimp)

lm_farms_prod(shrimp)

## Myanmar has 55309.51 tonnes of production

55309.51*3.888e-03 + 2.024e+01 # ~236 farms

55309.51/mean(shrimp$tonnes_per_farm) # ~ 165 farms rounding up

## mfgeneral
finfish <- comp_farms_production("finfish")

plot_farms_prod(finfish)

lm_farms_prod(finfish)

## Myanmar has 55309.51 tonnes of production

1419359*2.669e-03 + 4.052e+01 # ~3828.789 farms

1419359/mean(finfish$tonnes_per_farm) # ~ 1639.569 farms
```

All of the models prove to be significant. However, they estimate a lot more farms than just using the mean production per farm values... so we are likely being conservative with our current number-of-farm estimations.

### 2021-05-11 marine/STEP1_species_groups/STEP1_species_groups.Rmd
wrote READMEs and cleaned up organization
made the figures!

@@
                 !is.na(aq_group)) %>%
-  dplyr::filter(value >= 500) %>%
+  # dplyr::filter(value >= 500) %>%
   group_by(aq_group, country, species, year) %>%
@@
   # dplyr::filter(tonnes >= 500) %>%
-  group_by(country, aq_group, year) %>%
-  summarise(total_tonnes = sum(tonnes)) %>%
-  arrange(aq_group)
+  group_by(country, year) %>%
+  summarise(total_tonnes = sum(tonnes))# %>%
+ # arrange(aq_group)
 
@@
 
+## Take a look at the data 
 test <- fao_1 %>%

### 2021-05-11 marine/crustaceans/crustaceans_farms/STEP1_fao_crustacean_production.Rmd
made the figures!

--- 2021-03-23 marine_mapping_archive_v1/crustaceans/crustacean_farms/STEP1_fao_crustacean_production.Rmd
@@
 
+sum(explore$fao_tonnes_production) # 401719.1
+unique(explore$country) # 6 countries
+
 ```
+
+```{r}
+## write out bivalve taxa and production for Juliette
+fao_crustaceans_taxa_prod <- fao %>%
+  filter(species %in% crustaceans_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_crustaceans_taxa_prod$value) # 401733.5 - adds 14 tonnes
+
+unique(fao_crustaceans_taxa_prod$country) # 6 countries 
+```

### 2021-05-11 marine/crustaceans/crustaceans_farms/STEP2_crustacean_farm_locations.Rmd
made the figures!

--- 2021-02-09 marine/crustaceans/crustacean_farms/STEP2_crustacean_farm_locations.Rmd
@@
 
-Now we will map crustacean farms. Workflow will be as follows:
+Now we will map the remaining countries with crustacean farms. Workflow will be as follows: 
+ - Try to obtain exact locations of farms from published source or 
+ dataset (such as FAO or a research paper)
+ - If there are not exact locations or comprehensive locations, find the number of farms. 
+ - If there is no information at all, note it. We will gapfill later.
 
- - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
- - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
- -  If there is enough information to know there are a specific number of crustacean farms, equally allocate the farms across the coastline.
-If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise.
- - Lastly, if there is no evidence of marine crustacean farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be, i.e.
-what we've done for Russia for bivalves).
+For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).
 
-For each point, we will add a column for "data quality". It will be scored as very good (1.0), good (0.667), fair (0.333) or poor (0.0). 
- - Very Good qualifications: Locations taken from leases, or from a map with specific locations (i.e. EMOD, ASC, HELCOM etc.).
- - Good qualifications: Locations are projected or it is a only sample of total locations (NASO maps) 
- - Fair qualifications: A specific number of farms are placed on the coast, without knowing exact locations.
-Or Per province/state locations (i.e.
-placing a point randomly in each province) or sub regional location.
- - Bad qualifications: No data at all (randomly placed point(s) along the coast, a non-specific number), google maps estimates.
+5: Comprehensive number of exact farms
+
+4: Subset of exact locations, need to add a specific number of farms to existing locations. 
+  - country|species|farm locations
+  - country|species|additional points
+
+3: A specific number of farms are known, but no locations 
+ - country|species|additional points
+
+2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
+ - country, species, n_existing_points
+
+2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.
+
+1: No information on number of farms at all. Need to be gapfilled by tonnage. 
+ - country|species|# additional farms (this will be NA)
 
 ## Indonesia
-Can't find any infomration on crab farm locations in Indonesia. I will place one farm, randomly on the coast of Indonesia.
+Can't find any infomration on crab farm locations in Indonesia. This will be fully gapfilled. data_quality = 1
 
@@
 ```{r}
+idn_gf <- data.frame(iso3c = "IDN", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+write_csv(idn_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_idn.csv"))
 
-farms_idn <- data.frame(lat = c(0.3359943014669836),
-                        lon = c(117.55582991782983)) %>%
-  mutate(iso3c = "IDN") %>%
-  mutate(data_quality = 0.0)
-
-write_csv(farms_idn, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_idn.csv"))
-
-## visualize it 
-farms_idn <-  st_as_sf(farms_idn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_idn)
 ```
@@
 
-Can't find any datasets of marine crustacean farm locations in China. I will place one farm randomly on the coast of China.
+Can't find any datasets of marine crustacean farm locations in China. This will be fully gapfilled. data_quality = 1
 
@@
 ```{r}
-
-farms_chn <- data.frame(lat = c(29.378009267567716),
-                        lon = c(121.95043909100868)) %>%
-  mutate(iso3c = "CHN") %>%
-  mutate(data_quality = 0.0)
-
-write_csv(farms_chn, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_chn.csv"))
-
-## visualize it 
-farms_chn <-  st_as_sf(farms_chn, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_chn)
+chn_gf <- data.frame(iso3c = "CHN", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+write_csv(chn_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_chn.csv")) 
 ```
@@
 
- - I'll place points in the Khulna and Chittagong regions, since I can't find any other information on mud crab aquaculture locations in Bangladesh.
-
- - Khulna: 21.876081791221054, 89.49499697244659
- - Chittagong: 22.325919306644522, 91.76441856678511
-
 Source: 
@@
 
+ - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.
+
 ```{r}
-
-farms_bgd <- data.frame(lat = c(21.876081791221054, 22.325670145257305),
-                        lon = c(89.49499697244659, 91.76091935028879)) %>%
-  mutate(iso3c = "BGD") %>%
-  mutate(data_quality = 0.333)
-
-write_csv(farms_bgd, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_bgd.csv"))
-
-## visualize it 
-farms_bgd <-  st_as_sf(farms_bgd, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_bgd)
+bgd_gf <- data.frame(iso3c = "BGD", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+write_csv(bgd_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_bgd.csv")) 
 ```
@@
 
- - I'll place points in Ayeyarwaddy region and Rakhine state.
- - Ayeyarwaddy: 15.930407995930784, 94.76647475697742
- - Rakhine: 18.615093163569437, 94.24290607527016
-
 Source:
@@
 
+ - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.
+
 ```{r}
-
-farms_mmr <- data.frame(lat = c(15.930407995930784, 18.615093163569437),
-                        lon = c(94.76647475697742, 94.24290607527016)) %>%
-  mutate(iso3c = "MMR") %>%
-  mutate(data_quality = 0.333)
-
-write_csv(farms_mmr, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_mmr.csv"))
-
-## visualize it 
-farms_mmr <-  st_as_sf(farms_mmr, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_mmr)
+mmr_gf <- data.frame(iso3c = "MMR", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+write_csv(mmr_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_mmr.csv")) 
 ```
@@
 
- - Table on page 20: This is a table from 2004, but it will have to do.
-It also has production estimates, which is nice.
-I will randomly place a point along the coast in each province, and allocate the production accordingly in step 3..
-  - NOTE: for the production, we are assuming that not reported within a province == 0 production, due to the lack of data.
-
-  - Quang Ninh: prod = 0: 21.186050529545593, 107.60858937642442
-  - Hai Phong: prod = 1650: 20.840947248646557, 106.77685003845498
-  - Thai Binh: prod = 0: 20.454148639095266, 106.59728856581118
-  - Nam Dinh: prod = 0: 20.146554460540862, 106.3298019452741
-  - Ninh Binh: prod = 1005: 19.955496263213185, 106.03097468374126
-  - Thanh Hoa: prod = 970: 19.726817666482322, 105.87661730467457
-  - Nghe An: prod = 0: 18.982876968029743, 105.6165097440173
-  - Ha Tinh: prod = 200: 18.456817613512555, 105.92726656633255
-  - Quang Binh: prod = 110: 17.56001328746647, 106.58039999954293
-  - Quang Tri: prod = 20: 16.905826522213328, 107.19194145855845
-  - TT Hue: prod = 82: 16.495115996149718, 107.74891583338649
-  - Da Nang: prod = 0: 16.167986126005765, 108.15075180169012
-  - Quang Nam: prod = 135: 15.699026568754403, 108.48016289264334
-  - Quang Ngai: prod = 0: 15.010595152983287, 108.92174225624275
-  - Binh Dinh: prod = 130: 14.17668770026659, 109.19617116389627
-  - Phu Yen: prod = 0: 13.335760529041393, 109.29183511586322
-  - Khanh Hoa: prod = 0: 12.299111935360338, 109.23699322130719
-  - Ninh Thuân: prod = 5: 11.62183927318579, 109.1546891359726
-  - Binh Thuân: prod = 0: 10.830102342204183, 108.03702110643216
-  - Long An: prod = 250: 10.510731358280973, 106.7310999868549
-  - Tien Giang: prod = 0: 10.30006571666483, 106.78122716883196
-  - Ben Tre: prod = 637: 10.037866832581582, 106.69637036338817
-  - Tra Vinh: prod = 1196: 9.592223563185232, 106.54126727713718
-  - Soc Trang: prod = 0: 9.389580381208823, 106.1857446280396
-  - Bac Lieu: prod = 3466: 9.147921315425062, 105.59613926925006
-  - Ca Mau: prod = 0: 8.674166818318303, 105.12379673906345
-  - Kien Giang: prod = 170: 10.087872204898957, 104.88743812284027
-  - Can Tho: prod = 0: 10.055231, 105.789267
+ - Table on page 20: This is a table from 2004, but it will have to do. It also has production estimates, which is nice.
 
@@
 
+ - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.
+
 ```{r}
-
-farms_vnm <- data.frame(lat = c(21.186050529545593, 20.840947248646557, 20.454148639095266, 20.146554460540862, 19.955496263213185, 19.726817666482322, 18.982876968029743, 18.456817613512555, 17.56001328746647, 16.905826522213328, 16.495115996149718, 16.167986126005765, 15.699026568754403, 15.010595152983287, 14.17668770026659, 13.335760529041393, 12.299111935360338, 11.62183927318579, 10.830102342204183, 10.510731358280973, 10.30006571666483, 10.037866832581582, 9.592223563185232, 9.389580381208823, 9.147921315425062, 8.674166818318303, 10.087872204898957, 10.055819944690162),
-                        lon = c(107.60858937642442, 106.77685003845498, 106.59728856581118, 106.3298019452741, 106.03097468374126, 105.87661730467457, 105.6165097440173, 105.92726656633255, 106.58039999954293, 107.19194145855845, 107.74891583338649, 108.15075180169012, 108.48016289264334, 108.92174225624275, 109.19617116389627, 109.29183511586322, 109.23699322130719, 109.1546891359726, 108.03702110643216, 106.7310999868549, 106.78122716883196, 106.69637036338817, 106.54126727713718, 106.1857446280396, 105.59613926925006, 105.12379673906345,  104.88743812284027, 105.79073953273914),
-                        prod = c(0, 1650, 0, 0, 1005, 970, 0, 200, 110, 20, 82, 0, 135, 0, 130, 0, 0, 5, 0, 250, 0, 637, 1196, 0, 3466, 0, 170, 0), sub_rgn = c("Quang Ninh", "Hai Phong", "Thai Binh", "Nam Dinh", "Ninh Binh", "Thanh Hoa", "Nghe An", "Ha Tinh", "Quang Binh", "Quang Tri", "TT Hue", "Da Nang", "Quang Nam", "Quang Ngai", "Binh Dinh", "Phu Yen", "Khanh Hoa", "Ninh Thuân", "Binh Thuân", "Long An", "Tien Giang", "Ben Tre", "Tra Vinh", "Soc Trang", "Bac Lieu", "Ca Mau", "Kien Giang", "Can Tho")) %>%
-  mutate(iso3c = "VNM") %>%
-  mutate(data_quality = 0.333)
-
-write_csv(farms_vnm, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_vnm.csv"))
-
-## visualize it 
-farms_vnm_map <-  st_as_sf(farms_vnm, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_vnm_map)
+vnm_gf <- data.frame(iso3c = "VNM", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+write_csv(vnm_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_vnm.csv")) 
 ```
@@
 
- - I've saved the table in Aurora as a .csv.
-
- - I'll place a point in each location listed in the table, and use the production estimates to allocate the FAO production equally (although the number is almost the same as reported in the FAO, off by 3 tonnes).
-
 Consider using this data for future iterations... 
@@
 
-```{r}
-phl_mudcrab_prod <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/Philippines/phl_mudcrab_production.csv")) %>%
-  dplyr::select(-X6) %>%
-  mutate(`2017` = as.numeric(`2017`), 
-         `2018` = as.numeric(`2018`),
-         `2019` = as.numeric(`2019`)) %>%
-  pivot_longer(cols = c(`2017`, `2018`, `2019`), names_to = "year", values_to = "prod") %>%
-  dplyr::filter(!is.na(prod), 
-                year == 2017)
-
-## now we need to find coordinates for each province. I will randomly select a lat lon point along the coast of each province:
-
-provinces <- data.frame(Province = unique(sort(phl_mudcrab_prod$Province))) %>%
-  mutate(lat_lon = c("9.190611500208238, 125.52994229122065", "11.737731148020183, 122.36341263788152", "13.21836252920181, 123.77011641931539", "11.096612509189843, 122.04466274447995", "14.588280500720717, 120.39232212075018", "10.062398891617871, 124.08857333922121", "14.759345796261423, 120.79195178365572", "14.278379190276917, 122.80695157663077", "13.728018225223346, 123.21602051808212", "11.544441602769396, 122.87251489793287", "13.600373850277089, 124.08856214435265", "7.226273453773761, 125.8615542691359", "7.29064081849023, 125.70838297490391", "6.8067269257546394, 125.38044959114181", "7.021850825639651, 126.44668668618641", "10.249781995409927, 125.64231490812028", "11.457019560196713, 125.50124809292508", "18.35920136671901, 121.62457647441146", "14.294681717859676, 120.71661934172276", "10.565159685797113, 122.51279683720878", "16.5330902343553, 120.31511351999148", "8.187575265346036, 124.12440346213432", "10.86506672011331, 124.72028684317488", "17.08773382905305, 120.43638606220428", "17.205031284221167, 120.4139227279512", "10.891325726593882, 122.7831164266059", "6.994603962157642, 123.99059538388416", "13.344206870917525, 121.82133665840661", "12.576951933159716, 123.28286940887746", "14.510536378070825, 121.08748285435844", "8.483931963597566, 123.80942490173003", "8.846965587470466, 125.16333794567215", "9.943820309588942, 122.44630440874657", "12.509837523018708, 124.65010656730024", "13.415437014491157, 121.0922973705213", "10.038412865363988, 118.7206892394855", "14.855971440318308, 120.58766325017285", "16.124387999329027, 120.09336724359946", "14.664908885542868, 121.61549543341468", "12.585717059110207, 122.27016916837972", "12.007625357698121, 124.69126813617964", "12.818661572681938, 123.83950186846029", "6.373081834977807, 124.08215994073517", "9.555721530351239, 125.78630860627861", "9.013346905513, 126.23742298508941", "6.9053988560744335, 122.0691745144182", "8.18224915422801, 122.95491554623727", "7.81172076996685, 123.42354992829671", "7.703880319874889, 122.52615049321432", "15.272079732639275, 120.00987788280406")) %>%
-  separate(lat_lon, into = c("lat", "lon"), sep = ",")
-
-## Now join together with our larger dataset
-
-phl_lat_lon <- phl_mudcrab_prod %>%
-  left_join(provinces, by = "Province") %>%
-  dplyr::select(lat, lon, prod, "sub_rgn" = "Province") %>%
-  mutate(iso3c = "PHL") %>%
-  mutate(data_quality = 0.333)
-
-write_csv(phl_lat_lon, here("marine/crustaceans/crustacean_farms/data/crustacean_sites/farms_phl.csv"))
-
-## visualize it 
-farms_phl_map <-  st_as_sf(phl_lat_lon, coords = c("lon", "lat"), 
-                 crs = crs(gadm_latlon), agr = "constant")
-
-mapview(farms_phl_map)
-```
-
-# Join cell count dataframes
+ - Even though we have this decent information, it is not location or number based. Therefore this will be fully gapfilled. data_quality = 1.
 
 ```{r}
-farm_files <- list.files(here::here("marine/crustaceans/crustacean_farms/data/crustacean_sites"), full=TRUE)
-all_farms = plyr::ldply(farm_files, read_csv)
-
-all_farms_sf <- st_as_sf(all_farms, coords = c("lon", "lat"), 
-                         crs = crs(gadm_latlon), agr = "constant")
-
-mapview(all_farms_sf)
-
-write.csv(all_farms, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon_data_quality.csv"), row.names = FALSE)
-
-all_farms_1 <- all_farms %>%
-  dplyr::select(-data_quality)
-
-write.csv(all_farms_1, here::here("marine/crustaceans/crustacean_farms/data/global_crustacean_farm_lat_lon.csv"), row.names = FALSE)
+phl_gf <- data.frame(iso3c = "PHL", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+write_csv(phl_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_phl.csv")) 
 ```

### 2021-05-11 marine/salmon/salmon_farms/STEP1_fao_salmon_production.Rmd
made the figures!

--- 2021-02-04 marine/salmon/salmon_farm/STEP1_fao_salmon_production.Rmd
@@
 sum(explore$percent) # 100.01
+
+unique(explore$country) # - 16 countries 
 ```
+
+```{r}
+## write out bivalve taxa and production for Juliette
+fao_salmon_taxa_prod <- fao %>%
+  filter(species %in% salmon_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_salmon_taxa_prod$value) # 2754210 - adds 458 tonnes
+
+unique(fao_salmon_taxa_prod$country) # 16 countries 
+```

### 2021-05-11 analysis/R/comp_farms_production.R

@@ -1,0 +1,102 @@
+
+
+comp_farms_production <- function(species_type){
+# browser()
+# species_type <- "finfish"
+  
+if(species_type == "finfish"){
+  farm_files <- list.files(here("marine", sprintf('marine_fish_general/%s_farms/data/known_farm_sites_2_4_5', species_type)), full = TRUE)
+  
+  all_known_farms = plyr::ldply(farm_files, read_csv) %>%
+    mutate(type = "marine_fish_general")
+  
+  number_files <- list.files(here("marine", sprintf("marine_fish_general/%s_farms/data/known_number_farms_3", species_type)), full=TRUE)
+  
+  all_number_3 = plyr::ldply(number_files, read_csv)
+  
+  subset_farms_files <- list.files(here("marine", sprintf("marine_fish_general/%s_farms/data/subset_known_add_points_4", species_type)), full=TRUE)
+  
+  subset_add_4 = plyr::ldply(subset_farms_files, read_csv)
+  
+  # Read in relevant production data
+  
+  species_tonnes <- read_csv(here::here("marine", sprintf("marine_fish_general/%s_farms/data/fao_mariculture_%s.csv", species_type, species_type))) %>%
+    mutate(type = "marine_fish_general") %>%
+    filter(year == 2017)
+  
+  
+}else{
+  
+farm_files <- list.files(here("marine", sprintf('%s/%s_farms/data/known_farm_sites_2_4_5', species_type, species_type)), full = TRUE)
+
+all_known_farms = plyr::ldply(farm_files, read_csv) %>%
+  mutate(type = species_type)
+
+number_files <- list.files(here("marine", sprintf("%s/%s_farms/data/known_number_farms_3", species_type, species_type)), full=TRUE)
+
+all_number_3 = plyr::ldply(number_files, read_csv)
+
+subset_farms_files <- list.files(here("marine", sprintf("%s/%s_farms/data/subset_known_add_points_4", species_type, species_type)), full=TRUE)
+
+subset_add_4 = plyr::ldply(subset_farms_files, read_csv)
+
+# Read in relevant production data
+
+species_tonnes <- read_csv(here::here("marine", sprintf("%s/%s_farms/data/fao_mariculture_%s.csv", species_type, species_type, species_type))) %>%
+  mutate(type = species_type) %>%
+  filter(year == 2017)
+
+
+}
+
+
+
[…]

### 2021-05-18 analysis/paper_figs.Rmd
finalized figures

@@
 library(ggspatial)
+library(ggplot2)
+library(patchwork)
 
@@
 gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
-plot(gadm_latlon)
+# plot(gadm_latlon)
 
@@
 ```{r}
-all_farms_sf <- read_csv("../all_marine_aquaculture_farms_sources.csv") %>%
+all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources.csv") %>%
     st_as_sf(., 
@@
 
+test <- all_farms_sf %>%
+  filter(country == "United States of America")
+mapview(test) ## some being placed around great lakes... need to fix that
+
+fao_data <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv") %>%
+  group_by(country) %>%
+  summarise(prod = sum(total_tonnes))
 ```
@@
 
-all_farms <- read_csv("../all_marine_aquaculture_farms_sources.csv")
+all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
 
@@
 
+## Make the global map (Figure 1)
 ```{r}
@@
         legend.title=element_blank()) +
-  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9) )) +
+  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
+                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
     #  geom_vline(xintercept = 135) + # check to make sure it lines up
@@
 total_map
+
+# guides(colour=guide_legend(nrow=30))
 
@@
 plot_y <- axis_canvas(total_map, axis = "y") +
-  geom_histogramh(data = all_farms, aes(y = Y, fill = data_type), bins = 180) +
+  geom_histogram(data = all_farms, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
  #  geom_hline(yintercept = 0) + #  check to make sure it lines up
@@
 
+```
+
+## Make finer resolution maps (Figure 2)
+```{r}
 ## zoomed maps
@@
   annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.7, alpha = 0.7) + 
+  geom_spatial_point(size = 0.5, alpha = 0.7) + 
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-  coord_sf(crs = 4326, xlim = c(-75, -72), ylim = c(-46, -44), expand = FALSE) +
-  #coord_sf(crs = 4326) + 
+  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
+  # coord_sf(crs = 4326, xlim = c(-75, -72.5), ylim = c(-46, -44), expand = FALSE) +
   theme(legend.position = "bottom", ## put legend on bottom
@@
         legend.key = element_rect(fill = NA),
+        axis.text.x = element_text(angle = 60, hjust = 1),
 panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
@@
 
-## philippines
-phl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+## China - near 
+chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 1, alpha = 0.7) + 
+  geom_spatial_point(size = 0.5, alpha = 0.7) + 
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-  coord_sf(crs = 4326, xlim = c(120.25, 122.5), ylim = c(17, 19), expand = FALSE) +
+#   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
+  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
   #coord_sf(crs = 4326) + 
@@
         axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 60, hjust = 1),
+        legend.key = element_rect(fill = NA),
+panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+  ggtitle("D")
+  #border(linetype = "longdash")
+        #panel.border = element_rect(colour = "black", fill=NA, size=5))
+chn_zoom
+
+## Ecuador - Near Guayaquil
+ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+  annotation_map_tile(type = "osm", zoomin = 0) + 
+  geom_spatial_point(size = 0.5, alpha = 0.7) + 
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
+  #coord_sf(crs = 4326) + 
+  theme(legend.position = "bottom", 
+        legend.title=element_blank(), 
+        axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 60, hjust = 1),
 panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
@@
         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-phl_zoom
+ecu_zoom
 
-(chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (phl_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+## Norway
+nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+  annotation_map_tile(type = "osm", zoomin = 0) + 
+  geom_spatial_point(size = 0.5, alpha = 0.7) + 
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
+    coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
+  theme(legend.position = "bottom", 
+        legend.title=element_blank(), 
+        axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        legend.key = element_rect(fill = NA),
+        axis.text.x = element_text(angle = 60, hjust = 1),
+panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+  ggtitle("C")
+  #border(linetype = "longdash")
+        #panel.border = element_rect(colour = "black", fill=NA, size=5))
+nor_zoom
+
+(chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+
+plot1 <- (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "none") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none"))
+
+plot1 
+ggsave("analysis/figs/chl_ecu_zoom.jpg")
+
+plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+
+plot2
+ggsave("analysis/figs/nor_chn_zoom.jpg")
+
+## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final.jpg"
 
@@
 
-ARCHIVE: Other ways of trying
+ARCHIVE: Other ways of trying to visualize
 ```{r}
+
+## philippines
+# phl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+#   annotation_map_tile(type = "osm", zoomin = 0) + 
+#   geom_spatial_point(size = 1, alpha = 0.7) + 
+#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+#   coord_sf(crs = 4326, xlim = c(120.25, 122.5), ylim = c(17, 19), expand = FALSE) +
+#   #coord_sf(crs = 4326) + 
+#   theme(legend.position = "bottom", 
+#         legend.title=element_blank(), 
+#         axis.title.x = element_blank(), 
+#         axis.title.y = element_blank(),
+# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+#   ggtitle("B")
+#   #border(linetype = "longdash")
+#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
+# phl_zoom
+
+## California - bay area 
+# cal_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+#   annotation_map_tile(type = "osm", zoomin = 0) + 
+#   geom_spatial_point(size = 1, alpha = 0.7) + 
+#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+#   coord_sf(crs = 4326, xlim = c(-123, -121), ylim = c(37, 39), expand = FALSE) +
+#   #coord_sf(crs = 4326) + 
+#   theme(legend.position = "bottom", 
+#         legend.title=element_blank(), 
+#         axis.title.x = element_blank(), 
+#         axis.title.y = element_blank(),
+# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+#   ggtitle("B")
+#   #border(linetype = "longdash")
+#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
+# cal_zoom
+
+## New Zealand
+# nzl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+#   annotation_map_tile(type = "osm", zoomin = 0) + 
+#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
+#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+#   # coord_sf(crs = 4326, ylim = c(-48, -34), xlim = c(165, 180), expand = FALSE) + ## all of new zealand
+#    coord_sf(crs = 4326, ylim = c(-41, -34), xlim = c(172, 180), expand = FALSE) + ## north island
+#   theme(legend.position = "bottom", 
+#         legend.title=element_blank(), 
+#         axis.title.x = element_blank(), 
+#         axis.title.y = element_blank(),
+#         axis.text.x = element_text(angle = 60, hjust = 1),
+# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+#   ggtitle("D")
+#   #border(linetype = "longdash")
+#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
+# nzl_zoom
 
@@
 ```
-
-```{r}
-## by species group, colored by estimation type
-ggplot(data = world) +
-  geom_sf() + 
-  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.3) +
-  facet_wrap(~species)
-
-## by estimation type
-ggplot(data = world) +
-  geom_sf() + 
-  geom_point(data = all_farms, aes(x = X, y = Y), size = 0.3) +
-  facet_wrap(~data_type)
-
-## by estimation type, colored by species 
-ggplot(data = world) +
-  geom_sf() + 
-  geom_point(data = all_farms, aes(x = X, y = Y, col = species), size = 0.3) +
-  facet_wrap(~data_type)
-```

### 2021-05-18 marine/STEP1_species_groups/STEP1_species_groups.Rmd
finalized figures

--- 2021-04-23 marine/STEP1_species_groups/STEP1_species_groups.Rmd
@@
   summarise(tonnes = sum(value)) %>%
-  ungroup() %>%
+  ungroup() # %>%
   # dplyr::filter(tonnes >= 500) %>%
-  group_by(country, aq_group, year) %>%
-  summarise(total_tonnes = sum(tonnes)) %>%
-  arrange(aq_group)
+ #  group_by(country, year) %>%
+ #  summarise(total_tonnes = sum(tonnes))# %>%
+ # # arrange(aq_group)
 
@@
 
+## Take a look at the data 
 test <- fao_1 %>%
   dplyr::filter(aq_group == "bivalves")
-sum(test$total_tonnes) # 17435623
+sum(test$tonnes) # 17435623
 
@@
 sum(test$total_tonnes) # 5094133
+
+aq_groups <- read.csv("marine/STEP1_species_groups/int/marine_groups.csv")
+
+fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
+  filter(environment %in% c("Marine", "Brackishwater")) %>%
+  left_join(aq_groups) %>%
+  dplyr::filter(year == 2017,
+                !is.na(value),
+                !is.na(aq_group)) %>%
+  # dplyr::filter(value >= 500) %>%
+  group_by(aq_group, country, species, year) %>%
+  summarise(tonnes = sum(value)) %>%
+  ungroup()  %>%
+  # dplyr::filter(tonnes >= 500) %>%
+  group_by(country, year) %>%
+  summarise(total_tonnes = sum(tonnes))# %>%
+ # arrange(aq_group)
+sum(fao_1$total_tonnes) # 29662247 reported
+
+fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
+  filter(environment %in% c("Marine", "Brackishwater")) %>%
+  left_join(aq_groups) %>%
+  dplyr::filter(year == 2017,
+                !is.na(value),
+                !is.na(aq_group)) %>%
+   dplyr::filter(value < 500) %>%
+  group_by(aq_group, country, species, year) %>%
+  summarise(tonnes = sum(value)) %>%
+  ungroup()  %>%
+  # dplyr::filter(tonnes >= 500) %>%
+  group_by(country, year) %>%
+  summarise(total_tonnes = sum(tonnes))# %>%
+ # arrange(aq_group)
+
+sum(fao_1$total_tonnes) # 38731.97
+
+38731.97/29662247 # we exclude around 0.1% of marine aquaculture
 ```

### 2021-05-20 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
checked the median global tonnes/farm

@@
 avg_global_bivalve_tonnes_per_farm # 283.4135
+
+med_global_bivalve_tonnes_per_farm <- median(tonnes_per_farm$tonnes_per_farm)
+med_global_bivalve_tonnes_per_farm # 134.3808
 ```

### 2021-05-20 marine/marine_fish_general/finfish_farms/STEP3_gapfill_finfish.Rmd
checked the median global tonnes/farm

@@
 avg_global_marine_fish_general_tonnes_per_farm # 865.6905
+
+med_global_marine_fish_general_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
+med_global_marine_fish_general_tonnes_per_farm # 172.4093
 ```

### 2021-05-20 marine/salmon/salmon_farms/STEP3_gapfill_salmon.Rmd
made the figures!
checked the median global tonnes/farm

--- 2021-03-23 marine/salmon/salmon_farm/STEP3_gapfill_salmon.Rmd
@@
 
-farm_files <- list.files(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5"), full=TRUE)
+farm_files <- list.files(here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5"), full=TRUE)
 all_known_farms = plyr::ldply(farm_files, read_csv) %>%
@@
 
-number_files <- list.files(here("marine/salmon/salmon_farm/data/known_number_farms_3"), full=TRUE)
+number_files <- list.files(here("marine/salmon/salmon_farms/data/known_number_farms_3"), full=TRUE)
 all_number_3 = plyr::ldply(number_files, read_csv)
 
-subset_farms_files <- list.files(here("marine/salmon/salmon_farm/data/subset_known_add_points_4"), full=TRUE)
+subset_farms_files <- list.files(here("marine/salmon/salmon_farms/data/subset_known_add_points_4"), full=TRUE)
 subset_add_4 = plyr::ldply(subset_farms_files, read_csv)
 
-no_info_files <- list.files(here("marine/salmon/salmon_farm/data/no_info_1"), full=TRUE)
+no_info_files <- list.files(here("marine/salmon/salmon_farms/data/no_info_1"), full=TRUE)
 no_info_1 = plyr::ldply(no_info_files, read_csv)
@@
 ```{r}
-salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
+salmon_tonnes <- read_csv(here::here("marine/salmon/salmon_farms/data/fao_mariculture_salmon.csv")) %>%
   mutate(type = "salmon") %>%
@@
 avg_global_salmon_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
-avg_global_salmon_tonnes_per_farm # 930.3976
+avg_global_salmon_tonnes_per_farm # 927.156
+
+med_global_salmon_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
+med_global_salmon_tonnes_per_farm # 520.5484
 ```

### 2021-05-20 marine/shrimp/shrimp_farms/STEP3_gapfill_shrimp.Rmd
fixed some errors with greece (finfish), australia (bivalve), and belize (shrimp)
checked the median global tonnes/farm

@@
 avg_global_shrimp_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
-avg_global_shrimp_tonnes_per_farm # 337.7357
+avg_global_shrimp_tonnes_per_farm # 336.5783
+
+med_global_shrimp_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
+med_global_shrimp_tonnes_per_farm # 174.15
 ```

### 2021-05-20 marine/tuna/tuna_farms/STEP3_gapfill_tuna.Rmd
checked the median global tonnes/farm

@@
 avg_global_tuna_tonnes_per_farm # 277.4158
+
+med_global_tuna_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
+med_global_tuna_tonnes_per_farm # 172.3696
 ```

### 2021-05-21 marine/STEP1_species_groups/STEP1_species_groups.Rmd
did some checking for paper

@@
 
+test <- fao %>%
+  filter(year == 2017) %>%
+  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
+  mutate(environment2 = ifelse(Taxon_code == "AL", "seaweed", environment)) %>%
+  mutate(environment = ifelse(is.na(environment2), environment, environment2)) %>%
+  group_by(environment, year) %>%
+  summarise(prod = sum(value, na.rm = TRUE)) %>%
+  ungroup() %>%
+  mutate(total = sum(prod)) %>%
+  mutate(pct = prod/total)
 ```
@@
                 species != "Jellyfishes nei") ## delete freshwater, catfish species, tilapia, river species, seaweeds, jellyfish..
+
 ```

### 2021-05-27 workflow/place_unknown_farms.R
may 26th rerun with land mask

@@ -18,13 +18,19 @@ eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
 coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
 
 
+inverted_land <- land_mask
+inverted_land[is.na(inverted_land[])] <- .5
+inverted_land[inverted_land[]==1] <- NA
+inverted_land[inverted_land[]==.5] <- 1
+
 blank_raster <- food_raster
 blank_raster[] <- 1
 
 the_crs <- crs(fake_raster, asText = TRUE)
 
 ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
-  st_transform(the_crs)
+  st_transform(the_crs) #%>% 
+  #filter(HARB_SIZE_ != "L")
 
 # consider removing "L" HARB_SIZE_ points
 
@@ -54,6 +60,11 @@ rclmat <- matrix(m, ncol=3, byrow=TRUE)
 arctic_raster <- reclassify(arctic_raster, c(66,Inf, NA, 0,66,1))
 
 arctic_fixed <- resample(arctic_raster, blank_raster, method = "ngb")
+
+arctic_fixed <- inverted_land + arctic_fixed
+arctic_fixed[arctic_fixed[]==2] <- 1
+
+## add land mask
 
 for (i in 1:length(unique(need_national_allocation$iso3c))) {
   
@@ -122,8 +133,8 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
   
   dis_to_port_rast <- distanceFromPoints(this_raster_area, these_ports)
   port_test_rast <- dis_to_port_rast
-  port_test_rast[port_test_rast >35000 ] <- NA
-  suitability_rast <- port_test_rast+arctic_fixed
+  port_test_rast[port_test_rast >35000 ] <- NA # acceptable distance to port
+  suitability_rast <- port_test_rast+arctic_fixed # add in land mask
   
 
   this_coast_meters <- st_transform(this_simplified_coast, crs = "+proj=moll") %>% ## transform to a crs that can buffer in meters 
@@ -150,8 +161,9 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
       type = this_type_vector
     )
   
-  if (nrow(this_farm_points) != the_farm_number) stop
[…]

### 2021-05-27 workflow/place_unknown_farms.R
adding corrected script

@@ -149,7 +149,8 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
     st_union()%>% 
     sf::st_as_sf()
   
-  this_suitable_coast <- st_intersection(this_coast_meters, this_cell_polygons) %>% 
+  this_suitable_coast <- st_intersection(this_coast_meters, this_cell_polygons) %>%
+    st_collection_extract("LINESTRING") %>% 
     as_Spatial()
   
   # regularly sample points along line
@@ -165,7 +166,7 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
   
   #UNCOMMENT WHEN SAVING! 
   write_rds(this_farm_points, paste0("data/temp_data/temp_marine_final/temp_farms_", i, ".rds"))
-  print(paste0(this_iso3, " has been saved"))
+  print(paste0(i, " - ",this_iso3, " has been saved"))
   
 }
 
@@ -204,7 +205,7 @@ testing %>%
   right_join(need_national_allocation)
 
 
-write_rds(all_farms, "/data/all_modeled_marine_farms.rds")
+write_rds(all_farms, "data/all_modeled_marine_farms.rds")
 
 
 

### 2021-05-27 analysis/match_data_sources.Rmd
updated figs and stats with newly run farms

@@
 
-all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
+all_farms <- readRDS("data/all_modeled_marine_farms.rds") %>%
   left_join(all_farms_to_place) %>%
-  mutate(source = "modeled") %>%
-  mutate(estimated = ifelse(iso3c == "IND" & type == "bivalve", 0, estimated)) %>% # fix india mistake
-  rbind(data %>% mutate(source = "real", estimated = 0)) %>%
     mutate(data_type = case_when(
@@
   ))
+
 summary(all_farms)
+
+test <- all_farms %>%
+  st_drop_geometry() %>%
+  group_by(data_type) %>% 
+  summarise(n()) ## perfect!!
+
 ```
@@
 
-# check <- USA_bivalve_fix %>%
+# check <- USA_salmon_fix %>%
 #   st_drop_geometry() %>%
@@
 unique(all_farms_sources_final$data_year)
+unique(sort(all_farms_sources$country))
+unique(sort(all_farms_sources$iso3c)) ## 73 countries - perfect!
 

### 2021-05-27 analysis/paper_figs.Rmd
did some checking for paper
updated figs and stats with newly run farms

@@
   filter(country == "United States of America")
-mapview(test) ## some being placed around great lakes... need to fix that
+mapview(test)
+
+test <- all_farms_sf %>%
+  filter(iso3c == "HRV")
+mapview(test) ## one weird MFG from ASC
+
+test <- all_farms_sf %>%
+  filter(iso3c == "TUR")
+mapview(test) ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...
 
@@
 
+## Radial bar chart of estimation type per country
+
+```{r}
+library(tidyverse)
+library(viridis)
+library(hrbrthemes)
+library(RColorBrewer)
+library(colorspace)
+
+rank_rgn <- all_farms %>%
+  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
+  group_by(country) %>%
+  summarise(num_farms_total = n()) %>%
+  ungroup() %>%
+  arrange(num_farms_total)
+
+## Stuff for both plots
+# i think that this would look better with each stressor having its own color that is paired with ocean/land
+# 
+# pick 4 distinct colors and then create a pair with one being more brown or green and the other being more blue
+
+source_name <- data.frame(source = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
+
+type_1 <- "forestgreen"
+type_1 <- lighten(type_1, amount = -0.05)
+type_2 <- "orange1"
+type_2 <- lighten(type_2, amount = -0.05)
+type_3 <- "red3"
+type_3 <- lighten(type_3, amount = -0.05)
+
+gc_palette <- c(type_1, type_2, type_3)
+scales::show_col(gc_palette, n = 3)
+
+pal_df <- as_tibble(gc_palette) %>% 
+  rename(fill_value = value) %>% 
+  mutate(source = case_when(fill_value == type_1 ~ "known location",
+                            fill_value == type_2 ~ "modeled location, known number of farms",
+                            fill_value == type_3 ~ "modeled location, estimated number of farms"))
+
+## circle plot
+
+cutoff_value <-  1000
+
+by_country <- all_farms %>%
+  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
+  group_by(country, data_type) %>%
+  summarise(num_farms = n()) %>%
+  ungroup() %>%
+  group_by(country) %>%
+  mutate(num_farms_total = sum(num_farms)) %>%
+  ungroup() %>%
+  arrange(num_farms_total) %>%
+  filter(num_farms_total < cutoff_value)
+
+##grab the highest country to highlight red and id where the circle ends and then side bar chart begins
+highest_country <- by_country[dim(by_country)[1], "country"]
+farms_highest_country <- filter(by_country, country %in% highest_country$country) #used below
+
+# adjust the rank_rgn-adjust dataframe to match above
+rank_rgn_adj <- rank_rgn %>%
+  filter(country %in% by_country$country)
+
+# add empty space to create space in the circleplot for axes
+ empty_bar <- 5
+ to_add <- data.frame(matrix(NA, empty_bar, ncol(rank_rgn_adj)) )
+ colnames(to_add) = colnames(rank_rgn_adj)
+ to_add$country <- as.character(1:empty_bar)
+ rank_rgn_adj  <- rbind(to_add, rank_rgn_adj)
+
+ # some code to orient the country labels
+sequence_length = length(unique(rank_rgn_adj$country))
+first_sequence = c(1:(sequence_length%/%2)) 
+second_sequence = c((sequence_length%/%2+1):sequence_length) 
+first_angles = c(90 - 180/length(first_sequence) * first_sequence)
+second_angles = c(-90 - 180/length(second_sequence) * second_sequence)
+rank_rgn_adj$angle <- c(first_angles, second_angles)
+rank_rgn_adj$hjust <- c(rep(0, length(first_sequence)), 
+                    rep(1, length(second_sequence)))
+
+# color for region labels
+rank_rgn_adj <- rank_rgn_adj %>%
+  mutate(country = factor(country, unique(country))) %>%
+  mutate(color = "black") %>%
+  mutate(color = ifelse(is.na(num_farms_total), "white", color)) %>%
+  mutate(color = ifelse(country %in% highest_country$country, "red", color))
+
+## make the plot
+
+circle_theme <- theme(axis.line=element_blank(),
+                      axis.text.y=element_blank(),
+                      axis.ticks=element_blank(),
+                      axis.title.x=element_blank(),
+                      axis.title.y=element_blank(),
+                      legend.position="none",
+                      panel.background=element_blank(),
+                      panel.border=element_blank(),
+                      panel.grid.major=element_blank(),
+                      panel.grid.minor=element_blank(),
+                      plot.background=element_blank(),
+                      axis.text.x = element_blank())
+
+color_order <- c(type_1, type_2, type_3)
+
+pressures_adj_circle_plot <- by_country %>% 
+  mutate(prop_of_global_stacked = abs(num_farms)) %>% 
+  left_join(pal_df, by = c("data_type" = "source")) %>% 
+  mutate(fill_value = factor(fill_value, levels = color_order))
+
+ ggplot(data=pressures_adj_circle_plot, aes(x=country, y=prop_of_global_stacked, fill = fill_value)) +
+
+  geom_bar(stat="identity") +
+
+  # ## this adjust the inner circle size (ymin) and outer circle size (ymax), which can be expanded to include names
+   geom_errorbar(aes(
+       x     = 1,
+        ymin = -0.01,   # ymin  = -0.03, this is for when ocean bars stack inwards -0.01 for when not
+       ymax  = 0.035),
+       alpha = 0) +
+      # Country name text placement
+     geom_text(
+       data = rank_rgn_adj,
+       aes(x     = country,
+           y     = max(by_country$num_farms_total, na.rm=TRUE),
+           label = country,
+           angle = angle,
+           hjust = hjust),
+       inherit.aes = FALSE,
+       fontface = "bold",
+       alpha = 0.9,
+       size = 4,
+       color = rank_rgn_adj$color) +
+    # 
+   # georegion names
+    # geom_text(
+    #   data=rgn_shift,
+    #   aes(y = 0.02, x = name_x, label = georegion),
+    #   # aes(x=name_x,
+    #   #     y=name_y,
+    #   #     label=georegion),
+    #   inherit.aes=FALSE, size=7) +
+  #  
+  # # # Scale bar circles
+  # ## This adds the 0 line
+      geom_segment(
+        x = 0, 
+         y = 0, 
+         xend = dim(rank_rgn_adj)[1]+1, 
+         yend = 0, 
+         fill = NULL,
+        alpha = 1, color = "white", size = 0.1) + #color = "black for internal
+  #    
+  #  # Scale bar annotation, this adds the y-axis numbers
+      annotate("text",
+        x     = c(3, 3, 3),
+        y     = c(0, 0.0175, 0.035),
+        label = c(0, 0.0175, 0.035),
+        color = "darkgray", angle = -4, size = 4) +
+  #     
+  scale_color_identity() +
+   scale_fill_identity() +
+   # scale_fill_manual(values= rev(myPalette), c("Land: Disturbance", "Land: GHG", "Land: Water", "Land: Nutrient",
+   #                                    "Ocean: Disturbance", "Ocean: GHG", "Ocean: Water", "Ocean: Nutrient")) +
+  coord_polar() +
+ circle_theme
+
+```
+
 ARCHIVE: Other ways of trying to visualize
@@
 ```
+
+```{r}
+
+test_data <- all_farms %>%
+  filter(data_type != "known location")
+
+## create first plot
+total_map <- ggplot(data = world) +
+  geom_sf(fill = "white", lwd = 0.1) + 
+  geom_point(data = test_data, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
+#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
+  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
+  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
+  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
+  theme_bw() + 
+  theme(axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+        legend.position = "bottom", 
+        legend.title=element_blank()) +
+  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
+    #  geom_vline(xintercept = 135) + # check to make sure it lines up
+  #geom_hline(yintercept = 0) # check to make sure it lines up
+
+total_map
+
+ggsave("analysis/figs/map_fig_test.jpg")
+
+```

### 2021-05-27 analysis/paper_stats.Rmd
updated figs and stats with newly run farms

--- 2021-04-27 analysis/paper_stats.Rmd
@@
 library(janitor)
+library(countrycode)
 
@@
 
-# Global regions
+# Read in farms data
 
@@
 
-# this file includes ocean regions:
-gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
+all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
 
-gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
-plot(gadm_latlon)
+all_farms_sf <- all_farms %>%
+  st_as_sf(coords =c("X", "Y"))
 
-gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
-  mutate(reg_id = as.numeric(reg_id))
-```
-
-# Read in farms data and convert to sf
-
-```{r}
-all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources.csv") %>%
-    st_as_sf(., 
-           coords = c("X", "Y"),
-           crs = crs(food_raster), 
-           agr = "constant")
-
-all_farms <- all_farms_sf %>%
-  st_drop_geometry()
-
+# test <- all_farms_sf %>%
+#   filter(iso3c == "USA")
+# mapview(test)
 ```
@@
 
-# Chile, Norway, Peru, the United States, Canada and Ireland provided a substantial number of known locations (>1000).
+# Chile, Norway, and Ireland provided a substantial number of known locations (>1000).
 top_known <- all_farms %>%
@@
   mutate(pct = n_obs/total_obs*100)
+
+## How much mariculture production was included in our assessment?
+
+fao <- read_csv("data/fao_aquaculture_clean.csv")
+mar_sp_list <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2020/gh-pages/globalprep/mar/v2020/raw/species_list.csv")
+
+fw <- fao %>%
+  dplyr::filter(environment == "Freshwater") %>%
+  group_by(species) %>%
+  summarize(total = sum(value)) %>%
+  ungroup() %>%
+  arrange(total)
+
+data.frame(fw)
+
+test <- fao %>%
+  filter(year == 2017) %>%
+  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
+  mutate(environment2 = ifelse(Taxon_code == "AL", "seaweed", environment)) %>%
+  mutate(environment = ifelse(is.na(environment2), environment, environment2)) %>%
+  group_by(environment, year) %>%
+  summarise(prod = sum(value, na.rm = TRUE)) %>%
+  ungroup() %>%
+  mutate(total = sum(prod)) %>%
+  mutate(pct = prod/total)
+
+## total marine animal production is: 8090542 + 22920871 = 31011413
+
+## we include: 29623515
+prod_total <- read_csv("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/production_extracted_final.csv")
+
+sum(prod_total$total_tonnes) # 29623515
+
+29623515/31011413 # 0.9552456
 ```
 
-Check some of the data
+Countries with comprehensive farm locations 
+```{r}
+
+all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
+
+unique(sort(all_farms$country))
+
+country_spp_combos <- all_farms %>%
+  distinct(country, species)
+
+## read in each of the comprehensive locations
+
+bivalve_comp <- read_csv("marine/bivalve/bivalve_farms/output/bivalve_comp_tonnes_per_farm.csv")
+
+shrimp_comp <- read_csv("marine/shrimp/shrimp_farms/output/shrimp_comp_tonnes_per_farm.csv")
+
+salmon_comp <- read_csv("marine/salmon/salmon_farms/output/salmon_comp_tonnes_per_farm.csv")
+
+tuna_comp <- read_csv("marine/tuna/tuna_farms/output/tuna_comp_tonnes_per_farm.csv")
+
+finfish_comp <- read_csv("marine/marine_fish_general/finfish_farms/output/finfish_comp_tonnes_per_farm.csv")
+
+all_comp_farms <- rbind(finfish_comp, bivalve_comp, salmon_comp, tuna_comp, shrimp_comp) %>%
+    mutate(Species = case_when(
+      type == "salmon" ~ "Salmonids", 
+      type == "bivalve" ~ "Unfed or algae fed shellfish",
+      type == "marine_fish_general" ~ "General Marine Fish", 
+      type == "shrimp" ~ "Shrimp", 
+      type == "tuna" ~ "Tuna"
+    )) %>%
+  mutate(tonnes_per_farm = round(tonnes_per_farm, 2)) %>%
+  dplyr::select("Country" = "country", Species, "Number of farms" = "n_farms", "Tonnes of production" = "fao_tonnes_production", "Tonnes per farm" = "tonnes_per_farm") %>%
+  arrange(Country)
+
+unique(all_comp_farms$Country)
+
+write.csv(all_comp_farms, "analysis/output/all_comp_farms.csv", row.names = FALSE)
+
+comp_across_all <- all_comp_farms %>%
+  full_join(country_spp_combos, by = c("Country" = "country", "Species" = "species")) %>%
+  mutate(Country = case_when(
+    Country == "Iran" ~ "Iran (Islamic Rep. of)", 
+    Country == "Hong Kong " ~ "China, Hong Kong SAR",
+    TRUE ~ Country
+  )) %>%
+  filter(Country %in% all_comp_farms$Country) %>%
+  group_by(Country) %>%
+  summarise(n_obs = sum(`Number of farms`), 
+            n_species = n(),
+            tonnes = sum(`Tonnes of production`)) %>%
+  filter(!is.na(n_obs))
+
+sum(comp_across_all$tonnes) # account for 4328484 tonnes of production
+
+4328484/29623515 # these account for ~15% of production tonnage
+
+## these are the countries that are comprehensive across all species groups they report
+cat(comp_across_all$Country, sep = ", ")
+
+# tuna_spp <- read_csv("marine/tuna/tuna_farms/data/fao_mariculture_tuna_taxa_production.csv")
+```
+
+Score the different taxa maps for the global food paper:
+
+Score | Spatial Extent | Spatial Resolution | Temporal specificity | System specificity | System comprehensiveness
+-- | -- | -- | -- | -- | --
+5 | Represents entire spatial extent of the food system.
+| <= 5 arc minutes | Data is specific to 2017 | The data is reported to the level of our specific food type (e.g.
+cow mixed milk) | Data represents all foods within a system
+4 | Need to gapfill regions with relatively little production (e.g.
+Aland islands) | sub-national or raster with cells larger than 5-arc minutes | Data range includes 2017 and is likely to represent 2017 | Generalized to animal type, but not both rearing system or product (e.g.
+cows mixed) | Data represents majority of foods within a system
+3 | Need to gapfill countries with considerable production (e.g.
+Philippines) | National | Data range doesn't include 2017 and is likely to represent 2017.
+| Generalized to animal type, but not rearing system or product (e.g.
+cows) | Data represents half of foods within a system
+2 | Need to gapfill whole continents/georegions | Georegions | Data range includes 2017 and is unlikely to represent 2017 | Generalized to multiple animal types (e.g.
+cattle/ungulates) | Data represents minority of foods within a system
+1 | Generalized globally using site-level data.
+| Global/generalized | Data is older than 2017 and is unlikely to represent 2017 | Data is generalized across major food system (e.g.
+all reared animals) | Data represents minimum of foods within a system
+NA | Spatial extent is not relevant | Spatial resolution of the data is not relevant | Age of data isn't relevant | Data is not specific to a food system | Data is not specific to a food system
+
+**Salmonids farms map quality**
+ - Spatial extent: 4
+ - Spatial resolution: 5
+ - Temporal specificity: 4
+ - System specificity: 2
+ - System comprehensiveness: 4
+
+**Tuna farms map quality**
+ - Spatial extent: 5
+ - Spatial resolution: 5
+ - Temporal specificity: 4
+ - System specificity: 3
+ - System comprehensiveness: 5
+
+**Shrimp farms map quality**
+ - Spatial extent: 2
+ - Spatial resolution: 5
+ - Temporal specificity: 4
+ - System specificity: 2
+ - System comprehensiveness: 4
+
+**General marine fish farms map quality**
+ - Spatial extent: 2
+ - Spatial resolution: 5
+ - Temporal specificity: 4
+ - System specificity: 1
+ - System comprehensiveness: 4
+
+**Unfed or algae fed shellfish farms map quality**
+ - Spatial extent: 2
+ - Spatial resolution: 5
+ - Temporal specificity: 4
+ - System specificity: 2
+ - System comprehensiveness: 4
+
+**Other crustaceans farms map quality**
+ - Spatial extent: 1
+ - Spatial resolution: 1
+ - Temporal specificity: NA
+ - System specificity: 1
+ - System comprehensiveness: 4
+
+Some random exploring
 ```{r}

### 2021-05-27 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
rasterized production for global food

@@
 
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant")
+# data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+#   st_as_sf(., 
+#            coords = c("lon", "lat"),
+#            crs = crs(food_raster), 
+#            agr = "constant")
 
-all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
-  mutate(source = "modeled") %>% 
-  rbind(data %>% mutate(source = "real"))
+all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+
+# all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
+#   map_df(., readRDS) %>% 
+#   dplyr::rename(iso3c = iso3) %>% 
+#   dplyr::mutate(source = "modeled") %>% 
+#   rbind(data %>% mutate(source = "real"))
 
@@
 # ESP:FRA
-# ESP:MAR
-# ESP:PRT
 # HKG:CHN
-# HRV:BIH
-# HRV:MNE
-# HRV:SVN
 # IRL:GBR
-# JPN:RUS
-# KHM:VNM
-# MYS:BRN
-# MYS:THA
-# NLD:BEL
 # NLD:DEU
 # PRK:RUS
-# PRT:ESP
-# RUS:POL
-# SVN:ITA
+# SVN:HRV
 # THA:MMR
-# THA:MYS
 # TWN:CHN
 # USA:CAN
-# USA:MEX
-# VNM:KHM
 
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "ESP:MAR", "ESP", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ESP:MAR", "Spain", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "ESP:FRA", "ESP", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "HRV:BIH", "HRV", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HRV:BIH", "Croatia", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "HRV:MNE", "HRV", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HRV:MNE", "Croatia", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "HRV:SVN", "HRV", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "NLD:BEL", "NLD", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "NLD:BEL", "Netherlands", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "RUS:POL", "RUS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "RUS:POL", "Russia", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "SVN:ITA", "SVN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "SVN:ITA", "Slovenia", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
@@
   mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "USA:MEX", "USA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "USA:MEX", "United States", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0))
 
@@
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/prod_data_by_cell_iso3c.shp")
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE) ## overwrite file if already there
 

### 2021-05-27 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
rasterized production for global food

@@
 
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant") %>%
-  mutate(source = "real")
+# data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+#   st_as_sf(., 
+#            coords = c("lon", "lat"),
+#            crs = crs(food_raster), 
+#            agr = "constant") %>%
+#   mutate(source = "real")
 
-all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
- dplyr::mutate(source = "modeled") %>% 
-  #left_join(tonnage_per_farms)
-  rbind(data)
+all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+
+# all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
+#   map_df(., readRDS) %>% 
+#   rename(iso3c = iso3) %>% 
+#  dplyr::mutate(source = "modeled") %>% 
+#   #left_join(tonnage_per_farms)
+#   rbind(data)
 
@@
 # CHN:MAC
+# MMR:THA
 
@@
   mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% c("MMR:THA"), "MMR", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% c("MMR:THA"), "Myanmar", NAME_0))
 
@@
 
-fao <- read.csv(here::here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
+fao <- read.csv(here::here("marine/crustaceans/crustaceans_farms/data/fao_mariculture_crustaceans.csv")) %>%
   dplyr::filter(year == 2017) %>%

### 2021-05-27 marine/last_step_rasterize/finfish_rasterize_production.Rmd
rasterized production for global food

@@
 
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant")
-
-all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
-  mutate(source = "modeled") %>% 
-  rbind(data %>% mutate(source = "real"))
+all_farms <- readRDS("data/all_modeled_marine_farms.rds")
 
@@
 
-# ALB:MNE
 # CHN:HKG
@@
 # HKG:CHN
-# HRV:SVN
-# IDN:PNG
-# IDN:TLS
-# ISR:EGY
-# ITA:FRA
-# MYS:SGP
-# MYS:THA
+# MYS:IDN 
 # PRT:ESP
 # SGP:MYS
-# TUR:BGR
 # TUR:GRC
-# TWN:CHN
 
@@
   mutate(NAME_1 = as.character(NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% "ALB:MNE", "ALB", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ALB:MNE", "Albania", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "HRV:SVN", "HRV", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "HRV:SVN", "Croatia", NAME_0)) %>%    
-  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "ISR:EGY", "ISR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ISR:EGY", "Israel", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "ITA:FRA", "ITA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ITA:FRA", "Italy", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
+  mutate(GID_0 = ifelse(check %in% "MYS:IDN", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:IDN", "Malaysia", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "TUR:BGR", "TUR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "TUR:BGR", "Turkey", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "TUR:GRC", "TUR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0))
 
@@
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/prod_data_by_cell_iso3c.shp")
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)
 

### 2021-05-27 marine/last_step_rasterize/salmon_rasterize_production.Rmd
rasterized production for global food

--- 2021-04-05 marine/salmon/salmon_farm/STEP4_rasterize_production.Rmd
@@
 
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant")
-
-all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
-  mutate(source = "modeled") %>% 
-  #left_join(tonnage_per_farms)
-  rbind(data %>% mutate(source = "real"))
+all_farms <- readRDS("data/all_modeled_marine_farms.rds")
 
@@
 table(farms_sf$check)
+
+# CAN:USA
+# FIN:ALA
+# FIN:RUS
+# USA:CAN
 
@@
 
-fao <- read.csv(here("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv")) %>%
+fao <- read.csv(here("marine/salmon/salmon_farms/data/fao_mariculture_salmon.csv")) %>%
   dplyr::filter(year == 2017) %>%

### 2021-05-27 marine/last_step_rasterize/shrimp_rasterize_production.Rmd
rasterized production for global food

--- 2021-04-23 marine/shrimp/shrimp_farms/STEP4_rasterize_production.Rmd
@@
 # CHN:MAC
-# CRI:NIC
 # CRI:PAN
-# ECU:COL
-# GTM:HND
-# GTM:MEX
 # HND:NIC
 # HND:SLV
-# IDN:PNG
-# IDN:TLS
-# IRN:IRQ
-# MEX:GTM
+
 # MEX:USA
-# MYS:BRN
-# MYS:SGP
-# MYS:THA
-# PER:ECU
+# MMR:THA
+# MYS:IDN
+# NIC:CRI
 # SAU:KWT
-# SLV:HND
 # THA:MMR
 # THA:MYS
-# VNM:KHM
 
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "CRI:NIC", "CRI", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CRI:NIC", "Costa Rica", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "ECU:COL", "ECU", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ECU:COL", "Ecuador", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "GTM:HND", "GTM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "GTM:HND", "Guatemala", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "GTM:MEX", "GTM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "GTM:MEX", "Guatemala", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%   
-  mutate(GID_0 = ifelse(check %in% "IDN:PNG", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:PNG", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "IDN:TLS", "IDN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IDN:TLS", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "MEX:GTM", "MEX", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MEX:GTM", "Mexico", NAME_0)) %>%   
+  mutate(GID_0 = ifelse(check %in% "NIC:CRI", "NIC", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "NIC:CRI", "Nicaragua", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:THA", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:THA", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "PER:ECU", "PER", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "PER:ECU", "Peru", NAME_0)) %>% 
+  mutate(GID_0 = ifelse(check %in% "MYS:IDN", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:IDN", "Malaysia", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "SLV:HND", "SLV", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "SLV:HND", "El Salvador", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
@@
   mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0))
 

### 2021-05-27 marine/last_step_rasterize/tuna_rasterize_production.Rmd
rasterized production for global food

--- 2021-04-23 marine/tuna/tuna_farms/STEP4_rasterize_production.Rmd
@@
 
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant")
-
-all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-  map_df(., readRDS) %>% 
-  rename(iso3c = iso3) %>% 
-  mutate(source = "modeled") %>% 
-  #left_join(tonnage_per_farms)
-  rbind(data %>% mutate(source = "real"))
+all_farms <- readRDS("data/all_modeled_marine_farms.rds")
 
@@
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/prod_data_by_cell_iso3c.shp")
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)
 

### 2021-06-11 analysis/match_data_sources.Rmd
pushing latest changes to the map!

@@
     source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
-  ))
+  )) %>%
+  mutate(estimated = ifelse(is.na(estimated), 0, estimated))
 
@@
   summarise(n()) ## perfect!!
+
+test <- all_farms %>%
+  dplyr::filter(is.na(estimated))
 
@@
 ## Now save this as a csv
-st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources.csv", layer_options = "GEOMETRY=AS_XY")
+st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)
 

### 2021-06-11 analysis/paper_figs.Rmd
pushing latest changes to the map!

@@
 ```{r}
+library(dplyr)
+library(sf)
+library(raster)
+library(mapview)
+library(tidyverse)
+library(ggpubr)
+library(RColorBrewer)
+library(ggspatial)
+library(ggplot2)
+library(patchwork)
+
 ## zoomed maps
@@
 
-(chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
 

### 2021-06-11 archive/marine_mapping_OLD_v1/marine_fish_general/food_pressures/finfish_disturbance/STEP1_disturbance.Rmd
pushing latest changes to the map!

---
title: "Marine finfish disturbance"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "12/29/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in libaries and paths}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidyverse)
library(raster)
library(data.table)
library(raster)
library(rgdal)
library(here)

path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/"

food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"

food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

```

Because there are so many species of finfish included in our analysis, we will treat them all the same (i.e. same stocking density, cage volume, etc.). Although some fish likely do rear for longer than 1 year, we will assume that most are 1 year or less, and that the loss is minimal. Meaning that the production reported from the FAO is the true live weight tonnes.

Assumptions:

stocking density = 20 kg/m3 (Froelich et al. 2017)

depth = 10 m (Froelich et al. 2017)

volume = 9000 m3

##Methods

Read in the appropriate values 
```{r parameters from conversion table}

stocking_density <- 20
cage_volume <- 9000
```

###Calculate the total number of fish in the water (occupancy)
Read in production map

```{r}
production_raster <- rasterFromXYZ(read_csv(paste0(path_prep, "marine_fish_general_farm.csv")), crs = food_crs)

#plot(production_raster)
cellStats(production_raster, stat = "sum") # 3901214

```

```{r calculate finfish}
# Assume all kg are live weight 
# as live weight of finfish, in kg
finfish_live_kg  <- production_raster*1000
finfish_live_tonnes  <- production_raster

writeRaster(finfish_live_tonnes, file.path(path_prep, "finfish_occupancy/finfish_live_tonnes.tif"), format = "GTiff", overwrite = TRUE)
```

### Calculate the total area (from an aerial view) used for general finfish aquaculture

First we determine how many cages are required given cage dimensions, stocking densities, and kg living fish.

We used Gentry 2017 data to estimate 180,000 kg finfish (harvest weight) per cage.

This is based on 9000 m3 cage that we assume to be circular with a depth of 10 m.  We assume a stocking density of 20kg/m3.

```{r}

kg_per_cage <- cage_volume*stocking_density

```

Given the kg of finfish per cell we determine the number of cages needed as:

kg_finfish/180,000

We round this value up to the nearest whole number and multiply by 1.3 to include fallowing cages.

```{r}

cages <- ceiling(finfish_live_kg/kg_per_cage)

```

We the determine how much surface area the cages disturb including the inner cage area, a 5 meter buffer around the cage, and area for infrastructure.

```{r}
cage_depth_m <- 10
buffer <- 5
infrastructure <- 1.5 #50% of area to infrastructure

cage_area <- cage_volume/cage_depth_m
cage_radius <- sqrt(cage_area/pi)
cage_radius_buffer <- cage_radius + buffer
cage_area_with_buffer <- pi*cage_radius_buffer^2
cage_disturbance_m2 <- cage_area_with_buffer*infrastructure

total_disturbance_km2 <- cages * cage_disturbance_m2/1000000
total_disturbance_prop <- total_disturbance_km2/raster::area(total_disturbance_km2)
plot(total_disturbance_prop)
plot(total_disturbance_km2)

finfish_aquaculture_area_df <- as.data.frame(total_disturbance_prop, xy=TRUE) %>% 
  dplyr::rename(finfish_disturbance_prop = layer )

write_csv(finfish_aquaculture_area_df, file.path(path_prep, "marine_fish_general_disturbance_prop.csv"))

finfish_aquaculture_area_df_km2 <- as.data.frame(total_disturbance_km2, xy=TRUE) %>% 
  dplyr::rename(finfish_disturbance_km2 = layer)

write_csv(finfish_aquaculture_area_df_km2, file.path(path_prep, "marine_fish_general_disturbance_km2.csv"))

## save to datalayers folder with the correct naming conventions: 
final_layer_dist <- read_csv(file.path(path_prep, "marine_fish_general_disturbance_km2.csv"))

final_rast <- rasterFromXYZ(final_layer_dist, crs = food_crs)
crs(final_rast)
plot(final_rast)
cellStats(final_rast, "sum") # 49.87762
final_rast

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 66.1818
final_rast

writeRaster(final_rast, file.path(path_final, "marine_marine-fish-general_aquaculture_meat_disturbance.tif"), overwrite = TRUE)
```

Look at the pieces more closely
```{r}
norway <- raster::crop(total_disturbance_km2, extent(-25, 50, 50, 75))
plot(norway)
writeRaster(norway, file.path(path_prep, "finfish_occupancy/norway.tif"), overwrite=TRUE)

```

### 2021-06-11 archive/marine_mapping_OLD_v1/salmon/food_pressures/salmon_disturbance/STEP1_salmon_tonnes_to_livestock_conversion.Rmd
pushing latest changes to the map!

--- 2021-02-03 marine/salmon/food_pressures/salmon_disturbance/STEP1_salmon_tonnes_to_livestock_conversion.Rmd
@@
 ```{r wrangling production data}
-nor_prod <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>% 
+nor_prod <- read_csv(here("marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>% 
   filter(species == "Salmon") %>% 

### 2021-06-11 archive/marine_mapping_OLD_v1/salmon/food_pressures/salmon_nutrient/step1_nutrient.Rmd
pushing latest changes to the map!

---
title: "salmon_nutrient_pollution"
author: "*Compiled on `r date()` by `r Sys.info()['user']`*"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

This markdown uses models and species specific parameters from the paper *Hindcasts and Future Projections of Global Inland and Coastal Nitrogen and Phosphorus Loads Due to Finfish Aquaculture* (2013 Bouwman et al)

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

#parameters <- read_csv("data/salmon_parameters.csv") 
production <- read_csv(file.path(path_prep, "salmon_farm.csv"))
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

Salmon N/P pollution values

N: 49 kg/tonne of growth
P: 8 kg/tonne of growth

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P value
3. We report in total excess nutrients: Sum the N and P.
4. We report in tonnes, so divide by 1000. Save a total raster, a N raster, and a P raster.

```{r}

salmon_pollution <- production %>%
  dplyr::mutate(prod_growth = tonnes_production*0.95) %>%
  dplyr::mutate(prod_growth_N_poll = prod_growth*49,
                prod_growth_P_poll = prod_growth*8) %>% ## in kg pollution now
  # dplyr::mutate(PO4eq_kg = prod_growth_N_poll*0.42 + prod_growth_P_poll*3.07) %>% cut (01/14/2021)
  dplyr::mutate(total_N_P_tonnes = (prod_growth_N_poll + prod_growth_P_poll)/1000,
                N_poll_t = prod_growth_N_poll/1000,
                P_poll_t = prod_growth_P_poll/1000) %>%
  dplyr::select(x, y, total_N_P_tonnes, N_poll_t, P_poll_t)

sum(salmon_pollution$total_N_P_tonnes) # 148700.6

## save to dataprep folder with the correct naming conventions: 
write.csv(salmon_pollution, file.path(path_prep, "salmon_nutrient.csv"))

## Save total N + P layer

N_P_df <- salmon_pollution %>%
  dplyr::select(x,y,total_N_P_tonnes)

final_rast <- rasterFromXYZ(N_P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 148700.6

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 148700.6
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_final, "marine_salmon_aquaculture_meat_nutrient.tif"), overwrite = T)

## Save total N layer

N_df <- salmon_pollution %>%
  dplyr::select(x,y,N_poll_t)

final_rast <- rasterFromXYZ(N_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 127830.3

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 127830.3
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_salmon_aquaculture_meat_nutrientN.tif"), overwrite = T)

## Save total P layer

P_df <- salmon_pollution %>%
  dplyr::select(x,y,P_poll_t)

final_rast <- rasterFromXYZ(P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 20870.25

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 20870.25
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers/marine_salmon_aquaculture_meat_nutrientP.tif"), overwrite = T)
```

### 2021-06-11 archive/marine_mapping_OLD_v1/shrimp/food_pressures/shrimp_ghg/STEP1_ghg_emissions.Rmd
pushing latest changes to the map!

---
title: "Shrimp Aquaculture GHG"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

# Script Description

This markdown calculates the GHG emissions from shrimp aquaculture.

# Data information
We used [Seafood Carbon Emissions Tool data](http://seafoodco2.dal.ca/) to extract ghg emissions associated with carcass weight of shrimp from shrimp farming (we used the estimate from Whiteleg shrimp, since it was the exact same as the Giant Tiger Prawn, the only other shrimp/prawn species present in the data).

One factor that we added was aquatic N<sub>2</sub>O emissions as discussed in [Hu *et al*., 2012](https://pubs.acs.org/doi/full/10.1021/es300110x) and [MacLoid *et al*., 2019](http://www.fao.org/3/ca7130en/ca7130en.pdf).

# Methods 
 - Take midpoint of ghg low and ghg high from [seafood carbon emissions tool data](http://seafoodco2.dal.ca/):
 - Multiply by % energy (to cut out the feed emissions)
 - Add the N20 value from the MacLeod paper to the emissions intensity estimate we got for shrimp
 - Multiply emissions intensity estimate by tonnes of production in each cell

# Preamble
```{r setup, include = FALSE}
# getting packages we want
library(tidyverse)
library(here)
library(raster)
library(sf)
library(janitor)

# Raster templates
source(here("_spatial/template_raster.R"))

# File paths
raw   <- "/home/shares/food-systems/Food_footprint/_raw_data/"
prep_shrimp <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp"
prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/" 
path_final <- "/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"

# Import master_rgns xy df
master_rgns <- read_csv(here("_spatial/_output/food_rgns.csv"))
```

## Import
```{r}
## Read in farmed emissions data

farmed_emissions <- read_csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/seafood_carbon_emmisions_tool/d2020/Specie_List_-_11_24_2020,_11_39_21_AM_Farmed.csv")) %>%
  clean_names()

shrimp_production <- read_csv(file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/shrimp_farm.csv"))
```

# Wrangle

```{r}
## Filter for shrimp aquaculture
shrimp_emissions <- farmed_emissions %>%
  dplyr::filter(common_name %in% c("Giant tiger prawn", "Whiteleg shrimp"))

## grab the mean of ghg low and high (the 25th and 75th quantiles)
ghg_kgCO2_kg_fish <- mean(c(2.6, 6.1))

## now multiply by the percent of that which is energy emissions (61%)
ghg_energy_kgCO2_kg_fish <- ghg_kgCO2_kg_fish*0.61 ## 2.6535 kg CO2eq/ kg fish (live/carcass weight, ratioed)

# Adding Aquatic N2O
# From MacLeod et al. 
# "The amount of N2O per species-group was determined by multiplying the
# production by the N2O emission factor per kg of production (Hu et al., 2012), i.e.
# 1.69 gN2O-N per kg of production, or 0.791 kgCO2e/kgLW production. This equates
# to a conversion rate of N to N2O-N of 1.8 percent, which is higher that the 0.71
# percent used in Henriksson et al. (2014a). "

# 0.791 kgCO2e/kgLW production 
ghg_total_kgCO2_kg_fish <- 0.791 + ghg_energy_kgCO2_kg_fish

## convert to kgco2/tfish
GHG_kgCO2e_tfish <- ghg_total_kgCO2_kg_fish/0.001

## convert to MTco2e/tfish
GHG_MTCO2e_tfish <- GHG_kgCO2e_tfish/1000

shrimp_ghg <- shrimp_production %>%
  dplyr::mutate(ghg_tonnes = tonnes_production*GHG_MTCO2e_tfish) %>%
  dplyr::select(x, y, ghg_tonnes)

sum(shrimp_ghg$ghg_tonnes) # 17546741

write.csv(shrimp_ghg, file.path(prep_shrimp, "shrimp_ghg.csv"), row.names = FALSE)

## Now multiply this by our production raster
shrimp_production_raster <- rasterFromXYZ(shrimp_production)
plot(log(shrimp_production_raster + 1))
cellStats(shrimp_production_raster, "sum") # 5094133

ghg_em <- shrimp_production_raster*GHG_MTCO2e_tfish
plot(log(ghg_em + 1))
cellStats(ghg_em, "sum") # 17546741

#check
5094133*GHG_MTCO2e_tfish #17546741 
# it worked

## Transform CRS to be appropriate
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)

crs(ghg_em) <- crs(food_raster)
ghg_em

ghg_em_final <- projectRaster(ghg_em, food_raster, method = "ngb")
plot(log(ghg_em_final+1))
cellStats(ghg_em_final, "sum") #17546741
ghg_em_final

## Save the raster to datalayers folder
writeRaster(ghg_em_final, file.path(path_final, "marine_shrimp_aquaculture_meat_ghg.tif"), overwrite = TRUE)

```

### 2021-06-11 archive/marine_mapping_OLD_v1/tuna/food_pressures/tuna_nutrient/step1_nutrient.Rmd
pushing latest changes to the map!

---
title: "Tuna nutrient pollution"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "01/06/2021"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

This markdown uses models and species specific parameters from **Nitrogen and phosphorus budget in coastal and marine cage aquaculture and impacts of effluent loading on ecosystem: review and analysis towards model development**

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"
path_pre <- "/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers"

production <- read_csv(file.path(path_prep, "tuna_farm.csv"))
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

What I've found (we ended up only using global values):

**Preliminary model of nitrogen loads from southern bluefin tuna aquaculture** 
https://pubmed.ncbi.nlm.nih.gov/17669437/ 
 - Only lists N pollution values for Southern Bluefin Tuna in Australia. 
 - A range from 260 - 502 kg N / tonne growth 
 - Would use the mean: 281 kg N / tonnes growth

**Marine cage culture and the environment: effects on water quality and primary production** 
https://www.int-res.com/articles/aei2014/6/q006p151.pdf
 - "Some research studies have found significant increases in dissolved nitrogen. For example, AguadoGiménez et al. (2006) calculated the estimated dissolved nitrogen outputs of a bluefin tuna fattening operation in the Mediterranean could be 2−5.6 times greater than a comparable sea bream farm, with the potential for significant environmental impacts during peak production periods."
 - From Lex: seabream is 52 kg N / tonne = [104, 291.2] kg N / tonne : This would be for Europe

Aguado-Giminez: https://onlinelibrary.wiley.com/doi/full/10.1111/j.1365-2109.2006.01541.x

"The phosphorus output from a tuna fattening operation was calculated to be about 3−5 times higher than from sea
bream or sea bass farms because of differences in digestibility and feed formulation (Aguado-Giménez et al. 2006)"
 -  From Lex: Seabass is 17 kg P / tonne = [51, 85] kg P / tonne : for Europe
 - From Lex: Asian Seabass is [11, 16] kg P / tonne = [(33, 48), (55, 80)] kg P / tonne

**Nitrogen and phosphorus budget in coastal and marine cage aquaculture and impacts of effluent loading on ecosystem: review and analysis towards model development**
https://reader.elsevier.com/reader/sd/pii/S0025326X04003042?token=FD7F20D6183C00EC61F7CEED7BA11815BFA6A54438409343DAA77A2D5DEDDAD0BF5B8B2A55EED17F347FDE6E64F4FD72

 - General Cage Aquaculture
   - 132.5 kg N / tonne
   - 25 kg P / tonne

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P values
3. We report in PO4eq: Multiply P by by 3.07 to get PO4eq and N by 0.42 to get PO4eq. Sum the N and P PO4eq rasters.
4. We report in tonnes, so divide by 1000

 USE global values: 
  - General Cage Aquaculture
   - 132.5 kg N / tonne
   - 25 kg P / tonne

```{r}

tuna_pollution <- production %>%
  dplyr::mutate(prod_growth = tonnes_production*0.95) %>%
  dplyr::mutate(prod_growth_N_poll = prod_growth*132.5,
                prod_growth_P_poll = prod_growth*25) %>% ## in kg pollution now
  # dplyr::mutate(PO4eq_kg = prod_growth_N_poll*0.42 + prod_growth_P_poll*3.07) %>% cut (01/14/2021)
  dplyr::mutate(N_P_tonnes = (prod_growth_N_poll + prod_growth_P_poll)/1000, 
                P_poll_t = prod_growth_P_poll/1000, 
                N_poll_t = prod_growth_N_poll/1000) %>%
  dplyr::select(x, y, N_P_tonnes, P_poll_t, N_poll_t)

sum(tuna_pollution$N_P_tonnes) # 5546.982
sum(production$tonnes_production) # 37072.56

## save to dataprep folder with the correct naming conventions:
write.csv(tuna_pollution, file.path(path_prep, "tuna_nutrient.csv"))

## Save N + P layer
N_P_df <- tuna_pollution %>%
  dplyr::select(x, y, N_P_tonnes)

final_rast <- rasterFromXYZ(N_P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 5546.982

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 5546.982
final_rast

## Save to datalayers
writeRaster(final_rast, file.path(path_final, "marine_tuna_aquaculture_meat_nutrient.tif"), overwrite = T)

## Save N layer
N_df <- tuna_pollution %>%
  dplyr::select(x, y, N_poll_t)

final_rast <- rasterFromXYZ(N_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 4666.508

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 4666.508
final_rast

## Save to datalayers
writeRaster(final_rast, file.path(path_pre, "marine_tuna_aquaculture_meat_nutrientN.tif"), overwrite = T)

## Save P layer
P_df <- tuna_pollution %>%
  dplyr::select(x, y, P_poll_t)

final_rast <- rasterFromXYZ(P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 880.4733

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 880.4733
final_rast

## Save to datalayers
writeRaster(final_rast, file.path(path_pre, "marine_tuna_aquaculture_meat_nutrientP.tif"), overwrite = T)

```

ARCHIVE: 
```{r}
# fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
#   filter(environment %in% c("Marine", "Brackishwater"))
# 
# 
# ## Read in fao data and get a species list for salmon
# species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
#   distinct(species, aq_group)
# 
# # the list of species we are including
# tuna_list <- species_list$species[species_list$aq_group=="tuna"]
# tuna_list
# 
# ## write out shrimp taxa and production for Juliette
# fao_tuna_taxa_prod <- fao %>%
#   filter(species %in% tuna_list) %>%
#   filter(!is.na(value)) %>%
#   arrange(-value, country) %>%
#   filter(value>=500) %>%  # countries with less do not appear to be stable producers at this point
#   group_by(country, iso3c, species, year) %>%
#   dplyr::filter(year == 2017) %>%
#   summarize(fao_tonnes_production = sum(value)) %>%
#   arrange(country, iso3c, species, year)
# 
# ## set up lists of different regions
# asia <- c("JPN")
# 
# europe <- c("HRV", "MLT", "ESP", "TUR") 
# 
# australia <- c("AUS")
# 
# mexico <- c("MEX")
# 
# 
# 
# ## Read in production data 
# production_sf <- st_read(file.path("/home/sgclawson/github/food_systems/aquaculture/marine/tuna/tuna_nutrient/prod_data_by_cell_iso3c.shp")) %>%
#   dplyr::rename("tonnes_per_farm" = "tnns_p_")
# 
# ## Now we can do the actual analysis outlined above
# 
# nutrient_data <- production_sf %>%
#   dplyr::mutate(tonnes_growth = tonnes_per_farm*0.95) %>%   ## multiply by 0.95 to correct for growth outside seapen
#   
#   dplyr::mutate(N_poll = case_when(
#                   iso3c %in% asia ~ tonnes_growth*132.5,
#                   iso3c %in% europe ~ tonnes_growth*197.6,
#                   iso3c %in% mexico ~ tonnes_growth*132.5,
#                   iso3c %in% australia ~ tonnes_growth*281
#                 ),
#                 P_poll = case_when(
#                   iso3c %in% asia ~ tonnes_growth*54,
#                   iso3c %in% europe ~ tonnes_growth*68,
#                   iso3c %in% australia ~ tonnes_growth*25,
#                   iso3c %in% mexico ~ tonnes_growth*25
#                 )) %>%  ## get all of out pollution values by species group and region
#   
#   dplyr::mutate(po4eq_kg = N_poll*0.42 + P_poll*3.07) %>% ## get po4eq
#   
#   dplyr::mutate(po4eq_tonnes = po4eq_kg/1000) %>%
#   dplyr::select(po4eq_tonnes, geometry)
# 
# sum(nutrient_data$po4eq_tonnes) # 7603.354
# sum(fao_tuna_taxa_prod$fao_tonnes_production) # 37072.56
# 
# tuna_raster_check <- rasterize(nutrient_data, food_raster, field = "po4eq_tonnes", fun=sum)
# plot(log(tuna_raster_check+1))
# cellStats(tuna_raster_check, stat = "sum", na.rm = TRUE) # 7603.354
# 
# 
# tuna_raster <- rasterize(nutrient_data, food_raster, field = "po4eq_tonnes", fun=sum, background=0)
# plot(log(tuna_raster+1))
# 
# tuna_raster_df <- as.data.frame(tuna_raster, xy=TRUE) %>%
#   dplyr::select(x,y, po4eq_tonnes=layer)
# 
# cellStats(tuna_raster, stat = "sum") # 7603.354
# sum(tuna_raster_df$po4eq_tonnes) # 7603.354
# sum(nutrient_data$po4eq_tonnes, na.rm = TRUE) # 7603.354
# 
# ## save to dataprep folder with the correct naming conventions: 
# write.csv(tuna_raster_df, file.path(path_prep, "tuna_nutrient.csv"))
# 
# 
# final_rast <- rasterFromXYZ(tuna_raster_df, crs = food_crs)
# crs(final_rast)
# plot(final_rast)
# final_rast
# cellStats(final_rast, "sum") # 7603.354
# 
# final_area_fix <- final_rast/raster::area(final_rast)
# 
# final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")
# 
# final_rast <- final_rast_proj*raster::area(final_rast_proj)
# cellStats(final_rast, "sum") # 7603.354
# final_rast
# 
# ## Save to datalayers 
# writeRaster(final_rast, file.path(path_final, "marine_tuna_aquaculture_meat_nutrient.tif"), overwrite = T)
```

### 2021-06-11 archive/marine_mapping_OLD_v1/tuna/tuna_farms/STEP1_fao_tuna_production.Rmd
pushing latest changes to the map!

--- 2021-04-01 marine/tuna/tuna_farms/STEP1_fao_tuna_production.Rmd
@@
    mutate(percent = round((fao_tonnes_production/sum(fao_tonnes_production))*100, 2))
- sum(explore$fao_tonnes_production) # 37072.56
- unique(explore$country) # 7 countries 
 ```
-
-```{r}
-## write out bivalve taxa and production for Juliette
-fao_tuna_taxa_prod <- fao %>%
-  filter(species %in% tuna_list) %>%  
-  filter(!is.na(value)) %>%
-  arrange(-value, country) %>%
-  group_by(country, year) %>%
-  summarise(value = sum(value)) %>%
-  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
-  filter(year == 2017)
-
-sum(fao_tuna_taxa_prod$value) # 37072.56
-
-unique(fao_tuna_taxa_prod$country) # 16 countries 
-```

### 2021-06-11 workflow/place_unknown_farms.R

@@ -28,12 +28,23 @@ blank_raster[] <- 1
 
 the_crs <- crs(fake_raster, asText = TRUE)
 
-ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
-  st_transform(the_crs) #%>% 
-  #filter(HARB_SIZE_ != "L")
+# ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
+#   st_transform(the_crs) #%>% 
+#   #filter(HARB_SIZE_ != "L")
+
+ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/Commercial_ports.shp") %>%
+  st_transform(the_crs) %>%
+  filter(HARB_SIZE_ != "L")
 
 # consider removing "L" HARB_SIZE_ points
 
+# test <- ports_raw %>%
+#   filter(HARB_SIZE_ == "L")
+# mapview(test)
+# 
+# test2 <- ports_raw %>%
+#   filter(HARB_SIZE_ != "L")
+# mapview(test2)
 
 data <- read_csv("marine/output/all_marine_farms.csv") %>% 
   st_as_sf(., 
@@ -66,8 +77,9 @@ arctic_fixed[arctic_fixed[]==2] <- 1
 
 ## add land mask
 
-for (i in 1:length(unique(need_national_allocation$iso3c))) {
+for (i in 42:length(unique(need_national_allocation$iso3c))) {
   
+  # i = 1
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[i]
   
@@ -165,13 +177,13 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
   if (nrow(this_farm_points) != the_farm_number) break
   
   #UNCOMMENT WHEN SAVING! 
-  write_rds(this_farm_points, paste0("data/temp_data/temp_marine_final/temp_farms_", i, ".rds"))
+  write_rds(this_farm_points, paste0("data/temp_data/temp_no_L_ports/temp_farms_", i, ".rds"))
   print(paste0(i, " - ",this_iso3, " has been saved"))
   
 }
 
 
-all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
[…]

### 2021-06-17 analysis/SI_figs.Rmd
ran 3 different versions of the mapping. 10km, 35km, and 45km from ports

--- 2021-06-11 analysis/paper_figs.Rmd
@@
 ---
-title: "Figures for paper"
+title: "Figures for SI"
 author: "Gage Clawson (UCSB, NCEAS, OHI)"
-date: "05/10/2021"
+date: "06/14/2021"
 output: html_document
@@
 
-This script takes our final farms dataset and calculates summary statistics that will be used in the paper.
+This script takes our final farms dataset and creates the figures which will be showcased in the SI.
 

### 2021-06-17 analysis/paper_figs.Rmd
ran 3 different versions of the mapping. 10km, 35km, and 45km from ports

@@
 
-This script takes our final farms dataset and calculates summary statistics that will be used in the paper.
+This script takes our final farms dataset and creates the figures which will be showcased in the main manuscript.
 
@@
   filter(country == "United States of America")
-mapview(test)
+mapview(test, zcol = "data_type")
 
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
+all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv") %>% 
+  mutate(data_type_plot = case_when(
+    data_type == "modeled location, known number of farms" ~ "Modeled location, known number of farms",
+    data_type == "modeled location, estimated number of farms" ~ "Modeled location, estimated number of farms", 
+    data_type == "known location" ~ "Known location"
+  ))
 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
+                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("Known location \n n = 9,750", "Modeled location, known number of farms \n n = 10,519", "Modeled locations, estimated number of farms \n n = 75,073"))
     #  geom_vline(xintercept = 135) + # check to make sure it lines up
@@
 
-chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
   coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
@@
 ## China - near 
-chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
 #   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
@@
 ## Ecuador - Near Guayaquil
-ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
   coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
@@
 ## Norway
-nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
   # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
@@
 
-# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+## USA NE 
+usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
+  annotation_map_tile(type = "osm", zoomin = 0) + 
+  geom_spatial_point(size = 0.5, alpha = 0.7) + 
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
+  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
+    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
+  theme(legend.position = "bottom", 
+        legend.title=element_blank(), 
+        axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        legend.key = element_rect(fill = NA),
+        axis.text.x = element_text(angle = 60, hjust = 1),
+panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+  ggtitle("C")
+  #border(linetype = "longdash")
+        #panel.border = element_rect(colour = "black", fill=NA, size=5))
+usa_zoom
+
+## Plot with norway instead of USA
+# plot1 <- (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "none") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none"))
+# 
+# plot1
+# ggsave("analysis/figs/chl_ecu_zoom.jpg")
+# 
+# 
+# plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+# 
+# plot2
+# ggsave("analysis/figs/nor_chn_zoom.jpg")
+
+## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final_nor.jpg"
+
+## Plot with USA instead of norway
 
@@
 
-plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+plot2 <- (usa_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
 
 plot2
-ggsave("analysis/figs/nor_chn_zoom.jpg")
+ggsave("analysis/figs/usa_chn_zoom.jpg")
 
@@
 
-## Radial bar chart of estimation type per country
+ARCHIVE: Radial bar chart of estimation type per country
 

### 2021-06-17 analysis/paper_stats.Rmd
ran 3 different versions of the mapping. 10km, 35km, and 45km from ports

@@
 # mapview(test)
+
 ```
@@
 
-# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of the total estimated points, and only had 15 known location points
+# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of all points, and only had 15 known location points
 
 chn_data_estimated <- all_farms %>%
-  filter(iso3c == "CHN") %>%
-  filter(data_type == "modeled location, estimated number of farms")
-# 58151 points
-58151/75073 # 0.7745927 = 77%
+  filter(iso3c == "CHN") #%>%
+  #filter(data_type == "modeled location, estimated number of farms")
+# 58166 points
+58151/95342 # 0.6099201 = 61%
 

### 2021-06-17 workflow/place_unknown_farms.R

@@ -28,15 +28,12 @@ blank_raster[] <- 1
 
 the_crs <- crs(fake_raster, asText = TRUE)
 
-# ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
-#   st_transform(the_crs) #%>% 
-#   #filter(HARB_SIZE_ != "L")
 
 ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/Commercial_ports.shp") %>%
   st_transform(the_crs) %>%
-  filter(HARB_SIZE_ != "L")
+  filter(HARB_SIZE_ != "L") # remove L ports
 
-# consider removing "L" HARB_SIZE_ points
+
 
 # test <- ports_raw %>%
 #   filter(HARB_SIZE_ == "L")
@@ -73,13 +70,12 @@ arctic_raster <- reclassify(arctic_raster, c(66,Inf, NA, 0,66,1))
 arctic_fixed <- resample(arctic_raster, blank_raster, method = "ngb")
 
 arctic_fixed <- inverted_land + arctic_fixed
-arctic_fixed[arctic_fixed[]==2] <- 1
+arctic_fixed[arctic_fixed[]==2] <- 1 ## add land mask
 
-## add land mask
 
-for (i in 42:length(unique(need_national_allocation$iso3c))) {
-  
-  # i = 1
+for (i in 42) {
+  # 52:length(unique(need_national_allocation$iso3c))
+  # i = 42
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[i]
   
@@ -145,9 +141,13 @@ for (i in 42:length(unique(need_national_allocation$iso3c))) {
   
   dis_to_port_rast <- distanceFromPoints(this_raster_area, these_ports)
   port_test_rast <- dis_to_port_rast
-  port_test_rast[port_test_rast >35000 ] <- NA # acceptable distance to port
-  suitability_rast <- port_test_rast+arctic_fixed # add in land mask
-  
+  port_test_rast[port_test_rast >45000] <- NA # acceptable distance to port # we are doing 3; 10km, 35km, and 45km
+  port_test_rast[port_test_rast<1000] <- NA # need to be 1km away from ports/shipping lanes
+  suitability_rast <- port_test_rast + arctic_fixed # add in arctic mask
+  #plot(suitability_rast)
+  # mapview(suitability_rast)
+  # mapview(port_test_rast)
+  # plot(arctic_fixed)
[…]

### 2021-07-09 analysis/SI_figs.Rmd
fixed so many things

@@
 ```{r}
-all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources.csv") %>%
+all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>%
     st_as_sf(., 
@@
 
-fao_data <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv") %>%
-  group_by(country) %>%
-  summarise(prod = sum(total_tonnes))
 ```
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
+all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
 
@@
 
-## Make the global map (Figure 1)
+## Make the global map by species group (Supplementary Figures 1-6)
 ```{r}
@@
 
+for(i in c(1, 2,3, 6)){
+
+ # i = 4
+
+  spp_group <- unique(all_farms$species_group)[i]
+
+  all_farms_i <- all_farms %>%
+    filter(species_group == spp_group)
+
+  count_green_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "known location")
+
+  count_green <- count_green_df$n
+
+  count_yellow_df <-  all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled location, known number of farms")
+
+  count_yellow <- count_yellow_df$n
+
+  count_red_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled location, estimated number of farms")
+
+  count_red  <- count_red_df$n
+
 ## create first plot
@@
   geom_sf(fill = "white", lwd = 0.1) + 
-  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
+  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
 #  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
@@
         legend.position = "bottom", 
-        legend.title=element_blank()) +
+        legend.title=element_blank(),
+        text=element_text(family="Times New Roman")) +
   guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
   scale_color_manual(values = c("forestgreen", "orange1", "red3"),
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
-    #  geom_vline(xintercept = 135) + # check to make sure it lines up
-  #geom_hline(yintercept = 0) # check to make sure it lines up
+                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
+  # scale_color_manual(values = c("forestgreen", "orange1"),
+  #                   breaks = c("known location", "modeled location, known number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow))) +
+    # scale_color_manual(values = c("red3"),
+    #                 breaks = c("modeled location, estimated number of farms"), labels = c(sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
+  labs(title = sprintf("Supplmentary Figure %s: %s farms", i, spp_group))
 
-total_map
-
-# guides(colour=guide_legend(nrow=30))
+# total_map
 
@@
 plot_x <- axis_canvas(total_map, axis = "x") +
-  geom_histogram(data = all_farms, aes(X, fill = data_type), bins = 360)  +
+  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
   #  geom_vline(xintercept = 135) + # check to make sure it lines up
@@
 plot_y <- axis_canvas(total_map, axis = "y") +
-  geom_histogram(data = all_farms, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
+  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
  #  geom_hline(yintercept = 0) + #  check to make sure it lines up
@@
 ggdraw(plot_final)
-ggsave("analysis/figs/map_fig.jpg")
+
+ggsave(sprintf("analysis/figs/supp_map_fig_%s.jpg", spp_group))
+
+}
 
 ```
-
-## Make finer resolution maps (Figure 2)
-```{r}
-library(dplyr)
-library(sf)
-library(raster)
-library(mapview)
-library(tidyverse)
-library(ggpubr)
-library(RColorBrewer)
-library(ggspatial)
-library(ggplot2)
-library(patchwork)
-
-## zoomed maps
-
-chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-  annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
-  # coord_sf(crs = 4326, xlim = c(-75, -72.5), ylim = c(-46, -44), expand = FALSE) +
-  theme(legend.position = "bottom", ## put legend on bottom
-        legend.title=element_blank(), 
-        axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.key = element_rect(fill = NA),
-        axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-  ggtitle("A")  # + 
- #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
-chl_zoom
-
-## China - near 
-chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-  annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
-  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
-  #coord_sf(crs = 4326) + 
-  theme(legend.position = "bottom", 
-        legend.title=element_blank(), 
-        axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust = 1),
-        legend.key = element_rect(fill = NA),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-  ggtitle("D")
-  #border(linetype = "longdash")
-        #panel.border = element_rect(colour = "black", fill=NA, size=5))
-chn_zoom
-
-## Ecuador - Near Guayaquil
-ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-  annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
-  #coord_sf(crs = 4326) + 
-  theme(legend.position = "bottom", 
-        legend.title=element_blank(), 
-        axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-  ggtitle("B")
-  #border(linetype = "longdash")
-        #panel.border = element_rect(colour = "black", fill=NA, size=5))
-ecu_zoom
-
-## Norway
-nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-  annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
-    coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
-  theme(legend.position = "bottom", 
-        legend.title=element_blank(), 
-        axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.key = element_rect(fill = NA),
-        axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-  ggtitle("C")
-  #border(linetype = "longdash")
-        #panel.border = element_rect(colour = "black", fill=NA, size=5))
-nor_zoom
-
-# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
-
-plot1 <- (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "none") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none"))
-
-plot1 
-ggsave("analysis/figs/chl_ecu_zoom.jpg")
-
-plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
-
-plot2
-ggsave("analysis/figs/nor_chn_zoom.jpg")
-
-## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final.jpg"
-
-```
-
-## Radial bar chart of estimation type per country
-
-```{r}
-library(tidyverse)
-library(viridis)
-library(hrbrthemes)
-library(RColorBrewer)
-library(colorspace)
-
-rank_rgn <- all_farms %>%
-  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
-  group_by(country) %>%
-  summarise(num_farms_total = n()) %>%
-  ungroup() %>%
-  arrange(num_farms_total)
-
-## Stuff for both plots
-# i think that this would look better with each stressor having its own color that is paired with ocean/land
-# 
-# pick 4 distinct colors and then create a pair with one being more brown or green and the other being more blue
-
-source_name <- data.frame(source = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
-
-type_1 <- "forestgreen"
-type_1 <- lighten(type_1, amount = -0.05)
-type_2 <- "orange1"
-type_2 <- lighten(type_2, amount = -0.05)
-type_3 <- "red3"
-type_3 <- lighten(type_3, amount = -0.05)
-
-gc_palette <- c(type_1, type_2, type_3)
-scales::show_col(gc_palette, n = 3)
-
-pal_df <- as_tibble(gc_palette) %>% 
-  rename(fill_value = value) %>% 
-  mutate(source = case_when(fill_value == type_1 ~ "known location",
-                            fill_value == type_2 ~ "modeled location, known number of farms",
-                            fill_value == type_3 ~ "modeled location, estimated number of farms"))
-
-## circle plot
-
-cutoff_value <-  1000
-
-by_country <- all_farms %>%
-  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
-  group_by(country, data_type) %>%
-  summarise(num_farms = n()) %>%
-  ungroup() %>%
-  group_by(country) %>%
-  mutate(num_farms_total = sum(num_farms)) %>%
-  ungroup() %>%
-  arrange(num_farms_total) %>%
-  filter(num_farms_total < cutoff_value)
-
-##grab the highest country to highlight red and id where the circle ends and then side bar chart begins
-highest_country <- by_country[dim(by_country)[1], "country"]
-farms_highest_country <- filter(by_country, country %in% highest_country$country) #used below
-
-# adjust the rank_rgn-adjust dataframe to match above
-rank_rgn_adj <- rank_rgn %>%
-  filter(country %in% by_country$country)
-
-# add empty space to create space in the circleplot for axes
- empty_bar <- 5
- to_add <- data.frame(matrix(NA, empty_bar, ncol(rank_rgn_adj)) )
- colnames(to_add) = colnames(rank_rgn_adj)
- to_add$country <- as.character(1:empty_bar)
- rank_rgn_adj  <- rbind(to_add, rank_rgn_adj)
-
- # some code to orient the country labels
-sequence_length = length(unique(rank_rgn_adj$country))
-first_sequence = c(1:(sequence_length%/%2)) 
-second_sequence = c((sequence_length%/%2+1):sequence_length) 
-first_angles = c(90 - 180/length(first_sequence) * first_sequence)
-second_angles = c(-90 - 180/length(second_sequence) * second_sequence)
-rank_rgn_adj$angle <- c(first_angles, second_angles)
-rank_rgn_adj$hjust <- c(rep(0, length(first_sequence)), 
-                    rep(1, length(second_sequence)))
-
-# color for region labels
-rank_rgn_adj <- rank_rgn_adj %>%
-  mutate(country = factor(country, unique(country))) %>%
-  mutate(color = "black") %>%
-  mutate(color = ifelse(is.na(num_farms_total), "white", color)) %>%
-  mutate(color = ifelse(country %in% highest_country$country, "red", color))
-
-## make the plot
-
-circle_theme <- theme(axis.line=element_blank(),
-                      axis.text.y=element_blank(),
-                      axis.ticks=element_blank(),
-                      axis.title.x=element_blank(),
-                      axis.title.y=element_blank(),
-                      legend.position="none",
-                      panel.background=element_blank(),
-                      panel.border=element_blank(),
-                      panel.grid.major=element_blank(),
-                      panel.grid.minor=element_blank(),
-                      plot.background=element_blank(),
-                      axis.text.x = element_blank())
-
-color_order <- c(type_1, type_2, type_3)
-
-pressures_adj_circle_plot <- by_country %>% 
-  mutate(prop_of_global_stacked = abs(num_farms)) %>% 
-  left_join(pal_df, by = c("data_type" = "source")) %>% 
-  mutate(fill_value = factor(fill_value, levels = color_order))
-
- ggplot(data=pressures_adj_circle_plot, aes(x=country, y=prop_of_global_stacked, fill = fill_value)) +
-
-  geom_bar(stat="identity") +
-
-  # ## this adjust the inner circle size (ymin) and outer circle size (ymax), which can be expanded to include names
-   geom_errorbar(aes(
-       x     = 1,
-        ymin = -0.01,   # ymin  = -0.03, this is for when ocean bars stack inwards -0.01 for when not
-       ymax  = 0.035),
-       alpha = 0) +
-      # Country name text placement
-     geom_text(
-       data = rank_rgn_adj,
-       aes(x     = country,
-           y     = max(by_country$num_farms_total, na.rm=TRUE),
-           label = country,
-           angle = angle,
-           hjust = hjust),
-       inherit.aes = FALSE,
-       fontface = "bold",
-       alpha = 0.9,
-       size = 4,
-       color = rank_rgn_adj$color) +
-    # 
-   # georegion names
-    # geom_text(
-    #   data=rgn_shift,
-    #   aes(y = 0.02, x = name_x, label = georegion),
-    #   # aes(x=name_x,
-    #   #     y=name_y,
-    #   #     label=georegion),
-    #   inherit.aes=FALSE, size=7) +
-  #  
-  # # # Scale bar circles
-  # ## This adds the 0 line
-      geom_segment(
-        x = 0, 
-         y = 0, 
-         xend = dim(rank_rgn_adj)[1]+1, 
-         yend = 0, 
-         fill = NULL,
-        alpha = 1, color = "white", size = 0.1) + #color = "black for internal
-  #    
-  #  # Scale bar annotation, this adds the y-axis numbers
-      annotate("text",
-        x     = c(3, 3, 3),
-        y     = c(0, 0.0175, 0.035),
-        label = c(0, 0.0175, 0.035),
-        color = "darkgray", angle = -4, size = 4) +
-  #     
-  scale_color_identity() +
-   scale_fill_identity() +
-   # scale_fill_manual(values= rev(myPalette), c("Land: Disturbance", "Land: GHG", "Land: Water", "Land: Nutrient",
-   #                                    "Ocean: Disturbance", "Ocean: GHG", "Ocean: Water", "Ocean: Nutrient")) +
-  coord_polar() +
- circle_theme
-
-```
-
-ARCHIVE: Other ways of trying to visualize
-```{r}
-
-## philippines
-# phl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-#   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 1, alpha = 0.7) + 
-#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   coord_sf(crs = 4326, xlim = c(120.25, 122.5), ylim = c(17, 19), expand = FALSE) +
-#   #coord_sf(crs = 4326) + 
-#   theme(legend.position = "bottom", 
-#         legend.title=element_blank(), 
-#         axis.title.x = element_blank(), 
-#         axis.title.y = element_blank(),
-# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("B")
-#   #border(linetype = "longdash")
-#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-# phl_zoom
-
-## California - bay area 
-# cal_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-#   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 1, alpha = 0.7) + 
-#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   coord_sf(crs = 4326, xlim = c(-123, -121), ylim = c(37, 39), expand = FALSE) +
-#   #coord_sf(crs = 4326) + 
-#   theme(legend.position = "bottom", 
-#         legend.title=element_blank(), 
-#         axis.title.x = element_blank(), 
-#         axis.title.y = element_blank(),
-# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("B")
-#   #border(linetype = "longdash")
-#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-# cal_zoom
-
-## New Zealand
-# nzl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-#   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
-#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   # coord_sf(crs = 4326, ylim = c(-48, -34), xlim = c(165, 180), expand = FALSE) + ## all of new zealand
-#    coord_sf(crs = 4326, ylim = c(-41, -34), xlim = c(172, 180), expand = FALSE) + ## north island
-#   theme(legend.position = "bottom", 
-#         legend.title=element_blank(), 
-#         axis.title.x = element_blank(), 
-#         axis.title.y = element_blank(),
-#         axis.text.x = element_text(angle = 60, hjust = 1),
-# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("D")
-#   #border(linetype = "longdash")
-#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-# nzl_zoom
-
-## all together
-total_map <- ggplot(data = world) +
-  geom_sf(fill = "white", lwd = 0.1) + 
-  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.2) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
-  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
-  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  theme_bw() + 
-  theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(), 
-        legend.position = "none") 
-total_map
-
-## make longitude histogram
-
-lon_hist <- ggplot(data = all_farms) + 
-  geom_histogram(aes(X, fill = data_type), bins = 360) + 
-  # scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180)) +
-  # scale_y_reverse() +
-   theme_void() + 
-    theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(), 
-        legend.position = "none") # +
-  # geom_vline(xintercept = 135) 
-lon_hist
-
-## make latitude histogram
-lat_hist <- ggplot(data = all_farms) + 
-  geom_histogram(aes(Y, fill = data_type), bins = 180) + 
-  # scale_x_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  # xlim(-58, 73) + 
-  coord_flip() +
-   theme_void() + 
-    theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(), 
-        legend.position = "none") # + 
-  # geom_vline(xintercept = 0)
-
-lat_hist
-
-require(gridExtra)
-library(cowplot)
-library(egg)
-
-## using ggExtra
-library(ggExtra)
-ggExtra::ggMarginal(total_map, type = "histogram", groupFill = TRUE, size = 2)
-
-## using patchwork
-lon_hist + plot_spacer() + total_map + lat_hist + 
-  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))
-
-## using cowplot
-plot_grid(
-  lon_hist
-  , NULL
-  , total_map
-  , lat_hist
-  , ncol = 2
-  , nrow = 2
-  , rel_heights = c(0.2, 1)
-  , rel_widths = c(1, 0.2)
-)
-
-```
-
-```{r}
-
-test_data <- all_farms %>%
-  filter(data_type != "known location")
-
-## create first plot
-total_map <- ggplot(data = world) +
-  geom_sf(fill = "white", lwd = 0.1) + 
-  geom_point(data = test_data, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
-  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
-  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  theme_bw() + 
-  theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-        legend.position = "bottom", 
-        legend.title=element_blank()) +
-  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
-    #  geom_vline(xintercept = 135) + # check to make sure it lines up
-  #geom_hline(yintercept = 0) # check to make sure it lines up
-
-total_map
-
-ggsave("analysis/figs/map_fig_test.jpg")
-
-```

### 2021-07-09 analysis/SI_table_3.Rmd
fixed so many things

--- 2021-05-11 analysis/paper_stats.Rmd
@@
 ---
-title: "Summary stats for paper"
+title: "SI tables"
 author: "Gage Clawson (UCSB, NCEAS, OHI)"
@@
 
-This script takes our final farms dataset and calculates summary statistics that will be used in the paper.
+This script takes our final farms dataset and creates the .
 
@@
 ```
-
-# Global regions
-
-```{r}
-
-# this file includes ocean regions:
-gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
-
-gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
-plot(gadm_latlon)
-
-gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
-  mutate(reg_id = as.numeric(reg_id))
-```
-
-# Read in farms data and convert to sf
-
-```{r}
-all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources.csv") %>%
-    st_as_sf(., 
-           coords = c("X", "Y"),
-           crs = crs(food_raster), 
-           agr = "constant")
-
-all_farms <- all_farms_sf %>%
-  st_drop_geometry()
-
-```
-
-```{r}
-sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
-  clean_names() %>%
-  mutate(type = case_when(species == "Salmonids" ~ "salmon",
-                          species == "Unfed or algae fed shellfish" ~ "bivalve",
-                          species == "Shrimp" ~ "shrimp", 
-                          species == "Tuna" ~ "tuna", 
-                          species == "General Marine Fish" ~ "marine_fish_general", 
-                          species == "Crustaceans" ~ "crustaceans"))
-
-## Numbers by data type
-by_data_type <- all_farms %>%
-  group_by(data_type) %>%
-  summarise(n_obs = n()) %>%
-  mutate(total_obs = sum(n_obs)) %>% 
-  ungroup() %>%
-  mutate(pct = n_obs/total_obs*100)
-
-by_data_type
-# A tibble: 3 x 4
-#   data_type                                   n_obs total_obs   pct
-#   <chr>                                       <int>     <int> <dbl>
-# 1 known location                               9750     95341  10.2
-# 2 modeled location, estimated number of farms 75072     95341  78.7
-# 3 modeled location, known number of farms     10519     95341  11.0
-
-# How many countries have spatial locations information?
-known_countries <- all_farms %>%
-  filter(data_type == "known location") %>%
-  distinct(iso3c)
-
-# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of the total estimated points, and only had 15 known location points
-
-chn_data_estimated <- all_farms %>%
-  filter(iso3c == "CHN") %>%
-  filter(data_type == "modeled location, estimated number of farms")
-# 58151 points
-58151/75073 # 0.7745927 = 77%
-
-chn_data_known <- all_farms %>%
-  filter(iso3c == "CHN") %>%
-  filter(data_type == "known location") # 15 locations
-
-# Chile, Norway, Peru, the United States, Canada and Ireland provided a substantial number of known locations (>1000).
-top_known <- all_farms %>%
-  filter(data_type == "known location") %>%
-  group_by(iso3c) %>%
-    summarise(n_obs = n())
-
-# Only 5 countries (Cambodia, Mauritius, Myanmar, North Korea, and Russia) had no form of farm data at all, however, these countries only account for 0.5% of marine aquaculture production included.
-
-no_info_at_all <- sources %>%
-  dplyr::filter(known_farms_location == 0, known_farms_no_location == 0) ## only 5 with no information at all
-
-mar_production <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv")
-
-no_info_production <- mar_production %>%
-  filter(country %in% c("Cambodia", "Mauritius", "Myanmar", "Korea, Dem. People's Rep", "Russian Federation"))
-sum(no_info_production$total_tonnes) # 152800.1
-
-sum(mar_production$total_tonnes) # 29623515
-152800.1/29623515
-
-chn_production <- mar_production %>%
-  filter(country == "China")
-sum(chn_production$total_tonnes)
-17696822/29623515
-
-# Per species group, salmon was the most data rich (98% of points had location information, 1.13% of points were known with no location information, 0.87% estimated), followed by Tuna (34% of points had location information, 66% of points were known with no location information, 0% estimated).
-
-by_species_data_type <- all_farms %>%
-  group_by(species, data_type) %>%
-  summarise(n_obs = n()) %>%
-  mutate(total_obs = sum(n_obs)) %>% 
-  ungroup() %>%
-  mutate(pct = n_obs/total_obs*100)
-```
-
-Check some of the data
-```{r}
-by_type <- all_farms %>%
-  group_by(species) %>%
-  summarise(n_obs = n())
-
-by_country_type <- all_farms %>%
-  group_by(iso3c, species) %>%
-  summarise(n_obs = n()) %>%
-  left_join(sources) %>%
-  dplyr::select(iso3c, species, n_obs, number_of_total_farms) %>%
-  mutate(difference = n_obs - number_of_total_farms)
-
-by_data_type_country <- all_farms %>%
-  group_by(iso3c, species, data_type) %>%
-  summarise(n_obs = n()) %>%
-  ungroup() %>%
-  left_join(sources) %>%
-  dplyr::select(iso3c, species, data_type, n_obs, number_of_total_farms, known_farms_location, known_farms_no_location, estimated_farms)
-
-known <- by_data_type_country %>%
-  filter(data_type == "known location") %>%
-  dplyr::select(iso3c, species, data_type, n_obs, known_farms_location) %>%
-  mutate(difference = n_obs - known_farms_location)
-
-number_known <- by_data_type_country %>% 
-  filter(data_type == "modeled location, known number of farms") %>%
-  dplyr::select(iso3c, species, data_type, n_obs, known_farms_no_location) %>%
-  mutate(difference = n_obs - known_farms_no_location)
-
-estimated <- by_data_type_country %>% 
-  filter(data_type == "modeled location, estimated number of farms") %>%
-  dplyr::select(iso3c, species, data_type, n_obs, estimated_farms) %>%
-  mutate(difference = n_obs - estimated_farms)
-
-```
-
-```{r}
-
-all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
-
-unique(sort(all_farms$country))
-
-all_known_locations <- all_farms %>%
-  filter(data_type == "known location")
-
-unique(all_known_locations$country)
-
-## read in each of the comprehensive locations
-
-farms_folder <- file.path("aquaculture_mapping/marine")
-
-bivalve_comp_files <- list.files(here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5"), full=TRUE)
-
-bivalve_comp <- plyr::ldply(bivalve_comp_files, read_csv) %>%
-  mutate(type = "bivalve") %>%
-  dplyr::select(lat, lon, iso3c, data_quality, type)
-
-shrimp_comp_files <- list.files(here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5"), full=TRUE)
-
-shrimp_comp <- plyr::ldply(shrimp_comp_files, read_csv) %>%
-  mutate(type = "shrimp")%>%
-  dplyr::select(lat, lon, iso3c, data_quality, type)
-
-salmon_comp_files <- list.files(here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5"), full=TRUE)
-
-salmon_comp <- plyr::ldply(salmon_comp_files, read_csv) %>%
-  mutate(type = "salmon")%>%
-  dplyr::select(lat, lon, iso3c, data_quality, type)
-
-tuna_comp_files <- list.files(here("marine/tuna/tuna_farms/data/known_farm_sites_2_4_5"), full=TRUE)
-
-tuna_comp <- plyr::ldply(tuna_comp_files, read_csv) %>%
-  mutate(type = "tuna")%>%
-  dplyr::select(lat, lon, iso3c, data_quality, type)
-
-finfish_comp_files <- list.files(here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5"), full=TRUE)
-
-finfish_comp <- plyr::ldply(finfish_comp_files, read_csv) %>%
-  mutate(type = "finfish")%>%
-  dplyr::select(lat, lon, iso3c, data_quality, type)
-
-crustaceans_comp_files <- list.files(here("marine/crustaceans/crustaceans_farms/data/known_farm_sites_2_4_5"), full=TRUE)
-
-crustaceans_comp <- plyr::ldply(crustaceans_comp_files, read_csv) %>%
-  mutate(type = "crustaceans")%>%
-  dplyr::select(lat, lon, iso3c, data_quality, type)
-
-all_comp_farms <- rbind(finfish_comp, bivalve_comp, salmon_comp, tuna_comp, shrimp_comp) %>%
-  filter(data_quality == 5) %>%
-  group_by(iso3c, type) %>%
-  summarise(n_obs = n())
-
-unique(all_comp_farms$iso3c)
-
-## Countries that have comprehensive location data across all their species reported:
-# - ARE (1 type), GRC (2 type), MLT (2 types), NOR (3 types), CYP (1 type), HKG (2 type), BLG (1 type), BLZ (1 type), CAN (2 types), CHL (2 types), DNK (2 types), FIN (1 type), FRO (1 type), GBR (2 types), IRL (2 types), JEY (1 type)
-```

### 2021-07-09 analysis/match_data_sources.Rmd
fixed so many things

--- 2021-05-27 analysis/match_data_sources.Rmd
@@
 
-all_farms <- readRDS("data/all_modeled_marine_farms.rds") %>%
+all_farms <- readRDS("data/all_modeled_marine_farms_31km.rds") %>%
   left_join(all_farms_to_place) %>%
@@
                           species == "Crustaceans" ~ "crustaceans")) %>%
-  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms))
+mutate(species_group = case_when(species == "Salmonids" ~ "Salmonidae fish",
+                          species == "Unfed or algae fed shellfish" ~ "Unfed or algae fed bivalve molluscs",
+                          species == "Shrimp" ~ "Shrimps and prawns", 
+                          species == "Tuna" ~ "Bluefin tuna", 
+                          species == "General Marine Fish" ~ "General marine fish", 
+                          species == "Crustaceans" ~ "Non-shrimp crustaceans")) %>% 
+  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms)) %>%
+  mutate(data_type_2 = case_when(
+    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms == 0 ~ "A",
+    known_farms_location == 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "B",
+    known_farms_location > 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "C",
+    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "D",
+    known_farms_location == 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "F",
+  )) %>%
+  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "E", data_type_2)) %>%
+  mutate(data_type_2 = ifelse(iso3c == "IND" & species == "Unfed or algae fed shellfish", "E", data_type_2)) ## fix some mismatches
+
+## data types with comprehensive # of farms are A, B, and C. These all recieve their production/# of farms to get prod per farm.
+
+## data types D, and E recieve global prod per farm estimates.
+
+## read in all species production
+
+biv_prod <- read_csv("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv") %>%
+  mutate(type = "bivalve")
+crust_prod <- read_csv("marine/crustaceans/crustaceans_farms/data/fao_mariculture_crustaceans.csv") %>%
+  mutate(type = "crustaceans")
+finfish_prod <- read_csv("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv") %>%
+  mutate(type = "marine_fish_general")
+salmon_prod <- read_csv("marine/salmon/salmon_farms/data/fao_mariculture_salmon.csv") %>%
+  mutate(type = "salmon")
+shrimp_prod <- read_csv("marine/shrimp/shrimp_farms/data/fao_mariculture_shrimp.csv") %>%
+  mutate(type = "shrimp")
+tuna_prod <- read_csv("marine/tuna/tuna_farms/data/fao_mariculture_tuna.csv") %>%
+  mutate(type = "tuna")
+
+all_prod <- rbind(biv_prod, crust_prod, finfish_prod, salmon_prod, shrimp_prod, tuna_prod) %>%
+  filter(year == 2017)
+
+spp_prod_per_farm <- read_csv("analysis/data/prod_per_farm.csv")
+
+sources_prod <- sources %>%
+  left_join(all_prod, by = c("iso3c", "type")) %>%
+  left_join(spp_prod_per_farm) %>% 
+  mutate(tonnes_per_farm = case_when(
+    data_type_2 %in% c("A", "B", "C") ~ fao_tonnes_production/number_of_total_farms,
+    data_type_2 %in% c("D", "F") ~ spp_prod_per_farm,
+    data_type_2 %in% c("E") ~ fao_tonnes_production/number_of_total_farms
+  )) %>%
+  dplyr::select(-country.y, -spp_prod_per_farm) %>%
+  rename("country" = "country.x")
+
+sources_prod_SI_table <- sources_prod %>%
+  dplyr::select(country, species_group, fao_tonnes_production, number_of_total_farms, tonnes_per_farm, data_type_2) %>%
+  arrange(country)
+
+write.csv(sources_prod_SI_table, "analysis/tables/SI_table_3.csv", row.names = FALSE)
 
@@
 all_farms_sources <- all_farms %>%
-  left_join(sources, by = c("iso3c", "type")) %>%
+  left_join(sources_prod, by = c("iso3c", "type")) %>%
   mutate(data_source = case_when(
@@
     data_type == "known location" ~ data_year_farm_locations)) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, details, data_source, data_year, tonnes_per_farm, geometry)
 
 unique(all_farms_sources$data_year)
+
 ```
@@
   )) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
-# check <- CAN_salmon_fix %>%
-#   st_drop_geometry() %>%
-#   group_by(data_source) %>%
-#   summarise(n()) ## numbers are correct
+check <- CAN_salmon_fix %>%
+  st_drop_geometry() %>%
+  group_by(data_source) %>%
+  summarise(n()) ## numbers are correct
 
@@
   )) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
-# check <- CAN_bivalve_fix %>%
-#   st_drop_geometry() %>%
-#   group_by(data_source) %>%
-#   summarise(n()) ## numbers are correct
+check <- CAN_bivalve_fix %>%
+  st_drop_geometry() %>%
+  group_by(data_source) %>%
+  summarise(n()) ## numbers are correct
 
@@
   )) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
-# check <- USA_salmon_fix %>%
-#   st_drop_geometry() %>%
-#   group_by(data_source) %>%
-#   summarise(n()) ## numbers are correct
+check <- USA_salmon_fix %>%
+  st_drop_geometry() %>%
+  group_by(data_source) %>%
+  summarise(n()) ## numbers are correct
 
@@
   )) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
@@
   mutate(data_year = 2018) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
-# check <- USA_bivalve_fix %>%
-#   st_drop_geometry() %>%
-#   group_by(data_source) %>%
-#   summarise(n()) ## numbers are correct
+check <- USA_bivalve_fix %>%
+  st_drop_geometry() %>%
+  group_by(data_source) %>%
+  summarise(n()) ## numbers are correct
 
@@
   mutate(data_year = 2021) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
@@
   mutate(data_year = ifelse(row %in% c(1:40), dy_1, dy_2)) %>%
-  dplyr::select(iso3c, country, species, data_type, details, data_source, data_year, geometry)
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
 
@@
   rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix) %>%
-  mutate(data_year = as.numeric(data_year))
+  mutate(data_year = as.numeric(data_year)) %>%
+  dplyr::select(-species)
 
@@
 unique(sort(all_farms_sources$iso3c)) ## 73 countries - perfect! 
+unique(all_farms_sources_final$species_group)
 
 ## Now save this as a csv
-st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources.csv", layer_options = "GEOMETRY=AS_XY")
+st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources_31km.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)
 
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
+all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
 ```

### 2021-07-09 analysis/paper_figs.Rmd
fixed so many things

@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv") %>% 
+all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
   mutate(data_type_plot = case_when(
@@
         legend.position = "bottom", 
-        legend.title=element_blank()) +
+        legend.title=element_blank(),
+        text=element_text(family="Times New Roman")) +
   guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
@@
                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("Known location \n n = 9,750", "Modeled location, known number of farms \n n = 10,519", "Modeled locations, estimated number of farms \n n = 75,073"))
-    #  geom_vline(xintercept = 135) + # check to make sure it lines up
-  #geom_hline(yintercept = 0) # check to make sure it lines up
 
 total_map
-
-# guides(colour=guide_legend(nrow=30))
 
@@
 ggdraw(plot_final)
-ggsave("analysis/figs/map_fig.jpg")
+ggsave("analysis/figs/map_fig_18km.jpg")
 
@@
         axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("A")  # + 
@@
         legend.key = element_rect(fill = NA),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("D")
@@
         axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("B")
@@
         axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("C")
@@
 plot1
-ggsave("analysis/figs/chl_ecu_zoom.jpg")
+ggsave("analysis/figs/chl_ecu_zoom_31km.jpg")
 
@@
 plot2
-ggsave("analysis/figs/usa_chn_zoom.jpg")
+ggsave("analysis/figs/usa_chn_zoom_31km.jpg")
 
-## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final.jpg"
+## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder
 

### 2021-07-09 analysis/paper_stats.Rmd
fixed so many things

@@
 
-## How much mariculture production was included in our assessment?
+## How much fish and invertebrate mariculture production was included in our assessment?
 
@@
   mutate(environment = ifelse(is.na(environment2), environment, environment2)) %>%
+  filter(environment != "Freshwater") %>%
   group_by(environment, year) %>%
@@
 
-## total marine animal production is: 8090542 + 22920871 = 31011413
+## total fish and invertebrate mariculture production included is: 8090542 + 22920871 = 31011413
 
@@
 
+```{r}
+prod_per_farm <- read_csv("marine/output/all_points_to_add.csv") %>%
+  distinct(type,avg_tonnes_per_farm)
+
+production_by_grouping <- all_farms %>%
+  group_by(iso3c, species_group, data_type) %>%
+  summarise(n_obs = n())
+
+```
+
 Countries with comprehensive farm locations 
@@
 country_spp_combos <- all_farms %>%
-  distinct(country, species)
+  distinct(country, species_group)
 
@@
     mutate(Species = case_when(
-      type == "salmon" ~ "Salmonids", 
-      type == "bivalve" ~ "Unfed or algae fed shellfish",
-      type == "marine_fish_general" ~ "General Marine Fish", 
-      type == "shrimp" ~ "Shrimp", 
-      type == "tuna" ~ "Tuna"
+      type == "salmon" ~ "Salmonidae fish", 
+      type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
+      type == "marine_fish_general" ~ "General marine fish", 
+      type == "shrimp" ~ "Shrimps and prawns", 
+      type == "tuna" ~ "Bluefin tuna"
     )) %>%
@@
 
+sum(all_comp_farms$`Tonnes of production`) # 4963244
+
+4963244/29623515 # 0.1675441 = ~17%
+
 comp_across_all <- all_comp_farms %>%
-  full_join(country_spp_combos, by = c("Country" = "country", "Species" = "species")) %>%
+  full_join(country_spp_combos, by = c("Country" = "country", "Species" = "species_group")) %>%
   mutate(Country = case_when(
@@
 
-sum(comp_across_all$tonnes) # account for 4328484 tonnes of production
+sum(comp_across_all$tonnes, na.rm = TRUE) # account for 4328484 tonnes of production
 
-4328484/29623515 # these account for ~15% of production tonnage
+4328484/29623515 # these account for ~15% of included production tonnage
 
@@
 
-# tuna_spp <- read_csv("marine/tuna/tuna_farms/data/fao_mariculture_tuna_taxa_production.csv")
 ```

### 2021-07-09 analysis/validation_testing.Rmd
fixed so many things

--- 2021-07-09 analysis/SI_figs.Rmd
@@
 ---
-title: "Figures for SI"
+title: "Validation Testing"
 author: "Gage Clawson (UCSB, NCEAS, OHI)"
-date: "06/14/2021"
+date: "07/08/2021"
 output: html_document
@@
 
-This script takes our final farms dataset and creates the figures which will be showcased in the SI.
+This script tests our validation set of points against our actual known points.
 
@@
 ```
-
-# Global regions
-
-```{r}
-
-# this file includes ocean regions:
-gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")
-
-gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
-# plot(gadm_latlon)
-
-gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
-  mutate(reg_id = as.numeric(reg_id))
-```
-
-# Read in farms data and convert to sf
-
-```{r}
-all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>%
-    st_as_sf(., 
-           coords = c("X", "Y"),
-           crs = crs(food_raster), 
-           agr = "constant")
-
-all_farms <- all_farms_sf %>%
-  st_drop_geometry()
-
-test <- all_farms_sf %>%
-  filter(country == "United States of America")
-mapview(test)
-
-test <- all_farms_sf %>%
-  filter(iso3c == "HRV")
-mapview(test) ## one weird MFG from ASC
-
-test <- all_farms_sf %>%
-  filter(iso3c == "TUR")
-mapview(test) ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...
-
-```
-
-```{r}
-
-all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
-
-unique(sort(all_farms$country))
-
-all_farms_stat <- all_farms %>%
-  mutate(lon = round(X, 0), 
-         lat = round(Y, 0))
-
-lon_stat <- all_farms_stat %>%
-  group_by(lon) %>%
-  summarise(n())
-
-lat_stat <- all_farms_stat %>%
-  group_by(lat) %>%
-  summarise(n())
-
-```
-
-## Make the global map by species group (Supplementary Figures 1-6)
-```{r}
-world <- ne_countries(scale = "medium", returnclass = "sf")
-class(world)
-
-# https://stackoverflow.com/questions/8545035/scatterplot-with-marginal-histograms-in-ggplot2
-
-## This one works!
-
-for(i in c(1, 2,3, 6)){
-
- # i = 4
-
-  spp_group <- unique(all_farms$species_group)[i]
-
-  all_farms_i <- all_farms %>%
-    filter(species_group == spp_group)
-
-  count_green_df <- all_farms_i %>%
-    group_by(data_type) %>%
-    summarise(n = n()) %>%
-    filter(data_type == "known location")
-
-  count_green <- count_green_df$n
-
-  count_yellow_df <-  all_farms_i %>%
-    group_by(data_type) %>%
-    summarise(n = n()) %>%
-    filter(data_type == "modeled location, known number of farms")
-
-  count_yellow <- count_yellow_df$n
-
-  count_red_df <- all_farms_i %>%
-    group_by(data_type) %>%
-    summarise(n = n()) %>%
-    filter(data_type == "modeled location, estimated number of farms")
-
-  count_red  <- count_red_df$n
-
-## create first plot
-total_map <- ggplot(data = world) +
-  geom_sf(fill = "white", lwd = 0.1) + 
-  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
-  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
-  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  theme_bw() + 
-  theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-        legend.position = "bottom", 
-        legend.title=element_blank(),
-        text=element_text(family="Times New Roman")) +
-  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
-  # scale_color_manual(values = c("forestgreen", "orange1"),
-  #                   breaks = c("known location", "modeled location, known number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow))) +
-    # scale_color_manual(values = c("red3"),
-    #                 breaks = c("modeled location, estimated number of farms"), labels = c(sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
-  labs(title = sprintf("Supplmentary Figure %s: %s farms", i, spp_group))
-
-# total_map
-
-# Create marginal plots
-# Use geom_density/histogram for whatever you plotted on x/y axis 
-plot_x <- axis_canvas(total_map, axis = "x") +
-  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
-  #  geom_vline(xintercept = 135) + # check to make sure it lines up
-  coord_sf(xlim = c(-180, 180), expand = FALSE) +
-  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
-plot_x
-
-plot_y <- axis_canvas(total_map, axis = "y") +
-  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
- #  geom_hline(yintercept = 0) + #  check to make sure it lines up
-  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
-  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
- # coord_flip() 
-plot_y
-
-# Combine all plots into one
-plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
-plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
-ggdraw(plot_final)
-
-ggsave(sprintf("analysis/figs/supp_map_fig_%s.jpg", spp_group))
-
-}
-
-```

### 2021-07-09 marine/STEP1_species_groups/STEP1_species_groups.Rmd
fixed so many things

--- 2021-05-18 marine/STEP1_species_groups/STEP1_species_groups.Rmd
@@
 
+test <- fao %>%
+  filter(year == 2017) %>%
+  left_join(mar_sp_list, by = c("species" = "FAO_name")) %>%
+  mutate(environment2 = ifelse(Taxon_code == "AL", "seaweed", environment)) %>%
+  mutate(environment = ifelse(is.na(environment2), environment, environment2)) %>%
+  filter(environment != "Freshwater") %>%
+  group_by(environment, year) %>%
+  summarise(prod = sum(value, na.rm = TRUE)) %>%
+  ungroup() %>%
+  mutate(total = sum(prod)) %>%
+  mutate(pct = prod/total)
 ```

### 2021-07-09 marine/crustaceans/crustaceans_farms/STEP1_fao_crustacean_production.Rmd
fixed so many things

@@
   summarize(fao_tonnes_production = sum(value)) %>%
-  arrange(country, iso3c, species, year)
+  arrange(country, iso3c, species, year) %>%
+  ungroup() %>%
+  mutate(total = sum(fao_tonnes_production)) %>%
+  mutate(perc = fao_tonnes_production/total)
 

### 2021-07-09 marine/marine_fish_general/finfish_farms/STEP1_fao_finfish_production.Rmd
fixed so many things

@@
 
-## Explore some of the data:         
-explore <- read_csv(here("marine/marine_fish_general/finfish_farms/data/fao_mariculture_finfish.csv")) %>%
-   filter(year==2017) %>%
-   arrange(-fao_tonnes_production) %>%
-   mutate(percent = round(fao_tonnes_production/sum(fao_tonnes_production)*100,2))
+## look at all groups
 
-sum(explore$fao_tonnes_production) # 3901214
-unique(explore$country) # 37 countries
-
-## explore ASC and emod data
-
-emod_countries <- explore %>%
-  dplyr::filter(country %in% c("Cyprus", "Greece", "Malta", "Norway", "Spain"))
-sum(emod_countries$percent)
-sum(emod_countries$fao_tonnes_production)
-
-## ASC Countries
- # "Turkey", "Croatia", "Greece", "Albania", "Spain", "Japan", "Australia", "Mexico", "Panama", "United States of America", "Viet Nam", "Thailand"
-
-asc_countries <- explore %>%
-  dplyr::filter(country %in% c( "Turkey", "Croatia", "Albania", "Japan", "Australia", "Mexico", "Panama", "United States of America", "Viet Nam", "Thailand"))
-sum(asc_countries$percent)
-sum(asc_countries$fao_tonnes_production)
-
-unique(sort(asc_countries$country))
+all_groups_included <- aquaculture_groups %>%
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  filter(value < 500) %>%  # countries with less do not appear to be stable producers at this point
+  group_by(year, iso3c, aq_group) %>%
+  summarize(fao_tonnes_production = sum(value)) %>%
+  arrange(iso3c, aq_group) %>%
+  #filter(year == 2017) %>%
+  ungroup()
+  #mutate(total_prod = sum(fao_tonnes_production)) %>%
+  #mutate(prop_prod = fao_tonnes_production/total_prod)
 

### 2021-07-09 workflow/calc_dist_to_port.Rmd
fixed so many things

---
title: "Calculate average distance to ports from known mariculture locations"
author: "Gage Clawson"
date: "06/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sf)
library(spatialEco)
library(tidyverse)
library(raster)
library(rgeos)
library(rmapshaper)
library(mapview)

# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
source("../_spatial/template_raster.R")

```

Read in all known farms

```{r}
data <- read_csv("../marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant") 
```

Read in ports dataset 
```{r}
the_crs <- crs(fake_raster, asText = TRUE)

ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/Commercial_ports.shp") %>%
  st_transform(the_crs) %>%
  filter(HARB_SIZE_ != "L") # remove L ports
```

Calculate the distance from each known location to the closest port

```{r}
# st_nearest_points

# st_distance

test_data <- data[1:3, ]

dist_ports <- as.data.frame(st_distance(ports_raw, test_data))

min(dist_ports$V1)
min(dist_ports$V2)
min(dist_ports$V3)

mapview(test_data)

test_df_final <- dist_ports %>%
  pivot_longer(cols = c(V1, V2, V3)) %>%
  group_by(name) %>%
  summarise(min_dist = min(value))

## ok so that works... i just to calculate the distance from each point in the whole known location dataset, and find the min of each column

dist_ports <- as.data.frame(st_distance(ports_raw, data)) ## calculate distance to each port from each known mariculture location

write.csv(dist_ports, "int/distance_to_ports_raw.csv")

write.csv(dist_ports, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/distance_from_known_to_ports_raw.csv", row.names = FALSE)

dist_ports <- read_csv("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/distance_from_known_to_ports_raw.csv")

dist_ports_final <- dist_ports %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  summarise(closest_port_km = as.numeric(min(value)*0.001)) %>%
  ungroup()

## add in species group identifier

data_df <- data %>%
  mutate(row_num = row_number()) %>%
  mutate(name = paste("V", row_num, sep =""))

spp_group_dist <- dist_ports_final %>%
  ungroup() %>%
  left_join(data_df) # %>%
  # filter(closest_port_km >= 1)

mean(spp_group_dist$closest_port_km) # 31.30463 km
sd(spp_group_dist$closest_port_km) # 32.333 km
range(spp_group_dist$closest_port_km) #  0.1312871 to 531.2067646
median(spp_group_dist$closest_port_km) # 18.85009 km

summary(spp_group_dist)

spp_group_dist_final <- spp_group_dist %>%
  group_by(type) %>%
  summarise(dist_port = mean(closest_port)) %>%
  ungroup()

```

### 2021-07-09 workflow/place_unknown_farms.R

@@ -34,15 +34,6 @@ ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_p
   filter(HARB_SIZE_ != "L") # remove L ports
 
 
-
-# test <- ports_raw %>%
-#   filter(HARB_SIZE_ == "L")
-# mapview(test)
-# 
-# test2 <- ports_raw %>%
-#   filter(HARB_SIZE_ != "L")
-# mapview(test2)
-
 data <- read_csv("marine/output/all_marine_farms.csv") %>% 
   st_as_sf(., 
            coords = c("lon", "lat"),
@@ -56,10 +47,6 @@ need_national_allocation <- read_csv("marine/output/all_points_to_add.csv") %>%
   group_by(iso3c, type) %>% 
   summarize(num_farms = sum(num_additional_farms))
 
-all_the_farm_points <- data %>% 
-  dplyr::select(iso3c, type) %>%
-  .[0, ]
-
 # create arctic raster 
 arctic_raster <- raster("/home/shares/food-systems/Aquaculture_mapping/latitude_abs.tif")
 crs(arctic_raster) <- crs(fake_raster)
@@ -67,15 +54,15 @@ m <- c(-1000, -66, 1, 1000, 66, 1,  -66, 66, NA)
 rclmat <- matrix(m, ncol=3, byrow=TRUE)
 arctic_raster <- reclassify(arctic_raster, c(66,Inf, NA, 0,66,1))
 
-arctic_fixed <- resample(arctic_raster, blank_raster, method = "ngb")
+arctic_fixed <- raster::resample(arctic_raster, blank_raster, method = "ngb")
 
 arctic_fixed <- inverted_land + arctic_fixed
 arctic_fixed[arctic_fixed[]==2] <- 1 ## add land mask
 
 
-for (i in 42) {
-  # 52:length(unique(need_national_allocation$iso3c))
-  # i = 42
+for (i in 36:length(unique(need_national_allocation$iso3c))) {
+  
+  # i = 2
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[i]
   
@@ -86,7 +73,7 @@ for (i in 42) {
   
   this_type_vector <- this_farm_info %>% 
     group_by(type) %>% 
-    expand(types = seq(1:num_farms)) %>% 
+    tidyr::expand(types = seq(1:num_farms)) %>% 
     pull(type) %>% 
     sample()
   
[…]

### 2021-07-09 workflow/place_validation_farms.R

@@ -1,0 +1,273 @@
+## This script will place specific number of farms with known locations using our location modelling approach. The resulting dataset will serve as a validation method for our modelling. 
+
+
+#### load libraries and data ####
+#------------------------------------------------------------------------------#
+library(sf)
+library(spatialEco)
+library(tidyverse)
+library(raster)
+library(rgeos)
+library(rmapshaper)
+library(mapview)
+
+# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
+source("./_spatial/template_raster.R")
+gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
+gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
+land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
+eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
+eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
+coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
+
+
+inverted_land <- land_mask
+inverted_land[is.na(inverted_land[])] <- .5
+inverted_land[inverted_land[]==1] <- NA
+inverted_land[inverted_land[]==.5] <- 1
+
+blank_raster <- food_raster
+blank_raster[] <- 1
+
+the_crs <- crs(fake_raster, asText = TRUE)
+
+
+ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/Commercial_ports.shp") %>%
+  st_transform(the_crs) %>%
+  filter(HARB_SIZE_ != "L") # remove L ports
+
+
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant") 
+
+tonnage_per_farms <- read_csv("marine/output/all_points_to_add.csv") %>% 
[…]

### 2021-07-09 workflow/qualtiy_control_filters.R

@@ -1,296 +1,0 @@
-#------------------------------------------------------------------------------#
-## Project :  Aquaculture Mapping
-## Purpose :  Generate
-## Date    :  02/11/2021
-## Author  :  Gordon Blasco
-#------------------------------------------------------------------------------#
-
-
-#### load libraries and data ####
-#------------------------------------------------------------------------------#
-library(sf)
-library(spatialEco)
-library(tidyverse)
-library(raster)
-library(rgeos)
-
-# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
-source("./_spatial/template_raster.R")
-gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
-gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
-land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
-eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
-eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
-coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
-
-#x <- raster("/home/shares/food-systems/Aquaculture_mapping/Data/ports/distance-from-port-v20201104.tiff")
-
-#plot(x)
-# ports_gfw <- read_csv("/home/shares/food-systems/Aquaculture_mapping/Data/ports/named_anchorages_v2_20201104.csv") %>% 
-#   st_as_sf(coords = c("lon", "lat"),
-#            crs = 4326) %>% 
-#   head(400)
-
-#mapview::mapview(ports_gfw, zcol = "at_dock")
-
-the_crs <- crs(fake_raster, asText = TRUE)
-# depth and ports
-ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
-  st_transform(the_crs)
-
-#all_ports_sp <- as(ports_raw, "Spatial")
-#dist_ports_raster <- distanceFromPoints(food_raster, all_ports_sp)
[…]

### 2021-07-09 workflow/small_split.R

@@ -1,129 +1,0 @@
-#### load libraries and data ####
-#------------------------------------------------------------------------------#
-library(sf)
-library(spatialEco)
-library(tidyverse)
-library(raster)
-library(rgeos)
-
-# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
-source("./_spatial/template_raster.R")
-gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
-gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
-land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
-eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
-eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
-coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
-
-
-the_crs <- crs(fake_raster, asText = TRUE)
-
-ports_raw <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
-  st_transform(the_crs)
-
-
-
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant") 
-
-need_national_allocation <- read_csv("marine/output/all_points_to_add.csv") %>% 
-  group_by(iso3c, type) %>% 
-  summarize(num_farms = sum(num_additional_farms))
-
-all_the_farm_points <- data %>% 
-  dplyr::select(iso3c, type) %>%
-  .[0, ]
-
-
-#4326
-# use     #st_transform(crs = "+proj=moll") %>%  for buffering in meters
-
-for (i in 1:length(unique(need_national_allocation$iso3c))) {
-
-  this_iso3 <- unique(need_national_allocation$iso3c)[i]
-  
-  this_country <- gadm_full %>% 
-    filter(GID_0 == this_iso3) %>% 
-    group_by(GID_0) %>% 
[…]

### 2021-07-19 analysis/SI_figs.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

@@
   filter(country == "United States of America")
-mapview(test)
+mapview(test, zcol = "data_type_2")
+
+test <- all_farms_sf %>%
+  filter(iso3c == "MEX")
+mapview(test, zcol = "data_type_2")
 
@@
 
-for(i in c(1, 2,3, 6)){
+for(i in 1:6){
 
@@
 
+    count_type_df <- all_farms_i %>%
+    group_by(species_group) %>%
+    summarise(n=n())
+
+  count_type <- count_type_df$n
+
     count_green_df <- all_farms_i %>%
@@
     summarise(n = n()) %>%
-    filter(data_type == "known location")
+    filter(data_type == "known locations")
 
   count_green <- count_green_df$n
+
+if(is.empty(count_green) == TRUE){
+    count_green = 0
+  }
 
@@
     summarise(n = n()) %>%
-    filter(data_type == "modeled location, known number of farms")
+    filter(data_type == "modeled locations, known number of farms")
 
   count_yellow <- count_yellow_df$n
+
+if(is.empty(count_yellow) == TRUE){
+    count_yellow = 0
+  }
 
@@
     summarise(n = n()) %>%
-    filter(data_type == "modeled location, estimated number of farms")
+    filter(data_type == "modeled locations, estimated number of farms")
 
   count_red  <- count_red_df$n
+
+if(is.empty(count_red) == TRUE){
+    count_red = 0
+  }
 
@@
   geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
+  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
   scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
@@
         legend.title=element_blank(),
-        text=element_text(family="Times New Roman")) +
-  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
+        text=element_text(family="Times New Roman"), 
+        legend.justification='left',
+        legend.direction='horizontal') +
+  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow = ifelse(spp_group %in% c("Bluefin tuna", "Non-shrimp crustaceans"), 1, 2))) +
   scale_color_manual(values = c("forestgreen", "orange1", "red3"),
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
-  # scale_color_manual(values = c("forestgreen", "orange1"),
-  #                   breaks = c("known location", "modeled location, known number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow))) +
-    # scale_color_manual(values = c("red3"),
-    #                 breaks = c("modeled location, estimated number of farms"), labels = c(sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
-  labs(title = sprintf("Supplmentary Figure %s: %s farms", i, spp_group))
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE) +
+  labs(caption = sprintf("%s: N = %s", spp_group, count_type))
+
+# total_map
+
+# Create marginal plots
+# Use geom_density/histogram for whatever you plotted on x/y axis 
+plot_x <- axis_canvas(total_map, axis = "x") +
+  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
+  coord_sf(xlim = c(-180, 180), expand = FALSE) +
+  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
+
+plot_y <- axis_canvas(total_map, axis = "y") +
+  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
+  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
+  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
+ # coord_flip()
+
+# Combine all plots into one
+plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
+plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
+ggdraw(plot_final)
+
+ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", spp_group))
+}
+
+```
+
+## Make the global map by data type 2 (A,B,C,D,E,F) (Supplementary Figures 7-12)
+
+```{r}
+world <- ne_countries(scale = "medium", returnclass = "sf")
+class(world)
+
+# https://stackoverflow.com/questions/8545035/scatterplot-with-marginal-histograms-in-ggplot2
+
+## This one works!
+
+for(i in c(1:6)){
+
+ # i = 1
+
+  data_type_2_id <- unique(all_farms$data_type_2)[i]
+
+  all_farms_i <- all_farms %>%
+    filter(data_type_2 == data_type_2_id)
+
+  count_type_df <- all_farms_i %>%
+    group_by(data_type_2) %>%
+    summarise(n=n())
+
+  count_type <- count_type_df$n
+
+    count_green_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "known locations")
+
+  count_green <- count_green_df$n
+
+if(is.empty(count_green) == TRUE){
+    count_green = 0
+  }
+
+  count_yellow_df <-  all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled locations, known number of farms")
+
+  count_yellow <- count_yellow_df$n
+
+if(is.empty(count_yellow) == TRUE){
+    count_yellow = 0
+  }
+
+  count_red_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled locations, estimated number of farms")
+
+  count_red  <- count_red_df$n
+
+if(is.empty(count_red) == TRUE){
+    count_red = 0
+  }
+
+## create first plot
+total_map <- ggplot(data = world) +
+  geom_sf(fill = "white", lwd = 0.1) + 
+  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
+  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
+  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
+  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
+  theme_bw() + 
+  theme(axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+        legend.position = "bottom", 
+        legend.title=element_blank(),
+        text=element_text(family="Times New Roman"), 
+        legend.justification='left',
+        legend.direction='horizontal') +
+  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9) )) +
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE) +
+  labs(caption = sprintf("Data type %s: N = %s", data_type_2_id, count_type))
 
@@
   scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
 plot_x
@@
   scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
  # coord_flip() 
@@
 
-ggsave(sprintf("analysis/figs/supp_map_fig_%s.jpg", spp_group))
+ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", data_type_2_id))
 
@@
 ```
+
+## Make maps for diagram
+
+First map: 
+ - All data type A, and known locations from data type C and D
+
+ Second map: 
+ - Unknown locations from B, C, D, E, & F
+    - All F
+    - All E
+    - All B
+    - Unknown C
+    - Unknown D
+
+**First diagram map**
+```{r}
+
+  all_farms_i <- all_farms %>%
+    filter(data_type_2 %in% c("A", "C", "D")) %>%
+  filter(data_type == "known locations")
+
+    count_green_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "known locations")
+
+  count_green <- count_green_df$n
+
+if(is.empty(count_green) == TRUE){
+    count_green = 0
+  }
+
+  count_yellow_df <-  all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled locations, known number of farms")
+
+  count_yellow <- count_yellow_df$n
+
+if(is.empty(count_yellow) == TRUE){
+    count_yellow = 0
+  }
+
+  count_red_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled locations, estimated number of farms")
+
+  count_red  <- count_red_df$n
+
+if(is.empty(count_red) == TRUE){
+    count_red = 0
+  }
+
+## create first plot
+total_map <- ggplot(data = world) +
+  geom_sf(fill = "white", lwd = 0.1) + 
+  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
+  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
+  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
+  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
+  theme_bw() + 
+  theme(axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+        legend.position = "bottom", 
+        legend.title=element_blank(),
+        text=element_text(family="Times New Roman"),
+        legend.justification='left',
+        legend.direction='horizontal') +
+  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9))) +
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE)
+
+total_map
+
+# Create marginal plots
+# Use geom_density/histogram for whatever you plotted on x/y axis 
+plot_x <- axis_canvas(total_map, axis = "x") +
+  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
+  #  geom_vline(xintercept = 135) + # check to make sure it lines up
+  coord_sf(xlim = c(-180, 180), expand = FALSE) +
+  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
+
+plot_y <- axis_canvas(total_map, axis = "y") +
+  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
+ #  geom_hline(yintercept = 0) + #  check to make sure it lines up
+  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
+  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
+ # coord_flip()
+
+# Combine all plots into one
+plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
+plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
+ggdraw(plot_final)
+
+ggsave("analysis/si_figs/workflow_fig_1.jpg")
+
+```
+
+**Second diagram map**
+```{r}
+
+  all_farms_i <- all_farms %>%
+    filter(data_type_2 %in% c("B", "C", "D", "E", "F")) %>%
+  filter(data_type != "known locations")
+
+    count_green_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "known locations")
+
+  count_green <- count_green_df$n
+
+if(is.empty(count_green) == TRUE){
+    count_green = 0
+  }
+
+  count_yellow_df <-  all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled locations, known number of farms")
+
+  count_yellow <- count_yellow_df$n
+
+if(is.empty(count_yellow) == TRUE){
+    count_yellow = 0
+  }
+
+  count_red_df <- all_farms_i %>%
+    group_by(data_type) %>%
+    summarise(n = n()) %>%
+    filter(data_type == "modeled locations, estimated number of farms")
+
+  count_red  <- count_red_df$n
+
+if(is.empty(count_red) == TRUE){
+    count_red = 0
+  }
+
+## create first plot
+total_map <- ggplot(data = world) +
+  geom_sf(fill = "white", lwd = 0.1) + 
+  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
+  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
+  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
+  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
+  theme_bw() + 
+  theme(axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+        legend.position = "bottom", 
+        legend.title=element_blank(),
+        text=element_text(family="Times New Roman"),
+        legend.justification='left',
+        legend.direction='horizontal') +
+  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9))) +
+  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE)
+
+total_map
+
+# Create marginal plots
+# Use geom_density/histogram for whatever you plotted on x/y axis 
+plot_x <- axis_canvas(total_map, axis = "x") +
+  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
+  #  geom_vline(xintercept = 135) + # check to make sure it lines up
+  coord_sf(xlim = c(-180, 180), expand = FALSE) +
+  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
+
+plot_y <- axis_canvas(total_map, axis = "y") +
+  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
+ #  geom_hline(yintercept = 0) + #  check to make sure it lines up
+  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
+  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
+ # coord_flip()
+
+# Combine all plots into one
+plot_final <- insert_xaxis_grob(total_map, plot_x, position = "top")
+plot_final <- insert_yaxis_grob(plot_final, plot_y, position = "right") 
+ggdraw(plot_final)
+
+ggsave("analysis/si_figs/workflow_fig_2.jpg")
+
+```

### 2021-07-19 analysis/match_data_sources.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

@@
     mutate(data_type = case_when(
-    source == "real" ~ "known location", 
-    source == "modeled" & estimated == 0 ~ "modeled location, known number of farms",
-    source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
+    source == "real" ~ "known locations", 
+    source == "modeled" & estimated == 0 ~ "modeled locations, known number of farms",
+    source == "modeled" & estimated == 1 ~ "modeled locations, estimated number of farms"
   )) %>%
@@
   )) %>%
-  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "E", data_type_2)) %>%
+  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "D", data_type_2)) %>%
   mutate(data_type_2 = ifelse(iso3c == "IND" & species == "Unfed or algae fed shellfish", "E", data_type_2)) ## fix some mismatches
@@
   mutate(tonnes_per_farm = case_when(
+        str_detect(details, "Although") ~ fao_tonnes_production/number_of_total_farms,
     data_type_2 %in% c("A", "B", "C") ~ fao_tonnes_production/number_of_total_farms,
     data_type_2 %in% c("D", "F") ~ spp_prod_per_farm,
-    data_type_2 %in% c("E") ~ fao_tonnes_production/number_of_total_farms
-  )) %>%
+    data_type_2 %in% c("E") ~ fao_tonnes_production/number_of_total_farms  )) %>%
   dplyr::select(-country.y, -spp_prod_per_farm) %>%
@@
   mutate(data_source = case_when(
-    data_type == "modeled location, known number of farms" ~ datasource_number_of_farms,
-    data_type == "modeled location, estimated number of farms" ~ "NA", 
-    data_type == "known location" ~ datasource_farm_locations), 
+    data_type == "modeled locations, known number of farms" ~ datasource_number_of_farms,
+    data_type == "modeled locations, estimated number of farms" ~ "NA", 
+    data_type == "known locations" ~ datasource_farm_locations), 
   data_year = case_when(
-    data_type == "modeled location, known number of farms" ~ data_year_number_of_farms,
-    data_type == "modeled location, estimated number of farms" ~ "NA", 
-    data_type == "known location" ~ data_year_farm_locations)) %>%
+    data_type == "modeled locations, known number of farms" ~ data_year_number_of_farms,
+    data_type == "modeled locations, estimated number of farms" ~ "NA", 
+    data_type == "known locations" ~ data_year_farm_locations)) %>%
   dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, details, data_source, data_year, tonnes_per_farm, geometry)
@@
 all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
+
+test <- all_farms %>%
+  filter(iso3c == "IND", str_detect(species_group, "bivalve"))
 ```

### 2021-07-19 analysis/paper_figs.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

--- 2021-06-11 analysis/paper_figs.Rmd
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")
+all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
+  mutate(data_type_plot = case_when(
+    data_type == "modeled locations, known number of farms" ~ "Modeled locations, known number of farms",
+    data_type == "modeled locations, estimated number of farms" ~ "Modeled locations, estimated number of farms", 
+    data_type == "known locations" ~ "Known locations"
+  ))
 
@@
   geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
+  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
   scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
@@
         legend.position = "bottom", 
-        legend.title=element_blank()) +
+        legend.title=element_blank(),
+        text=element_text(family="Times New Roman")) +
   guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
-    #  geom_vline(xintercept = 135) + # check to make sure it lines up
-  #geom_hline(yintercept = 0) # check to make sure it lines up
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n n = 9,750", "Modeled locations, known number of farms \n n = 10,519", "Modeled locations, estimated number of farms \n n = 75,073"))
 
 total_map
-
-# guides(colour=guide_legend(nrow=30))
 
@@
   geom_histogram(data = all_farms, aes(X, fill = data_type), bins = 360)  +
-  #  geom_vline(xintercept = 135) + # check to make sure it lines up
   coord_sf(xlim = c(-180, 180), expand = FALSE) +
   scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"))
 plot_x
@@
   scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
- # coord_flip() 
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"))
+
 plot_y
@@
 ggdraw(plot_final)
-ggsave("analysis/figs/map_fig.jpg")
+ggsave("analysis/figs/map_fig_31km.jpg")
 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
   coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
-  # coord_sf(crs = 4326, xlim = c(-75, -72.5), ylim = c(-46, -44), expand = FALSE) +
   theme(legend.position = "bottom", ## put legend on bottom
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
+                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
   coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
-  #coord_sf(crs = 4326) + 
   theme(legend.position = "bottom", 
@@
         legend.key = element_rect(fill = NA),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("D")
-  #border(linetype = "longdash")
-        #panel.border = element_rect(colour = "black", fill=NA, size=5))
 chn_zoom
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
+                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
   coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
-  #coord_sf(crs = 4326) + 
   theme(legend.position = "bottom", 
@@
         axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("B")
-  #border(linetype = "longdash")
-        #panel.border = element_rect(colour = "black", fill=NA, size=5))
 ecu_zoom
 
-## Norway
-nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
+# ## Norway
+# nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
+#   annotation_map_tile(type = "osm", zoomin = 0) + 
+#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
+#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
+#                     breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
+#     coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
+#   theme(legend.position = "bottom", 
+#         legend.title=element_blank(), 
+#         axis.title.x = element_blank(), 
+#         axis.title.y = element_blank(),
+#         legend.key = element_rect(fill = NA),
+#         axis.text.x = element_text(angle = 60, hjust = 1),
+#         text=element_text(family="Times New Roman"),
+# panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
+#   ggtitle("C")
+# nor_zoom
+
+## USA NE 
+usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
-    coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
+                    breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
+    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
   theme(legend.position = "bottom", 
@@
         axis.text.x = element_text(angle = 60, hjust = 1),
-panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
+        text=element_text(family="Times New Roman"),
+panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
   ggtitle("C")
-  #border(linetype = "longdash")
-        #panel.border = element_rect(colour = "black", fill=NA, size=5))
-nor_zoom
 
-# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+usa_zoom
+
+## Plot with USA instead of norway
 
@@
 plot1
-ggsave("analysis/figs/chl_ecu_zoom.jpg")
+ggsave("analysis/figs/chl_ecu_zoom_31km.jpg")
 
-plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+plot2 <- (usa_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
 
 plot2
-ggsave("analysis/figs/nor_chn_zoom.jpg")
+ggsave("analysis/figs/usa_chn_zoom_31km.jpg")
 
-## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final.jpg"
+## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder
 
 ```
-
-## Radial bar chart of estimation type per country
-
-```{r}
-library(tidyverse)
-library(viridis)
-library(hrbrthemes)
-library(RColorBrewer)
-library(colorspace)
-
-rank_rgn <- all_farms %>%
-  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
-  group_by(country) %>%
-  summarise(num_farms_total = n()) %>%
-  ungroup() %>%
-  arrange(num_farms_total)
-
-## Stuff for both plots
-# i think that this would look better with each stressor having its own color that is paired with ocean/land
-# 
-# pick 4 distinct colors and then create a pair with one being more brown or green and the other being more blue
-
-source_name <- data.frame(source = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
-
-type_1 <- "forestgreen"
-type_1 <- lighten(type_1, amount = -0.05)
-type_2 <- "orange1"
-type_2 <- lighten(type_2, amount = -0.05)
-type_3 <- "red3"
-type_3 <- lighten(type_3, amount = -0.05)
-
-gc_palette <- c(type_1, type_2, type_3)
-scales::show_col(gc_palette, n = 3)
-
-pal_df <- as_tibble(gc_palette) %>% 
-  rename(fill_value = value) %>% 
-  mutate(source = case_when(fill_value == type_1 ~ "known location",
-                            fill_value == type_2 ~ "modeled location, known number of farms",
-                            fill_value == type_3 ~ "modeled location, estimated number of farms"))
-
-## circle plot
-
-cutoff_value <-  1000
-
-by_country <- all_farms %>%
-  mutate(country = ifelse(country == "United Kingdom (Scotland) ", "United Kingdom", country)) %>%
-  group_by(country, data_type) %>%
-  summarise(num_farms = n()) %>%
-  ungroup() %>%
-  group_by(country) %>%
-  mutate(num_farms_total = sum(num_farms)) %>%
-  ungroup() %>%
-  arrange(num_farms_total) %>%
-  filter(num_farms_total < cutoff_value)
-
-##grab the highest country to highlight red and id where the circle ends and then side bar chart begins
-highest_country <- by_country[dim(by_country)[1], "country"]
-farms_highest_country <- filter(by_country, country %in% highest_country$country) #used below
-
-# adjust the rank_rgn-adjust dataframe to match above
-rank_rgn_adj <- rank_rgn %>%
-  filter(country %in% by_country$country)
-
-# add empty space to create space in the circleplot for axes
- empty_bar <- 5
- to_add <- data.frame(matrix(NA, empty_bar, ncol(rank_rgn_adj)) )
- colnames(to_add) = colnames(rank_rgn_adj)
- to_add$country <- as.character(1:empty_bar)
- rank_rgn_adj  <- rbind(to_add, rank_rgn_adj)
-
- # some code to orient the country labels
-sequence_length = length(unique(rank_rgn_adj$country))
-first_sequence = c(1:(sequence_length%/%2)) 
-second_sequence = c((sequence_length%/%2+1):sequence_length) 
-first_angles = c(90 - 180/length(first_sequence) * first_sequence)
-second_angles = c(-90 - 180/length(second_sequence) * second_sequence)
-rank_rgn_adj$angle <- c(first_angles, second_angles)
-rank_rgn_adj$hjust <- c(rep(0, length(first_sequence)), 
-                    rep(1, length(second_sequence)))
-
-# color for region labels
-rank_rgn_adj <- rank_rgn_adj %>%
-  mutate(country = factor(country, unique(country))) %>%
-  mutate(color = "black") %>%
-  mutate(color = ifelse(is.na(num_farms_total), "white", color)) %>%
-  mutate(color = ifelse(country %in% highest_country$country, "red", color))
-
-## make the plot
-
-circle_theme <- theme(axis.line=element_blank(),
-                      axis.text.y=element_blank(),
-                      axis.ticks=element_blank(),
-                      axis.title.x=element_blank(),
-                      axis.title.y=element_blank(),
-                      legend.position="none",
-                      panel.background=element_blank(),
-                      panel.border=element_blank(),
-                      panel.grid.major=element_blank(),
-                      panel.grid.minor=element_blank(),
-                      plot.background=element_blank(),
-                      axis.text.x = element_blank())
-
-color_order <- c(type_1, type_2, type_3)
-
-pressures_adj_circle_plot <- by_country %>% 
-  mutate(prop_of_global_stacked = abs(num_farms)) %>% 
-  left_join(pal_df, by = c("data_type" = "source")) %>% 
-  mutate(fill_value = factor(fill_value, levels = color_order))
-
- ggplot(data=pressures_adj_circle_plot, aes(x=country, y=prop_of_global_stacked, fill = fill_value)) +
-
-  geom_bar(stat="identity") +
-
-  # ## this adjust the inner circle size (ymin) and outer circle size (ymax), which can be expanded to include names
-   geom_errorbar(aes(
-       x     = 1,
-        ymin = -0.01,   # ymin  = -0.03, this is for when ocean bars stack inwards -0.01 for when not
-       ymax  = 0.035),
-       alpha = 0) +
-      # Country name text placement
-     geom_text(
-       data = rank_rgn_adj,
-       aes(x     = country,
-           y     = max(by_country$num_farms_total, na.rm=TRUE),
-           label = country,
-           angle = angle,
-           hjust = hjust),
-       inherit.aes = FALSE,
-       fontface = "bold",
-       alpha = 0.9,
-       size = 4,
-       color = rank_rgn_adj$color) +
-    # 
-   # georegion names
-    # geom_text(
-    #   data=rgn_shift,
-    #   aes(y = 0.02, x = name_x, label = georegion),
-    #   # aes(x=name_x,
-    #   #     y=name_y,
-    #   #     label=georegion),
-    #   inherit.aes=FALSE, size=7) +
-  #  
-  # # # Scale bar circles
-  # ## This adds the 0 line
-      geom_segment(
-        x = 0, 
-         y = 0, 
-         xend = dim(rank_rgn_adj)[1]+1, 
-         yend = 0, 
-         fill = NULL,
-        alpha = 1, color = "white", size = 0.1) + #color = "black for internal
-  #    
-  #  # Scale bar annotation, this adds the y-axis numbers
-      annotate("text",
-        x     = c(3, 3, 3),
-        y     = c(0, 0.0175, 0.035),
-        label = c(0, 0.0175, 0.035),
-        color = "darkgray", angle = -4, size = 4) +
-  #     
-  scale_color_identity() +
-   scale_fill_identity() +
-   # scale_fill_manual(values= rev(myPalette), c("Land: Disturbance", "Land: GHG", "Land: Water", "Land: Nutrient",
-   #                                    "Ocean: Disturbance", "Ocean: GHG", "Ocean: Water", "Ocean: Nutrient")) +
-  coord_polar() +
- circle_theme
-
-```
-
-ARCHIVE: Other ways of trying to visualize
-```{r}
-
-## philippines
-# phl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-#   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 1, alpha = 0.7) + 
-#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   coord_sf(crs = 4326, xlim = c(120.25, 122.5), ylim = c(17, 19), expand = FALSE) +
-#   #coord_sf(crs = 4326) + 
-#   theme(legend.position = "bottom", 
-#         legend.title=element_blank(), 
-#         axis.title.x = element_blank(), 
-#         axis.title.y = element_blank(),
-# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("B")
-#   #border(linetype = "longdash")
-#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-# phl_zoom
-
-## California - bay area 
-# cal_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-#   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 1, alpha = 0.7) + 
-#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   coord_sf(crs = 4326, xlim = c(-123, -121), ylim = c(37, 39), expand = FALSE) +
-#   #coord_sf(crs = 4326) + 
-#   theme(legend.position = "bottom", 
-#         legend.title=element_blank(), 
-#         axis.title.x = element_blank(), 
-#         axis.title.y = element_blank(),
-# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("B")
-#   #border(linetype = "longdash")
-#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-# cal_zoom
-
-## New Zealand
-# nzl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
-#   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
-#   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
-#   # coord_sf(crs = 4326, ylim = c(-48, -34), xlim = c(165, 180), expand = FALSE) + ## all of new zealand
-#    coord_sf(crs = 4326, ylim = c(-41, -34), xlim = c(172, 180), expand = FALSE) + ## north island
-#   theme(legend.position = "bottom", 
-#         legend.title=element_blank(), 
-#         axis.title.x = element_blank(), 
-#         axis.title.y = element_blank(),
-#         axis.text.x = element_text(angle = 60, hjust = 1),
-# panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("D")
-#   #border(linetype = "longdash")
-#         #panel.border = element_rect(colour = "black", fill=NA, size=5))
-# nzl_zoom
-
-## all together
-total_map <- ggplot(data = world) +
-  geom_sf(fill = "white", lwd = 0.1) + 
-  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.2) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
-  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
-  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  theme_bw() + 
-  theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(), 
-        legend.position = "none") 
-total_map
-
-## make longitude histogram
-
-lon_hist <- ggplot(data = all_farms) + 
-  geom_histogram(aes(X, fill = data_type), bins = 360) + 
-  # scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180)) +
-  # scale_y_reverse() +
-   theme_void() + 
-    theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(), 
-        legend.position = "none") # +
-  # geom_vline(xintercept = 135) 
-lon_hist
-
-## make latitude histogram
-lat_hist <- ggplot(data = all_farms) + 
-  geom_histogram(aes(Y, fill = data_type), bins = 180) + 
-  # scale_x_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  # xlim(-58, 73) + 
-  coord_flip() +
-   theme_void() + 
-    theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(), 
-        legend.position = "none") # + 
-  # geom_vline(xintercept = 0)
-
-lat_hist
-
-require(gridExtra)
-library(cowplot)
-library(egg)
-
-## using ggExtra
-library(ggExtra)
-ggExtra::ggMarginal(total_map, type = "histogram", groupFill = TRUE, size = 2)
-
-## using patchwork
-lon_hist + plot_spacer() + total_map + lat_hist + 
-  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))
-
-## using cowplot
-plot_grid(
-  lon_hist
-  , NULL
-  , total_map
-  , lat_hist
-  , ncol = 2
-  , nrow = 2
-  , rel_heights = c(0.2, 1)
-  , rel_widths = c(1, 0.2)
-)
-
-```
-
-```{r}
-
-test_data <- all_farms %>%
-  filter(data_type != "known location")
-
-## create first plot
-total_map <- ggplot(data = world) +
-  geom_sf(fill = "white", lwd = 0.1) + 
-  geom_point(data = test_data, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
-#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
-  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
-  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
-  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
-  theme_bw() + 
-  theme(axis.title.x = element_blank(),
-          axis.title.y = element_blank(),
-        legend.position = "bottom", 
-        legend.title=element_blank()) +
-  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
-  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
-    #  geom_vline(xintercept = 135) + # check to make sure it lines up
-  #geom_hline(yintercept = 0) # check to make sure it lines up
-
-total_map
-
-ggsave("analysis/figs/map_fig_test.jpg")
-
-```

### 2021-07-19 analysis/paper_stats.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

@@
 
-# test <- all_farms_sf %>%
-#   filter(iso3c == "USA")
-# mapview(test)
-
 ```
@@
 # 1 known location                               9750     95341  10.2
-# 2 modeled location, estimated number of farms 75072     95341  78.7
+# 2 modeled location, estimated number of farms 75073     95341  78.7
 # 3 modeled location, known number of farms     10519     95341  11.0
@@
 
-# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of all points, and only had 15 known location points
+# China represented 61% of all farms (N=58,166), but only 15 had known locations.
 
 chn_data_estimated <- all_farms %>%
-  filter(iso3c == "CHN") #%>%
-  #filter(data_type == "modeled location, estimated number of farms")
+  filter(iso3c == "CHN") 
 # 58166 points
-58151/95342 # 0.6099201 = 61%
+58166/95342 # 0.6099201 = 61%
 
@@
 
-no_info_at_all <- sources %>%
-  dplyr::filter(known_farms_location == 0, known_farms_no_location == 0) ## only 5 with no information at all
+no_info <- all_farms %>%
+  group_by(iso3c) %>%
+  mutate(check = all(data_type_2 == "F")) %>%
+  filter(check == TRUE) 
+unique(no_info$country)
+
+# [1] "Cambodia"                              "Myanmar"                              
+# [3] "Mauritius"                             "Democratic People’s Republic of Korea"
+# [5] "Russian Federation"
 
@@
 
-no_info_production <- mar_production %>%
-  filter(country %in% c("Cambodia", "Mauritius", "Myanmar", "Korea, Dem. People's Rep", "Russian Federation"))
-sum(no_info_production$total_tonnes) # 152800.1
+sum(no_info$tonnes_per_farm) # 155205.1
 
 sum(mar_production$total_tonnes) # 29623515
-152800.1/29623515
+
+155205.1/29623515 # 0.005239253
 
@@
 sum(chn_production$total_tonnes)
-17696822/29623515
+17696822/29623515 # 0.597391
 
@@
 by_species_data_type <- all_farms %>%
-  group_by(species, data_type) %>%
+  group_by(species_group, data_type) %>%
   summarise(n_obs = n()) %>%
@@
 
-## total fish and invertebrate mariculture production included is: 8090542 + 22920871 = 31011413
+## total fish and invertebrate mariculture production is: 8090542 + 22920871 = 31011413
 
@@
 
+Countries with comprehensive farm locations
+
+However, 16 countries (representing 10% of fish and invertebrate mariculture production) had comprehensive farm locations across all taxa (i.e. no estimation or interpolation required, Table S3)
 ```{r}
-prod_per_farm <- read_csv("marine/output/all_points_to_add.csv") %>%
-  distinct(type,avg_tonnes_per_farm)
 
-production_by_grouping <- all_farms %>%
-  group_by(iso3c, species_group, data_type) %>%
-  summarise(n_obs = n())
+all_comp <- all_farms %>%
+  group_by(iso3c) %>%
+  mutate(check = all(data_type_2 == "A")) %>%
+  filter(check == TRUE)
+
+sort(unique(all_comp$country))
+
+print(unique(all_comp$country))
+
+cat(paste(sort(unique(all_comp$country)), collapse= "', '"))
+
+# Belize, Bulgaria, Canada, Chile, Cyprus, Denmark, Faroe Islands, Finland, French Polynesia, Greece, Hong Kong , Ireland, Jersey, Malta, Norway, United Arab Emirates, United Kingdom
+
+## how much production do they account for?
+
+mar_production <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv")
+
+comp_prod <- mar_production %>%
+  filter(country %in% c('Belize', 'Bulgaria', 'Canada', 'Chile', 'Cyprus', 'Denmark', 'Faroe Islands', 'Finland', 'French Polynesia', 'Greece', 'China, Hong Kong SAR', 'Ireland', 'Jersey', 'Malta', 'Norway', 'United Arab Emirates', 'United Kingdom'))
+
+sum(comp_prod$total_tonnes) # 3203584
+
+3203584/31011413 # 0.1033034 ~ 10%
 
@@
 
-Countries with comprehensive farm locations 
+Countries with comprehensive "number of farm" information
+
+"Thirty-six of the countries in the table have comprehensive “number of farm” data across all types of mariculture they produce (data types A, B, or C), accounting for 12% of the global fish and invertebrate mariculture production (Albania, Belize, Bulgaria, Canada, Chile, Colombia, Croatia, Cyprus, Denmark, El Salvador, Faroe Islands, Finland, French Polynesia, Germany, Greece, Guatemala, Guernsey, Hong Kong, Ireland, Italy, Jersey, Madagascar, Malta, Netherlands, New Zealand, Norway, Peru, Portugal, Singapore, Slovenia, South Africa, Sri Lanka, Tunisia, Turkey, United Arab Emirates, United Kingdom)."
+
 ```{r}
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
+all_comp <- all_farms %>%
+  group_by(iso3c) %>%
+  mutate(check = all(data_type_2 %in% c("A", "B", "C"))) %>%
+  filter(check == TRUE)
+sort(unique(all_comp$country))
 
-unique(sort(all_farms$country))
+cat(paste(sort(unique(all_comp$country)), collapse= "', '"))
 
-country_spp_combos <- all_farms %>%
-  distinct(country, species_group)
+# Albania', 'Belize', 'Bulgaria', 'Canada', 'Chile', 'Colombia', 'Croatia', 'Cyprus', 'Denmark', 'El Salvador ', 'Faroe Islands', 'Finland', 'French Polynesia', 'Germany', 'Greece', 'Guatemala', 'Guernsey', 'Hong Kong ', 'Ireland', 'Italy', 'Jersey', 'Madagascar', 'Malta', 'Netherlands', 'New Zealand', 'Norway', 'Peru', 'Portugal', 'Singapore', 'Slovenia', 'South Africa', 'Sri Lanka', 'Tunisia', 'Turkey', 'United Arab Emirates', 'United Kingdom
 
-## read in each of the comprehensive locations
+## how much production do they account for?
 
-bivalve_comp <- read_csv("marine/bivalve/bivalve_farms/output/bivalve_comp_tonnes_per_farm.csv")
+mar_production <- read_csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv")
 
-shrimp_comp <- read_csv("marine/shrimp/shrimp_farms/output/shrimp_comp_tonnes_per_farm.csv")
+comp_prod <- mar_production %>%
+  filter(country %in% c('Albania', 'Belize', 'Bulgaria', 'Canada', 'Chile', 'Colombia', 'Croatia', 'Cyprus', 'Denmark', 'El Salvador ', 'Faroe Islands', 'Finland', 'French Polynesia', 'Germany', 'Greece', 'Guatemala', 'Guernsey', 'Hong Kong ', 'Ireland', 'Italy', 'Jersey', 'Madagascar', 'Malta', 'Netherlands', 'New Zealand', 'Norway', 'Peru', 'Portugal', 'Singapore', 'Slovenia', 'South Africa', 'Sri Lanka', 'Tunisia', 'Turkey', 'United Arab Emirates', 'United Kingdom'))
 
-salmon_comp <- read_csv("marine/salmon/salmon_farms/output/salmon_comp_tonnes_per_farm.csv")
+sum(comp_prod$total_tonnes) # 3788091
 
-tuna_comp <- read_csv("marine/tuna/tuna_farms/output/tuna_comp_tonnes_per_farm.csv")
+3788091/31011413 # 0.1221515 ~ 10%
 
-finfish_comp <- read_csv("marine/marine_fish_general/finfish_farms/output/finfish_comp_tonnes_per_farm.csv")
+```
 
-all_comp_farms <- rbind(finfish_comp, bivalve_comp, salmon_comp, tuna_comp, shrimp_comp) %>%
-    mutate(Species = case_when(
-      type == "salmon" ~ "Salmonidae fish", 
-      type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
-      type == "marine_fish_general" ~ "General marine fish", 
-      type == "shrimp" ~ "Shrimps and prawns", 
-      type == "tuna" ~ "Bluefin tuna"
-    )) %>%
-  mutate(tonnes_per_farm = round(tonnes_per_farm, 2)) %>%
-  dplyr::select("Country" = "country", Species, "Number of farms" = "n_farms", "Tonnes of production" = "fao_tonnes_production", "Tonnes per farm" = "tonnes_per_farm") %>%
-  arrange(Country)
+Using the country/species grouping combinations with presumed comprehensive farm count data (N=74, 17% of production included, data type A/B/C, see Table S3)
+```{r}
 
- unique(all_comp_farms$Country)
+test <- all_farms %>%
+  filter(data_type_2 %in% c("A", "B", "C")) %>%
+  group_by(country, species_group)
 
-write.csv(all_comp_farms, "analysis/output/all_comp_farms.csv", row.names = FALSE)
+cat(paste(sort(unique(test$country)), collapse= "', '"))
 
-sum(all_comp_farms$`Tonnes of production`) # 4963244
+sum(test$tonnes_per_farm)
 
-4963244/29623515 # 0.1675441 = ~17%
-
-comp_across_all <- all_comp_farms %>%
-  full_join(country_spp_combos, by = c("Country" = "country", "Species" = "species_group")) %>%
-  mutate(Country = case_when(
-    Country == "Iran" ~ "Iran (Islamic Rep. of)", 
-    Country == "Hong Kong " ~ "China, Hong Kong SAR",
-    TRUE ~ Country
-  )) %>%
-  filter(Country %in% all_comp_farms$Country) %>%
-  group_by(Country) %>%
-  summarise(n_obs = sum(`Number of farms`), 
-            n_species = n(),
-            tonnes = sum(`Tonnes of production`)) %>%
-  filter(!is.na(n_obs))
-
-sum(comp_across_all$tonnes, na.rm = TRUE) # account for 4328484 tonnes of production
-
-4328484/29623515 # these account for ~15% of included production tonnage
-
-## these are the countries that are comprehensive across all species groups they report
-cat(comp_across_all$Country, sep = ", ")
+4963244/29623515 # 0.1675441 ~ 17%
 
@@
  - System comprehensiveness: 4
-
-Some random exploring
-```{r}
-by_type <- all_farms %>%
-  group_by(species) %>%
-  summarise(n_obs = n())
-
-by_country_type <- all_farms %>%
-  group_by(iso3c, species) %>%
-  summarise(n_obs = n()) %>%
-  left_join(sources) %>%
-  dplyr::select(iso3c, species, n_obs, number_of_total_farms) %>%
-  mutate(difference = n_obs - number_of_total_farms)
-
-by_data_type_country <- all_farms %>%
-  group_by(iso3c, species, data_type) %>%
-  summarise(n_obs = n()) %>%
-  ungroup() %>%
-  left_join(sources) %>%
-  dplyr::select(iso3c, species, data_type, n_obs, number_of_total_farms, known_farms_location, known_farms_no_location, estimated_farms)
-
-known <- by_data_type_country %>%
-  filter(data_type == "known location") %>%
-  dplyr::select(iso3c, species, data_type, n_obs, known_farms_location) %>%
-  mutate(difference = n_obs - known_farms_location)
-
-number_known <- by_data_type_country %>% 
-  filter(data_type == "modeled location, known number of farms") %>%
-  dplyr::select(iso3c, species, data_type, n_obs, known_farms_no_location) %>%
-  mutate(difference = n_obs - known_farms_no_location)
-
-estimated <- by_data_type_country %>% 
-  filter(data_type == "modeled location, estimated number of farms") %>%
-  dplyr::select(iso3c, species, data_type, n_obs, estimated_farms) %>%
-  mutate(difference = n_obs - estimated_farms)
-
-```

### 2021-07-19 analysis/validation_testing.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

@@
 library(RCurl)
-library("rnaturalearth")
-library("rnaturalearthdata")
-library(cowplot) 
-library(ggpubr)
-library(RColorBrewer)
-library(OpenStreetMap)
-library(ggspatial)
 library(ggplot2)
-library(patchwork)
+library(fasterize)
+library(tabularaster)
+library(countrycode)
+library(caret)
 
@@
 
+cell_rast_df <- raster_df(food_raster) %>%
+  dplyr::select(1:2)
+
+## establish CRSs
+
+## food 81km2 at equator 
+eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask.tif"))
+plot(area(eez_81))
+
+## 36km2 equal area
+eez_36_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask_cea_36km.tif"))
+
+new_crs <- "+proj=cea +lat_ts=45 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
+new_raster <- raster(nrows=3000, ncols=4736, xmn=-14207430, xmx=14208570, ymn=-9000182, ymx=8999818, crs = new_crs)
+
+## 25km2 equal area
+eez_25_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask_cea_25km.tif"))
+
+cea_25_crs <- crs(eez_25_cea)
+plot(eez_25_cea)
+
+## 1/4 degree cells 
+eez_quart_cell <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask_quarter_degree.tif"))
+
+quarter_crs <- crs(eez_quart_cell)
+
 ```
+
+Read in validation dataset
+
+```{r}
+validation_all <- readRDS(file.path("data/all_validation_farms.rds"))  %>%
+  mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
+                          type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
+                          type == "shrimp" ~ "Shrimps and prawns", 
+                          type == "tuna" ~ "Bluefin tuna", 
+                          type == "marine_fish_general" ~ "General marine fish"))
+
+table_3 <- read_csv("analysis/tables/SI_table_3.csv")
+
+iso <-   data.frame(iso3c = countrycode(table_3$country, origin = 'country.name', destination = 'iso3c'))
+
+table_3_iso3c <- table_3 %>%
+  cbind(iso)
+
+data_type_val <- validation_all %>%
+  left_join(table_3_iso3c, by = c("iso3c", "species_group"))
+
+data_type_A <- data_type_val %>%
+  filter(data_type_2 == "A")
+
+mapview(data_type_A, zcol = "source")
+
+table_3_A <- table_3_iso3c %>%
+  filter(data_type_2 == "A")
+
+```
+
+Split data
+
+```{r}
+validation_farms <- data_type_A %>%
+ filter(source == "modeled validation") %>%
+  mutate(count_farms = 1)
+
+val_farms_cea_36 <- validation_farms %>%
+  st_transform(crs = new_crs)
+
+val_farms_cea_25 <- validation_farms %>%
+  st_transform(crs = cea_25_crs)
+
+val_farms_quarter <- validation_farms %>%
+  st_transform(crs = quarter_crs)
+
+real_farms <- data_type_A %>%
+  filter(source == "real") %>%
+  mutate(count_farms = 1)
+
+real_farms_cea_36 <- real_farms %>%
+  st_transform(crs = new_crs)
+
+real_farms_cea_25 <- real_farms %>%
+  st_transform(crs = cea_25_crs)
+
+real_farms_quart <- real_farms %>%
+  st_transform(crs = quarter_crs)
+```
+
+Rasterize data to count number of farms per raster cell with 36km2 equal area
+
+```{r}
+
+val_rast <- rasterize(val_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum")
+
+plot(val_rast, col = "black")
+#s <- raster::select(val_rast)
+#plot(s)
+
+real_rast <- rasterize(real_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8455
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8455    8455
+
+```
+
+Use our EEZ mask to create a confusion matrix for CEA 36km2 cell sizes
+
+ - AUC of ~0.61
+```{r}
+
+plot(eez_36_cea, col = "black")
+
+world_coast <- as.data.frame(eez_36_cea) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask_cea_36km))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8446
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8377
+
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms
+
+test <- rast_stack*eez_36_cea
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8455    7917
+
+## we are losing some farms...
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction       0       1
+#          0 1171915    2492
+#          1    2762     695
+#                                           
+#                Accuracy : 0.9955          
+#                  95% CI : (0.9954, 0.9957)
+#     No Information Rate : 0.9973          
+#     P-Value [Acc > NIR] : 1.0000000       
+#                                           
+#                   Kappa : 0.207           
+#                                           
+#  Mcnemar's Test P-Value : 0.0002063       
+#                                           
+#             Sensitivity : 0.9976          
+#             Specificity : 0.2181          
+#          Pos Pred Value : 0.9979          
+#          Neg Pred Value : 0.2010          
+#              Prevalence : 0.9973          
+#          Detection Rate : 0.9949          
+#    Detection Prevalence : 0.9971          
+#       Balanced Accuracy : 0.6079          
+#                                           
+#        'Positive' Class : 0
+
+library(pROC)
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.6019
+
+library(pROC)
+library(randomForest)
+
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 0.6068
+
+roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
+
+roc.df <- data.frame(tpp = roc.info$sensitivities*100,
+                     fpp = (1-roc.info$specificities)*100,
+                     thresholds = roc.info$thresholds)
+
+#### ROC curve try #2
+# https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
+
+library(ROCR)
+
+pred = eez_cells_df$pred_count
+
+pred = prediction(pred, eez_cells_df$real_count)
+
+perf = performance(pred, "acc")
+plot(perf)
+
+perf_cost <- performance(pred, "cost")
+plot(perf_cost)
+
+roc = performance(pred, "tpr", "fpr")
+
+plot(roc, colorize = T, lwd=2)
+abline(a=0, b=1)
+
+auc = performance(pred, measure = "auc")
+print(auc@y.values)
+# 0.6091016
+
+```
+
+Use our EEZ mask to create a confusion matrix for CEA 25km2 cell sizes
+
+ - AUC of ~0.59 - worse than 36km2... makes sense! 
+```{r}
+
+val_rast <- rasterize(val_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum")
+
+plot(val_rast, col = "black")
+#s <- raster::select(val_rast)
+#plot(s)
+
+real_rast <- rasterize(real_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8455
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8455    8455
+
+plot(eez_25_cea, col = "black")
+
+world_coast <- as.data.frame(eez_25_cea) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask_cea_25km))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8450
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8386
+
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms. This is likely due to reprojection weirdness
+
+test <- rast_stack*eez_25_cea
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8450    8386
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction       0       1
+#          0 1689389    2864
+#          1    3071     654
+#                                           
+#                Accuracy : 0.9965          
+#                  95% CI : (0.9964, 0.9966)
+#     No Information Rate : 0.9979          
+#     P-Value [Acc > NIR] : 1.000000        
+#                                           
+#                   Kappa : 0.1788          
+#                                           
+#  Mcnemar's Test P-Value : 0.007496        
+#                                           
+#             Sensitivity : 0.9982          
+#             Specificity : 0.1859          
+#          Pos Pred Value : 0.9983          
+#          Neg Pred Value : 0.1756          
+#              Prevalence : 0.9979          
+#          Detection Rate : 0.9961          
+#    Detection Prevalence : 0.9978          
+#       Balanced Accuracy : 0.5920          
+#                                           
+#        'Positive' Class : 0
+
+library(pROC)
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.6019
+
+library(pROC)
+library(randomForest)
+
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 0.6068
+
+roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
+
+roc.df <- data.frame(tpp = roc.info$sensitivities*100,
+                     fpp = (1-roc.info$specificities)*100,
+                     thresholds = roc.info$thresholds)
+
+#### ROC curve try #2
+# https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
+
+library(ROCR)
+
+pred = eez_cells_df$pred_count
+
+pred = prediction(pred, eez_cells_df$real_count)
+
+perf = performance(pred, "acc")
+plot(perf)
+
+perf_cost <- performance(pred, "cost")
+plot(perf_cost)
+
+roc = performance(pred, "tpr", "fpr")
+
+plot(roc, colorize = T, lwd=2)
+abline(a=0, b=1)
+
+auc = performance(pred, measure = "auc")
+print(auc@y.values)
+# 0.5920433
+
+```
+
+Use our EEZ mask to create a confusion matrix for 0.25 X 0.25 degree cell sizes (about 769.3152km2 at equator). Average cell size is 490.3108 km2
+
+ - AUC of ~0.7241861 ; makes sense that is it better!
+
+```{r}
+test <- raster::area(eez_quart_cell)
+
+cellStats(test, "mean") # 490.3108
+
+mean(test@data@values) # 490.3108
+
+val_rast <- rasterize(val_farms_quarter, eez_quart_cell, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum")
+
+plot(val_rast, col = "black")
+#s <- raster::select(val_rast)
+#plot(s)
+
+real_rast <- rasterize(real_farms_quart, eez_quart_cell, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8455
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8455    8455
+
+plot(eez_quart_cell, col = "black")
+
+world_coast <- as.data.frame(eez_quart_cell) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask_quarter_degree))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8124
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8080
+
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra farms. This is likely due to reprojection weirdness
+
+test <- rast_stack*eez_quart_cell
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8124    8080
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction     0     1
+#          0 84497   619
+#          1   982   527
+#                                           
+#                Accuracy : 0.9815          
+#                  95% CI : (0.9806, 0.9824)
+#     No Information Rate : 0.9868          
+#     P-Value [Acc > NIR] : 1               
+#                                           
+#                   Kappa : 0.3878          
+#                                           
+#  Mcnemar's Test P-Value : <2e-16          
+#                                           
+#             Sensitivity : 0.9885          
+#             Specificity : 0.4599          
+#          Pos Pred Value : 0.9927          
+#          Neg Pred Value : 0.3492          
+#              Prevalence : 0.9868          
+#          Detection Rate : 0.9754          
+#    Detection Prevalence : 0.9826          
+#       Balanced Accuracy : 0.7242          
+#                                           
+#        'Positive' Class : 0
+
+recall <- 527/(527+619) # 0.46
+
+precision <- 527 / (527 + 982) # 0.3492379
+
+accuracy <- (84497 + 982)/(84497 + 982 + 527 + 619) # 0.9867706
+
+f_measure <- (2*recall*precision)/(recall + precision) # 0.33
+
+specificity = (84497)/(84497 + 982) # 0.9885118
+
+balanced_accuracy <- (recall + specificity)/2 # 0.7242 - this is also the AUC - which is pretty good.
+
+g_measure <- sqrt(precision*recall) # 0.401
+
+library(pROC)
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.7242
+
+library(pROC)
+library(randomForest)
+
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 72.42
+
+roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
+
+roc.df <- data.frame(tpp = roc.info$sensitivities*100,
+                     fpp = (1-roc.info$specificities)*100,
+                     thresholds = roc.info$thresholds)
+
+#### ROC curve try #2
+# https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
+
+library(ROCR)
+
+pred = eez_cells_df$pred_count
+
+pred = prediction(pred, eez_cells_df$real_count)
+
+perf = performance(pred, "acc")
+plot(perf)
+
+perf_cost <- performance(pred, "cost")
+plot(perf_cost)
+
+roc = performance(pred, "tpr", "fpr")
+
+plot(roc, colorize = T, lwd=2)
+abline(a=0, b=1)
+
+auc = performance(pred, measure = "auc")
+print(auc@y.values)
+# 0.7241861
+
+```
+
+Use our EEZ mask to create a confusion matrix for XX degree cell sizes (about 81km2 at equator)
+
+ - AUC of ~ 0.5950; about the same as the 25km2 size. Makes sense, because the average area is somewhere around there (since this isnt equal area). 
+```{r}
+
+val_rast <- rasterize(validation_farms, eez_81, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum")
+
+plot(val_rast, col = "black")
+#s <- raster::select(val_rast)
+#plot(s)
+
+real_rast <- rasterize(real_farms, eez_81, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8455
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8455    8455
+
+plot(eez_81, col = "black")
+
+world_coast <- as.data.frame(eez_81) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8452
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8350
+
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra farms. This is likely due to reprojection weirdness
+
+test <- rast_stack*eez_81
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8124    8080
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction      0      1
+#          0 757504   2266
+#          1   2137    541
+#                                           
+#                Accuracy : 0.9942          
+#                  95% CI : (0.9941, 0.9944)
+#     No Information Rate : 0.9963          
+#     P-Value [Acc > NIR] : 1.00000         
+#                                           
+#                   Kappa : 0.1944          
+#                                           
+#  Mcnemar's Test P-Value : 0.05373         
+#                                           
+#             Sensitivity : 0.9972          
+#             Specificity : 0.1927          
+#          Pos Pred Value : 0.9970          
+#          Neg Pred Value : 0.2020          
+#              Prevalence : 0.9963          
+#          Detection Rate : 0.9935          
+#    Detection Prevalence : 0.9965          
+#       Balanced Accuracy : 0.5950          
+#                                           
+#        'Positive' Class : 0
+
+library(pROC)
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.5950
+
+library(pROC)
+library(randomForest)
+
+roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 0.5950
+
+roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
+
+roc.df <- data.frame(tpp = roc.info$sensitivities*100,
+                     fpp = (1-roc.info$specificities)*100,
+                     thresholds = roc.info$thresholds)
+
+#### ROC curve try #2
+# https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
+
+library(ROCR)
+
+pred = eez_cells_df$pred_count
+
+pred = prediction(pred, eez_cells_df$real_count)
+
+perf = performance(pred, "acc")
+plot(perf)
+
+perf_cost <- performance(pred, "cost")
+plot(perf_cost)
+
+roc = performance(pred, "tpr", "fpr")
+
+plot(roc, colorize = T, lwd=2)
+abline(a=0, b=1)
+
+auc = performance(pred, measure = "auc")
+print(auc@y.values)
+# 0.5950
+
+```
+
+Resampling test: 
+```{r}
+
+### Manual equal rebalancing
+z_ind <- which(eez_cells_df$pred_count == 1)
+zz_ind <- which(eez_cells_df$pred_count == 0)
+
+nsamp = 3455
+pick_z <- sample(z_ind, nsamp)
+pick_zz <- sample(zz_ind, nsamp)
+
+new_data <- eez_cells_df[c(pick_z, pick_zz), ]
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(new_data$pred_count), reference = as.factor(new_data$real_count))
+
+confusion_mat
+
+library(ROCR)
+
+pred = new_data$pred_count
+
+pred = prediction(pred, new_data$real_count)
+
+perf = performance(pred, "acc")
+plot(perf)
+
+perf_cost <- performance(pred, "cost")
+plot(perf_cost)
+
+roc = performance(pred, "tpr", "fpr")
+
+plot(roc, colorize = T, lwd=2)
+abline(a=0, b=1)
+
+auc = performance(pred, measure = "auc")
+print(auc@y.values)
+# 0.7264348
+
+#### Over/undersampling 
+install.packages("ROSE")
+library(ROSE)
+
+test <- eez_cells_df %>%
+  filter(pred_count == 1)
+
+## not sure what the statistically correct way of picking the sampling number is... 
+data_balanced_under <- ovun.sample(pred_count ~ real_count, data = eez_cells_df, method = "under", N = 8455)
+table(data_balanced_under$data)
+
+#           real_count
+# pred_count    0    1
+#          0 4894  106
+#          1 2761  694
+
+## still pretty unbalanced, but it is a lot better than it was...
+
+recall <- 694/(694+106) # 0.8675
+
+precision <- 694 / (694 + 2761) # 0.20
+
+accuracy <- (4894 + 2761)/(4894 + 2761 + 106 + 694) # 0.91
+
+f_measure <- (2*recall*precision)/(recall + precision) # 0.33
+
+sensitivity = (4894)/(4894 + 2761) # 0.64
+
+balanced_accuracy <- (recall + sensitivity)/2 # 0.75 - this is also the AUC - which is pretty good.
+
+g_measure <- sqrt(precision*recall) # 0.42
+
+false_pos_rate <- 2761/(2761+4894) # 0.36
+
+```

### 2021-07-19 workflow/coast_buffer.R

@@ -1,0 +1,233 @@
+## This script will buffer the coastline of each place which has known locations and save each as a file. When it is done it will compile them all together and rasterize.
+## We will use this raster to validate our model. 
+
+#### load libraries and data ####
+#------------------------------------------------------------------------------#
+library(sf)
+library(spatialEco)
+library(tidyverse)
+library(raster)
+library(rgeos)
+library(rmapshaper)
+library(mapview)
+library(fasterize)
+
+# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
+source("./_spatial/template_raster.R")
+gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
+gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
+land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
+eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
+eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
+coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
+
+
+inverted_land <- land_mask
+inverted_land[is.na(inverted_land[])] <- .5
+inverted_land[inverted_land[]==1] <- NA
+inverted_land[inverted_land[]==.5] <- 1
+
+blank_raster <- food_raster
+blank_raster[] <- 1
+
+the_crs <- crs(fake_raster, asText = TRUE)
+
+
+
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant") 
+
+
+data <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
+  st_as_sf(., 
+           coords = c("X", "Y"),
[…]

### 2021-07-19 workflow/coast_buffer_archive.R

@@ -1,0 +1,320 @@
+## This script will buffer the coastline of each place which has known locations and save each as a file. When it is done it will compile them all together and rasterize.
+## We will use this raster to validate our model. 
+
+#### load libraries and data ####
+#------------------------------------------------------------------------------#
+library(sf)
+library(spatialEco)
+library(tidyverse)
+library(raster)
+library(rgeos)
+library(rmapshaper)
+library(mapview)
+library(fasterize)
+
+# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
+source("./_spatial/template_raster.R")
+gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
+gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
+land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
+eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
+eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
+coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
+
+
+inverted_land <- land_mask
+inverted_land[is.na(inverted_land[])] <- .5
+inverted_land[inverted_land[]==1] <- NA
+inverted_land[inverted_land[]==.5] <- 1
+
+blank_raster <- food_raster
+blank_raster[] <- 1
+
+the_crs <- crs(fake_raster, asText = TRUE)
+
+
+
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
+           agr = "constant") 
+
+
+data <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
+  st_as_sf(., 
+           coords = c("X", "Y"),
[…]

### 2021-07-19 workflow/place_unknown_farms.R

@@ -177,7 +177,6 @@ for (i in 36:length(unique(need_national_allocation$iso3c))) {
     st_as_sf() %>% 
     st_union()%>% 
     sf::st_as_sf()
-
   
   this_suitable_coast <- st_intersection(this_coast_meters, this_cell_polygons) %>%
    st_collection_extract("LINESTRING") %>%  # comment this out for <= 200m

### 2021-07-19 workflow/place_validation_farms.R

@@ -231,9 +231,8 @@ for (i in 1:length(unique(need_validation_allocation$iso3c))) {
 all_farms <- list.files("data/temp_data/temp_validation", pattern = "rds$", full.names = TRUE) %>% 
   map_df(., readRDS) %>% 
   rename(iso3c = iso3) %>% 
-  dplyr::mutate(source = "modeled") %>% 
-  rbind(data %>% dplyr::mutate(source = "real")) %>% 
-  left_join(tonnage_per_farms)
+  dplyr::mutate(source = "modeled validation") %>% 
+  rbind(data %>% dplyr::mutate(source = "real")) 
 
 n_placed_known <- all_farms %>% 
   st_set_geometry(NULL) %>% 

### 2021-07-19 analysis/paper_figs.Rmd
fine tuned figure 2

@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n n = 9,750", "Modeled locations, known number of farms \n n = 10,519", "Modeled locations, estimated number of farms \n n = 75,073"))
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n N = 9,750", "Modeled locations, known number of farms \n N = 10,519", "Modeled locations, estimated number of farms \n N = 75,073"))
 

### 2021-08-12 analysis/SI_figs.Rmd
cleaned up scripts and READMEs

@@
 ```{r}
-all_farms_sf <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>%
+all_farms_sf <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
     st_as_sf(., 
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv")
 
@@
 
-if(is.empty(count_green) == TRUE){
+if(is_empty(count_green) == TRUE){
     count_green = 0
@@
 
-if(is.empty(count_yellow) == TRUE){
+if(is_empty(count_yellow) == TRUE){
     count_yellow = 0
@@
 
-if(is.empty(count_red) == TRUE){
+if(is_empty(count_red) == TRUE){
     count_red = 0

### 2021-08-12 analysis/match_data_sources.Rmd
cleaned up scripts and READMEs

@@
 
-This script takes the farms dataset produced from prior steps, and matches to our data source spreadsheet, so that each point in the final database has a source associated with it (or an NA, if it was estimated).
+This script takes the farms dataset produced from prior steps, and matches to our data source spreadsheet (created manually in our literature review), so that each point in the final database has a source associated with it (or an NA, if it was estimated).
 
@@
 
-all_farms <- readRDS("data/all_modeled_marine_farms_31km.rds") %>%
+all_farms <- readRDS("data/all_modeled_marine_farms_final.rds") %>%
   left_join(all_farms_to_place) %>%
@@
 
-## data types D, and E recieve global prod per farm estimates.
+## data types D, E, and F receive global prod per farm estimates.
 
@@
                species == "Unfed or algae fed shellfish", 
-               data_type == "known location") %>%
+               data_type == "known locations") %>%
   separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
@@
                species == "General Marine Fish", 
-               data_type == "known location") %>%
+               data_type == "known locations") %>%
   separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>% 
@@
   filter(iso3c != "USA"|species != "Salmonids") %>%
-  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known location") %>%
-  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known location") %>%
-  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known location") %>%
+  filter(iso3c != "USA"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
+  filter(iso3c != "AUS"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
+  filter(iso3c != "TWN"|species != "General Marine Fish"|data_type != "known locations") %>%
   filter(iso3c != "USA"|species != "Shrimp") %>%
@@
 ## Now save this as a csv
-st_write(all_farms_sources_final, "all_marine_aquaculture_farms_sources_31km.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)
+st_write(all_farms_sources_final, "data/all_marine_aquaculture_farms_sources_final.csv", layer_options = "GEOMETRY=AS_XY", delete_dsn = TRUE)
 
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv")
 
 test <- all_farms %>%
-  filter(iso3c == "IND", str_detect(species_group, "bivalve"))
+  filter(iso3c == "CRI", str_detect(species_group, "hrimp")) %>%
+    st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
+
+mapview(test)
+
 ```

### 2021-08-12 analysis/paper_figs.Rmd
cleaned up scripts and READMEs

@@
 library(patchwork)
+library(rfishbase)
 
@@
   filter(iso3c == "HRV")
-mapview(test) ## one weird MFG from ASC
+mapview(test, zcol = "data_type") ## one weird MFG from ASC
 
 test <- all_farms_sf %>%
-  filter(iso3c == "TUR")
-mapview(test) ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...
+  filter(iso3c == "ECU")
+mapview(test, zcol = "data_type") ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...
+
+test <- all_farms_sf %>%
+  filter(data_type_2 %in% c("A", "B", "C"))
+sum(test$tonnes_per_farm)
+
+3568135/sum(all_farms_sf$tonnes_per_farm) # 0.1203892
+
+4963244/sum(all_farms_sf$tonnes_per_farm) # 0.1674603
 
@@
 
-all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>% 
   mutate(data_type_plot = case_when(
@@
   annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
+  geom_spatial_point(size = 1.25, alpha = 0.7) + 
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
@@
   annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
+  geom_spatial_point(size = 1.3, alpha = 0.7) + 
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
@@
   annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 0.5, alpha = 0.7) + 
+  geom_spatial_point(size = 1.5, alpha = 0.7) + 
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
@@
 panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
-  ggtitle("C")
+  ggtitle("C") # + 
+ # scale_alpha_manual(values = c(0.7, 0.7, 1))
 
@@
 
-## Plot with USA instead of norway
+## Chile and Ecuador
 
@@
 ggsave("analysis/figs/chl_ecu_zoom_31km.jpg")
+
+## USA and China
 

### 2021-08-12 analysis/paper_stats.Rmd
cleaned up scripts and READMEs

@@
   st_as_sf(coords =c("X", "Y"))
+
+sum(all_farms$tonnes_per_farm) # 29638328
+
+data_type_A <- all_farms %>%
+  filter(data_type_2 == "A")
+
+sum(data_type_A$tonnes_per_farm) # 3568135
+
+data_type_no_A <- all_farms %>%
+  filter(data_type_2 != "A")
+sum(data_type_no_A$tonnes_per_farm) # 26070193
+
+26070193/29638328 # 0.8796108
+
+test <- all_farms %>%
+  filter(species_group == "General marine fish")
+
+sum(test$tonnes_per_farm) # 3909255
+
+3909255/29638328 # 0.1318986
 

### 2021-08-12 analysis/validation_testing.Rmd
cleaned up scripts and READMEs

@@
 eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_validation_mask.tif"))
-plot(area(eez_81))
+plot(raster::area(eez_81))
+
+cellStats(raster::area(eez_81), "mean")
+
+test <- data.frame(raster::values(raster::area(eez_81)))
 
@@
 ```{r}
-validation_all <- readRDS(file.path("data/all_validation_farms.rds"))  %>%
+validation_all <- readRDS(file.path("data/all_validation_farms_fix_shrimp.rds"))  %>%
   mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
@@
 
- - AUC of ~0.61
+ - AUC of ~0.60
 ```{r}
@@
 
-sum(eez_cells_df$predicted, na.rm = TRUE) # 8446
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8442
 
@@
 # layer.1 layer.2 
-#    8455    7917
+#    8442    8377
 
@@
 
- - AUC of ~0.59 - worse than 36km2... makes sense! 
+ - AUC of ~0.58 - worse than 36km2... makes sense! 
 ```{r}
@@
 
-sum(eez_cells_df$predicted, na.rm = TRUE) # 8450
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8445
 
@@
 # layer.1 layer.2 
-#    8450    8386
+#    8445    8386
 
@@
 
- - AUC of ~0.7241861 ; makes sense that is it better!
+ - AUC of ~7042 ; makes sense that is it better!
 
@@
 plot(val_rast, col = "black")
-#s <- raster::select(val_rast)
-#plot(s)
 
@@
 
-## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra farms. This is likely due to reprojection weirdness
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra farms.
 
@@
 ```
-
-Resampling test: 
-```{r}
-
-### Manual equal rebalancing
-z_ind <- which(eez_cells_df$pred_count == 1)
-zz_ind <- which(eez_cells_df$pred_count == 0)
-
-nsamp = 3455
-pick_z <- sample(z_ind, nsamp)
-pick_zz <- sample(zz_ind, nsamp)
-
-new_data <- eez_cells_df[c(pick_z, pick_zz), ]
-
-confusion_mat <- caret::confusionMatrix(data = as.factor(new_data$pred_count), reference = as.factor(new_data$real_count))
-
-confusion_mat
-
-library(ROCR)
-
-pred = new_data$pred_count
-
-pred = prediction(pred, new_data$real_count)
-
-perf = performance(pred, "acc")
-plot(perf)
-
-perf_cost <- performance(pred, "cost")
-plot(perf_cost)
-
-roc = performance(pred, "tpr", "fpr")
-
-plot(roc, colorize = T, lwd=2)
-abline(a=0, b=1)
-
-auc = performance(pred, measure = "auc")
-print(auc@y.values)
-# 0.7264348
-
-#### Over/undersampling 
-install.packages("ROSE")
-library(ROSE)
-
-test <- eez_cells_df %>%
-  filter(pred_count == 1)
-
-## not sure what the statistically correct way of picking the sampling number is... 
-data_balanced_under <- ovun.sample(pred_count ~ real_count, data = eez_cells_df, method = "under", N = 8455)
-table(data_balanced_under$data)
-
-#           real_count
-# pred_count    0    1
-#          0 4894  106
-#          1 2761  694
-
-## still pretty unbalanced, but it is a lot better than it was...
-
-recall <- 694/(694+106) # 0.8675
-
-precision <- 694 / (694 + 2761) # 0.20
-
-accuracy <- (4894 + 2761)/(4894 + 2761 + 106 + 694) # 0.91
-
-f_measure <- (2*recall*precision)/(recall + precision) # 0.33
-
-sensitivity = (4894)/(4894 + 2761) # 0.64
-
-balanced_accuracy <- (recall + sensitivity)/2 # 0.75 - this is also the AUC - which is pretty good.
-
-g_measure <- sqrt(precision*recall) # 0.42
-
-false_pos_rate <- 2761/(2761+4894) # 0.36
-
-```

### 2021-08-12 marine/STEP1_species_groups/STEP1_species_groups.Rmd
cleaned up scripts and READMEs

@@
 ---
-title: "Exploring FAO aquaculture data"
+title: "Prepping FAO aquaculture data"
+author: "Gage Clawson (USCB, NCEAS, OHI)"
 output: html_document
@@
 ---
+
+This script preps and classifies the FAO aquaculture data to the appropriate production types and species.
 
@@
 
+Read in the raw FAO data
 ```{r}
@@
 
-## explore marine
+## Prep marine and brackish-water
 ```{r}
@@
 
-Classify species into aquaculture groups 
+Classify species into mariculture groups consistent with MacLeod et al. 2020 (https://www.nature.com/articles/s41598-020-68231-8)
+
+Need to classify into these groups, for easier mapping and pressure calculations:
+ - Bivalves (Unfed or algae fed bivalve molluscs)
+ - Tuna (Bluefin tuna)
+ - Salmonids (Salmonidae fish)
+ - Shrimps and Prawns
+ - crustaceans (Non-shrimp crustaceans)
+ - marine fish general (General marine fish)
+
 ```{r}
-# Need to classify into these groups, for easier mapping and pressure calculations: 
-#  - Bivalves
-#  - Tuna
-#  - Salmonids
-#  - Shrimps and Prawns
-#  - crustaceans
-#  - marine fish general (all the other finfish species)
 
@@
   summarise(tonnes = sum(value)) %>%
-  ungroup() # %>%
-  # dplyr::filter(tonnes >= 500) %>%
- #  group_by(country, year) %>%
- #  summarise(total_tonnes = sum(tonnes))# %>%
- # # arrange(aq_group)
+  ungroup()
 
@@
 
+```
+
+Explore the data
+
+```{r}
 ## Take a look at the data 
@@
   dplyr::filter(aq_group == "crustaceans")
-sum(test$total_tonnes) # 5094133
+sum(test$total_tonnes) #
 
@@
   dplyr::filter(aq_group == "marine_fish_general")
-sum(test$total_tonnes) # 5094133
+sum(test$total_tonnes) #
 
@@
   dplyr::filter(aq_group == "tuna")
-sum(test$total_tonnes) # 5094133
+sum(test$total_tonnes) #
 
@@
   dplyr::filter(aq_group == "salmonids")
-sum(test$total_tonnes) # 5094133
+sum(test$total_tonnes) #
 

### 2021-08-12 marine/STEP1_species_groups/STEP2_ASC_data_prep.Rmd
cleaned up scripts and READMEs

--- 2021-03-23 marine_mapping_archive_v1/STEP1_species_groups/STEP2_ASC_data_prep.Rmd
@@
 title: "Prep ASC data"
+author: "Gage Clawson (USCB, NCEAS, OHI)"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```
-
-See how many countries from FAO are represented in ASC for marine_fish_general category
-
-```{r}
-fao_marine_fish <- fao_all %>%
-  dplyr::filter(aq_group == "marine_fish_general")
-
-ASC_marine_fish <- ASC_all_sf %>%
-  dplyr::filter(aq_group == "marine_fish_general")
-
-setdiff(fao_marine_fish$country, ASC_marine_fish$cert_country)
-
-#  [1] "Bangladesh"               "Cambodia"                 "China"                   
-#  [4] "China, Hong Kong SAR"     "Costa Rica"               "Cyprus"                  
-#  [7] "Egypt"                    "France"                   "India"                   
-# [10] "Indonesia"                "Iran (Islamic Rep. of)"   "Israel"                  
-# [13] "Italy"                    "Korea, Republic of"       "Malaysia"                
-# [16] "Malta"                    "Mauritius"                "Norway"                  
-# [19] "Philippines"              "Portugal"                 "Saudi Arabia"            
-# [22] "Singapore"                "Taiwan Province of China" "Tunisia"                 
-# [25] "United Arab Emirates"
-
-setdiff(ASC_marine_fish$cert_country, fao_marine_fish$country)
-# [1] "Netherlands" "Denmark"     "Germany"
-
-unique(ASC_marine_fish$cert_country)
-```
-
-See how many countries from FAO are represented in ASC for bivalves category
-
-```{r}
-fao_bivalve <- fao_all %>%
-  dplyr::filter(aq_group == "bivalves")
-
-ASC_bivalve <- ASC_all_sf %>%
-  dplyr::filter(aq_group == "bivalves")
-
-setdiff(fao_bivalve$country, ASC_bivalve$cert_country)
-
-#  [1] "Brazil"                   "Bulgaria"                 "Cambodia"                
-#  [4] "Canada"                   "China, Hong Kong SAR"     "Croatia"                 
-#  [7] "Cuba"                     "Denmark"                  "French Polynesia"        
-# [10] "Germany"                  "Greece"                   "Guernsey"                
-# [13] "India"                    "Indonesia"                "Ireland"                 
-# [16] "Italy"                    "Jersey"                   "Korea, Dem. People's Rep"
-# [19] "Malaysia"                 "Netherlands"              "Norway"                  
-# [22] "Philippines"              "Russian Federation"       "Slovenia"                
-# [25] "Spain"                    "Sweden"                   "Taiwan Province of China"
-# [28] "Thailand"                        "United States of America"
-
-setdiff(ASC_bivalve$cert_country, fao_bivalve$country)
-# United kingdom spelled differently.. don't worry about it
-
-unique(ASC_bivalve$cert_country)
-```
-
-Tuna
-```{r}
-fao_tuna <- fao_all %>%
-  dplyr::filter(aq_group == "tuna")
-
-ASC_tuna <- ASC_all_sf %>%
-  dplyr::filter(aq_group == "tuna")
-
-unique(fao_tuna$country)
-```
-
-Crustaceans
-```{r}
-fao_crust <- fao_all %>%
-  dplyr::filter(aq_group == "crustaceans")
-
-ASC_crust <- ASC_all_sf %>%
-  dplyr::filter(aq_group == "crustaceans")
-
-unique(fao_crust$country)
-```

### 2021-08-12 marine/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
cleaned up scripts and READMEs

--- 2021-03-23 marine_mapping_archive_v1/bivalve/bivalve_farms/STEP1_fao_bivalve_production.Rmd
@@
 
-## Read in fao data and get a species list for salmon 
+## Read in fao data and get a species list for bivalve 
 species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
@@
 
-## write out bivalve taxa and production for Juliette
+## write out bivalve taxa and production
 fao_bivalve_taxa_prod <- fao %>%
@@
   arrange(country, iso3c, species, year)
+
+sum(fao_bivalve_taxa_prod$fao_tonnes_production) # 17435623
+unique(fao_bivalve_taxa_prod$country) # 42 countries
 
@@
 
+Species included: 
 Abalones nei, American cupped oyster, Aquatic invertebrates nei, Australian mussel, Blacklip pearl oyster, Blood cockle, Blue mussel, Butter clam, Chilean mussel, Cholga mussel, Choro mussel, Clams, etc.

### 2021-08-12 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
cleaned up scripts and READMEs

@@
 title: "Location of Bivalve Farms"
-author: "Gage Clawson (USCB, NCEAS, OHI)"
+author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/14/2020"
 output: html_document

### 2021-08-12 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
updated figs and stats with newly run farms
cleaned up scripts and READMEs

@@
 output: html_document
+author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/14/2020"
+output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
+
+This script takes the number of farms information collected in STEP2 and calculates a global tonnes of production per farm, and calculates the number of remaining farms needed to place in our placement model.
 
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library(here)
+library(dplyr)
+library(tidyverse)
 ```
@@
   mutate(tonnes_per_farm = fao_tonnes_production/n_farms)
+
+write.csv(tonnes_per_farm, "output/bivalve_comp_tonnes_per_farm.csv", row.names = FALSE)
 

### 2021-08-12 marine/crustaceans/crustaceans_farms/STEP1_fao_crustacean_production.Rmd
cleaned up scripts and READMEs

--- 2021-03-23 marine_mapping_archive_v1/crustaceans/crustacean_farms/STEP1_fao_crustacean_production.Rmd
@@
 ---
-title: "FAO crustaceam production"
+title: "FAO crustacean production"
 author: "Gage Clawson (UCSB, NCEAS, OHI)"
@@
 ---
+
+## Clean FAO crustacean data
 
@@
 
-## write out crustacean taxa and production for Juliette
+## write out crustacean taxa and production
 fao_crustaceans_taxa_prod <- fao %>%
@@
   summarize(fao_tonnes_production = sum(value)) %>%
-  arrange(country, iso3c, species, year)
+  arrange(country, iso3c, species, year) %>%
+  ungroup() %>%
+  mutate(total = sum(fao_tonnes_production)) %>%
+  mutate(perc = fao_tonnes_production/total)
 
+## write out a file with the specific taxa included  
 write.csv(fao_crustaceans_taxa_prod, here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans_taxa_production.csv"), row.names=FALSE)
@@
 
+## explore the data     
  explore <- read_csv(here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
@@
 
+sum(explore$fao_tonnes_production) # 401719.1
+unique(explore$country) # 6 countries
+
 ```
+
+```{r}
+## look at crustacean taxa and production
+fao_crustaceans_taxa_prod <- fao %>%
+  filter(species %in% crustaceans_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_crustaceans_taxa_prod$value) # 401733.5 - adds 14 tonnes
+
+unique(fao_crustaceans_taxa_prod$country) # 6 countries 
+```

### 2021-08-12 marine/crustaceans/crustaceans_farms/STEP3_gapfill_crustaceans.Rmd
made the figures!
cleaned up scripts and READMEs

--- 2021-03-23 marine/crustaceans/crustacean_farms/STEP3_gapfill_crustaceans.Rmd
@@
 ---
-title: "Gapfilling the number of farms to add for shrimp countries based on tonnes of production"
+title: "Gapfilling the number of farms to add for crustacean countries based on tonnes of production"
+author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/14/2020"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
+
+This script takes the number of farms information collected in STEP2 and calculates a global tonnes of production per farm, and calculates the number of remaining farms needed to place in our placement model.
 
@@
 ```{r}
-avg_global_shrimp_tonnes_per_farm = 337.7357
-avg_global_shrimp_tonnes_per_farm # 337.7357
+avg_global_shrimp_tonnes_per_farm = 336.5783
+avg_global_shrimp_tonnes_per_farm # 336.5783
 ```

### 2021-08-12 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
cleaned up scripts and READMEs

@@
 
-# data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-#   st_as_sf(., 
-#            coords = c("lon", "lat"),
-#            crs = crs(food_raster), 
-#            agr = "constant")
-
-all_farms <- readRDS("data/all_modeled_marine_farms.rds")
-
-# all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-#   map_df(., readRDS) %>% 
-#   dplyr::rename(iso3c = iso3) %>% 
-#   dplyr::mutate(source = "modeled") %>% 
-#   rbind(data %>% mutate(source = "real"))
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+      st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
 bivalve_farms <- all_farms %>%
-  filter(type == "bivalve")
+  filter(species_group == "Unfed or algae fed bivalve molluscs")
 
@@
 # CHN:MAC
-# ESP:FRA
+# CHN:PRK
+# DEU:NLD
 # HKG:CHN
 # IRL:GBR
+# MYS:BRN
 # NLD:DEU
-# PRK:RUS
 # SVN:HRV
-# THA:MMR
 # TWN:CHN
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "ESP:FRA", "ESP", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "ESP:FRA", "Spain", NAME_0)) %>%    
+    mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "DEU:NLD", "DEU", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "DEU:NLD", "Germany", NAME_0)) %>%    
   mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
+    mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "PRK:RUS", "PRK", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "PRK:RUS", "North Korea", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
@@
   ungroup() %>%
-  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
+  # mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
   dplyr::select(iso3c, tonnes_per_farm, geometry)
@@
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE) ## overwrite file if already there
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/updated/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE) ## overwrite file if already there
 
@@
 
-write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/bivalve_farm_updated.csv")
+write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/updated/bivalve_farm_updated.csv")
 

### 2021-08-12 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
cleaned up scripts and READMEs

@@
 
-# data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-#   st_as_sf(., 
-#            coords = c("lon", "lat"),
-#            crs = crs(food_raster), 
-#            agr = "constant") %>%
-#   mutate(source = "real")
-
-all_farms <- readRDS("data/all_modeled_marine_farms.rds")
-
-# all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
-#   map_df(., readRDS) %>% 
-#   rename(iso3c = iso3) %>% 
-#  dplyr::mutate(source = "modeled") %>% 
-#   #left_join(tonnage_per_farms)
-#   rbind(data)
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+      st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
 crust_farms <- all_farms %>%
-  filter(type == "crustaceans")
+  filter(species_group == "Non-shrimp crustaceans")
 ```
@@
 # CHN:HKG
-# CHN:MAC
-# MMR:THA
+# CHN:PRK
 
@@
   mutate(NAME_1 = as.character(NAME_1)) %>%
-  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% c("MMR:THA"), "MMR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% c("MMR:THA"), "Myanmar", NAME_0))
+  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:PRK"), "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:PRK"), "China", NAME_0))
 
@@
 plot(log(crustacean_raster_check+1))
+# s <- raster::select(crustacean_raster_check)
+# plot(s)
 cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 401719.1
@@
 
-write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/crustaceans_farm_updated.csv")
+write_csv(crustacean_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/crustaceans/updated/crustaceans_farm_updated.csv")
 

### 2021-08-12 marine/last_step_rasterize/finfish_rasterize_production.Rmd
cleaned up scripts and READMEs

@@
 
-all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+# all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+      st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
 finfish_farms <- all_farms %>%
-  filter(type == "marine_fish_general")
+  filter(species_group == "General marine fish")
 
@@
 # CHN:HKG
-# CHN:MAC
+# CHN:PRK
 # CYP:XAD
-# EGY:ISR
 # ESP:PRT
@@
 # HKG:CHN
-# MYS:IDN 
-# PRT:ESP
+# IDN:MYS
+# MYS:BRN
+# MYS:SGP
 # SGP:MYS
-# TUR:GRC
+# TWN:CHN
 
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "EGY:ISR", "EGY", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "EGY:ISR", "Egypt", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:IDN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:IDN", "Malaysia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "PRT:ESP", "PRT", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "PRT:ESP", "Portugal", NAME_0)) %>% 
+  mutate(GID_0 = ifelse(check %in% "IDN:MYS", "IDN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>% 
+  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
+  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "TUR:GRC", "TUR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0))
+  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))
 
@@
   ungroup() %>%
-  mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
+ # mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
   dplyr::select(iso3c, tonnes_per_farm, geometry)
@@
 farms_sf_prod <- st_as_sf(farms_prod)
-mapview(farms_sf_prod)
+mapview(farms_sf_prod, cex = "tonnes_per_farm")
 
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/updated/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)
 
@@
 plot(log(finfish_raster + 1))
+# s<-raster::select(finfish_raster)
+# plot(s)
 
@@
 
-write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/marine_fish_general_farm_updated.csv")
+write_csv(finfish_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/marine_fish_general/updated/marine_fish_general_farm_updated.csv")
 

### 2021-08-12 marine/last_step_rasterize/salmon_rasterize_production.Rmd
cleaned up scripts and READMEs

@@
 gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
-plot(gadm_latlon)
 
@@
 
-all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+# all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+      st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
 salmon_farms <- all_farms %>%
-  filter(type == "salmon")
+  filter(species_group == "Salmonidae fish")
 
@@
 mapview(filter(farms_sf, check == "RUS:RUS"))
-mapview(farms_sf)
+mapview(farms_sf, cex = "tonnes_per_farm")
 # some annoying mismatches due to raster resolution. Fix these
@@
 plot(log(salmon_raster + 1))
+# s <- raster::select(salmon_raster)
+# plot(s)
 
@@
 
-write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/salmon_farm_updated.csv")
+write_csv(salmon_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/salmon/updated/salmon_farm_updated.csv")
 

### 2021-08-12 marine/last_step_rasterize/shrimp_rasterize_production.Rmd
cleaned up scripts and READMEs

@@
 
-all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+# all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+      st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
 shrimp_farms <- all_farms %>%
-  filter(type == "shrimp")
+  filter(species_group == "Shrimps and prawns")
 
@@
 # CHN:MAC
+# CHN:PRK
 # CRI:PAN
@@
 # HND:SLV
-
+# IRN:IRQ
 # MEX:USA
-# MMR:THA
-# MYS:IDN
-# NIC:CRI
+# MYS:BRN
+# MYS:SGP
+# PAN:CRI
 # SAU:KWT
-# THA:MMR
-# THA:MYS
+# SLV:GTM
+# TWN:CHN
 
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "NIC:CRI", "NIC", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "NIC:CRI", "Nicaragua", NAME_0)) %>%  
+  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MMR:THA", "MMR", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:IDN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:IDN", "Malaysia", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "PAN:CRI", "PAN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "PAN:CRI", "Panama", NAME_0)) %>%    
   mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
   mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "THA:MMR", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MMR", "Thailand", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0))
+  mutate(GID_0 = ifelse(check %in% "SLV:GTM", "SLV", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "SLV:GTM", "El Salvador", NAME_0)) %>%  
+  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))
 
@@
 
-# FAO salmon production data per country
+# FAO shrimp production data per country
 ```{r}
@@
 farms_sf <- st_as_sf(farms_prod)
-mapview(farms_sf)
+mapview(farms_sf, cex = "tonnes_per_farm")
 
@@
 
-write_csv(shrimp_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/shrimp_farm_updated.csv")
+write_csv(shrimp_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp/updated/shrimp_farm_updated.csv")
 

### 2021-08-12 marine/last_step_rasterize/tuna_rasterize_production.Rmd
cleaned up scripts and READMEs

@@
 
-all_farms <- readRDS("data/all_modeled_marine_farms.rds")
+# all_farms <- readRDS("data/all_modeled_marine_farms_final.rds")
+
+all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+      st_as_sf(., 
+           coords = c("X", "Y"),
+           crs = crs(food_raster), 
+           agr = "constant")
 
 tuna_farms <- all_farms %>%
-  dplyr::filter(type == "tuna")
+  dplyr::filter(species_group == "Bluefin tuna")
 
@@
 farms_sf_prod <- st_as_sf(farm_production)
-mapview(farms_sf_prod)
+mapview(farms_sf_prod, cex = "tonnes_per_farm")
 
 ## write the production data so that we can use it for the nutrient layer. 
-st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)
+st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/updated/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE)
 
@@
 plot(log(tuna_raster_check+1))
+# s <- raster::select(tuna_raster_check)
+# plot(s)
+
 cellStats(tuna_raster_check, stat = "sum", na.rm = TRUE) # 37072.56
@@
 
-write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm_updated.csv")
+write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/updated/tuna_farm_updated.csv")
 

### 2021-08-12 marine/marine_fish_general/finfish_farms/STEP1_fao_finfish_production.Rmd
cleaned up scripts and READMEs

@@
 
-## write out marine fish taxa and production for Juliette
+## write out marine fish taxa and production
 fao_finfish_taxa_prod <- fao %>%
@@
 ```{r}
-## write out bivalve taxa and production for Juliette
+## explore out bivalve taxa and production
 fao_finfish_taxa_prod <- fao %>%

### 2021-08-12 marine/marine_fish_general/finfish_farms/STEP3_gapfill_finfish.Rmd
updated figs and stats with newly run farms
cleaned up scripts and READMEs

@@
 title: "Gapfilling the number of farms to add for marine_fish_general countries based on tonnes of production"
+author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/14/2020"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
+
+This script takes the number of farms information collected in STEP2 and calculates a global tonnes of production per farm, and calculates the number of remaining farms needed to place in our placement model.
 
@@
   mutate(tonnes_per_farm = fao_tonnes_production/n_farms)
+
+write.csv(tonnes_per_farm, "output/finfish_comp_tonnes_per_farm.csv", row.names = FALSE)
 

### 2021-08-12 marine/salmon/salmon_farms/STEP1_fao_salmon_production.Rmd
cleaned up scripts and READMEs

--- 2021-02-04 marine/salmon/salmon_farm/STEP1_fao_salmon_production.Rmd
@@
   summarize(fao_tonnes_production = sum(value)) %>%
-  arrange(country, iso3c, year)
+  arrange(country, iso3c, year) %>%
+  filter(year == 2017)
 
@@
 sum(explore$percent) # 100.01
+
+unique(explore$country) # - 16 countries 
 ```
+
+```{r}
+## explore out salmon taxa and production
+fao_salmon_taxa_prod <- fao %>%
+  filter(species %in% salmon_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, species, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_salmon_taxa_prod$value) # 2753752 - adds 458 tonnes
+
+unique(fao_salmon_taxa_prod$country) # 16 countries
+
+test <- fao_salmon_taxa_prod %>%
+  filter(str_detect(species, "almon"))
+
+unique(test$country)
+
+sum(test$value)
+
+2753752 - 2569126
+```

### 2021-08-12 marine/salmon/salmon_farms/STEP3_gapfill_salmon.Rmd
updated figs and stats with newly run farms
cleaned up scripts and READMEs

@@
 ---
-title: "Untitled"
+title: "Estimate tonnage per farm and farms to place"
+author: "Gage Clawson (UCSB, NCEAS, OHI)"
+date: "10/09/2020"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
+
+In this script we estimate the average tonnage per known farm for 2017 and estimate the remaining number of farms to place for data-limited countries.
 
@@
   mutate(tonnes_per_farm = fao_tonnes_production/n_farms)
+
+write.csv(tonnes_per_farm, "output/salmon_comp_tonnes_per_farm.csv", row.names = FALSE)
 

### 2021-08-12 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
cleaned up scripts and READMEs

--- 2021-02-04 marine/shrimp/shrimp_farms/STEP1_fao_shrimp_production.Rmd
@@
 
-## Read in fao data and get a species list for salmon 
+## Read in fao data and get a species list for shrimp
 species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
@@
 
-## write out shrimp taxa and production for Juliette
+## write out shrimp taxa and production
 fao_shrimp_taxa_prod <- fao %>%
@@
   arrange(country, iso3c, species, year)
+
+taxa_group <- fao_shrimp_taxa_prod %>%
+  group_by(species) %>%
+  summarise(tonnes = sum(fao_tonnes_production)) %>%
+  mutate(percent = tonnes/sum(tonnes))
 
@@
 ```
+
+```{r}
+## explore out shrimp taxa and production 
+fao_shrimp_taxa_prod <- fao %>%
+  filter(species %in% shrimp_list) %>%  
+  filter(!is.na(value)) %>%
+  arrange(-value, country) %>%
+  group_by(country, year) %>%
+  summarise(value = sum(value)) %>%
+  filter(value>=500) %>% # countries with less do not appear to be stable producers at this point
+  filter(year == 2017)
+
+sum(fao_shrimp_taxa_prod$value) # 5095394 - adds ~1000 tonnes
+
+unique(fao_shrimp_taxa_prod$country) # 35 countries 
+```

### 2021-08-12 marine/tuna/tuna_farms/STEP1_fao_tuna_production.Rmd
cleaned up scripts and READMEs

@@
 
-## write out tuna taxa and production for Juliette
+## write out tuna taxa and production
 fao_tuna_taxa_prod <- fao %>%
@@
 ```{r}
-## write out bivalve taxa and production for Juliette
+## explore out bivalve taxa and production 
 fao_tuna_taxa_prod <- fao %>%

### 2021-08-12 marine/tuna/tuna_farms/STEP3_gapfill_tuna.Rmd
updated figs and stats with newly run farms
cleaned up scripts and READMEs

@@
 title: "Gapfilling the number of farms to add for tuna countries based on tonnes of production"
+author: "Gage Clawson (NCEAS, UCSB, OHI)"
+date: "12/14/2020"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
+
+This script takes the number of farms information collected in STEP2 and calculates a global tonnes of production per farm, and calculates the number of remaining farms needed to place in our placement model.
 
@@
   mutate(tonnes_per_farm = fao_tonnes_production/n_farms)
+
+write.csv(tonnes_per_farm, "output/tuna_comp_tonnes_per_farm.csv", row.names = FALSE)
 

### 2021-08-12 workflow/coast_buffer_archive.R

@@ -1,320 +1,0 @@
-## This script will buffer the coastline of each place which has known locations and save each as a file. When it is done it will compile them all together and rasterize.
-## We will use this raster to validate our model. 
-
-#### load libraries and data ####
-#------------------------------------------------------------------------------#
-library(sf)
-library(spatialEco)
-library(tidyverse)
-library(raster)
-library(rgeos)
-library(rmapshaper)
-library(mapview)
-library(fasterize)
-
-# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
-source("./_spatial/template_raster.R")
-gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
-gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
-land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
-eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
-eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
-coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
-
-
-inverted_land <- land_mask
-inverted_land[is.na(inverted_land[])] <- .5
-inverted_land[inverted_land[]==1] <- NA
-inverted_land[inverted_land[]==.5] <- 1
-
-blank_raster <- food_raster
-blank_raster[] <- 1
-
-the_crs <- crs(fake_raster, asText = TRUE)
-
-
-
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant") 
-
-
-data <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
-  st_as_sf(., 
-           coords = c("X", "Y"),
-           crs = crs(food_raster), 
[…]

### 2021-08-12 workflow/place_unknown_farms.R

@@ -1,3 +1,6 @@
+## This script will place specific number of farms with unknown locations using our location modelling approach.
+
+
 #### load libraries and data ####
 #------------------------------------------------------------------------------#
 library(sf)
@@ -28,10 +31,11 @@ blank_raster[] <- 1
 
 the_crs <- crs(fake_raster, asText = TRUE)
 
-
-ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/Commercial_ports.shp") %>%
+## New port data for 2019
+ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/d2019/WPI.shp") %>%
   st_transform(the_crs) %>%
-  filter(HARB_SIZE_ != "L") # remove L ports
+  filter(HARBORSIZE != "L", # filter out large ports 
+         HARBORTYPE != "LC") # filter out lake or canals
 
 
 data <- read_csv("marine/output/all_marine_farms.csv") %>% 
@@ -60,9 +64,9 @@ arctic_fixed <- inverted_land + arctic_fixed
 arctic_fixed[arctic_fixed[]==2] <- 1 ## add land mask
 
 
-for (i in 36:length(unique(need_national_allocation$iso3c))) {
-  
-  # i = 2
+for (i in 1:length(unique(need_national_allocation$iso3c))) {
+
+  # i = 7
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[i]
   
@@ -110,15 +114,20 @@ for (i in 36:length(unique(need_national_allocation$iso3c))) {
     
     this_eez <- st_crop(this_eez, this_bbox)
     
+
   }else if(this_iso3 == "RUS"){
     this_bbox <- st_bbox(c(xmin = 28, xmax = 180, ymax = 66, ymin = 39.72669), crs = st_crs(this_area)) ## make it easier since the arctic will be classed out later anyways
     
     this_eez <- st_crop(this_eez, this_bbox)
     
+
+    
   } else if(this_iso3 == "NZL"){
     this_bbox <- st_bbox(c(xmin = 160.6098, xmax = 180, ymax = -25.88826, ymin = -55.94930), crs = st_crs(this_area)) ## make it easier since the arctic will be classed out later anyways
     
     this_eez <- st_crop(this_eez, this_bbox)
+    
+
     
   } else{
     
[…]

### 2021-08-12 workflow/place_validation_farms.R

@@ -32,9 +32,12 @@ blank_raster[] <- 1
 the_crs <- crs(fake_raster, asText = TRUE)
 
 
-ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/Commercial_ports.shp") %>%
+## New port data for 2019
+ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/d2019/WPI.shp") %>%
   st_transform(the_crs) %>%
-  filter(HARB_SIZE_ != "L") # remove L ports
+  filter(HARBORSIZE != "L", # filter out large ports 
+         HARBORTYPE != "LC") # filter out lake or canals
+
 
 
 data <- read_csv("marine/output/all_marine_farms.csv") %>% 
@@ -47,11 +50,30 @@ tonnage_per_farms <- read_csv("marine/output/all_points_to_add.csv") %>%
   distinct(type, avg_tonnes_per_farm)
 
 
+data_final <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+  mutate(type = case_when(species_group == "Salmonidae fish" ~ "salmon",
+                                   species_group == "Unfed or algae fed bivalve molluscs" ~ "bivalve",
+                                   species_group == "Shrimps and prawns" ~ "shrimp", 
+                                 species_group == "Bluefin tuna" ~ "tuna", 
+                                   species_group ==  "General marine fish" ~ "marine_fish_general",
+                          species_group == "Non-shrimp crustaceans" ~ "crustaceans")) %>%
+  filter(data_type_2 == "A") %>%
+  group_by(iso3c, type) %>%
+  summarise(num_farms = n())
+
+sum(data_final$num_farms)
+
+
 need_validation_allocation <- data %>%
   st_drop_geometry() %>%
   group_by(iso3c, type) %>%
   summarise(num_farms = n()) %>%
-  ungroup()
+  ungroup() %>%
+  group_by(iso3c, type) %>%
+  filter(num_farms %in% c(data_final$num_farms)) %>%
+  filter(iso3c %in% c(data_final$iso3c))
+
+sum(need_validation_allocation$num_farms) # 8470... not exactly right... but its ok, we will fix it later. 
 
 
 # create arctic raster 
@@ -67,9 +89,9 @@ arctic_fixed <- inverted_land + arctic_fixed
[…]

### 2021-10-14 marine/united_states/US_mapping.Rmd
started looking into state-by-state US mariculture locations

---
title: "Location of United States Aquaculture Farms"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script maps all known US mariculture farms

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(raster)
library(tidyverse)
library(stringr)
library(PBSmapping)
library(maptools)
library(rgdal)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)
library(tmap)
library(leaflet)
library(ggplot2)
library(maps)
library(mapdata)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

# Raster

Standard raster used for this analysis

```{r, include = FALSE}

source(here("_spatial/template_raster.R"))

```

## US Northeast

Source:
Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 17, 2020] 
https://www.northeastoceandata.org/data-download/

"This dataset should be considered a work in progress"

States:

 - NY
 - CT
 - ME
 - NH
 - MA
 - Federal waters

Species: 
 - "Shellfish"  "Multi-trophic or other" "Seaweed" "Finfish"

**This data set is not "comprehensive" but provides good sources to look through for individual states (see below). These are polygons.**

```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}

us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))

us_ne_active <- us_ne %>%
  filter(status != "Unknown")

us_ne_active$area = st_area(us_ne_active)

# unique(us_ne_active$state) # "Federal waters" "NY"             "CT"             "MA"             "ME"             "NH"   
# unique(us_ne_active$genSpecies) # [1] "Shellfish"  "Multi-trophic or other" "Seaweed" "Finfish"

usa <- map_data('usa')

state <- map_data("state")

ne <- subset(state, region %in% c("new york", "maine", "new hampshire", "massachusetts", "connecticut"))

  ggplot() +
  geom_sf(data = us_ne_active, col = "red") + 
  geom_polygon(data=ne, aes(x=long, y=lat, group=group), fill = "gray") + 
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
    labs(title = "US NE Regional Ocean Council data", caption = "Not comprehensive")

```

## Maine:

 - https://www.maine.gov/dmr/aquaculture/leases/aquaculturemap.html
 - I think we will want to use both "limited purpose" and regular leases.
 - Limited purpose leases are for scientific or smaller/shorter term mariculture projects, that last up to 3 years.
 - I think this can be considered "comprehensive". 
 - Update to date as of September 2021.
 - Has species types specified. 
 - Red polygons for the leases. Blue points for the limited purpose. Limited purpose has length and width measurements, so regardless we will have area for both if needed.

```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))

# mapview(maine_aq_lease)

maine_aq_lease_active <- maine_aq_lease %>%
  dplyr::filter(STATUS == "A") # 149 leases

```

```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
maine_aq_lp <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_Limited_Purpose_Aquaculture_Sites/MaineDMR_Aquaculture_-_Limited_Purpose_Aquaculture_Sites.shp"))

# mapview(maine_aq_lp)

maine_aq_lp_active <- maine_aq_lp %>%
  dplyr::filter(Status == "A") # 749 limited purpose leases active

maine <- subset(state, region %in% c("maine"))

  ggplot() +
  geom_sf(data = maine_aq_lease_active, col = "red") + 
  geom_polygon(data=maine, aes(x=long, y=lat, group=group), fill = "gray") + 
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
    labs(title = "Maine data", caption = "Comprehensive, up-to-date (2021)") +
    geom_sf(data = maine_aq_lp_active, col = "blue", alpha = 0.1, size = 0.5)
```

## Alaska:

 - https://adfg.maps.arcgis.com/apps/webappviewer/index.html?id=f3ca95493c1042b39e42a3ecb5dcad6a
 - Will be considered "comprehensive". 
 - Up-to-date as of 2020
 - Specifies species type
 - Csvs with lat lons, but have a "corner" dataset, which we could make into polygons. Has area associated with each site. 
 - Shown in red. 
 - Has 62 active sites.

```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
library(usmap)

alaska_details <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Details.csv"))

alaska_corners <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Corners.csv")) ## each group of corners is a polygon representing one farming operation. So, we will need to somehow make those polygons and find the centroid of each group to get points. Save as polygons and as points if possible? Maybe don't even need the exact polygons, since we know the area of each. Almost all are active.

library(tigris)

ak <- counties("Alaska", cb = TRUE) %>%
  filter(NAME %in% c("Aleutians East", "Lake and Peninsula", "Bristol Bay", "Kodiak Island", "Kenai Peninsula", "Anchorage", "Yakutat", "Hoonah-Angoon", "Haines", "Sitka", "Juneau", "Prince of Wales-Hyder", "Ketchikan Gateway", "Wrangell", "Petersburg", "Valdez-Cordova"))

alaska_details_sf <- st_as_sf(alaska_details, coords = c("x", "y"), crs = crs(ak))
alaska_corners_sf <- st_as_sf(alaska_corners, coords = c("x", "y"), crs = crs(ak))

ggplot() +
  geom_sf(data = alaska_corners_sf, col = "red", shape = 5) + 
  geom_sf(data=ak, fill = "gray") + 
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
    labs(title = "Alaska data", caption = "Comprehensive, up-to-date (2020)")

```

## California:

 - https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=187229&inline
 - Report current as of May 2021
 - There is a map with commercial locations and a table with exact farm numbers (pages 7 and 8). We could likely estimate or find the location via Google. 
 - And cross reference with the locations listed here: https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/california_locs.png)

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/california_commercial.png)

## New Hampshire:

 - https://granit.unh.edu/data/search
 - Comprehensive
 - Up-to-date as of 2020
 - Polygons 
 - 40 sites

```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
nh_aq <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/New_Hampshire/GRANIT_20211011184728/2020_Aquaculture_Sites.shp")) # 40 sites, assume all active

nh <- counties("New Hampshire", cb = TRUE) %>%
  filter(NAME %in% c("Rockingham"))

  ggplot() +
  geom_sf(data = nh_aq, col = "red") + 
 # geom_polygon(data=nh, aes(x=long, y=lat, group=group), fill = "gray") + 
    geom_sf(data = nh, fill = "gray") + 
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
    labs(title = "New Hampshire data", caption = "Comprehensive, up-to-date (2020)")
```

## Florida:

"ESI Human Use and Socio-Economc Resources Points" data

 - https://geodata.myfwc.com/datasets/myfwc::esi-human-use-and-socio-economic-resources-points-florida/about
 - 2015 data
 - 64 sites
 - Point data, no area
 - Not comprehensive (?), only represents points which are at risk from oil spills (which could be relevant to our project).

```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}

fl_data <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Florida/ESI_Human-Use_and_Socio-Economic_Resources_Points_Florida/ESI_Human-Use_and_Socio-Economic_Resources_Points_Florida.shp"))

unique(fl_data$TYPE)

fl_aq <- fl_data %>%
  filter(TYPE == "AQUACULTURE")

fl <- subset(state, region %in% c("florida"))

  ggplot() +
  geom_sf(data = fl_aq, col = "red") + 
  geom_polygon(data=fl, aes(x=long, y=lat, group=group), fill = "gray") + 
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
    labs(title = "Florida data", caption = "Not Comprehensive, 2015 data")

```

Offshore aquaculture in Florida

 - As far as I can tell, none yet: https://www.flseagrant.org/aquaculture/openocean/

Other than the above, I can't find much info for Florida. Google maps shows a couple shrimp farms.

## Alabama:

 - "Alabama has an emerging oyster industry with 13 farms comprising of 25 acres in 2015. Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise." from https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
 - This has a map... probably our best source for Alabama!: https://alaquaculture.com/state/#list-of-operating-farms

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/alabama_Farms.png)

## Mississippi:

 - Can't find much information for Mississippi.

## Louisana:

 - Pretty much all freshwater from what I can tell.

## Texas:

 - https://www.pewtrusts.org/en/research-and-analysis/articles/2020/05/21/texas-says-shucks-lets-give-oyster-growing-a-try
 - Seems like a very new industry in Texas.

 - Seafood watch 
https://www.seafoodwatch.org/-/m/sfw/pdf/reports/s/mba_seafoodwatch_usfarmedshrimpreport.pdf
 - "Most commercial shrimp aquaculture production in the US is located in Texas, which has seven commercial farms."

http://www.texasaquaculture.org/TxShrimpFms.html
 - They have 9 Texas locations listed here. One is definitely freshwater prawns. Unclear if they are land-based or not (I guess all shrimp farms are techincally land-based since they are ponds). Need to explore these more. 
 - These are current as of 2018.

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/texas_shrimp.png)

## Oregon:

 - Map of general areas where you are allowed to commercially harvest or grow shellfish in Oregon: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/ClassifiedCommercialShellfishGrowingMap.pdf

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/or_areas.png)

 - Shellfish distributors list: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/Shellfishdealers.pdf

 - 2020 shellfish production report: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/AnnualShellfishProductionReport.pdf

## Connecticut:

Shellfish bed managed

 - https://portal.ct.gov/DOAG/Aquaculture1/Aquaculture/Shellfish-Area-Classifications--Maps
 - Only Shellfish
 - Polygons 
 - I believe that these are large areas that have been **approved** for shellfish aquaculture, but not the exact locations of the aquaculture. So this probably isn't helpful.

However, worst case, we could use the data from the Northeast ocean council dataset:

"Connecticut – Data on Connecticut aquaculture was derived from two datasets provided by the State of Connecticut Department of Agriculture/Bureau of Aquaculture and the State of Connecticut Department of Environmental Protection. One dataset contains the location of natural shellfish beds. Natural beds managed by the state, town or used for recreational harvesting were selected from this dataset, resulting in 1855 polygons. The number of beds in use at any given time is subject to change. The second dataset contains 46 polygons representing the approximate geographical location of permitted “Certificate for Aquaculture  Operation” gear sites in the Connecticut coastal waters of Long Island Sound via the State of Connecticut Application for Joint Programmatic General Permit for Aquaculture Department of the Army General Permit. These datasets are up to date as of January 15, 2016. For more information on CT Aquaculture and Shellfish, see the CT Aquaculture Mapping Atlas."

```{r}

ct_shellfish <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/Shellfish_Bed_Managed_shp/SHELLFISH_BED_MANAGED.shp"))

ct <- counties("Connecticut", cb = TRUE)

  ggplot() +
  geom_sf(data = ct_shellfish, col = "red") + 
    geom_sf(data = ct, fill = "gray") + 
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
    labs(title = "Connecticut data", caption = "Not Comprehensive, General 'approved' areas")
```

Another map, this is probably what we need (seaweed and shellfish): https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46

## Washington:

Approved growing areas map

 - https://fortress.wa.gov/doh/oswpviewer/index.html

"DNR leases deep water sites for finfish net pens and floating shellfish rafts and longlines. Salmon aquaculture operations have existed in Washington since the 1970s and are scattered throughout Puget Sound. Current net pen leases include salmon aquaculture, delayed-release salmon, and herring. The use of floating shellfish culture began in 1975 with mussel raft culture in Penn Cove. Current floating shellfish culture on rafts or longlines include oysters, mussels, and scallops."

What we used for global: 
Our Sound, Our Salmon, 2017. [Accessed January 31, 2020] http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/puget_sound.png)

## All states:

 - https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
 - Current as of 2015 
 - Can definitely use for California to cross reference
 - Has partial data for other states too

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/all_states_partial.png)

## North Carolina:

Shellfish

 - https://deq.nc.gov/about/divisions/marine-fisheries/licenses-permits-and-leases/shellfish-lease-and-franchise#stats-and-figures
 - Comprehensive for shellfish... just need to figure out how download it. 
 - I believe Shellfish is pretty much the only mariculture that occurs in NC. 
 - Has number totals of leases 
 - Will likely need to send an email.

 ![Has lease info for the entire state](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/nc_map.png)

## Virginia:

Shellfish

 - https://mrc.virginia.gov/links.shtm
 - They have oyster lease and application data, which *I think* is the only type of aquaculture there. The map isn't downloadable from what I can tell though, so I bet we will have to email to access.
 - They also have a phone app.

 ![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/va_map.png)

## Maryland:

Shellfish

 - They have individual lease application maps in PDFs, but they would take forever to go through. They must have some sort of internal dataset where they store the approved lease info?: https://dnr.maryland.gov/fisheries/pages/aquaculture/applications.aspx

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/maryland_apps.png)

## Delaware:

"Delaware is the only coastal state with no commercial shellfish aquaculture; a multimillion dollar business in our neighboring states up and down the East Coast."

 - Don't have to worry about Delaware.

## South Carolina:

 - Super small industry here. 
 - https://www.scseagrant.org/aquaculture/
 - https://www.scseagrant.org/wp-content/uploads/Economic-Contribution-of-Oyster-Mariculture-SC.pdf
 - Only 9 farms, all oyster, as of 2021

## Georgia:

 - https://www.gpb.org/news/2020/11/09/will-georgias-fledgling-oyster-industry-sink-it-swims
 - Highly unlikely there are any marine farms here. I think marine aquaculture might be illegal here? And even if it wasn't, they most likely haven't even had a harvest since it was legalized (see above article).

## Massachusetts:

https://www.mass.gov/service-details/aquaculture
  - "Massachusetts has 378 shellfish leases. Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise."

https://www.mass.gov/doc/2020-dmf-annual-report/download
 - 386 "private shellfish propogation" permits in 2020

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/mass_permit.png)
 - Also has production data per town or region.

## Rhode Island:

 - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
 - No download option.

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/rhode_island_map.png)

## Hawaii

https://hdoa.hawaii.gov/ai/aquaculture-and-livestock-support-services-branch/aquaculture-in-hawaii/

 - Not much info. There is definitely both offshore aquaculture and shrimp aquaculture in Hawaii.

## New Jersey

https://www.nj.gov/agriculture/divisions/anr/sea/

 - "Currently, the program licenses more than 100 finfish, shellfish and aquatic plant producers in the state."

https://www.nj.gov/dep/fgw/pdf/marine/shellfish_leasing_policy_atlantic.pdf

 - this has maps of all shellfish leases in 2020.. but they are all pdf.

## New York

Suffolk County

 - Lease mapper: https://gis.suffolkcountyny.gov/portal/apps/View/index.html?appid=6ae708a346f340ada850544fe25ce0fb
 - Its not totally unreasonable to think that this is the only place in New York that does mariculture? Since its coast is so small.

 - Shellfish map for NY and CT, this seems like what we would need: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46

![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/ny_shell.png)

### 2021-12-14 marine/united_states/US_mapping.Rmd
updated us mapping exploration script

@@
 ---
-title: "Location of United States Aquaculture Farms"
-author: "Gage Clawson (UCSB, NCEAS, OHI)"
-date: "10/28/2020"
-output: html_document
+title: 'Mariculture farms in the United States'
+author: "*Compiled on `r date()` by `r Sys.info()['user']`*"
+output: 
+  html_document:
+    code_folding: show
+    toc: true
+    toc_depth: 3
+    toc_float: yes
+    number_sections: false
+    theme: cerulean
+    highlight: haddock
+    includes: 
+pdf_document:
+  toc: true
 editor_options: 
@@
 
-This script maps all known US mariculture farms
+Exploring maps and data for all known US mariculture farms
 
@@
 library(mapdata)
+library(readr)
 
@@
 
+usa <- map_data('usa')
+
+state <- map_data("state")
 ```
-
-# Raster
-
-Standard raster used for this analysis
 
@@
 
-## US Northeast
+## Overview
+
+There are 23 states with marine coasts.
+
+**There is comprehensive downloadable data for 5 states: **
+
+ - Maine, Alaska, New Hampshire, New York(?), Connecticut(?)
+
+**There are publicly available map viewers (leases or farm locations) which seem to be comprehensive, but are NOT downloadable for 4 states:**
+
+ - Alabama, North Carolina, Virginia, Rhode Island
+
+**There is general info on lease holders, what they farm, and what municipality or city they are in for 6 states:**
+
+ - California: general areas with acreage for commercial farms
+ - Oregon: map of places were commercial harvest/growing is allowed
+ - Maryland: Have INDIVIDUAL pdf maps of all lease applications and if they were accepted or not...
+ - New Jersey: Have pdf maps of all existing shellfish leases and those issued in 2020
+ - Massachusetts: Have number of growers per municipality with acreage and species type; also a subset of farms are available in the NE data viewer.
+ - South Carolina: Apparently have 9 oyster farms as of 2021
+
+**Subset of farms downloadable for 1 state:**
+
+ - Florida: A map of mariculture farms which are at risk of oil spills
+
+**Couldn't really find any information on 5 states:**
+
+ - Hawaii, Washington, Texas, Louisiana, Mississippi
+
+**Probably no mariculture for 2 states:**
+
+ - Delaware: Commercial harvest is illegal
+ - Georgia: From what I could tell, oyster farming was illegal here as recent as 2020
+
+## Comprehensive, downloadable
+
+### Maine
+
+ - https://www.maine.gov/dmr/aquaculture/leases/aquaculturemap.html
+ - I think we will want to use both "limited purpose" and regular leases.
+ - Limited purpose leases are for scientific or smaller/shorter term mariculture projects, that last up to 3 years.
+ - I think this can be considered "comprehensive". 
+ - Update to date as of September 2021.
+ - Has species types specified. 
+ - Red polygons for the leases. Blue points for the limited purpose. Limited purpose has length and width measurements, so regardless we will have area for both if needed.
+
+```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))
+
+# mapview(maine_aq_lease)
+
+maine_aq_lease_active <- maine_aq_lease %>%
+  dplyr::filter(STATUS == "A") # 149 leases
+
+```
+
+```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+maine_aq_lp <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_Limited_Purpose_Aquaculture_Sites/MaineDMR_Aquaculture_-_Limited_Purpose_Aquaculture_Sites.shp"))
+
+# mapview(maine_aq_lp)
+
+maine_aq_lp_active <- maine_aq_lp %>%
+  dplyr::filter(Status == "A") # 749 limited purpose leases active
+
+maine <- subset(state, region %in% c("maine"))
+
+ggplot() +
+  geom_sf(data = maine_aq_lease_active, col = "red") + 
+  geom_polygon(data=maine, aes(x=long, y=lat, group=group), fill = "gray") + 
+  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
+        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
+    labs(title = "Maine data", caption = "Comprehensive, up-to-date (2021)") +
+    geom_sf(data = maine_aq_lp_active, col = "blue", alpha = 0.1, size = 0.5)
+
+```
+
+### Alaska
+
+ - https://adfg.maps.arcgis.com/apps/webappviewer/index.html?id=f3ca95493c1042b39e42a3ecb5dcad6a
+ - Will be considered "comprehensive". 
+ - Up-to-date as of 2020
+ - Specifies species type
+ - Csvs with lat lons, but have a "corner" dataset, which we could make into polygons. Has area associated with each site. 
+ - Shown in red. 
+ - Has 62 active sites.
+
+```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+library(usmap)
+
+alaska_details <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Details.csv"))
+
+alaska_corners <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Corners.csv")) ## each group of corners is a polygon representing one farming operation.
+So, we will need to somehow make those polygons and find the centroid of each group to get points.
+Save as polygons and as points if possible?
+Maybe don't even need the exact polygons, since we know the area of each.
+Almost all are active.
+
+library(tigris)
+
+ak <- counties("Alaska", cb = TRUE) %>%
+  filter(NAME %in% c("Aleutians East", "Lake and Peninsula", "Bristol Bay", "Kodiak Island", "Kenai Peninsula", "Anchorage", "Yakutat", "Hoonah-Angoon", "Haines", "Sitka", "Juneau", "Prince of Wales-Hyder", "Ketchikan Gateway", "Wrangell", "Petersburg", "Valdez-Cordova"))
+
+alaska_details_sf <- st_as_sf(alaska_details, coords = c("x", "y"), crs = crs(ak))
+alaska_corners_sf <- st_as_sf(alaska_corners, coords = c("x", "y"), crs = crs(ak))
+
+ggplot() +
+  geom_sf(data = alaska_corners_sf, col = "red", shape = 5) + 
+  geom_sf(data=ak, fill = "gray") + 
+  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
+        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
+    labs(title = "Alaska data", caption = "Comprehensive, up-to-date (2020)")
+
+```
+
+### New Hampshire
+
+ - https://granit.unh.edu/data/search
+ - Comprehensive
+ - Up-to-date as of 2020
+ - Polygons 
+ - 40 sites
+
+```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+nh_aq <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/New_Hampshire/GRANIT_20211011184728/2020_Aquaculture_Sites.shp")) # 40 sites, assume all active
+
+nh <- counties("New Hampshire", cb = TRUE) %>%
+  filter(NAME %in% c("Rockingham"))
+
+  ggplot() +
+  geom_sf(data = nh_aq, col = "red") + 
+ # geom_polygon(data=nh, aes(x=long, y=lat, group=group), fill = "gray") + 
+    geom_sf(data = nh, fill = "gray") + 
+  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
+        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
+    labs(title = "New Hampshire data", caption = "Comprehensive, up-to-date (2020)")
+```
+
+### Connecticut
+
+Shellfish bed managed
+
+ - https://portal.ct.gov/DOAG/Aquaculture1/Aquaculture/Shellfish-Area-Classifications--Maps
+ - Only Shellfish
+ - Polygons 
+ - I believe that these are large areas that have been **approved** for shellfish aquaculture, but not the exact locations of the aquaculture. So this probably isn't helpful.
+
+From the Northeast ocean council dataset:
+
+"Connecticut – Data on Connecticut aquaculture was derived from two datasets provided by the State of Connecticut Department of Agriculture/Bureau of Aquaculture and the State of Connecticut Department of Environmental Protection.
+One dataset contains the location of natural shellfish beds.
+Natural beds managed by the state, town or used for recreational harvesting were selected from this dataset, resulting in 1855 polygons.
+The number of beds in use at any given time is subject to change.
+The second dataset contains 46 polygons representing the approximate geographical location of permitted “Certificate for Aquaculture  Operation” gear sites in the Connecticut coastal waters of Long Island Sound via the State of Connecticut Application for Joint Programmatic General Permit for Aquaculture Department of the Army General Permit.
+These datasets are up to date as of January 15, 2016.
+For more information on CT Aquaculture and Shellfish, see the CT Aquaculture Mapping Atlas."
+
+```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+
+ct_shellfish <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/Shellfish_Bed_Managed_shp/SHELLFISH_BED_MANAGED.shp"))
+
+ct <- counties("Connecticut", cb = TRUE)
+
+  ggplot() +
+  geom_sf(data = ct_shellfish, col = "red") + 
+    geom_sf(data = ct, fill = "gray") + 
+  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
+        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
+    labs(title = "Connecticut data", caption = "Not Comprehensive, General 'approved' areas")
+```
+
+Another map combined with NY, this is what we need (seaweed and shellfish): https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
+
+### New York
+
+ - Lease mapper for Suffolk County: https://gis.suffolkcountyny.gov/portal/apps/View/index.html?appid=6ae708a346f340ada850544fe25ce0fb
+
+ - Shellfish map for NY and CT, this seems like what we would need: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
+ - Pretty easy to pull lat/lon coordinates from the attribute table on the web map.
+ - CT has species and culture type. NY only has shellfish on the map
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/ny_shell.png)
+
+## Maps with no download
+
+### Alabama
+
+ - "Alabama has an emerging oyster industry with 13 farms comprising of 25 acres in 2015.
+Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise." from https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
+ - This has a map... probably our best source for Alabama!: https://alaquaculture.com/state/#list-of-operating-farms
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/alabama_Farms.png)
+
+### North Carolina
+
+Shellfish
+
+ - https://deq.nc.gov/about/divisions/marine-fisheries/licenses-permits-and-leases/shellfish-lease-and-franchise#stats-and-figures
+ - Comprehensive for shellfish... just need to figure out how download it. 
+ - I believe Shellfish is pretty much the only mariculture that occurs in NC. 
+ - Has number totals of leases 
+ - Will likely need to send an email to NCDEQ
+
+ ![Has lease info for the entire state](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/nc_map.png)
+
+### Virginia
+
+Shellfish
+
+ - https://mrc.virginia.gov/links.shtm
+ - They have oyster lease and application data, which *I think* is the only type of aquaculture there. The map isn't downloadable from what I can tell though, so I bet we will have to email to access.
+ - They also have a phone app.
+ - web.info@mrc.virginia.gov
+
+ ![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/va_map.png)
+
+### Rhode Island
+
+ - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
+ - No download option.
+ - Julia Livermore: julia.livermore@dem.ri.gov
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/rhode_island_map.png)
+
+## General lease info, areas, etc
+
+### California
+
+ - https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=187229&inline
+ - Report current as of May 2021
+ - There is a map with commercial locations and a table with exact farm numbers (pages 7 and 8). We could likely estimate or find the location via Google. 
+ - And cross reference with the locations listed here: https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/california_locs.png)
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/california_commercial.png)
+
+### Oregon
+
+ - Map of general areas where you are allowed to commercially harvest or grow shellfish in Oregon: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/ClassifiedCommercialShellfishGrowingMap.pdf
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/or_areas.png)
+
+ - Shellfish distributors list: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/Shellfishdealers.pdf
+
+ - 2020 shellfish production report: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/AnnualShellfishProductionReport.pdf
+
+### Maryland
+
+Shellfish
+
+ - They have individual lease application maps in PDFs, but they would take forever to go through.
+They must have some sort of internal dataset where they store the approved lease info?: https://dnr.maryland.gov/fisheries/pages/aquaculture/applications.aspx
+ - Maude Morris: maudee.morris@maryland.gov
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/maryland_apps.png)
+
+### South Carolina
+
+ - Super small industry here. 
+ - https://www.scseagrant.org/aquaculture/
+ - https://www.scseagrant.org/wp-content/uploads/Economic-Contribution-of-Oyster-Mariculture-SC.pdf
+ - Only 9 farms, all oyster, as of 2021
+
+### New Jersey
+
+https://www.nj.gov/agriculture/divisions/anr/sea/
+
+ - "Currently, the program licenses more than 100 finfish, shellfish and aquatic plant producers in the state."
+
+https://www.nj.gov/dep/fgw/pdf/marine/shellfish_leasing_policy_atlantic.pdf
+
+ - this has maps of all shellfish leases in 2020.. but they are all pdf.
+ - Amanda Wenczel: amanda.wenczel@ag.nj.gov
+
+### Massachusetts
+
+https://www.mass.gov/service-details/aquaculture
+  - "Massachusetts has 378 shellfish leases.
+Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise.
+  - Sean Bowen: Sean.Bowen@mass.gov
+
+https://www.mass.gov/doc/2020-dmf-annual-report/download
+ - 386 "private shellfish propogation" permits in 2020
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/mass_permit.png)
+ - Also has production data per town or region.
+
+## Subset available
+
+### US Northeast dataset
 
@@
 
-## Maine:
-
- - https://www.maine.gov/dmr/aquaculture/leases/aquaculturemap.html
- - I think we will want to use both "limited purpose" and regular leases.
- - Limited purpose leases are for scientific or smaller/shorter term mariculture projects, that last up to 3 years.
- - I think this can be considered "comprehensive". 
- - Update to date as of September 2021.
- - Has species types specified. 
- - Red polygons for the leases. Blue points for the limited purpose. Limited purpose has length and width measurements, so regardless we will have area for both if needed.
-
-```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
-maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))
-
-# mapview(maine_aq_lease)
-
-maine_aq_lease_active <- maine_aq_lease %>%
-  dplyr::filter(STATUS == "A") # 149 leases
-
-```
-
-```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
-maine_aq_lp <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_Limited_Purpose_Aquaculture_Sites/MaineDMR_Aquaculture_-_Limited_Purpose_Aquaculture_Sites.shp"))
-
-# mapview(maine_aq_lp)
-
-maine_aq_lp_active <- maine_aq_lp %>%
-  dplyr::filter(Status == "A") # 749 limited purpose leases active
-
-maine <- subset(state, region %in% c("maine"))
-
-  ggplot() +
-  geom_sf(data = maine_aq_lease_active, col = "red") + 
-  geom_polygon(data=maine, aes(x=long, y=lat, group=group), fill = "gray") + 
-  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
-    labs(title = "Maine data", caption = "Comprehensive, up-to-date (2021)") +
-    geom_sf(data = maine_aq_lp_active, col = "blue", alpha = 0.1, size = 0.5)
-```
-
-## Alaska:
-
- - https://adfg.maps.arcgis.com/apps/webappviewer/index.html?id=f3ca95493c1042b39e42a3ecb5dcad6a
- - Will be considered "comprehensive". 
- - Up-to-date as of 2020
- - Specifies species type
- - Csvs with lat lons, but have a "corner" dataset, which we could make into polygons. Has area associated with each site. 
- - Shown in red. 
- - Has 62 active sites.
-
-```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
-library(usmap)
-
-alaska_details <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Details.csv"))
-
-alaska_corners <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Corners.csv")) ## each group of corners is a polygon representing one farming operation.
-So, we will need to somehow make those polygons and find the centroid of each group to get points.
-Save as polygons and as points if possible?
-Maybe don't even need the exact polygons, since we know the area of each.
-Almost all are active.
-
-library(tigris)
-
-ak <- counties("Alaska", cb = TRUE) %>%
-  filter(NAME %in% c("Aleutians East", "Lake and Peninsula", "Bristol Bay", "Kodiak Island", "Kenai Peninsula", "Anchorage", "Yakutat", "Hoonah-Angoon", "Haines", "Sitka", "Juneau", "Prince of Wales-Hyder", "Ketchikan Gateway", "Wrangell", "Petersburg", "Valdez-Cordova"))
-
-alaska_details_sf <- st_as_sf(alaska_details, coords = c("x", "y"), crs = crs(ak))
-alaska_corners_sf <- st_as_sf(alaska_corners, coords = c("x", "y"), crs = crs(ak))
-
-ggplot() +
-  geom_sf(data = alaska_corners_sf, col = "red", shape = 5) + 
-  geom_sf(data=ak, fill = "gray") + 
-  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
-    labs(title = "Alaska data", caption = "Comprehensive, up-to-date (2020)")
-
-```
-
-## California:
-
- - https://nrm.dfg.ca.gov/FileHandler.ashx?DocumentID=187229&inline
- - Report current as of May 2021
- - There is a map with commercial locations and a table with exact farm numbers (pages 7 and 8). We could likely estimate or find the location via Google. 
- - And cross reference with the locations listed here: https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/california_locs.png)
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/california_commercial.png)
-
-## New Hampshire:
-
- - https://granit.unh.edu/data/search
- - Comprehensive
- - Up-to-date as of 2020
- - Polygons 
- - 40 sites
-
-```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
-nh_aq <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/New_Hampshire/GRANIT_20211011184728/2020_Aquaculture_Sites.shp")) # 40 sites, assume all active
-
-nh <- counties("New Hampshire", cb = TRUE) %>%
-  filter(NAME %in% c("Rockingham"))
-
-  ggplot() +
-  geom_sf(data = nh_aq, col = "red") + 
- # geom_polygon(data=nh, aes(x=long, y=lat, group=group), fill = "gray") + 
-    geom_sf(data = nh, fill = "gray") + 
-  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
-    labs(title = "New Hampshire data", caption = "Comprehensive, up-to-date (2020)")
-```
-
-## Florida:
+### Florida
 
@@
 
-## Alabama:
+### All states
 
- - "Alabama has an emerging oyster industry with 13 farms comprising of 25 acres in 2015.
-Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise." from https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
- - This has a map... probably our best source for Alabama!: https://alaquaculture.com/state/#list-of-operating-farms
+ - https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
+ - Current as of 2015 
+ - Can definitely use for California to cross reference
+ - Has partial data for other states too
 
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/alabama_Farms.png)
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/all_states_partial.png)
 
-## Mississippi:
+## Not much info
 
- - Can't find much information for Mississippi.
+### Mississippi
 
-## Louisana:
+ - Can't much info on Mississippi mariculture..
+
+### Louisana
 
@@
 
-## Texas:
+### Texas
 
@@
 
-## Oregon:
-
- - Map of general areas where you are allowed to commercially harvest or grow shellfish in Oregon: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/ClassifiedCommercialShellfishGrowingMap.pdf
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/or_areas.png)
-
- - Shellfish distributors list: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/Shellfishdealers.pdf
-
- - 2020 shellfish production report: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/AnnualShellfishProductionReport.pdf
-
-## Connecticut:
-
-Shellfish bed managed
-
- - https://portal.ct.gov/DOAG/Aquaculture1/Aquaculture/Shellfish-Area-Classifications--Maps
- - Only Shellfish
- - Polygons 
- - I believe that these are large areas that have been **approved** for shellfish aquaculture, but not the exact locations of the aquaculture. So this probably isn't helpful.
-
-However, worst case, we could use the data from the Northeast ocean council dataset:
-
-"Connecticut – Data on Connecticut aquaculture was derived from two datasets provided by the State of Connecticut Department of Agriculture/Bureau of Aquaculture and the State of Connecticut Department of Environmental Protection.
-One dataset contains the location of natural shellfish beds.
-Natural beds managed by the state, town or used for recreational harvesting were selected from this dataset, resulting in 1855 polygons.
-The number of beds in use at any given time is subject to change.
-The second dataset contains 46 polygons representing the approximate geographical location of permitted “Certificate for Aquaculture  Operation” gear sites in the Connecticut coastal waters of Long Island Sound via the State of Connecticut Application for Joint Programmatic General Permit for Aquaculture Department of the Army General Permit.
-These datasets are up to date as of January 15, 2016.
-For more information on CT Aquaculture and Shellfish, see the CT Aquaculture Mapping Atlas."
-
-```{r}
-
-ct_shellfish <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/Shellfish_Bed_Managed_shp/SHELLFISH_BED_MANAGED.shp"))
-
-ct <- counties("Connecticut", cb = TRUE)
-
-  ggplot() +
-  geom_sf(data = ct_shellfish, col = "red") + 
-    geom_sf(data = ct, fill = "gray") + 
-  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
-    labs(title = "Connecticut data", caption = "Not Comprehensive, General 'approved' areas")
-```
-
-Another map, this is probably what we need (seaweed and shellfish): https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
-
-## Washington:
+### Washington
 
@@
 
-## All states:
+### Hawaii
 
- - https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
- - Current as of 2015 
- - Can definitely use for California to cross reference
- - Has partial data for other states too
+https://hdoa.hawaii.gov/ai/aquaculture-and-livestock-support-services-branch/aquaculture-in-hawaii/
 
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/all_states_partial.png)
+ - Not much info. There is definitely both offshore aquaculture and shrimp aquaculture in Hawaii.
 
-## North Carolina:
+## No mariculture?
 
-Shellfish
-
- - https://deq.nc.gov/about/divisions/marine-fisheries/licenses-permits-and-leases/shellfish-lease-and-franchise#stats-and-figures
- - Comprehensive for shellfish... just need to figure out how download it. 
- - I believe Shellfish is pretty much the only mariculture that occurs in NC. 
- - Has number totals of leases 
- - Will likely need to send an email.
-
- ![Has lease info for the entire state](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/nc_map.png)
-
-## Virginia:
-
-Shellfish
-
- - https://mrc.virginia.gov/links.shtm
- - They have oyster lease and application data, which *I think* is the only type of aquaculture there. The map isn't downloadable from what I can tell though, so I bet we will have to email to access.
- - They also have a phone app.
-
- ![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/va_map.png)
-
-## Maryland:
-
-Shellfish
-
- - They have individual lease application maps in PDFs, but they would take forever to go through.
-They must have some sort of internal dataset where they store the approved lease info?: https://dnr.maryland.gov/fisheries/pages/aquaculture/applications.aspx
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/maryland_apps.png)
-
-## Delaware:
+### Delaware
 
@@
 
-## South Carolina:
-
- - Super small industry here. 
- - https://www.scseagrant.org/aquaculture/
- - https://www.scseagrant.org/wp-content/uploads/Economic-Contribution-of-Oyster-Mariculture-SC.pdf
- - Only 9 farms, all oyster, as of 2021
-
-## Georgia:
+### Georgia
 
@@
 
-## Massachusetts:
+## Species/production breakdown for US
 
-https://www.mass.gov/service-details/aquaculture
-  - "Massachusetts has 378 shellfish leases.
-Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise."
+Take a look at the species in the US that FAO reports
 
-https://www.mass.gov/doc/2020-dmf-annual-report/download
- - 386 "private shellfish propogation" permits in 2020
+ - These totals really don't match what NOAA reports in their 2019 report...
+They report 44094 metric tonnes of marine aquaculture production for 2018...
+versus 203687 from FAO.
+I think this has to do with NOAA reporting meat weight and FAO reporting live weight (includes shells)
+ - https://media.fisheries.noaa.gov/2021-05/FUS2019-FINAL-webready-2.3.pdf?null=
+ - NOAA also reports that the Gulf region produces the most marine aquaculture by volume.. which seems problematic for us considering we have very poor data for the Gulf states.
+```{r, message=FALSE}
+fao_data_all <- read_csv("../../data/fao_aquaculture_clean.csv")
 
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/mass_permit.png)
- - Also has production data per town or region.
+fao_data_us <- fao_data_all %>%
+  filter(iso3c == "USA")
 
-## Rhode Island:
+fao_data_us_group <- fao_data_us %>%
+  filter(year == 2018)
 
- - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
- - No download option.
+marine <- fao_data_us_group %>%
+  filter(environment == "Marine") %>%
+  filter(!is.na(value))
 
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/rhode_island_map.png)
+# unique(marine$species)
 
-## Hawaii
+# 16 marine spp
+#  [1] "Atlantic salmon"             "Blue mussel"                 "Northern quahog(=Hard clam)"
+#  [4] "Sand gaper"                  "American cupped oyster"      "Red drum"                   
+#  [7] "Whiteleg shrimp"             "Longfin yellowtail"          "Abalones nei"               
+# [10] "Butter clam"                 "Cupped oysters nei"          "Japanese carpet shell"      
+# [13] "Marine fishes nei"           "Pacific cupped oyster"       "Pacific geoduck"            
+# [16] "Pacific littleneck clam"
 
-https://hdoa.hawaii.gov/ai/aquaculture-and-livestock-support-services-branch/aquaculture-in-hawaii/
+## there were 4 species with NA production (so actually 20 marine species total)
+marine_na <- fao_data_us_group %>%
+  filter(environment == "Marine") %>%
+  filter(is.na(value))
+#unique(marine_na$species)
+# [1] "Cockles nei"          "European flat oyster" "Olympia oyster"       "Pacific horse clam"
 
- - Not much info. There is definitely both offshore aquaculture and shrimp aquaculture in Hawaii.
+# sum(marine$value, na.rm = TRUE)
 
-## New Jersey
-
-https://www.nj.gov/agriculture/divisions/anr/sea/
-
- - "Currently, the program licenses more than 100 finfish, shellfish and aquatic plant producers in the state."
-
-https://www.nj.gov/dep/fgw/pdf/marine/shellfish_leasing_policy_atlantic.pdf
-
- - this has maps of all shellfish leases in 2020.. but they are all pdf.
-
-## New York
-
-Suffolk County
-
- - Lease mapper: https://gis.suffolkcountyny.gov/portal/apps/View/index.html?appid=6ae708a346f340ada850544fe25ce0fb
- - Its not totally unreasonable to think that this is the only place in New York that does mariculture? Since its coast is so small.
-
- - Shellfish map for NY and CT, this seems like what we would need: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/ny_shell.png)
+# 203687 total tonnes for marine.. does this seem correct? 
+```

### 2021-12-16 marine/united_states/US_mapping.Rmd
added more info to doc

@@
 
-**There is general info on lease holders, what they farm, and what municipality or city they are in for 6 states:**
+**There is general info on lease holders, what they farm, and what municipality or city they are in for 7 states:**
 
@@
  - South Carolina: Apparently have 9 oyster farms as of 2021
+ - Washington: Approximate locations of commercial net pens.
 
@@
 
-**Couldn't really find any information on 5 states:**
+**Couldn't really find any information on 4 states:**
 
- - Hawaii, Washington, Texas, Louisiana, Mississippi
+ - Hawaii, Texas, Louisiana, Mississippi
 
@@
 
+### Washington
+
+Approved growing areas map
+
+ - https://fortress.wa.gov/doh/oswpviewer/index.html
+
+"DNR leases deep water sites for finfish net pens and floating shellfish rafts and longlines.
+Salmon aquaculture operations have existed in Washington since the 1970s and are scattered throughout Puget Sound.
+Current net pen leases include salmon aquaculture, delayed-release salmon, and herring.
+The use of floating shellfish culture began in 1975 with mussel raft culture in Penn Cove.
+Current floating shellfish culture on rafts or longlines include oysters, mussels, and scallops."
+
+Locations of commercial marine net pens
+ - https://ecology.wa.gov/Water-Shorelines/Shoreline-coastal-management/Aquaculture/Net-pens
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/washington_pens.png)
+
 ## Subset available
@@
 
-Offshore aquaculture in Florida
-
- - As far as I can tell, none yet: https://www.flseagrant.org/aquaculture/openocean/
-
 Other than the above, I can't find much info for Florida. Google maps shows a couple shrimp farms.
@@
 
-### Washington
-
-Approved growing areas map
-
- - https://fortress.wa.gov/doh/oswpviewer/index.html
-
-"DNR leases deep water sites for finfish net pens and floating shellfish rafts and longlines.
-Salmon aquaculture operations have existed in Washington since the 1970s and are scattered throughout Puget Sound.
-Current net pen leases include salmon aquaculture, delayed-release salmon, and herring.
-The use of floating shellfish culture began in 1975 with mussel raft culture in Penn Cove.
-Current floating shellfish culture on rafts or longlines include oysters, mussels, and scallops."
-
-What we used for global: 
-Our Sound, Our Salmon, 2017. [Accessed January 31, 2020] http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/puget_sound.png)
-
 ### Hawaii
@@
 
- - These totals really don't match what NOAA reports in their 2019 report...
-They report 44094 metric tonnes of marine aquaculture production for 2018...
-versus 203687 from FAO.
-I think this has to do with NOAA reporting meat weight and FAO reporting live weight (includes shells)
- - https://media.fisheries.noaa.gov/2021-05/FUS2019-FINAL-webready-2.3.pdf?null=
- - NOAA also reports that the Gulf region produces the most marine aquaculture by volume.. which seems problematic for us considering we have very poor data for the Gulf states.
 ```{r, message=FALSE}
@@
 ```
+
+FAO reports 16 different marine species of production in 2018.
+Additionally, there were 4 species that were previously harvested but had no harvest for 2018.
+FAO reports a total of 203687 live weight tonnes for 2018.
+
+NOAA Fisheries of the United States 2019 Report: 
+https://media.fisheries.noaa.gov/2021-05/FUS2019-FINAL-webready-2.3.pdf?null=
+
+ - NOAA report 44094 metric tonnes of marine aquaculture production for 2018...
+versus 203687 from FAO.
+I think this has to do with NOAA reporting meat weight and FAO reporting live weight (includes shells)
+ - NOAA also reports that the Gulf region produces th e most marine aquaculture by volume.. which seems problematic for us considering we have very poor farm level data for the Gulf states.
+
+![gulf](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/us_mariculture.png)
+
+2018 Census of Aquaculture: https://www.nass.usda.gov/Publications/AgCensus/2017/Online_Resources/Aquaculture/Aqua.pdf
+
+ - Table 1 shows aquaculture farms per state, but it is not split between marine and freshwater from what I can tell. Also split by species group (mollusk, crustaceans, etc.)
+ - Table 10 shows saltwater acres and number of farms used for aquaculture production.
+However, there are landlocked states, so we don't know if it is actually marine or on-land saltwater aquaculture.
+It does seem reasonable that this would be pretty close to the actual number of farms..
+ - Table 11 shows sources of water, with "Saltwater" included. This is just where the water comes from. 
+ - Table 12 mollusks off bottom seems reasonable to think most of these will be in marine environments. Almost all of the states listed are coastal states.
+
+ - It seems like "Mollusks off bottom", "Mollusks on bottom", "Sea vegetables" are the only ones that I am 80% sure are marine farms... 
+ - They also have data at the county level. I know this wouldn't be perfect, but we could filter for coastal counties.

### 2022-01-28 analysis/SI_figs.Rmd
updated for resubmission!

@@
 
-ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", spp_group))
+ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", spp_group), units = "in", width = 8.07, height = 5.34)
 }
@@
 
-ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", data_type_2_id))
+ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", data_type_2_id), units = "in", width = 8.07, height = 5.34)
 
@@
 
-ggsave("analysis/si_figs/workflow_fig_1.jpg")
+ggsave("analysis/si_figs/workflow_fig_1.jpg", units = "in", width = 8.07, height = 5.34)
 
@@
 
-ggsave("analysis/si_figs/workflow_fig_2.jpg")
+ggsave("analysis/si_figs/workflow_fig_2.jpg", units = "in", width = 8.07, height = 5.34)
 

### 2022-01-28 analysis/match_data_sources.Rmd
updated for resubmission!

@@
 
+library(readxl)    
+read_excel_allsheets <- function(filename, tibble = FALSE) {
+    # I prefer straight data.frames
+    # but if you like tidyverse tibbles (the default with read_excel)
+    # then just pass tibble = TRUE
+    sheets <- readxl::excel_sheets(filename)
+    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
+    if(!tibble) x <- lapply(x, as.data.frame)
+    names(x) <- sheets
+    x
+}
+
+data <- read_excel_allsheets("analysis/data/mariculture_mapping_sources_raw.xlsx")
+
+df <- plyr::ldply(data, as.data.frame) %>%
+  mutate(`Data year: farm locations` = as.character(`Data year: farm locations`),
+         `Data year: number of farms` = as.character(`Data year: number of farms`))
+
 data <- read_csv(file.path("marine/output/all_marine_farms.csv")) %>% 
@@
 # read in our sources spreadsheet (manually uploaded by GC)
-sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
+sources <- df %>%
   clean_names() %>%
@@
   mutate(data_year_number_of_farms = as.character(data_year_number_of_farms)) %>%
+ # mutate(estimated_farms = ifelse(is.na(estimated_farms), estimated_farms_2, estimated_farms)) %>%
+  dplyr::select(-id) %>%
   mutate(data_type_2 = case_when(
@@
 
-## data types with comprehensive # of farms are A, B, and C. These all recieve their production/# of farms to get prod per farm.
+## data types with comprehensive # of farms are A, B, and C. These all receive their production/# of farms to get prod per farm.
 
@@
 
+test <- all_farms_sources %>%
+  filter(iso3c == "CHN", 
+         species_group == "Shrimps and prawns")
+
+## will need to fix china bivalve and shrimp
+
+sum(all_farms_sources$tonnes_per_farm) # 29639681
+sum(all_prod$fao_tonnes_production) # 29623515
+
+29623515 - 29639681 # off by about 16k.. probably because of rounding issues 
 ```
@@
 # Salmon: CAN, USA
-# Shrimp: USA 
-# Bivalve: AUS, CAN, USA
+# Shrimp: USA, CHN 
+# Bivalve: AUS, CAN, USA, CHN
 # General marine fish: TWN
@@
 
+## China bivalve fix
+### There are 11 farms from ASC...
+
+# read in ASC dataset for China bivalves
+farms_chn <- read.csv(here("marine/bivalve/bivalve_farms/data/ASC_bivalve_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "CHN") %>%
+  mutate(data_quality = 2)
+
+## so it looks like the first 11 rows are the ASC rows.. the geometries are not as precise 
+CHN_bivalve_fix <- all_farms_sources_gadm %>%
+  dplyr::filter(iso3c == "CHN", 
+               species == "Unfed or algae fed shellfish", 
+               data_type == "known locations") %>%
+  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
+  mutate(row = row_number()) %>%
+  mutate(data_source = ifelse(row %in% c(1:11), ds_1, ds_2)) %>%
+  mutate(data_year = 2021) %>%
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
+
+## do the same for China shrimp
+
+farms_chn <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
+  dplyr::filter(iso3c == "CHN") %>%
+  mutate(data_quality = 2)
+
+## so it looks like the first 4 rows are the ASC rows.. the geometries are not as precise 
+CHN_shrimp_fix <- all_farms_sources_gadm %>%
+  dplyr::filter(iso3c == "CHN", 
+               species == "Shrimp", 
+               data_type == "known locations") %>%
+  separate(col = data_source, into = c("ds_1", "ds_2"), sep = ";") %>%
+  mutate(row = row_number()) %>%
+  mutate(data_source = ifelse(row %in% c(1:4), ds_1, ds_2)) %>%
+  mutate(data_year = 2021) %>%
+  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, tonnes_per_farm, details, data_source, data_year, geometry)
+
 ##### Now add these back into total dataset #####
@@
   filter(iso3c != "USA"|species != "Shrimp") %>%
-  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix) %>%
+  filter(iso3c != "CHN"|species != "Unfed or algae fed shellfish"|data_type != "known locations") %>%
+  filter(iso3c != "CHN"|species != "Shrimp"|data_type != "known locations") %>%
+  rbind(TWN_finfish_fix, USA_bivalve_fix, USA_salmon_fix, USA_shrimp_fix, CAN_bivalve_fix, CAN_salmon_fix, AUS_bivalve_fix, CHN_bivalve_fix, CHN_shrimp_fix) %>%
   mutate(data_year = as.numeric(data_year)) %>%
@@
 unique(all_farms_sources_final$species_group)
+sum(all_farms_sources_final$tonnes_per_farm) # 29639681
 
@@
 test <- all_farms %>%
-  filter(iso3c == "CRI", str_detect(species_group, "hrimp")) %>%
+  filter(iso3c == "GBR", str_detect(species_group, "almo")) %>%
     st_as_sf(., 

### 2022-01-28 analysis/paper_figs.Rmd
updated for resubmission!

@@
 test <- all_farms_sf %>%
-  filter(iso3c == "ECU")
+  filter(iso3c == "AUS")
 mapview(test, zcol = "data_type") ## one weird MFG from ASC.. i think these are fine. Justifiable since it is from the ASC...
@@
 
+test <- all_farms %>%
+  group_by(data_type) %>%
+  summarise(n_farms = n())
 ```
@@
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n N = 9,750", "Modeled locations, known number of farms \n N = 10,519", "Modeled locations, estimated number of farms \n N = 75,073"))
+                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c("Known locations \n N = 16,138", "Modeled locations, known number of farms \n N = 9,951", "Modeled locations, estimated number of farms \n N = 69,354"))
 
@@
 ggdraw(plot_final)
-ggsave("analysis/figs/map_fig_31km.jpg")
+ggsave("analysis/figs/map_fig_final.jpg", units = "in", width = 8.07, height = 5.34)
 
@@
 
-# ## Norway
-# nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
+## USA NW
+# usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
 #   annotation_map_tile(type = "osm", zoomin = 0) + 
-#   geom_spatial_point(size = 0.5, alpha = 0.7) + 
+#   geom_spatial_point(size = 1.5, alpha = 0.7) + 
 #   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
-#                     breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
-#     coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
+#                     breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
+#   coord_sf(crs = 4326, xlim = c(-123, -122), ylim = c(47, 48), expand = FALSE) +
+#  # coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + 
+#   #coord_sf(crs = 4326, xlim = c(-45, -25), ylim = c(70, 125), expand = FALSE) +
+#  # st_crop(xmin = -20, xmax = 45, ymin = 30, ymax = 73) +
 #   theme(legend.position = "bottom", 
@@
 # panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
-#   ggtitle("C")
-# nor_zoom
+#   ggtitle("C") # + 
+#  # scale_alpha_manual(values = c(0.7, 0.7, 1))
+# 
+# usa_zoom
 
-## USA NE 
-usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
+## Australia 
+aus_zoom <- ggplot(all_farms %>%
+                     filter(iso3c == "AUS"), aes(X,Y, col = data_type_plot)) +
   annotation_map_tile(type = "osm", zoomin = 0) + 
-  geom_spatial_point(size = 1.5, alpha = 0.7) + 
+  geom_spatial_point(size = 1.3, alpha = 0.7) + 
   scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                     breaks = c("Known locations", "Modeled locations, known number of farms", "Modeled locations, estimated number of farms")) +
-    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
+coord_sf(crs = 4326, xlim = c(135.5, 138), ylim = c(-36, -34), expand = FALSE) + 
+  #coord_sf(crs = 4326, xlim = c(135.8, 136.8), ylim = c(-35, -34.5), expand = FALSE) + 
   theme(legend.position = "bottom", 
@@
         axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 60, hjust = 1),
         legend.key = element_rect(fill = NA),
-        axis.text.x = element_text(angle = 60, hjust = 1),
         text=element_text(family="Times New Roman"),
 panel.border = element_rect(colour = "grey69", fill=NA, size=3, linetype = "longdash")) +
-  ggtitle("C") # + 
- # scale_alpha_manual(values = c(0.7, 0.7, 1))
-
-usa_zoom
+  ggtitle("C")
+aus_zoom
 
@@
 plot1
-ggsave("analysis/figs/chl_ecu_zoom_31km.jpg")
+ggsave("analysis/figs/chl_ecu_zoom.jpg", units = "in", width = 8.07, height = 5.35)
 
-## USA and China
+## AUS and China
 
-plot2 <- (usa_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
+plot2 <- (aus_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
 
 plot2
-ggsave("analysis/figs/usa_chn_zoom_31km.jpg")
+ggsave("analysis/figs/aus_chn_zoom.jpg", units = "in", width = 8.07, height = 5.35)
 
@@
 
+plot1 / plot2
 ```

### 2022-01-28 analysis/paper_stats.Rmd
updated for resubmission!

@@
 
-sum(all_farms$tonnes_per_farm) # 29638328
+sum(all_farms$tonnes_per_farm) # 29642964
 
@@
   filter(data_type_2 != "A")
-sum(data_type_no_A$tonnes_per_farm) # 26070193
+sum(data_type_no_A$tonnes_per_farm) # 26074829
 
-26070193/29638328 # 0.8796108
+26074829/29642964 # 0.8796296 # ~88% of production is data limited
 
@@
 #   <chr>                                        <int>     <int> <dbl>
-# 1 known location                               9750     95341  10.2
-# 2 modeled location, estimated number of farms 75073     95341  78.7
-# 3 modeled location, known number of farms     10519     95341  11.0
+# 1 known locations                              16032     95331  16.8
+# 2 modeled locations, estimated number of farms 69348     95331  72.7
+# 3 modeled locations, known number of farms      9951     95331  10.4
 
@@
 known_countries <- all_farms %>%
-  filter(data_type == "known location") %>%
+  filter(data_type == "known locations") %>%
   distinct(iso3c)
@@
 # 58166 points
-58166/95342 # 0.6099201 = 61%
+58166/95443 # 0.6094318 = ~61%
 
@@
   filter(iso3c == "CHN") %>%
-  filter(data_type == "known location") # 15 locations
+  filter(data_type == "known locations") # 5739 locations
 
@@
 top_known <- all_farms %>%
-  filter(data_type == "known location") %>%
+  filter(data_type == "known locations") %>%
   group_by(iso3c) %>%
@@
 
-sum(no_info$tonnes_per_farm) # 155205.1
+sum(no_info$tonnes_per_farm) # 156132.3
 
@@
 
-155205.1/29623515 # 0.005239253
+156132.3/29623515 # 0.005270553
 
@@
 
-However, 16 countries (representing 10% of fish and invertebrate mariculture production) had comprehensive farm locations across all taxa (i.e. no estimation or interpolation required, Table S3)
+However, 17 countries (representing 10% of fish and invertebrate mariculture production) had comprehensive farm locations across all taxa (i.e. no estimation or interpolation required, Table S3)
 ```{r}
@@
 
-"Thirty-six of the countries in the table have comprehensive “number of farm” data across all types of mariculture they produce (data types A, B, or C), accounting for 12% of the global fish and invertebrate mariculture production (Albania, Belize, Bulgaria, Canada, Chile, Colombia, Croatia, Cyprus, Denmark, El Salvador, Faroe Islands, Finland, French Polynesia, Germany, Greece, Guatemala, Guernsey, Hong Kong, Ireland, Italy, Jersey, Madagascar, Malta, Netherlands, New Zealand, Norway, Peru, Portugal, Singapore, Slovenia, South Africa, Sri Lanka, Tunisia, Turkey, United Arab Emirates, United Kingdom)."
+"Thirty-six countries have comprehensive “number of farm” data across all types of mariculture they produce (data types A, B, or C), accounting for 12% of the global fish and invertebrate mariculture production."
 
 ```{r}
-
 all_comp <- all_farms %>%
   group_by(iso3c) %>%
-  mutate(check = all(data_type_2 %in% c("A", "B", "C"))) %>%
+  mutate(check = all(data_type_2 %in% c("A","B","C"))) %>%
   filter(check == TRUE)
+
 sort(unique(all_comp$country))
+
+print(unique(all_comp$country))
 
@@
 
-# Albania', 'Belize', 'Bulgaria', 'Canada', 'Chile', 'Colombia', 'Croatia', 'Cyprus', 'Denmark', 'El Salvador ', 'Faroe Islands', 'Finland', 'French Polynesia', 'Germany', 'Greece', 'Guatemala', 'Guernsey', 'Hong Kong ', 'Ireland', 'Italy', 'Jersey', 'Madagascar', 'Malta', 'Netherlands', 'New Zealand', 'Norway', 'Peru', 'Portugal', 'Singapore', 'Slovenia', 'South Africa', 'Sri Lanka', 'Tunisia', 'Turkey', 'United Arab Emirates', 'United Kingdom
+# 'Albania', 'Belize', 'Bulgaria', 'Canada', 'Chile', 'Colombia', 'Croatia', 'Cyprus', 'Denmark', 'El Salvador ', 'Faroe Islands', 'Finland', 'French Polynesia', 'Germany', 'Greece', 'Guatemala', 'Guernsey', 'Hong Kong ', 'Ireland', 'Italy', 'Jersey', 'Madagascar', 'Malta', 'Netherlands', 'New Zealand', 'Norway', 'Peru', 'Portugal', 'Singapore', 'Slovenia', 'South Africa', 'Sri Lanka', 'Tunisia', 'Turkey', 'United Arab Emirates', 'United Kingdom'
 
@@
 
-3788091/31011413 # 0.1221515 ~ 10%
-
+3788091/31011413 # 0.1221515 ~ 12%
 ```
 
-Using the country/species grouping combinations with presumed comprehensive farm count data (N=74, 17% of production included, data type A/B/C, see Table S3)
+"Using the country/species grouping combinations with presumed comprehensive farm count data (N=74, 17% of production included, data type A/B/C, see Table S3)"
 ```{r}
@@
 
+length(unique(test$country))
+
 sum(test$tonnes_per_farm)
@@
 
+test2 <- test %>%
+  group_by(country, species_group) %>%
+  summarise(n()) # 74 combos
+
+```
+
+```{r}
+by_data_type_spp <- all_farms %>%
+  group_by(data_type, species_group) %>%
+  summarise(n_obs = n()) %>%
+  mutate(total_obs = sum(n_obs)) %>% 
+  ungroup() %>%
+  mutate(pct = n_obs/total_obs*100)
+
+by_spp <- all_farms %>%
+  group_by(species_group) %>%
+  summarise(n_obs = n()) %>%
+  mutate(total_obs = sum(n_obs)) %>% 
+  ungroup() %>%
+  mutate(pct = n_obs/total_obs*100)
 ```

### 2022-01-28 analysis/validation_testing.Rmd
updated for resubmission!

--- 2021-07-09 analysis/validation_testing.Rmd
@@
 
+cell_rast_df <- raster_df(food_raster) %>%
+  dplyr::select(1:2)
+
+## establish CRSs
+
+## food 81km2 at equator 
+eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask.tif"))
+plot(raster::area(eez_81))
+plot(eez_81)
+cellStats(raster::area(eez_81), "mean")
+
+test <- data.frame(raster::values(raster::area(eez_81)))
+
+## 36km2 equal area
+eez_36_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_cea_36km.tif"))
+plot(eez_36_cea)
+
+new_crs <- "+proj=cea +lat_ts=45 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
+new_raster <- raster(nrows=3000, ncols=4736, xmn=-14207430, xmx=14208570, ymn=-9000182, ymx=8999818, crs = new_crs)
+
+## 25km2 equal area
+eez_25_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_cea_25km.tif"))
+
+cea_25_crs <- crs(eez_25_cea)
+plot(eez_25_cea)
+
+## 1/4 degree cells 
+eez_quart_cell <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_quarter_degree.tif"))
+
+quarter_crs <- crs(eez_quart_cell)
+
 ```
+
+Read in validation dataset
+
+```{r}
+validation_all <- readRDS(file.path("data/all_validation_farms_resubmission.rds"))  %>%
+  mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
+                          type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
+                          type == "shrimp" ~ "Shrimps and prawns", 
+                          type == "tuna" ~ "Bluefin tuna", 
+                          type == "marine_fish_general" ~ "General marine fish"))
+
+table_3 <- read_csv("analysis/tables/SI_table_3.csv")
+
+iso <-   data.frame(iso3c = countrycode(table_3$country, origin = 'country.name', destination = 'iso3c'))
+
+table_3_iso3c <- table_3 %>%
+  cbind(iso)
+
+data_type_val <- validation_all %>%
+  left_join(table_3_iso3c, by = c("iso3c", "species_group"))
+
+data_type_A <- data_type_val %>%
+ filter(data_type_2 %in% c("A"))
+
+table_3_A <- table_3_iso3c %>%
+  filter(data_type_2 %in% c("A"))
+
+```
+
+Split data
+
+```{r}
+validation_farms <- data_type_A %>%
+ filter(source == "modeled validation") %>%
+  mutate(count_farms = 1)
+
+val_farms_cea_36 <- validation_farms %>%
+  st_transform(crs = new_crs)
+
+val_farms_cea_25 <- validation_farms %>%
+  st_transform(crs = cea_25_crs)
+
+val_farms_quarter <- validation_farms %>%
+  st_transform(crs = quarter_crs)
+
+real_farms <- data_type_A %>%
+  filter(source == "real") %>%
+  mutate(count_farms = 1)
+
+real_farms_cea_36 <- real_farms %>%
+  st_transform(crs = new_crs)
+
+real_farms_cea_25 <- real_farms %>%
+  st_transform(crs = cea_25_crs)
+
+real_farms_quart <- real_farms %>%
+  st_transform(crs = quarter_crs)
+```
+
+Rasterize data to count number of farms per raster cell with 36km2 equal area
+
+```{r}
+
+val_rast <- rasterize(val_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum") # 8552
+
+plot(val_rast, col = "black")
+#s <- raster::select(val_rast)
+#plot(s)
+
+real_rast <- rasterize(real_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8552
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8552    8552
+
+```
+
+Use our EEZ mask to create a confusion matrix for CEA 36km2 cell sizes
+
+ - AUC of ~0.60
+```{r}
+
+plot(eez_36_cea, col = "black")
+
+world_coast <- as.data.frame(eez_36_cea) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask_cea_36km))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8535
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8473
+
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms
+
+test <- rast_stack*eez_36_cea
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8535    8473
+
+## we are losing some farms...
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+#           Reference
+# Prediction       0       1
+#          0 1171909    2552
+#          1    2721     682
+#                                           
+#                Accuracy : 0.9955          
+#                  95% CI : (0.9954, 0.9956)
+#     No Information Rate : 0.9973          
+#     P-Value [Acc > NIR] : 1.00000         
+#                                           
+#                   Kappa : 0.2033          
+#                                           
+#  Mcnemar's Test P-Value : 0.02069         
+#                                           
+#             Sensitivity : 0.9977          
+#             Specificity : 0.2109          
+#          Pos Pred Value : 0.9978          
+#          Neg Pred Value : 0.2004          
+#              Prevalence : 0.9973          
+#          Detection Rate : 0.9949          
+#    Detection Prevalence : 0.9971          
+#       Balanced Accuracy : 0.6043          
+#                                           
+#        'Positive' Class : 0
+
+# library(pROC)
+# roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.6019
+# 
+# 
+# library(pROC)
+# library(randomForest)
+# 
+# 
+# roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 0.6068
+# 
+# roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
+# 
+# roc.df <- data.frame(tpp = roc.info$sensitivities*100,
+#                      fpp = (1-roc.info$specificities)*100,
+#                      thresholds = roc.info$thresholds)
+# 
+# 
+# #### ROC curve try #2
+# # https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
+# 
+# library(ROCR)
+#   
+#  
+# pred = eez_cells_df$pred_count
+# 
+# pred = prediction(pred, eez_cells_df$real_count)
+# 
+# perf = performance(pred, "acc")
+# plot(perf)
+# 
+# perf_cost <- performance(pred, "cost")
+# plot(perf_cost)
+# 
+# roc = performance(pred, "tpr", "fpr")
+# 
+# plot(roc, colorize = T, lwd=2)
+# abline(a=0, b=1)
+# 
+# auc = performance(pred, measure = "auc")
+# print(auc@y.values)
+# # 0.6091016
+
+```
+
+Use our EEZ mask to create a confusion matrix for CEA 25km2 cell sizes
+
+ - AUC of ~0.59 - worse than 36km2... makes sense! 
+```{r}
+
+val_rast <- rasterize(val_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum")
+
+plot(val_rast, col = "black")
+#s <- raster::select(val_rast)
+#plot(s)
+
+real_rast <- rasterize(real_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8552
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8552    8552
+
+plot(eez_25_cea, col = "black")
+
+world_coast <- as.data.frame(eez_25_cea) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask_cea_25km))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8536
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8482
+
+## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms. This is likely due to reprojection weirdness
+
+test <- rast_stack*eez_25_cea
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8536    8482
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction       0       1
+#          0 1689310    2929
+#          1    3100     639
+#                                           
+#                Accuracy : 0.9964          
+#                  95% CI : (0.9964, 0.9965)
+#     No Information Rate : 0.9979          
+#     P-Value [Acc > NIR] : 1.00000         
+#                                           
+#                   Kappa : 0.1731          
+#                                           
+#  Mcnemar's Test P-Value : 0.02857         
+#                                           
+#             Sensitivity : 0.9982          
+#             Specificity : 0.1791          
+#          Pos Pred Value : 0.9983          
+#          Neg Pred Value : 0.1709          
+#              Prevalence : 0.9979          
+#          Detection Rate : 0.9961          
+#    Detection Prevalence : 0.9978          
+#       Balanced Accuracy : 0.5886          
+#                                           
+#        'Positive' Class : 0
+
+```
+
+Use our EEZ mask to create a confusion matrix for 0.25 X 0.25 degree cell sizes (about 769.3152km2 at equator). Average cell size is 490.3108 km2
+
+ - AUC of ~72.05 ; makes sense that is it better!
+
+```{r}
+test <- raster::area(eez_quart_cell)
+
+cellStats(test, "mean") # 490.3108
+
+mean(test@data@values) # 490.3108
+
+val_rast <- rasterize(val_farms_quarter, eez_quart_cell, field = "count_farms", fun = "sum")
+plot(val_rast)
+
+cellStats(val_rast, "sum")
+
+plot(val_rast, col = "black")
+
+real_rast <- rasterize(real_farms_quart, eez_quart_cell, field = "count_farms", fun = "sum")
+plot(real_rast)
+
+cellStats(real_rast, "sum") # 8552
+plot(real_rast, col = "black")
+
+rast_stack <- stack(val_rast, real_rast)
+cellStats(rast_stack, "sum")
+
+# layer.1 layer.2 
+#    8552    8552
+
+plot(eez_quart_cell, col = "black")
+
+world_coast <- as.data.frame(eez_quart_cell) %>%
+  mutate(cell = row_number()) %>%
+  filter(!is.na(eez_validation_mask_quarter_degree))
+
+eez_cells_df <- as.data.frame(rast_stack) %>%
+  rename("predicted" = "layer.1", "real" = "layer.2") %>%
+  mutate(pred_count = ifelse(predicted >=1, 1, 0),
+         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
+  mutate(real_count = ifelse(real>=1,1,0)) %>%
+  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
+         real_count = ifelse(is.na(real_count), 0, real_count), 
+         real = ifelse(is.na(real), 0, real),
+         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
+  mutate(cell = row_number()) %>% 
+  filter(cell %in% c(world_coast$cell))
+
+sum(eez_cells_df$predicted, na.rm = TRUE) # 8124
+
+sum(eez_cells_df$real, na.rm = TRUE) # 8173
+
+## still missing some farms..
+
+test <- rast_stack*eez_quart_cell
+
+cellStats(test,"sum") 
+# layer.1 layer.2 
+#    8124    8173
+
+#### make a confusion matrix
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction     0     1
+#          0 84570   639
+#          1   902   514
+#                                           
+#                Accuracy : 0.9822          
+#                  95% CI : (0.9813, 0.9831)
+#     No Information Rate : 0.9867          
+#     P-Value [Acc > NIR] : 1               
+#                                           
+#                   Kappa : 0.3912          
+#                                           
+#  Mcnemar's Test P-Value : 2.486e-11       
+#                                           
+#             Sensitivity : 0.9894          
+#             Specificity : 0.4458          
+#          Pos Pred Value : 0.9925          
+#          Neg Pred Value : 0.3630          
+#              Prevalence : 0.9867          
+#          Detection Rate : 0.9763          
+#    Detection Prevalence : 0.9837          
+#       Balanced Accuracy : 0.7176          
+#                                           
+#        'Positive' Class : 0
+
+```
+
+Use our suitability mask to create a confusion matrix for XX degree cell sizes (about 81km2 at equator, ~10km of coastline) with data type A real farms
+
+ - What % of data type A real farms fall into a suitable cell?
+ - What % fall out of a suitable cell? 
+ - What % of suitable cells do not have any farms in them? 
+ - etc.
+
+At 5 arc minute resolution (~10 km of coastline at the equator), when comparing our suitable areas to data type A real farms, we have a balanced accuracy of 0.81.
+Conducting this same analysis at a coarser resolution of 0.25 degrees (~30 km of coastline at the equator), we see a higher balanced accuracy of xx.
+Given this, we suggest utilizing our maps at a resolution of 5 arc minutes or larger, as 5 arc minutes produces a defensible accuracy, and aligns with other types of food production maps (e.g.
+MAPSPAM, FAO, etc).
+
+When comparing to the coarser resolution of 0.25 degrees, the AUC jumps to 0.84.
+
+```{r}
+
+suitability_81 <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suitability.tif")
+plot(suitability_81)
+
+real_rast <- rasterize(real_farms 
+                       , 
+                       suitability_81, field = "count_farms", fun = "sum")
+
+plot(real_rast, col = 'red')
+
+cellStats(real_rast, "sum") # 8179
+plot(real_rast, col = "black")
+
+# norway_suit <- raster::crop(suitability_81, extent(-25, 50, 50, 75))
+# norway_farm <- raster::crop(real_rast, extent(-25, 50, 50, 75))
+# 
+# plot(norway_suit)
+# plot(norway_farm, add = TRUE, col = "red")
+# 
+# chile_suit <- raster::crop(suitability_81, extent(-80, -70, -44, -40))
+# chile_farm <- raster::crop(real_rast, extent(-80, -70, -44, -40))
+# 
+# plot(chile_suit)
+# plot(chile_farm, add = TRUE, col = "red")
+# 
+real_suit_stack <- stack(real_rast, suitability_81)
+
+real_suit_df <- as.data.frame(real_suit_stack) %>%
+  mutate(layer_count = ifelse(layer >=1, 1, 0),
+         suit_count = ifelse(ocean_land_suitability >=1, 1, 0)) %>%
+  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
+         suit_count = ifelse(is.na(suit_count), 0, suit_count))
+# 
+# 
+# analysis1 <- real_suit_df %>%
+#   filter(layer >= 1, ocean_land_suitability == 1)
+# 
+# sum(analysis1$layer) # 8179
+# 5277/8179 # 0.6451889 = 65% of real farms fall into suitable areas...
+# 
+# analysis2 <- real_suit_df %>%
+#   filter(layer >= 1, is.na(ocean_land_suitability))
+# 
+# sum(analysis2$layer) # 2902
+# 
+# 2902/8179 # 35% fall out of suitable areas
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction       0       1
+#          0 6402310     932
+#          1  118298    1660
+#                                           
+#                Accuracy : 0.9817          
+#                  95% CI : (0.9816, 0.9818)
+#     No Information Rate : 0.9996          
+#     P-Value [Acc > NIR] : 1               
+#                                           
+#                   Kappa : 0.0263          
+#                                           
+#  Mcnemar's Test P-Value : <2e-16          
+#                                           
+#             Sensitivity : 0.98186         
+#             Specificity : 0.64043         
+#          Pos Pred Value : 0.99985         
+#          Neg Pred Value : 0.01384         
+#              Prevalence : 0.99960         
+#          Detection Rate : 0.98147         
+#    Detection Prevalence : 0.98161         
+#       Balanced Accuracy : 0.81114         
+#                                           
+#        'Positive' Class : 0
+
+#### Now look at other resolutions
+
+## 36km2 equal area
+suitability_36 <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suit_36km.tif")
+plot(suitability_36)
+
+real_rast <- rasterize(real_farms_cea_36
+                       , 
+                       suitability_36, field = "count_farms", fun = "sum")
+
+plot(real_rast, col = 'red')
+
+cellStats(real_rast, "sum") # 8552
+plot(real_rast, col = "black")
+
+real_suit_stack <- stack(real_rast, suitability_36)
+
+real_suit_df <- as.data.frame(real_suit_stack) %>%
+  mutate(layer_count = ifelse(layer >=1, 1, 0),
+         suit_count = ifelse(ocean_land_suit_36km >=1, 1, 0)) %>%
+  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
+         suit_count = ifelse(is.na(suit_count), 0, suit_count))
+
+analysis1 <- real_suit_df %>%
+  filter(layer >= 1, ocean_land_suit_36km == 1)
+
+sum(analysis1$layer) # 5505
+5505/8552 # 0.6437091 = 64% of real farms fall into suitable areas...
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction        0        1
+#          0 13967424     1337
+#          1   237288     1951
+#                                           
+#                Accuracy : 0.9832          
+#                  95% CI : (0.9831, 0.9833)
+#     No Information Rate : 0.9998          
+#     P-Value [Acc > NIR] : 1               
+#                                           
+#                   Kappa : 0.0156          
+#                                           
+#  Mcnemar's Test P-Value : <2e-16          
+#                                           
+#             Sensitivity : 0.983295        
+#             Specificity : 0.593370        
+#          Pos Pred Value : 0.999904        
+#          Neg Pred Value : 0.008155        
+#              Prevalence : 0.999769        
+#          Detection Rate : 0.983068        
+#    Detection Prevalence : 0.983162        
+#       Balanced Accuracy : 0.788332        
+#                                           
+#        'Positive' Class : 0
+
+# This makes sense given the finer resolution
+
+## 25km2 equal area
+suitability_25 <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suit_25km.tif")
+plot(suitability_25)
+
+real_rast <- rasterize(real_farms_cea_25
+                       , 
+                       suitability_25, field = "count_farms", fun = "sum")
+
+plot(real_rast, col = 'red')
+
+cellStats(real_rast, "sum") # 8552
+plot(real_rast, col = "black")
+
+real_suit_stack <- stack(real_rast, suitability_25)
+
+real_suit_df <- as.data.frame(real_suit_stack) %>%
+  mutate(layer_count = ifelse(layer >=1, 1, 0),
+         suit_count = ifelse(ocean_land_suit_25km >=1, 1, 0)) %>%
+  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
+         suit_count = ifelse(is.na(suit_count), 0, suit_count))
+
+analysis1 <- real_suit_df %>%
+  filter(layer >= 1, ocean_land_suit_25km == 1)
+
+sum(analysis1$layer) # 5518
+5518/8552 # 0.6452292 = 65% of real farms fall into suitable areas...
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction        0        1
+#          0 20112053     1505
+#          1   343120     2122
+#                                           
+#                Accuracy : 0.9832          
+#                  95% CI : (0.9831, 0.9832)
+#     No Information Rate : 0.9998          
+#     P-Value [Acc > NIR] : 1               
+#                                           
+#                   Kappa : 0.0118          
+#                                           
+#  Mcnemar's Test P-Value : <2e-16          
+#                                           
+#             Sensitivity : 0.983226        
+#             Specificity : 0.585057        
+#          Pos Pred Value : 0.999925        
+#          Neg Pred Value : 0.006146        
+#              Prevalence : 0.999823        
+#          Detection Rate : 0.983051        
+#    Detection Prevalence : 0.983125        
+#       Balanced Accuracy : 0.784141        
+#                                           
+#        'Positive' Class : 0
+
+## quarter degree cells
+
+suitability_quart <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_land_suit_quart.tif")
+plot(suitability_quart)
+
+real_rast <- rasterize(real_farms_quart
+                       , 
+                       suitability_quart, field = "count_farms", fun = "sum")
+
+plot(real_rast, col = 'red')
+
+cellStats(real_rast, "sum") # 8179
+plot(real_rast, col = "black")
+
+real_suit_stack <- stack(real_rast, suitability_quart)
+
+real_suit_df <- as.data.frame(real_suit_stack) %>%
+  mutate(layer_count = ifelse(layer >=1, 1, 0),
+         suit_count = ifelse(ocean_land_suit_quart >=1, 1, 0)) %>%
+  mutate(layer_count = ifelse(is.na(layer_count), 0, layer_count),
+         suit_count = ifelse(is.na(suit_count), 0, suit_count))
+
+analysis1 <- real_suit_df %>%
+  filter(layer >= 1, ocean_land_suit_quart == 1)
+
+sum(analysis1$layer) # 5380
+5380/8179 # 0.6577821 = 66% of real farms fall into suitable areas...
+
+confusion_mat <- caret::confusionMatrix(data = as.factor(real_suit_df$suit_count), reference = as.factor(real_suit_df$layer_count))
+
+confusion_mat
+
+# Confusion Matrix and Statistics
+# 
+#           Reference
+# Prediction      0      1
+#          0 709283    325
+#          1  13933    779
+#                                         
+#                Accuracy : 0.9803        
+#                  95% CI : (0.98, 0.9806)
+#     No Information Rate : 0.9985        
+#     P-Value [Acc > NIR] : 1             
+#                                         
+#                   Kappa : 0.0959        
+#                                         
+#  Mcnemar's Test P-Value : <2e-16        
+#                                         
+#             Sensitivity : 0.98073       
+#             Specificity : 0.70562       
+#          Pos Pred Value : 0.99954       
+#          Neg Pred Value : 0.05295       
+#              Prevalence : 0.99848       
+#          Detection Rate : 0.97924       
+#    Detection Prevalence : 0.97969       
+#       Balanced Accuracy : 0.84318       
+#                                         
+#        'Positive' Class : 0  
+```
+
+```{r}
+# gentry <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/gentry/karakoenig"))
+```

### 2022-01-28 marine/STEP1_species_groups/STEP1_species_groups.Rmd
updated for resubmission!

@@
   dplyr::filter(aq_group == "salmonids")
-sum(test$total_tonnes) #
+sum(test$tonnes) # 2753752
 
@@
 38731.97/29662247 # we exclude around 0.1% of marine aquaculture
+
+## what is the proportion of marine salmon aquaculture that we include?
+
+# we include 2753752 tonnes of marien salmon aquaculture
+fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
+ filter(environment %in% c("Marine", "Brackishwater")) %>%
+  left_join(aq_groups) %>%
+  dplyr::filter(year == 2017,
+                !is.na(value),
+                !is.na(aq_group)) %>%
+  # dplyr::filter(value < 500) %>%
+  dplyr::filter(aq_group == "salmonids") %>%
+  group_by(aq_group, country, species, year) %>%
+  summarise(tonnes = sum(value)) %>%
+  ungroup()  %>%
+  # dplyr::filter(tonnes >= 500) %>%
+  group_by(country, year) %>%
+  summarise(total_tonnes = sum(tonnes))# %>%
+ # arrange(aq_group)
+
+sum(fao_1$total_tonnes) # 2754748
+
+2753752/2754748 # we include 0.9996384
+
+## What proportion does freshwater salmon production account for? 
+fao_1 <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
+ # filter(environment %in% c("Marine", "Brackishwater")) %>%
+  left_join(aq_groups) %>%
+  dplyr::filter(year == 2017, 
+                Taxon_code %in% c(NA, "F"),
+                aq_group %in% c(NA, "salmonids")) %>%
+  dplyr::filter(aq_group == "salmonids"|str_detect(species, "trout|Trout|salmon|Salmon|char|Char|whitefish")) %>%
+  # dplyr::filter(year == 2017,
+               # !is.na(value)) %>%
+                #!is.na(aq_group)) %>%
+  # dplyr::filter(value < 500) %>%
+  # dplyr::filter(aq_group == "salmonids") %>%
+  group_by(aq_group, country, species, year, environment) %>%
+  summarise(tonnes = sum(value)) %>%
+  ungroup()  %>%
+  # dplyr::filter(tonnes >= 500) %>%
+  group_by(environment) %>%
+  summarise(total_tonnes = sum(tonnes, na.rm = TRUE))# %>%
+ # arrange(aq_group)
+
+fao_1
+
+# A tibble: 3 × 2
+#   environment   total_tonnes
+#   <chr>                <dbl>
+# 1 Brackishwater       28086.
+# 2 Freshwater         676537.
+# 3 Marine            2726662.
+
+2726662 + 28086 # 2754748
+
+676537/2754748 # 0.2455894
 ```

### 2022-01-28 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
updated for resubmission!

@@
 
-Current data is from ASC, only 11 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of China.
+Current data is from ASC and https://zenodo.org/record/3881612, only 11 + 4737 = 4748 farms, so probably not comprehensive, just a drop in the bucket compared to the production of China.
 There are likely many more farms than this.
@@
 
+Fu, Y., Deng, J., Wang, H., Comber, A., Yang, W., Wu, W., You, S., Lin, Y., Wang, K., 2021.
+A new satellite-derived dataset for marine aquaculture areas in China’s coastal region.
+Earth Syst.
+Sci.
+Data 13, 1829–1842.
+https://doi.org/10.5194/essd-13-1829-2021
+
+Fu et al., 2021
+
 ```{r}
@@
 
-write_csv(farms_chn, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
+farms_chn_2 <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_biv_chn.csv") %>%
+  dplyr::select(-id) %>%
+  mutate(data_quality = 2)
+
+farms_chn_fin <- rbind(farms_chn, farms_chn_2)
+
+write_csv(farms_chn_fin, here("marine/bivalve/bivalve_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
 
@@
 
-## USA
-
-Based on the two datasets below, we have an existing 442 bivalve farms. We need to add 761 points to existing 442 (a final total of 1203 points)
+# USA
+
+Based on the two datasets below, we have an existing 1010 bivalve farms. We need to add 193 points to existing 1010 (a final total of 1203 points)
 
 Our current information is taken from many different state level sources, but we are definitely still missing some, as California is not included...
-
- - However, per FAO 2005, there were 1203 saltwater shellfish farms in the USA
+we have farm/lease locations from 8 different states:
+
+ - Alaska
+ - Alabama
+ - Connecticut
+ - Maine
+ - North Carolina
+ - New Hampshire
+ - Rhode Island
+ - Washington
+
+ - However, per FAO 2005, there were 1203 saltwater shellfish farms in the USA.. unclear if this is in marine environments, but it is the best we have. 
   - http://www.fao.org/fishery/countrysector/naso_usa/en
 
+## Maine
+
+ - Viewer: https://www.maine.gov/dmr/aquaculture/leases/aquaculturemap.html
+ - Download: https://dmr-maine.opendata.arcgis.com/datasets/maine::mainedmr-aquaculture-aq-leases/about
+ - I think we will want to use regular leases only.
+ - Limited purpose leases are for scientific or smaller/shorter term mariculture projects, that last up to 3 years.
+ - I think this can be considered "comprehensive". 
+ - Update to date as of 2019.
+ - Has species types specified.
+
+Locations of aquaculture leases in Maine, 2019. . Maine Department of Marine Resources. https://dmr-maine.opendata.arcgis.com/datasets/maine::mainedmr-aquaculture-aq-leases/about
+
+```{r}
+maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))
+
+# mapview(maine_aq_lease)
+
+maine_aq_lease_active <- maine_aq_lease %>%
+  dplyr::filter(STATUS == "A") %>% # 149 leases
+  dplyr::filter(str_detect(PRIMARYSP, "Oyster|Mussel|Clam|mussels|Scallop")) %>%
+  dplyr::filter(!str_detect(PRIMARYSP, "Salmon"))
+
+unique(maine_aq_lease_active$PRIMARYSP)
+
+us_me_bivalve_mol <- st_transform(maine_aq_lease_active, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+us_me_bivalve_pts <- st_centroid(us_me_bivalve_mol)
+# check
+plot(st_geometry(us_me_bivalve_mol))
+plot(st_geometry(st_centroid(us_me_bivalve_mol)), add=TRUE)
+
+us_me_bivalve_pts_latlon <- st_transform(us_me_bivalve_pts, crs = "+init=epsg:4326")
+
+farms_us_me <- data.frame(do.call(rbind, st_geometry(us_me_bivalve_pts_latlon))) # get lat lon
+names(farms_us_me) <- c("lon", "lat") 
+farms_us_me <- farms_us_me %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 4,
+         subregion = "Maine")
+
+mapview(us_me_bivalve_pts_latlon)
+```
+
+## Rhode Island
+
+ - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
+ - Julia Livermore: julia.livermore@dem.ri.gov
+ - Current as of August 2021
+ - Shellfish and kelp
+
+RIDEM Marine Fisheries Maps Approved Aquaculture Areas in Rhode Island, 2021.
+.
+Rhode Island Department of Environmental Management.
+https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
+
+```{r}
+rhode_island <- read_sf("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Rhode_Island/ri_aq_sites.kml")
+
+ri_active_biv <- rhode_island %>%
+  filter(GPS_Source %in% c("Approved", "Expanded", "PD App")) %>%
+  filter(Oysters == "Yes" | Clams == "Yes" | Scallops == "Yes")
+
+us_ri_bivalve_mol <- st_transform(ri_active_biv, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+us_ri_bivalve_pts <- st_centroid(us_ri_bivalve_mol)
+# check
+plot(st_geometry(us_ri_bivalve_mol))
+plot(st_geometry(st_centroid(us_ri_bivalve_mol)), add=TRUE)
+
+us_ri_bivalve_pts_latlon <- st_transform(us_ri_bivalve_pts, crs = "+init=epsg:4326")
+
+mapview(us_ri_bivalve_pts_latlon)
+
+farms_us_ri <- data.frame(do.call(rbind, st_geometry(us_ri_bivalve_pts_latlon))) # get lat lon
+names(farms_us_ri) <- c("lon", "lat") 
+farms_us_ri <- farms_us_ri %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 4,
+         subregion = "Rhode Island")
+
+```
+
+## North Carolina
+
+ - https://deq.nc.gov/about/divisions/marine-fisheries/licenses-permits-and-leases/shellfish-lease-and-franchise#stats-and-figures
+ - Comprehensive for shellfish... just need to figure out how download it. 
+ - I believe Shellfish is pretty much the only mariculture that occurs in NC. 
+ - Has number totals of leases.
+ - Download using protocol described for CT.
+ - Current as of 12/21/2021
+
+North Carolina Division of Marine Fisheries Shellfish Lease and Franchise Program, 2021.
+North Carolina Division of Marine Fisheries.
+https://deq.nc.gov/about/divisions/marine-fisheries/licenses-permits-and-leases/shellfish-lease-and-franchise#stats-and-figures
+
+```{r}
+library(geojsonio)
+spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/North_Carolina/NC_shellfish_leases.geojson",  what = "sp") %>%
+  st_as_sf()
+
+unique(spdf$Status)
+
+nc_active <- spdf %>%
+  filter(Status %in% c("Active", "Approved")) # 423 active leases... wow!
+
+us_nc_bivalve_mol <- st_transform(nc_active, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+us_nc_bivalve_pts <- st_centroid(us_nc_bivalve_mol)
+# check
+plot(st_geometry(us_nc_bivalve_mol))
+plot(st_geometry(st_centroid(us_nc_bivalve_mol)), add=TRUE)
+
+us_nc_bivalve_pts_latlon <- st_transform(us_nc_bivalve_pts, crs = "+init=epsg:4326")
+
+mapview(us_nc_bivalve_pts_latlon)
+
+farms_us_nc <- data.frame(do.call(rbind, st_geometry(us_nc_bivalve_pts_latlon))) # get lat lon
+names(farms_us_nc) <- c("lon", "lat") 
+farms_us_nc <- farms_us_nc %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 4,
+         subregion = "North Carolina")
+
+```
+
+## Alaska
+
+- https://adfg.maps.arcgis.com/apps/webappviewer/index.html?id=f3ca95493c1042b39e42a3ecb5dcad6a
+ - Will be considered "comprehensive". 
+ - Up-to-date as of 2020
+ - Specifies species type
+ - Csvs with lat lons, but have a "corner" dataset, which we could make into polygons. Has area associated with each site. 
+ - Shown in red. 
+ - Has 62 active sites.
+
+Alaska Department of Fish and Game Aquatic Farming Operations, 2020. Alaska Department of Fish and Game. https://adfg.maps.arcgis.com/apps/webappviewer/index.html?id=f3ca95493c1042b39e42a3ecb5dcad6a
+
+```{r}
+alaska_details <- read.csv(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alaska/Active Aquatic Farming Operation Details.csv"))
+
+farms_us_ak <- alaska_details %>%
+  dplyr::select("lat" = "LATITUDE", "lon" = "LONGITUDE") %>%
+  dplyr::mutate(iso3c = "USA", data_quality = 4, subregion = "Alaska")
+
+```
+
+## New Hampshire
+
+ - https://granit.unh.edu/data/search
+ - Comprehensive
+ - Up-to-date as of 2020
+ - Polygons 
+ - 40 sites
+
+NHDES Marine Aquaculture Data, 2020. New Hampshire Department of Environmental Services. https://granit.unh.edu/data
+
+```{r}
+nh_aq <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/New_Hampshire/GRANIT_20211011184728/2020_Aquaculture_Sites.shp")) %>% # 40 sites, assume all active
+  dplyr::filter(Shellfish == "Yes") # 39 sites
+
+us_nh_bivalve_mol <- st_transform(nh_aq, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+us_nh_bivalve_pts <- st_centroid(us_nh_bivalve_mol)
+# check
+plot(st_geometry(us_nh_bivalve_mol))
+plot(st_geometry(st_centroid(us_nh_bivalve_mol)), add=TRUE)
+
+us_nh_bivalve_pts_latlon <- st_transform(us_nh_bivalve_pts, crs = "+init=epsg:4326")
+
+mapview(us_nh_bivalve_pts_latlon)
+
+farms_us_nh <- data.frame(do.call(rbind, st_geometry(us_nh_bivalve_pts_latlon))) # get lat lon
+names(farms_us_nh) <- c("lon", "lat") 
+farms_us_nh <- farms_us_nh %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 4,
+         subregion = "New Hampshire") 
+```
+
+## Connecticut
+
+Map combined with NY, this is what we need (seaweed and shellfish): https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
+
+Current as of 2019
+
+New York and Connecticut’s Shellfish and Seaweed Aquaculture Viewer, 2019.
+New York Department of Environmental Conservation.
+https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
+
+```{r}
+library(geojsonio)
+spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/CT_Aquaculture_gear/CT_aquaculture_gear.geojson",  what = "sp") %>%
+  st_as_sf() %>%
+  filter(Species != "kelp",
+         ActivePerm == "yes")
+
+mapview(spdf)
+
+us_ct_bivalve_mol <- st_transform(spdf, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+us_ct_bivalve_pts <- st_centroid(us_ct_bivalve_mol)
+# check
+plot(st_geometry(us_ct_bivalve_mol))
+plot(st_geometry(st_centroid(us_ct_bivalve_mol)), add=TRUE)
+
+us_ct_bivalve_pts_latlon <- st_transform(us_ct_bivalve_pts, crs = "+init=epsg:4326")
+
+mapview(us_ct_bivalve_pts_latlon)
+
+farms_us_ct <- data.frame(do.call(rbind, st_geometry(us_ct_bivalve_pts_latlon))) # get lat lon
+names(farms_us_ct) <- c("lon", "lat") 
+farms_us_ct <- farms_us_ct %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 4,
+         subregion = "Connecticut") 
+```
+
+## Alabama
+
+ - Here is a map with Shellfish leases!: https://aldcnr.maps.arcgis.com/apps/webappviewer/index.html?id=a32dad8dacd249ea86bcb80dd951a424
+
+Alabama Marine Resources Division: Shellfish Aquaculture Siting Tool, 2021.
+Alabama Marine Resources Division.
+https://aldcnr.maps.arcgis.com/apps/webappviewer/index.html?id=a32dad8dacd249ea86bcb80dd951a424
+
+```{r}
+library(geojsonio)
+spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alabama/Alabama_Shellfish_Leases.geojson",  what = "sp") %>%
+  st_as_sf() %>%
+  dplyr::filter(Status %in% c("Current", "Current Commercial"))
+
+mapview(spdf)
+
+us_al_bivalve_mol <- st_transform(spdf, crs = "+init=epsg:3035") # convert to equal area projealion to find centroids. 
+us_al_bivalve_pts <- st_centroid(us_al_bivalve_mol)
+# check
+plot(st_geometry(us_al_bivalve_mol))
+plot(st_geometry(st_centroid(us_al_bivalve_mol)), add=TRUE)
+
+us_al_bivalve_pts_latlon <- st_transform(us_al_bivalve_pts, crs = "+init=epsg:4326")
+
+mapview(us_al_bivalve_pts_latlon)
+
+farms_us_al <- data.frame(do.call(rbind, st_geometry(us_al_bivalve_pts_latlon))) # get lat lon
+names(farms_us_al) <- c("lon", "lat") 
+farms_us_al <- farms_us_al %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 4,
+         subregion = "Alabama") 
+```
+
 ## US Northeast - NY, CT, ME, NH
+
+ Only used this for exploration
  - Regional Ocean Council 2018
@@
 
-us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))
-
-unique(us_ne$allSpecies)
-
-unique(fao_bivalve_spp$species)
-
-## need to filter allSpecies for anything with "Oyster", "Mussel", "Shellfish", "Clam", "Quahog",
-
-# id bivalves and active sites
-bivalve_species <- grep("Oyster|Mussel|Shellfish|Clam|Quahog", unique(us_ne$allSpecies), value=TRUE)
-
-us_ne_bivalve <- us_ne %>%
-  filter(allSpecies %in% bivalve_species) %>%
-  filter(status == "Active")
-unique(us_ne_bivalve$state)
-
-us_ne_bivalve_mol <- st_transform(us_ne_bivalve, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
-us_ne_bivalve_pts <- st_centroid(us_ne_bivalve_mol)
-# check
-plot(st_geometry(us_ne_bivalve_mol))
-plot(st_geometry(st_centroid(us_ne_bivalve_mol)), add=TRUE)
-
-us_ne_bivalve_pts_latlon <- st_transform(us_ne_bivalve_pts, crs = "+init=epsg:4326")
-
-farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
-names(farms_us_ne) <- c("lon", "lat") 
-farms_us_ne <- farms_us_ne %>%
-  mutate(iso3c = "USA") %>%
-  mutate(data_quality = 4)
-
-# all_farms_sf <- st_as_sf(farms_us_ne, coords = c("lon", "lat"), 
-#                          crs = crs(gadm_latlon), agr = "constant")
+# us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))
 # 
-# mapview(all_farms_sf)
-
-```
-
-## USA - WA, RI 
+# unique(us_ne$allSpecies)
+# 
+# unique(fao_bivalve_spp$species)
+# 
+# ## need to filter allSpecies for anything with "Oyster", "Mussel", "Shellfish", "Clam", "Quahog", 
+# 
+# # id bivalves and active sites
+# bivalve_species <- grep("Oyster|Mussel|Shellfish|Clam|Quahog", unique(us_ne$allSpecies), value=TRUE)
+# 
+# 
+# us_ne_bivalve <- us_ne %>%
+#   filter(allSpecies %in% bivalve_species) %>%
+#   filter(status == "Active")
+# unique(us_ne_bivalve$state)
+# 
+# us_ne_bivalve_mol <- st_transform(us_ne_bivalve, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+# us_ne_bivalve_pts <- st_centroid(us_ne_bivalve_mol)
+# # check
+# plot(st_geometry(us_ne_bivalve_mol))
+# plot(st_geometry(st_centroid(us_ne_bivalve_mol)), add=TRUE)
+# 
+# us_ne_bivalve_pts_latlon <- st_transform(us_ne_bivalve_pts, crs = "+init=epsg:4326") 
+# 
+# farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
+# names(farms_us_ne) <- c("lon", "lat") 
+# farms_us_ne <- farms_us_ne %>%
+#   mutate(iso3c = "USA") %>%
+#   mutate(data_quality = 4) 
+# 
+# # all_farms_sf <- st_as_sf(farms_us_ne, coords = c("lon", "lat"), 
+# #                          crs = crs(gadm_latlon), agr = "constant")
+# # 
+# # mapview(all_farms_sf)
+
+```
+
+## Washington
  - Aquaculture, Office for Coastal Management (OCM), 2018
+ - This dataset has shellfish farms for Washington and Rhode Island, we will use the Washington farms
 
@@
   dplyr::filter(!(status %in% c(NA, "Pending", "Restricted-Relay", "Not Available", "Conditional Closure", "Prohibited"))) %>%
-dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York"))) ## filter out the states we already have
+dplyr::filter(!(state %in% c("Maine", "Connecticut", "New York", "North Carolina", "Alabama", "New Hampshire", "Alaska", "Rhode Island"))) ## filter out the states we already have
 
@@
 
+mapview(us_aqua_bivalve_pts_latlon)
+
 farms_us_aqua <- data.frame(do.call(rbind, st_geometry(us_aqua_bivalve_pts_latlon))) 
@@
 farms_us_aqua <- farms_us_aqua %>%
-  mutate(iso3c = "USA") %>%
+  mutate(iso3c = "USA", subregion = "Washington") %>%
   mutate(data_quality = 4)
-
-farms_usa_total <- rbind(farms_us_ne, farms_us_aqua)
+```
+
+## Combine all USA data
+
+```{r}
+farms_usa_total <- rbind(farms_us_aqua, farms_us_ak, farms_us_al, farms_us_ct, farms_us_me, farms_us_nc, farms_us_nh, farms_us_ri)
 
@@
 
-usa_additional <- data.frame(iso3c = "USA", type = "bivalve", num_additional_farms = 761 , data_quality = 4, total_farms = 1203)
+usa_additional <- data.frame(iso3c = "USA", type = "bivalve", num_additional_farms = 193 , data_quality = 4, total_farms = 1203)
 write.csv(usa_additional, here("marine/bivalve/bivalve_farms/data/subset_known_add_points_4/add_farms_usa.csv"), row.names = FALSE)
@@
   summarise(n())
+
+```
+
+## UK; Scotland
+ - sticking with emodnet for this, since it is comprehensive for the entire country (UK), even if a year behind the scottish gov reporting.
+
+```{r}
+farms_eu_UK <- eu_fao_countries %>%
+  filter(COUNTRY == "United Kingdom") # 358.. but only 259 listed as active. Lets compare to the data from scottish gov.  
+mapview(farms_eu_UK)
+
+farms_uk <- farms_eu_final %>%
+  filter()
+
+## load in data and select active sites, "Seawater" and "Seawater and Freshwater sites", and any sites that contain "Salmon" "Arctic Char" or "Rainbow Trout"
+
+scotland_csv <- as.data.frame(read_csv(file.path(path, "Scotland/Scotland_site_details_2021_raw.csv")))
+
+# Subset to salmonidae farms
+sub_scotland <- scotland_csv %>% 
+  dplyr::select(ID = `Marine Scotland Site ID`, Easting, Northing, `Producing in Last 3 Years`, `Aquaculture Type`, `Water Type`, Species, subregion = `Local Authority` ) %>% 
+  filter(`Producing in Last 3 Years` == c("Yes", "New"),
+         `Water Type` %in% c("Seawater", "Freshwater and Seawater"),
+         str_detect(Species, "mussel|scallop|Oyster|oyster|urchin|Urchin|Scallop|clam|Clam")) # Only 164 reporting actgive here...
+however, emodnet reports sites not in scotland and in other places in the uk...
+so i think we should stick with that actually...
+especially since they grab their data from the same source..
+even if outdated.
 

### 2022-01-28 marine/bivalve/bivalve_farms/STEP3_gapfill_biv.Rmd
updated for resubmission!

@@
 
-write.csv(tonnes_per_farm, "output/bivalve_comp_tonnes_per_farm.csv", row.names = FALSE)
+write.csv(tonnes_per_farm, "marine/bivalve/bivalve_farms/output/bivalve_comp_tonnes_per_farm.csv", row.names = FALSE)
 
 avg_global_bivalve_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
-avg_global_bivalve_tonnes_per_farm # 283.4135
+avg_global_bivalve_tonnes_per_farm # 283.4135 v1; 283.4135 v2
 

### 2022-01-28 marine/china_data.Rmd
updated for resubmission!

---
title: "Location of Salmon Farms"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

In this script we need to allocate the appropriate number of farms per species group from this Chinese dataset: https://zenodo.org/record/3881612

In this dataset they split the aquaculture groups into "MAC" (Marine Animal Culture) and "MPC" (Marine Plant Culture). Because we exclude plant culture in our project, we can ignore this. For the MAC points, we need to allocate the appropriate number of farms to each species group which has reported production in China.

To do this, I will calculate percentages of production per each species group in China, and apply those percentages to allocate number of farms from this dataset. So for example, if Bivalves make up 90% of production in China, and there are 100 farms in this dataset, Bivalves will be allocated 90 of those farms, randomly.

We will write each dataset to Aurora, and read them in when prepping each species group farm points in each species group folder (i.e. the "shrimp/" folder or the "bivalve/" folder).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(stringr)
library(rgdal)
library(PBSmapping)
library(maptools)
library(sf)
library(lwgeom)
library(data.table)
library(here)
library(mapview)

path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"

```

# Raster

Standard raster used for this analysis

```{r}

source(here("_spatial/template_raster.R"))

```

# Global regions

```{r}

gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- projectRaster(gadm, food_raster)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

```{r}

gadm_df <- tabularaster::as_tibble(gadm_latlon, value = TRUE, cells = TRUE) %>% 
  mutate(cellvalue = round(cellvalue, 0))

gadm_reg <- dplyr::left_join(gadm_df, gadm_codes, by = c("cellvalue" = "reg_id"))

```

```{r}
china <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/Marine aquaculture areas in the China’s coastal region.shp")

# MPC = marine plant culture
# MAC = marine animal culture

MAC <- china %>%
  filter(Class == "MAC") # 5724 points.. better than what we have... how do we split it into our species classes? By %s of production/farms randomly?

plot(MAC)

MAC_fix <- MAC %>%
  st_zm(drop = TRUE)

# MAC_fix$geometry <- sf_use_s2(MAC_fix$geometry, use_s2 = FALSE)

summary(MAC_fix)

mapview(MAC_fix)

## Read in production data for China

prod <- read.csv("marine/STEP1_species_groups/int/tonnes_per_country_group.csv") %>%
  filter(country == "China") %>%
  mutate(prop = total_tonnes/sum(total_tonnes))

chn_pts <- st_centroid(st_make_valid(MAC_fix))

chn_pts_latlon <- st_transform(chn_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

plot(chn_pts_latlon)
mapview(chn_pts_latlon)

farms_chn <- data.frame(do.call(rbind, st_geometry(chn_pts_latlon)))
names(farms_chn) <- c("lon", "lat")

farms_all_chn <- farms_chn %>%
  cbind(iso3c = "CHN") %>%
  mutate(id = 1:5724)

## We need 0.82762193*5724 = 4737 rows for Bivalves

farms_biv_chn <-  farms_all_chn %>%
  slice_sample(prop = 0.82762193)

## We need 0.01616285*5724 = 93 rows for crustaceans

farms_crust_chn <- farms_all_chn %>%
  dplyr::filter(!(id %in% c(farms_biv_chn$id))) %>%
  slice_sample(n = 93)

## We need 0.08020417*5724 = 459 rows for marine fish general

farms_mfg_chn <- farms_all_chn %>%
  dplyr::filter(!(id %in% c(farms_biv_chn$id, farms_crust_chn$id))) %>%
  slice_sample(n = 459)

## We need 0.07601105*5724 =  435 rows for shrimp

farms_shrimp_chn <- farms_all_chn %>%
  dplyr::filter(!(id %in% c(farms_biv_chn$id, farms_crust_chn$id, farms_mfg_chn$id))) %>%
  slice_sample(n = 435)

435 + 459 + 93 + 4737 # perfect

write.csv(farms_shrimp_chn, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_shrimp_chn.csv", row.names = FALSE)

write.csv(farms_mfg_chn, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_mfg_chn.csv", row.names = FALSE)

write.csv(farms_biv_chn, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_biv_chn.csv", row.names = FALSE)

write.csv(farms_crust_chn, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_crust_chn.csv", row.names = FALSE)

## Now lets take a look at each of them

check <- st_as_sf(farms_biv_chn, coords = c("lon", "lat"), 
                         crs = crs(gadm_latlon), agr = "constant")

mapview(check)

```

### 2022-01-28 marine/compile_data_for_placement.Rmd
wrote READMEs and cleaned up organization
updated for resubmission!

--- 2021-03-23 marine/LAST_STEP_compile_data.Rmd
@@
 
-# crustacean_farms <- read_csv(here("marine/crustaceans/crustacean_farms/output/all_known_crustacean_farms_final.csv")) ## there are none
+crustacean_farms <- read_csv(here("marine/crustaceans/crustaceans_farms/output/all_known_crustaceans_farms_final.csv")) ## there are none
 
@@
 
-salmon_farms <-  read_csv(here("marine/salmon/salmon_farm/output/all_known_salmon_farms_final.csv")) %>%
+salmon_farms <-  read_csv(here("marine/salmon/salmon_farms/output/all_known_salmon_farms_final.csv")) %>%
   dplyr::select(-subregion)
@@
 
-all_farms <- rbind(bivalve_farms, finfish_farms, shrimp_farms, tuna_farms, salmon_farms)
+all_farms <- rbind(bivalve_farms, finfish_farms, shrimp_farms, tuna_farms, salmon_farms, crustacean_farms)
 
@@
 
-crustacean_farms_add <- read_csv(here("marine/crustaceans/crustacean_farms/output/crustaceans_points_to_add_final.csv"))
+crustacean_farms_add <- read_csv(here("marine/crustaceans/crustaceans_farms/output/crustaceans_points_to_add_final.csv"))
 
@@
 
-salmon_farms_add <-  read_csv(here("marine/salmon/salmon_farm/output/salmon_points_to_add_final.csv"))
+salmon_farms_add <-  read_csv(here("marine/salmon/salmon_farms/output/salmon_points_to_add_final.csv"))
 
@@
 ```
+
+```{r}
+countries_1 <- data.frame(iso3c = unique(all_farms$iso3c))
+
+countries_2 <- data.frame(iso3c = unique(all_point_additions$iso3c))
+
+all_countries <- rbind(countries_1, countries_2)
+
+length(unique(all_countries$iso3c)) # 73 total countries mapped 
+```

### 2022-01-28 marine/crustaceans/crustaceans_farms/STEP2_crustacean_farm_locations.Rmd
updated for resubmission!

@@
 
-Can't find any datasets of marine crustacean farm locations in China. This will be fully gapfilled. data_quality = 1
-
-Source: 
-NA
+Current data is from https://zenodo.org/record/3881612, only 93 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of China.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
 
 ```{r}
-chn_gf <- data.frame(iso3c = "CHN", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
-write_csv(chn_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_chn.csv")) 
+# chn_gf <- data.frame(iso3c = "CHN", type = "crustaceans", num_additional_farms = NA, data_quality = 1)
+# write_csv(chn_gf, here("marine/crustaceans/crustacean_farms/data/no_info_1/gf_chn.csv"))
+
+farms_chn <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_crust_chn.csv") %>%
+  dplyr::select(-id) %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_chn, here("marine/crustaceans/crustaceans_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
+
 ```

### 2022-01-28 marine/crustaceans/crustaceans_farms/STEP3_gapfill_crustaceans.Rmd
updated for resubmission!

@@
 
-no_info_files <- list.files(here("marine/crustaceans/crustacean_farms/data/no_info_1"), full=TRUE)
+no_info_files <- list.files(here("marine/crustaceans/crustaceans_farms/data/no_info_1"), full=TRUE)
 no_info_1 = plyr::ldply(no_info_files, read_csv)
+
+farm_files <- list.files(here("marine/crustaceans/crustaceans_farms/data/known_farm_sites_2_4_5"), full=TRUE)
+all_known_farms = plyr::ldply(farm_files, read_csv) %>%
+  mutate(type = "crustaceans")
+
+subset_gapfill_2 <- all_known_farms %>%
+  filter(data_quality == 2)
 
@@
 ```{r}
-crustaceans_tonnes <- read_csv(here::here("marine/crustaceans/crustacean_farms/data/fao_mariculture_crustaceans.csv")) %>%
+crustaceans_tonnes <- read_csv(here::here("marine/crustaceans/crustaceans_farms/data/fao_mariculture_crustaceans.csv")) %>%
   mutate(type = "crustaceans") %>%
@@
 
+Gapfill CHN (data quality = 2)
+
+```{r}
+## start with the subset of locations that need gapfilling based on tonnes/farm
+gapfill_2 <- subset_gapfill_2 %>%
+  group_by(iso3c, type) %>%
+  summarise(n_existing_farms = n()) %>%
+  ungroup() %>%
+  left_join(crustaceans_tonnes) %>%
+  mutate(avg_tonnes_per_farm = avg_global_shrimp_tonnes_per_farm) %>%
+  mutate(tonnes_accounted_for = avg_tonnes_per_farm*n_existing_farms) %>%
+  mutate(tonnes_remaining = fao_tonnes_production - tonnes_accounted_for) %>%
+  mutate(tonnes_remaining = ifelse(tonnes_remaining <= 0, 0, tonnes_remaining)) %>%
+  mutate(num_additional_farms = ceiling(tonnes_remaining/avg_tonnes_per_farm)) %>%
+  dplyr::select(iso3c, type, num_additional_farms, avg_tonnes_per_farm) %>%
+  mutate(estimated = 1) %>%
+  filter(num_additional_farms != 0)
+
+number_additional_points <- 
+  rbind(gapfill_1, gapfill_2)
+
+```
+
 ```{r}
@@
 
-write.csv(gapfill_1, here("marine/crustaceans/crustacean_farms/output/crustaceans_points_to_add_final.csv"), row.names = FALSE)
+write.csv(number_additional_points, here("marine/crustaceans/crustaceans_farms/output/crustaceans_points_to_add_final.csv"), row.names = FALSE)
+
+all_known_farms_final <- all_known_farms %>%
+  dplyr::select(-data_quality)
+
+write.csv(all_known_farms_final, here("marine/crustaceans/crustaceans_farms/output/all_known_crustaceans_farms_final.csv"), row.names = FALSE)
 ```
@@
 
-test_2 <- gapfill_1 %>%
+test_2 <- number_additional_points %>%
   dplyr::select(iso3c)

### 2022-01-28 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
updated for resubmission!

@@
 # CHN:PRK
-# DEU:NLD
+# CHN:TWN
+# CHN:VNM
 # HKG:CHN
 # IRL:GBR
-# MYS:BRN
+# KHM:VNM
 # NLD:DEU
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "DEU:NLD", "DEU", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "DEU:NLD", "Germany", NAME_0)) %>%    
+      mutate(GID_0 = ifelse(check %in% "CHN:TWN", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:TWN", "China", NAME_0)) %>%
+      mutate(GID_0 = ifelse(check %in% "CHN:VNM", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:VNM", "China", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
-    mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%  
+    mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
@@
 
-cellStats(bivalve_raster, stat = "sum") # 17435623
-sum(bivalve_raster_df$tonnes_production) # 17435623
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17435623
-sum(fao$fao_tonnes_production) # 17435623
+cellStats(bivalve_raster, stat = "sum") # 17436803
+sum(bivalve_raster_df$tonnes_production) # 17436803
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17436803
+sum(fao$fao_tonnes_production) # 17435623 - slightly off?
 

### 2022-01-28 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
updated for resubmission!

@@
 
-sum(farms_sf$tonnes_per_farm) # 401719.1
+sum(farms_sf$tonnes_per_farm) # 402573.6
 sum(fao$fao_tonnes_production) # 401719.1
@@
 # plot(s)
-cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 401719.1
+cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 402573.6
 
@@
 
-cellStats(crustacean_raster, stat = "sum") # 401719.1
-sum(crustacean_raster_df$tonnes_production) # 401719.1
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 401719.1
+cellStats(crustacean_raster, stat = "sum") # 402573.6
+sum(crustacean_raster_df$tonnes_production) # 402573.6
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 402573.6
 sum(fao$fao_tonnes_production) # 401719.1

### 2022-01-28 marine/last_step_rasterize/finfish_rasterize_production.Rmd
updated for resubmission!

@@
 # CHN:PRK
+# CHN:TWN
 # CYP:XAD
@@
 # IDN:MYS
-# MYS:BRN
 # MYS:SGP
 # SGP:MYS
-# TWN:CHN
 
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
+    mutate(GID_0 = ifelse(check %in% "CHN:TWN", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:TWN", "China", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>% 
-  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
   mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
@@
   mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
-  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0))
 
@@
 
-mapview(farms_sf_correct) # this all looks reasonable, no crazy points
 ```
@@
 
-cellStats(finfish_raster, stat = "sum") # 3901214
-sum(finfish_raster_df$tonnes_production) # 3901214
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3901214
+cellStats(finfish_raster, stat = "sum") # 3909255
+sum(finfish_raster_df$tonnes_production) # 3909255
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3909255
 sum(fao$fao_tonnes_production) #3901214

### 2022-01-28 marine/last_step_rasterize/salmon_rasterize_production.Rmd
updated for resubmission!

@@
 # FIN:RUS
+# TUR:GRC
 # USA:CAN
@@
   mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))
+  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))  %>%
+    mutate(GID_0 = ifelse(check %in% "TUR:GRC", "TUR", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0))
 
@@
 
-cellStats(salmon_raster, stat = "sum") # 2753752
-sum(salmon_raster_df$tonnes_production) # 2753752
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2753752
+cellStats(salmon_raster, stat = "sum") # 2756155
+sum(salmon_raster_df$tonnes_production) # 2756155
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2756155
 sum(fao$fao_tonnes_production) #2753752

### 2022-01-28 marine/last_step_rasterize/shrimp_rasterize_production.Rmd
updated for resubmission!

@@
 # CHN:HKG
-# CHN:MAC
 # CHN:PRK
+# CHN:VNM
 # CRI:PAN
@@
 # HND:SLV
+# IDN:MYS 
 # IRN:IRQ
+# KHM:VNM 
 # MEX:USA
@@
 # SLV:GTM
-# TWN:CHN
+# THA:MYS -
 
@@
   mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
+  mutate(GID_0 = ifelse(check %in% "CHN:VNM", "CHN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "CHN:VNM", "China", NAME_0)) %>%
   mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
+    mutate(GID_0 = ifelse(check %in% "IDN:MYS", "IDN", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>%  
+      mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%  
   mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
@@
   mutate(NAME_0 = ifelse(check %in% "SLV:GTM", "El Salvador", NAME_0)) %>%
-  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
-  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))
+  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
+  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0))
 
@@
 
-cellStats(shrimp_raster, stat = "sum") # 5094133
-sum(shrimp_raster_df$tonnes_production) # 5094133
-sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5094133
-sum(fao$fao_tonnes_production) # 5094133
+cellStats(shrimp_raster, stat = "sum") # 5097823
+sum(shrimp_raster_df$tonnes_production) # 5097823
+sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5097823
+sum(fao$fao_tonnes_production) # 5094133 - a bit off bc of rounding with our model
 

### 2022-01-28 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
updated figs and stats with newly run farms
updated for resubmission!

@@
   dplyr::filter(aq_grop == "marine_fish_general")
+mapview(ASC_finfish)
 
@@
 ## China
-Can't find any datasets of marine finfish farm locations in China. This will need to be fully gapfilled.
-
-Source: 
-NA
-
-```{r}
-chn_gf <- data.frame(iso3c = "CHN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
-write_csv(chn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_chn.csv"))
+
+Current data is from https://zenodo.org/record/3881612 only 459 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of China.
+There are likely many more farms than this.
+Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm.
+For now we need to mark the data quality as 2.
+
+```{r}
+# chn_gf <- data.frame(iso3c = "CHN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
+# write_csv(chn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_chn.csv"))
+
+farms_chn <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_mfg_chn.csv") %>%
+  dplyr::select(-id) %>%
+  mutate(data_quality = 2)
+
+write_csv(farms_chn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
 

### 2022-01-28 marine/salmon/salmon_farms/STEP2_salmon_farm_locations.Rmd
made the figures!
updated for resubmission!

--- 2021-03-23 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
@@
 path <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations"
-fao_salmon <- read_csv("marine/salmon/salmon_farm/data/fao_mariculture_salmon.csv") %>%
+fao_salmon <- read_csv("marine/salmon/salmon_farms/data/fao_mariculture_salmon.csv") %>%
      dplyr::filter(year == 2017)
@@
 http://aquaculture.scotland.gov.uk/
+
+To download:
+
+http://aquaculture.scotland.gov.uk/data/site_details.aspx
+
+Click "CSV export"
+
 ```{r}
-## get scotland data: http://aquaculture.scotland.gov.uk/
-# Load in data and select sites that have been producing in the last 3 years
 
-#### TODO #### This could probably be improved by setting up a way to webscrape these data... not sure how this was compiled previously.
+## load in data and select active sites, "Seawater" and "Seawater and Freshwater sites", and any sites that contain "Salmon" "Arctic Char" or "Rainbow Trout"
 
-scotland_csv <- as.data.frame(read_csv(file.path(path, "Scotland/Scotland_site_details.csv")))
+scotland_csv <- as.data.frame(read_csv(file.path(path, "Scotland/Scotland_site_details_2021_raw.csv")))
 
-# Subset to salmon farms
+unique(scotland_csv$Species)
+
+# Subset to salmonidae farms
 sub_scotland <- scotland_csv %>% 
   dplyr::select(ID = `Marine Scotland Site ID`, Easting, Northing, `Producing in Last 3 Years`, `Aquaculture Type`, `Water Type`, Species, subregion = `Local Authority` ) %>% 
-  filter(`Producing in Last 3 Years` == c("Yes", "New"),
+  filter(`Producing in Last 3 Years` %in% c("Yes", "New"),
          `Water Type` %in% c("Seawater", "Freshwater and Seawater"),
-         grepl("Salmon", Species))
+         str_detect(Species, "Salmon|Trout"))
+
+unique(sub_scotland$Species)
+
+## While there are >350 sites in the data which are deemed to have produced Salmonidae species, only 110 of them have operated in the past 3 years, which is what we include in our map.
 
@@
 
-write_csv(farms_scotland, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_scotland.csv"))
+write_csv(farms_scotland, here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5/farms_scotland.csv"))
 
@@
   dplyr::select(lon, lat, iso3c) %>%
-  mutate(data_quality = 2)
+  mutate(data_quality = 2) %>%
+  mutate(subregion = "Washington")
 
-write_csv(farms_ps, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ps_usa.csv"))
+write_csv(farms_ps, here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5/farms_ps_usa.csv"))
 
@@
 ## US Northeast
+DEPRECATED:
 Source:
-Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 17, 2020] https://www.northeastoceandata.org/data-download/
+Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 17, 2020]
 
@@
 
-us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))
-
-# id salmon and active sites
-salmon_species <- grep("Salmon|salmon", unique(us_ne$allSpecies), value=TRUE)
-
-us_ne_salmon <- us_ne %>%
-  filter(allSpecies %in% salmon_species) %>%
-  filter(status == "Active")
-
-us_ne_salmon_mol <- st_transform(us_ne_salmon, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
-us_ne_salmon_pts <- st_centroid(us_ne_salmon_mol)
-# check
-plot(st_geometry(us_ne_salmon_mol))
-plot(st_geometry(st_centroid(us_ne_salmon_mol)), add=TRUE)
-
-us_ne_salmon_pts_latlon <- st_transform(us_ne_salmon_pts, crs = "+init=epsg:4326")
-
-farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon))) 
-names(farms_us_ne) <- c("lon", "lat")
-farms_us_ne <- farms_us_ne %>%
-  mutate(iso3c = "USA") %>%
-  mutate(data_quality = 2)
-
-write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ne_usa.csv"))
+# us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))
+# 
+# 
+# # id salmon and active sites
+# salmon_species <- grep("Salmon|salmon", unique(us_ne$allSpecies), value=TRUE)
+# 
+# us_ne_salmon <- us_ne %>%
+#   filter(allSpecies %in% salmon_species) %>%
+#   filter(status == "Active")
+# 
+# us_ne_salmon_mol <- st_transform(us_ne_salmon, crs = "+init=epsg:3035") # convert to equal area projection to find centroids.
+# us_ne_salmon_pts <- st_centroid(us_ne_salmon_mol)
+# # check
+# plot(st_geometry(us_ne_salmon_mol))
+# plot(st_geometry(st_centroid(us_ne_salmon_mol)), add=TRUE)
+# 
+# us_ne_salmon_pts_latlon <- st_transform(us_ne_salmon_pts, crs = "+init=epsg:4326")
+# 
+# farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon)))
+# names(farms_us_ne) <- c("lon", "lat")
+# farms_us_ne <- farms_us_ne %>%
+#   mutate(iso3c = "USA") %>%
+#   mutate(data_quality = 2)
+# 
+# write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ne_usa.csv"))
 
@@
 
+# United States
+
+## Maine
+
+Locations of aquaculture leases in Maine, 2019. Maine Department of Marine Resources. https://dmr-maine.opendata.arcgis.com/datasets/maine::mainedmr-aquaculture-aq-leases/about
+
+```{r}
+maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))
+
+# mapview(maine_aq_lease)
+
+maine_aq_lease_active <- maine_aq_lease %>%
+  dplyr::filter(STATUS == "A") %>% # 149 leases
+  dplyr::filter(str_detect(PRIMARYSP, "Salmon")) # 22 leases.. matches the northeast data
+
+us_me_salmon_mol <- st_transform(maine_aq_lease_active, crs = "+init=epsg:3035") # convert to equal area projection to find centroids.
+us_me_salmon_pts <- st_centroid(us_me_salmon_mol)
+# check
+plot(st_geometry(us_me_salmon_mol))
+plot(st_geometry(st_centroid(us_me_salmon_mol)), add=TRUE)
+
+us_me_salmon_pts_latlon <- st_transform(us_me_salmon_pts, crs = "+init=epsg:4326")
+
+farms_us_me <- data.frame(do.call(rbind, st_geometry(us_me_salmon_pts_latlon)))
+names(farms_us_me) <- c("lon", "lat")
+farms_us_me <- farms_us_me %>%
+  mutate(iso3c = "USA") %>%
+  mutate(data_quality = 2) %>%
+  mutate(subregion = "Maine")
+
+write_csv(farms_us_me, here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5/farms_maine_usa.csv"))
+
+```
+
 # Join cell count dataframes
@@
 
-farm_files <- list.files(here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5"), full=TRUE)
+farm_files <- list.files(here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5"), full=TRUE)
 all_farms = plyr::ldply(farm_files, read_csv)
@@
 
-write.csv(all_farms_1, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)
+write.csv(all_farms_1, here("marine/salmon/salmon_farms/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)
 
-write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), row.names = FALSE)
+write.csv(all_farms, here("marine/salmon/salmon_farms/data/global_salmon_farm_lat_lon_quality.csv"), row.names = FALSE)
 

### 2022-01-28 marine/salmon/salmon_farms/STEP3_gapfill_salmon.Rmd
updated for resubmission!

@@
 
-write.csv(tonnes_per_farm, "output/salmon_comp_tonnes_per_farm.csv", row.names = FALSE)
+write.csv(tonnes_per_farm, "marine/salmon/salmon_farms/output/salmon_comp_tonnes_per_farm.csv", row.names = FALSE)
 
 avg_global_salmon_tonnes_per_farm = mean(tonnes_per_farm$tonnes_per_farm)
-avg_global_salmon_tonnes_per_farm # 927.156
+avg_global_salmon_tonnes_per_farm # 927.156 v1; 938.2249 v2 ; 866.4024 v3 after scotland correction
 
 med_global_salmon_tonnes_per_farm = median(tonnes_per_farm$tonnes_per_farm)
-med_global_salmon_tonnes_per_farm # 520.5484
+med_global_salmon_tonnes_per_farm # 520.5484 v1; 520.5484 v2 ; 520.5484 v3
 ```
@@
 
-write.csv(number_additional_points, here("marine/salmon/salmon_farm/output/salmon_points_to_add_final.csv"), row.names = FALSE)
+write.csv(number_additional_points, here("marine/salmon/salmon_farms/output/salmon_points_to_add_final.csv"), row.names = FALSE)
 ```
@@
 
-write.csv(all_known_farms_final, here("marine/salmon/salmon_farm/output/all_known_salmon_farms_final.csv"), row.names = FALSE)
+write.csv(all_known_farms_final, here("marine/salmon/salmon_farms/output/all_known_salmon_farms_final.csv"), row.names = FALSE)
 ```

### 2022-01-28 marine/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
updated figs and stats with newly run farms
updated for resubmission!

@@
 # Indonesia 
-Current data is from ASC, only 5 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Indonesia.
+Current data is from ASC, only 5 farms, so probably not comprehensive, just a drop in the bucket compared to the production of Indonesia.
 There are likely many more farms than this.
@@
 
-Current data is from ASC, only 4 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of China.
+Current data is from https://zenodo.org/record/3881612 and ASC, only 435 + 4 = 439 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of China.
 There are likely many more farms than this.
@@
 
-write_csv(farms_chn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
+farms_chn_2 <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_shrimp_chn.csv") %>%
+  dplyr::select(-id) %>%
+  mutate(data_quality = 2)
+
+farms_chn_fin <- rbind(farms_chn, farms_chn_2)
+
+write_csv(farms_chn_fin, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
 

### 2022-01-28 marine/united_states/US_mapping.Rmd
updated for resubmission!

@@
 
-**There is comprehensive downloadable data for 5 states: **
+**There is comprehensive downloadable data for 7 states: **
 
- - Maine, Alaska, New Hampshire, New York(?), Connecticut(?)
+ - Maine, Alaska, New Hampshire, Connecticut, North Carolina, Rhode Island, Alabama
 
-**There are publicly available map viewers (leases or farm locations) which seem to be comprehensive, but are NOT downloadable for 4 states:**
+**There are publicly available map viewers (leases or farm locations) which seem to be comprehensive, but are NOT downloadable for 1 state:**
 
- - Alabama, North Carolina, Virginia, Rhode Island
+ - Virginia
 
-**There is general info on lease holders, what they farm, and what municipality or city they are in for 7 states:**
+**There is general info on lease holders, what they farm, and what municipality or city they are in for 6 states:**
 
@@
  - Oregon: map of places were commercial harvest/growing is allowed
- - Maryland: Have INDIVIDUAL pdf maps of all lease applications and if they were accepted or not...
  - New Jersey: Have pdf maps of all existing shellfish leases and those issued in 2020
@@
 
-**Subset of farms downloadable for 1 state:**
+**Subset of farms or outdated downloadable for 2 states:**
 
  - Florida: A map of mariculture farms which are at risk of oil spills
+ - Maryland: Have INDIVIDUAL pdf maps of all lease applications and if they were accepted or not... And was able to download lease data from 2013.
 
@@
 
- - Delaware: Commercial harvest is illegal
+ - Delaware: Commercial harvest is illegal; apparently one farm but not production (Halley)
  - Georgia: From what I could tell, oyster farming was illegal here as recent as 2020
+ - New York: No production (Halley)
 
@@
 
- - https://www.maine.gov/dmr/aquaculture/leases/aquaculturemap.html
- - I think we will want to use both "limited purpose" and regular leases.
+ - Viewer: https://www.maine.gov/dmr/aquaculture/leases/aquaculturemap.html
+ - Download: https://dmr-maine.opendata.arcgis.com/datasets/maine::mainedmr-aquaculture-aq-leases/about
+ - I think we will want to use regular leases only.
  - Limited purpose leases are for scientific or smaller/shorter term mariculture projects, that last up to 3 years.
  - I think this can be considered "comprehensive". 
- - Update to date as of September 2021.
+ - Update to date as of 2019.
  - Has species types specified.
- - Red polygons for the leases. Blue points for the limited purpose. Limited purpose has length and width measurements, so regardless we will have area for both if needed.
 
@@
 
+## leave out limited purpose 
 ```
@@
 
-Shellfish bed managed
-
- - https://portal.ct.gov/DOAG/Aquaculture1/Aquaculture/Shellfish-Area-Classifications--Maps
- - Only Shellfish
- - Polygons 
- - I believe that these are large areas that have been **approved** for shellfish aquaculture, but not the exact locations of the aquaculture. So this probably isn't helpful.
-
 From the Northeast ocean council dataset:
@@
 
-```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+Map combined with NY, this is what we need (seaweed and shellfish).
+We will extract the data using the methods described below: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
 
-ct_shellfish <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/Shellfish_Bed_Managed_shp/SHELLFISH_BED_MANAGED.shp"))
+Current as of 2019
 
-ct <- counties("Connecticut", cb = TRUE)
+Extract data following these protocols: https://stackoverflow.com/questions/50161492/how-do-i-scrape-data-from-an-arcgis-online-map/50213419#50213419
 
-  ggplot() +
-  geom_sf(data = ct_shellfish, col = "red") + 
-    geom_sf(data = ct, fill = "gray") + 
-  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + 
-    labs(title = "Connecticut data", caption = "Not Comprehensive, General 'approved' areas")
+CT points json: https://services7.arcgis.com/9fAJJI91yoj2y4Yi/arcgis/rest/services/ConnecticutShellfishOnline2018Draft/FeatureServer/0/query?where=0%3D0&outFields=%2A&f=json
+
+CT polygons json: https://services7.arcgis.com/9fAJJI91yoj2y4Yi/arcgis/rest/services/ConnecticutShellfishOnline2018Draft/FeatureServer/1/query?where=0%3D0&outFields=%2A&f=json
+
+Roadmap for polygons
+
+Viewer: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
+
+Item data endpoint (just replace id): https://www.arcgis.com/sharing/rest/content/items/f8799cefbb4c4751a209710d14b9ad46/data
+
+Search for layer you want and grab link ("CT Aquaculture Gear): https://services7.arcgis.com/9fAJJI91yoj2y4Yi/arcgis/rest/services/ConnecticutShellfishOnline2018Draft/FeatureServer/1
+
+Run query using that link to output geojson: https://services7.arcgis.com/9fAJJI91yoj2y4Yi/arcgis/rest/services/ConnecticutShellfishOnline2018Draft/FeatureServer/1/query?where=0%3D0&outFields=%2A&f=geojson
+
+And copy-paste the text in here to save as geojson: https://geojson.io
+
+Check the downloaded geojson file: 
+```{r}
+library(geojsonio)
+spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/CT_Aquaculture_gear/CT_aquaculture_gear.geojson",  what = "sp") %>%
+  st_as_sf()
+
+mapview(spdf)
+
+# library(geojsonio)
+# spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/CT_aquacultre_points/CT_aquaculture_points.geojson",  what = "sp") %>%
+#   st_as_sf()
+# 
+# 
+# plot(spdf)
+# 
+# mapview(spdf)
+
 ```
-
-Another map combined with NY, this is what we need (seaweed and shellfish): https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
-
-### New York
-
- - Lease mapper for Suffolk County: https://gis.suffolkcountyny.gov/portal/apps/View/index.html?appid=6ae708a346f340ada850544fe25ce0fb
-
- - Shellfish map for NY and CT, this seems like what we would need: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
- - Pretty easy to pull lat/lon coordinates from the attribute table on the web map.
- - CT has species and culture type. NY only has shellfish on the map
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/ny_shell.png)
-
-## Maps with no download
-
-### Alabama
-
- - "Alabama has an emerging oyster industry with 13 farms comprising of 25 acres in 2015.
-Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise." from https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
- - This has a map... probably our best source for Alabama!: https://alaquaculture.com/state/#list-of-operating-farms
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/alabama_Farms.png)
 
@@
  - I believe Shellfish is pretty much the only mariculture that occurs in NC. 
- - Has number totals of leases 
- - Will likely need to send an email to NCDEQ
+ - Has number totals of leases.
+ - Download using protocol described for CT.
+ - Current as of 12/21/2021
 
- ![Has lease info for the entire state](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/nc_map.png)
+Roadmap to download
+
+Viewer: https://www.arcgis.com/apps/webappviewer/index.html?id=de86f3bb9e634005b12f69a8a5947367&extent=-8551979.8781%2C4121555.1994%2C-8515290.1046%2C4140072.0696%2C102100
+
+Item data endpoint (just replace id): https://www.arcgis.com/sharing/rest/content/items/de86f3bb9e634005b12f69a8a5947367/data
+
+Search for layer you want and grab link ("Leases" is the layer you want): https://services2.arcgis.com/kCu40SDxsCGcuUWO/arcgis/rest/services/Lease_DB_View/FeatureServer/2
+
+Run query using that link to output geojson: https://services2.arcgis.com/kCu40SDxsCGcuUWO/arcgis/rest/services/Lease_DB_View/FeatureServer/2/query?where=0%3D0&outFields=%2A&f=geojson
+
+And copy-paste the text in here to save as geojson: https://geojson.io. Once it shows in the map, click "Save" and Save as a geojson file.
+
+Check to see if it worked
+```{r}
+library(geojsonio)
+spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/North_Carolina/NC_shellfish_leases.geojson",  what = "sp") %>%
+  st_as_sf()
+
+mapview(spdf)
+
+```
+
+### Rhode Island
+
+ - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
+ - Julia Livermore: julia.livermore@dem.ri.gov
+ - Current as of August 2021
+ - Shellfish and kelp
+
+Roadmap to download
+
+Viewer: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
+
+I found my way to here:
+https://risegis.ri.gov/hosting/rest/services/RIDEM/Marine_Fisheries_Map_Layers/MapServer/0
+
+Then run query using that link to output geojson: https://risegis.ri.gov/hosting/rest/services/RIDEM/Marine_Fisheries_Map_Layers/MapServer/0/query?where=0%3D0&outFields=%2A&f=geojson
+
+And copy-paste the text in here to save as kml (for some reason, saving as geojson was not working for this one): https://geojson.io. Once it shows in the map, click "Save" and Save as a kml file.
+
+Check to see if it worked
+
+```{r}
+
+rhode_island <- read_sf("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Rhode_Island/ri_aq_sites.kml")
+
+mapview(rhode_island)
+
+```
+
+### Alabama
+
+ - "Alabama has an emerging oyster industry with 13 farms comprising of 25 acres in 2015.
+Shellfish farms are a source of healthy protein and can contribute to healthy marine ecosystems by cleaning the water column, providing habitat for other sea life, and helping protect shorelines from storm surges and sea level rise." from https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
+ - This has a map : https://alaquaculture.com/state/#list-of-operating-farms
+ - Here is an even better map with Shellfish leases!: https://aldcnr.maps.arcgis.com/apps/webappviewer/index.html?id=a32dad8dacd249ea86bcb80dd951a424
+
+Roadmap to download
+
+Viewer: https://aldcnr.maps.arcgis.com/apps/webappviewer/index.html?id=a32dad8dacd249ea86bcb80dd951a424
+
+Item data endpoint (just replace id): https://www.arcgis.com/sharing/rest/content/items/a32dad8dacd249ea86bcb80dd951a424/data
+
+Search for layer you want and grab link ("Leases" is the layer you want): https://services7.arcgis.com/jcVUvxpWnajErgCr/arcgis/rest/services/Shellfish_Riparian_Leases_Revised/FeatureServer/0
+
+Run query using that link to output geojson: https://services7.arcgis.com/jcVUvxpWnajErgCr/arcgis/rest/services/Shellfish_Riparian_Leases_Revised/FeatureServer/0/query?where=0%3D0&outFields=%2A&f=geojson
+
+And copy-paste the text in here to save as geojson: https://geojson.io. Once it shows in the map, click "Save" and Save as a geojson file.
+
+Leases current as of: 11/29/2021
+
+```{r}
+library(geojsonio)
+spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alabama/Alabama_Shellfish_Leases.geojson",  what = "sp") %>%
+  st_as_sf()
+
+mapview(spdf)
+
+```
+
+## Maps with no download
 
@@
  ![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/va_map.png)
-
-### Rhode Island
-
- - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
- - No download option.
- - Julia Livermore: julia.livermore@dem.ri.gov
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/rhode_island_map.png)
 
@@
  - 2020 shellfish production report: https://www.oregon.gov/oda/shared/Documents/Publications/FoodSafety/AnnualShellfishProductionReport.pdf
-
-### Maryland
-
-Shellfish
-
- - They have individual lease application maps in PDFs, but they would take forever to go through.
-They must have some sort of internal dataset where they store the approved lease info?: https://dnr.maryland.gov/fisheries/pages/aquaculture/applications.aspx
- - Maude Morris: maudee.morris@maryland.gov
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/maryland_apps.png)
 
@@
 
+### Maryland
+
+Shellfish
+
+ - They have individual lease application maps in PDFs, but they would take forever to go through.
+They must have some sort of internal dataset where they store the approved lease info?: https://dnr.maryland.gov/fisheries/pages/aquaculture/applications.aspx
+ - Maude Morris: maudee.morris@maryland.gov
+
+![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/maryland_apps.png)
+
+List of farms for VA and MD (addresses are on land though): https://oysterrecovery.org/oyster-farms/
+
+Maryland has a viewer for 2013 active leases: https://maryland.maps.arcgis.com/apps/webappviewer/index.html?id=f7db2acc81554601b44c13733a66a60f
+
+ - This viewer has a layer named "ActiveOysterLeases", however, it looks like the last time it was updated is 2013.. I will still download this. Worst case we use this.
+
+I found the layer here: https://gisapps.dnr.state.md.us/arcgis2/rest/services/Biota/ActiveOysterLeases/MapServer/0
+
+Run query using that link to output json (for some reason it won't let me output geojson): https://gisapps.dnr.state.md.us/arcgis2/rest/services/Biota/ActiveOysterLeases/MapServer/0/query?where=0%3D0&outFields=%2A&f=json
+
+```{r include = FALSE}
+
+# test out package to download
+devtools::install_github("yonghah/esri2sf")
+library("esri2sf")
+
+url <- "https://gisapps.dnr.state.md.us/arcgis2/rest/services/Biota/ActiveOysterLeases/MapServer/0"
+df <- esri2sf(url)
+mapview(df)
+
+#st_write(df, file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maryland/maryland_2013_oyster_leases.shp"))
+
+```
+
+```{r echo = FALSE, warning=FALSE, message = FALSE, results = 'hide'}
+md <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maryland/maryland_2013_oyster_leases.shp"))
+```
+
 ### All states
@@
  - https://aop.maps.arcgis.com/apps/Cascade/index.html?appid=e97ddd2cd9cf46218cefeed813e26c87
+ - another link to map? https://aop.maps.arcgis.com/apps/Shortlist/index.html?appid=32864a80775b4f8abaeb072f0718ee57
  - Current as of 2015 
@@
  - Has partial data for other states too
-
-![](/home/sgclawson/github/aquaculture_mapping/marine/united_states/pics/all_states_partial.png)
+ - ask Halley for contact
 
@@
 And even if it wasn't, they most likely haven't even had a harvest since it was legalized (see above article).
+
+### New York
+
+ - According to Halley, there is currently no production in New York state, especially since their coastline is so small.
 
@@
  - They also have data at the county level. I know this wouldn't be perfect, but we could filter for coastal counties.
+
+## Climate stressors for marine aquaculture

### 2022-01-28 workflow/calc_dist_to_port.Rmd
cleaned up scripts and READMEs
updated for resubmission!

@@
 ---
+
+This script calculates an average distance to closest port from all of the known mariculture locations.
 
@@
 
-## ok so that works... i just to calculate the distance from each point in the whole known location dataset, and find the min of each column
+## ok so that works... i just need to calculate the distance from each point in the whole known location dataset, and find the min of each column
 
@@
 
-write.csv(dist_ports, "int/distance_to_ports_raw.csv")
+# write.csv(dist_ports, "int/distance_to_ports_raw.csv")
 
@@
 
-mean(spp_group_dist$closest_port_km) # 31.30463 km
-sd(spp_group_dist$closest_port_km) # 32.333 km
-range(spp_group_dist$closest_port_km) #  0.1312871 to 531.2067646
-median(spp_group_dist$closest_port_km) # 18.85009 km
+mean(spp_group_dist$closest_port_km) # 31.30463 km v1; 39.82486 v2; 39.65138 v3 scotland fix
+sd(spp_group_dist$closest_port_km) # 32.333 km v1; 34.9805 v2; 34.94368 v3
+range(spp_group_dist$closest_port_km) #  0.1312871 to 531.2067646 v1; 0.1309383 533.2698526 v2; 0.1309383 533.2698526 v3
+median(spp_group_dist$closest_port_km) # 18.85009 km v1; 28.56732 v2; 28.33052 v3
 
@@
   group_by(type) %>%
-  summarise(dist_port = mean(closest_port)) %>%
+  summarise(dist_port = mean(closest_port_km)) %>%
   ungroup()

### 2022-01-28 workflow/coast_buffer.R

@@ -40,18 +40,18 @@ data <- read_csv("marine/output/all_marine_farms.csv") %>%
            crs = crs(food_raster), 
            agr = "constant") 
 
-
-data <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
-  st_as_sf(., 
-           coords = c("X", "Y"),
-           crs = crs(food_raster), 
-           agr = "constant") %>%
-  filter(data_type_2 == "A")
+ 
+# data <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
+#   st_as_sf(., 
+#            coords = c("X", "Y"),
+#            crs = crs(food_raster), 
+#            agr = "constant") %>%
+#   filter(data_type_2 == "A")
 
 
 need_validation_allocation <- data %>%
   st_drop_geometry() %>%
-  group_by(iso3c, species_group) %>%
+  group_by(iso3c, type) %>%
   summarise(num_farms = n()) %>%
   ungroup()
 
@@ -137,7 +137,13 @@ for (i in 1:length(unique(need_validation_allocation$iso3c))) {
 # [1] "ARE" "AUS" "BGR" "BLZ" "CAN" "CHL" "CYP" "DNK" "ESP" "FIN" "FRA" "FRO" "GBR" "GRC" "HKG" "IRL" "ITA" "JEY" "MEX"
 # [20] "MLT" "NOR" "PYF" "SAU" "SWE" "USA"
 
+mydir <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/validation_coast_buffer"
+delfiles <- dir(path=mydir ,pattern="*.tif.aux.xml")
+file.remove(file.path(mydir, delfiles))
+
+
 all_coasts <- list.files("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/validation_coast_buffer", pattern = "temp_eez", full.names = TRUE)
+
 
 # all_coasts_stack <- raster::stack(all_coasts)
 # plot(all_coasts_stack[[18]], col = "red")
@@ -147,10 +153,10 @@ allrasters <- lapply(all_coasts, raster)
 
 allrasters$fun <- sum
 
-plot(allrasters[[12]])
+plot(allrasters[[18]])
 
-s <- raster::select(allrasters[[12]])
-plot(s)
+# s <- raster::select(allrasters[[12]])
+# plot(s)
[…]

### 2022-01-28 workflow/place_unknown_farms.R

@@ -62,11 +62,11 @@ arctic_fixed <- raster::resample(arctic_raster, blank_raster, method = "ngb")
 
 arctic_fixed <- inverted_land + arctic_fixed
 arctic_fixed[arctic_fixed[]==2] <- 1 ## add land mask
-
+sf::sf_use_s2(FALSE)
 
 for (i in 1:length(unique(need_national_allocation$iso3c))) {
 
-  # i = 7
+  # i = 2
   ## 1.a get country shape file
   this_iso3 <- unique(need_national_allocation$iso3c)[i]
   
@@ -90,8 +90,7 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
     st_union() %>% # union all touching polygons
     sf::st_as_sf() %>%
     ungroup()
-  #select(GID_0) %>% 
-  
+
   # plot(this_country)
   # class(this_country)
   
@@ -170,9 +169,11 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
   port_test_rast <- dis_to_port_rast
   
   
-  # 31.30463*1000 # 31304.63 meters 
+  # 31.30463*1000 # 31304.63 meters v1
+  # 39.824*1000 = 39824 meters v2
+  # 39.65138*1000 = 39651 meters v3 scotland fix 
   
-  port_test_rast[port_test_rast >31305] <- NA # acceptable distance to port # we are doing 2; the mean (31.305 kilometers) and median (18.850 kilometers) of distance from known locations to ports 
+  port_test_rast[port_test_rast >39651] <- NA # acceptable distance to port # we are doing 2; the mean (31.305 kilometers v1; changed to 39824 for v2; changed to 39651 for v3) 
   port_test_rast[port_test_rast<1000] <- NA # need to be 1km away from ports/shipping lanes
   suitability_rast <- port_test_rast + arctic_fixed # add in arctic mask
   
@@ -319,13 +320,13 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
   }
   
   #UNCOMMENT WHEN SAVING! 
-  write_rds(this_farm_points, paste0("data/temp_data/temp_final_shrimp_fix/temp_farms_", i, ".rds"))
+  write_rds(this_farm_points, paste0("data/temp_data/temp_final_resub_scotland/temp_farms_", i, ".rds"))
   print(paste0(i, " - ",this_iso3, " has been saved"))
[…]

### 2022-01-28 workflow/place_validation_farms.R

@@ -50,31 +50,32 @@ tonnage_per_farms <- read_csv("marine/output/all_points_to_add.csv") %>%
   distinct(type, avg_tonnes_per_farm)
 
 
-data_final <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
-  mutate(type = case_when(species_group == "Salmonidae fish" ~ "salmon",
-                                   species_group == "Unfed or algae fed bivalve molluscs" ~ "bivalve",
-                                   species_group == "Shrimps and prawns" ~ "shrimp", 
-                                 species_group == "Bluefin tuna" ~ "tuna", 
-                                   species_group ==  "General marine fish" ~ "marine_fish_general",
-                          species_group == "Non-shrimp crustaceans" ~ "crustaceans")) %>%
-  filter(data_type_2 == "A") %>%
-  group_by(iso3c, type) %>%
-  summarise(num_farms = n())
-
-sum(data_final$num_farms)
+# data_final <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
+#   mutate(type = case_when(species_group == "Salmonidae fish" ~ "salmon",
+#                                    species_group == "Unfed or algae fed bivalve molluscs" ~ "bivalve",
+#                                    species_group == "Shrimps and prawns" ~ "shrimp", 
+#                                  species_group == "Bluefin tuna" ~ "tuna", 
+#                                    species_group ==  "General marine fish" ~ "marine_fish_general",
+#                           species_group == "Non-shrimp crustaceans" ~ "crustaceans")) %>%
+#   filter(data_type_2 == "A") %>%
+#   group_by(iso3c, type) %>%
+#   summarise(num_farms = n())
+# 
+# sum(data_final$num_farms)
 
 
 need_validation_allocation <- data %>%
   st_drop_geometry() %>%
   group_by(iso3c, type) %>%
   summarise(num_farms = n()) %>%
-  ungroup() %>%
-  group_by(iso3c, type) %>%
-  filter(num_farms %in% c(data_final$num_farms)) %>%
-  filter(iso3c %in% c(data_final$iso3c))
+  ungroup() 
+# 
+# %>%
[…]

### 2022-02-01 analysis/validation_testing.Rmd
added more documentation to some scripts

@@
 
-This script tests our validation set of points against our actual known points.
+## Summary
+
+This script tests conducts an accuracy assessment of our model vs the actual, known mariculture locations.
+
+We try this in two different ways.
+
+1) We compare our random placement of data type A farms into our suitable areas, to the locations of real mariculture locations.
+The analysis conducted uses a confusion matrix, which calculates the AUC (area under the curve) to test the accuracy of the placement of our points.
+However, we decided to not use this portion of the analysis in the final manuscript, because the accuracy assessment which makes more sense is conducted in bullet 2 below.
+
+2) We compare out suitability layer with cells that contain data type A farms.
+This allows us to see how well our suitability layer overlaps with known, comprehensive farms.
+In bullet 1, we compare one instance of randomly placing farms into our suitabiltiy layer with data type A farms.
+I believe if we had ran the model thousands of times, randomly placing data type A farms, it would result in the same conclusion (or something very close) as just comparing our entire suitability layer with data type A farms.
+
+We do each of these analyses at 4 different resolutions.
+The native 0.083 degree resolution that we work with all of the global food rasters at.
+25km2 and 36km2 equal area, and 0.25 degree resolutions.
+This allows us to see how well our model works at different resolutions.
 
@@
 
-## establish CRSs
+```
+
+```{r}
+
+## establish CRSs and read in the EEZ masks
 
@@
 
-Read in validation dataset
+## Method 1: Compare randomly placed farms to real farms
+
+Read in validation dataset.. i.e. the farms that we placed in data type A countries using our modelling technique.
 
@@
 
-Split data
+Split data into real and modelled
 
@@
 
+## Method 2: Compare suitability layer to data type A real farms.
+
 Use our suitability mask to create a confusion matrix for XX degree cell sizes (about 81km2 at equator, ~10km of coastline) with data type A real farms
@@
 ```{r}
+
+## read in the full suitability mask
 
@@
 
+Take a quick look at the gentry files to see what resolution they use. 
 ```{r}

### 2022-02-01 workflow/coast_buffer.R

@@ -40,13 +40,7 @@ data <- read_csv("marine/output/all_marine_farms.csv") %>%
            crs = crs(food_raster), 
            agr = "constant") 
 
- 
-# data <- read_csv("all_marine_aquaculture_farms_sources_31km.csv") %>% 
-#   st_as_sf(., 
-#            coords = c("X", "Y"),
-#            crs = crs(food_raster), 
-#            agr = "constant") %>%
-#   filter(data_type_2 == "A")
+
 
 
 need_validation_allocation <- data %>%
@@ -55,7 +49,7 @@ need_validation_allocation <- data %>%
   summarise(num_farms = n()) %>%
   ungroup()
 
-
+rgdal::setCPLConfigOption("GDAL_PAM_ENABLED", "FALSE") # this line is necessary so you don't write .tif.aux.xml files along with your .tif files. 
 
 for (i in 1:length(unique(need_validation_allocation$iso3c))) {
   
@@ -97,7 +91,7 @@ for (i in 1:length(unique(need_validation_allocation$iso3c))) {
       ms_simplify() 
     
     
-    ## buffer coast 1 mile inland
+    ## buffer coast inland a bit
     this_eez <- st_transform(this_simplified_coast, crs = "+proj=moll") %>% ## transform to a crs that can buffer in meters
       st_buffer(dist = 4000) %>% # buffer in meters km
       st_transform(crs = crs(the_crs))
@@ -137,17 +131,17 @@ for (i in 1:length(unique(need_validation_allocation$iso3c))) {
 # [1] "ARE" "AUS" "BGR" "BLZ" "CAN" "CHL" "CYP" "DNK" "ESP" "FIN" "FRA" "FRO" "GBR" "GRC" "HKG" "IRL" "ITA" "JEY" "MEX"
 # [20] "MLT" "NOR" "PYF" "SAU" "SWE" "USA"
 
-mydir <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/validation_coast_buffer"
-delfiles <- dir(path=mydir ,pattern="*.tif.aux.xml")
-file.remove(file.path(mydir, delfiles))
+## delete aux files if they were created
+# mydir <- "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/validation_coast_buffer"
+# delfiles <- dir(path=mydir ,pattern="*.tif.aux.xml")
[…]

### 2022-02-01 workflow/place_validation_farms.R

@@ -1,4 +1,4 @@
-## This script will place specific number of farms with known locations using our location modelling approach. The resulting dataset will serve as a validation method for our modelling. 
+## This script will place specific number of farms with known locations using our location modelling approach. It will also save our suitability maps for each country with known farms. The resulting files will serve as validation methods for our modelling. 
 
 
 #### load libraries and data ####
@@ -50,30 +50,12 @@ tonnage_per_farms <- read_csv("marine/output/all_points_to_add.csv") %>%
   distinct(type, avg_tonnes_per_farm)
 
 
-# data_final <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
-#   mutate(type = case_when(species_group == "Salmonidae fish" ~ "salmon",
-#                                    species_group == "Unfed or algae fed bivalve molluscs" ~ "bivalve",
-#                                    species_group == "Shrimps and prawns" ~ "shrimp", 
-#                                  species_group == "Bluefin tuna" ~ "tuna", 
-#                                    species_group ==  "General marine fish" ~ "marine_fish_general",
-#                           species_group == "Non-shrimp crustaceans" ~ "crustaceans")) %>%
-#   filter(data_type_2 == "A") %>%
-#   group_by(iso3c, type) %>%
-#   summarise(num_farms = n())
-# 
-# sum(data_final$num_farms)
-
 
 need_validation_allocation <- data %>%
   st_drop_geometry() %>%
   group_by(iso3c, type) %>%
   summarise(num_farms = n()) %>%
   ungroup() 
-# 
-# %>%
-#   group_by(iso3c, type) %>%
-#   filter(num_farms %in% c(data_final$num_farms)) %>%
-#   filter(iso3c %in% c(data_final$iso3c))
 
 sum(need_validation_allocation$num_farms) # 16138
 
@@ -222,6 +204,7 @@ for(i in 1:length(unique(need_validation_allocation$iso3c))) {
   
   suitability_rast_shrimp <- port_test_rast ## save a suitability raster for shrimp placement
   
+  ## comment these out if you want to resave the suitability layers.. only need to do if the distance from port variables change.
   # writeRaster(suitability_rast, paste0("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean/suitability_rast_subset_", this_iso3, ".tif"))
[…]

### 2022-02-01 workflow/place_validation_farms.R
added all countries to suitability mask

@@ -59,6 +59,7 @@ need_validation_allocation <- data %>%
 
 sum(need_validation_allocation$num_farms) # 16138
 
+
 # create arctic raster 
 arctic_raster <- raster("/home/shares/food-systems/Aquaculture_mapping/latitude_abs.tif")
 crs(arctic_raster) <- crs(fake_raster)
@@ -76,6 +77,7 @@ rgdal::setCPLConfigOption("GDAL_PAM_ENABLED", "FALSE")
 
 
 for(i in 1:length(unique(need_validation_allocation$iso3c))) {
+  
   
   # i = 1
   ## 1.a get country shape file
@@ -205,9 +207,8 @@ for(i in 1:length(unique(need_validation_allocation$iso3c))) {
   suitability_rast_shrimp <- port_test_rast ## save a suitability raster for shrimp placement
   
   ## comment these out if you want to resave the suitability layers.. only need to do if the distance from port variables change.
-  # writeRaster(suitability_rast, paste0("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean/suitability_rast_subset_", this_iso3, ".tif"))
-  # writeRaster(suitability_rast_shrimp, paste0("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_and_land/suitability_rast_subset_", this_iso3, ".tif"))
-
+  # writeRaster(suitability_rast, paste0("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean/suitability_rast_subset_", this_iso3, ".tif"), overwrite = TRUE)
+  # writeRaster(suitability_rast_shrimp, paste0("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/ocean_and_land/suitability_rast_subset_", this_iso3, ".tif"), overwrite = TRUE)
   
   if(shrimp_info == "no"){
     
@@ -421,7 +422,7 @@ unique(mos)
 mos[mos == 0] <- NA
 mos[mos >0] <- 1
 
-plot(mos, col = "black")
+plot(mos)
 
 
[…]

### 2022-03-02 analysis/paper_stats.Rmd
cleaned code and updated readme

@@
 ```
-
-Score the different taxa maps for the global food paper:
-
-Score | Spatial Extent | Spatial Resolution | Temporal specificity | System specificity | System comprehensiveness
--- | -- | -- | -- | -- | --
-5 | Represents entire spatial extent of the food system.
-| <= 5 arc minutes | Data is specific to 2017 | The data is reported to the level of our specific food type (e.g.
-cow mixed milk) | Data represents all foods within a system
-4 | Need to gapfill regions with relatively little production (e.g.
-Aland islands) | sub-national or raster with cells larger than 5-arc minutes | Data range includes 2017 and is likely to represent 2017 | Generalized to animal type, but not both rearing system or product (e.g.
-cows mixed) | Data represents majority of foods within a system
-3 | Need to gapfill countries with considerable production (e.g.
-Philippines) | National | Data range doesn't include 2017 and is likely to represent 2017.
-| Generalized to animal type, but not rearing system or product (e.g.
-cows) | Data represents half of foods within a system
-2 | Need to gapfill whole continents/georegions | Georegions | Data range includes 2017 and is unlikely to represent 2017 | Generalized to multiple animal types (e.g.
-cattle/ungulates) | Data represents minority of foods within a system
-1 | Generalized globally using site-level data.
-| Global/generalized | Data is older than 2017 and is unlikely to represent 2017 | Data is generalized across major food system (e.g.
-all reared animals) | Data represents minimum of foods within a system
-NA | Spatial extent is not relevant | Spatial resolution of the data is not relevant | Age of data isn't relevant | Data is not specific to a food system | Data is not specific to a food system
-
-**Salmonids farms map quality**
- - Spatial extent: 4
- - Spatial resolution: 5
- - Temporal specificity: 4
- - System specificity: 2
- - System comprehensiveness: 4
-
-**Tuna farms map quality**
- - Spatial extent: 5
- - Spatial resolution: 5
- - Temporal specificity: 4
- - System specificity: 3
- - System comprehensiveness: 5
-
-**Shrimp farms map quality**
- - Spatial extent: 2
- - Spatial resolution: 5
- - Temporal specificity: 4
- - System specificity: 2
- - System comprehensiveness: 4
-
-**General marine fish farms map quality**
- - Spatial extent: 2
- - Spatial resolution: 5
- - Temporal specificity: 4
- - System specificity: 1
- - System comprehensiveness: 4
-
-**Unfed or algae fed shellfish farms map quality**
- - Spatial extent: 2
- - Spatial resolution: 5
- - Temporal specificity: 4
- - System specificity: 2
- - System comprehensiveness: 4
-
-**Other crustaceans farms map quality**
- - Spatial extent: 1
- - Spatial resolution: 1
- - Temporal specificity: NA
- - System specificity: 1
- - System comprehensiveness: 4

### 2022-03-02 analysis/validation_testing.Rmd
cleaned code and updated readme

--- 2022-01-28 analysis/validation_testing.Rmd
@@
 
-This script tests our validation set of points against our actual known points.
+## Summary
+
+This script tests conducts an accuracy assessment of our model vs the actual, known mariculture locations.
+
+We compare out suitability layer with cells that contain data type A farms.
+This allows us to see how well our suitability layer overlaps with known, comprehensive farms.
+In bullet 1, we compare one instance of randomly placing farms into our suitabiltiy layer with data type A farms.
+I believe if we had ran the model thousands of times, randomly placing data type A farms, it would result in the same conclusion (or something very close) as just comparing our entire suitability layer with data type A farms.
+
+We do these analyses at 4 different resolutions.
+The native 0.083 degree resolution that we work with all of the global food rasters at.
+25km2 and 36km2 equal area, and 0.25 degree resolutions.
+This allows us to see how well our model works at different resolutions.
 
@@
 
-## establish CRSs
-
-## food 81km2 at equator 
-eez_81 <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask.tif"))
-plot(raster::area(eez_81))
-plot(eez_81)
-cellStats(raster::area(eez_81), "mean")
-
-test <- data.frame(raster::values(raster::area(eez_81)))
-
-## 36km2 equal area
-eez_36_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_cea_36km.tif"))
-plot(eez_36_cea)
-
-new_crs <- "+proj=cea +lat_ts=45 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs"
-new_raster <- raster(nrows=3000, ncols=4736, xmn=-14207430, xmx=14208570, ymn=-9000182, ymx=8999818, crs = new_crs)
-
-## 25km2 equal area
-eez_25_cea <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_cea_25km.tif"))
-
-cea_25_crs <- crs(eez_25_cea)
-plot(eez_25_cea)
-
-## 1/4 degree cells 
-eez_quart_cell <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/data_type_A_eez/eez_validation_mask_quarter_degree.tif"))
-
-quarter_crs <- crs(eez_quart_cell)
-
 ```
 
-Read in validation dataset
-
-```{r}
-validation_all <- readRDS(file.path("data/all_validation_farms_resubmission.rds"))  %>%
-  mutate(species_group = case_when(type == "salmon" ~ "Salmonidae fish",
-                          type == "bivalve" ~ "Unfed or algae fed bivalve molluscs",
-                          type == "shrimp" ~ "Shrimps and prawns", 
-                          type == "tuna" ~ "Bluefin tuna", 
-                          type == "marine_fish_general" ~ "General marine fish"))
-
-table_3 <- read_csv("analysis/tables/SI_table_3.csv")
-
-iso <-   data.frame(iso3c = countrycode(table_3$country, origin = 'country.name', destination = 'iso3c'))
-
-table_3_iso3c <- table_3 %>%
-  cbind(iso)
-
-data_type_val <- validation_all %>%
-  left_join(table_3_iso3c, by = c("iso3c", "species_group"))
-
-data_type_A <- data_type_val %>%
- filter(data_type_2 %in% c("A"))
-
-table_3_A <- table_3_iso3c %>%
-  filter(data_type_2 %in% c("A"))
-
-```
-
-Split data
-
-```{r}
-validation_farms <- data_type_A %>%
- filter(source == "modeled validation") %>%
-  mutate(count_farms = 1)
-
-val_farms_cea_36 <- validation_farms %>%
-  st_transform(crs = new_crs)
-
-val_farms_cea_25 <- validation_farms %>%
-  st_transform(crs = cea_25_crs)
-
-val_farms_quarter <- validation_farms %>%
-  st_transform(crs = quarter_crs)
-
-real_farms <- data_type_A %>%
-  filter(source == "real") %>%
-  mutate(count_farms = 1)
-
-real_farms_cea_36 <- real_farms %>%
-  st_transform(crs = new_crs)
-
-real_farms_cea_25 <- real_farms %>%
-  st_transform(crs = cea_25_crs)
-
-real_farms_quart <- real_farms %>%
-  st_transform(crs = quarter_crs)
-```
-
-Rasterize data to count number of farms per raster cell with 36km2 equal area
-
-```{r}
-
-val_rast <- rasterize(val_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
-plot(val_rast)
-
-cellStats(val_rast, "sum") # 8552
-
-plot(val_rast, col = "black")
-#s <- raster::select(val_rast)
-#plot(s)
-
-real_rast <- rasterize(real_farms_cea_36, new_raster, field = "count_farms", fun = "sum")
-plot(real_rast)
-
-cellStats(real_rast, "sum") # 8552
-plot(real_rast, col = "black")
-
-rast_stack <- stack(val_rast, real_rast)
-cellStats(rast_stack, "sum")
-
-# layer.1 layer.2 
-#    8552    8552
-
-```
-
-Use our EEZ mask to create a confusion matrix for CEA 36km2 cell sizes
-
- - AUC of ~0.60
-```{r}
-
-plot(eez_36_cea, col = "black")
-
-world_coast <- as.data.frame(eez_36_cea) %>%
-  mutate(cell = row_number()) %>%
-  filter(!is.na(eez_validation_mask_cea_36km))
-
-eez_cells_df <- as.data.frame(rast_stack) %>%
-  rename("predicted" = "layer.1", "real" = "layer.2") %>%
-  mutate(pred_count = ifelse(predicted >=1, 1, 0),
-         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
-  mutate(real_count = ifelse(real>=1,1,0)) %>%
-  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
-         real_count = ifelse(is.na(real_count), 0, real_count), 
-         real = ifelse(is.na(real), 0, real),
-         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
-  mutate(cell = row_number()) %>% 
-  filter(cell %in% c(world_coast$cell))
-
-sum(eez_cells_df$predicted, na.rm = TRUE) # 8535
-
-sum(eez_cells_df$real, na.rm = TRUE) # 8473
-
-## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms
-
-test <- rast_stack*eez_36_cea
-
-cellStats(test,"sum") 
-# layer.1 layer.2 
-#    8535    8473
-
-## we are losing some farms...
-
-#### make a confusion matrix
-
-confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
-
-confusion_mat
-
-# Confusion Matrix and Statistics
-#           Reference
-# Prediction       0       1
-#          0 1171909    2552
-#          1    2721     682
-#                                           
-#                Accuracy : 0.9955          
-#                  95% CI : (0.9954, 0.9956)
-#     No Information Rate : 0.9973          
-#     P-Value [Acc > NIR] : 1.00000         
-#                                           
-#                   Kappa : 0.2033          
-#                                           
-#  Mcnemar's Test P-Value : 0.02069         
-#                                           
-#             Sensitivity : 0.9977          
-#             Specificity : 0.2109          
-#          Pos Pred Value : 0.9978          
-#          Neg Pred Value : 0.2004          
-#              Prevalence : 0.9973          
-#          Detection Rate : 0.9949          
-#    Detection Prevalence : 0.9971          
-#       Balanced Accuracy : 0.6043          
-#                                           
-#        'Positive' Class : 0
-
-# library(pROC)
-# roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE) # 0.6019
-# 
-# 
-# library(pROC)
-# library(randomForest)
-# 
-# 
-# roc(eez_cells_df$real_count, eez_cells_df$pred_count, plot = TRUE, percent = TRUE, xlab = "False Positive Percentage", ylab = "True Positive Percentage", col = "#377eb8", lwd = 4, print.auc = TRUE) # 0.6068
-# 
-# roc.info <- roc(eez_cells_df$real_count, eez_cells_df$pred_count, legacy.axes = TRUE)
-# 
-# roc.df <- data.frame(tpp = roc.info$sensitivities*100,
-#                      fpp = (1-roc.info$specificities)*100,
-#                      thresholds = roc.info$thresholds)
-# 
-# 
-# #### ROC curve try #2
-# # https://www.datatechnotes.com/2019/03/how-to-create-roc-curve-in-r.html
-# 
-# library(ROCR)
-#   
-#  
-# pred = eez_cells_df$pred_count
-# 
-# pred = prediction(pred, eez_cells_df$real_count)
-# 
-# perf = performance(pred, "acc")
-# plot(perf)
-# 
-# perf_cost <- performance(pred, "cost")
-# plot(perf_cost)
-# 
-# roc = performance(pred, "tpr", "fpr")
-# 
-# plot(roc, colorize = T, lwd=2)
-# abline(a=0, b=1)
-# 
-# auc = performance(pred, measure = "auc")
-# print(auc@y.values)
-# # 0.6091016
-
-```
-
-Use our EEZ mask to create a confusion matrix for CEA 25km2 cell sizes
-
- - AUC of ~0.59 - worse than 36km2... makes sense! 
-```{r}
-
-val_rast <- rasterize(val_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
-plot(val_rast)
-
-cellStats(val_rast, "sum")
-
-plot(val_rast, col = "black")
-#s <- raster::select(val_rast)
-#plot(s)
-
-real_rast <- rasterize(real_farms_cea_25, eez_25_cea, field = "count_farms", fun = "sum")
-plot(real_rast)
-
-cellStats(real_rast, "sum") # 8552
-plot(real_rast, col = "black")
-
-rast_stack <- stack(val_rast, real_rast)
-cellStats(rast_stack, "sum")
-
-# layer.1 layer.2 
-#    8552    8552
-
-plot(eez_25_cea, col = "black")
-
-world_coast <- as.data.frame(eez_25_cea) %>%
-  mutate(cell = row_number()) %>%
-  filter(!is.na(eez_validation_mask_cea_25km))
-
-eez_cells_df <- as.data.frame(rast_stack) %>%
-  rename("predicted" = "layer.1", "real" = "layer.2") %>%
-  mutate(pred_count = ifelse(predicted >=1, 1, 0),
-         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
-  mutate(real_count = ifelse(real>=1,1,0)) %>%
-  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
-         real_count = ifelse(is.na(real_count), 0, real_count), 
-         real = ifelse(is.na(real), 0, real),
-         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
-  mutate(cell = row_number()) %>% 
-  filter(cell %in% c(world_coast$cell))
-
-sum(eez_cells_df$predicted, na.rm = TRUE) # 8536
-
-sum(eez_cells_df$real, na.rm = TRUE) # 8482
-
-## still missing some farms.. but nothing egregious. This is probably ok. The results wouldn't change much even if we had the extra ~80 farms. This is likely due to reprojection weirdness
-
-test <- rast_stack*eez_25_cea
-
-cellStats(test,"sum") 
-# layer.1 layer.2 
-#    8536    8482
-
-#### make a confusion matrix
-
-confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
-
-confusion_mat
-
-# Confusion Matrix and Statistics
-# 
-#           Reference
-# Prediction       0       1
-#          0 1689310    2929
-#          1    3100     639
-#                                           
-#                Accuracy : 0.9964          
-#                  95% CI : (0.9964, 0.9965)
-#     No Information Rate : 0.9979          
-#     P-Value [Acc > NIR] : 1.00000         
-#                                           
-#                   Kappa : 0.1731          
-#                                           
-#  Mcnemar's Test P-Value : 0.02857         
-#                                           
-#             Sensitivity : 0.9982          
-#             Specificity : 0.1791          
-#          Pos Pred Value : 0.9983          
-#          Neg Pred Value : 0.1709          
-#              Prevalence : 0.9979          
-#          Detection Rate : 0.9961          
-#    Detection Prevalence : 0.9978          
-#       Balanced Accuracy : 0.5886          
-#                                           
-#        'Positive' Class : 0
-
-```
-
-Use our EEZ mask to create a confusion matrix for 0.25 X 0.25 degree cell sizes (about 769.3152km2 at equator). Average cell size is 490.3108 km2
-
- - AUC of ~72.05 ; makes sense that is it better!
-
-```{r}
-test <- raster::area(eez_quart_cell)
-
-cellStats(test, "mean") # 490.3108
-
-mean(test@data@values) # 490.3108
-
-val_rast <- rasterize(val_farms_quarter, eez_quart_cell, field = "count_farms", fun = "sum")
-plot(val_rast)
-
-cellStats(val_rast, "sum")
-
-plot(val_rast, col = "black")
-
-real_rast <- rasterize(real_farms_quart, eez_quart_cell, field = "count_farms", fun = "sum")
-plot(real_rast)
-
-cellStats(real_rast, "sum") # 8552
-plot(real_rast, col = "black")
-
-rast_stack <- stack(val_rast, real_rast)
-cellStats(rast_stack, "sum")
-
-# layer.1 layer.2 
-#    8552    8552
-
-plot(eez_quart_cell, col = "black")
-
-world_coast <- as.data.frame(eez_quart_cell) %>%
-  mutate(cell = row_number()) %>%
-  filter(!is.na(eez_validation_mask_quarter_degree))
-
-eez_cells_df <- as.data.frame(rast_stack) %>%
-  rename("predicted" = "layer.1", "real" = "layer.2") %>%
-  mutate(pred_count = ifelse(predicted >=1, 1, 0),
-         real_mod_count = ifelse(predicted >=1&real>=1, 1, 0)) %>%
-  mutate(real_count = ifelse(real>=1,1,0)) %>%
-  mutate(pred_count = ifelse(is.na(pred_count), 0, pred_count),
-         real_count = ifelse(is.na(real_count), 0, real_count), 
-         real = ifelse(is.na(real), 0, real),
-         predicted = ifelse(is.na(predicted), 0, predicted)) %>%
-  mutate(cell = row_number()) %>% 
-  filter(cell %in% c(world_coast$cell))
-
-sum(eez_cells_df$predicted, na.rm = TRUE) # 8124
-
-sum(eez_cells_df$real, na.rm = TRUE) # 8173
-
-## still missing some farms..
-
-test <- rast_stack*eez_quart_cell
-
-cellStats(test,"sum") 
-# layer.1 layer.2 
-#    8124    8173
-
-#### make a confusion matrix
-
-confusion_mat <- caret::confusionMatrix(data = as.factor(eez_cells_df$pred_count), reference = as.factor(eez_cells_df$real_count))
-
-confusion_mat
-
-# Confusion Matrix and Statistics
-# 
-#           Reference
-# Prediction     0     1
-#          0 84570   639
-#          1   902   514
-#                                           
-#                Accuracy : 0.9822          
-#                  95% CI : (0.9813, 0.9831)
-#     No Information Rate : 0.9867          
-#     P-Value [Acc > NIR] : 1               
-#                                           
-#                   Kappa : 0.3912          
-#                                           
-#  Mcnemar's Test P-Value : 2.486e-11       
-#                                           
-#             Sensitivity : 0.9894          
-#             Specificity : 0.4458          
-#          Pos Pred Value : 0.9925          
-#          Neg Pred Value : 0.3630          
-#              Prevalence : 0.9867          
-#          Detection Rate : 0.9763          
-#    Detection Prevalence : 0.9837          
-#       Balanced Accuracy : 0.7176          
-#                                           
-#        'Positive' Class : 0
-
-```
+## Method: Compare suitability layer to data type A real farms.
 
@@
 ```
-
-```{r}
-# gentry <- raster(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/suitability_rasts/gentry/karakoenig"))
-```

### 2022-03-02 marine/compile_data_for_placement.Rmd
cleaned code and updated readme

@@
 ---
+
+This script compiles all of the location data and the modeling information data into two datasets:
+
+ - all_marine_farms.csv : Lat/Lon locations of all known marine aquaculture farms globally.
+ - all_points_to_add.csv : Number of farms per each species group to place in suitable areas, within each country.
 

### 2022-03-02 marine/last_step_rasterize/shrimp_rasterize_production.Rmd
cleaned code and updated readme

@@
 plot(log(shrimp_raster + 1))
+cellStats(shrimp_raster, "sum")
 
@@
 
+writeRaster(shrimp_raster, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/production/rasters/shrimp_production_rast.tif")
 ```

### 2022-03-02 _spatial/create_world_maps.R

@@ -5,10 +5,6 @@
 ## Author  :  Gordon Blasco
 #------------------------------------------------------------------------------#
 
-# Outputs:
-#
-#
-
 
 #### Create Coastline ####
 #------------------------------------------------------------------------------#
@@ -57,66 +53,9 @@ writeRaster(eez_mask, "/home/shares/food-systems/Food_footprint/_raw_data/Aquacu
             overwrite=TRUE)
 
 
-#### distance to port raster ####
-#------------------------------------------------------------------------------#
-ports_points <- st_read("/home/shares/clean-seafood/raw_data/ports_data/Commercial_ports.shp") %>% 
-  as("Spatial")
-
-ports_dist_raster <- distanceFromPoints(fake_raster, ports_points)
-writeRaster(ports_dist_raster, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/dist_to_ports_raster.tiff",
-            overwrite=TRUE)
 
 
 
-grid = sf::st_as_sf(fake_raster, as_points = TRUE)
-grid$NDVI = NULL
-grid
 
-
-pol_sp = as(fake_raster, "SpatialPolygonsDataFrame")
-pol = st_as_sf(pol_sp)
-dist <- st_distance(pol, coastline)
-saveRDS(dist, "distance_matrix.rds")
-#### dissolve eez ####
-#------------------------------------------------------------------------------#
-gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
-
-all <- gadm_full %>% 
-  filter(GID_0 == "CHN") %>% 
-  group_by(GID_0) %>% 
-  st_union() %>% # union all touching polygons
-  sf::st_as_sf() #%>%
-  #select(GID_0) %>% 
   
 
-chin <- eez_sf %>% 
-  filter(ISO_Ter1 == "CHN") %>% 
-  group_by(ISO_Ter1)%>% 
-  st_union() %>% 
-  sf::st_as_sf() %>% 
-  ungroup() %>% 
-  bind_rows(all) 
-
-
-
-chin_mask <- chin %>% 
-  fasterize::fasterize(food_raster)
-
-bathy_prep <- bathy_raw %>% 
-  projectRaster(to = food_raster)
-
-x <- chin_mask*bathy_prep
-plot(x)
-
-test <- chin %>% 
-  ungroup() %>% 
[…]

### 2022-03-02 archive/marine_mapping_OLD_v1/salmon/salmon_farm/R/fao_mar_clean.R

@@ -1,27 +1,0 @@
-mar_split <- function(m) {
-  ### Deal with special cases of countries, specific to MAR: Netherlands Antilles reported multiple ways, including 'Bonaire/S.Eustatius/Saba' 
-  ### - fao_major_area reports 'Antilles' as one region, but OHI considers as four 
-  ###   reported regions; break up and distribute values 
-  
-# Currently only marine aquaculture in this region, and only Montenegro has a coastline   
- m <- m %>% 
-    mutate(country = ifelse(country=='Serbia and Montenegro' & environment %in% c("Marine", "Brackishwater"), "Montenegro", country))
-    
-  m_channel <- m %>%
-    filter(country == 'Channel Islands') %>%
-    mutate(
-      value            = value/2,
-      'Guernsey'        = value,
-      'Jersey'           = value) %>%
-    select(-value, -country) %>%
-    gather(country, value, -species, -fao_major_area, -environment, -year) %>%
-    mutate(country = as.character(country))  
-  m <- m %>%
-    filter(country != 'Channel Islands') %>%
-    bind_rows(m_channel) %>%  
-    arrange(country, fao_major_area, environment, species, year, value) 
-  
-  
-  return(m)
-}
-

### 2022-03-02 workflow/coast_buffer.R

@@ -1,230 +1,0 @@
-## This script will buffer the coastline of each place which has known locations and save each as a file. When it is done it will compile them all together and rasterize.
-## We will use this raster to validate our model. 
-
-#### load libraries and data ####
-#------------------------------------------------------------------------------#
-library(sf)
-library(spatialEco)
-library(tidyverse)
-library(raster)
-library(rgeos)
-library(rmapshaper)
-library(mapview)
-library(fasterize)
-
-# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
-source("./_spatial/template_raster.R")
-gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
-gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
-land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
-eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
-eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
-coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
-
-
-inverted_land <- land_mask
-inverted_land[is.na(inverted_land[])] <- .5
-inverted_land[inverted_land[]==1] <- NA
-inverted_land[inverted_land[]==.5] <- 1
-
-blank_raster <- food_raster
-blank_raster[] <- 1
-
-the_crs <- crs(fake_raster, asText = TRUE)
-
-
-
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
-           agr = "constant") 
-
-
-
-
-need_validation_allocation <- data %>%
-  st_drop_geometry() %>%
-  group_by(iso3c, type) %>%
-  summarise(num_farms = n()) %>%
[…]

### 2022-03-02 workflow/place_unknown_farms.R

@@ -169,11 +169,9 @@ for (i in 1:length(unique(need_national_allocation$iso3c))) {
   port_test_rast <- dis_to_port_rast
   
   
-  # 31.30463*1000 # 31304.63 meters v1
-  # 39.824*1000 = 39824 meters v2
   # 39.65138*1000 = 39651 meters v3 scotland fix 
   
-  port_test_rast[port_test_rast >39651] <- NA # acceptable distance to port # we are doing 2; the mean (31.305 kilometers v1; changed to 39824 for v2; changed to 39651 for v3) 
+  port_test_rast[port_test_rast >39651] <- NA # acceptable distance to port # we are doing 2; the mean (changed to 39651 for v3) 
   port_test_rast[port_test_rast<1000] <- NA # need to be 1km away from ports/shipping lanes
   suitability_rast <- port_test_rast + arctic_fixed # add in arctic mask
   
@@ -333,10 +331,6 @@ all_farms <- list.files("data/temp_data/temp_final_resub_scotland", pattern = "r
   rbind(data %>% dplyr::mutate(source = "real")) %>% 
   left_join(tonnage_per_farms)
 
-test <- all_farms %>%
-  filter(iso3c == "USA")
-
-mapview(test, zcol = "source")
 
 test <- all_farms %>%
   filter(type == "shrimp", 

### 2022-03-02 workflow/place_validation_farms.R

@@ -1,488 +1,0 @@
-## This script will place specific number of farms with known locations using our location modelling approach. It will also save our suitability maps for each country with known farms. The resulting files will serve as validation methods for our modelling. 
-
-
-#### load libraries and data ####
-#------------------------------------------------------------------------------#
-library(sf)
-library(spatialEco)
-library(tidyverse)
-library(raster)
-library(rgeos)
-library(rmapshaper)
-library(mapview)
-
-# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
-source("./_spatial/template_raster.R")
-gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
-gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
-land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
-eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
-eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
-coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
-
-
-inverted_land <- land_mask
-inverted_land[is.na(inverted_land[])] <- .5
-inverted_land[inverted_land[]==1] <- NA
-inverted_land[inverted_land[]==.5] <- 1
-
-blank_raster <- food_raster
-blank_raster[] <- 1
-
-the_crs <- crs(fake_raster, asText = TRUE)
-
-
-## New port data for 2019
-ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/d2019/WPI.shp") %>%
-  st_transform(the_crs) %>%
-  filter(HARBORSIZE != "L", # filter out large ports 
-         HARBORTYPE != "LC") # filter out lake or canals
-
-
-
-data <- read_csv("marine/output/all_marine_farms.csv") %>% 
-  st_as_sf(., 
-           coords = c("lon", "lat"),
-           crs = crs(food_raster), 
[…]

### 2022-03-02 workflow/save_suitability_layer.R

@@ -1,0 +1,310 @@
+## This script will save our suitability maps for each country with known farms. The resulting file will serve as validation methods for our modelling. 
+
+
+#### load libraries and data ####
+#------------------------------------------------------------------------------#
+library(sf)
+library(spatialEco)
+library(tidyverse)
+library(raster)
+library(rgeos)
+library(rmapshaper)
+library(mapview)
+
+# load in crs, coastlines, eez, masks, country shapes, ports, depth, and rasters
+source("./_spatial/template_raster.R")
+gadm_diss <- st_read("/home/shares/food-systems/Global_datasets/World_map/World_ISO_dissolve.shp")
+gadm_full <- st_read("/home/shares/food-systems/Global_datasets/World_map/gadm36.shp")
+land_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/land_mask.tif")
+eez_mask <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/eez_mask.tif")
+eez_sf <- st_read("/home/shares/food-systems/Global_datasets/EEZ/eez_v10.shp")
+coastline <- readRDS("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline.rds")
+
+
+inverted_land <- land_mask
+inverted_land[is.na(inverted_land[])] <- .5
+inverted_land[inverted_land[]==1] <- NA
+inverted_land[inverted_land[]==.5] <- 1
+
+blank_raster <- food_raster
+blank_raster[] <- 1
+
+the_crs <- crs(fake_raster, asText = TRUE)
+
+
+## New port data for 2019
+ports_raw <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/world_port_index/d2019/WPI.shp") %>%
+  st_transform(the_crs) %>%
+  filter(HARBORSIZE != "L", # filter out large ports 
+         HARBORTYPE != "LC") # filter out lake or canals
+
+
+
+data <- read_csv("marine/output/all_marine_farms.csv") %>% 
+  st_as_sf(., 
+           coords = c("lon", "lat"),
+           crs = crs(food_raster), 
[…]

### 2022-03-02 marine/bivalve/bivalve_farms/STEP2_bivalve_farm_locations.Rmd
cleaned code even more and updated README

@@
 library(countrycode)
+# library(remotes)
+# install_github("yonghah/esri2sf")
+library("esri2sf")
 
@@
 
-Based on the two datasets below, we have an existing 1010 bivalve farms. We need to add 193 points to existing 1010 (a final total of 1203 points)
+Based on the datasets below, we have an existing 1010 bivalve farms. We need to add 193 points to existing 1010 (a final total of 1203 points)
 
@@
 ```{r}
-maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))
+maine_aq_lease <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_AQ_Leases/MaineDMR_Aquaculture_AQ_Leases.shp")
 
@@
  - Lease map here: https://ridemgis.maps.arcgis.com/apps/webappviewer/index.html?id=8beb98d758f14265a84d69758d96742f
- - Julia Livermore: julia.livermore@dem.ri.gov
  - Current as of August 2021
@@
 ```{r}
-rhode_island <- read_sf("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Rhode_Island/ri_aq_sites.kml")
+rhode_island <- esri2sf("https://risegis.ri.gov/hosting/rest/services/RIDEM/Marine_Fisheries_Map_Layers/MapServer/0")
+mapview(rhode_island)
 
@@
 ```{r}
-library(geojsonio)
-spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/North_Carolina/NC_shellfish_leases.geojson",  what = "sp") %>%
-  st_as_sf()
-
-unique(spdf$Status)
-
-nc_active <- spdf %>%
+url <- "https://services2.arcgis.com/kCu40SDxsCGcuUWO/arcgis/rest/services/Lease_DB_View/FeatureServer/2"
+nc_shellfish <- esri2sf(url)
+
+nc_active <- nc_shellfish %>%
   filter(Status %in% c("Active", "Approved")) # 423 active leases... wow!
@@
 
-```{r}
-library(geojsonio)
-spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Connecticut/CT_Aquaculture_gear/CT_aquaculture_gear.geojson",  what = "sp") %>%
+Roadmap for polygons
+
+Viewer: https://www.arcgis.com/apps/webappviewer/index.html?id=f8799cefbb4c4751a209710d14b9ad46
+
+Item data endpoint (just replace id): https://www.arcgis.com/sharing/rest/content/items/f8799cefbb4c4751a209710d14b9ad46/data
+
+Search for layer you want and grab link ("CT Aquaculture Gear): https://services7.arcgis.com/9fAJJI91yoj2y4Yi/arcgis/rest/services/ConnecticutShellfishOnline2018Draft/FeatureServer/1
+
+Now download using esri2sf R package.
+
+```{r}
+
+url <- "https://services7.arcgis.com/9fAJJI91yoj2y4Yi/arcgis/rest/services/ConnecticutShellfishOnline2018Draft/FeatureServer/1"
+ct_shellfish <- esri2sf(url) %>%
   st_as_sf() %>%
@@
 
-mapview(spdf)
-
-us_ct_bivalve_mol <- st_transform(spdf, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
+mapview(ct_shellfish)
+
+us_ct_bivalve_mol <- st_transform(ct_shellfish, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
 us_ct_bivalve_pts <- st_centroid(us_ct_bivalve_mol)
@@
 
-```{r}
-library(geojsonio)
-spdf <- geojson_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Alabama/Alabama_Shellfish_Leases.geojson",  what = "sp") %>%
+Roadmap to download
+
+Viewer: https://aldcnr.maps.arcgis.com/apps/webappviewer/index.html?id=a32dad8dacd249ea86bcb80dd951a424
+
+Item data endpoint (just replace id): https://www.arcgis.com/sharing/rest/content/items/a32dad8dacd249ea86bcb80dd951a424/data
+
+Search for layer you want and grab link ("Leases" is the layer you want): https://services7.arcgis.com/jcVUvxpWnajErgCr/arcgis/rest/services/Shellfish_Riparian_Leases_Revised/FeatureServer/0
+
+Download using esri2sf
+
+```{r}
+
+al_oyster <- esri2sf("https://services7.arcgis.com/jcVUvxpWnajErgCr/arcgis/rest/services/Shellfish_Riparian_Leases_Revised/FeatureServer/0") %>%
   st_as_sf() %>%
@@
 
-mapview(spdf)
-
-us_al_bivalve_mol <- st_transform(spdf, crs = "+init=epsg:3035") # convert to equal area projealion to find centroids. 
+mapview(al_oyster)
+
+us_al_bivalve_mol <- st_transform(al_oyster, crs = "+init=epsg:3035") # convert to equal area projealion to find centroids. 
 us_al_bivalve_pts <- st_centroid(us_al_bivalve_mol)
@@
          subregion = "Alabama") 
-```
-
-## US Northeast - NY, CT, ME, NH
-
- Only used this for exploration
- - Regional Ocean Council 2018
-
-Source: 
-Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 2020] https://www.northeastoceandata.org/data-download/
-
-```{r}
-
-# us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))
-# 
-# unique(us_ne$allSpecies)
-# 
-# unique(fao_bivalve_spp$species)
-# 
-# ## need to filter allSpecies for anything with "Oyster", "Mussel", "Shellfish", "Clam", "Quahog", 
-# 
-# # id bivalves and active sites
-# bivalve_species <- grep("Oyster|Mussel|Shellfish|Clam|Quahog", unique(us_ne$allSpecies), value=TRUE)
-# 
-# 
-# us_ne_bivalve <- us_ne %>%
-#   filter(allSpecies %in% bivalve_species) %>%
-#   filter(status == "Active")
-# unique(us_ne_bivalve$state)
-# 
-# us_ne_bivalve_mol <- st_transform(us_ne_bivalve, crs = "+init=epsg:3035") # convert to equal area projection to find centroids. 
-# us_ne_bivalve_pts <- st_centroid(us_ne_bivalve_mol)
-# # check
-# plot(st_geometry(us_ne_bivalve_mol))
-# plot(st_geometry(st_centroid(us_ne_bivalve_mol)), add=TRUE)
-# 
-# us_ne_bivalve_pts_latlon <- st_transform(us_ne_bivalve_pts, crs = "+init=epsg:4326") 
-# 
-# farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_bivalve_pts_latlon))) # get lat lon
-# names(farms_us_ne) <- c("lon", "lat") 
-# farms_us_ne <- farms_us_ne %>%
-#   mutate(iso3c = "USA") %>%
-#   mutate(data_quality = 4) 
-# 
-# # all_farms_sf <- st_as_sf(farms_us_ne, coords = c("lon", "lat"), 
-# #                          crs = crs(gadm_latlon), agr = "constant")
-# # 
-# # mapview(all_farms_sf)
-
 ```

### 2022-03-02 marine/salmon/salmon_farms/STEP2_salmon_farm_locations.Rmd
cleaned code even more and updated README

@@
 
-# United States
-Salmon aquaculture occurs along the Atlantic coast and in Puget sound.
-
-Puget Sound data (2018 data): http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/
-
-## Puget Sound
-
-Source: 
-Our Sound, Our Salmon, 2017. [Accessed January 31, 2020] http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/
-
- - NOT comprehensive, existing points need gapfilling
-
-```{r}
-
-farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
-  mutate(iso3c = "USA") %>%
-  dplyr::select(lon, lat, iso3c) %>%
-  mutate(data_quality = 2) %>%
-  mutate(subregion = "Washington")
-
-write_csv(farms_ps, here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5/farms_ps_usa.csv"))
-
-```
-
-## US Northeast
-DEPRECATED:
-Source:
-Northeast Regional Ocean Council, 2018. Northeast ocean data: aquaculture. [Accessed January 17, 2020]
-
- - NOT comprehensive, existing points need gapfilling
-
-```{r}
-
-# us_ne <- st_read(file.path(path,"USA/NE/US_NE_Aquaculture.shp"))
-# 
-# 
-# # id salmon and active sites
-# salmon_species <- grep("Salmon|salmon", unique(us_ne$allSpecies), value=TRUE)
-# 
-# us_ne_salmon <- us_ne %>%
-#   filter(allSpecies %in% salmon_species) %>%
-#   filter(status == "Active")
-# 
-# us_ne_salmon_mol <- st_transform(us_ne_salmon, crs = "+init=epsg:3035") # convert to equal area projection to find centroids.
-# us_ne_salmon_pts <- st_centroid(us_ne_salmon_mol)
-# # check
-# plot(st_geometry(us_ne_salmon_mol))
-# plot(st_geometry(st_centroid(us_ne_salmon_mol)), add=TRUE)
-# 
-# us_ne_salmon_pts_latlon <- st_transform(us_ne_salmon_pts, crs = "+init=epsg:4326")
-# 
-# farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon)))
-# names(farms_us_ne) <- c("lon", "lat")
-# farms_us_ne <- farms_us_ne %>%
-#   mutate(iso3c = "USA") %>%
-#   mutate(data_quality = 2)
-# 
-# write_csv(farms_us_ne, here("marine/salmon/salmon_farm/data/known_farm_sites_2_4_5/farms_ne_usa.csv"))
-
-```
-
 # New Zealand
@@
 
-Locations of aquaculture leases in Maine, 2019. Maine Department of Marine Resources. https://dmr-maine.opendata.arcgis.com/datasets/maine::mainedmr-aquaculture-aq-leases/about
+Locations of aquaculture leases in Maine, 2019. Maine Department of Marine Resources. 
+ - Viewer: https://maine.maps.arcgis.com/apps/webappviewer/index.html?id=b846cf37b1d64c988f89eafa085c8b7a
+ - Download: https://dmr-maine.opendata.arcgis.com/datasets/maine::mainedmr-aquaculture-aq-leases/about
+ - We will want to use regular leases only.
+ - Limited purpose leases are for scientific or smaller/shorter term mariculture projects, that last up to 3 years.
+ - I think this can be considered "comprehensive". 
+ - Update to date as of download date
+ - Has species types specified.
+
+ - geojson API link for download: https://opendata.arcgis.com/datasets/a0b3c775cfc243a2b92df328ad85c642_2.geojson
 
 ```{r}
-maine_aq_lease <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_-_AQ_Leases/MaineDMR_Aquaculture_-_AQ_Leases.shp"))
+me_geojson <- geojson_read("https://opendata.arcgis.com/datasets/a0b3c775cfc243a2b92df328ad85c642_2.geojson",  what = "sp") %>% st_as_sf() %>%
+  mutate(download_date = date, 
+         data_year = year) %>%
+  clean_names()
+mapview(me_geojson)
+
+#st_write(me_geojson, "/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_AQ_Leases/MaineDMR_Aquaculture_AQ_Leases.shp", delete_dsn = TRUE)
+
+maine_aq_lease <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/USA/Maine/MaineDMR_Aquaculture_AQ_Leases/MaineDMR_Aquaculture_AQ_Leases.shp")
 
@@
 
+## Puget Sound
+
+Source: 
+Our Sound, Our Salmon, 2017. [Accessed January 31, 2020] http://www.moldychum.com/violations-prompt-washington-state-cancel-atlantic-salmon-farm-lease/
+
+ - NOT comprehensive, existing points need gapfilling
+
+```{r}
+
+farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
+  mutate(iso3c = "USA") %>%
+  dplyr::select(lon, lat, iso3c) %>%
+  mutate(data_quality = 2) %>%
+  mutate(subregion = "Washington")
+
+write_csv(farms_ps, here("marine/salmon/salmon_farms/data/known_farm_sites_2_4_5/farms_ps_usa.csv"))
+
+```
+
 # Join cell count dataframes
